### 2018-04-27 paper.tex
First commit

\documentclass[oneside, 10pt]{amsart}
\usepackage[breaklinks=true]{hyperref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{enumitem}

\addbibresource{lemma.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\rk}{rk}
\newcommand{\XX}[1]{\mathcal{X}_{#1}}
\newcommand{\RR}[1]{\mathcal{R}_{#1}}

\newtheorem{thm}{Theorem}
\Crefname{thm}{Theorem}{Theorems}
\numberwithin{equation}{section}

\newtheorem{lem}{Lemma}
\numberwithin{lem}{section}
\Crefname{lemma}{Lemma}{Lemmas}

\newtheorem{cor}[lem]{Corollary}
\Crefname{cor}{Corollary}{Corollaries}

\newtheorem{prop}[lem]{Proposition}
\Crefname{prop}{Proposition}{Propositions}

\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}

\theoremstyle{definition}

\newtheorem{def}[lem]{Definition}
\Crefname{def}{Definition}{Definitions}
\newtheorem{example}[lem]{Example}
\Crefname{example}{Example}{Examples}

\theoremstyle{remark}

\newtheorem{rem}[lem]{Remark}
\Crefname{rem}{Remark}{Remarks}

\title{On $K_2$-analogue of Serre problem for $\SL_4$}
\keywords {Steinberg group, $K_2$-functor, Serre problem
 {\em Mathematical Subject Classification (2010):} 19C20}
\author {Sergey Sinchuk}
\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
\email {sinchukss at gmail.com}
\date {\today}

\begin{document}   
\maketitle

\section{Introduction}

\section{Preliminaries}

\section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}

\section{Proof of the main result}

\subsection{Structure theorem for Steinberg groups}
The aim of section is to formulate sufficient conditions implying the main structure result for Steinberg groups

Let $\mu$ be a microweight of the root system $\Phi$. Denote by $N_\mu$
\begin{def}

\end{def}

\printbibliography
\end{document}

### 2018-04-27 paper.tex
Minor

@@
 
-\newtheorem{def}[lem]{Definition}
+%\newtheorem{def}[lem]{Definition}
 \Crefname{def}{Definition}{Definitions}
@@
 
+\subsection{Steinberg groups and relative Steinberg groups}
+
+\subsection{Rehmann-Soule theorem}
+
 \section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}
@@
 
-\subsection{Structure theorem for Steinberg groups}
+\subsection{General structure theorem for Steinberg groups}
 The aim of section is to formulate sufficient conditions implying the main structure result for Steinberg groups
@@
 Let $\mu$ be a microweight of the root system $\Phi$. Denote by $N_\mu$
-\begin{def}
 
-\end{def}
+\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $SL_4$}
+
+\subsection{Proof of the theorem on \texorpdfstring{$\mathbb{P}^1$}{P1}-glueing for $K_2$}
+
+\section{Applications}
+
+\subsection{Bruhat--Tits buildings}
+
+\subsection{\texorpdfstring{$A^1$}{A1}-invariance of the fundamental group}
+
+\newpage
 

### 2018-05-01 paper.tex
Added construction of sigma maps

@@
 \documentclass[oneside, 10pt]{amsart}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
 \usepackage[breaklinks=true]{hyperref}
@@
 
-\addbibresource{lemma.bib}
+\addbibresource{paper.bib}
 \renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
@@
 \DeclareMathOperator{\St}{St}
+\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\T}{T}
+\DeclareMathOperator{\GL}{GL}
 \DeclareMathOperator{\SL}{SL}
+\DeclareMathOperator{\Aut}{Aut}
+\DeclareMathOperator{\K}{K}
 \DeclareMathOperator{\rk}{rk}
+
 \newcommand{\XX}[1]{\mathcal{X}_{#1}}
@@
 
-\newtheorem{lem}{Lemma}
-\numberwithin{lem}{section}
+\newtheorem{lemma}{Lemma}
+\numberwithin{lemma}{section}
 \Crefname{lemma}{Lemma}{Lemmas}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\arabic{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemma}
 
-\newtheorem{cor}[lem]{Corollary}
+\newtheorem{cor}[lemma]{Corollary}
 \Crefname{cor}{Corollary}{Corollaries}
 
-\newtheorem{prop}[lem]{Proposition}
+\newtheorem{prop}[lemma]{Proposition}
 \Crefname{prop}{Proposition}{Propositions}
@@
 \Crefname{def}{Definition}{Definitions}
-\newtheorem{example}[lem]{Example}
+\newtheorem{example}[lemma]{Example}
 \Crefname{example}{Example}{Examples}
@@
 
-\newtheorem{rem}[lem]{Remark}
+\newtheorem{rem}[lemma]{Remark}
 \Crefname{rem}{Remark}{Remarks}
@@
 \subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $SL_4$}
+Let $R$ be a local ring and assume that $n\geq 4$.
+For $1\leq k\leq n$ denote by $\delta_k$ the $n\times n$ matrix of $\GL(n, R[t, t^{-1}])$ which differs from the unit matrix 
+ only by the element $t$ on the $k$-th place of its diagonal.
+Recall from~\cite[Corollary~4]{Ka77} that there exists unique automorphisms $\beta_{\delta_k}$, $\beta_{\delta_k^{-1}}$ of $\St(n, R[t, t^{-1}])$
+ modeling conjugation with matrices $\delta_k$ and $\delta_k^{-1}$ (see diagram~\eqref{eq:sigma-diagram} below)
+
+Our immediate goal is to define analogues of these automorphisms on the level of Steinberg group $\St(n, R[t])$.
+First of all, let us introduce the subgroups of $\St(n, R[t])$ on which these morphisms will be defined.
+Denote by $\mathcal{X}_k$ (resp. $\mathcal{X}^k$) the set consisting of those generators $x_{ij}(\xi)$ of $\St(n, R[t])$ for which 
+ either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
+Denote by $N_k$ and $N^k$ the subgroups of $\St(n, R[t])$ generated by $\mathcal{X}_k$ and $\mathcal{X}^k$, respectively.
+Our goal is to construct mutually inverse morphisms $\sigma_k$, $\sigma_k^{-1}$ fitting into the following diagram.
+\begin{equation} \label{eq:sigma-diagram}
+\xymatrix{ N_k\ar@{-->}[r]^{\sigma_k}\ar@<-0.0ex>[d] & N^k \ar@<-0.0ex>[d] \ar@{-->}[r]^{\sigma_k^{-1}} & N_k \ar[d] \\ 
+          \St(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{\beta_{\delta_k}} \ar[d]_{\pi} & \St(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{\beta_{\delta_k^{-1}}} \ar[d]_{\pi} & \St(n, R[t, t^{-1}]) \ar[d]_{\pi} \\
+          \GL(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R[t, t^{-1}])}
+\end{equation}
+For $n\geq 5$ these morphisms have already been constructed by Tulenbaev, see \S~3 of~\cite{Tu83}.
+Thus, in the sequel we are mainly interested in the case $n=4$.
+To simplify notation, we limit ourselves to constructing the map $\sigma_1$, so everywhere in the sequel we assume that $k=1$.
+
+Of course, the map of right conjugation with $\delta_1$ induces the obvious one-to-one set-theoretic correspondence between $\mathcal{X}_1$ and $\mathcal{X}^1$. 
+However, there seems to be no reasonable description of the complete set of relations between the elements $\mathcal{X}_1$ that would allow one to describe $N_1$
+ as a group given by generators and relations.
+Thus, in order to define $\sigma_1$ we will use the alternate description of $N^1$ given in terms of ``another presentation''.
+We start with the following simple observation.
+\begin{lemma} \label{lem:n1-decomp} There is an isomorphism $N_1 \cong N_{1,0} \rtimes P_1^-(R)$, where $N_{1,0}$ denotes the subgroup $\St(n, R[t], tR[t])$
+ and $P_1^-(R)$ is the subgroup of $\St(n, R)$ generated by $x_{ij}(\xi)$ with $i\neq 1$.
+\end{lemma}
+
+Recall that the universal property of semidirect products asserts that for any group $H$ acting on a group $N$ via $\phi \colon H \to \Aut(N)$ and any group homomorphisms
+ $f_N\colon N \to G$, $f_H\colon H \to G$ satisfying 
+\begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ n\in N,\ h\in H,\end{equation} there exists a unique map $f\colon N \rtimes H \to G$
+ extending $f_N$ and $f_H$. 
+Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct the following two maps and verify that they satisfy~\eqref{eq:coherence-condition}:
+\[ (\sigma_1)_{P_1^-(R)} \colon P_1^-(R) \to N^1, \ \ (\sigma_1)_{N_{1,0}} \colon N_{1,0} \to N^1.\]
+
+It is easy to define the first map $(\sigma_1)_{P_1^-(R)}$.
+Using the decomposition $P_1^-(R) \cong U^-_1 \rtimes L_1$ where 
+\[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in R \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in R\rangle \]
+we apply the universal property of semidirect products once again 
+ and define $(\sigma_1)_{P_1^-(R)}$ by requiring that it acts identically on $L_1$ 
+and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(R)}(x_{i1}(\xi))= x_{i1}(t\xi)$.
+
+Before we proceed with the construction of the second map $(\sigma_1)_{N_{1,0}}$ we need to recall several technical
+ constructions pertaining to ``another presentation'' of the group $N_{1,0}$.
+
+For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ satisfying $u^tv = 0$ and having at least two zero entries.
+Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R[t]^n$ such that $u^t \cdot v = 0$ there
+ is a decomposition of $(w^t u) \cdot v$ into a sum of elements of $D(u)$, called {\it canonical decomposition}:
+\setcounter{equation}{1}
+\renewcommand{\theequation}{\arabic{equation}}
+\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\end{equation}
+where $u_{ij}=e_iu_j-e_ju_i,$ and $c_{ij}(v, w)=v_iw_j-v_jw_i.$
+
+Let $A$ be a commutative ring and $I$ be a splitting ideal of $A$.
+Let $u, v \in A^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
+Recall from 3.8, 3.10 of~\cite{Ka77} that under these assumptions one can define certain element
+ $x(u, v)$ of $\St(n, A)$ such that $\pi(x(u, v)) = t(u, v) = 1 + uv^t$.
+The following properties of $x(u, v)$ are standard (cf.~\cite[Lemma~1.1]{Tu83}).
+\begin{lemma} \label{lem:xsmall-properties}
+\begin{lemlist}
+ \item \label{item:xsmall-scalar} If $v$ or $w$ has at least two zero components, then 
+ \begin{equation}\nonumber x(v, wa) = x(va, w).\end{equation}
+ \item \label{item:xsmall-additivity} If $w_1$ and $w_2$ have at least one common zero coordinate then
+ \begin{equation}\nonumber x(v, w_1)x(v, w_2) = x(v, w_1+w_2).\end{equation}
+ \item \label{item:xsmall-commute} If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$
+  both have at least two zero components then $x(v, w)$ and $x(v', w')$ commute.
+\end{lemlist}
+\end{lemma}
+
+Let $u \in E(n, A)e_1$, $v \in I^n$ be such that $u^tv = 0$.
+Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, A, I)$:
+\begin{equation} \label{eq:sigma-definition}
+ F(u, v) = \prod\limits_{i=1}^r x(u,  v_i),\ \
+ S(v, u) = \prod\limits_{i=1}^r x( v_i, u).
+\end{equation}
+Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
+Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover
+ $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
+
+Recall from~\cite{LS17} that it is possible to give a presentation of the relative Steinberg group $\St(n, A, I)$ formulated in terms of elements $F(u, v)$, $S(v, u)$.
+More formally, \cite[Proposition 3.10]{LS17} asserts that $\St(n,\,A,\,I)$ admits presentation with the set of generators
+\begin{multline*} \{F(u,\,v)\mid u\in E(n,\,A)e_1,\ v\in I^n,\ u^tv=0\}\, \cup \\ \cup \{S(u,\,v)\mid u\in I^n,\ v\in E(n,\,A)e_1,\ u^tv=0\}\end{multline*}
+subject to relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{R\arabic{equation}}
+\begin{align}
+&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
+&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
+&F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj3} \\
+&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g\!\in \E(n, A). \label{coinc} \end{align}
+Here $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $A^n$.
+
+\setcounter{equation}{3}
+\renewcommand{\theequation}{\arabic{equation}}
+
+To define the map $(\sigma_1)_{N_{1,0}}$ we will invoke the above presentation in the special case $A=R[t]$, $I=tR[t]$.
+Indeed, define $\sigma_1$ on $N_{1,0}=\St(n, R[t], tR[t])$ by the following identities: 
+\begin{equation}
+ \sigma_1(F(u, v)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot t u, \delta_1 \cdot t^{-1} v_i),\ \
+ \sigma_1(S(v, u)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot v_i, \delta_1 \cdot u).
+\end{equation}
+
+\begin{lemma} \label{lem:cor-conj}
+ \begin{lemlist}
+   \item \label{item:correctness} The elements $\sigma_1(F(u, v))$ and $\sigma_1(S(v, u))$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
+   \item \label{item:conjugation} For any $g \in N^1$ one has 
+      \begin{equation}
+          \nonumber {}^g\left(\sigma_1(F(u, v))\right) = \sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right),\ \ 
+                    {}^g\left(\sigma_1(S(u, v))\right) = \sigma_1\left(S(g' \cdot u, {g'}^{*} \cdot v)\right),                    
+      \end{equation}
+      where $g' = {}^{\delta_1}\pi(g).$
+ \end{lemlist}
+\end{lemma}
+\begin{proof}[Short proof]
+ The first assertion can be easily verified using the canonical decomposition and~\cref{lem:xsmall-properties}
+  (compare with Tulenbaev's argument after~\cite[Lemma~1.1]{Tu83}).
+
+ The second assertion can be proved similarly to~\cite[3.14]{Ka77}, (cf. also with the proof of~\cite[Lemma~4.4d]{LS17}).
+\end{proof}
+\begin{proof}[Long proof]
+ Let us verify the first assertion. Let $v = \sum_r v^r$ be a decomposition as above. 
+ Since each $v^r$ is orthogonal to $u$ we can write the canonical decomposition  
+ $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
+ \cref{lem:xsmall-properties} allows us to rewrite the right-hand side of~\ref{eq:sigma-definition} in such a way that 
+  it does not depend on the choice of decomposition for $v$:
+ \begin{multline}
+  \prod\limits_r x(\delta_1^{-1} ut, \delta_1 v^rt^{-1}) = \prod\limits_{r}\prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v^r, w)t^{-1}) = \\ 
+   = \prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v, w)t^{-1}). 
+ \end{multline}
+
+ We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
+ Choose $w\in R^n$ so that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
+ We can write ${}^g\left(\sigma_1\left(F(u, v)\right)\right)$ as follows:
+ \begin{equation} \nonumber
+   \prod\limits_{1\leq i<j\leq n} x(\pi(g) \cdot \delta_1^{-1} \cdot t u, \pi(g)^* \cdot \delta_1 \cdot t^{-1} u_{ij}c_{ij})
+                                   = \prod\limits_{1\leq i<j\leq n} x(\delta_1^{-1} \cdot g'\cdot t u, \delta_1 \cdot {g'}^* \cdot t^{-1} u_{ij}c_{ij}).
+ \end{equation} 
+ Now for every factor in the right-hand side we do the following.
+ If $\{i, j\} = \{h, k\}$ or $\{i, j\} \cap \{h, k\} = \emptyset$ we leave the term unchanged.
+ Otherwise, if, $|\{i, j\} \cap \{h, k\}| = 1$,  say $j = h$, $i\neq k$, we further decompose it as follows:
+  \begin{equation} \nonumber
+    x(\delta_1^{-1} \cdot t u', \delta_1 \cdot {g'}^* \cdot u_{ij} (c_{ij} t^{-1})) = 
+     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ij} (c_{ij} t^{-1})) \cdot 
+     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ki} (c_{ij} t^{-1})).
+  \end{equation}
+  Here $u' = g'  u = t_{jk}(\xi') \cdot u$.
+  Notice that ${g'}^*u_{ij} = t_{kj}(-\xi') \cdot u_{ij} = e_iu_j - e_ju_i + e_k\xi'u_i =u'_{ij}+u'_{ki}\xi'$.
+
+  Thus, we arrive at a product $\prod_{s} x(\delta_1^{-1} \cdot u't, \delta_1 \cdot v'_s t^{-1}) $, where $v'_s \in D(u')$ and
+   $\sum v'_s = {g'}^*v$. Clearly, this product equals $\sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right)$ by definition.
+\end{proof}
+
+\begin{cor}
+ The map $\sigma_1$ preserves relations~\eqref{add4}--\eqref{conj3}.
+\end{cor}
+\begin{proof}
+ For~\eqref{add4}--\eqref{add5} this is an immediate corollary of the first assertion of the previous lemma.
+ For~\eqref{conj3} this follows from the second part of the lemma applied in the special case $g = \sigma_1(F(u, v)) \in N^1$.
+\end{proof}
+
+It remains to verify that $\sigma_1$ preserves~\eqref{coinc}.
+Let us do this at first in the special case when $g^*$ belongs to the subset $G_0 = H_{12}(R) \cdot U^+_1(R) \cdot U^-_1(R)$.
+Here we denote by $H_{12}(R)$ the subgroup of $T(n, R)$ generated by semisimple root elements $ h_{12}(\xi)$, $\xi \in R^*$.
+
+Since the only nonzero components of $u = g^* \cdot e_2$ are $u_1$ and $u_2$ we can present $v = g \cdot e_1$ as a sum $v' + v''$, where 
+ $v'_i=0$, $i>2$ and $v''_1=v''_2=0$.
+Since $v', v'' \in D(u)$ and $u \in D(v)$, from the definition of $\sigma_1$ we obtain that:
+\begin{multline} \label{eq:special-case}
+ \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)) = x(\delta_1^{-1} \cdot v'a, \delta_1\cdot  u) \cdot x(\delta_1^{-1}\cdot v''a, \delta_1 \cdot u) = \\
+  = x(\delta_1^{-1} va, \delta_1 \cdot u) = x(\delta_1^{-1} vat^{-1}, \delta_1 \cdot ut) = \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) 
+\end{multline}
+
+To obtain the assertion in the general case notice that for $R$ local the group $\E(n, R)$ admits the following decomposition:
+\[\E(n, R) = \mathrm{EP}_1(R) \cdot H_{12}(R) \cdot U^-_1(R) \cdot U^+_1(R).\]
+This can be either obtained as a corollary of Gauss decomposition or can be proved by a direct calculation. %TODO: Give reference
+
+Applying transpose-inverse automorphism $(-)^*$ to the above decomposition and invoking~\cref{lem:n1-decomp} we obtain that $\E(n, R[t]) = \pi(N_1) \cdot G_0$.
+Thus, every $g \in \E(n, R[t])$ can be factored as $\pi(n) \cdot h$ for some $n\in N_1$ and $h \in G_0$.
+Since $\pi(n) = {}^{\delta_1} \pi(n')$ for some $n' \in N^1$ it remains to apply~\cref{item:conjugation} and~\eqref{eq:special-case} to obtain the required assertion:
+\begin{multline} \nonumber \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) = {}^{n'}(\sigma_1(F(h \cdot e_1, h^* \cdot e_2a))) = \\
+                           = {}^{n'}(\sigma_1(S(h \cdot e_1a, h^* \cdot e_2))) = \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)). \end{multline}
+
+Thus, we have completed the construction of the map $(\sigma_1)_{N_{1,0}}$.
+It is not hard to verify that the condition~\eqref{eq:coherence-condition} is satisfied with these definitions,
+ therefore, we have also completed the construction of the map $\sigma_1$.
 

### 2018-05-22 paper.tex
Copypasted contents from a1inv-k2; fixed some bugs

@@
 \DeclareMathOperator{\T}{T}
+\DeclareMathOperator{\Hom}{Hom}
 \DeclareMathOperator{\GL}{GL}
@@
 
+\newcommand{\ZZ}{\mathbb{Z}}
 \newcommand{\XX}[1]{\mathcal{X}_{#1}}
@@
 
-\subsection{General structure theorem for Steinberg groups}
-The aim of section is to formulate sufficient conditions implying the main structure result for Steinberg groups
+\subsection{$\sigma$-automorphisms}
+%Our notation and conventions follows~\cite[\S~4]{Vav09}.
+Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
+We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of vectors $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
+As usual, $P(\Phi^\vee)$ denotes the lattice spanned by the \emph{fundamental weights $\varpi_i$}.
+Recall that $\varpi_i$ are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$
+
+Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
+Consequently, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$
+defines a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$.
+
+Consider the action of $H=\Hom(\ZZ \Phi, R^*)$ on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ given by
+\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
+Since $\chi$ is a character, this action respects the set of Steinberg relations $\mathcal{R}_{\Phi, R}$ and therefore gives a well-defined action of $H$ on $\St(\Phi, R)$.
+
+In the sequel we will be mostly interested in the following example.
+\begin{example}
+Let $A$ be a ring, take $R$ to be the ring of Laurent polynomials $A[t, t^{-1}]$ and let $\alpha_i \in \Pi$ be a simple root.
+Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
+It is easy to see that
+\begin{equation}\label{eq:sigma_act} \sigma_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi),\end{equation}
+where $m_k(\alpha)$ denotes the coefficient in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum m_k(\alpha) \alpha_k$.
+\end{example}
+
+One of the key steps of our proof of Suslin lemma for $K_2$ is to define an analogue of $\sigma_i$ for the group $\St(A[t])$.
+Of course, we cannot expect such map to be automorphism or even be defined on the whole group $\St(A[t])$.
+However, it turns out that for certain $i$ is still possible to define certain subgroups of $\St(A[t])$ and the maps modeling $\sigma_i$ between them.
+
+\subsection{Structure theorem for Steinberg groups}
+
+sufficient conditions implying the main structure result for Steinberg groups.
 
@@
 \renewcommand{\theequation}{R\arabic{equation}}
+
 \begin{align}
@@
 &S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
-&F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj3} \\
-&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g\!\in \E(n, A). \label{coinc} \end{align}
+&F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
+&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, A).
+\end{align}
 Here $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $A^n$.
@@
 
-\newpage
+\DeclareRobustCommand{\VAN}[2]{#2}
+\printbibliography
 
-\printbibliography
 \end{document}

### 2018-05-23 paper.tex
Defined sigma-pairs

@@
 
-%\newtheorem{def}[lem]{Definition}
-\Crefname{def}{Definition}{Definitions}
+\newtheorem{dfn}[lemma]{Definition}
+\Crefname{dfn}{Definition}{Definitions}
 \newtheorem{example}[lemma]{Example}
@@
 
-\subsection{$\sigma$-automorphisms}
+\subsection{$\sigma$-homomorphisms}
 %Our notation and conventions follows~\cite[\S~4]{Vav09}.
 Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
+ i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+
 We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of vectors $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
@@
 \begin{example}
-Let $A$ be a ring, take $R$ to be the ring of Laurent polynomials $A[t, t^{-1}]$ and let $\alpha_i \in \Pi$ be a simple root.
+Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
 Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
 It is easy to see that
-\begin{equation}\label{eq:sigma_act} \sigma_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi),\end{equation}
-where $m_k(\alpha)$ denotes the coefficient in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum m_k(\alpha) \alpha_k$.
+\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
 \end{example}
 
-One of the key steps of our proof of Suslin lemma for $K_2$ is to define an analogue of $\sigma_i$ for the group $\St(A[t])$.
-Of course, we cannot expect such map to be automorphism or even be defined on the whole group $\St(A[t])$.
-However, it turns out that for certain $i$ is still possible to define certain subgroups of $\St(A[t])$ and the maps modeling $\sigma_i$ between them.
+One of the key steps of in the proof of Suslin lemma for $K_2$ is to define analogue of maps $\beta_i^\pm$ on the level of the group $\St(\Phi, A[t])$.
+Of course, one cannot expect such maps to be automorphisms or even be defined on the whole group $\St(\Phi, A[t])$.
+Thus, our first goal is to define the subgroups of $\St(\Phi, A[t])$ on which these morphisms could, in principle, be defined.
+
+In the sequel we assume that $i$ is a vertex of the Dynkin diagram $D(\Phi)$ of $\Phi$ with the property that $m_i(\alpha_{\max})=1$.
+Denote by $\mathcal{X}_i$ (resp. $\mathcal{X}^i$) the subsets of $\mathcal{X}_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
+$m_i(\alpha) > 0$ (resp. $m_i(\alpha)<0$) implies that $\xi \in A[t]$ is divisible by $t$.
+% either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
+Denote by $N_i$ and $N^i$ the subgroups of $\St(\Phi, A[t])$ generated by $\mathcal{X}_i$ and $\mathcal{X}^i$, respectively.
+%Our goal is to construct mutually inverse morphisms $\sigma_k$, $\sigma_k^{-1}$ fitting into the following diagram.
+
+\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertice $i\in D(\Phi)$},
+ if these maps fit into the following diagram.
+\begin{equation} \label{eq:sigma-diagram}
+\xymatrix{ N_k\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^k \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_k \ar[d] \\ 
+          \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^+} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^-} & \St(\Phi, R)} 
+\end{equation}
+In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 
+ the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R$.
+%As before, we denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
+         % \GL(n, R) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R)
+\end{dfn}
 
@@
 
-Our immediate goal is to define analogues of these automorphisms on the level of Steinberg group $\St(n, R[t])$.
-First of all, let us introduce the subgroups of $\St(n, R[t])$ on which these morphisms will be defined.
-Denote by $\mathcal{X}_k$ (resp. $\mathcal{X}^k$) the set consisting of those generators $x_{ij}(\xi)$ of $\St(n, R[t])$ for which 
- either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
-Denote by $N_k$ and $N^k$ the subgroups of $\St(n, R[t])$ generated by $\mathcal{X}_k$ and $\mathcal{X}^k$, respectively.
-Our goal is to construct mutually inverse morphisms $\sigma_k$, $\sigma_k^{-1}$ fitting into the following diagram.
-\begin{equation} \label{eq:sigma-diagram}
-\xymatrix{ N_k\ar@{-->}[r]^{\sigma_k}\ar@<-0.0ex>[d] & N^k \ar@<-0.0ex>[d] \ar@{-->}[r]^{\sigma_k^{-1}} & N_k \ar[d] \\ 
-          \St(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{\beta_{\delta_k}} \ar[d]_{\pi} & \St(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{\beta_{\delta_k^{-1}}} \ar[d]_{\pi} & \St(n, R[t, t^{-1}]) \ar[d]_{\pi} \\
-          \GL(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R[t, t^{-1}]) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R[t, t^{-1}])}
-\end{equation}
-For $n\geq 5$ these morphisms have already been constructed by Tulenbaev, see \S~3 of~\cite{Tu83}.
+For $n\geq 5$ $\sigma-$morphisms have already been constructed by Tulenbaev, see \S~3 of~\cite{Tu83}.
 Thus, in the sequel we are mainly interested in the case $n=4$.

### 2018-06-05 paper.tex
Introduced set of adjacency classes

@@
 \DeclareMathOperator{\rk}{rk}
+
+\newcommand{\rA}{\mathsf{A}}
+\newcommand{\rB}{\mathsf{B}}
+\newcommand{\rC}{\mathsf{C}}
+\newcommand{\rD}{\mathsf{D}}
+\newcommand{\rE}{\mathsf{E}}
+\newcommand{\rF}{\mathsf{F}}
+\newcommand{\rG}{\mathsf{G}}
 
@@
 
+Our notation and conventions follows~\cite[\S~4]{Vav09}.
+Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
+ i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+
+We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of coroots $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
+As usual, $P(\Phi^\vee)$ denotes the lattice spanned by the \emph{fundamental weights $\varpi_i$},
+ that are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$ %TODO: Mistake?
+
 \subsection{Steinberg groups and relative Steinberg groups}
@@
 
-\subsection{$\sigma$-homomorphisms}
-%Our notation and conventions follows~\cite[\S~4]{Vav09}.
-Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
- i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
-
-We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of vectors $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
-As usual, $P(\Phi^\vee)$ denotes the lattice spanned by the \emph{fundamental weights $\varpi_i$}.
-Recall that $\varpi_i$ are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$
-
+\subsection{$\sigma$-pairs}
 Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
@@
 
-In the sequel we assume that $i$ is a vertex of the Dynkin diagram $D(\Phi)$ of $\Phi$ with the property that $m_i(\alpha_{\max})=1$.
+In the sequel we assume that $i$ is a vertex of the Dynkin diagram $D(\Phi)$ of $\Phi$ with the property that $m_i(\alpha_{\max})=1$ (of course, this implies that $\Phi$ is not of type $\rE_8, \rF_4$ or $\rG_2$).
 Denote by $\mathcal{X}_i$ (resp. $\mathcal{X}^i$) the subsets of $\mathcal{X}_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
@@
 
-\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertice $i\in D(\Phi)$},
+\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertex $i\in D(\Phi)$},
  if these maps fit into the following diagram.
 \begin{equation} \label{eq:sigma-diagram}
-\xymatrix{ N_k\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^k \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_k \ar[d] \\ 
+\xymatrix{ N_i\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^i \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_i \ar[d] \\ 
           \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^+} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^-} & \St(\Phi, R)} 
@@
 
+For the remainder of this subsection our main goal will be to verify that an analogue of the group decomposition from \cite[Lemma~3.1f]{Tu83} holds for $\St(\Phi, A)$
+ provided $\St(\Phi, R)$ admits at least one $\sigma$-pair.
+
+Denote by $\widetilde{W}$ the subgroup of $\St(\Phi, A)$ generated by elements $w_\alpha(1)$.
+The subgroup $\widetilde{W}$ acts on $\St(\Phi, A)$ via conjugation, for example, 
+ the action on the generators of $\mathcal{X}_{\Phi, A}$ can be expressed via the formula ${}^{w_\alpha(1)} \!x_{\beta}(\xi) = x_{\sigma_{\alpha}(\beta)} ( \pm \xi)$.
+It is easy to see that the action of $\widetilde{W}$ on the set of root subgroups $\{X_\alpha \mid \alpha \in \Phi \}$ of $\St(\Phi, R)$ coincides with the obvious
+ action of the Weyl group $W(\Phi)$ on it. Since $N_i$ and $N^i$ are generated by root subgroups we immediately obtain the following statement.
+\begin{lemma} The set of elements in the orbit of $N_i$ (resp. $N^i$) under the conjugation action of $\widetilde{W}$ 
+is in bijective correspondence with 
+the set of adjacency classes of $W(\Phi)$ with respect to its Levi subgroup $W_i = W(\Delta_i)$. %TODO: Unsure whether it is true at all :)
+\end{lemma}
+In the sequel we denote by $\Sigma$ the set of elements in $\widetilde{W}$ whose projections in $W(\Phi)$ form the set of representatives for
+ right adjacency classes of $W(\Phi)$ with respect to $W_i$. %We can assume these representatives to be short
+
 \subsection{Structure theorem for Steinberg groups}
@@
 
-\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $SL_4$}
+\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $\SL_4$}
 Let $R$ be a local ring and assume that $n\geq 4$.

### 2018-07-06 paper.tex
Imported sheet with RS-theorem

@@
 \subsection{Rehmann-Soule theorem}
+
+Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
+Denote by $B$ the ring $\mathfrak{m}[t^{-1}] + A[t]$ with the obvious $\mathbb{Z}$-grading.
+Clearly, the $k$-th homogeneous component $B_k$ of $B$ equals $A\cdot t^k$ for $k \geq 0$ or $B_k = \mathfrak{m} \cdot t^k$ for $k<0$.
+
+For $n \geq 1$ consider the following collections of generators:
+\[\XX{n} = \{ x_\alpha(\xi) \mid \xi \in B_k,\text{ for } k\leq n\}. \]
+It is obvious that $\XX{n} \subseteq \XX{n+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
+
+Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
+Denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
+ three families of relations:
+\begin{align}
+ \label{eq:am} \tag{$a_m$} x_\alpha(\xi) x_\alpha(\eta) & = x_\alpha(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
+ \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
+ \nonumber                                                     &       & \xi \in B_k,\ \eta \in B_l,\ l,k\leq m;\\
+ \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
+ \nonumber                                                    &                                                  & \xi \in B_k,\ \eta \in B_l,\ l, k, l+k \leq m.
+\end{align}
+
+The aim of this subsection is to the following analogue of~\cite[Lemma~3.3]{Tu83}. 
+\begin{lemma}\label{lem:tul3.3}
+ For all simply-laced root systems of rank $\geq 3$ the natural inclusion of generators induces an isomorphism $G_1 \to \St(\Phi, B).$
+\end{lemma}
+Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
+ %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
+Instead, we have to employ a variant of much longer argument of U.~Rehmann and C.~Soul{\'e}, see~\cite{Re75,RS76}.
+
+%Denote by $F(S)$ the free group on the generating set $S$.
+%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
+%well, not so clear, actually :)
+To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 1$.
+Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
+
+\begin{rem}
+There are two reasons why we can't simply refer to~\cite{Re75} or~\cite{RS76} for the proof of~\cref{lem:tul3.3}.
+The first is that Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to establish this fact starting from $m = 1$.
+The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
+(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
+% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
+\end{rem}
+
+We will use the following commutator identities (cf.~\cite[H1]{Re75}):
+\begin{align}
+% \label{eq:H1i}   [a, bc] = [a, b]\cdot {}^b[a, c] = [a, b] \cdot [b, [a, c]] \cdot [a, c];& \\
+ \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
+ \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].&
+\end{align}
+
+The following lemma is reminiscent of~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
+\begin{lemma}
+ Suppose $m \geq 1$.
+ Let $\alpha, \beta, \alpha', \beta'$ be such that $\alpha + \beta = \alpha' + \beta'$.
+ Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
+  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
+ Then in the group $G_m$ the following relations hold:
+ \begin{align}
+  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] &= [x_{\alpha'}(\xi'), x_{\beta'}(\eta')] & \\
+  \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] & = 1 & \text{in the case } \gamma\in\{\alpha, \beta, \alpha + \beta\},\\
+  \nonumber                                     &                          & \text{$\zeta \in B_{k''}$, $k''\leq m$.}
+ \end{align}
+\end{lemma}
+\begin{proof}
+ Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
+ Therefore, we can repeat the argument of~\cite[Proposition 1.1]{Re75} verbatim.
+\end{proof}
+
+To prove that $\theta_m$ is an isomorphism we construct the missing generators of $G_{m+1}$ in $G_m$ and then show that they satisfy relations $\RR{m+1}$.
+
+For every $\xi \in B_{m+1}$ and $\alpha\in \Phi$ there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$.
+Thus, we can make the following definition:
+\begin{equation} \label{eq:defmpn} x_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)],\end{equation} 
+and from~\eqref{item:i} its correctness (i.\,e. the independence of the choice of $\alpha'$) follows.
+
+We now turn to the verification of relations $(a_{m+1})$, $(b_{m+1})$, $(c_{m+1})$.
+Notice first that \eqref{eq:H1ii} and~\eqref{item:ii} immediately imply $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
+
+To verify relations $(c_{m+1})$ it suffices to show that
+\begin{equation}
+\label{eq:verify-bmp1} [x_\alpha(\xi), x_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)],\ a \in A,\ \xi \in B_k,\ k\leq 0.
+\end{equation}
+We can find root subsystem $\Psi \subseteq \Phi$ of type $\mathsf{A}_3$ containing the roots $\alpha, \alpha'$.
+Choose basis $\{\alpha,\beta,\gamma\}$ of $\Psi$ so that $\alpha'=\beta$ and the Dynkin diagram of $\Psi$ looks as follows:
+\begin{equation}\label{eq:diagA3} \xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.\end{equation}
+Let us verify~\eqref{eq:verify-bmp1}:
+\begin{align*}
+   [x_\alpha(\xi), x_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{eq:defmpn} for a suitable $a'\in A$} \\ 
+ = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
+ = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$} \\
+ = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
+ %TODO: There's a mistake at this moment --- k = 0, m = 1 and the needed relation is not in G_1 -- :(
+ = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
+ = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}.}
+\end{align*}
+
+Now, let us show that relations $(b_{m+1})$ hold. 
+Without loss of generality we may also assume $k \leq l=m+1$, thus $\eta = bt^{m+1}$ for some $b\in A$.
+
+\begin{enumerate}
+\item \label{case:1} First consider the case $k \leq 0$. There are two further subcases.
+ \begin{enumerate}
+  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
+  As before, without loss of generality we may assume that $\alpha, \alpha'$ are contained in a root system $\Psi$ of type $\mathsf{A}_3$,
+   whose simple roots are labeled as in~\eqref{eq:diagA3} and, moreover, $\alpha'=\alpha + \beta$.
+  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we get (recall that $\xi \in B_k$):
+   \begin{multline} \nonumber
+   [x_\alpha(\xi), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
+  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
+  \end{multline}
+  \item Case $\alpha \perp \alpha'$. As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
+  \begin{multline} \nonumber
+   [x_\alpha(\xi), x_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(bt^m), x_{-\beta}(t)]] = \\   
+  = [[x_\alpha(\xi), x_{\beta+\gamma}(bt^m)], {}^{x_{\beta+\gamma}(bt^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(bt^m)}\![x_{\alpha+\beta+\gamma}(bt^m\xi), x_{-\beta}(t)] = 1.
+  \end{multline}
+ \end{enumerate}
+
+\item \label{case:2} Now assume $1 \leq k \leq m+1$. 
+At first we want to prove $(b_{m+1})$ only in the special case $\xi=t^k$.
+We proceed by induction on $k$ starting with $k=1$.
+Again, there are two cases.
+\begin{enumerate}
+ \item \label{case:2a} Case $\alpha\not\perp\alpha'$ is handled similarly to the Case~\eqref{case:1a} with the only
+  difference that we have to refer to the inductive assumption rather than~\eqref{eq:bm} in the case $k=m+1$.
+  \begin{multline} \nonumber
+   [x_\alpha(t^k), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(t^k), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
+  = [[x_\alpha(t^k), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
+  \end{multline}
+
+ \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
+\begin{align*}
+{}^{x_\gamma(t^k)}x_\alpha(bt^{m+1}) = {}^{x_\gamma(t^k)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by $(c_{m+1})$}\\
+ = [x_{-\beta}(b't^{m+1}), {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
+ = [[x_{-\beta-\gamma}(b''t^{m+1-k}), x_\gamma(t^k)], {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]          & \text{ by $(c_{m+1})$}\\
+ = [x_{-\beta-\gamma}(b''t^{m+1-k)}), [x_\gamma(t^k), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-k \leq m$}\\
+ = x_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_{m+1})$.} \end{align*}
+ Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
+ \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
+\end{enumerate}
+Thus we have demonstrated $(b_{m+1})$ in the special case $a=1$.
+\item Now let us prove $(b_{m+1})$ for arbitrary $\xi = at^k$, $a\in A$ and $1\leq k\leq m+1$. Again, there are two subcases.
+\begin{enumerate}
+\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
+ \begin{align*} [x_\alpha(at^k), x_{\alpha + \beta}(bt^{m+1})] = [x_\alpha(at^k), [x_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b)]] & \text{ by $(c_{m+1})$} \\
+  = [[x_\alpha(at^k), x_{\alpha+\beta+\gamma}(t^{m+1})], {}^{x_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b)] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
+  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
+\item Case $\alpha \perp \alpha'$.
+ % mu        0  1 m+1
+ % vu        1  0 k
+ % mu'       0  1 m+1-k
+ % mu - mu'  0  0 k
+ % nu + mu'  1  1 m+1
+ %           a  b t
+The required identity follows from the following chain of equalities:
+\begin{align*}
+ x_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{x_{-\beta}(t^k)}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
+ = {}^{x_{-\beta}(t^k)}\![x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(c_{m+1})$} \\
+ = [x_{\alpha}(bt^{m+1}) x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(b_k)$ or Case~\eqref{case:2} if $k=m+1$ }\\
+ = {}^{x_{\alpha}(bt^{m+1})}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by~\eqref{eq:H1ii} and $(c_{m+1})$} \\
+ = x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by Case~\eqref{case:3a}.}
+\end{align*}
+\end{enumerate}
+\end{enumerate}
 

### 2018-07-31 paper.tex
Fixed statement of Lemma 2.1

@@
 
-For $n \geq 1$ consider the following collections of generators:
+For $n \geq 1$ consider the following collections of homogeneous generators:
 \[\XX{n} = \{ x_\alpha(\xi) \mid \xi \in B_k,\text{ for } k\leq n\}. \]
@@
 Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
-Denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
+Fir $m\geq 2$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
  three families of relations:
@@
 
-The aim of this subsection is to the following analogue of~\cite[Lemma~3.3]{Tu83}. 
+Now define the group $G_1$ presented by generators $\mathcal{X}_1$ and the set of relations $\RR{1}$ consisting of 
+ the above families of relations $(a_1)$, $(b_1)$, $(c_1)$ with one extra family of relations
+\begin{equation} \nonumber \tag{$d_1$}
+[[x_{\alpha}(\xi t), x_{\beta}(\eta)],  x_{\gamma}(\zeta t)] = [[x_{\alpha}(\xi t), x_{\beta}(\eta t)],  x_{\gamma}(\zeta)], 
+\end{equation}
+where $\alpha, \beta, \gamma \in \Phi$ are such that $\alpha+\beta+\gamma \in \Phi$ and $\xi, \eta, \zeta \in A$.
+
+The aim of this subsection is to demonstrate the following analogue of~\cite[Lemma~3.3]{Tu83}. 
 \begin{lemma}\label{lem:tul3.3}
- For all simply-laced root systems of rank $\geq 3$ the natural inclusion of generators induces an isomorphism $G_1 \to \St(\Phi, B).$
+ Let $\Phi$ be a simply-laced root systems of rank $\geq 3$. 
+ Then the natural inclusion of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces an isomorphism $G_n \to G_{n+1}$ for $n\geq 1$.
+ Consequently, the group $\St(\Phi, B)$ is isomorphic to $G_1$.
 \end{lemma}
@@
  %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
-Instead, we have to employ a variant of much longer argument of U.~Rehmann and C.~Soul{\'e}, see~\cite{Re75,RS76}.
+Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.
 
@@
 %well, not so clear, actually :)
-To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 1$.
+To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$.
 Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
 
-\begin{rem}
-There are two reasons why we can't simply refer to~\cite{Re75} or~\cite{RS76} for the proof of~\cref{lem:tul3.3}.
-The first is that Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to establish this fact starting from $m = 1$.
-The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
-(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
+%\begin{rem}
+%There are two reasons why we can't simply refer to~\cite{Re75} or~\cite{RS76} for the proof of~\cref{lem:tul3.3}.
+%The first is that we want to prove Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to %establish this fact starting from $m = 1$.
+%The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
+%(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
 % (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
-\end{rem}
+%\end{rem}
 

### 2018-08-03 paper.tex
Added relations e1 d1

@@
 Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
-Fir $m\geq 2$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
+For $m\geq 1$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
  three families of relations:
@@
 
-Now define the group $G_1$ presented by generators $\mathcal{X}_1$ and the set of relations $\RR{1}$ consisting of 
- the above families of relations $(a_1)$, $(b_1)$, $(c_1)$ with one extra family of relations
-\begin{equation} \nonumber \tag{$d_1$}
-[[x_{\alpha}(\xi t), x_{\beta}(\eta)],  x_{\gamma}(\zeta t)] = [[x_{\alpha}(\xi t), x_{\beta}(\eta t)],  x_{\gamma}(\zeta)], 
-\end{equation}
-where $\alpha, \beta, \gamma \in \Phi$ are such that $\alpha+\beta+\gamma \in \Phi$ and $\xi, \eta, \zeta \in A$.
+ \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
+\begin{align} \nonumber \tag{$d_1$}
+[[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
+\nonumber \tag{$e_1$}
+[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta+\gamma \not\in \Phi. \end{align}
+ \end{lemma}
 
-The aim of this subsection is to demonstrate the following analogue of~\cite[Lemma~3.3]{Tu83}. 
+The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
+It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
+ a map $\theta_n\colon G_n \to G_{n+1}$ for $n\geq 2$.
 \begin{lemma}\label{lem:tul3.3}
  Let $\Phi$ be a simply-laced root systems of rank $\geq 3$.
- Then the natural inclusion of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces an isomorphism $G_n \to G_{n+1}$ for $n\geq 1$.
- Consequently, the group $\St(\Phi, B)$ is isomorphic to $G_1$.
+
+ Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
 \end{lemma}

### 2018-08-07 paper.tex
Minor

@@
 
+It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
+ a map $\theta_n\colon G_n \to G_{n+1}$.
 The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
-It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
- a map $\theta_n\colon G_n \to G_{n+1}$ for $n\geq 2$.
 \begin{lemma}\label{lem:tul3.3}
  Let $\Phi$ be a simply-laced root systems of rank $\geq 3$. 
-
+ Then $ $
  Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
@@
 In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 
- the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R$.
+ the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R = A[t, t^{-1}]$.
 %As before, we denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.

### 2018-08-13 paper.tex
Minor
Added some intro

@@
 
+The aim of this note is to show that $\K_2$-analogue of Horrocks theorem holds for the unstable group $K_{2, 4}(R)$.
+From this we deduce an improved version of Tulenbayev's theorem on early stability for linear $K_2$-groups.
+
+Let $R$ be a commutative ring and $\St(n, R)$ be the Steinberg group of rank $n$.
+Denote by $\K_2(n, R)$ (resp. $\K_1(n, R)$) the kernel (resp. cokernel) of the canonical map $\phi\colon \St(n, R) \to \GL(n, R)$.
+Recall that in~\cite[Theorem~5.1]{Tu83} M.~Tulenbayev proves the following result.
+\begin{thm*} For $n \geq 5$ the Steinberg group functor $\St(n, -)$ satisfies $\mathbb{P}^1$-glueing, i.\,e. for every
+ local ring $R$ the following square is pullback:
+ \[\xymatrix{ \St(n, R)    \ar[r]\ar[d] & \ar[d] \St(n, R[t^{-1}] \\ 
+              \St(\Phi, R[t]) \ar[r]       &        \St(n, R[t, t^{-1}]).}\]
+\end{thm*}
+The above theorem should be considered as a ``$\K_2$-analogue'' of Horrocks theorem on projective modules (see e.\,g.~\cite[Ch.~IV]{Lam10}).
+Recall that this theorem asserts that $\mathbb{P}^1$-glueing holds for the functor $\mathrm{VB}_n$ 
+ associating to each commutative ring $R$ the set of rank $n$ vector bundles over $R$.
+On the level of $\K_1$ the analogous statement was first obtained by A.~Suslin for the functor $\K_1(n, R)$ under the assumption $n\geq 3$, see~\cite{Su77}.
+
+A lot of effort has been put afterwards into generalizing Suslin's results to other groups (see e.\,g.~\cite{Abe83}). 
+One of the more recent results in this direction is~\cite[Theorem~1.1]{St-poly} due to A.~Stavrova, in which
+ $\mathbb{P}^1$-glueing for $K_1$ is proved for a large class of isotropic reductive groups.
+
+\subsection{Acknowledgements}
+The author would like to thank Anastasia Stavrova and Andrei Lavrenov for numerous helpful discussions regarding this paper.
+
 \section{Preliminaries}
@@
 
-\subsection{Rehmann-Soule theorem}
+\subsection{Rehmann-Soul{\'e} theorem}
 
@@
 \nonumber \tag{$e_1$}
-[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta+\gamma \not\in \Phi. \end{align}
+[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta \perp \gamma \end{align}
  \end{lemma}

### 2018-08-13 paper.tex
Writing introduction

@@
 \DeclareMathOperator{\rk}{rk}
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
 
@@
 
-The aim of this note is to show that $\K_2$-analogue of Horrocks theorem holds for the unstable group $K_{2, 4}(R)$.
-From this we deduce an improved version of Tulenbayev's theorem on early stability for linear $K_2$-groups.
+The aim of this note is to show that $\K_2$-analogue of Horrocks theorem holds for the unstable group $K_{2}(4, R)$.
+From this theorem deduce an improved version of Tulenbayev's theorem on early stability for linear $K_2$-groups.
 
@@
 Recall that in~\cite[Theorem~5.1]{Tu83} M.~Tulenbayev proves the following result.
+%TODO: Maybe formulate the final result, i. e. early stability theorem
 \begin{thm*} For $n \geq 5$ the Steinberg group functor $\St(n, -)$ satisfies $\mathbb{P}^1$-glueing, i.\,e. for every
  local ring $R$ the following square is pullback:
- \[\xymatrix{ \St(n, R)    \ar[r]\ar[d] & \ar[d] \St(n, R[t^{-1}] \\ 
+ \[\xymatrix{ \St(n, R)    \ar[r]\ar[d] & \ar[d] \St(n, R[t^{-1}]) \\ 
               \St(\Phi, R[t]) \ar[r]       &        \St(n, R[t, t^{-1}]).}\]
 \end{thm*}
-The above theorem should be considered as a ``$\K_2$-analogue'' of Horrocks theorem on projective modules (see e.\,g.~\cite[Ch.~IV]{Lam10}).
-Recall that this theorem asserts that $\mathbb{P}^1$-glueing holds for the functor $\mathrm{VB}_n$ 
- associating to each commutative ring $R$ the set of rank $n$ vector bundles over $R$.
-On the level of $\K_1$ the analogous statement was first obtained by A.~Suslin for the functor $\K_1(n, R)$ under the assumption $n\geq 3$, see~\cite{Su77}.
+It is not hard to see that $\mathbb{P}^1$-glueing property holds simulteneously for Steinberg group functor $\St(n, -)$ and the functor $\K_2(n, -)$.
+Therefore the above theorem should be considered as a ``$\K_2$-analogue'' of the classical Horrocks theorem on projective modules (see e.\,g.~\cite[Ch.~IV]{Lam10}).
+Recall that the latter result asserts that $\mathbb{P}^1$-glueing holds for the functor $\mathrm{VB}_n$ associating to each commutative ring $R$ the set of rank $n$ vector bundles over $R$ (the set $\mathrm{VB}_n$ should be thus considered as the unstable analogue of $K_0$-functor).
 
+The corresponding result on $\mathbb{P}^1$-glueing for for the functor $\K_1(n, R)$,  $n\geq 3$ was first obtained by A.~Suslin as one of the two ingredients in the proof of the $\K_1$-analogue of Serre problem, see~\cite{Su77}.
 A lot of effort has been put afterwards into generalizing Suslin's results to other groups (see e.\,g.~\cite{Abe83}).
-One of the more recent results in this direction is~\cite[Theorem~1.1]{St-poly} due to A.~Stavrova, in which
- $\mathbb{P}^1$-glueing for $K_1$ is proved for a large class of isotropic reductive groups.
+One of the more recent results in this direction is~\cite[Theorem~1.1]{St-poly} due to A.~Stavrova, in which $\mathbb{P}^1$-glueing property is proved for functors $\K_1^G$ modeled on a large class of isotropic reductive groups (consisting, roughly speaking, of groups having local isotropic rank at least $2$).
+%TODO: Better phrasing
+
+Let $\mathcal{F}\colon \catname{CRings} \to \catname{Sets}_*$ be a functor from commutative rings to pointed sets.
+We say that an analogue of Serre problem holds for $\mathcal{F}$ if for any field $k$ there is an isomorphism $\mathcal{F}(k[t_1, \ldots, t_n]) = \mathcal{F}(k)$.
+The well-known counterexample of P.~Cohn shows that the $\K_1$-analogue of Serre problem fails for $\K_1(2, -)$, see~\cite[\S~I.8]{Lam10}.
+Similarly, it is known that an analogue of Serre problem fails for $\K_2(3, -)$, see~\cite{We14}.
+Thus one might ask whether an analogue of Serre problem holds for $\K_2(4, -)$, the only case not covered by Tulenbayev's theorem.
+
+Typically, the proof of an analogue of Serre problem for a functor $\mathcal{F}$ (e.\,g. $\mathrm{VB}_n$, $K_1^G$, $K_2(n, -)$) reduces the following two steps: 
+\begin{enumerate}
+ \item proving that an analogue of local-global principle holds for $\mathcal{F}$ (see ??? for the definition below);
+ \item proving that $\mathcal{F}$ satisfies $\mathbb{P}^1$-glueing.
+\end{enumerate}
+
+In~\cite{LS17} A.~Lavrenov and the author showed that the local-global principle holds for $\St(4, -)$.
+
+Our first main result shows that it is indeed so.
+\begin{thm}
+ The functor $\St(4, -)$ satisfies $\mathbb{P}^1$-glueing.
+\end{thm}
+Consequently, there is an isomorphism $\K_2(4, k[t_1, \ldots, t_n]) \cong \K_2(4, k)$
+To deduce the local-global principle for $K_2(4, -)$ which has already been obtained in~\cite{LS17} this
 

### 2018-08-14 paper.tex
Writing introduction

--- 2018-08-07 paper.tex
@@
 
+The aim of this note is to show that $\K_2$-analogue of Horrocks theorem holds for the unstable group $\K_2(4, R)$.
+From this theorem we deduce an improved version of Tulenbayev's theorem on early stability for linear $\K_2$-groups.
+
+Let $R$ be a commutative ring and $\St(n, R)$ be the Steinberg group of rank $n$.
+Denote by $\K_2(n, R)$ (resp. $\K_1(n, R)$) the kernel (resp. cokernel) of the canonical map $\phi\colon \St(n, R) \to \GL(n, R)$.
+Recall that in~\cite[Theorem~5.1]{Tu83} M.~Tulenbayev proves the following result.
+%TODO: Maybe formulate the final result, i. e. early stability theorem
+\begin{thm*} For $n \geq 5$ the Steinberg group functor $\St(n, -)$ satisfies $\mathbb{P}^1$-glueing, i.\,e. for every
+ local ring $R$ the following square is pullback:
+ \[\xymatrix{ \St(n, R)    \ar[r]\ar[d] & \ar[d] \St(n, R[t^{-1}]) \\ 
+              \St(\Phi, R[t]) \ar[r]       &        \St(n, R[t, t^{-1}]).}\]
+\end{thm*}
+In turn, our first main result is the following.
+\begin{thm} \label{thm:horrocks-sl4} The functor $\St(4, -)$ also satisfies $\mathbb{P}^1$-glueing. \end{thm}
+
+It is not hard to see that $\mathbb{P}^1$-glueing property holds for the Steinberg group functor $\St(n, -)$ iff it holds for the functor $\K_2(n, -)$.
+Therefore the above results should be considered as ``$\K_2$-analogues'' of the classical Horrocks theorem on projective modules (see e.\,g.~\cite[Ch.~IV]{Lam10}).
+Recall that the latter asserts that $\mathbb{P}^1$-glueing holds for the functor $\mathrm{VB}_n$ associating to each commutative ring $R$
+ the set of constant rank $n$ vector bundles over $R$ ($\mathrm{VB}_n$ thus can be considered as the unstable analogue of $K_0$-functor).
+
+Recall that Horrocks theorem usually appears in the context of Serre problem and its analogues for other functors.
+Let $\mathcal{F}\colon \catname{CRings} \to \catname{Sets}_*$ be a functor from commutative rings to pointed sets. 
+We say that an analogue of Serre problem holds for $\mathcal{F}$ if for any field $k$ there is an isomorphism $\mathcal{F}(k[t_1, \ldots, t_n]) = \mathcal{F}(k)$. 
+Typically, the proof of an analogue of Serre problem for a functor $\mathcal{F}$ (e.\,g. $\mathrm{VB}_n$, $K_1(n, -)$, $K_2(n, -)$) 
+ breaks down into the following two steps: 
+\begin{enumerate}
+ \item proving that an analogue of local-global principle holds for $\mathcal{F}$ (see ??? for the definition below);
+ \item proving that $\mathcal{F}$ satisfies $\mathbb{P}^1$-glueing.
+\end{enumerate}
+
+The proof of the analogue of Serre problem for the functor $\K_1(n, R)$ was for the first time obtained by A.~Suslin under the assumption $n\geq 3$, see~\cite{Su77}.
+A lot of effort has been put afterwards into generalizing Suslin's results to other groups (see e.\,g.~\cite{Abe83, St-poly}).
+\begin{comment}
+One of the more recent results in this direction is~\cite[Theorem~1.1]{St-poly} due to A.~Stavrova, 
+ in which $\mathbb{P}^1$-glueing property is proved for functors $\K_1^G$ modeled on a large class of isotropic reductive groups 
+  (consisting, roughly speaking, of groups having local isotropic rank at least $2$). %TODO: Better phrasing
+\end{comment}
+
+The well-known counterexample of P.~Cohn shows that the $\K_1$-analogue of Serre problem fails for $\K_1(2, -)$ and thus Suslin's result cannot be improved, see~\cite[\S~I.8]{Lam10}
+Similarly, it is known that an analogue of Serre problem fails for $\K_2(3, -)$, see~\cite{We14}.
+Thus, our~\cref{thm:horrocks-sl4} completely settles the remaining case $n=4$ not already covered by the results of Wendt and Tulenbayev.
+
+Previously in~\cite{LS17} A.~Lavrenov and the author showed that the local-global principle holds for $\St(4, -)$.
+As said before, this together with~\cref{thm:horrocks-sl4} allows us to show the following.
+\begin{thm} \label{thm:Serre-problem} %TODO: Fix statement
+  For any field $k$ there is an isomorphism $\K_2(4, k[t_1, \ldots, t_n]) \cong \K_2(4, k)$.
+  In fact Tulenbayev early stability theorem can be proved starting with the bound $n=4$... 
+\end{thm}
+
+\subsection{Acknowledgements}
+The author would like to thank Anastasia Stavrova and Andrei Lavrenov for posing the problem and numerous helpful discussions regarding this paper.
+The author would also like to thank ??? for financial support.
+
 \section{Preliminaries}

### 2018-08-15 paper.tex
Writing RS-theorem

@@
 
-The well-known counterexample of P.~Cohn shows that the $\K_1$-analogue of Serre problem fails for $\K_1(2, -)$ and thus Suslin's result cannot be improved, see~\cite[\S~I.8]{Lam10}
+The well-known counterexample of P.~Cohn shows that the $\K_1$-analogue of Serre problem fails for $\K_1(2, -)$ which shows that Suslin's result cannot be improved, see~\cite[\S~I.8]{Lam10}
 Similarly, it is known that an analogue of Serre problem fails for $\K_2(3, -)$, see~\cite{We14}.
@@
 Previously in~\cite{LS17} A.~Lavrenov and the author showed that the local-global principle holds for $\St(4, -)$.
-As said before, this together with~\cref{thm:horrocks-sl4} allows us to show the following.
+As said before, this together with~\cref{thm:horrocks-sl4} allows us to show the following result, which is an improvement of Tulenbayev stability theorem.
 \begin{thm} \label{thm:Serre-problem} %TODO: Fix statement
@@
 \end{thm}
+It is clear that the positive solution of Serre problem for $\K_2(n, -)$ for $n\geq 4$ is a corollary of this result.
+%TODO: Add couple of further corollaries
 
@@
 
-\subsection{Rehmann-Soul{\'e} theorem}
+\section{Rehmann--Soul{\'e} theorem}
+The aim of this section is to prove a variant of Rehmann--Soul{\'e} theorem on presentation of Steinberg groups.
 
@@
 
-For $n \geq 1$ consider the following collections of homogeneous generators:
-\[\XX{n} = \{ x_\alpha(\xi) \mid \xi \in B_k,\text{ for } k\leq n\}. \]
-It is obvious that $\XX{n} \subseteq \XX{n+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
+In what follows we will be concerned with finding a compact presentation of the Steinberg group $\St(4, B)$.
+This presentation is analogous to the that~\cite[Lemma~3.3]{Tu83}, which is formulated for $\St(n, B)$, $n\geq 5$.
 
-Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
-For $m\geq 1$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
- three families of relations:
+For $m \geq 1$ consider the following set of generators:
+\[\XX{m} = \{ x_{ij}(\xi) \mid \xi \in B_k,\text{ for } k\leq m,\ 1\leq i, j\leq 4,\ i\neq j\}. \]
+It is obvious that $\XX{m} \subseteq \XX{m+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
+
+For $m\geq 1$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following three families of relations:
 \begin{align}
- \label{eq:am} \tag{$a_m$} x_\alpha(\xi) x_\alpha(\eta) & = x_\alpha(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
+ \label{eq:am} \tag{$a_m$} x_{ij}(\xi) x_{ij}(\eta) & = x_{ij}(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
  \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
@@
  \end{align}
+
+There are several reasons why we can't simply refer to the original results of U.~Rehmann and C.~Soul{\'e}~\cite{Re75} or~\cite{RS76}.
+The first is that we want to prove Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to %establish this fact starting from $m = 1$.
+%The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
+%(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
+% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
 
@@
 Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
-
-%\begin{rem}
-%There are two reasons why we can't simply refer to~\cite{Re75} or~\cite{RS76} for the proof of~\cref{lem:tul3.3}.
-%The first is that we want to prove Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to %establish this fact starting from $m = 1$.
-%The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
-%(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
-% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
-%\end{rem}
 

### 2018-08-18 paper.tex
Writing section of Rehmann theorem

@@
 It is clear that the positive solution of Serre problem for $\K_2(n, -)$ for $n\geq 4$ is a corollary of this result.
-%TODO: Add couple of further corollaries
+%TODO: Add corollary: some building in simply-connected
+%TODO: if 2 is invertible and E = SL then H_2(SL_4(R)) = H_2(SL_4(R[t]))
 
@@
 \section{Preliminaries}
-
+\begin{comment}
 Our notation and conventions follows~\cite[\S~4]{Vav09}.
@@
  that are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$ %TODO: Mistake?
+\end{comment}
 
@@
 
-\section{Rehmann--Soul{\'e} theorem}
-The aim of this section is to prove a variant of Rehmann--Soul{\'e} theorem on presentation of Steinberg groups.
+\[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]
+\[ [[x_{ij}(a t^{-1}), x_{jk}(b t^{-1})],  x_{kl}(c)] = [x_{ik}(a b t^{-1}),  x_{kl}(c t^{-1})] \]
+\[ \sigma_i [[x_{ij}(a), x_{jk}(b t^{-1})],  x_{kl}(c)] \sigma_i^{-1} =  \sigma_i [x_{ik}(a b),  x_{kl}(c t^{-1})] \sigma_i^{-1} \]
+\begin{multline}
+[[x_{ij}(at^{-1}), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] = \sigma_i [[ x_{ij}(a), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] \sigma_i^{-1} = \\
+\sigma_i \sigma_k^{-1} \sigma_l^{-1} [[ x_{ij}(a), x_{jk}(b)], x_{jl}(c)] \sigma_l \sigma_k \sigma_i^{-1} = 1
+\end{multline}
+\[ [b, c] =1,\ [a^c, b] = c^{-1} a c b c^{-1} a^{-1} c b^{-1} =  c^{-1} a b  a^{-1} b^{-1} c = [a, b]^c \]
 
+We need to prove that $\sigma_i$ commute with $x_{jk}(a)$ if $j\neq i, k \neq i$.
+
+\section{A variant of Rehmann theorem}
 Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
@@
 Clearly, the $k$-th homogeneous component $B_k$ of $B$ equals $A\cdot t^k$ for $k \geq 0$ or $B_k = \mathfrak{m} \cdot t^k$ for $k<0$.
+If $a$ is a homogeneous element of $B$ we denote its homogeneous degree by $|a|$.
 
-In what follows we will be concerned with finding a compact presentation of the Steinberg group $\St(4, B)$.
-This presentation is analogous to the that~\cite[Lemma~3.3]{Tu83}, which is formulated for $\St(n, B)$, $n\geq 5$.
+In what follows we will be concerned with finding a presentation of the Steinberg group $\St(4, B)$ in terms of those generators $x_{ij}(\xi)$
+ for which $\xi$ is homogeneous of degree $\leq 1$ (i.\,e. $|\xi| \leq 1$).
+Our presentation should be thought of as an extension of~\cite[Lemma~3.3]{Tu83} to the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
+Alternatively, our result can be thought of as a variant of the classical theorem of Rehmann~\cite{Re75} (cf. also with Rehmann--Soul{\'e} theorem in~\cite{RS76}).
+
+There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and need to repeat arguments from these papers.
+\begin{itemize}
+ \item Rehmann and Soul{\'e} deal with usual polynomial rings rather than $\mathbb{Z}$-graded rings
+  (i.\,e. their result corresponds to the special case $\mathfrak{m}=0$ of our result);
+ \item their presentation is formulated in terms of generators $x_{ij}(\xi)$ with $|\xi| \leq 2$ while for our purposes we need a presentation in terms
+  of the smaller set of generators with $| \xi |\leq 1$;
+ \item it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while work with
+  arbitrary coefficient ring $A$.
+\end{itemize}
 
@@
 
-There are several reasons why we can't simply refer to the original results of U.~Rehmann and C.~Soul{\'e}~\cite{Re75} or~\cite{RS76}.
-The first is that we want to prove Rehmann and Soul{\'e} prove that $G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$, while we want to %establish this fact starting from $m = 1$.
  %The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
-%(it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}).
+%().
 % (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
@@
  \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
-\begin{align} \nonumber \tag{$d_1$}
+\begin{align} 
+\nonumber \tag{$d_1$}
 [[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
+\nonumber \tag{$df_1$}
+[[x_{ij}(a t), x_{jk}(b t)],  x_{kl}(c)] & = [x_{ik}(a b t),  x_{kl}(c t)]\\
 \nonumber \tag{$e_1$}
-[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta \perp \gamma \end{align}
+[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta \perp \gamma \\
+\nonumber \tag{$ef_1$}
+[[x_{ij}(at), x_{jk}(bt)], x_{jl}(ct) ]& = 1
+\end{align}
  \end{lemma}

### 2018-08-19 paper.tex
Writing section on Rehmann theorem

@@
 Denote by $B$ the ring $\mathfrak{m}[t^{-1}] + A[t]$ with the obvious $\mathbb{Z}$-grading.
-Clearly, the $k$-th homogeneous component $B_k$ of $B$ equals $A\cdot t^k$ for $k \geq 0$ or $B_k = \mathfrak{m} \cdot t^k$ for $k<0$.
-If $a$ is a homogeneous element of $B$ we denote its homogeneous degree by $|a|$.
+In other words, as a module $B$ decomposes as a direct sum of its homogeneous components $\oplus_k B_k$,
+ where each $B_k$ is either $A\cdot t^k$ for $k \geq 0$ or $\mathfrak{m} \cdot t^k$ for $k<0$.
+%If $a$ is a homogeneous element of $B$ (i.\,e. an element of some $B_k$) we denote its homogeneous degree by $|a|$.
 
-In what follows we will be concerned with finding a presentation of the Steinberg group $\St(4, B)$ in terms of those generators $x_{ij}(\xi)$
- for which $\xi$ is homogeneous of degree $\leq 1$ (i.\,e. $|\xi| \leq 1$).
-Our presentation should be thought of as an extension of~\cite[Lemma~3.3]{Tu83} to the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
-Alternatively, our result can be thought of as a variant of the classical theorem of Rehmann~\cite{Re75} (cf. also with Rehmann--Soul{\'e} theorem in~\cite{RS76}).
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
+The aim of this section is to find a presentation of the Steinberg group $\St(\Phi, B)$ in terms of generators $x_{\alpha}(\xi)$
+ for which $\xi$ is homogeneous of degree $\leq 1$, see~\cref{prop:tul3.3} below.
+Our presentation should be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
+Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} which works for $\Phi=\rA_\ell$, $\ell\geq 4$ does not generalize to the case $\ell=3$, 
+ so we are forced to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on
+ finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
 
-There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and need to repeat arguments from these papers.
+For $m \geq 1$ consider the following set of Steinberg generators:
+\[\XX{m} = \{ x_{\alpha}(\xi) \mid \xi \in B_d,\text{ for } d\leq m,\ \alpha\in\Phi\}. \]
+Clearly, $\XX{m} \subseteq \XX{m+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
+
+\begin{rem}
+There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and need to reproduce arguments from these papers.
 \begin{itemize}
  \item Rehmann and Soul{\'e} deal with usual polynomial rings rather than $\mathbb{Z}$-graded rings
-  (i.\,e. their result corresponds to the special case $\mathfrak{m}=0$ of our result);
- \item their presentation is formulated in terms of generators $x_{ij}(\xi)$ with $|\xi| \leq 2$ while for our purposes we need a presentation in terms
-  of the smaller set of generators with $| \xi |\leq 1$;
- \item it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while work with
+  (i.\,e. their results correspond to the special case $\mathfrak{m}=0$ of our result);
+ \item Presentations from~\cite{Re75,RS76} are formulated in terms of generating set $\XX{2}$ which is not sufficient for our purposes
+  (we need a presentation in terms of $\XX{1}$);
+ \item it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we work with
   arbitrary coefficient ring $A$.
 \end{itemize} 
+\end{rem}
 
-For $m \geq 1$ consider the following set of generators:
-\[\XX{m} = \{ x_{ij}(\xi) \mid \xi \in B_k,\text{ for } k\leq m,\ 1\leq i, j\leq 4,\ i\neq j\}. \]
-It is obvious that $\XX{m} \subseteq \XX{m+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
-
-For $m\geq 1$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following three families of relations:
+For $m\geq 2$ define $G_m$ as the group presented by generators $\mathcal{X}_m$ and the following three families of relations:
 \begin{align}
- \label{eq:am} \tag{$a_m$} x_{ij}(\xi) x_{ij}(\eta) & = x_{ij}(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
- \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
- \nonumber                                                     &       & \xi \in B_k,\ \eta \in B_l,\ l,k\leq m;\\
- \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
- \nonumber                                                    &  & \xi \in B_k,\ \eta \in B_l,\ l, k, l+k \leq m.
+ \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
+ \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\beta}(\eta))] &  = 1, & \text{in the case $\alpha+\beta\not\in\Phi\cup\{0\}$,}\\
+ \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
+ \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\beta}(\eta)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\xi\eta), & \text{in the case $\alpha+\beta\in \Phi$,}\\
+ \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m;
  \end{align}
-
- %The second is that they prove their results only in the special case $B = A[t]$, moreover, they make assumptions about the ground ring $A$
-%().
+For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $a_1, b_1, c_1$ as above and the following extra family of relations:
+\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta}(\eta)], x_{\gamma}(\zeta) ] & = 1, & \xi,\eta,\zeta\in B_1,\ \alpha + \beta \in \Phi,\ \alpha + \beta + \gamma \not\in \Phi\cup\{0\}.
+\end{align}
 % (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
-
- \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
-\begin{align} 
-\nonumber \tag{$d_1$}
-[[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
-\nonumber \tag{$df_1$}
-[[x_{ij}(a t), x_{jk}(b t)],  x_{kl}(c)] & = [x_{ik}(a b t),  x_{kl}(c t)]\\
-\nonumber \tag{$e_1$}
-[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta \perp \gamma \\
-\nonumber \tag{$ef_1$}
-[[x_{ij}(at), x_{jk}(bt)], x_{jl}(ct) ]& = 1
-\end{align}
- \end{lemma}
 
@@
  a map $\theta_n\colon G_n \to G_{n+1}$.
-The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
-\begin{lemma}\label{lem:tul3.3}
- Let $\Phi$ be a simply-laced root systems of rank $\geq 3$. 
- Then $ $
- Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
+Our main goal is to show the following result.
+\begin{prop}\label{prop:tul3.3}
+ For $n\geq 1$ the map $\theta_n$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
+  and four families of relations $a_1$, $b_1$, $c_1$, $d_1$.
+\end{prop}
+
+ \begin{lemma} In the group $G_1$ the following relation holds:
+\begin{align} 
+ [[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha+\beta}(a b t),  x_{\gamma}(c t)].
+\end{align}
  \end{lemma}
-Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
- %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
-Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.
 

### 2018-08-19 paper.tex
Writing section on Rehmann theorem

@@
 Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} which works for $\Phi=\rA_\ell$, $\ell\geq 4$ does not generalize to the case $\ell=3$,
+%TODO: Explain why we are dealing with general \Phi rather than just the case \rA_3 -- Reason the difficulty is the same
  so we are forced to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on
  finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
+
+We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi \times \Phi \times \Phi$ an {\it $\rA_3$-triple}
+ if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
+ $\xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.$ %TODO: Draw better diagram :)
 
@@
 
+\begin{comment} 
 \begin{rem}
@@
   (we need a presentation in terms of $\XX{1}$);
- \item it is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we work with
-  arbitrary coefficient ring $A$.
+ \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we work with
+  arbitrary coefficient rings $A$.
 \end{itemize} 
 \end{rem}
+\end{comment} %TODO: Find proper place for this discussion - it may not be appropriate here
 
@@
  \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\beta}(\eta)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\xi\eta), & \text{in the case $\alpha+\beta\in \Phi$,}\\
- \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m;
+ \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
  \end{align}
-For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $a_1, b_1, c_1$ as above and the following extra family of relations:
-\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta}(\eta)], x_{\gamma}(\zeta) ] & = 1, & \xi,\eta,\zeta\in B_1,\ \alpha + \beta \in \Phi,\ \alpha + \beta + \gamma \not\in \Phi\cup\{0\}.
+For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $a_1, b_1, c_1$ as above and the following additional family of relations:
+\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta+\gamma}(\eta)], x_{\beta}(\zeta) ] & = 1, 
+ & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple }.
 \end{align}
@@
  For $n\geq 1$ the map $\theta_n$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
-  and four families of relations $a_1$, $b_1$, $c_1$, $d_1$.
+  and families of relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
 \end{prop}
-
- \begin{lemma} In the group $G_1$ the following relation holds:
-\begin{align} 
- [[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha+\beta}(a b t),  x_{\gamma}(c t)].
-\end{align}
- \end{lemma}
-
+%TODO: Deduce 2nd assertion from 1st
+To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$.
+Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
 %Denote by $F(S)$ the free group on the generating set $S$.
@@
 %well, not so clear, actually :)
-To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$.
-Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
 
@@
 
-To prove that $\theta_m$ is an isomorphism we construct the missing generators of $G_{m+1}$ in $G_m$ and then show that they satisfy relations $\RR{m+1}$.
+\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in the group $G_1$:
+\begin{align} 
+ [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha+\beta}(a b t),  x_{\gamma}(c t)].
+\end{align}
+ \end{lemma}
+\begin{proof}
+ \begin{align*}
+   [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] = [{}^{x_{\beta}(b t)}\!x_{\alpha}(at), [x_{\gamma}(c),x_{\beta}(b t)]] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
+                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\
+                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(bct)] & \text{ by $(d_1)$. \qedhere}
+ \end{align*}
+
+\end{proof}
+
+To prove that $\theta_m$ is an isomorphism we construct the missing generators of $G_{m+1}$ in $G_m$ and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.
 
@@
 We can find root subsystem $\Psi \subseteq \Phi$ of type $\mathsf{A}_3$ containing the roots $\alpha, \alpha'$.
-Choose basis $\{\alpha,\beta,\gamma\}$ of $\Psi$ so that $\alpha'=\beta$ and the Dynkin diagram of $\Psi$ looks as follows:
-\begin{equation}\label{eq:diagA3} \xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.\end{equation}
+Choose basis $\{\alpha,\beta,\gamma\}$ of $\Psi$ so that $\alpha'=\beta$ and the Dynkin diagram of $\Psi$ looks as follows: HERE WAS A DIAGRAM
+
 Let us verify~\eqref{eq:verify-bmp1}:

### 2018-08-19 paper.tex
Minor

@@
  \end{align}
-For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $a_1, b_1, c_1$ as above and the following additional family of relations:
+For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $(a_1), (b_1), (c_1)$ as above and the following additional family of relations:
 \begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta+\gamma}(\eta)], x_{\beta}(\zeta) ] & = 1, 
@@
 
-It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
- a map $\theta_n\colon G_n \to G_{n+1}$.
-Our main goal is to show the following result.
+The natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces a map $\theta_n\colon G_n \to G_{n+1}$.
+Our goal is to show the following result.
 \begin{prop}\label{prop:tul3.3}
@@
 %TODO: Deduce 2nd assertion from 1st
-To prove~\cref{lem:tul3.3} it suffices to show that the natural map $\theta_m \colon G_m \to G_{m+1}$ is an isomorphism for $m\geq 2$.
+Notice that the second assertion follows from the first one.
 Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
@@
 
-The following lemma is reminiscent of~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
+The following lemma is similar to~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
 \begin{lemma}
@@
  Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
- Therefore, we can repeat the argument of~\cite[Proposition 1.1]{Re75} verbatim.
+ Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim.
 \end{proof}
 
-\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in the group $G_1$:
+\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in $G_1$:
 \begin{align} 
- [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha+\beta}(a b t),  x_{\gamma}(c t)].
+ [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha}(at), x_{\beta+\gamma}(N_{\beta, \gamma}b c t)].
 \end{align}
@@
    [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] = [{}^{x_{\beta}(b t)}\!x_{\alpha}(at), [x_{\gamma}(c),x_{\beta}(b t)]] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
-                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\
-                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(bct)] & \text{ by $(d_1)$. \qedhere}
+                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\ 
+                                                       %TODO:  Missing structure constants...
+                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct)] & \text{ by $(d_1)$. \qedhere}
  \end{align*}
@@
 
-To prove that $\theta_m$ is an isomorphism we construct the missing generators of $G_{m+1}$ in $G_m$ and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.
+To construct a map splitting to $\theta_m$ we construct the missing generators of $G_{m+1}$ in $G_m$ 
+ and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.
 

### 2018-08-20 paper.tex
Used d1

@@
 
-We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi \times \Phi \times \Phi$ an {\it $\rA_3$-triple}
+We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi^3$ an {\it $\rA_3$-triple}
  if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
@@
  \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
- \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\beta}(\eta))] &  = 1, & \text{in the case $\alpha+\beta\not\in\Phi\cup\{0\}$,}\\
+ \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
  \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
- \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\beta}(\eta)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\xi\eta), & \text{in the case $\alpha+\beta\in \Phi$,}\\
+ \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
  \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
  \end{align}
-For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_m$, three families of relations $(a_1), (b_1), (c_1)$ as above and the following additional family of relations:
-\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha}(\xi), x_{\beta+\gamma}(\eta)], x_{\beta}(\zeta) ] & = 1, 
- & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple }.
+For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_1$, 
+three above families of relations $(a_1), (b_1), (c_1)$ and the following additional family of relations:
+\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha+\beta+\gamma}(\xi), x_{-\gamma}(\eta)], x_{\beta+\gamma}(\zeta) ] & = 1, 
+ & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple. }
 \end{align}
@@
 
-The natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces a map $\theta_n\colon G_n \to G_{n+1}$.
+The obvious embedding of generators $\mathcal{X}_m \subseteq \mathcal{X}_{m+1}$ induces a map $f_m\colon G_m \to G_{m+1}$.
 Our goal is to show the following result.
 \begin{prop}\label{prop:tul3.3}
- For $n\geq 1$ the map $\theta_n$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
-  and families of relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
+ For $m\geq 1$ the map $f_m$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
+  and relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
 \end{prop}
@@
  Suppose $m \geq 1$.
- Let $\alpha, \beta, \alpha', \beta'$ be such that $\alpha + \beta = \alpha' + \beta'$.
+ Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
  Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
   $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
- Then in the group $G_m$ the following relations hold:
- \begin{align}
-  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] &= [x_{\alpha'}(\xi'), x_{\beta'}(\eta')] & \\
-  \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] & = 1 & \text{in the case } \gamma\in\{\alpha, \beta, \alpha + \beta\},\\
-  \nonumber                                     &                          & \text{$\zeta \in B_{k''}$, $k''\leq m$.}
- \end{align}
+ Then the following relations holds in $G_m$:
+ \begin{equation}
+  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
+ \end{equation}
+ Moreover for every $\zeta \in B_{k''}$, $k''\leq m$ and $\gamma\in\{\alpha, \beta, \alpha + \beta\}$
+  the following relation holds in $G_m$:
+ \begin{equation}
+ \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
+ \end{equation}
 \end{lemma}
@@
  Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
- Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim.
+ Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim in our situation.
+ %TODO: Write down this argument, at least a part of it?
 \end{proof}
 
-\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ the following relation holds in $G_1$:
+For every $\xi \in B_{m+1}$ and $\alpha\in \Phi$ there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$,
+so we can define the following element of $G_m$:
+\begin{equation} \label{eq:defmpn} S_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)].\end{equation} 
+From~\eqref{item:i} it follows that $S_\alpha(\xi)$ does not depend of the choice of $\alpha'$.
+
+%To show that $f_m$ is an isomorphism we construct a map $g_m \colon G_{m+1} \to G_m$ in the opposite direction.
+%We define it on generators $\mathcal{X}_{m+1}$ and then verify that it is well defined.
+%Clearly, $g_m$ should be defined as the identity map on the subset of generators $\mathcal{X}_m \subseteq \mathcal{X}_{m+1}$.
+%Now if $x_{\alpha}(\xi)$ is an element of $\mathcal{X}_{m+1}\setminus \mathcal{X}_m$
+%there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$, 
+% therefore we can set 
+%\[g_m(x_\alpha(\xi)) = [x_{\alpha-\alpha'}(\xi'), x_{\alpha'}(N_{\alpha-\alpha',\alpha'} t)].\]
+%It follows from~\eqref{item:i} that this definition does not depend on the choice of $\alpha'$.
+
+Let us show that elements $S_\alpha(\xi)$ satisfy the relations $(a_{m+1})$, $(b_{m+1})$ and $(c_{m+1})$.
+From \eqref{eq:H1ii} and~\eqref{item:ii} it follows that $S_\alpha(\xi)$  satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
+\begin{comment}
+\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ and $a,b,c \in A$ the following relation holds in $G_1$:
 \begin{align} 
- [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] & = [x_{\alpha}(at), x_{\beta+\gamma}(N_{\beta, \gamma}b c t)].
+ [x_{\alpha}(a), [x_{\beta}(b t), x_{\gamma}(c t)]] & = [x_{\beta+\alpha}(N_{\beta, \alpha}a b t), x_{\gamma}(ct)].
 \end{align}
@@
  \begin{align*}
-   [[x_{\beta}(b t), x_{\alpha}(a t)],  x_{\gamma}(c)] = [{}^{x_{\beta}(b t)}\!x_{\alpha}(at), [x_{\gamma}(c),x_{\beta}(b t)]] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
-                                                       = {}^{x_{\beta}(b t)}[ x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct) ] & \text{ by $(b_1)$ and $(c_1)$}\\ 
-                                                       %TODO:  Missing structure constants...
-                                                       = [x_{\alpha}(at), x_{\beta +\gamma}(N_{\beta,\gamma}bct)] & \text{ by $(d_1)$. \qedhere}
+   [x_{\alpha}(a), [x_{\beta}(b t), x_{\gamma}(c t)]] = [[x_{\alpha}(a), x_{\beta}(b t)], {}^{x_{\beta}(b t)}\!x_{\gamma}(ct)] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
+                                                       = {}^{x_{\beta}(b t)}[x_{\alpha +\beta}(N_{\alpha,\beta}abt), x_{\gamma}(ct) ] & \text{ by $(b_1)$ and $(c_1)$}\\ 
+                                                       = [x_{\alpha +\beta}(N_{\alpha,\beta}abt), x_{\gamma}(ct)] & \text{ by $(d_1)$. \qedhere}
  \end{align*}  
+\end{proof}
+\end{comment}
 
-\end{proof}
+\begin{lemma} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
+ $a\in A$, $\xi \in B_k$, $k \leq 0$ the following relation holds in $G_m$: 
+\begin{equation}
+\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)].
+\end{equation}
+\end{lemma}
+\begin{proof}
+By \cite[Lemma~3.1.2]{RS76} we can assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
+\begin{align*}
+   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
+ = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
+ = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$}
+\end{align*} 
+There are two cases.
+\begin{enumerate}
+ \item \label{case:cm-1} Case $m=1$, $k = 0$.
+ \begin{align*}
+   RHS  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$.}\\
+        = [x_\alpha(t\xi), x_\beta(at^m)]                                 & \text{ by~\eqref{item:i}. }   
+ \end{align*}  
+ This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. Why is this true?
 
-To construct a map splitting to $\theta_m$ we construct the missing generators of $G_{m+1}$ in $G_m$ 
- and then show that they satisfy relations $a_{m+1}$, $b_{m+1}$ and $c_{m+1}$.
-
-For every $\xi \in B_{m+1}$ and $\alpha\in \Phi$ there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$.
-Thus, we can make the following definition:
-\begin{equation} \label{eq:defmpn} x_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)],\end{equation} 
-and from~\eqref{item:i} its correctness (i.\,e. the independence of the choice of $\alpha'$) follows.
-
-We now turn to the verification of relations $(a_{m+1})$, $(b_{m+1})$, $(c_{m+1})$.
-Notice first that \eqref{eq:H1ii} and~\eqref{item:ii} immediately imply $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
-
-To verify relations $(c_{m+1})$ it suffices to show that
-\begin{equation}
-\label{eq:verify-bmp1} [x_\alpha(\xi), x_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)],\ a \in A,\ \xi \in B_k,\ k\leq 0.
-\end{equation}
-We can find root subsystem $\Psi \subseteq \Phi$ of type $\mathsf{A}_3$ containing the roots $\alpha, \alpha'$.
-Choose basis $\{\alpha,\beta,\gamma\}$ of $\Psi$ so that $\alpha'=\beta$ and the Dynkin diagram of $\Psi$ looks as follows: HERE WAS A DIAGRAM
-
-Let us verify~\eqref{eq:verify-bmp1}:
+ \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $k < 0$.
  \begin{align*}
-   [x_\alpha(\xi), x_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{eq:defmpn} for a suitable $a'\in A$} \\ 
- = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
- = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$} \\
- = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
+ RHS = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
  %TODO: There's a mistake at this moment --- k = 0, m = 1 and the needed relation is not in G_1 -- :(
@@
 \end{align*}
+
+\end{enumerate}
+\end{proof}
 

### 2018-08-21 paper.tex
Slightly rewritten text

@@
  Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
- Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
-  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
+ Assume, moreover, that $\xi \in B_d$, $\xi' \in B_{d'}$, $\eta \in B_e$, $\eta' \in B_{e'}$ are such that 
+  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $d,d',e,e'\leq m$ satisfying $d+e=d'+e' = m+1$.
  Then the following relations holds in $G_m$:
@@
 
-\begin{lemma} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
- $a\in A$, $\xi \in B_k$, $k \leq 0$ the following relation holds in $G_m$: 
+\begin{lemma} \label{lem:bmp1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
+ $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
 \begin{equation}
-\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)].
+\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
 \end{equation}
@@
 \begin{proof}
-By \cite[Lemma~3.1.2]{RS76} we can assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
+By \cite[Lemma~3.1.2]{RS76} we may assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
 \begin{align*}
@@
 \end{align*} 
-There are two cases.
+Denote by $R$ the expression in the right hand side of the above formula.
 \begin{enumerate}
- \item \label{case:cm-1} Case $m=1$, $k = 0$.
+ \item \label{case:cm-1} Case $m=1$, $d = 0$.
  \begin{align*}
-   RHS  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$.}\\
+   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$}\\
         = [x_\alpha(t\xi), x_\beta(at^m)]                               & \text{ by~\eqref{item:i}. }   
@@
 
- \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $k < 0$.
+ \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $d < 0$.
  \begin{align*}
- RHS = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
- %TODO: There's a mistake at this moment --- k = 0, m = 1 and the needed relation is not in G_1 -- :(
+ R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
  = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
- = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}.}
+ = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}. \qedhere}
 \end{align*}
@@
 
-Now, let us show that relations $(b_{m+1})$ hold. 
-Without loss of generality we may also assume $k \leq l=m+1$, thus $\eta = bt^{m+1}$ for some $b\in A$.
-
+It will be convenient for us to extend the definition of $S_\alpha(\xi)$ by allowing $\xi$ to take values in $B_d$ for $d\leq m$.
+In this case we simply set $S_\alpha(\xi) = x_\alpha(\xi)$.
+\begin{lemma}
+ For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
+ the following relation holds in $G_m$:
+  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
+\end{lemma}
+\begin{proof}
+Write $\eta = bt^{m+1}$ for some $b\in A$.
 \begin{enumerate}
-\item \label{case:1} First consider the case $k \leq 0$. There are two further subcases.
+\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
  \begin{enumerate}
   \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
-  As before, without loss of generality we may assume that $\alpha, \alpha'$ are contained in a root system $\Psi$ of type $\mathsf{A}_3$,
-   whose simple roots are labeled as in~\eqref{eq:diagA3} and, moreover, $\alpha'=\alpha + \beta$.
-  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we get (recall that $\xi \in B_k$):
+  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
+  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
+  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
    \begin{multline} \nonumber
-   [x_\alpha(\xi), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
-  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
+   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
+  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
   \end{multline}
-  \item Case $\alpha \perp \alpha'$. As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
+  %What this really proves: $b_{m}(\alpha, |\xi|, -\gamma, 1)$ and $b_m(\alpha, |\xi|, \alpha+\beta+\gamma, m)$ implies $b_{m+1}(\alpha, |\xi|, \alpha+\beta, m+1 )$.
+  \item Case $\alpha \perp \alpha'$. 
+  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
   \begin{multline} \nonumber
-   [x_\alpha(\xi), x_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(bt^m), x_{-\beta}(t)]] = \\   
-  = [[x_\alpha(\xi), x_{\beta+\gamma}(bt^m)], {}^{x_{\beta+\gamma}(bt^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(bt^m)}\![x_{\alpha+\beta+\gamma}(bt^m\xi), x_{-\beta}(t)] = 1.
+   [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
+  = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
   \end{multline}
@@
 
-\item \label{case:2} Now assume $1 \leq k \leq m+1$. 
-At first we want to prove $(b_{m+1})$ only in the special case $\xi=t^k$.
-We proceed by induction on $k$ starting with $k=1$.
-Again, there are two cases.
+\item \label{case:2} Now assume $1 \leq d \leq m+1$.
+At first we want to prove~\eqref{eq:verify-bmp2} only in the special case $\xi=t^d$,
+We proceed by induction on $d$, so we can assume that \eqref{eq:verify-bmp2} holds for $\xi = t^e$, $e<d$.
+Again, there are two subcases.
 \begin{enumerate}
  \item \label{case:2a} Case $\alpha\not\perp\alpha'$ is handled similarly to the Case~\eqref{case:1a} with the only
-  difference that we have to refer to the inductive assumption rather than~\eqref{eq:bm} in the case $k=m+1$.
+  difference that we must refer to the inductive assumption instead of~\eqref{eq:bm} in the case $d=m+1$:
+  %TODO: No real induction going on here...
   \begin{multline} \nonumber
-   [x_\alpha(t^k), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(t^k), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
-  = [[x_\alpha(t^k), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
+   [S_\alpha(t^d), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(t^d), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
+  = [[S_\alpha(t^d), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1.
   \end{multline}
@@
 \begin{align*}
-{}^{x_\gamma(t^k)}x_\alpha(bt^{m+1}) = {}^{x_\gamma(t^k)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by $(c_{m+1})$}\\
- = [x_{-\beta}(b't^{m+1}), {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
- = [[x_{-\beta-\gamma}(b''t^{m+1-k}), x_\gamma(t^k)], {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]          & \text{ by $(c_{m+1})$}\\
- = [x_{-\beta-\gamma}(b''t^{m+1-k)}), [x_\gamma(t^k), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-k \leq m$}\\
- = x_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_{m+1})$.} \end{align*}
+{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
+ = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
+ = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$}\\
+ = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
+ = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$,\eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \end{align*}
  Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
@@
 \end{enumerate}
-Thus we have demonstrated $(b_{m+1})$ in the special case $a=1$.
-\item Now let us prove $(b_{m+1})$ for arbitrary $\xi = at^k$, $a\in A$ and $1\leq k\leq m+1$. Again, there are two subcases.
+This finishes the proof of~\eqref{eq:verify-bmp2} in the special case $a=1$.
+\item Now we deduce~\eqref{eq:verify-bmp2} for arbitrary $\xi = at^d$, $a\in A$ and $1\leq d\leq m+1$. Again, there are two subcases.
 \begin{enumerate}
 \item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
- \begin{align*} [x_\alpha(at^k), x_{\alpha + \beta}(bt^{m+1})] = [x_\alpha(at^k), [x_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b)]] & \text{ by $(c_{m+1})$} \\
-  = [[x_\alpha(at^k), x_{\alpha+\beta+\gamma}(t^{m+1})], {}^{x_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b)] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
+ \begin{align*} 
+ [S_\alpha(at^d), S_{\alpha + \beta}(bt^{m+1})] = 
+ [S_\alpha(at^d), [S_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b')]] & \text{ by~\cref{lem:bmp1}} \\
+  = [[x_\alpha(at^d), S_{\alpha+\beta+\gamma}(t^{m+1})], {}^{S_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b')] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
   = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
 \item Case $\alpha \perp \alpha'$.
- % mu        0  1 m+1
- % vu        1  0 k
- % mu'       0  1 m+1-k
- % mu - mu'  0  0 k
- % nu + mu'  1  1 m+1
- %           a  b t
-The required identity follows from the following chain of equalities:
 \begin{align*}
- x_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{x_{-\beta}(t^k)}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
- = {}^{x_{-\beta}(t^k)}\![x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(c_{m+1})$} \\
- = [x_{\alpha}(bt^{m+1}) x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(b_k)$ or Case~\eqref{case:2} if $k=m+1$ }\\
- = {}^{x_{\alpha}(bt^{m+1})}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by~\eqref{eq:H1ii} and $(c_{m+1})$} \\
- = x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by Case~\eqref{case:3a}.}
+ S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
+ = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
+ = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\cref{lem:bmp1} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
+ = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
+ = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}
 \end{align*}
+from which the required identity follows. \qedhere
 \end{enumerate}
 \end{enumerate}
+\end{proof}
 

### 2018-08-21 paper.tex
Minor fix

@@
  $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
-\begin{equation}
-\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
+\begin{equation} \nonumber
+[x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
 \end{equation}
@@
 In this case we simply set $S_\alpha(\xi) = x_\alpha(\xi)$.
+
+Now suppose  $1 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $d\leq m$) or~\cref{lem:bmp1} (in the case $d=m+1$) imply that
+\begin{equation} \label{eq:verify-bmp1'} 
+[S_\alpha(\xi), x_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
+\end{equation}
+
 \begin{lemma}
@@
  = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
- = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$}\\
+ = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by~\eqref{eq:verify-bmp1'}}\\
  = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
- = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$,\eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \end{align*}
+ = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$ and \eqref{eq:verify-bmp1'}} \end{align*}
  Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
@@
  S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
- = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
- = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\cref{lem:bmp1} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
- = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
+ = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'}} \\
+ = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
+ = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
  = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}

### 2018-08-27 paper.tex
Minor fixes

@@
 \begin{align*}
-{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
+{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
  = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
@@
  = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
- = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$ and \eqref{eq:verify-bmp1'}} \end{align*}
+ = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by~\eqref{eq:verify-bmp1'}} \end{align*}
  Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):

### 2018-08-28 paper.tex
Minor

@@
 
-Now suppose  $1 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $d\leq m$) or~\cref{lem:bmp1} (in the case $d=m+1$) imply that
+Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $1\leq d\leq m$) or~\cref{lem:bmp1} (in the case $d=0,m+1$) imply that
 \begin{equation} \label{eq:verify-bmp1'} 
@@
   \end{multline}
-  %What this really proves: $b_{m}(\alpha, |\xi|, -\gamma, 1)$ and $b_m(\alpha, |\xi|, \alpha+\beta+\gamma, m)$ implies $b_{m+1}(\alpha, |\xi|, \alpha+\beta, m+1 )$.
+  What this really proves: $PERP(d, 1)$ and $NONPERP(d, m)$ imply $NONPERP(d, m+1)$.
   \item Case $\alpha \perp \alpha'$. 
@@
   \begin{multline} \nonumber
-   [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
-  = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
+   [S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
+  = [[S_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
   \end{multline}

### 2018-08-28 paper.tex
Written down claims

@@
 \begin{proof}
-Write $\eta = bt^{m+1}$ for some $b\in A$.
+We can assume that $\eta = bt^{m+1}$ for some $b\in A$.
+
+Claim 1: $\perp(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$.
+\begin{align*}
+[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]]
+ & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
+ = [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)]
+ & \text{ by~$\perp(d, 1)$}\\
+ = 1
+ & \text{ by~$\angle(d, m)$.} \end{align*}
+
+Claim 2: $\perp(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$.
+ \begin{align*}
+[S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(t), x_{-\beta}(b't^m)]]
+ & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
+ = [[S_\alpha(t^d), x_{\alpha+\beta+\gamma}(t)], {}^{x_{\alpha+\beta+\gamma}(t)}\!x_{-\gamma}(b't^m)]
+ & \text{ by~$\perp(d, 1)$}\\
+ = 1
+ & \text{ by~$\angle(d, m)$.} \end{align*}
+
+Claim 2: (first line of equalities proves nothing for $d=0$)
+\begin{align*}
+{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] 
+& \text{ by~\cref{lem:bmp1}}\\
+ = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
+ & \text{ by $\angle(d, m+1)$}\\
+ = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
+ & \text{ by~\eqref{eq:verify-bmp1'}}\\
+ = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
+ & \text{ by~\eqref{eq:H1iii} and~$\perp(m+1-d, 0)$}\\
+ = S_{\alpha}(b'''t^{m+1})                                                                            
+ & \text{ by~\eqref{eq:verify-bmp1'}} \end{align*}
+
+\begin{align*}
+ S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
+ & \text{ by previous line}\\
+ = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:verify-bmp1'}} \\
+ = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:verify-bmp1'} and $\angle(d, m+1)$ }\\
+ = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
+ = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
+ & \text{ by $\angle(m+1, m+1)$,}
+\end{align*}
+
 \begin{enumerate}

### 2018-08-29 paper.tex
Broken up the last lemma into 4 separate lemmas

--- 2018-08-28 paper.tex
@@
 
-\begin{lemma}
- For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
- the following relation holds in $G_m$:
-  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
+We need to introduce additional notation.
+For $a,b\leq m+1$ we denote by $\bot(a, b)$ (resp. $\angle(a,b)$) the set consisting of all relations $[S_\alpha(\xi), S_{\alpha'}(\eta)] = 1$
+for which $\xi \in B_a$, $\eta \in B_b$ and $\alpha$ and $\alpha'$ are orthogonal (resp. form a sharp angle). 
+We denote by $\bot_0(d, m+1)$ the subset of $\bot(d, m+1)$
+consisting of those relations for which, moreover, $\eta = t^{m+1}$.
+
+\begin{lemma} \label{claim1} For $d\leq m+1$ relations $\bot_0(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$. \end{lemma}
+\begin{proof}
+Without loss of generality we may assume that $\alpha' = \alpha + \beta$
+  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
+Write $\eta = bt^{m+1}$ for some $b\in A$.
+\begin{align*} 
+[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
+= [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(d, 1)$}\\
+= 1
+ & \text{ by~$\angle(d, m)$. \qedhere} \end{align*} 
+\end{proof}
+
+\begin{lemma} \label{claim2} For $1\leq d\leq m+1$ relations $\angle(d, m+1)$ imply $\bot_0(d, m+1)$. \end{lemma}
+\begin{proof}
+As before, without loss of generality we may assume $\alpha' = \gamma$ for some $\mathsf{A}_3$-triple $(\alpha, \beta, \gamma)$.
+ \begin{align*}
+ {}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
+ = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
+ & \text{ by $\angle(d, m+1)$}\\
+ = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
+ & \text{ by~\eqref{eq:verify-bmp1'}}\\
+ = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
+ & \text{ by~\eqref{eq:H1iii} and $(b_{m+1-d})$}\\
+ = S_{\alpha}(b'''t^{m+1})                                                                            
+ & \text{ by~\eqref{eq:verify-bmp1'}.} \end{align*}
+Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
+ $b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b,$ from which the claim follows.
+\end{proof}
+
+\begin{lemma} \label{claim3}
+ For $d\leq m+1$ relations $\bot_0(d, m+1)$, $\angle(d, d)$ and $\angle(m+1, m+1)$ imply $\bot(d, m+1)$.
 \end{lemma}
 \begin{proof}
-Write $\eta = bt^{m+1}$ for some $b\in A$.
+ \begin{align*} 
+ S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
+ & \text{ by $\bot_0(m+1, d)$}\\
+ = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:verify-bmp1'}} \\
+ = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:verify-bmp1'} and $\angle(d, d)$ }\\
+ = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
+ & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
+ = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
+ & \text{ by $\angle(m+1, m+1)$. \qedhere}
+\end{align*}
+\end{proof}
+
+\begin{lemma}
+Elements $S_\alpha(\xi)$ satisfy relations $(b_{m+1})$.
+ \end{lemma}
+\begin{proof}
+We need to show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\perp(d, m+1)$ for $d\leq m+1$.
+\begin{enumerate}
+ \item Relations $\angle(d, m+1)$, $d\leq m$ follow from~\cref{claim1}. 
+ \item Relations $\bot(d, m+1)$ with $d\leq 0$ can verified by direct computation:
+ \begin{align*} 
+ [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] & \text{ by~\eqref{item:i},\eqref{eq:defmpn}} \\
+ = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] &
+ \text{ by \eqref{eq:H1iii} and $(b_1)$} \\
+ = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] &
+ \text{ by $(b_m)$ and $(c_m)$} \\
+ = 1 & \text{ by $(b_m)$.}
+\end{align*}
+ \item Relations $\bot_0(d, m+1)$ with $1\leq d\leq m$ follows from~\cref{claim2}.
+ \item Relations $\angle(m+1, m+1)$ follow from~\cref{claim1}, consequently relations $\bot_0(m+1, m+1)$ follow from~\cref{claim2}.
+ \item Relations $\bot(d, m+1)$, $0\leq d\leq m+1$ follow from~\cref{claim3} and the previous two assertions.
+\end{enumerate}
+\begin{comment}
  \begin{enumerate}
@@
 \end{enumerate}
+\end{comment}
 \end{proof}

### 2018-08-29 paper.tex
Minor fixes

@@
 \begin{equation} \label{eq:verify-bmp1'} 
-[S_\alpha(\xi), x_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
+[S_\alpha(\xi), S_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
 \end{equation}
@@
 We need to introduce additional notation.
-For $a,b\leq m+1$ we denote by $\bot(a, b)$ (resp. $\angle(a,b)$) the set consisting of all relations $[S_\alpha(\xi), S_{\alpha'}(\eta)] = 1$
+For $a,b\leq m+1$ we denote by $\bot(a, b)$ (resp. $\angle(a,b)$) the family of all relations $[S_\alpha(\xi), S_{\alpha'}(\eta)] = 1$
 for which $\xi \in B_a$, $\eta \in B_b$ and $\alpha$ and $\alpha'$ are orthogonal (resp. form a sharp angle). 
-We denote by $\bot_0(d, m+1)$ the subset of $\bot(d, m+1)$
-consisting of those relations for which, moreover, $\eta = t^{m+1}$.
+We denote by $\bot_0(a, b)$ the subset of $\bot(a, b)$
+consisting of those relations for which $\xi = t^{a} \in B_a$.
 
-\begin{lemma} \label{claim1} For $d\leq m+1$ relations $\bot_0(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$. \end{lemma}
+\begin{lemma} \label{claim1} In $G_m$ relations $\bot_0(1, d)$ and $\angle(d, m)$ imply $\angle(d, m+1)$ for $d\leq m+1$ \end{lemma}
 \begin{proof}
@@
 [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
-= [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(d, 1)$}\\
+= [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(1, d)$}\\
 = 1
@@
 
-\begin{lemma} \label{claim2} For $1\leq d\leq m+1$ relations $\angle(d, m+1)$ imply $\bot_0(d, m+1)$. \end{lemma}
+\begin{lemma} \label{claim2} In $G_m$ relations $\angle(d, m+1)$ imply $\bot_0(d, m+1)$ for  $1\leq d\leq m+1$. \end{lemma}
 \begin{proof}
@@
 \begin{lemma} \label{claim3}
- For $d\leq m+1$ relations $\bot_0(d, m+1)$, $\angle(d, d)$ and $\angle(m+1, m+1)$ imply $\bot(d, m+1)$.
+ In $G_m$ relations $\bot_0(d, m+1)$, $\angle(d, d)$ and $\angle(m+1, m+1)$ imply $\bot(d, m+1)$ for $d\leq m+1$.
 \end{lemma}
@@
  S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
- & \text{ by $\bot_0(m+1, d)$}\\
+ & \text{ by $\bot_0(d, m+1)$}\\
  = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
@@
 \begin{proof}
-We need to show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\perp(d, m+1)$ for $d\leq m+1$.
+We need to show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\bot(d, m+1)$ for $d\leq m+1$.
 \begin{enumerate}
@@
 \end{align*}
- \item Relations $\bot_0(d, m+1)$ with $1\leq d\leq m$ follows from~\cref{claim2}.
+ \item Relations $\bot_0(d, m+1)$ with $1\leq d\leq m$ follow from~\cref{claim2}.
  \item Relations $\angle(m+1, m+1)$ follow from~\cref{claim1}, consequently relations $\bot_0(m+1, m+1)$ follow from~\cref{claim2}.

### 2018-08-29 paper.tex
Explained more philosophy

@@
 Denote by $B$ the ring $\mathfrak{m}[t^{-1}] + A[t]$ with the obvious $\mathbb{Z}$-grading.
-In other words, as a module $B$ decomposes as a direct sum of its homogeneous components $\oplus_k B_k$,
+In other words, as a module $B$ decomposes into a direct sum of its homogeneous components $\oplus_k B_k$,
  where each $B_k$ is either $A\cdot t^k$ for $k \geq 0$ or $\mathfrak{m} \cdot t^k$ for $k<0$.
-%If $a$ is a homogeneous element of $B$ (i.\,e. an element of some $B_k$) we denote its homogeneous degree by $|a|$.
-
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
-The aim of this section is to find a presentation of the Steinberg group $\St(\Phi, B)$ in terms of generators $x_{\alpha}(\xi)$
- for which $\xi$ is homogeneous of degree $\leq 1$, see~\cref{prop:tul3.3} below.
-Our presentation should be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
-Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} which works for $\Phi=\rA_\ell$, $\ell\geq 4$ does not generalize to the case $\ell=3$,
-%TODO: Explain why we are dealing with general \Phi rather than just the case \rA_3 -- Reason the difficulty is the same
- so we are forced to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on
- finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
-
-We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi^3$ an {\it $\rA_3$-triple}
- if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
- $\xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.$ %TODO: Draw better diagram :)
 
@@
 
-\begin{comment} 
+%If $a$ is a homogeneous element of $B$ (i.\,e. an element of some $B_k$) we denote its homogeneous degree by $|a|$.
+
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
+The main result of this section is~\cref{prop:tul3.3} which gives a presentation of Steinberg group $\St(\Phi, B)$ in terms of generating set $\mathcal{X}_1$.
+In the sequel we will need this presentation only in the special case $\Phi=\rA_3$.
+However, we preferred to prove a more general statement since the proof in the special case $\Phi=\rA_3$ has almost the same length.
+
+This presentation give by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
+Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$,
+%TODO: Explain why we are dealing with general \Phi rather than just the case \rA_3 -- Reason the difficulty is the same
+ which forces us to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on
+ finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
+
 \begin{rem}
-There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and need to reproduce arguments from these papers.
+There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and instead need to reprove everything by hand.
 \begin{itemize}
@@
   (i.\,e. their results correspond to the special case $\mathfrak{m}=0$ of our result);
- \item Presentations from~\cite{Re75,RS76} are formulated in terms of generating set $\XX{2}$ which is not sufficient for our purposes
-  (we need a presentation in terms of $\XX{1}$);
- \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we work with
-  arbitrary coefficient rings $A$.
+ \item Presentations from~\cite{Re75,RS76} are given in terms of generating set $\XX{2}$ rather than $\mathcal{X}_1$ which is not precise enough for our purposes;
+ \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we must work with arbitrary coefficient ring $A$.
 \end{itemize} 
 \end{rem}
-\end{comment} %TODO: Find proper place for this discussion - it may not be appropriate here
+
+We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi^3$ an {\it $\rA_3$-triple}
+ if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
+ $\xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.$ %TODO: Draw better diagram :)
 
@@
 For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_1$, 
-three above families of relations $(a_1), (b_1), (c_1)$ and the following additional family of relations:
+three above families of relations $(a_1), (b_1), (c_1)$ and the following additional family:
 \begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha+\beta+\gamma}(\xi), x_{-\gamma}(\eta)], x_{\beta+\gamma}(\zeta) ] & = 1, 
@@
 \end{prop}
-%TODO: Deduce 2nd assertion from 1st
-Notice that the second assertion follows from the first one.
-Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
-%Denote by $F(S)$ the free group on the generating set $S$.
-%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
-%well, not so clear, actually :)
+\begin{rem}
+ The above presentation seems to be the shortest possible in the cases $\Phi=\rA_3, \rD_\ell$.
+On the other hand, the analogue of the above proposition for $\Phi=\rA_\ell$, $\ell\geq 4$ and $\Phi=\rE_\ell$ holds without additional relation $(d_1)$.
+For $\rA_\ell$ this is proved in~\cite[Lemma~3.3]{Tu83}, for $\rE_\ell$ this can be easily deduced using the amalgamation technique (see~???).
+\end{rem}
 
@@
 \end{comment}
+\end{proof}
+
+\begin{proof}[Proof of~\cref{prop:tul3.3}]
+ %TODO: Deduce 2nd assertion from 1st
+Notice that the second assertion follows from the first one.
+Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
+%Denote by $F(S)$ the free group on the generating set $S$.
+%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
+%well, not so clear, actually :)
+
 \end{proof}

### 2018-08-30 paper.tex
Fixed couple of issues; removed old proof

@@
 Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
-Denote by $B$ the ring $\mathfrak{m}[t^{-1}] + A[t]$ with the obvious $\mathbb{Z}$-grading.
-In other words, as a module $B$ decomposes into a direct sum of its homogeneous components $\oplus_k B_k$,
- where each $B_k$ is either $A\cdot t^k$ for $k \geq 0$ or $\mathfrak{m} \cdot t^k$ for $k<0$.
+Denote by $B$ the subring $\mathfrak{m}[t^{-1}] + A[t]$ of the Laurent polynomial ring $A[t, t^{-1}]$ with the $\mathbb{Z}$-grading induced by the grading on $A[t, t^{-1}]$.
+As an additive group $B$ decomposes into a direct sum of its homogeneous components $\oplus_{k\in\mathbb{Z}} B_k$,
+ where each $B_k \subseteq B$ is equal either to $A\cdot t^k$ for $k \geq 0$ or to $\mathfrak{m} \cdot t^k$ for $k<0$.
 
@@
 
-This presentation give by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
+This presentation given by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
 Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$,
@@
  \item Presentations from~\cite{Re75,RS76} are given in terms of generating set $\XX{2}$ rather than $\mathcal{X}_1$ which is not precise enough for our purposes;
- \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we must work with arbitrary coefficient ring $A$.
+ \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we must work with general coefficient ring $A$.
 \end{itemize} 
@@
 \begin{align*}
-   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
- = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
- = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$}
+   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]
+   &  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
+ = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             
+ &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
+ = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             
+ &  \text{ by $(b_1)$}
 \end{align*} 
@@
  \begin{align*}
-   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$}\\
-        = [x_\alpha(t\xi), x_\beta(at^m)]                               & \text{ by~\eqref{item:i}. }   
+   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
+   & \text{ by $(d_1)$}\\
+      = {}^{x_{\beta+\gamma}(1)}[x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
+   & \text{ by~\eqref{eq:H1ii}, $(b_1)$, $(c_1)$} \\
+      = [x_\alpha(\xi), [x_{\beta + \gamma}(1), x_{-\gamma}(a't^m)]] 
+   & \text{ by $(b_1)$, \eqref{eq:H1iii}}\\
+      = [x_\alpha(t\xi), x_\beta(at)]
+   & \text{ by~\eqref{item:i},\eqref{eq:defmpn}.}
  \end{align*}  
- This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. Why is this true?
+ %This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. 
+ %Why is this true?
 
@@
  \begin{align*}
- R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
- = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
- = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}. \qedhere}
+ R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]     
+ &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
+ = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         
+ &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
+ = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  
+ &  \text{ by~\eqref{eq:H1iii}. \qedhere}
 \end{align*}
@@
 \end{enumerate}
-\begin{comment}
- \begin{enumerate}
-\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
- \begin{enumerate}
-  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
-  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
-  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
-  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
-   \begin{multline} \nonumber
-   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
-  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
-  \end{multline}
-  What this really proves: $PERP(d, 1)$ and $NONPERP(d, m)$ imply $NONPERP(d, m+1)$.
-  \item Case $\alpha \perp \alpha'$. 
-  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
-  \begin{multline} \nonumber
-   [S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
-  = [[S_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
-  \end{multline}
- \end{enumerate}
-
-\item \label{case:2} Now assume $1 \leq d \leq m+1$.
-At first we want to prove~\eqref{eq:verify-bmp2} only in the special case $\xi=t^d$,
-We proceed by induction on $d$, so we can assume that \eqref{eq:verify-bmp2} holds for $\xi = t^e$, $e<d$.
-Again, there are two subcases.
-\begin{enumerate}
- \item \label{case:2a} Case $\alpha\not\perp\alpha'$ is handled similarly to the Case~\eqref{case:1a} with the only
-  difference that we must refer to the inductive assumption instead of~\eqref{eq:bm} in the case $d=m+1$:
-  %TODO: No real induction going on here...
-  \begin{multline} \nonumber
-   [S_\alpha(t^d), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(t^d), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
-  = [[S_\alpha(t^d), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1.
-  \end{multline}
-
- \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
-\begin{align*}
-{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
- = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
- = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by~\eqref{eq:verify-bmp1'}}\\
- = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
- = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by~\eqref{eq:verify-bmp1'}} \end{align*}
- Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
- \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
-\end{enumerate}
-This finishes the proof of~\eqref{eq:verify-bmp2} in the special case $a=1$.
-\item Now we deduce~\eqref{eq:verify-bmp2} for arbitrary $\xi = at^d$, $a\in A$ and $1\leq d\leq m+1$. Again, there are two subcases.
-\begin{enumerate}
-\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
- \begin{align*} 
- [S_\alpha(at^d), S_{\alpha + \beta}(bt^{m+1})] = 
- [S_\alpha(at^d), [S_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b')]] & \text{ by~\cref{lem:bmp1}} \\
-  = [[x_\alpha(at^d), S_{\alpha+\beta+\gamma}(t^{m+1})], {}^{S_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b')] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
-  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
-\item Case $\alpha \perp \alpha'$.
-\begin{align*}
- S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
- = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'}} \\
- = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\eqref{eq:verify-bmp1'} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
- = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
- = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}
-\end{align*}
-from which the required identity follows. \qedhere
-\end{enumerate}
-\end{enumerate}
-\end{comment}
 \end{proof}
@@
 \begin{proof}[Proof of~\cref{prop:tul3.3}]
- %TODO: Deduce 2nd assertion from 1st
+Define the map $g_m\colon G_{m+1} \to G_m$ by $g_m(x_\alpha(\xi)) = S_\alpha(\xi)$.
+In view of the above lemmata this map is well-defined. It is clear that $g_m$ is inverse to $f_m$, which proves the first claim.
+
 Notice that the second assertion follows from the first one.

### 2018-08-30 paper.tex
Minor fixes; better Dynkin diagram; proof of Proposition 3.2

@@
 \usepackage[matrix,arrow,curve]{xy}
+\usepackage{tikz}
 \usepackage{enumitem}
@@
 \DeclareMathOperator{\Hom}{Hom}
+\DeclareMathOperator{\colim}{colim}
 \DeclareMathOperator{\GL}{GL}
@@
  if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
- $\xymatrix{\circ_\alpha \ar@{-}[r] & \circ_\beta \ar@{-}[r] & \circ_\gamma}.$ %TODO: Draw better diagram :)
+\begin{tikzpicture}
+\draw[fill=black] 
+(0,0) circle [radius=.1] node [below] {$\alpha$} --
+(1,0) circle [radius=.1] node [below] {$\beta$} --
+(2,0) circle [radius=.1] node [below] {$\gamma$}
+\end{tikzpicture}.
 
@@
 \begin{align}
-% \label{eq:H1i}   [a, bc] = [a, b]\cdot {}^b[a, c] = [a, b] \cdot [b, [a, c]] \cdot [a, c];& \\
  \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
@@
 
-%To show that $f_m$ is an isomorphism we construct a map $g_m \colon G_{m+1} \to G_m$ in the opposite direction.
-%We define it on generators $\mathcal{X}_{m+1}$ and then verify that it is well defined.
-%Clearly, $g_m$ should be defined as the identity map on the subset of generators $\mathcal{X}_m \subseteq \mathcal{X}_{m+1}$.
-%Now if $x_{\alpha}(\xi)$ is an element of $\mathcal{X}_{m+1}\setminus \mathcal{X}_m$
-%there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$, 
-% therefore we can set 
-%\[g_m(x_\alpha(\xi)) = [x_{\alpha-\alpha'}(\xi'), x_{\alpha'}(N_{\alpha-\alpha',\alpha'} t)].\]
-%It follows from~\eqref{item:i} that this definition does not depend on the choice of $\alpha'$.
-
 Let us show that elements $S_\alpha(\xi)$ satisfy the relations $(a_{m+1})$, $(b_{m+1})$ and $(c_{m+1})$.
 From \eqref{eq:H1ii} and~\eqref{item:ii} it follows that $S_\alpha(\xi)$ satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
-\begin{comment}
-\begin{lemma} For every $\rA_3$-triple $(\alpha, \beta, \gamma)$ in $\Phi$ and $a,b,c \in A$ the following relation holds in $G_1$:
-\begin{align} 
- [x_{\alpha}(a), [x_{\beta}(b t), x_{\gamma}(c t)]] & = [x_{\beta+\alpha}(N_{\beta, \alpha}a b t), x_{\gamma}(ct)].
-\end{align}
- \end{lemma}
-\begin{proof}
- \begin{align*}
-   [x_{\alpha}(a), [x_{\beta}(b t), x_{\gamma}(c t)]] = [[x_{\alpha}(a), x_{\beta}(b t)], {}^{x_{\beta}(b t)}\!x_{\gamma}(ct)] &  \text{ by~\eqref{eq:H1iii} and~$(b_1)$} \\ 
-                                                       = {}^{x_{\beta}(b t)}[x_{\alpha +\beta}(N_{\alpha,\beta}abt), x_{\gamma}(ct) ] & \text{ by $(b_1)$ and $(c_1)$}\\ 
-                                                       = [x_{\alpha +\beta}(N_{\alpha,\beta}abt), x_{\gamma}(ct)] & \text{ by $(d_1)$. \qedhere}
- \end{align*}  
-\end{proof}
-\end{comment}
-
 \begin{lemma} \label{lem:bmp1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
@@
  \end{align*}  
- %This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. 
- %Why is this true?
-
  \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $d < 0$.
@@
 
-Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{lem:bmp1} and \eqref{eq:defmpn} (in the case $1\leq d\leq m$) or~\cref{lem:bmp1} (in the case $d=0,m+1$) imply that
+Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{item:i} and \eqref{eq:defmpn} (in the case $1\leq d\leq m$) or~\cref{lem:bmp1} (in the case $d=0,m+1$) imply that
 \begin{equation} \label{eq:verify-bmp1'} 
@@
 \begin{proof}
-We need to show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\bot(d, m+1)$ for $d\leq m+1$.
+We must show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\bot(d, m+1)$ for $d\leq m+1$.
 \begin{enumerate}
@@
 
-Notice that the second assertion follows from the first one.
-Indeed, this would give the required isomorphism $G_1 \cong \St(\Phi, B)$ since $\langle \XX{\infty} \mid \RR{\infty} \rangle$ is evidently isomorphic to $\St(\Phi, B)$.
-%Denote by $F(S)$ the free group on the generating set $S$.
-%It is clear that $\RR{n}\subseteq\RR{n+1}$, moreover $\langle \RR{n} \rangle = \langle \RR{\infty}\rangle \cap F(\XX{n})$.
-%well, not so clear, actually :)
+Denote by $G_\infty$ the group presented by generators $\mathcal{X}_\infty$ and relations $(a_\infty)$, $(b_\infty)$, $(c_\infty)$.
+By the above argument there is an isomorphism between $G_1$ and $\colim\limits_{n\to\infty} G_n \cong G_\infty$.
 
+Denote by $i\colon G_\infty \to \St(\Phi, B)$ the map induced by the obvious embedding of $\mathcal{X}_\infty$ into the set of 
+ Steinberg generators of $\St(\Phi, B)$.  
+Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
+ $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_i$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_i\in B_i$, is a well-defined map.
+It is clear that $i$ and $j$ are mutually inverse. 
 \end{proof}

### 2018-08-31 paper.tex
Purged more comments; better names for labels; improved narration in remark 3.3

@@
 
-%If $a$ is a homogeneous element of $B$ (i.\,e. an element of some $B_k$) we denote its homogeneous degree by $|a|$.
-
 Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
@@
 In the sequel we will need this presentation only in the special case $\Phi=\rA_3$.
-However, we preferred to prove a more general statement since the proof in the special case $\Phi=\rA_3$ has almost the same length.
+However, we preferred to prove a more general statement since the proof in the special case $\Phi=\rA_3$ would have almost the same length.
 
 This presentation given by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
-Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$,
-%TODO: Explain why we are dealing with general \Phi rather than just the case \rA_3 -- Reason the difficulty is the same
- which forces us to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on
- finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
+Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$, which forces us to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
 
@@
  \item Presentations from~\cite{Re75,RS76} are given in terms of generating set $\XX{2}$ rather than $\mathcal{X}_1$ which is not precise enough for our purposes;
- \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while we must work with general coefficient ring $A$.
+ \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while our theorem should work with a general coefficient ring $A$.
 \end{itemize} 
@@
 \draw[fill=black] 
-(0,0) circle [radius=.1] node [below] {$\alpha$} --
-(1,0) circle [radius=.1] node [below] {$\beta$} --
-(2,0) circle [radius=.1] node [below] {$\gamma$}
+(0,0) circle [radius=.1] node [above] {$\alpha$} --
+(1,0) circle [radius=.1] node [above] {$\beta$} --
+(2,0) circle [radius=.1] node [above] {$\gamma$};
 \end{tikzpicture}.
@@
 \end{align}
-% (this can be replaced by the weaker assumption that $A$ is additively generated by its units).
 
@@
 \begin{prop}\label{prop:tul3.3}
- For $m\geq 1$ the map $f_m$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$
-  and relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
+ For $m\geq 1$ the map $f_m$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$ and relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
 \end{prop}
 \begin{rem}
- The above presentation seems to be the shortest possible in the cases $\Phi=\rA_3, \rD_\ell$.
-On the other hand, the analogue of the above proposition for $\Phi=\rA_\ell$, $\ell\geq 4$ and $\Phi=\rE_\ell$ holds without additional relation $(d_1)$.
-For $\rA_\ell$ this is proved in~\cite[Lemma~3.3]{Tu83}, for $\rE_\ell$ this can be easily deduced using the amalgamation technique (see~???).
-\end{rem}
+   Notice that for $\Phi=\rA_\ell$, $\ell\geq 4$ the group $\St(\Phi, B)$ admits a shorter presentation with family~ $(d_1)$ omitted (see~\cite[Lemma~3.3]{Tu83}).
+   This is also true for $\Phi=\rE_\ell$ since $\St(\rE_\ell, R)$ can be presented as an amalgamated product of several copies of $\St(\rA_4, R)$, (cf. e.\,g.~\cite[Lemmas~3,7)]{S15}).   
+  On the other hand, we believe that the above presentation is the shortest possible in the cases $\Phi=\rA_3, \rD_\ell$. \end{rem}
 
@@
 
-The following lemma is similar to~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
 \begin{lemma}
@@
  \begin{equation}
-  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
+  \label{eq:S-correctness} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
  \end{equation}
@@
  \begin{equation}
- \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
+ \label{eq:S-commutes} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
  \end{equation}
@@
 \begin{proof}
- Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
- Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim in our situation.
- %TODO: Write down this argument, at least a part of it?
+ Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= A \cdot t^i$ for $i=k,k',l,'l'$.
+ This means that without loss of generality we may assume that $\mathfrak{m}=0$ and $B = A[t]$.
+ But now our statement is not different from~\cite[Proposition 1.1]{Re75} (or~\cite[Proposition~3.2.2]{RS76} in the case $g=1$)
+  and can be proved by the same argument which remains valid for a general coeffient ring $A$.
 \end{proof}
@@
 so we can define the following element of $G_m$:
-\begin{equation} \label{eq:defmpn} S_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)].\end{equation} 
-From~\eqref{item:i} it follows that $S_\alpha(\xi)$ does not depend of the choice of $\alpha'$.
+\begin{equation} \label{eq:S-definition} S_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)].\end{equation} 
+From~\eqref{eq:S-correctness} it follows that $S_\alpha(\xi)$ does not depend of the choice of $\alpha'$.
 
 Let us show that elements $S_\alpha(\xi)$ satisfy the relations $(a_{m+1})$, $(b_{m+1})$ and $(c_{m+1})$.
-From \eqref{eq:H1ii} and~\eqref{item:ii} it follows that $S_\alpha(\xi)$ satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
-\begin{lemma} \label{lem:bmp1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
+From \eqref{eq:H1ii} and~\eqref{eq:S-commutes} it follows that $S_\alpha(\xi)$ satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
+\begin{lemma} \label{lem:cm-plus1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
  $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
@@
    [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]
-   &  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
+   &  \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
  = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             
@@
       = [x_\alpha(t\xi), x_\beta(at)]
-   & \text{ by~\eqref{item:i},\eqref{eq:defmpn}.}
+   & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}.}
  \end{align*}  
@@
  R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]     
- &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
+ &  \text{ by~\eqref{eq:S-correctness} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
  = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         
- &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
+ &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{eq:S-commutes},\eqref{eq:S-definition} if $m=1$} \\
  = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  
@@
 
-Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{item:i} and \eqref{eq:defmpn} (in the case $1\leq d\leq m$) or~\cref{lem:bmp1} (in the case $d=0,m+1$) imply that
-\begin{equation} \label{eq:verify-bmp1'} 
+Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{eq:S-correctness} and \eqref{eq:S-definition} (in the case $1\leq d\leq m$) or~\cref{lem:cm-plus1} (in the case $d=0,m+1$) imply that
+\begin{equation} \label{eq:cm-plus1-generalized} 
 [S_\alpha(\xi), S_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
@@
 \begin{align*} 
-[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
+[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{eq:S-correctness} and~\eqref{eq:S-definition}}\\
 = [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(1, d)$}\\
@@
  \begin{align*}
- {}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
+ {}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:cm-plus1}}\\
  = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
@@
  = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
- & \text{ by~\eqref{eq:verify-bmp1'}}\\
+ & \text{ by~\eqref{eq:cm-plus1-generalized}}\\
  = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
@@
  = S_{\alpha}(b'''t^{m+1})                                                                            
- & \text{ by~\eqref{eq:verify-bmp1'}.} \end{align*}
+ & \text{ by~\eqref{eq:cm-plus1-generalized}.} \end{align*}
 Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
@@
  = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:verify-bmp1'}} \\
+ & \text{ by~\eqref{eq:cm-plus1-generalized}} \\
  = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:verify-bmp1'} and $\angle(d, d)$ }\\
+ & \text{ by~\eqref{eq:cm-plus1-generalized} and $\angle(d, d)$ }\\
  = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
+ & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:cm-plus1-generalized}} \\
  = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:bm-plus1}
 Elements $S_\alpha(\xi)$ satisfy relations $(b_{m+1})$.
@@
  \begin{align*} 
- [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] & \text{ by~\eqref{item:i},\eqref{eq:defmpn}} \\
+ [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}} \\
  = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] &

### 2018-09-06 paper.tex
Minor

@@
 
-\section{A variant of Rehmann theorem}
+\section{Rehmann theorem for Laurent polynomials}
 Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
@@
 Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
- $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_i$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_i\in B_i$, is a well-defined map.
+ $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_k$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_k\in B_k$, is a well-defined map.
 It is clear that $i$ and $j$ are mutually inverse. 
@@
 \section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}
+
+\begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
+$ $
+
+\end{lemma}
 

### 2018-09-23 paper.tex
Moved potentially unneeded section to separate file

@@
 
-\section{Rehmann theorem for Laurent polynomials}
-Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
-Denote by $B$ the subring $\mathfrak{m}[t^{-1}] + A[t]$ of the Laurent polynomial ring $A[t, t^{-1}]$ with the $\mathbb{Z}$-grading induced by the grading on $A[t, t^{-1}]$.
-As an additive group $B$ decomposes into a direct sum of its homogeneous components $\oplus_{k\in\mathbb{Z}} B_k$,
- where each $B_k \subseteq B$ is equal either to $A\cdot t^k$ for $k \geq 0$ or to $\mathfrak{m} \cdot t^k$ for $k<0$.
-
-For $m \geq 1$ consider the following set of Steinberg generators:
-\[\XX{m} = \{ x_{\alpha}(\xi) \mid \xi \in B_d,\text{ for } d\leq m,\ \alpha\in\Phi\}. \]
-Clearly, $\XX{m} \subseteq \XX{m+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.
-
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
-The main result of this section is~\cref{prop:tul3.3} which gives a presentation of Steinberg group $\St(\Phi, B)$ in terms of generating set $\mathcal{X}_1$.
-In the sequel we will need this presentation only in the special case $\Phi=\rA_3$.
-However, we preferred to prove a more general statement since the proof in the special case $\Phi=\rA_3$ would have almost the same length.
-
-This presentation given by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
-Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$, which forces us to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).
-
-\begin{rem}
-There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and instead need to reprove everything by hand.
-\begin{itemize}
- \item Rehmann and Soul{\'e} deal with usual polynomial rings rather than $\mathbb{Z}$-graded rings
-  (i.\,e. their results correspond to the special case $\mathfrak{m}=0$ of our result);
- \item Presentations from~\cite{Re75,RS76} are given in terms of generating set $\XX{2}$ rather than $\mathcal{X}_1$ which is not precise enough for our purposes;
- \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while our theorem should work with a general coefficient ring $A$.
-\end{itemize} 
-\end{rem}
-
-We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi^3$ an {\it $\rA_3$-triple}
- if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
-\begin{tikzpicture}
-\draw[fill=black] 
-(0,0) circle [radius=.1] node [above] {$\alpha$} --
-(1,0) circle [radius=.1] node [above] {$\beta$} --
-(2,0) circle [radius=.1] node [above] {$\gamma$};
-\end{tikzpicture}.
-
-For $m\geq 2$ define $G_m$ as the group presented by generators $\mathcal{X}_m$ and the following three families of relations:
-\begin{align}
- \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
- \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
- \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
- \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
- \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
- \end{align}
-For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_1$, 
-three above families of relations $(a_1), (b_1), (c_1)$ and the following additional family:
-\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha+\beta+\gamma}(\xi), x_{-\gamma}(\eta)], x_{\beta+\gamma}(\zeta) ] & = 1, 
- & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple. }
-\end{align}
-
-The obvious embedding of generators $\mathcal{X}_m \subseteq \mathcal{X}_{m+1}$ induces a map $f_m\colon G_m \to G_{m+1}$.
-Our goal is to show the following result.
-\begin{prop}\label{prop:tul3.3}
- For $m\geq 1$ the map $f_m$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$ and relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
-\end{prop}
-\begin{rem}
-   Notice that for $\Phi=\rA_\ell$, $\ell\geq 4$ the group $\St(\Phi, B)$ admits a shorter presentation with family~ $(d_1)$ omitted (see~\cite[Lemma~3.3]{Tu83}).
-   This is also true for $\Phi=\rE_\ell$ since $\St(\rE_\ell, R)$ can be presented as an amalgamated product of several copies of $\St(\rA_4, R)$, (cf. e.\,g.~\cite[Lemmas~3,7)]{S15}).   
-  On the other hand, we believe that the above presentation is the shortest possible in the cases $\Phi=\rA_3, \rD_\ell$. \end{rem}
-
-We will use the following commutator identities (cf.~\cite[H1]{Re75}):
-\begin{align}
- \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
- \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].&
-\end{align}
-
-\begin{lemma}
- Suppose $m \geq 1$.
- Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
- Assume, moreover, that $\xi \in B_d$, $\xi' \in B_{d'}$, $\eta \in B_e$, $\eta' \in B_{e'}$ are such that 
-  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $d,d',e,e'\leq m$ satisfying $d+e=d'+e' = m+1$.
- Then the following relations holds in $G_m$:
- \begin{equation}
-  \label{eq:S-correctness} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
- \end{equation}
- Moreover for every $\zeta \in B_{k''}$, $k''\leq m$ and $\gamma\in\{\alpha, \beta, \alpha + \beta\}$
-  the following relation holds in $G_m$:
- \begin{equation}
- \label{eq:S-commutes} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
- \end{equation}
-\end{lemma}
-\begin{proof}
- Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= A \cdot t^i$ for $i=k,k',l,'l'$.
- This means that without loss of generality we may assume that $\mathfrak{m}=0$ and $B = A[t]$.
- But now our statement is not different from~\cite[Proposition 1.1]{Re75} (or~\cite[Proposition~3.2.2]{RS76} in the case $g=1$)
-  and can be proved by the same argument which remains valid for a general coeffient ring $A$.
-\end{proof}
-
-For every $\xi \in B_{m+1}$ and $\alpha\in \Phi$ there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$,
-so we can define the following element of $G_m$:
-\begin{equation} \label{eq:S-definition} S_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)].\end{equation} 
-From~\eqref{eq:S-correctness} it follows that $S_\alpha(\xi)$ does not depend of the choice of $\alpha'$.
-
-Let us show that elements $S_\alpha(\xi)$ satisfy the relations $(a_{m+1})$, $(b_{m+1})$ and $(c_{m+1})$.
-From \eqref{eq:H1ii} and~\eqref{eq:S-commutes} it follows that $S_\alpha(\xi)$ satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
-\begin{lemma} \label{lem:cm-plus1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
- $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
-\begin{equation} \nonumber
-[x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
-\end{equation}
-\end{lemma}
-\begin{proof}
-By \cite[Lemma~3.1.2]{RS76} we may assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
-\begin{align*}
-   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]
-   &  \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
- = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             
- &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
- = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             
- &  \text{ by $(b_1)$}
-\end{align*} 
-Denote by $R$ the expression in the right hand side of the above formula.
-\begin{enumerate}
- \item \label{case:cm-1} Case $m=1$, $d = 0$.
- \begin{align*}
-   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
-   & \text{ by $(d_1)$}\\
-      = {}^{x_{\beta+\gamma}(1)}[x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
-   & \text{ by~\eqref{eq:H1ii}, $(b_1)$, $(c_1)$} \\
-      = [x_\alpha(\xi), [x_{\beta + \gamma}(1), x_{-\gamma}(a't^m)]] 
-   & \text{ by $(b_1)$, \eqref{eq:H1iii}}\\
-      = [x_\alpha(t\xi), x_\beta(at)]
-   & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}.}
- \end{align*}  
- \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $d < 0$.
- \begin{align*}
- R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]     
- &  \text{ by~\eqref{eq:S-correctness} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
- = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         
- &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{eq:S-commutes},\eqref{eq:S-definition} if $m=1$} \\
- = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  
- &  \text{ by~\eqref{eq:H1iii}. \qedhere}
-\end{align*}
-
-\end{enumerate}
-\end{proof}
-
-It will be convenient for us to extend the definition of $S_\alpha(\xi)$ by allowing $\xi$ to take values in $B_d$ for $d\leq m$.
-In this case we simply set $S_\alpha(\xi) = x_\alpha(\xi)$.
-
-Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{eq:S-correctness} and \eqref{eq:S-definition} (in the case $1\leq d\leq m$) or~\cref{lem:cm-plus1} (in the case $d=0,m+1$) imply that
-\begin{equation} \label{eq:cm-plus1-generalized} 
-[S_\alpha(\xi), S_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
-\end{equation}
-
-We need to introduce additional notation.
-For $a,b\leq m+1$ we denote by $\bot(a, b)$ (resp. $\angle(a,b)$) the family of all relations $[S_\alpha(\xi), S_{\alpha'}(\eta)] = 1$
-for which $\xi \in B_a$, $\eta \in B_b$ and $\alpha$ and $\alpha'$ are orthogonal (resp. form a sharp angle). 
-We denote by $\bot_0(a, b)$ the subset of $\bot(a, b)$
-consisting of those relations for which $\xi = t^{a} \in B_a$.
-
-\begin{lemma} \label{claim1} In $G_m$ relations $\bot_0(1, d)$ and $\angle(d, m)$ imply $\angle(d, m+1)$ for $d\leq m+1$ \end{lemma}
-\begin{proof}
-Without loss of generality we may assume that $\alpha' = \alpha + \beta$
-  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
-Write $\eta = bt^{m+1}$ for some $b\in A$.
-\begin{align*} 
-[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{eq:S-correctness} and~\eqref{eq:S-definition}}\\
-= [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(1, d)$}\\
-= 1
- & \text{ by~$\angle(d, m)$. \qedhere} \end{align*} 
-\end{proof}
-
-\begin{lemma} \label{claim2} In $G_m$ relations $\angle(d, m+1)$ imply $\bot_0(d, m+1)$ for  $1\leq d\leq m+1$. \end{lemma}
-\begin{proof}
-As before, without loss of generality we may assume $\alpha' = \gamma$ for some $\mathsf{A}_3$-triple $(\alpha, \beta, \gamma)$.
- \begin{align*}
- {}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:cm-plus1}}\\
- = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
- & \text{ by $\angle(d, m+1)$}\\
- = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
- & \text{ by~\eqref{eq:cm-plus1-generalized}}\\
- = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
- & \text{ by~\eqref{eq:H1iii} and $(b_{m+1-d})$}\\
- = S_{\alpha}(b'''t^{m+1})                                                                            
- & \text{ by~\eqref{eq:cm-plus1-generalized}.} \end{align*}
-Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
- $b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b,$ from which the claim follows.
-\end{proof}
-
-\begin{lemma} \label{claim3}
- In $G_m$ relations $\bot_0(d, m+1)$, $\angle(d, d)$ and $\angle(m+1, m+1)$ imply $\bot(d, m+1)$ for $d\leq m+1$.
-\end{lemma}
-\begin{proof}
- \begin{align*} 
- S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
- & \text{ by $\bot_0(d, m+1)$}\\
- = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:cm-plus1-generalized}} \\
- = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:cm-plus1-generalized} and $\angle(d, d)$ }\\
- = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
- & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:cm-plus1-generalized}} \\
- = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
- & \text{ by $\angle(m+1, m+1)$. \qedhere}
-\end{align*}
-\end{proof}
-
-\begin{lemma} \label{lem:bm-plus1}
-Elements $S_\alpha(\xi)$ satisfy relations $(b_{m+1})$.
- \end{lemma}
-\begin{proof}
-We must show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\bot(d, m+1)$ for $d\leq m+1$.
-\begin{enumerate}
- \item Relations $\angle(d, m+1)$, $d\leq m$ follow from~\cref{claim1}. 
- \item Relations $\bot(d, m+1)$ with $d\leq 0$ can verified by direct computation:
- \begin{align*} 
- [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}} \\
- = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] &
- \text{ by \eqref{eq:H1iii} and $(b_1)$} \\
- = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] &
- \text{ by $(b_m)$ and $(c_m)$} \\
- = 1 & \text{ by $(b_m)$.}
-\end{align*}
- \item Relations $\bot_0(d, m+1)$ with $1\leq d\leq m$ follow from~\cref{claim2}.
- \item Relations $\angle(m+1, m+1)$ follow from~\cref{claim1}, consequently relations $\bot_0(m+1, m+1)$ follow from~\cref{claim2}.
- \item Relations $\bot(d, m+1)$, $0\leq d\leq m+1$ follow from~\cref{claim3} and the previous two assertions.
-\end{enumerate}
-\end{proof}
-
-\begin{proof}[Proof of~\cref{prop:tul3.3}]
-Define the map $g_m\colon G_{m+1} \to G_m$ by $g_m(x_\alpha(\xi)) = S_\alpha(\xi)$.
-In view of the above lemmata this map is well-defined. It is clear that $g_m$ is inverse to $f_m$, which proves the first claim.
-
-Denote by $G_\infty$ the group presented by generators $\mathcal{X}_\infty$ and relations $(a_\infty)$, $(b_\infty)$, $(c_\infty)$.
-By the above argument there is an isomorphism between $G_1$ and $\colim\limits_{n\to\infty} G_n \cong G_\infty$.
-
-Denote by $i\colon G_\infty \to \St(\Phi, B)$ the map induced by the obvious embedding of $\mathcal{X}_\infty$ into the set of 
- Steinberg generators of $\St(\Phi, B)$.  
-Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
- $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_k$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_k\in B_k$, is a well-defined map.
-It is clear that $i$ and $j$ are mutually inverse. 
-\end{proof}
-
 \section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}
-
+\subsection{$\sigma$-pairs}
+Let $\Phi$ be a root system
 \begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
@@
 
-\subsection{$\sigma$-pairs}
 Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.

### 2018-09-23 rehmann.tex
Moved potentially unneeded section to separate file

\section{Rehmann theorem for Laurent polynomials}
Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
Denote by $B$ the subring $\mathfrak{m}[t^{-1}] + A[t]$ of the Laurent polynomial ring $A[t, t^{-1}]$ with the $\mathbb{Z}$-grading induced by the grading on $A[t, t^{-1}]$.
As an additive group $B$ decomposes into a direct sum of its homogeneous components $\oplus_{k\in\mathbb{Z}} B_k$,
 where each $B_k \subseteq B$ is equal either to $A\cdot t^k$ for $k \geq 0$ or to $\mathfrak{m} \cdot t^k$ for $k<0$.

For $m \geq 1$ consider the following set of Steinberg generators:
\[\XX{m} = \{ x_{\alpha}(\xi) \mid \xi \in B_d,\text{ for } d\leq m,\ \alpha\in\Phi\}. \]
Clearly, $\XX{m} \subseteq \XX{m+1}$, denote by $\XX{\infty}$ the union of all $\XX{n}$'s.

Let $\Phi$ be a reduced irreducible root system of rank $\geq 3$.
The main result of this section is~\cref{prop:tul3.3} which gives a presentation of Steinberg group $\St(\Phi, B)$ in terms of generating set $\mathcal{X}_1$.
In the sequel we will need this presentation only in the special case $\Phi=\rA_3$. However, we preferred to prove a more general statement since the proof in the special case $\Phi=\rA_3$ would have almost the same length.

This presentation given by~\cref{prop:tul3.3} can be thought of as an analogue of~\cite[Lemma~3.3]{Tu83} in the case $n=4$ (with variables $t$ and $t^{-1}$ swapped).
Notice that Tulenbaev's short proof of \cite[Lemma~3.3]{Tu83} in the case $\Phi=\rA_\ell$, $\ell\geq 4$ does not work in the case $\Phi=\rA_3$, which forces us to recourse to a much longer argument inspired by the proof of Rehmann--Soul{\'e} theorem on finite presentation of Steinberg groups over polynomial rings (cf.~\cite{Re75, RS76}).

\begin{rem}
There are several reasons why we can not simply refer to~\cite{Re75} or~\cite{RS76} and instead need to reprove everything by hand.
\begin{itemize}
 \item Rehmann and Soul{\'e} deal with usual polynomial rings rather than $\mathbb{Z}$-graded rings
  (i.\,e. their results correspond to the special case $\mathfrak{m}=0$ of our result);
 \item Presentations from~\cite{Re75,RS76} are given in terms of generating set $\XX{2}$ rather than $\mathcal{X}_1$ which is not precise enough for our purposes;
 \item It is assumed that $A=k$ is a field in~\cite{Re75} and that $A=\mathbb{Z}$ in~\cite{RS76}, while our theorem should work with a general coefficient ring $A$.
\end{itemize} 
\end{rem}

We need one additional technical definition. We call an ordered triple of roots $(\alpha, \beta, \gamma) \in \Phi^3$ an {\it $\rA_3$-triple}
 if these vectors form a basis of a root subsystem $\Psi \subseteq \Phi$ of type $\rA_3$, and moreover if the Dynkin diagram of $\Psi$ with respect to this basis has the form
\begin{tikzpicture}
\draw[fill=black] 
(0,0) circle [radius=.1] node [above] {$\alpha$} --
(1,0) circle [radius=.1] node [above] {$\beta$} --
(2,0) circle [radius=.1] node [above] {$\gamma$};
\end{tikzpicture}.

For $m\geq 2$ define $G_m$ as the group presented by generators $\mathcal{X}_m$ and the following three families of relations:
\begin{align}
 \label{eq:am} \tag{$a_m$} x_{\alpha}(\xi) x_{\alpha}(\eta) & = x_{\alpha}(\xi+\eta),&  \xi,\eta\in B_d,\ d\leq m;&\\
 \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
 \nonumber                                                     &       & \xi \in B_d,\ \eta \in B_e,\ d,e\leq m;\\
 \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
 \nonumber                                                    &  & \xi \in B_d,\ \eta \in B_e,\ d, e, d+e \leq m.
 \end{align}
For $m=1$ define $G_1$ as the group presented by generators $\mathcal{X}_1$, 
three above families of relations $(a_1), (b_1), (c_1)$ and the following additional family:
\begin{align}  \label{eq:d1} \tag{$d_1$} [[x_{\alpha+\beta+\gamma}(\xi), x_{-\gamma}(\eta)], x_{\beta+\gamma}(\zeta) ] & = 1, 
 & \xi,\eta,\zeta\in B_1,\ \text{ $(\alpha, \beta, \gamma)$ is an $\rA_3$-triple. }
\end{align}

The obvious embedding of generators $\mathcal{X}_m \subseteq \mathcal{X}_{m+1}$ induces a map $f_m\colon G_m \to G_{m+1}$.
Our goal is to show the following result.
\begin{prop}\label{prop:tul3.3}
 For $m\geq 1$ the map $f_m$ is an isomorphism. Consequently, $\St(\Phi, B)$ can be presented by generators $\mathcal{X}_1$ and relations $(a_1)$, $(b_1)$, $(c_1)$, $(d_1)$.
\end{prop}
\begin{rem}
   Notice that for $\Phi=\rA_\ell$, $\ell\geq 4$ the group $\St(\Phi, B)$ admits a shorter presentation with family~ $(d_1)$ omitted (see~\cite[Lemma~3.3]{Tu83}).
   This is also true for $\Phi=\rE_\ell$ since $\St(\rE_\ell, R)$ can be presented as an amalgamated product of several copies of $\St(\rA_4, R)$, (cf. e.\,g.~\cite[Lemmas~3,7)]{S15}).   
  On the other hand, we believe that the above presentation is the shortest possible in the cases $\Phi=\rA_3, \rD_\ell$. \end{rem}

We will use the following commutator identities (cf.~\cite[H1]{Re75}):
\begin{align}
 \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
 \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].&
\end{align}

\begin{lemma}
 Suppose $m \geq 1$.
 Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
 Assume, moreover, that $\xi \in B_d$, $\xi' \in B_{d'}$, $\eta \in B_e$, $\eta' \in B_{e'}$ are such that 
  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $d,d',e,e'\leq m$ satisfying $d+e=d'+e' = m+1$.
 Then the following relations holds in $G_m$:
 \begin{equation}
  \label{eq:S-correctness} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
 \end{equation}
 Moreover for every $\zeta \in B_{k''}$, $k''\leq m$ and $\gamma\in\{\alpha, \beta, \alpha + \beta\}$
  the following relation holds in $G_m$:
 \begin{equation}
 \label{eq:S-commutes} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
 \end{equation}
\end{lemma}
\begin{proof}
 Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= A \cdot t^i$ for $i=k,k',l,'l'$.
 This means that without loss of generality we may assume that $\mathfrak{m}=0$ and $B = A[t]$.
 But now our statement is not different from~\cite[Proposition 1.1]{Re75} (or~\cite[Proposition~3.2.2]{RS76} in the case $g=1$)
  and can be proved by the same argument which remains valid for a general coeffient ring $A$.
\end{proof}

For every $\xi \in B_{m+1}$ and $\alpha\in \Phi$ there exist $\xi' \in B_m$ and $\alpha'\in \Phi$ such that $\xi = t\xi'$ and $\alpha-\alpha'\in\Phi$,
so we can define the following element of $G_m$:
\begin{equation} \label{eq:S-definition} S_\alpha(\xi) := [x_{\alpha-\alpha'}(N_{\alpha-\alpha',\alpha'} \xi'), x_{\alpha'}(t)].\end{equation} 
From~\eqref{eq:S-correctness} it follows that $S_\alpha(\xi)$ does not depend of the choice of $\alpha'$.

Let us show that elements $S_\alpha(\xi)$ satisfy the relations $(a_{m+1})$, $(b_{m+1})$ and $(c_{m+1})$.
From \eqref{eq:H1ii} and~\eqref{eq:S-commutes} it follows that $S_\alpha(\xi)$ satisfy $(a_{m+1})$ and hence $(b_{m+1})$ in the special case $\alpha=\alpha'$.
\begin{lemma} \label{lem:cm-plus1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
 $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
\begin{equation} \nonumber
[x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
\end{equation}
\end{lemma}
\begin{proof}
By \cite[Lemma~3.1.2]{RS76} we may assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
\begin{align*}
   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]
   &  \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
 = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             
 &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
 = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             
 &  \text{ by $(b_1)$}
\end{align*} 
Denote by $R$ the expression in the right hand side of the above formula.
\begin{enumerate}
 \item \label{case:cm-1} Case $m=1$, $d = 0$.
 \begin{align*}
   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
   & \text{ by $(d_1)$}\\
      = {}^{x_{\beta+\gamma}(1)}[x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't)] 
   & \text{ by~\eqref{eq:H1ii}, $(b_1)$, $(c_1)$} \\
      = [x_\alpha(\xi), [x_{\beta + \gamma}(1), x_{-\gamma}(a't^m)]] 
   & \text{ by $(b_1)$, \eqref{eq:H1iii}}\\
      = [x_\alpha(t\xi), x_\beta(at)]
   & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}.}
 \end{align*}  
 \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $d < 0$.
 \begin{align*}
 R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]     
 &  \text{ by~\eqref{eq:S-correctness} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
 = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         
 &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{eq:S-commutes},\eqref{eq:S-definition} if $m=1$} \\
 = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  
 &  \text{ by~\eqref{eq:H1iii}. \qedhere}
\end{align*}

\end{enumerate}
\end{proof}

It will be convenient for us to extend the definition of $S_\alpha(\xi)$ by allowing $\xi$ to take values in $B_d$ for $d\leq m$.
In this case we simply set $S_\alpha(\xi) = x_\alpha(\xi)$.

Now suppose  $0 \leq d \leq m+1$. Clearly \eqref{eq:S-correctness} and \eqref{eq:S-definition} (in the case $1\leq d\leq m$) or~\cref{lem:cm-plus1} (in the case $d=0,m+1$) imply that
\begin{equation} \label{eq:cm-plus1-generalized} 
[S_\alpha(\xi), S_{\alpha'}(\eta)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi \eta),\ \xi \in B_d, \eta \in B_{m+1-d}.
\end{equation}

We need to introduce additional notation.
For $a,b\leq m+1$ we denote by $\bot(a, b)$ (resp. $\angle(a,b)$) the family of all relations $[S_\alpha(\xi), S_{\alpha'}(\eta)] = 1$
for which $\xi \in B_a$, $\eta \in B_b$ and $\alpha$ and $\alpha'$ are orthogonal (resp. form a sharp angle). 
We denote by $\bot_0(a, b)$ the subset of $\bot(a, b)$
consisting of those relations for which $\xi = t^{a} \in B_a$.

\begin{lemma} \label{claim1} In $G_m$ relations $\bot_0(1, d)$ and $\angle(d, m)$ imply $\angle(d, m+1)$ for $d\leq m+1$ \end{lemma}
\begin{proof}
Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
Write $\eta = bt^{m+1}$ for some $b\in A$.
\begin{align*} 
[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] & \text{ by~\eqref{eq:S-correctness} and~\eqref{eq:S-definition}}\\
= [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] & \text{ by~$\bot_0(1, d)$}\\
= 1
 & \text{ by~$\angle(d, m)$. \qedhere} \end{align*} 
\end{proof}

\begin{lemma} \label{claim2} In $G_m$ relations $\angle(d, m+1)$ imply $\bot_0(d, m+1)$ for  $1\leq d\leq m+1$. \end{lemma}
\begin{proof}
As before, without loss of generality we may assume $\alpha' = \gamma$ for some $\mathsf{A}_3$-triple $(\alpha, \beta, \gamma)$.
 \begin{align*}
 {}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:cm-plus1}}\\
 = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
 & \text{ by $\angle(d, m+1)$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
 & \text{ by~\eqref{eq:cm-plus1-generalized}}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
 & \text{ by~\eqref{eq:H1iii} and $(b_{m+1-d})$}\\
 = S_{\alpha}(b'''t^{m+1})                                                                            
 & \text{ by~\eqref{eq:cm-plus1-generalized}.} \end{align*}
Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
 $b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b,$ from which the claim follows.
\end{proof}

\begin{lemma} \label{claim3}
 In $G_m$ relations $\bot_0(d, m+1)$, $\angle(d, d)$ and $\angle(m+1, m+1)$ imply $\bot(d, m+1)$ for $d\leq m+1$.
\end{lemma}
\begin{proof}
 \begin{align*} 
 S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
 & \text{ by $\bot_0(d, m+1)$}\\
 = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:cm-plus1-generalized}} \\
 = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:cm-plus1-generalized} and $\angle(d, d)$ }\\
 = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:cm-plus1-generalized}} \\
 = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
 & \text{ by $\angle(m+1, m+1)$. \qedhere}
\end{align*}
\end{proof}

\begin{lemma} \label{lem:bm-plus1}
Elements $S_\alpha(\xi)$ satisfy relations $(b_{m+1})$.
 \end{lemma}
\begin{proof}
We must show that $S_\alpha(\xi)$ satisfy $\angle(d, m+1)$ and $\bot(d, m+1)$ for $d\leq m+1$.
\begin{enumerate}
 \item Relations $\angle(d, m+1)$, $d\leq m$ follow from~\cref{claim1}. 
 \item Relations $\bot(d, m+1)$ with $d\leq 0$ can verified by direct computation:
 \begin{align*} 
 [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] & \text{ by~\eqref{eq:S-correctness},\eqref{eq:S-definition}} \\
 = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] &
 \text{ by \eqref{eq:H1iii} and $(b_1)$} \\
 = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] &
 \text{ by $(b_m)$ and $(c_m)$} \\
 = 1 & \text{ by $(b_m)$.}
\end{align*}
 \item Relations $\bot_0(d, m+1)$ with $1\leq d\leq m$ follow from~\cref{claim2}.
 \item Relations $\angle(m+1, m+1)$ follow from~\cref{claim1}, consequently relations $\bot_0(m+1, m+1)$ follow from~\cref{claim2}.
 \item Relations $\bot(d, m+1)$, $0\leq d\leq m+1$ follow from~\cref{claim3} and the previous two assertions.
\end{enumerate}
\end{proof}

\begin{proof}[Proof of~\cref{prop:tul3.3}]
Define the map $g_m\colon G_{m+1} \to G_m$ by $g_m(x_\alpha(\xi)) = S_\alpha(\xi)$.
In view of the above lemmata this map is well-defined. It is clear that $g_m$ is inverse to $f_m$, which proves the first claim.

Denote by $G_\infty$ the group presented by generators $\mathcal{X}_\infty$ and relations $(a_\infty)$, $(b_\infty)$, $(c_\infty)$.
By the above argument there is an isomorphism between $G_1$ and $\colim\limits_{n\to\infty} G_n \cong G_\infty$.

Denote by $i\colon G_\infty \to \St(\Phi, B)$ the map induced by the obvious embedding of $\mathcal{X}_\infty$ into the set of 
 Steinberg generators of $\St(\Phi, B)$.  
Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
 $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_k$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_k\in B_k$, is a well-defined map.
It is clear that $i$ and $j$ are mutually inverse. 
\end{proof}

### 2018-09-24 paper.tex
Started rewriting stuff

@@
 Our notation and conventions follows~\cite[\S~4]{Vav09}.
-Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
- i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+Let $\Phi$ be an irreducible root system
 
-We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of coroots $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
-As usual, $P(\Phi^\vee)$ denotes the lattice spanned by the \emph{fundamental weights $\varpi_i$},
  that are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$ %TODO: Mistake?
@@
 
-\section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}
+\section{Tulenbaev's factorization theorem}
+Let $\Phi$ be a root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
+ i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+
+We denote by $\Phi^\vee$ the corresponding dual root system, which, by definition, consists of all coroots 
+ $\alpha^\vee = \frac{2}{(\alpha, \alpha)} \alpha$, where $\alpha \in \Phi$.
+We denote by $P(\Phi^\vee)$ the integral lattice spanned by the \emph{fundamental co-weights $\varpi^\vee_i$} (i.\,e. weights of the dual root system).
+Recall that the co-weights $\varpi^\vee_i$ are uniquely determined by the property $(\varpi_i^\vee, \alpha_j) = \delta_{ij}$.
+
+Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
+Thus, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ we can define a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$
+ via the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$.
+
+Every character $\chi \in \Hom(\ZZ \Phi, R^*)$ acts on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
+\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
+It is not hard to check that the above formula gives a well-defined automorphism of $\St(\Phi, R)$ which we also denote by $\chi$.
+
+\begin{example}
+Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
+Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
+It is easy to see that
+\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
+\end{example}
+
 \subsection{$\sigma$-pairs}
-Let $\Phi$ be a root system
+
 \begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
@@
 \section{Proof of the main result}
-
-Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
-Consequently, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$
-defines a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$.
-
-Consider the action of $H=\Hom(\ZZ \Phi, R^*)$ on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ given by
-\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
-Since $\chi$ is a character, this action respects the set of Steinberg relations $\mathcal{R}_{\Phi, R}$ and therefore gives a well-defined action of $H$ on $\St(\Phi, R)$.
-
-In the sequel we will be mostly interested in the following example.
-\begin{example}
-Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
-Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
-It is easy to see that
-\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
-\end{example}
 

### 2018-09-25 paper.tex
Writing stuff

@@
 \DeclareMathOperator{\rk}{rk}
+\DeclareMathOperator{\Sym}{Sym}
 \newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
@@
 \newcommand{\ZZ}{\mathbb{Z}}
+\newcommand{\UU}{\hat{\mathrm{U}}}
 \newcommand{\XX}[1]{\mathcal{X}_{#1}}
@@
 Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
-Thus, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ we can define a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$
- via the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$.
+Thus, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ we can define a map of abelian groups $\chi(\varpi, \varepsilon) \in \Hom(\ZZ \Phi, R^*)$
+ via the formula $\chi(\varpi, \varepsilon)(\beta) = \varepsilon ^ {(\varpi, \beta)}$.
 
-Every character $\chi \in \Hom(\ZZ \Phi, R^*)$ acts on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
-\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
-It is not hard to check that the above formula gives a well-defined automorphism of $\St(\Phi, R)$ which we also denote by $\chi$.
+Every map of abelian groups $\chi \in \Hom(\ZZ \Phi, R^*)$ specifies an action on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
+\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \alpha\in \Phi,\ \xi \in R. \end{equation}
+It is not hard to check that this action is compatible with Steinberg relations $\mathcal{R}_{\Phi, R}$ and 
+ hence gives a well-defined automorphism of $\St(\Phi, R)$ which we denote by the same symbol $\chi$.
 
+\begin{comment}
 \begin{example}
-Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
-Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
+Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
+Now if $\varpi \in P(\Phi^\vee)$ is a coweight then there is a pair of mutually inverse automorphisms $(\chi_{\varpi, t}, \chi_{-\varpi, t} = \chi_{\varpi, t^{-1}})$ 
+ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}} = \chi_{-\varpi_i, t}$.
 It is easy to see that
@@
 
-\subsection{$\sigma$-pairs}
+One of the key steps of in the proof of Horrocks theorem for $K_2$ is to define analogue of maps $\beta_i^\pm$ on the level of the group $\St(\Phi, A[t])$.
+Of course, one cannot expect such maps to be automorphisms or even be defined on the whole group $\St(\Phi, A[t])$.
+Thus, our first goal is to define the subgroups of $\St(\Phi, A[t])$ on which these morphisms could, in principle, be defined.
+\end{comment}
 
-\begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
-$ $
+Let $\varpi \in P(\Phi^\vee)$ be a co-weight of $\Phi$ as above.
+Denote by $\mathcal{X}(\varpi)$ the subset of $\mathcal{X}_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
+$(\alpha, \varpi) < 0$ implies that $\xi \in A[t]$ is divisible by $t^{-(\alpha, \varpi)}$.
+% either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
+Denote by $N(\varpi)$ the subgroup of $\St(\Phi, A[t])$ generated by $\mathcal{X}(\varpi)$.
 
-\end{lemma}
+\begin{dfn}
+Let $A$ be a ring and $R = A[t, t^{-1}]$ be the ring of Laurent polynomials over $A$.
+
+By definition, a {\it $\sigma$-pair for $\varpi$} is a quadruple $(N(\varpi), N(-\varpi), \sigma(\varpi), \sigma(-\varpi))$ consisting of the following data:
+\begin{itemize}
+ \item a pair of subgroups $N(\varpi), N(-\varpi) \subseteq \St(\Phi, A[t])$;
+ \item a pair of mutually inverse group-theoretic bijections $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$
+  fitting into the following commutative diagram:
+\begin{equation} \label{eq:sigma-diagram}
+\xymatrix{ N(\varpi) \ar@{-->}[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar@{-->}[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
+          \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
+          \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, R).} \end{equation}  
+\end{itemize}
+\end{dfn}
+
+\subsection{Factorization theorem} 
+For a ring $R$ we denote by $\Sym(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
+ If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$. 
+Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
+It is clear that $H$ is a functor on the category of commutative rings.
+
+%Similarly $\Sym(\Phi, A[t, t^{-1}], M[t, t^{-1}]$ denotes the subgroup of $\St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$ generated by elements of the form $h_\alpha(1+q)^{}$
+As before $A$ is a commutative local ring with the maximal ideal $M$.
+
+$j_+\colon A[t] \to A[t, t^{-1}]$. We write $j_+^*$ instead of $\St(\Phi, j_+)$.
+
+Denote by $V_0$ the set $\St(\Phi, A[t]) \times H(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$. 
+We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
+\begin{enumerate}
+ \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $H(A[t])$;
+ \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;
+\end{enumerate}
 
 \section{Proof of the main result}
-
-One of the key steps of in the proof of Suslin lemma for $K_2$ is to define analogue of maps $\beta_i^\pm$ on the level of the group $\St(\Phi, A[t])$.
-Of course, one cannot expect such maps to be automorphisms or even be defined on the whole group $\St(\Phi, A[t])$.
-Thus, our first goal is to define the subgroups of $\St(\Phi, A[t])$ on which these morphisms could, in principle, be defined.
 
@@
  if these maps fit into the following diagram.
-\begin{equation} \label{eq:sigma-diagram}
-\xymatrix{ N_i\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^i \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_i \ar[d] \\ 
-          \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^+} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^-} & \St(\Phi, R)} 
-\end{equation}
 In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 

### 2018-09-25 paper.tex
Improved treatment of sigmas

@@
 \begin{dfn}
-Let $A$ be a ring and $R = A[t, t^{-1}]$ be the ring of Laurent polynomials over $A$.
+By definition, a {\it $\sigma$-pair for $\varpi$} is a pair of mutually inverse group homomorphisms $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$ satisfying
+\begin{equation} \label{eq:sigmadef}
+\sigma(\pm \varpi)(x_\alpha(\xi)) = x_\alpha(t^{(\pm \varpi, \alpha)}\cdot \xi), 
+ \text{ for all } x_\alpha(\xi) \in \mathcal{X}(\pm\varpi).
+\end{equation}\end{dfn}
+It is clear that any maps $\sigma(\varpi), \sigma(-\varpi)$ satisfying~\eqref{eq:sigmadef} automatically fit into the following commutative diagram:
+\begin{equation} \label{eq:sigma-diagram}
+\xymatrix{ N(\varpi) \ar[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
+          \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
+          \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, A[t, t^{-1}]).} \end{equation}
 
-By definition, a {\it $\sigma$-pair for $\varpi$} is a quadruple $(N(\varpi), N(-\varpi), \sigma(\varpi), \sigma(-\varpi))$ consisting of the following data:
+\begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$.
+However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori claim that maps $\sigma(\pm\varpi)$ with the property~\eqref{eq:sigmadef} exist.
+\end{rem}
+
+\begin{comment}
 \begin{itemize}
  \item a pair of subgroups $N(\varpi), N(-\varpi) \subseteq \St(\Phi, A[t])$;
- \item a pair of mutually inverse group-theoretic bijections $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$
+ \item a pair of mutually inverse group-theoretic bijections 
   fitting into the following commutative diagram:
-\begin{equation} \label{eq:sigma-diagram}
-\xymatrix{ N(\varpi) \ar@{-->}[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar@{-->}[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
-          \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
-          \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, R).} \end{equation}  
 \end{itemize}
-\end{dfn}
+\end{comment}
 

### 2018-09-25 paper.tex
Minor

@@
 \subsection{Steinberg groups and relative Steinberg groups}
+\subsection{Relative Steinberg groups}
 
@@
 \begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$.
-However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori claim that maps $\sigma(\pm\varpi)$ with the property~\eqref{eq:sigmadef} exist.
+However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori be sure that formulas~\eqref{eq:sigmadef} specify well-defined maps between $N(\varpi)$ and $N(-\varpi)$.
 \end{rem}
@@
 Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
-It is clear that $H$ is a functor on the category of commutative rings.
 
@@
 \begin{enumerate}
- \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $H(A[t])$;
+ \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $\UU(\Phi^+,A[t])$;
  \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;

### 2018-09-26 paper.tex
Added definition of Steinberg groups

@@
 
-\subsection{Steinberg groups and relative Steinberg groups}
+\subsection{Steinberg groups}
+Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
+Recall that the \emph{Steinberg group} $\St(\Phi, R)$ is defined by means of generators
+$\mathcal{X}_{\Phi, R} = \{x_{\alpha}(\xi) \mid \xi\in R, \alpha\in\Phi\}$ and the set of relations $\mathcal{R}_{\Phi, R}$ 
+consisting of the following two families of relations:
+\begin{align}
+& \phantom{[}
+x_\alpha(s) x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
+& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
+ x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
+\end{align}
+The indices $i$, $j$ appearing in the right-hand side of the above relation range over
+all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
+%The structure constants $N_{\alpha \beta i j}=\pm 1,2,3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and can be computed precisely.
+
+It is clear the above construction is functorial in $R$ and so there is a functor $\St(\Phi, -)\colon \catname{CRings}\to \catname{Groups}$.
 \subsection{Relative Steinberg groups}
+First of all, let us recall the definition of the category of pairs. 
+As suggested by the notation, the objects of $\catname{Pairs}$ are pairs $(R, I)$ consisting of a unital commutative ring $R$ and an ideal $I \trianglelefteq R$.
+The set of morphisms between $(R, I)$ and $(S, J)$ is defined as the set of all ring-theoretic maps $f\colon R\to S$ such that $f(I)\subseteq J$.
+There is an obvious fully faithful embedding $\iota\colon \catname{CRings} \to \catname{Pairs}$ defined on objects by $\iota(R) = (R, R)$.
+Now if there is a functor $F\colon \catname{CRings}\to \catname{Grp}$ then its {\it relativization} is another functor $\widetilde{F}\colon \catname{Pairs} \to \catname{Groups}$
+such that $\widetilde{F} \iota = F$.
 
+Recall that there is a way to ``relativize`` the Steinberg group functor, that is define a group-valued functor $\St(\Phi, -)$ on the category of pairs
+ in a way compatible with the embedding
+
+\begin{equation}
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r] & \St(\Phi, R/I) \ar[r] & 1 }
+\end{equation}
+
+\subsection{Various stuff}
 \[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]

### 2018-09-26 paper.tex
Minor

@@
 \newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\UU}{\hat{\mathrm{U}}}
-\newcommand{\XX}[1]{\mathcal{X}_{#1}}
-\newcommand{\RR}[1]{\mathcal{R}_{#1}}
+\newcommand{\UU}{\hat{\mathrm{U}}}      % Unipotent subgroup on the Steinberg level
+\newcommand{\StB}{\hat{\mathrm{B}}}     % Borel subgroup on the Steinberg level
+\newcommand{\StH}{\hat{\mathrm{H}}}     % Torus on the Steinberg level
+\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
+\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
 
@@
 Recall that the \emph{Steinberg group} $\St(\Phi, R)$ is defined by means of generators
-$\mathcal{X}_{\Phi, R} = \{x_{\alpha}(\xi) \mid \xi\in R, \alpha\in\Phi\}$ and the set of relations $\mathcal{R}_{\Phi, R}$ 
+$\XX_{\Phi, R} = \{x_{\alpha}(\xi) \mid \xi\in R, \alpha\in\Phi\}$ and the set of relations $\RR{\Phi, R}$ 
 consisting of the following two families of relations:
@@
 
-It is clear the above construction is functorial in $R$ and so there is a functor $\St(\Phi, -)\colon \catname{CRings}\to \catname{Groups}$.
+It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the correponding map of Steinberg groups by $f_*$.
+
+\subsection{Some distinguished subgroups}
+%TODO: definition of h_\alpha(\xi)
+%TODO: definition of Steinberg symbols
+
+We denote by $\StH(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements $h_\alpha(\xi)$, $\xi\in R^*$ and by $\StB(\Phi, R)$ the product of the two subgroups $\StH(\Phi, R)$ and $\UU(\Phi^+, R)$ inside $\St(\Phi, R)$.
+
+By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
+ If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$.
+
+There is the following chain of inclusions:
+\begin{equation}
+  \Sym(\Phi, R) \subseteq \StH(\Phi, R) \subseteq \StB(\Phi, R) \subseteq \St(\Phi, R)
+\end{equation}
+
 \subsection{Relative Steinberg groups}
@@
 As suggested by the notation, the objects of $\catname{Pairs}$ are pairs $(R, I)$ consisting of a unital commutative ring $R$ and an ideal $I \trianglelefteq R$.
-The set of morphisms between $(R, I)$ and $(S, J)$ is defined as the set of all ring-theoretic maps $f\colon R\to S$ such that $f(I)\subseteq J$.
+The set of morphisms between $(R, I)$ and $(S, J)$ consists, by definition, of all ring-theoretic maps $f\colon R\to S$ such that $f(I)\subseteq J$.
 There is an obvious fully faithful embedding $\iota\colon \catname{CRings} \to \catname{Pairs}$ defined on objects by $\iota(R) = (R, R)$.
-Now if there is a functor $F\colon \catname{CRings}\to \catname{Grp}$ then its {\it relativization} is another functor $\widetilde{F}\colon \catname{Pairs} \to \catname{Groups}$
-such that $\widetilde{F} \iota = F$.
+%Now if there is a functor $F\colon \catname{CRings}\to \catname{Grp}$ then its {\it relativization} is another functor $\widetilde{F}\colon \catname{Pairs} \to \catname{Groups}$ such that $\widetilde{F} \iota = F$.
 
@@
 
-Every map of abelian groups $\chi \in \Hom(\ZZ \Phi, R^*)$ specifies an action on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
+Every map of abelian groups $\chi \in \Hom(\ZZ \Phi, R^*)$ specifies an action on the set of generators $\XX_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
 \begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \alpha\in \Phi,\ \xi \in R. \end{equation}
-It is not hard to check that this action is compatible with Steinberg relations $\mathcal{R}_{\Phi, R}$ and 
+It is not hard to check that this action is compatible with Steinberg relations $\RR{\Phi, R}$ and 
  hence gives a well-defined automorphism of $\St(\Phi, R)$ which we denote by the same symbol $\chi$.
 
-\begin{comment}
-\begin{example}
-Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
-Now if $\varpi \in P(\Phi^\vee)$ is a coweight then there is a pair of mutually inverse automorphisms $(\chi_{\varpi, t}, \chi_{-\varpi, t} = \chi_{\varpi, t^{-1}})$ 
- of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}} = \chi_{-\varpi_i, t}$.
-It is easy to see that
-\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
-\end{example}
-
-One of the key steps of in the proof of Horrocks theorem for $K_2$ is to define analogue of maps $\beta_i^\pm$ on the level of the group $\St(\Phi, A[t])$.
-Of course, one cannot expect such maps to be automorphisms or even be defined on the whole group $\St(\Phi, A[t])$.
-Thus, our first goal is to define the subgroups of $\St(\Phi, A[t])$ on which these morphisms could, in principle, be defined.
-\end{comment}
-
 Let $\varpi \in P(\Phi^\vee)$ be a co-weight of $\Phi$ as above.
-Denote by $\mathcal{X}(\varpi)$ the subset of $\mathcal{X}_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
-$(\alpha, \varpi) < 0$ implies that $\xi \in A[t]$ is divisible by $t^{-(\alpha, \varpi)}$.
-% either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
-Denote by $N(\varpi)$ the subgroup of $\St(\Phi, A[t])$ generated by $\mathcal{X}(\varpi)$.
+Denote by $\XX(\varpi)$ the subset of $\XX_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
+$(\alpha, \varpi) < 0$ implies that $\xi \in A[t]$ is divisible by $t^{-(\alpha, \varpi)}$. Denote by $N(\varpi)$ the subgroup of $\St(\Phi, A[t])$ generated by $\XX(\varpi)$.
 
@@
 \sigma(\pm \varpi)(x_\alpha(\xi)) = x_\alpha(t^{(\pm \varpi, \alpha)}\cdot \xi), 
- \text{ for all } x_\alpha(\xi) \in \mathcal{X}(\pm\varpi).
+ \text{ for all } x_\alpha(\xi) \in \XX(\pm\varpi).
 \end{equation}\end{dfn}
-It is clear that any maps $\sigma(\varpi), \sigma(-\varpi)$ satisfying~\eqref{eq:sigmadef} automatically fit into the following commutative diagram:
+It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$.
+Moreover, the maps $\sigma(\varpi), \sigma(-\varpi)$ make the following diagram commute:
 \begin{equation} \label{eq:sigma-diagram}
@@
 
-\begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$.
-However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori be sure that formulas~\eqref{eq:sigmadef} specify well-defined maps between $N(\varpi)$ and $N(-\varpi)$.
+\begin{rem} Despite the fact that formula~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, we cannot a priori be sure that~\eqref{eq:sigmadef} actually {\it defines} them, i.\,e.
+gives well-defined maps between $N(\pm\varpi)$.
+This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, so we cannot verify that $\sigma(\pm\varpi)$ preserves these relations.
 \end{rem}
 
-\begin{comment}
-\begin{itemize}
- \item a pair of subgroups $N(\varpi), N(-\varpi) \subseteq \St(\Phi, A[t])$;
- \item a pair of mutually inverse group-theoretic bijections 
-  fitting into the following commutative diagram:
-\end{itemize}
-\end{comment}
+\subsection{Factorization theorem} 
+Throughout this section $A$ denote a commutative local ring with the maximal ideal $M$.
 
-\subsection{Factorization theorem} 
-For a ring $R$ we denote by $\Sym(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
- If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$. 
 Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
@@
 $j_+\colon A[t] \to A[t, t^{-1}]$. We write $j_+^*$ instead of $\St(\Phi, j_+)$.
+
+Throughout this section we use the following notation.
+\begin{itemize}
+ \item 
+\end{itemize}
 
@@
 \section{Proof of the main result}
-
-In the sequel we assume that $i$ is a vertex of the Dynkin diagram $D(\Phi)$ of $\Phi$ with the property that $m_i(\alpha_{\max})=1$ (of course, this implies that $\Phi$ is not of type $\rE_8, \rF_4$ or $\rG_2$).
-Denote by $\mathcal{X}_i$ (resp. $\mathcal{X}^i$) the subsets of $\mathcal{X}_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
-$m_i(\alpha) > 0$ (resp. $m_i(\alpha)<0$) implies that $\xi \in A[t]$ is divisible by $t$.
-% either $i\neq k$ (resp. $j\neq k$) or $\xi\in R[t]$ is divisible by $t$.
-Denote by $N_i$ and $N^i$ the subgroups of $\St(\Phi, A[t])$ generated by $\mathcal{X}_i$ and $\mathcal{X}^i$, respectively.
-%Our goal is to construct mutually inverse morphisms $\sigma_k$, $\sigma_k^{-1}$ fitting into the following diagram.
-
-\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertex $i\in D(\Phi)$},
- if these maps fit into the following diagram.
-In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 
- the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R = A[t, t^{-1}]$.
-%As before, we denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
-         % \GL(n, R) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R)
-\end{dfn}
-
 For the remainder of this subsection our main goal will be to verify that an analogue of the group decomposition from \cite[Lemma~3.1f]{Tu83} holds for $\St(\Phi, A)$

### 2018-09-27 paper.tex
Written down definition of eq. rel

@@
 \newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
+\newcommand{\ext}[1]{\mu_{#1}}           % Map from St(Ф, R, I) --> St(Ф, R)
 
@@
 By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
- If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$.
+$\Sym(\Phi, R)$ is contained in $\K_2(\Phi, R)$ and is a central subgroup of $\St(\Phi, R)$ provided $\rk(\Phi)\geq 2$.
 
@@
 \begin{equation}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r] & \St(\Phi, R/I) \ar[r] & 1 }
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{R}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
 \end{equation}
+
+\begin{multline}
+ \{ t, u \}'_\alpha = h_{\alpha}(u) ^ {h_{?}(t)} =  y_\alpha(t(u-1)) \cdot y_{-\alpha}\left(-t^{-1}(u^{-1}-1)\right)^{x_\alpha(-t)} \cdot y_\alpha\left(t(u-1)\right)^{w_\alpha(-t)} \cdot \\
+\cdot y_\alpha(u-1) \cdot y_{-\alpha}\left(-(u^{-1}-1)\right)^{x_\alpha(-1)} \cdot y_\alpha(u-1)^{w_\alpha(-1)}.
+\end{multline}
 
@@
 
-\begin{rem} Despite the fact that formula~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, we cannot a priori be sure that~\eqref{eq:sigmadef} actually {\it defines} them, i.\,e.
-gives well-defined maps between $N(\pm\varpi)$.
+\begin{rem} Despite the fact that formula~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, 
+ we cannot a priori be sure that~\eqref{eq:sigmadef} actually {\it defines} them, i.\,e. gives well-defined maps between $N(\pm\varpi)$.
 This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, so we cannot verify that $\sigma(\pm\varpi)$ preserves these relations.
@@
 \subsection{Factorization theorem} 
-Throughout this section $A$ denote a commutative local ring with the maximal ideal $M$.
-
+Throughout this section $A$ denote a commutative local ring with the maximal ideal $m$.
 Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
-
-%Similarly $\Sym(\Phi, A[t, t^{-1}], M[t, t^{-1}]$ denotes the subgroup of $\St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$ generated by elements of the form $h_\alpha(1+q)^{}$
-As before $A$ is a commutative local ring with the maximal ideal $M$.
 
@@
 
-Denote by $V_0$ the set $\St(\Phi, A[t]) \times H(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$. 
+Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
 We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
 \begin{enumerate}
- \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $\UU(\Phi^+,A[t])$;
- \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;
+ \item $(a \cdot u, b, \beta) \sim (a, j_+^*(u) \cdot b, \beta)$, where $u$ is an element $\UU(\Phi^+, A[t])$;
+ \item $(a \cdot \ext{A[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
+  %and $b$ acts on $j^*_+(\gamma)$ via the conjugation action of $\St(\Phi, R)$ on $\St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$;
+ \item $(a, b \cdot u, \beta) \sim (a, b, u\cdot \beta)$, where $u$ is an element of $\UU(\Phi^+, m[t, t^{-1}])$;
+ \item $(a, b \cdot \{ t, a \}_\alpha, \beta) \sim (a, b, \{ t, a \}'_\alpha \cdot \beta) $, where $a \in (1+m)^*$
+  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in ???
 \end{enumerate}

### 2018-09-27 paper.tex
Introduced relative Steinberg symbol

@@
 \newcommand{\StH}{\hat{\mathrm{H}}}     % Torus on the Steinberg level
+\newcommand{\StW}{\hat{\mathrm{W}}}     % weyl on the Steinberg level
 \newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
@@
 
-It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the correponding map of Steinberg groups by $f_*$.
+It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the corresponding map of Steinberg groups by $f_*$.
 
-\subsection{Some distinguished subgroups}
-%TODO: definition of h_\alpha(\xi)
-%TODO: definition of Steinberg symbols
+Recall that for $\alpha\in\Phi$, $\varepsilon\in R^*$ the semisimple root elements $h_\alpha(\varepsilon)$ are defined as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
+Denote by $\StW(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements
+$w_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$, and by $\StH(\Phi,R)$
+ the subgroup generated by all elements $h_\alpha(\varepsilon)$, $\varepsilon\in R^*$, $\alpha\in\Phi$.
+We also denote by $\StB(\Phi, R)$ the product of the two subgroups $\StH(\Phi, R)$ and $\UU(\Phi^+, R)$ inside $\St(\Phi, R)$.
 
-We denote by $\StH(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements $h_\alpha(\xi)$, $\xi\in R^*$ and by $\StB(\Phi, R)$ the product of the two subgroups $\StH(\Phi, R)$ and $\UU(\Phi^+, R)$ inside $\St(\Phi, R)$.
-
-By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
+For $u, v \in R^*$ and $\alpha\in\Phi$ the element $\{u,v\}_\alpha=h_\alpha(uv)h_\alpha(u)^{-1}h_\alpha(v)^{-1}$ will be
+ called a {\it Steinberg symbol}. By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{u, v\}_\alpha$, $u, v \in R^*$. 
 $\Sym(\Phi, R)$ is contained in $\K_2(\Phi, R)$ and is a central subgroup of $\St(\Phi, R)$ provided $\rk(\Phi)\geq 2$.
 
-There is the following chain of inclusions:
+There is the following chain of obvious inclusions between the subgroups introduced above:
 \begin{equation}
@@
 
-\subsection{Relative Steinberg groups}
+\subsection{Relative Steinberg groups} \label{sec:relative-steinberg}
 First of all, let us recall the definition of the category of pairs. 
@@
 \begin{equation}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{R}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{I}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
 \end{equation}
 
-\begin{multline}
+%Now suppose that $t, u \in R^*$ are invertible elements such that $u-1 \in I$. 
+In the sequel we will also need a {\it relative Steinberg symbol}, i.\,e. a map
+\begin{equation*} \{-, -\}'_\alpha \colon R^* \times (1 + I)^* \to \St(\Phi, R, I) \end{equation*}
+such that $ \ext{I} \{u, v\}'_\alpha = \{u, v\}_\alpha$. It is not hard to verify that the image under $\mu_I$ of the element
+\begin{equation} f(\alpha, t, u)= y_\alpha(t(u-1)) \cdot y_{-\alpha}(-t^{-1}(u^{-1}-1))^{x_\alpha(-t)} \cdot y_{\alpha}(t(u-1))^{w_\alpha(-t)}, \end{equation}
+equals $w_\alpha(tu) \cdot w_\alpha(-t)$. This allows us to set $\{t, u \}'_\alpha := f(\alpha, t, u) f(\alpha, 1, u)^{-1}.$
+Now, obviously $\mu_I\{ t, u \}'_\alpha = w_\alpha(tu) w_\alpha(-t) w_\alpha(1) w_\alpha(-u) = \{t, u\}_\alpha,$ as claimed.
+\begin{rem}
+ Our relative Steinberg symbols differs from the one defined in~\cite{Ste73} in that
+  it takes values in $\St(\Phi, R, I)$ rather than the group $\St(\Phi, R)$. %Elaborate on this...
+\end{rem}
+
+\begin{comment}
  \{ t, u \}'_\alpha = h_{\alpha}(u) ^ {h_{?}(t)} =  y_\alpha(t(u-1)) \cdot y_{-\alpha}\left(-t^{-1}(u^{-1}-1)\right)^{x_\alpha(-t)} \cdot y_\alpha\left(t(u-1)\right)^{w_\alpha(-t)} \cdot \\
 \cdot y_\alpha(u-1) \cdot y_{-\alpha}\left(-(u^{-1}-1)\right)^{x_\alpha(-1)} \cdot y_\alpha(u-1)^{w_\alpha(-1)}.
-\end{multline}
+\end{comment}
 
@@
  we cannot a priori be sure that~\eqref{eq:sigmadef} actually {\it defines} them, i.\,e. gives well-defined maps between $N(\pm\varpi)$.
-This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, so we cannot verify that $\sigma(\pm\varpi)$ preserves these relations.
-\end{rem}
+This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, 
+ so we cannot verify that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
 
@@
  \item $(a \cdot u, b, \beta) \sim (a, j_+^*(u) \cdot b, \beta)$, where $u$ is an element $\UU(\Phi^+, A[t])$;
- \item $(a \cdot \ext{A[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
-  %and $b$ acts on $j^*_+(\gamma)$ via the conjugation action of $\St(\Phi, R)$ on $\St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$;
+ \item $(a \cdot \ext{m[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
  \item $(a, b \cdot u, \beta) \sim (a, b, u\cdot \beta)$, where $u$ is an element of $\UU(\Phi^+, m[t, t^{-1}])$;
  \item $(a, b \cdot \{ t, a \}_\alpha, \beta) \sim (a, b, \{ t, a \}'_\alpha \cdot \beta) $, where $a \in (1+m)^*$
-  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in ???
+  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in~\cref{sec:relative-steinberg}
 \end{enumerate}

### 2018-09-27 paper.tex
Started proofreading construction of sigmas

@@
 
-\begin{dfn}
-By definition, a {\it $\sigma$-pair for $\varpi$} is a pair of mutually inverse group homomorphisms $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$ satisfying
+\begin{dfn} \label{dfn:sigma-pair}
+By definition, a {\it $\sigma$-pair for $\varpi$} is a pair of mutually inverse group homomorphisms 
+%$\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$ 
+$\xymatrix{ \sigma(\varpi)\colon N(\varpi) \ar[r] & \ar@<-1.0ex>[l] N(-\varpi)\colon \sigma(-\varpi) }$ satisfying
 \begin{equation} \label{eq:sigmadef}
@@
 
-\begin{rem} Despite the fact that formula~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, 
- we cannot a priori be sure that~\eqref{eq:sigmadef} actually {\it defines} them, i.\,e. gives well-defined maps between $N(\pm\varpi)$.
+\begin{rem} Despite the fact that property~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, 
+ a priori we do not know whether well-defined maps between $N(\pm\varpi)$ with this property exist.
 This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, 
- so we cannot verify that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
+ so we cannot be sure that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
 
@@
 Throughout this section $A$ denote a commutative local ring with the maximal ideal $m$.
-Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.
-
 $j_+\colon A[t] \to A[t, t^{-1}]$. We write $j_+^*$ instead of $\St(\Phi, j_+)$.
@@
 Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
-We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
+We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 4 elementary transformations:
 \begin{enumerate}
@@
 
-\subsection{Structure theorem for Steinberg groups}
-
-sufficient conditions implying the main structure result for Steinberg groups.
-
-Let $\mu$ be a microweight of the root system $\Phi$. Denote by $N_\mu$
-
 \subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $\SL_4$}
+\begin{comment}
 Let $R$ be a local ring and assume that $n\geq 4$.
@@
  modeling conjugation with matrices $\delta_k$ and $\delta_k^{-1}$ (see diagram~\eqref{eq:sigma-diagram} below)
+\end{comment}
+The aim of this subsection is to show that for the root system $\Phi=\rA_3$ and $\varpi = \varpi_1^\vee$
+ there exists a $\sigma$-pair in the sense of~\cref{dfn:sigma-pair}.
+Notice that for $\Phi = \rA_\ell, \ell \geq 4$ and $\varpi=\varpi_k^\vee$, $k=1,\ldots,\ell+1$ 
+the corresponding $\sigma$-pair has been constructed by Tulenbaev in the beginning of~\S~3 in~\cite{Tu83} 
+ (where the corresponding maps and subgroups are denoted $\xymatrix{\delta_k \ar[r] \colon N_k & \ar@<-1.0ex>[l] N^k \colon \delta_k^{-1}}$).
 
-For $n\geq 5$ $\sigma-$morphisms have already been constructed by Tulenbaev, see \S~3 of~\cite{Tu83}.
-Thus, in the sequel we are mainly interested in the case $n=4$.
-To simplify notation, we limit ourselves to constructing the map $\sigma_1$, so everywhere in the sequel we assume that $k=1$.
-
+\begin{comment}
 Of course, the map of right conjugation with $\delta_1$ induces the obvious one-to-one set-theoretic correspondence between $\mathcal{X}_1$ and $\mathcal{X}^1$. 
@@
  as a group given by generators and relations.
-Thus, in order to define $\sigma_1$ we will use the alternate description of $N^1$ given in terms of ``another presentation''.
+\end{comment}
+In order to define the desired map $\sigma_1 = \sigma(\varpi^\vee_1)$ we will use the alternate description of $N(\varpi_1^\vee)$ given in terms of ``another presentation''.
 We start with the following simple observation.
-\begin{lemma} \label{lem:n1-decomp} There is an isomorphism $N_1 \cong N_{1,0} \rtimes P_1^-(R)$, where $N_{1,0}$ denotes the subgroup $\St(n, R[t], tR[t])$
+\begin{lemma} \label{lem:n1-decomp} For $n\geq 4$ there is an isomorphism $N(\varpi_1^\vee) \cong N_{0} \rtimes P_1^-(R)$, where $N_{0}$ denotes the subgroup $\St(n, R[t], tR[t])$
  and $P_1^-(R)$ is the subgroup of $\St(n, R)$ generated by $x_{ij}(\xi)$ with $i\neq 1$.
@@
 \begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ n\in N,\ h\in H,\end{equation} there exists a unique map $f\colon N \rtimes H \to G$
- extending $f_N$ and $f_H$. 
+ extending $f_N$ and $f_H$.  %TODO: Where did I take this? :)
+
 Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct the following two maps and verify that they satisfy~\eqref{eq:coherence-condition}:
-\[ (\sigma_1)_{P_1^-(R)} \colon P_1^-(R) \to N^1, \ \ (\sigma_1)_{N_{1,0}} \colon N_{1,0} \to N^1.\]
+\[ (\sigma_1)_{P_1^-(R)} \colon P_1^-(R) \to N(-\varpi_1^\vee), \ \ (\sigma_1)_{N_{0}} \colon N_{0} \to N(-\varpi_1^\vee).\]
 

### 2018-09-28 paper.tex
Added interlude on weight elements

@@
 
+%TODO: define Weyl elements w_{\alpha}(\varepsilon)
 Recall that for $\alpha\in\Phi$, $\varepsilon\in R^*$ the semisimple root elements $h_\alpha(\varepsilon)$ are defined as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
@@
 such that $ \ext{I} \{u, v\}'_\alpha = \{u, v\}_\alpha$. It is not hard to verify that the image under $\mu_I$ of the element
-\begin{equation} f(\alpha, t, u)= y_\alpha(t(u-1)) \cdot y_{-\alpha}(-t^{-1}(u^{-1}-1))^{x_\alpha(-t)} \cdot y_{\alpha}(t(u-1))^{w_\alpha(-t)}, \end{equation}
+\begin{equation*} f(\alpha, t, u)= y_\alpha(t(u-1)) \cdot y_{-\alpha}(-t^{-1}(u^{-1}-1))^{x_\alpha(-t)} \cdot y_{\alpha}(t(u-1))^{w_\alpha(-t)}, \end{equation*}
 equals $w_\alpha(tu) \cdot w_\alpha(-t)$. This allows us to set $\{t, u \}'_\alpha := f(\alpha, t, u) f(\alpha, 1, u)^{-1}.$
-Now, obviously $\mu_I\{ t, u \}'_\alpha = w_\alpha(tu) w_\alpha(-t) w_\alpha(1) w_\alpha(-u) = \{t, u\}_\alpha,$ as claimed.
+Now, since $\mu_I\{ t, u \}'_\alpha = w_\alpha(tu) w_\alpha(-t) w_\alpha(1) w_\alpha(-u) = \{t, u\}_\alpha,$ 
+ we have defined the desired symbol.
 \begin{rem}
@@
 \end{rem}
-
-\begin{comment}
- \{ t, u \}'_\alpha = h_{\alpha}(u) ^ {h_{?}(t)} =  y_\alpha(t(u-1)) \cdot y_{-\alpha}\left(-t^{-1}(u^{-1}-1)\right)^{x_\alpha(-t)} \cdot y_\alpha\left(t(u-1)\right)^{w_\alpha(-t)} \cdot \\
-\cdot y_\alpha(u-1) \cdot y_{-\alpha}\left(-(u^{-1}-1)\right)^{x_\alpha(-1)} \cdot y_\alpha(u-1)^{w_\alpha(-1)}.
-\end{comment}
 
@@
 
+\begin{example}
+For $1\leq k\leq \ell+1$ and $\varepsilon \in R^*$ denote by $d_k(\varepsilon)$ the matrix from $\GL(\ell+1, R)$ which differs from the unit matrix 
+ only by having the element $\varepsilon$ on the $k$-th place of its diagonal.
+Recall from~\cite[Corollary~4]{Ka77} that for any $g \in \GL(\ell+1, R)$ there exists an automorphism $\beta_g$ of $\St(\ell+1, R)$ 
+ ''modeling`` the automorphism $\alpha_g \colon \GL(\ell+1, R) \to \GL(\ell+1, R)$ of inner conjugation by $g$, i.\,e. such that $\phi \beta_g = \alpha_g \phi$.
+
+It is clear that in the linear case the map $\chi(\varpi_k, \varepsilon)$ coincides with $\beta_{d_k(\varepsilon)}$, 
+ while for other Chevalley groups the maps $\chi(\varpi, k)$ model automorphisms of inner conjugation by weight elements $h_\varpi(\varepsilon)$
+  in the sense of~\cite[\S~4]{Vav09}.
+\end{example}
+
 Let $\varpi \in P(\Phi^\vee)$ be a co-weight of $\Phi$ as above.
@@
 
-\begin{rem} Despite the fact that property~\eqref{eq:sigmadef} determines the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ uniquely, 
- a priori we do not know whether well-defined maps between $N(\pm\varpi)$ with this property exist.
+\begin{rem} Despite the fact that property~\eqref{eq:sigmadef} determines the maps $\sigma(\pm \varpi)$, $\sigma(-\varpi)$ uniquely, 
+ we do not know whether maps with this property actually exist.
 This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, 
- so we cannot be sure that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
+ so we cannot be sure a priori that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
 
@@
 
-\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $\SL_4$}
-\begin{comment}
-Let $R$ be a local ring and assume that $n\geq 4$.
-For $1\leq k\leq n$ denote by $\delta_k$ the $n\times n$ matrix of $\GL(n, R[t, t^{-1}])$ which differs from the unit matrix 
- only by the element $t$ on the $k$-th place of its diagonal.
-Recall from~\cite[Corollary~4]{Ka77} that there exists unique automorphisms $\beta_{\delta_k}$, $\beta_{\delta_k^{-1}}$ of $\St(n, R[t, t^{-1}])$
- modeling conjugation with matrices $\delta_k$ and $\delta_k^{-1}$ (see diagram~\eqref{eq:sigma-diagram} below)
-\end{comment}
+\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-pair for the Steinberg group of rank 3}
 The aim of this subsection is to show that for the root system $\Phi=\rA_3$ and $\varpi = \varpi_1^\vee$
@@
 
-\begin{comment}
-Of course, the map of right conjugation with $\delta_1$ induces the obvious one-to-one set-theoretic correspondence between $\mathcal{X}_1$ and $\mathcal{X}^1$. 
-However, there seems to be no reasonable description of the complete set of relations between the elements $\mathcal{X}_1$ that would allow one to describe $N_1$
- as a group given by generators and relations.
-\end{comment}
-In order to define the desired map $\sigma_1 = \sigma(\varpi^\vee_1)$ we will use the alternate description of $N(\varpi_1^\vee)$ given in terms of ``another presentation''.
-We start with the following simple observation.
-\begin{lemma} \label{lem:n1-decomp} For $n\geq 4$ there is an isomorphism $N(\varpi_1^\vee) \cong N_{0} \rtimes P_1^-(R)$, where $N_{0}$ denotes the subgroup $\St(n, R[t], tR[t])$
- and $P_1^-(R)$ is the subgroup of $\St(n, R)$ generated by $x_{ij}(\xi)$ with $i\neq 1$.
+To simplify notation, throughout this section we set $N_1 = N(\varpi_1)$, $N^1 = N(-\varpi_1)$.
+We only construct one of the maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
+ for shortness we denote it by $\sigma_1$.
+
+In order to define the desired map $\sigma_1$ we will use the alternate description of the subgroup $N_1 = N(\varpi_1^\vee)$
+given in terms of ``another presentation''. We start with the following simple observation.
+\begin{lemma} \label{lem:n1-decomp} For $n\geq 4$ there is an isomorphism $N_1 \cong N_{0} \rtimes P_1^-(A)$, 
+ where $N_{0}$ denotes the subgroup $\St(n, A[t], tA[t])$ and $P_1^-(A)$ is the subgroup of $\St(n, A)$ generated by $x_{ij}(\xi)$ with $i\neq 1$.
 \end{lemma}
 
-Recall that the universal property of semidirect products asserts that for any group $H$ acting on a group $N$ via $\phi \colon H \to \Aut(N)$ and any group homomorphisms
- $f_N\colon N \to G$, $f_H\colon H \to G$ satisfying 
-\begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ n\in N,\ h\in H,\end{equation} there exists a unique map $f\colon N \rtimes H \to G$
- extending $f_N$ and $f_H$.  %TODO: Where did I take this? :)
+Recall that the universal property of semidirect products asserts that for any group $H$ acting on a group $N$ via $\phi \colon H \to \Aut(N)$ 
+and any group homomorphisms $f_N\colon N \to G$, $f_H\colon H \to G$ satisfying 
+\begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ n\in N,\ h\in H,\end{equation} 
+there exists a unique map $f\colon N \rtimes H \to G$ extending $f_N$ and $f_H$.
 
-Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct the following two maps and verify that they satisfy~\eqref{eq:coherence-condition}:
-\[ (\sigma_1)_{P_1^-(R)} \colon P_1^-(R) \to N(-\varpi_1^\vee), \ \ (\sigma_1)_{N_{0}} \colon N_{0} \to N(-\varpi_1^\vee).\]
+Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct the maps 
+\[ (\sigma_1)_{P_1^-(A)} \colon P_1^-(A) \to N^1, \ \ (\sigma_1)_{N_{0}} \colon N_{0} \to N^1\]
+and then verify that they satisfy~\eqref{eq:coherence-condition}.
 
-It is easy to define the first map $(\sigma_1)_{P_1^-(R)}$.
-Using the decomposition $P_1^-(R) \cong U^-_1 \rtimes L_1$ where 
-\[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in R \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in R\rangle \]
+It is easy to define the first map $(\sigma_1)_{P_1^-(A)}$, indeed, using the decomposition $P_1^-(A) \cong U^-_1 \rtimes L_1$ where 
+\[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in A \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in A\rangle \]
 we apply the universal property of semidirect products once again 
- and define $(\sigma_1)_{P_1^-(R)}$ by requiring that it acts identically on $L_1$ 
-and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(R)}(x_{i1}(\xi))= x_{i1}(t\xi)$.
+and define $(\sigma_1)_{P_1^-(A)}$ by requiring that it acts identically on $L_1$ (notice that $L_1 \subseteq N^1$)
+and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(A)}(x_{i1}(\xi))= x_{i1}(t\xi)$.
 
 Before we proceed with the construction of the second map $(\sigma_1)_{N_{1,0}}$ we need to recall several technical
- constructions pertaining to ``another presentation'' of the group $N_{1,0}$.
+ constructions pertaining to ``another presentation'' of the group $N_{0}$.
 
-For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ satisfying $u^tv = 0$ and having at least two zero entries.
+For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ having at least two zero entries and satisfying $u^tv = 0$.
 Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R[t]^n$ such that $u^t \cdot v = 0$ there
@@
 \renewcommand{\theequation}{\arabic{equation}}
-\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\end{equation}
-where $u_{ij}=e_iu_j-e_ju_i,$ and $c_{ij}(v, w)=v_iw_j-v_jw_i.$
+\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\text{ where $u_{ij}=e_iu_j-e_ju_i,$ $c_{ij}(v, w)=v_iw_j-v_jw_i.$}\end{equation}
 

### 2018-09-28 paper.tex
Moved section on another presentation to the preliminaries

@@
 There is an obvious fully faithful embedding $\iota\colon \catname{CRings} \to \catname{Pairs}$ defined on objects by $\iota(R) = (R, R)$.
-%Now if there is a functor $F\colon \catname{CRings}\to \catname{Grp}$ then its {\it relativization} is another functor $\widetilde{F}\colon \catname{Pairs} \to \catname{Groups}$ such that $\widetilde{F} \iota = F$.
 
@@
 
-%Now suppose that $t, u \in R^*$ are invertible elements such that $u-1 \in I$. 
 In the sequel we will also need a {\it relative Steinberg symbol}, i.\,e. a map
@@
  Our relative Steinberg symbols differs from the one defined in~\cite{Ste73} in that
-  it takes values in $\St(\Phi, R, I)$ rather than the group $\St(\Phi, R)$. %Elaborate on this...
+  it takes values in $\St(\Phi, R, I)$ rather than in $\St(\Phi, R)$. %Elaborate on this...
 \end{rem}
+
+\subsection{Another presentation of linear Steinberg groups} \label{sec:another-presentation}
+%TODO: Formulate why do we write what we write
+Throughout this subsection $R$ denotes a commutative ring and $I$ its splitting ideal.
+
+For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ having at least two zero entries and satisfying $u^tv = 0$.
+Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R[t]^n$ such that $u^t \cdot v = 0$ there
+ is a decomposition of $(w^t u) \cdot v$ into a sum of elements of $D(u)$, called {\it canonical decomposition}:
+
+\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\text{ where $u_{ij}=e_iu_j-e_ju_i,$ $c_{ij}(v, w)=v_iw_j-v_jw_i.$}\end{equation}
+Let $u, v \in R^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
+Recall from 3.8, 3.10 of~\cite{Ka77} that under these assumptions one can define certain element
+ $x(u, v)$ of $\St(n, R)$ such that $\phi(x(u, v)) = t(u, v) = 1 + uv^t$.
+The following properties of $x(u, v)$ are standard (cf.~\cite[Lemma~1.1]{Tu83}).
+\begin{lemma} \label{lem:xsmall-properties}
+\begin{lemlist}
+ \item \label{item:xsmall-scalar} If $v$ or $w$ has at least two zero entries, then 
+ \begin{equation}\nonumber x(v, wa) = x(va, w).\end{equation} %TODO: What is ''a``?
+ \item \label{item:xsmall-additivity} If $w_1$ and $w_2$ have at least one common zero entry then
+ \begin{equation}\nonumber x(v, w_1)x(v, w_2) = x(v, w_1+w_2).\end{equation}
+ \item \label{item:xsmall-commute} If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$
+  both have at least two zero entries then $x(v, w)$ and $x(v', w')$ commute.
+\end{lemlist}
+\end{lemma}
+
+Let $u \in E(n, R)e_1$, $v \in I^n$ be such that $u^tv = 0$.
+Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, R, I)$:
+\begin{equation} \label{eq:sigma-definition}
+ F(u, v) = \prod\limits_{i=1}^r x(u,  v_i),\ \
+ S(v, u) = \prod\limits_{i=1}^r x( v_i, u).
+\end{equation}
+Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
+Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover
+ $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
+
+Recall from~\cite{LS17} that it is possible to give a presentation of the relative Steinberg group $\St(n, R, I)$ 
+formulated in terms of elements $F(u, v)$, $S(v, u)$.
+More formally, \cite[Proposition 3.10]{LS17} asserts that $\St(n,\,R,\,I)$ admits presentation with the set of generators
+\begin{multline*} \{F(u,\,v)\mid u\in E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}\, \cup \\ \cup \{S(u,\,v)\mid u\in I^n,\ v\in E(n,\,R)e_1,\ u^tv=0\}\end{multline*}
+subject to relations
+\begin{align}
+&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
+&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
+&F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
+&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, R).
+\end{align}
+Here $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $R^n$.
 
@@
 To simplify notation, throughout this section we set $N_1 = N(\varpi_1)$, $N^1 = N(-\varpi_1)$.
-We only construct one of the maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
+We only construct one of the desired maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
  for shortness we denote it by $\sigma_1$.
 
-In order to define the desired map $\sigma_1$ we will use the alternate description of the subgroup $N_1 = N(\varpi_1^\vee)$
-given in terms of ``another presentation''. We start with the following simple observation.
+In order to define $\sigma_1$ we will use the description of the subgroup $N_1 = N(\varpi_1^\vee)$ given in terms of ``another presentation''.
+We start with the following simple observation.
 \begin{lemma} \label{lem:n1-decomp} For $n\geq 4$ there is an isomorphism $N_1 \cong N_{0} \rtimes P_1^-(A)$, 
@@
 
-Recall that the universal property of semidirect products asserts that for any group $H$ acting on a group $N$ via $\phi \colon H \to \Aut(N)$ 
+Recall that the universal property of semidirect products gives for any group $H$ acting on a group $N$ via $\phi \colon H \to \Aut(N)$ 
 and any group homomorphisms $f_N\colon N \to G$, $f_H\colon H \to G$ satisfying 
-\begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ n\in N,\ h\in H,\end{equation} 
-there exists a unique map $f\colon N \rtimes H \to G$ extending $f_N$ and $f_H$.
+\begin{equation} \label{eq:coherence-condition} f_N(\phi(h)(n)) = f_H(h) f_N(n) f_H(h)^{-1},\ (n\in N,\ h\in H) \end{equation} 
+a unique map $f\colon N \rtimes H \to G$ extending $f_N$ and $f_H$.
 
-Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct the maps 
+Thus, by the above lemma, in order to construct the map $\sigma_1$ we need to construct two maps 
 \[ (\sigma_1)_{P_1^-(A)} \colon P_1^-(A) \to N^1, \ \ (\sigma_1)_{N_{0}} \colon N_{0} \to N^1\]
@@
 we apply the universal property of semidirect products once again 
-and define $(\sigma_1)_{P_1^-(A)}$ by requiring that it acts identically on $L_1$ (notice that $L_1 \subseteq N^1$)
+and define $(\sigma_1)_{P_1^-(A)}$ by requiring that it acts identically on $L_1$ (notice that $L_1 \subseteq N^1$) %TODO: Language???
 and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(A)}(x_{i1}(\xi))= x_{i1}(t\xi)$.
 
-Before we proceed with the construction of the second map $(\sigma_1)_{N_{1,0}}$ we need to recall several technical
- constructions pertaining to ``another presentation'' of the group $N_{0}$.
+%TODO: define \delta_1 & \delta_1^{-1} -- these are not matrices
 
-For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ having at least two zero entries and satisfying $u^tv = 0$.
-Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R[t]^n$ such that $u^t \cdot v = 0$ there
- is a decomposition of $(w^t u) \cdot v$ into a sum of elements of $D(u)$, called {\it canonical decomposition}:
-\setcounter{equation}{1}
-\renewcommand{\theequation}{\arabic{equation}}
-\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\text{ where $u_{ij}=e_iu_j-e_ju_i,$ $c_{ij}(v, w)=v_iw_j-v_jw_i.$}\end{equation}
+To define the map $(\sigma_1)_{N_{1,0}}$ we will invoke the presentation of the relative Steinberg group given in~\cref{sec:another-presentation}
+in the special case $R=A[t]$, $I=tA[t]$.
 
-Let $A$ be a commutative ring and $I$ be a splitting ideal of $A$.
-Let $u, v \in A^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
-Recall from 3.8, 3.10 of~\cite{Ka77} that under these assumptions one can define certain element
- $x(u, v)$ of $\St(n, A)$ such that $\pi(x(u, v)) = t(u, v) = 1 + uv^t$.
-The following properties of $x(u, v)$ are standard (cf.~\cite[Lemma~1.1]{Tu83}).
-\begin{lemma} \label{lem:xsmall-properties}
-\begin{lemlist}
- \item \label{item:xsmall-scalar} If $v$ or $w$ has at least two zero components, then 
- \begin{equation}\nonumber x(v, wa) = x(va, w).\end{equation}
- \item \label{item:xsmall-additivity} If $w_1$ and $w_2$ have at least one common zero coordinate then
- \begin{equation}\nonumber x(v, w_1)x(v, w_2) = x(v, w_1+w_2).\end{equation}
- \item \label{item:xsmall-commute} If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$
-  both have at least two zero components then $x(v, w)$ and $x(v', w')$ commute.
-\end{lemlist}
-\end{lemma}
-
-Let $u \in E(n, A)e_1$, $v \in I^n$ be such that $u^tv = 0$.
-Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, A, I)$:
-\begin{equation} \label{eq:sigma-definition}
- F(u, v) = \prod\limits_{i=1}^r x(u,  v_i),\ \
- S(v, u) = \prod\limits_{i=1}^r x( v_i, u).
-\end{equation}
-Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
-Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover
- $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
-
-Recall from~\cite{LS17} that it is possible to give a presentation of the relative Steinberg group $\St(n, A, I)$ formulated in terms of elements $F(u, v)$, $S(v, u)$.
-More formally, \cite[Proposition 3.10]{LS17} asserts that $\St(n,\,A,\,I)$ admits presentation with the set of generators
-\begin{multline*} \{F(u,\,v)\mid u\in E(n,\,A)e_1,\ v\in I^n,\ u^tv=0\}\, \cup \\ \cup \{S(u,\,v)\mid u\in I^n,\ v\in E(n,\,A)e_1,\ u^tv=0\}\end{multline*}
-subject to relations
-\setcounter{equation}{0}
-\renewcommand{\theequation}{R\arabic{equation}}
-
-\begin{align}
-&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
-&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
-&F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
-&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, A).
-\end{align}
-Here $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $A^n$.
-
-\setcounter{equation}{3}
-\renewcommand{\theequation}{\arabic{equation}}
-
-To define the map $(\sigma_1)_{N_{1,0}}$ we will invoke the above presentation in the special case $A=R[t]$, $I=tR[t]$.
-Indeed, define $\sigma_1$ on $N_{1,0}=\St(n, R[t], tR[t])$ by the following identities: 
+Indeed, define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
 \begin{equation}

### 2018-09-28 paper.tex
Renamed varpi to omega in many places

@@
 
-Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
-Thus, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ we can define a map of abelian groups $\chi(\varpi, \varepsilon) \in \Hom(\ZZ \Phi, R^*)$
- via the formula $\chi(\varpi, \varepsilon)(\beta) = \varepsilon ^ {(\varpi, \beta)}$.
+Notice that for $\omega \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\omega, \beta) \in \ZZ $.
+Thus, for $\varepsilon \in R^*$ and $\omega \in P(\Phi^\vee)$ we can define a map of abelian groups $\chi(\omega, \varepsilon) \in \Hom(\ZZ \Phi, R^*)$
+ via the formula $\chi(\omega, \varepsilon)(\beta) = \varepsilon ^ {(\omega, \beta)}$.
 
@@
 It is clear that in the linear case the map $\chi(\varpi_k, \varepsilon)$ coincides with $\beta_{d_k(\varepsilon)}$, 
- while for other Chevalley groups the maps $\chi(\varpi, k)$ model automorphisms of inner conjugation by weight elements $h_\varpi(\varepsilon)$
+ while for other Chevalley groups the maps $\chi(\omega, k)$ model automorphisms of inner conjugation by weight elements $h_\omega(\varepsilon)$
   in the sense of~\cite[\S~4]{Vav09}.
@@
 
-Let $\varpi \in P(\Phi^\vee)$ be a co-weight of $\Phi$ as above.
-Denote by $\XX(\varpi)$ the subset of $\XX_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
-$(\alpha, \varpi) < 0$ implies that $\xi \in A[t]$ is divisible by $t^{-(\alpha, \varpi)}$. Denote by $N(\varpi)$ the subgroup of $\St(\Phi, A[t])$ generated by $\XX(\varpi)$.
+Let $\omega \in P(\Phi^\vee)$ be a co-weight of $\Phi$ as above.
+Denote by $\XX(\omega)$ the subset of $\XX_{\Phi, A[t]}$ consisting of those generators $x_{\alpha}(\xi)$ of $\St(\Phi, A[t])$ for which 
+$(\alpha, \omega) < 0$ implies that $\xi \in A[t]$ is divisible by $t^{-(\alpha, \omega)}$. Denote by $N(\omega)$ the subgroup of $\St(\Phi, A[t])$ generated by $\XX(\omega)$.
 
 \begin{dfn} \label{dfn:sigma-pair}
-By definition, a {\it $\sigma$-pair for $\varpi$} is a pair of mutually inverse group homomorphisms 
-%$\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$ 
-$\xymatrix{ \sigma(\varpi)\colon N(\varpi) \ar[r] & \ar@<-1.0ex>[l] N(-\varpi)\colon \sigma(-\varpi) }$ satisfying
+By definition, a {\it $\sigma$-pair for $\omega$} is a pair of mutually inverse group homomorphisms 
+$\xymatrix{ \sigma(\omega)\colon N(\omega) \ar[r] & \ar@<-1.0ex>[l] N(-\omega)\colon \sigma(-\omega) }$ satisfying
 \begin{equation} \label{eq:sigmadef}
-\sigma(\pm \varpi)(x_\alpha(\xi)) = x_\alpha(t^{(\pm \varpi, \alpha)}\cdot \xi), 
- \text{ for all } x_\alpha(\xi) \in \XX(\pm\varpi).
+\sigma(\pm \omega)(x_\alpha(\xi)) = x_\alpha(t^{(\pm \omega, \alpha)}\cdot \xi), 
+ \text{ for all } x_\alpha(\xi) \in \XX(\pm\omega).
 \end{equation}\end{dfn}
-It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$.
-Moreover, the maps $\sigma(\varpi), \sigma(-\varpi)$ make the following diagram commute:
+It is clear that the maps $\sigma(\omega)$, $\sigma(-\omega)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\omega$.
+Moreover, the maps $\sigma(\omega), \sigma(-\omega)$ make the following diagram commute:
 \begin{equation} \label{eq:sigma-diagram}
-\xymatrix{ N(\varpi) \ar[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
+\xymatrix{ N(\omega) \ar[r]^{\sigma(\omega)}\ar@{^{(}->}[d] & N(-\omega) \ar@{^{(}->}[d] \ar[r]^{\sigma(-\omega)} & N(\omega) \ar@{^{(}->}[d] \\ 
           \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
-          \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, A[t, t^{-1}]).} \end{equation}
+          \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(\omega, t)} & \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(-\omega, t)} & \St(\Phi, A[t, t^{-1}]).} \end{equation}
 
-\begin{rem} Despite the fact that property~\eqref{eq:sigmadef} determines the maps $\sigma(\pm \varpi)$, $\sigma(-\varpi)$ uniquely, 
+\begin{rem} Despite the fact that property~\eqref{eq:sigmadef} determines the maps $\sigma(\pm \omega)$, $\sigma(-\omega)$ uniquely, 
  we do not know whether maps with this property actually exist.
-This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\varpi)$ between the generators $\XX(\pm\varpi)$, 
- so we cannot be sure a priori that $\sigma(\pm\varpi)$ preserve these relations. \end{rem}
+This is caused by the fact there is no direct description of the set of relations which hold in $N(\pm\omega)$ between the generators $\XX(\pm\omega)$, 
+ so we cannot be sure a priori that $\sigma(\pm\omega)$ preserve these relations. \end{rem}
 
@@
 \subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-pair for the Steinberg group of rank 3}
-The aim of this subsection is to show that for the root system $\Phi=\rA_3$ and $\varpi = \varpi_1^\vee$
+The aim of this subsection is to show that for the root system $\Phi=\rA_3$ and $\omega = \varpi_1^\vee$
  there exists a $\sigma$-pair in the sense of~\cref{dfn:sigma-pair}.
-Notice that for $\Phi = \rA_\ell, \ell \geq 4$ and $\varpi=\varpi_k^\vee$, $k=1,\ldots,\ell+1$ 
+Notice that for $\Phi = \rA_\ell, \ell \geq 4$ and $\omega=\varpi_k^\vee$, $k=1,\ldots,\ell+1$ 
 the corresponding $\sigma$-pair has been constructed by Tulenbaev in the beginning of~\S~3 in~\cite{Tu83} 

### 2018-09-28 paper.tex
Formulated presentation as a proposition

@@
 %TODO: Formulate why do we write what we write
-Throughout this subsection $R$ denotes a commutative ring and $I$ its splitting ideal.
+Throughout this subsection $R$ denotes a commutative ring.
 
@@
 
-Let $u \in E(n, R)e_1$, $v \in I^n$ be such that $u^tv = 0$.
-Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, R, I)$:
+Now let $I$ be a splitting ideal of $R$.
+Let $u \in E(n, R)e_1$, $v \in I^n$ be vectors such that $u^tv = 0$.
+Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, R, I) \leq \St(n, R)$:
 \begin{equation} \label{eq:sigma-definition}
@@
 Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
-Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover
- $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
+Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
 
-Recall from~\cite{LS17} that it is possible to give a presentation of the relative Steinberg group $\St(n, R, I)$ 
-formulated in terms of elements $F(u, v)$, $S(v, u)$.
-More formally, \cite[Proposition 3.10]{LS17} asserts that $\St(n,\,R,\,I)$ admits presentation with the set of generators
-\begin{multline*} \{F(u,\,v)\mid u\in E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}\, \cup \\ \cup \{S(u,\,v)\mid u\in I^n,\ v\in E(n,\,R)e_1,\ u^tv=0\}\end{multline*}
-subject to relations
+It is possible to give a presentation of the relative Steinberg group $\St(n, R, I)$ formulated in terms of elements $F(u, v)$, $S(v, u)$.
+\begin{prop}[\text{\cite[Proposition 3.10]{LS17}}] \label{prop:rel-presentation}
+ For any $n\geq 4$ the group $\St(n,\,R,\,I)$ can be presented by means of generators $F(u,\,v)$, $S(v,\,u)$ (where $u\in E(n,\,R)e_1,$ and $v\in I^n$ are such that $u^tv=0$) subject to the following relations:
 \begin{align}
@@
 \end{align}
-Here $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $R^n$.
+\end{prop}
+In the above statement $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $R^n$.
+\begin{rem}
+Using essentially the same reasoning as in~\cite[Proposition~8]{S15} it is not hard to show that the above presentation still holds for $\St(\Phi, R, I)$ without the assumption that $I$ is splitting.
+\end{rem}
 

### 2018-10-01 paper.tex
Moved everything

@@
 
+For $g\in \GL(n, R)$ we denote by $g^*$ the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$.
+We denote by $e_i$ the standard basis vector of $R^n$. For a pair of vectors $u, v \in R^n$ such that $u^tv = 0$ we denote by
+$t(u, v)$ the rank $1$ matrix $e + uv^t$. Notice that $t(u, v)$ lies in $\E(n, R)$ provided $u$ or $v$ is unimodular. %TODO: Reference
+
+%TODO: Introduce notation for GL(n, R); E(n, R)
+
 \subsection{Steinberg groups}
@@
 
+\subsection{Another presentation of linear Steinberg groups} \label{sec:another-presentation}
+Throughout this subsection $R$ denotes a commutative ring.
+
+For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all vectors $v$ which are orthogonal to $u$ (i.\,e. $u^tv = 0$) and have at least two zero entries.
+Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R^n$ such that $u^t v = 0$ there
+ is a decomposition of $(w^t u) \cdot v$ into a sum of elements of $D(u)$, called {\it canonical decomposition}:
+\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\end{equation}
+where $u_{ij} =e_iu_j-e_ju_i \in D(u)$ and $c_{ij}(v, w) =v_iw_j-v_jw_i \in R$.
+Let $u, v \in R^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
+Recall from 3.8, 3.10 of~\cite{Ka77} that under these assumptions one can define certain element
+ $x(u, v)$ of $\St(n, R)$ such that $\phi(x(u, v)) = t(u, v) = 1 + uv^t$.
+Let us recall the standard properties of $x(u, v)$ (cf.~\cite[Lemma~1.1]{Tu83}).
+\begin{itemize}
+ \item If $v$ or $w$ has at least two zero entries, then
+  \begin{equation} \label{item:xsmall-scalar} x(v, wa) = x(va, w), \text{ for $a\in R$} \end{equation}
+ \item If $w_1$ and $w_2$ have at least one common zero entry then
+ \begin{equation} \label{item:xsmall-additivity} x(v, w_1) \cdot x(v, w_2) = x(v, w_1+w_2).\end{equation}
+ \item If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$ both have at least two zero entries then 
+  \begin{equation} \label{item:xsmall-commute} [x(v, w),\ x(v', w')] = 1 \end{equation}
+\end{itemize}
+\begin{comment}
+Now let $I$ be a splitting ideal of $R$.
+Let $u \in E(n, R)e_1$, $v \in I^n$ be vectors such that $u^tv = 0$.
+Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, R, I) \leq \St(n, R)$:
+\begin{equation} \label{eq:sigma-definition}
+ F(u, v) = \prod\limits_{i=1}^r x(u,  v_i),\ \
+ S(v, u) = \prod\limits_{i=1}^r x( v_i, u).
+\end{equation}
+Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
+Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
+\end{comment}
+
 \subsection{Relative Steinberg groups} \label{sec:relative-steinberg}
@@
  Our relative Steinberg symbols differs from the one defined in~\cite{Ste73} in that
-  it takes values in $\St(\Phi, R, I)$ rather than in $\St(\Phi, R)$. %Elaborate on this...
+  it takes values in $\St(\Phi, R, I)$ rather than $\St(\Phi, R)$. %Elaborate on this...
 \end{rem}
 
-\subsection{Another presentation of linear Steinberg groups} \label{sec:another-presentation}
-%TODO: Formulate why do we write what we write
-Throughout this subsection $R$ denotes a commutative ring.
+In the sequel we will need an explicit presentation of the relative linear Steinberg group by means of generators and relations.
+The presentation we formulate below should be thought of as an ''improved`` version of the presentation of the relative linear Steinberg group
+ given by Tulenbaev in~\cite[Definition~1.5]{Tu83} (cf. also~\cite[Proposition~3.2]{LS17}).
+We refer the reader to~\cite[Section~3]{LS17} for the discussion why this presentation is better than Tulenbaev's one
+ (the short answer is: it remains useful in the case $\Phi = \rA_3$).
 
-For $u \in R^n$ we denote by $D(u)$ the subset of $R^n$ consisting of all $v$ having at least two zero entries and satisfying $u^tv = 0$.
-Recall from 3.2 of~\cite{Ka77} that for every $u, v, w \in R[t]^n$ such that $u^t \cdot v = 0$ there
- is a decomposition of $(w^t u) \cdot v$ into a sum of elements of $D(u)$, called {\it canonical decomposition}:
-
-\begin{equation} \label{eq:canonical} (w^tu) \cdot v=\sum_{i<j}u_{ij} c_{ij}(v, w),\text{ where $u_{ij}=e_iu_j-e_ju_i,$ $c_{ij}(v, w)=v_iw_j-v_jw_i.$}\end{equation}
-Let $u, v \in R^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
-Recall from 3.8, 3.10 of~\cite{Ka77} that under these assumptions one can define certain element
- $x(u, v)$ of $\St(n, R)$ such that $\phi(x(u, v)) = t(u, v) = 1 + uv^t$.
-The following properties of $x(u, v)$ are standard (cf.~\cite[Lemma~1.1]{Tu83}).
-\begin{lemma} \label{lem:xsmall-properties}
-\begin{lemlist}
- \item \label{item:xsmall-scalar} If $v$ or $w$ has at least two zero entries, then 
- \begin{equation}\nonumber x(v, wa) = x(va, w).\end{equation} %TODO: What is ''a``?
- \item \label{item:xsmall-additivity} If $w_1$ and $w_2$ have at least one common zero entry then
- \begin{equation}\nonumber x(v, w_1)x(v, w_2) = x(v, w_1+w_2).\end{equation}
- \item \label{item:xsmall-commute} If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$
-  both have at least two zero entries then $x(v, w)$ and $x(v', w')$ commute.
-\end{lemlist}
-\end{lemma}
-
-Now let $I$ be a splitting ideal of $R$.
-Let $u \in E(n, R)e_1$, $v \in I^n$ be vectors such that $u^tv = 0$.
-Recall from \S~4 of~\cite{LS17} that one can define the following elements of $\St(n, R, I) \leq \St(n, R)$:
-\begin{equation} \label{eq:sigma-definition}
- F(u, v) = \prod\limits_{i=1}^r x(u,  v_i),\ \
- S(v, u) = \prod\limits_{i=1}^r x( v_i, u).
-\end{equation}
-Here $\{v_r\}$, $r=1,\ldots,N$ is any collection of elements of $I^n \cap D(u)$ such that $\sum_{r=1}^N v_r = v$.
-Since $u$ is unimodular, such a collection always exists by~\eqref{eq:canonical}, moreover $F(u, v)$ and $S(u, v)$ do not depend on its choice. %TODO: Give reference
-
-It is possible to give a presentation of the relative Steinberg group $\St(n, R, I)$ formulated in terms of elements $F(u, v)$, $S(v, u)$.
 \begin{prop}[\text{\cite[Proposition 3.10]{LS17}}] \label{prop:rel-presentation}
- For any $n\geq 4$ the group $\St(n,\,R,\,I)$ can be presented by means of generators $F(u,\,v)$, $S(v,\,u)$ (where $u\in E(n,\,R)e_1,$ and $v\in I^n$ are such that $u^tv=0$) subject to the following relations:
+ Assume that $I$ is a splitting ideal of a commutative ring $R$. 
+ Then for any $\ell\geq 3$ the group $\St(\rA_\ell,\,R,\,I)$ can be presented by means of two families of generators $F(u,\,v)$, $S(v,\,u)$
+  (where $u\in \E(n,\,R)e_1,$ and $v\in I^n$ are such that $u^tv=0$) subject to the following relations:
 \begin{align}
@@
 \end{prop}
-In the above statement $g^*$ denotes the contragradient matrix, i.\,e. $g^* = {g^{-1}}^t$ and $e_i$ is the standard basis vector of $R^n$.
 \begin{rem}
-Using essentially the same reasoning as in~\cite[Proposition~8]{S15} it is not hard to show that the above presentation still holds for $\St(\Phi, R, I)$ without the assumption that $I$ is splitting.
+Although we will not need this, using essentially the same reasoning as in~\cite[Proposition~8]{S15} it is not hard to show that 
+$\St(\rA_\ell, R, I)$ still admits the above presentation without the assumption that $I$ is splitting.
 \end{rem}
@@
 
-Indeed, define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
+%TODO: Pick a decomposition  $v = \sum v_i$
+Indeed, for $u \in E(n, A[t])$ and $v \in tA[t]$ define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
 \begin{equation}

### 2018-10-01 paper.tex
Rewriting stuff

@@
 \DeclareMathOperator{\Hom}{Hom}
+\DeclareMathOperator{\Um}{Um}
 \DeclareMathOperator{\colim}{colim}
@@
 \subsection{Another presentation of linear Steinberg groups} \label{sec:another-presentation}
-Throughout this subsection $R$ denotes a commutative ring.
+Throughout this subsection $R$ denotes a commutative ring and $n \geq 4$.
 
@@
 \end{comment}
+
+Now assume that $I$ is an ideal of ring $R$ embedded as a subring into a larger ring $S$.
+Let $d$ be an element of the subgroup $T(n, S)$ of diagonal matrices of $\GL(n, S)$ such that $d \cdot I^n \subseteq R^n$.
+Now for $u \in \Um(n, R)$, $v \in I^n$ such that $u^tv = 0$ and $d^* u = d^{-1}u \in R^n$ we want to define certain elements $X_d(u, v) \in \St(n, R)$.
+If $v = \sum v_i$ is a decomposition of $v$ into a sum of elements $v_i \in D(u) \cap I^n$ (e.\,g.
+the canonical decomposition~\eqref{eq:canonical}), we set $X_d(u, v) = \prod x(d^{-1}u, dv_i)$.
+\begin{lemma} %\label{lem:cor-conj}
+ The element $X^g(u, v)$ is well-defined, i.\,e. it does not depend on the choice of  decomposition for $v$.
+\end{lemma}
+\begin{proof}
+ The idea is to decompose each factor $x(d^{-1}u, dv_i)$ further using the canonical decomposition of $v_i$ and then using~\eqref{item:xsmall-scalar}--\eqref{item:xsmall-commute} arrive to the canonical decomposition of $v$ by reordering and collecting factors (cf.~with Tulenbaev's argument after~\cite[Lemma~1.1]{Tu83}).
+
+ Let $v = \sum_r v^r$ be a decomposition as above. 
+ Since each $v^r$ is orthogonal to $u$ we can write the canonical decomposition  
+ $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
+ Using~\eqref{item:xsmall-scalar}--\eqref{item:xsmall-commute} we can rewrite $X_d(u, v)$ as follows:
+ \begin{multline*} \prod\limits_r x(d^{-1}u, dv^r) = \prod\limits_{r}\prod\limits_{i<j} x(d^{-1} u, du_{ij}c_{ij}(v^r, w)) =  \prod\limits_{i<j} x(d_1^{-1} u, d u_{ij}c_{ij}(v, w)).
+\qedhere \end{multline*}
+\end{proof}
+
+%TODO: Pick a decomposition  $v = \sum v_i$
+Indeed, for $u \in E(n, A[t])$ and $v \in tA[t]$ define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
+\begin{equation}
+ \sigma_1(F(u, v)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot t u, \delta_1 \cdot t^{-1} v_i),\ \
+ \sigma_1(S(v, u)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot v_i, \delta_1 \cdot u).
+\end{equation}
+
+\begin{lemma} \label{lem:cor-conj}
+ \begin{lemlist}
+   \item \label{item:correctness} The elements $\sigma_1(F(u, v))$ and $\sigma_1(S(v, u))$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
+   \item \label{item:conjugation} For any $g \in N^1$ one has 
+      \begin{equation}
+          \nonumber {}^g\left(\sigma_1(F(u, v))\right) = \sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right),\ \ 
+                    {}^g\left(\sigma_1(S(u, v))\right) = \sigma_1\left(S(g' \cdot u, {g'}^{*} \cdot v)\right),                    
+      \end{equation}
+      where $g' = {}^{\delta_1}\pi(g).$
+ \end{lemlist}
+\end{lemma}
+\begin{proof}[Short proof] 
+ The second assertion can be proved similarly to~\cite[3.14]{Ka77}, (cf. also with the proof of~\cite[Lemma~4.4d]{LS17}).
+\end{proof}
+\begin{proof}[Long proof]
+ We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
+ Choose $w\in R^n$ so that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
+ We can write ${}^g\left(\sigma_1\left(F(u, v)\right)\right)$ as follows:
+ \begin{equation} \nonumber
+   \prod\limits_{1\leq i<j\leq n} x(\pi(g) \cdot \delta_1^{-1} \cdot t u, \pi(g)^* \cdot \delta_1 \cdot t^{-1} u_{ij}c_{ij})
+                                   = \prod\limits_{1\leq i<j\leq n} x(\delta_1^{-1} \cdot g'\cdot t u, \delta_1 \cdot {g'}^* \cdot t^{-1} u_{ij}c_{ij}).
+ \end{equation} 
+ Now for every factor in the right-hand side we do the following.
+ If $\{i, j\} = \{h, k\}$ or $\{i, j\} \cap \{h, k\} = \emptyset$ we leave the term unchanged.
+ Otherwise, if, $|\{i, j\} \cap \{h, k\}| = 1$,  say $j = h$, $i\neq k$, we further decompose it as follows:
+  \begin{equation} \nonumber
+    x(\delta_1^{-1} \cdot t u', \delta_1 \cdot {g'}^* \cdot u_{ij} (c_{ij} t^{-1})) = 
+     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ij} (c_{ij} t^{-1})) \cdot 
+     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ki} (c_{ij} t^{-1})).
+  \end{equation}
+  Here $u' = g'  u = t_{jk}(\xi') \cdot u$.
+  Notice that ${g'}^*u_{ij} = t_{kj}(-\xi') \cdot u_{ij} = e_iu_j - e_ju_i + e_k\xi'u_i =u'_{ij}+u'_{ki}\xi'$.
+
+  Thus, we arrive at a product $\prod_{s} x(\delta_1^{-1} \cdot u't, \delta_1 \cdot v'_s t^{-1}) $, where $v'_s \in D(u')$ and
+   $\sum v'_s = {g'}^*v$. Clearly, this product equals $\sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right)$ by definition.
+\end{proof}
 
@@
 
-%TODO: Pick a decomposition  $v = \sum v_i$
-Indeed, for $u \in E(n, A[t])$ and $v \in tA[t]$ define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
-\begin{equation}
- \sigma_1(F(u, v)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot t u, \delta_1 \cdot t^{-1} v_i),\ \
- \sigma_1(S(v, u)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot v_i, \delta_1 \cdot u).
-\end{equation}
-
-\begin{lemma} \label{lem:cor-conj}
- \begin{lemlist}
-   \item \label{item:correctness} The elements $\sigma_1(F(u, v))$ and $\sigma_1(S(v, u))$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
-   \item \label{item:conjugation} For any $g \in N^1$ one has 
-      \begin{equation}
-          \nonumber {}^g\left(\sigma_1(F(u, v))\right) = \sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right),\ \ 
-                    {}^g\left(\sigma_1(S(u, v))\right) = \sigma_1\left(S(g' \cdot u, {g'}^{*} \cdot v)\right),                    
-      \end{equation}
-      where $g' = {}^{\delta_1}\pi(g).$
- \end{lemlist}
-\end{lemma}
-\begin{proof}[Short proof]
- The first assertion can be easily verified using the canonical decomposition and~\cref{lem:xsmall-properties}
-  (compare with Tulenbaev's argument after~\cite[Lemma~1.1]{Tu83}).
-
- The second assertion can be proved similarly to~\cite[3.14]{Ka77}, (cf. also with the proof of~\cite[Lemma~4.4d]{LS17}).
-\end{proof}
-\begin{proof}[Long proof]
- Let us verify the first assertion. Let $v = \sum_r v^r$ be a decomposition as above. 
- Since each $v^r$ is orthogonal to $u$ we can write the canonical decomposition  
- $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
- \cref{lem:xsmall-properties} allows us to rewrite the right-hand side of~\ref{eq:sigma-definition} in such a way that 
-  it does not depend on the choice of decomposition for $v$:
- \begin{multline}
-  \prod\limits_r x(\delta_1^{-1} ut, \delta_1 v^rt^{-1}) = \prod\limits_{r}\prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v^r, w)t^{-1}) = \\ 
-   = \prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v, w)t^{-1}). 
- \end{multline}
-
- We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
- Choose $w\in R^n$ so that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
- We can write ${}^g\left(\sigma_1\left(F(u, v)\right)\right)$ as follows:
- \begin{equation} \nonumber
-   \prod\limits_{1\leq i<j\leq n} x(\pi(g) \cdot \delta_1^{-1} \cdot t u, \pi(g)^* \cdot \delta_1 \cdot t^{-1} u_{ij}c_{ij})
-                                   = \prod\limits_{1\leq i<j\leq n} x(\delta_1^{-1} \cdot g'\cdot t u, \delta_1 \cdot {g'}^* \cdot t^{-1} u_{ij}c_{ij}).
- \end{equation} 
- Now for every factor in the right-hand side we do the following.
- If $\{i, j\} = \{h, k\}$ or $\{i, j\} \cap \{h, k\} = \emptyset$ we leave the term unchanged.
- Otherwise, if, $|\{i, j\} \cap \{h, k\}| = 1$,  say $j = h$, $i\neq k$, we further decompose it as follows:
-  \begin{equation} \nonumber
-    x(\delta_1^{-1} \cdot t u', \delta_1 \cdot {g'}^* \cdot u_{ij} (c_{ij} t^{-1})) = 
-     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ij} (c_{ij} t^{-1})) \cdot 
-     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ki} (c_{ij} t^{-1})).
-  \end{equation}
-  Here $u' = g'  u = t_{jk}(\xi') \cdot u$.
-  Notice that ${g'}^*u_{ij} = t_{kj}(-\xi') \cdot u_{ij} = e_iu_j - e_ju_i + e_k\xi'u_i =u'_{ij}+u'_{ki}\xi'$.
-
-  Thus, we arrive at a product $\prod_{s} x(\delta_1^{-1} \cdot u't, \delta_1 \cdot v'_s t^{-1}) $, where $v'_s \in D(u')$ and
-   $\sum v'_s = {g'}^*v$. Clearly, this product equals $\sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right)$ by definition.
-\end{proof}
-
 \begin{cor}

### 2018-10-02 paper.tex
Rewriting stuff

--- 2018-10-01 paper.tex
@@
 where $u_{ij} =e_iu_j-e_ju_i \in D(u)$ and $c_{ij}(v, w) =v_iw_j-v_jw_i \in R$.
+
 Let $u, v \in R^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
@@
 \end{comment}
+
+Now assume that $I$ is an ideal of ring $R$ embedded as a subring into a larger ring $S$. 
+Let $d$ be an element of the subgroup $T(n, S)$ of diagonal matrices of $\GL(n, S)$, notice that $d^* = d^{-1}$.
+Let $u \in \Um(n, R)$ and $v \in I^n$ be such that $u^tv = 0$ and let $v = \sum v_i$ 
+ be a decomposition of $v$ into a sum of elements $v_i \in D(u) \cap I^n$ (e.\,g. the canonical decomposition~\eqref{eq:canonical}),
+
+Under the assumption $d^{-1}u \in R^n$, $d \cdot I^n \subseteq R^n$ set 
+ \begin{equation} X_d(u, v) = \prod_i x(d^{-1}u, dv_i) \in \St(n, R). \end{equation}
+Under the assumption $d u\in R^n$, $d^{-1} \cdot I^n \subseteq R^n$ set 
+ \begin{equation} Y_d(v, u) = \prod_i x(d^{-1} v_i, du) \in \St(n, R). \end{equation}
+
+\begin{lemma} %\label{lem:cor-conj}
+ The elements $X_d(u, v)$, $Y_d(u, v)$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
+\end{lemma}
+\begin{proof}
+\begin{comment}
+ Decompose each factor $x(d^{-1}u, dv_i)$ further using the canonical decomposition of $v_i$ and then 
+  use relations~\eqref{item:xsmall-scalar}--\eqref{item:xsmall-commute} to reorder and collect factors
+  in such a way that  arrive to the canonical decomposition of $v$ by (cf.~with Tulenbaev's argument after~\cite[Lemma~1.1]{Tu83}).
+\end{comment} 
+ Let $v = \sum_r v^r$ be a decomposition as above. 
+ Since each $v^r$ is orthogonal to $u$ we can write the canonical decomposition  
+ $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
+ Now from~\eqref{item:xsmall-scalar}--\eqref{item:xsmall-commute} we obtain:
+ \begin{multline*} \prod\limits_r x(d^{-1}u, dv^r) = \prod\limits_{r}\prod\limits_{i<j} x(d^{-1} u, du_{ij}c_{ij}(v^r, w)) =
+  \prod\limits_{i<j} x(d^{-1} u, d u_{ij}c_{ij}(v, w)). \qedhere \end{multline*}
+\end{proof}
+
+\begin{lemma} Suppose that $g = x_{hk}(\xi)$ is a generator of $\St(n, R)$ such that $m = d\phi(g)d^{-1} \in \E(n, R)$, then 
+ \begin{equation*} g \cdot X_d(u, v) \cdot g^{-1} = X_d(mu, m^*v) \text{ and } g \cdot Y_d(v, u) \cdot g^{-1} = Y_d(mv, m^*u). \end{equation*}
+\end{lemma}
+\begin{proof}
+Similar to~\cite[3.14]{Ka77}, cf. also with the proof of~\cite[Lemma~4.4d]{LS17}.
+\begin{comment} % Do not remove
+ Choose $w\in R^n$ such that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
+ By~\cite[3.12]{Ka77} we can write $g \cdot X_d(u, v) \cdot g^{-1}$ as follows:
+ \begin{equation} \nonumber
+   \prod\limits_{1\leq i<j\leq n} x(\phi(g) \cdot d^{-1} \cdot u, \phi(g)^* \cdot d \cdot u_{ij}c_{ij})
+ = \prod\limits_{1\leq i<j\leq n} x( d^{-1} \cdot m \cdot u, d \cdot m^* \cdot u_{ij}c_{ij}).
+ \end{equation} 
+ Now for every factor in the right-hand side we do the following:
+ if $\{i, j\} = \{h, k\}$ or $\{i, j\} \cap \{h, k\} = \emptyset$ we leave the factor unchanged,
+ otherwise, if, $|\{i, j\} \cap \{h, k\}| = 1$,  say $j = h$, $i\neq k$, we further decompose it as follows:
+  \begin{equation} \nonumber
+     x(d^{-1} \cdot u', d \cdot m^* \cdot u_{ij} c_{ij}) = 
+     x(d^{-1} \cdot u', d \cdot u'_{ij} c_{ij}) \cdot 
+     x(d^{-1} \cdot u', d \cdot u'_{ki} c_{ij}).
+  \end{equation}
+  Here $u' = m  u = t_{jk}(\xi') \cdot u$ for some $\xi' \in R$.
+  Notice that $m^* \cdot u_{ij} = t_{kj}(-\xi') \cdot u_{ij} = e_iu_j - e_ju_i + e_k\xi'u_i =u'_{ij}+u'_{ki}\xi'$.
+
+  Thus, we have written the expression in the form $\prod_{s} x(d^{-1} \cdot u', d \cdot v'_s) $, where $v'_s \in D(u')$ and
+   $\sum v'_s = m^*v$. It is clear now, that the latter expression equals $X_d(m u, m^* v)$.
+\end{comment} 
+\end{proof}
 
@@
 
-%TODO: define \delta_1 & \delta_1^{-1} -- these are not matrices
-
 To define the map $(\sigma_1)_{N_{1,0}}$ we will invoke the presentation of the relative Steinberg group given in~\cref{sec:another-presentation}
 in the special case $R=A[t]$, $I=tA[t]$.
+%We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
 
-%TODO: Pick a decomposition  $v = \sum v_i$
 Indeed, for $u \in E(n, A[t])$ and $v \in tA[t]$ define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
@@
 \end{lemma}
-\begin{proof}[Short proof]
- The first assertion can be easily verified using the canonical decomposition and~\cref{lem:xsmall-properties}
-  (compare with Tulenbaev's argument after~\cite[Lemma~1.1]{Tu83}).
-
- The second assertion can be proved similarly to~\cite[3.14]{Ka77}, (cf. also with the proof of~\cite[Lemma~4.4d]{LS17}).
-\end{proof}
-\begin{proof}[Long proof]
- Let us verify the first assertion. Let $v = \sum_r v^r$ be a decomposition as above. 
- Since each $v^r$ is orthogonal to $u$ we can write the canonical decomposition  
- $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
- \cref{lem:xsmall-properties} allows us to rewrite the right-hand side of~\ref{eq:sigma-definition} in such a way that 
-  it does not depend on the choice of decomposition for $v$:
- \begin{multline}
-  \prod\limits_r x(\delta_1^{-1} ut, \delta_1 v^rt^{-1}) = \prod\limits_{r}\prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v^r, w)t^{-1}) = \\ 
-   = \prod\limits_{i<j} x(\delta_1^{-1} ut, \delta_1 u_{ij}c_{ij}(v, w)t^{-1}). 
- \end{multline}
-
- We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
- Choose $w\in R^n$ so that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
- We can write ${}^g\left(\sigma_1\left(F(u, v)\right)\right)$ as follows:
- \begin{equation} \nonumber
-   \prod\limits_{1\leq i<j\leq n} x(\pi(g) \cdot \delta_1^{-1} \cdot t u, \pi(g)^* \cdot \delta_1 \cdot t^{-1} u_{ij}c_{ij})
-                                   = \prod\limits_{1\leq i<j\leq n} x(\delta_1^{-1} \cdot g'\cdot t u, \delta_1 \cdot {g'}^* \cdot t^{-1} u_{ij}c_{ij}).
- \end{equation} 
- Now for every factor in the right-hand side we do the following.
- If $\{i, j\} = \{h, k\}$ or $\{i, j\} \cap \{h, k\} = \emptyset$ we leave the term unchanged.
- Otherwise, if, $|\{i, j\} \cap \{h, k\}| = 1$,  say $j = h$, $i\neq k$, we further decompose it as follows:
-  \begin{equation} \nonumber
-    x(\delta_1^{-1} \cdot t u', \delta_1 \cdot {g'}^* \cdot u_{ij} (c_{ij} t^{-1})) = 
-     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ij} (c_{ij} t^{-1})) \cdot 
-     x(\delta_1^{-1} \cdot u' t, \delta_1 \cdot u'_{ki} (c_{ij} t^{-1})).
-  \end{equation}
-  Here $u' = g'  u = t_{jk}(\xi') \cdot u$.
-  Notice that ${g'}^*u_{ij} = t_{kj}(-\xi') \cdot u_{ij} = e_iu_j - e_ju_i + e_k\xi'u_i =u'_{ij}+u'_{ki}\xi'$.
-
-  Thus, we arrive at a product $\prod_{s} x(\delta_1^{-1} \cdot u't, \delta_1 \cdot v'_s t^{-1}) $, where $v'_s \in D(u')$ and
-   $\sum v'_s = {g'}^*v$. Clearly, this product equals $\sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right)$ by definition.
-\end{proof}
 

### 2018-10-04 paper.tex
Rewriting stuff

@@
 \usepackage{enumitem}
+\usepackage[notref,notcite]{showkeys}
 
@@
 We denote by $e_i$ the standard basis vector of $R^n$. For a pair of vectors $u, v \in R^n$ such that $u^tv = 0$ we denote by
-$t(u, v)$ the rank $1$ matrix $e + uv^t$. Notice that $t(u, v)$ lies in $\E(n, R)$ provided $u$ or $v$ is unimodular. %TODO: Reference
+$t(u, v)$ the rank $1$ matrix $e + uv^t$. Notice that $t(u, v)$ lies in $\E(n, R)$ provided $u$ or $v$ is unimodular. %TODO: Reference + other case
 
@@
 
+\begin{comment}
 Let $u, v \in R^n$ be such that $u^t v = 0$ and assume, moreover, that either $u$ or $v$ has at least one zero entry.
@@
 Let us recall the standard properties of $x(u, v)$ (cf.~\cite[Lemma~1.1]{Tu83}).
+
 \begin{itemize}
@@
 \end{itemize}
-\begin{comment}
+
 Now let $I$ be a splitting ideal of $R$.
@@
 
-Now assume that $I$ is an ideal of ring $R$ embedded as a subring into a larger ring $S$. 
+\begin{lemma} \label{lem:xsmall-properties}
+ Let $v, w \in R^n$ be such that $v^t w = 0$ and assume, moreover, that either $v$ or $w$ has at least one zero entry.
+ Under these assumptions one can define certain element $x(v, w) \in \St(n, R)$ such that $\phi(x(v, w)) = t(v, w) = 1 + vw^t$.
+ The elements $x(v, w)$ enjoy the following properties:
+ \begin{lemlist}
+  \item \label{item:xsmall-scalar} If $v$ or $w$ has at least two zero entries, then $x(v, wa) = x(va, w)$ for $a\in R$. 
+  \item \label{item:xsmall-additivity} If $w_1$ and $w_2$ have at least two zero entries of which at least one entry is common
+   then $x(v, w_1) \cdot x(v, w_2) = x(v, w_1+w_2)$ and $x(w_1, v) \cdot x(w_2, v) = x(w_1 + w_2, v)$.
+  \item \label{item:xsmall-commute} If $v$, $v'$ are simultaneously orthogonal to $w$ and $w'$ and the elements $w, w'$ both have at least two zero entries then 
+   $[x(v, w),\ x(v', w')] = 1$.
+  \item \label{item:xsmall-conj} If $g = x_{ij}(\xi)$ is a Steinberg generator and $v$ or $w$ has at least two zero entries then
+   $g \cdot x(v, w) \cdot g^{-1} = x(gv, g^*w)$.
+ \end{lemlist}
+\end{lemma}
+\begin{proof}
+ See~\cite[Lemma~1.1]{Tu83}.
+\end{proof}
+
+Now assume that $I$ is an ideal of a ring $R$ which itself is a subring of a larger ring $S$. 
 Let $d$ be an element of the subgroup $T(n, S)$ of diagonal matrices of $\GL(n, S)$, notice that $d^* = d^{-1}$.
@@
 
-\begin{lemma} %\label{lem:cor-conj}
+\begin{lemma} \label{lem:xy-wd}
  The elements $X_d(u, v)$, $Y_d(u, v)$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
@@
  $v^r = \sum_{i<j} u_{ij} c_{ij}(v^r, w)$, moreover, $\sum_{r} c_{ij}(v^r, w) = c_{ij}(v, w)$.
- Now from~\eqref{item:xsmall-scalar}--\eqref{item:xsmall-commute} we obtain:
+ Now using~\cref{lem:xsmall-properties} we obtain:
  \begin{multline*} \prod\limits_r x(d^{-1}u, dv^r) = \prod\limits_{r}\prod\limits_{i<j} x(d^{-1} u, du_{ij}c_{ij}(v^r, w)) =
@@
 
-\begin{lemma} Suppose that $g = x_{hk}(\xi)$ is a generator of $\St(n, R)$ such that $m = d\phi(g)d^{-1} \in \E(n, R)$, then 
+\begin{lemma} \label{lem:xy-conj} Suppose that $g = x_{hk}(\xi)$ is a generator of $\St(n, R)$ such that $m = d\phi(g)d^{-1} \in \E(n, R)$, then 
  \begin{equation*} g \cdot X_d(u, v) \cdot g^{-1} = X_d(mu, m^*v) \text{ and } g \cdot Y_d(v, u) \cdot g^{-1} = Y_d(mv, m^*u). \end{equation*}
@@
 \begin{proof}
-Similar to~\cite[3.14]{Ka77}, cf. also with the proof of~\cite[Lemma~4.4d]{LS17}.
-\begin{comment} % Do not remove
+Direct computation using~\cref{lem:xsmall-properties} (cf. with~\cite[3.14]{Ka77} or~\cite[Lemma~4.4d]{LS17}).
+\begin{comment} % ***** Do not remove *****
  Choose $w\in R^n$ such that $w^t u = 1$ and write $v = \sum_{1\leq i<j\leq n} u_{ij} c_{ij}$, where $u_{ij}$ and $c_{ij} = c_{ij}(v, w)$ are as in~\eqref{eq:canonical}. 
- By~\cite[3.12]{Ka77} we can write $g \cdot X_d(u, v) \cdot g^{-1}$ as follows:
+ By~\cref{lem:xsmall-properties} we can write $g \cdot X_d(u, v) \cdot g^{-1}$ as follows:
  \begin{equation} \nonumber
@@
 &F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
-&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, R).
+&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, R). \label{coef-move}
 \end{align}
@@
 Every map of abelian groups $\chi \in \Hom(\ZZ \Phi, R^*)$ specifies an action on the set of generators $\XX_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
-\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \alpha\in \Phi,\ \xi \in R. \end{equation}
+\begin{equation*} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \alpha\in \Phi,\ \xi \in R. \end{equation*}
 It is not hard to check that this action is compatible with Steinberg relations $\RR{\Phi, R}$ and 
@@
 
-\begin{example}
+\begin{example} \label{exm:chi-linear}
 For $1\leq k\leq \ell+1$ and $\varepsilon \in R^*$ denote by $d_k(\varepsilon)$ the matrix from $\GL(\ell+1, R)$ which differs from the unit matrix 
@@
 
-To define the map $(\sigma_1)_{N_{1,0}}$ we will invoke the presentation of the relative Steinberg group given in~\cref{sec:another-presentation}
-in the special case $R=A[t]$, $I=tA[t]$.
+To define the map $(\sigma_1)_{N_{1,0}}$ we invoke the presentation of the relative Steinberg group $\St(n, A[t], tA[t])$ given in~\cref{prop:rel-presentation}.
+%and the elements constructed in~\cref{sec:another-presentation}. in the special case $R=A[t]$, $I=tA[t]$.
 %We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
 
-Indeed, for $u \in E(n, A[t])$ and $v \in tA[t]$ define $\sigma_1$ on $N_{0}=\St(n, A[t], tA[t])$ by the following identities: 
+Denote by $\delta_1$ the matrix $d_1(t) \in \GL(A[t, t^{-1}])$ from~\cref{exm:chi-linear}.
+Now for $u \in E(n, A[t])$ and $v \in tA[t]$ we can define the map $\sigma_1$ on the generators of $N_{0}=\St(n, A[t], tA[t])$ 
+ using the elements defined in~\cref{sec:another-presentation}:
+\begin{equation*}
+ (\sigma_1)_{N_0} (F(u, v)) = X_{\delta_1 \cdot t^{-1}}(u, v),\ (\sigma_1)_{N_0} (S(v, u)) = Y_{\delta_1}(v, u).
+\end{equation*}
+
+\begin{comment}
 \begin{equation}
@@
 \end{lemma}
+\end{comment}
 
-\begin{cor}
- The map $\sigma_1$ preserves relations~\eqref{add4}--\eqref{conj3}.
-\end{cor}
+\begin{prop}
+ If $A$ is a local ring them the map $(\sigma_1)_{N_0}$ preserves relations~\eqref{add4}--\eqref{coef-move}.
+ In particular, the map $(\sigma_1)_{N_0}$ is well-defined.
+\end{prop}
 \begin{proof}
- For~\eqref{add4}--\eqref{add5} this is an immediate corollary of the first assertion of the previous lemma.
+ For~\eqref{add4}--\eqref{add5} this is an immediate corollary of~\cref{item:xsmall-additivity} and~\cref{lem:xy-wd}
  For~\eqref{conj3} this follows from the second part of the lemma applied in the special case $g = \sigma_1(F(u, v)) \in N^1$.

### 2018-10-04 paper.tex
Rewriting stuff

@@
 &F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
-&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, R). \label{coef-move}
+&F(me_1,\,m^*e_2a)=S(me_1a,\,m^*e_2),\ \text{for all}\ a\in I,\, m \in \E(n, R). \label{coef-move}
 \end{align}
@@
 
-To simplify notation, throughout this section we set $N_1 = N(\varpi_1)$, $N^1 = N(-\varpi_1)$.
+To simplify notation, throughout this section we set $N_1 = N(\varpi_1^\vee)$, $N^1 = N(-\varpi_1^\vee)$.
 We only construct one of the desired maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
@@
 
-It is easy to define the first map $(\sigma_1)_{P_1^-(A)}$, indeed, using the decomposition $P_1^-(A) \cong U^-_1 \rtimes L_1$ where 
+It is easy to define the first map $(\sigma_1)_{P_1^-(A)}$, indeed, using the decomposition $P_1^-(A) \cong U^-_1 \rtimes L_1$ where %TODO: Language???
 \[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in A \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in A\rangle \]
@@
 
-To define the map $(\sigma_1)_{N_{1,0}}$ we invoke the presentation of the relative Steinberg group $\St(n, A[t], tA[t])$ given in~\cref{prop:rel-presentation}.
-%and the elements constructed in~\cref{sec:another-presentation}. in the special case $R=A[t]$, $I=tA[t]$.
-%We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.
+%To define the map $(\sigma_1)_{N_{0}}$ we invoke the presentation of the relative Steinberg group $\St(n, A[t], tA[t])$ given in~\cref{prop:rel-presentation}.
 
 Denote by $\delta_1$ the matrix $d_1(t) \in \GL(A[t, t^{-1}])$ from~\cref{exm:chi-linear}.
-Now for $u \in E(n, A[t])$ and $v \in tA[t]$ we can define the map $\sigma_1$ on the generators of $N_{0}=\St(n, A[t], tA[t])$ 
+Now for $u \in \E(n, A[t])$ and $v \in (tA[t])^n$ we can define the map $(\sigma_1)_{N_0}$ on the generators of $N_{0}=\St(n, A[t], tA[t])$ 
  using the elements defined in~\cref{sec:another-presentation}:
@@
 \end{equation*}
-
-\begin{comment}
-\begin{equation}
- \sigma_1(F(u, v)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot t u, \delta_1 \cdot t^{-1} v_i),\ \
- \sigma_1(S(v, u)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot v_i, \delta_1 \cdot u).
-\end{equation}
-
-\begin{lemma} \label{lem:cor-conj}
- \begin{lemlist}
-   \item \label{item:correctness} The elements $\sigma_1(F(u, v))$ and $\sigma_1(S(v, u))$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
-   \item \label{item:conjugation} For any $g \in N^1$ one has 
-      \begin{equation}
-          \nonumber {}^g\left(\sigma_1(F(u, v))\right) = \sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right),\ \ 
-                    {}^g\left(\sigma_1(S(u, v))\right) = \sigma_1\left(S(g' \cdot u, {g'}^{*} \cdot v)\right),                    
-      \end{equation}
-      where $g' = {}^{\delta_1}\pi(g).$
- \end{lemlist}
-\end{lemma}
-\end{comment}
+It is clear that the above elements belong to $N^1$.
 
@@
 \begin{proof}
- For~\eqref{add4}--\eqref{add5} this is an immediate corollary of~\cref{item:xsmall-additivity} and~\cref{lem:xy-wd}
- For~\eqref{conj3} this follows from the second part of the lemma applied in the special case $g = \sigma_1(F(u, v)) \in N^1$.
-\end{proof}
+ For~\eqref{add4}--\eqref{add5} this is an immediate corollary of~\cref{item:xsmall-additivity} and~\cref{lem:xy-wd}.
+ By~\cref{lem:xy-conj} for $g \in N^1$ one has 
+ \begin{equation} \label{eq:xy-conj-n1}
+  g \cdot X_{\delta_1 t^{-1}}(u', v') \cdot g^{-1} = X_{\delta_1 t^{-1}}(mu', m^*v'), \text{ where } m = \delta_1 \cdot \phi(g) \cdot \delta_1^{-1}.
+ \end{equation}
+ To obtain that $(\sigma_1)_{N_0}$ preserves~\eqref{conj3} it remains to put $g = X_{\delta_1 t^{-1}}(u, v)$.
 
-It remains to verify that $\sigma_1$ preserves~\eqref{coinc}.
-Let us do this at first in the special case when $g^*$ belongs to the subset $G_0 = H_{12}(R) \cdot U^+_1(R) \cdot U^-_1(R)$.
-Here we denote by $H_{12}(R)$ the subgroup of $T(n, R)$ generated by semisimple root elements $ h_{12}(\xi)$, $\xi \in R^*$.
+ Let us verify that $\sigma_1$ preserves~\eqref{coef-move}, i.\,e. that for $a\in tA[t]$ and $m \in \E(n, A[t])$ one has
+ $X_{\delta_1 t^{-1}}(me_1, m^*e_2 a) = Y_{\delta_1}(me_1 a, m^* e_2)$.
+ Let us do this at first in the special case when $m^* \in \E(n, A[t])$ belongs to the subset $G_0 = H_{12}(A) \cdot U^+_1(A) \cdot U^-_1(A)$.
+ Here we denote by $H_{12}(A)$ the subgroup of $T(n, A)$ generated by semisimple root elements $ h_{12}(\xi)$, $\xi \in A^*$.
 
-Since the only nonzero components of $u = g^* \cdot e_2$ are $u_1$ and $u_2$ we can present $v = g \cdot e_1$ as a sum $v' + v''$, where 
- $v'_i=0$, $i>2$ and $v''_1=v''_2=0$.
-Since $v', v'' \in D(u)$ and $u \in D(v)$, from the definition of $\sigma_1$ we obtain that:
+ Since the only nonzero entries of $v = m^* e_2$ are $v_1$ and $v_2$ we can write $u = m e_1$ as a sum $u' + u''$, where 
+  $u'_i=0$, $i>2$ and $u''_1=v''_2=0$.
+ Since $u', u'' \in D(u)$ and $u \in D(v)$, from Lemmas~\ref{lem:xy-wd}--\ref{lem:xy-conj} we obtain that:
  \begin{multline} \label{eq:special-case}
- \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)) = x(\delta_1^{-1} \cdot v'a, \delta_1\cdot  u) \cdot x(\delta_1^{-1}\cdot v''a, \delta_1 \cdot u) = \\
-  = x(\delta_1^{-1} va, \delta_1 \cdot u) = x(\delta_1^{-1} vat^{-1}, \delta_1 \cdot ut) = \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) 
+  Y_{\delta_1}(me_1 a, m^* e_2) = x(\delta_1^{-1} \cdot u'a, \delta_1\cdot  v) \cdot x(\delta_1^{-1}\cdot u''a, \delta_1 \cdot v) = \\
+   = x(\delta_1^{-1} ua, \delta_1 \cdot v) = x(\delta_1^{-1}t \cdot u, \delta_1t^{-1} \cdot v a) = X_{\delta_1 t^{-1}}(me_1, m^*e_2 a).
 \end{multline}
 
-To obtain the assertion in the general case notice that for $R$ local the group $\E(n, R)$ admits the following decomposition:
-\[\E(n, R) = \mathrm{EP}_1(R) \cdot H_{12}(R) \cdot U^-_1(R) \cdot U^+_1(R).\]
+ To obtain the assertion in the general case notice that for $A$ local the group $\E(n, A)$ admits the following decomposition:
+ \[\E(n, A) = \mathrm{EP}_1(A) \cdot H_{12}(A) \cdot U^-_1(A) \cdot U^+_1(A).\]
  This can be either obtained as a corollary of Gauss decomposition or can be proved by a direct calculation. %TODO: Give reference
 
-Applying transpose-inverse automorphism $(-)^*$ to the above decomposition and invoking~\cref{lem:n1-decomp} we obtain that $\E(n, R[t]) = \pi(N_1) \cdot G_0$.
-Thus, every $g \in \E(n, R[t])$ can be factored as $\pi(n) \cdot h$ for some $n\in N_1$ and $h \in G_0$.
-Since $\pi(n) = {}^{\delta_1} \pi(n')$ for some $n' \in N^1$ it remains to apply~\cref{item:conjugation} and~\eqref{eq:special-case} to obtain the required assertion:
-\begin{multline} \nonumber \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) = {}^{n'}(\sigma_1(F(h \cdot e_1, h^* \cdot e_2a))) = \\
-                           = {}^{n'}(\sigma_1(S(h \cdot e_1a, h^* \cdot e_2))) = \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)). \end{multline}
+ Applying transpose-inverse automorphism $(-)^*$ to the above decomposition and invoking~\cref{lem:n1-decomp} we obtain that $\E(n, A[t]) = \phi(N_1) \cdot G_0$.
+ Thus, every $m \in \E(n, A[t])$ can be factored as $\phi(n) \cdot h$ for some $n\in N_1$ and $h \in G_0$.
+ Since $\phi(n) = \delta_1 \phi(n') \delta_1^{-1}$ for some $n' \in N^1$ it remains to apply~\eqref{eq:xy-conj-n1} and~\eqref{eq:special-case}: 
+ \begin{multline} \nonumber X_{\delta_1 t^{-1}}(me_1, m^*e_2 a) = {}^{n'}(X_{\delta_1 t^{-1}}(he_1, h^*e_2 a)) = \\
+                            = {}^{n'}(Y_{\delta_1}(he_1 a, h^*e_2)) = Y_{\delta_1}(me_1 a, m^* e_2). \end{multline} 
+\end{proof}
 

### 2018-10-10 paper.tex
Written down some formalism of Tulenbaev maps; more notation

@@
 
+\subsection{Formalism of Tulenbaev factorization theorem}
+
+\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
+\[\xymatrix{
+G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
+                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
+G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
+                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
+In addition, we require these maps to satisfy the following list of axioms:
+\begin{enumerate}
+ \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
+ \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
+ \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
+ %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
+ \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
+\end{enumerate}
+
+\end{dfn}
+We want to define a relation on the set of triples $V = G_1 \times G_2 \times G_3$.
+By definition, two triples $v = (x, y, z)$, $v'=(x', y', z')$ are said to be congruent (denoted $v \sim v'$)
+ if there exists a triple $(a, b, c) \in G_{12}\times G_{13} \times G_{23}$ such that
+\begin{align}
+ x' =& x \cdot g_1^3(b) \cdot g_1^2(a), \\ 
+ y' =& g_2^1(a)^{-1} \cdot y \cdot g_2^3(c), \\
+ z' =& g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z.
+\end{align}
+\begin{lemma} 
+ The relation $\sim$ is transitive. 
+\end{lemma}
+\begin{proof}
+\begin{equation*} x'' = x' \cdot g_1^3(b') \cdot g_1^2(a') = 
+ x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a') \end{equation*}
+\begin{equation*} y'' = g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc') \end{equation*}
+
+Using (3) for every $a \in G_{12}$, $b \in G_{13}$ one has $g_3^1(b^{g_1^2(a)}) = g_3^1(b)^{h_1 g_1^2(a)} = g_3^1(b)^{h_2g_2^1(a)}$.
+Using (4) for every $c \in G_{23}$ and $z \in G_3$ one has $z ^{h_2 g_2^3(c)} = z^{ h_3 g_3^2(c)} = g_3^2(c)^{-1} \cdot z \cdot g_3^2(c)$;
+Therefore:
+\begin{multline*}
+  z'' = g_2^3(c')^{-1} \cdot g_3^1(b')^{-h_2(y')} \cdot z' = g_2^3(c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \right)} g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z =
+  \\ = g_2^3(cc')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \right)} \cdot g_3^1(b)^{-h_2(y)} \cdot z = 
+       g_2^3(cc')^{-1} \cdot g_3^1(b \cdot b' ^ {g_1^2(a)^{-1}})^{- h_2 \left( y \right)} \cdot z.
+\end{multline*}
+\end{proof}
+
 \subsection{Factorization theorem} 
-Throughout this section $A$ denote a commutative local ring with the maximal ideal $m$.
+Throughout this section $A$ denote a commutative local ring with the maximal ideal $M$.
 $j_+\colon A[t] \to A[t, t^{-1}]$. We write $j_+^*$ instead of $\St(\Phi, j_+)$.
@@
 \begin{itemize}
- \item 
+ \item $G$ denotes the Steinberg group $\St(\Phi, A[t, t^{-1}])$;
+ \item $G^+$ denotes the Steinberg group $\St(\Phi, A[t])$;
+ \item $G_M$ denotes the relative Steinberg group $\St(\Phi, A[t, t^{-1}], M[t, t^{-1}]$;
+ \item $G^+_M$ denotes the relative Steinberg group $\St(\Phi, A[t], M[t])$;
+ \item $B$ denotes the subgroup $\StB(\Phi, A[t, t^{-1}]) \leq G$;
+ \item $U^+$ denotes the subgroup $\UU(\Phi^+, A[t])$;
+ \item $B_M$ denotes the subgroup $\UU(\Phi^+, M[t, t^{-1}]) \cdot \Sym(???) \leq G_M$
+ \item $U^+_M$ denotes the subgroup $\UU(\Phi^+, M[t])$.
 \end{itemize}
+
+\[\xymatrix{
+U^+_M \ar@{^{(}->}[rr] \ar@{^{(}->}[dd] \ar@{^{(}->}[rd] &                        & B_M \ar[dd]^(.3){i_2^3} \ar@{^{(}->}[rd]^{i^2_3} &           \\
+                                & G^+_M \ar[rr]^(.3){i^1_3} \ar^(.3){i^3_1}[dd] &                   & G_M \ar[dd] \\
+U^+ \ar@{^{(}->}[rr]^(.3){i_2^1} \ar@{^{(}->}[rd]_{i_1^2}          &                        & B \ar@{^{(}->}[rd]         &           \\
+                                & G^+ \ar[rr]              &                   & G}\]
 

### 2018-10-11 paper.tex
Written down star operation

@@
 \end{enumerate}
+\end{dfn}
+Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
+We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
+\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z)\]
 
-\end{dfn}
-We want to define a relation on the set of triples $V = G_1 \times G_2 \times G_3$.
-By definition, two triples $v = (x, y, z)$, $v'=(x', y', z')$ are said to be congruent (denoted $v \sim v'$)
- if there exists a triple $(a, b, c) \in G_{12}\times G_{13} \times G_{23}$ such that
-\begin{align}
- x' =& x \cdot g_1^3(b) \cdot g_1^2(a), \\ 
- y' =& g_2^1(a)^{-1} \cdot y \cdot g_2^3(c), \\
- z' =& g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z.
-\end{align}
-\begin{lemma} 
- The relation $\sim$ is transitive. 
+\begin{lemma} For every $v \in V$ one has 
+ \begin{equation*}(a', b', c') \star \left( (a, b, c) \star v \right) = (a \cdot a', b \cdot {b'}^{g_1^2(a)^{-1}}, c \cdot c') \star v.\end{equation*}
 \end{lemma}
 \begin{proof}
-\begin{equation*} x'' = x' \cdot g_1^3(b') \cdot g_1^2(a') = 
- x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a') \end{equation*}
-\begin{equation*} y'' = g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc') \end{equation*}
+Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$, then straightforward computation shows that:
+\begin{align*} 
+ x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a'),\\
+ y'' =& g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc'). \end{align*}
 
@@
 \begin{multline*}
-  z'' = g_2^3(c')^{-1} \cdot g_3^1(b')^{-h_2(y')} \cdot z' = g_2^3(c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \right)} g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z =
-  \\ = g_2^3(cc')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \right)} \cdot g_3^1(b)^{-h_2(y)} \cdot z = 
-       g_2^3(cc')^{-1} \cdot g_3^1(b \cdot b' ^ {g_1^2(a)^{-1}})^{- h_2 \left( y \right)} \cdot z.
+  z'' = g_2^3(c')^{-1} \cdot g_3^1(b')^{-h_2(y')} \cdot z' = \\ 
+  = g_2^3(c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \right)} g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z = \\
+  = g_2^3(c \cdot c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \right)} \cdot g_3^1(b)^{-h_2(y)} \cdot z = \\
+  = g_2^3(c \cdot c')^{-1} \cdot g_3^1(b \cdot {b'} ^ {g_1^2(a)^{-1}})^{- h_2 \left( y \right)} \cdot z. \qedhere
 \end{multline*}
 \end{proof}
+
+Now we define a relation on the set $V$.
+By definition, two elements $v$, $v'$ are declared congruent (denoted $v \sim v'$)
+ if $v' = w \star v$ for some triple $(a, b, c) \in W$. In view of thea above lemma this relation is an equivalence relation
+ and we denote the quotient set of $V$ modulo this relation by $V'$.
 

### 2018-10-11 paper.tex
Added definition of precrpssed modules

@@
 \DeclareMathOperator{\Sym}{Sym}
+\DeclareMathOperator{\Ker}{Ker}
 \newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
@@
 
+Let us recall some basic terminology pertaining to crossed modules (cf.~\cite[\S~3.3]{BHS11}).
+Let $M$ and $N$ be groups, of which $N$ acts on $M$ on the right.
+By definition, a {\it precrossed module} is a group morphism $\mu \colon M \to N$ such that $\mu(m^n) = \mu(m)^n = n^{-1} \cdot \mu(m) \cdot n$.
+A precrossed module is called a {\it crossed module} if additionally Peiffer identity is satisfied, i.\,e.
+for $m, m'\in M$ one has $m^{-1} m' m = {m'}^{\mu(m)}$.
+A morphism between (pre)crossed modules $\mu \colon M \to N$ and $\mu'\colon M \to N$ is a pair $(f, g)$ of group morphisms $f\colon M \to M'$, $g \colon N \to N'$ such that the diagram 
+\begin{equation} \xymatrix{ M \ar[r]^{\mu} \ar[d]_{f} & N \ar[d]^{g} \\ M' \ar[r]^{\mu'} & N'}\end{equation} commutes and moreover $f(m^n) = f(m)^{g(n)}$.
+
+\subsection{Factorizations of Steinberg groups}
+
+\begin{lemma}\label{lem:bruhat}
+Let $\Phi$ be any irreducible root system.
+Let $\Phi^+$, $\Phi^{+'}$ be two systems of positive roots in $\Phi$.
+ \begin{lemlist}
+\item  The Steinberg group
+$\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
+\begin{equation}\label{eq:bruhat}
+\St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
+\ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right).
+\end{equation}
+\item Assume that $uwhvl=u'w'h'v'l'$ for some $u,u'\in \UU(\Phi^{+'}, A)$, $w,w'\in W(\Phi)$,
+$h,h'\in H(\Phi,A)$, and $l,l'\in \Ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)$. Then
+$w=w'$,
+$$
+h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr),
+$$
+and
+there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
+and $b\in\UU(\Phi^+,m)$ such that
+$$
+b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}.
+$$
+ \end{lemlist}
+\end{lemma}
+
+%TODO: Formulate Gauss decomposition
+
+\begin{comment}
 \subsection{Various stuff}
@@
 We need to prove that $\sigma_i$ commute with $x_{jk}(a)$ if $j\neq i, k \neq i$.
+\end{comment}
 
@@
 We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
-\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z)\]
+\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z).\]
 
@@
 
+\begin{lemma}
+ Then the kernel of $h_3\colon G_3\to G_1$ is generated by $g_3^1(\Ker(g_1^3))$.
+\end{lemma}
+
 \subsection{Factorization theorem} 
@@
 
+\begin{comment}                                
 Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
@@
 \end{enumerate}
+\end{comment}
 

### 2018-10-12 paper.tex
Improved presentation for Lemma on star-operation

@@
 Let $M$ and $N$ be groups, of which $N$ acts on $M$ on the right.
-By definition, a {\it precrossed module} is a group morphism $\mu \colon M \to N$ such that $\mu(m^n) = \mu(m)^n = n^{-1} \cdot \mu(m) \cdot n$.
-A precrossed module is called a {\it crossed module} if additionally Peiffer identity is satisfied, i.\,e.
-for $m, m'\in M$ one has $m^{-1} m' m = {m'}^{\mu(m)}$.
-A morphism between (pre)crossed modules $\mu \colon M \to N$ and $\mu'\colon M \to N$ is a pair $(f, g)$ of group morphisms $f\colon M \to M'$, $g \colon N \to N'$ such that the diagram 
-\begin{equation} \xymatrix{ M \ar[r]^{\mu} \ar[d]_{f} & N \ar[d]^{g} \\ M' \ar[r]^{\mu'} & N'}\end{equation} commutes and moreover $f(m^n) = f(m)^{g(n)}$.
+By definition, a {\it precrossed module} is a group morphism $\mu \colon M \to N$ such that $\mu(m^n) = \mu(m)^n = n^{-1} \cdot \mu(m) \cdot n$
+ (if we let $N$ act on itself by conjugation on the right, this means precisely that $\mu$ is preserves the action of $N$).
+A precrossed module is called a {\it crossed module} if additionally Peiffer identity is satisfied, i.\,e. for $m, m_1\in M$ one has $m^{-1} m_1 m = m_1^{\mu(m)}$.
+By definition, a morphism $\nu \colon \mu \to \mu'$ of two (pre)crossed modules $\mu \colon M \to N$ and $\mu'\colon M \to N$ is a pair $\nu=(f, g)$ of group morphisms 
+ $f\colon M \to M'$, $g \colon N \to N'$ such that the diagram 
+\begin{equation} \xymatrix{ M \ar[r]^{\mu} \ar[d]_{f} & N \ar[d]^{g} \\ M' \ar[r]^{\mu'} & N'}\end{equation} 
+commutes and moreover $f(m^n) = f(m)^{g(n)}$ for all $n\in N$, $m\in $M.
 
@@
 \subsection{Formalism of Tulenbaev factorization theorem}
-
-\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
+%{\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
+Suppose we are given a commutative diagram of groups
 \[\xymatrix{
@@
                                 & G_1 \ar[rr]_{h_1}              &                   & G}\]
-In addition, we require these maps to satisfy the following list of axioms:
+such that $g_1^3$ is a precrossed module, $h_3$ is a crossed module and, moreover, that $(g_3^1, h_1) \colon g_1^3 \to h_3$ is a map of precrossed modules.
+\begin{comment}In addition, we require these maps to satisfy the following list of axioms:
 \begin{enumerate}
@@
  \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
- %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
  \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
 \end{enumerate}
-\end{dfn}
+\end{comment}
+%\end{dfn}
+
 Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
-We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
+We define an operation $\star \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
 \[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z).\]
@@
 \begin{proof}
-Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$, then straightforward computation shows that:
+Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$.
+Since $g_1^3$ is a precrossed module we immediately obtain:
 \begin{align*} 
@@
 
-Using (3) for every $a \in G_{12}$, $b \in G_{13}$ one has $g_3^1(b^{g_1^2(a)}) = g_3^1(b)^{h_1 g_1^2(a)} = g_3^1(b)^{h_2g_2^1(a)}$.
-Using (4) for every $c \in G_{23}$ and $z \in G_3$ one has $z ^{h_2 g_2^3(c)} = z^{ h_3 g_3^2(c)} = g_3^2(c)^{-1} \cdot z \cdot g_3^2(c)$;
-Therefore:
+Since $(g_3^1, h_1)$ is a map of precrossed modules, for every $a \in G_{12}$, $b \in G_{13}$ one has $g_3^1(b^{g_1^2(a)}) = g_3^1(b)^{h_1 g_1^2(a)} = g_3^1(b)^{h_2g_2^1(a)}$.
+Since $h_3$ satisfies Peiffer identity, for every $c \in G_{23}$ and $z \in G_3$ one has $z ^{h_2 g_2^3(c)} = z^{ h_3 g_3^2(c)} = g_3^2(c)^{-1} \cdot z \cdot g_3^2(c)$, hence
 \begin{multline*}

### 2018-10-12 paper.tex
Written down final implication of 4.1

@@
 \subsection{Formalism of Tulenbaev factorization theorem}
-%{\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
-Suppose we are given a commutative diagram of groups
-\[\xymatrix{
-G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
+Suppose we are given a cube-like commutative diagram of groups
+\begin{equation} \label{eq:cube} \begin{split} \xymatrix{
+G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar@{-->}[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                 & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
-G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
-                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
+G_{12} \ar@{-->}[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar@{-->}[rd]_{h_2}         &           \\
+                                & G_1 \ar[rr]_{h_1}              &                   & G} \end{split} \end{equation}
 such that $g_1^3$ is a precrossed module, $h_3$ is a crossed module and, moreover, that $(g_3^1, h_1) \colon g_1^3 \to h_3$ is a map of precrossed modules.
-\begin{comment}In addition, we require these maps to satisfy the following list of axioms:
-\begin{enumerate}
- \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
- \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
- \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
- \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
-\end{enumerate}
-\end{comment}
-%\end{dfn}
 
-Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
+Set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
 We define an operation $\star \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
@@
 \begin{align*} 
- x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a'),\\
+ x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a)^{-1}}) g_1^2(a \cdot a'),\\
  y'' =& g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc'). \end{align*}
@@
 
-Now we define a relation on the set $V$.
-By definition, two elements $v$, $v'$ are declared congruent (denoted $v \sim v'$)
- if $v' = w \star v$ for some triple $(a, b, c) \in W$. In view of thea above lemma this relation is an equivalence relation
- and we denote the quotient set of $V$ modulo this relation by $V'$.
+The above lemma allows us to define an equivalence relation on the set $V$ as follows.
+By definition, two elements $v, v' \in V$ are congruent (denoted $v \sim v'$)
+ if $v' = w \star v$ for some triple $(a, b, c) \in W$.
 
-\begin{lemma}
- Then the kernel of $h_3\colon G_3\to G_1$ is generated by $g_3^1(\Ker(g_1^3))$.
-\end{lemma}
+\begin{lemma} Suppose that the back face $(f_{12}, f_{23}, g_2^1, g_2^3)$ of~\eqref{eq:cube} is pullback.
+If for some $z\in G_3$ holds $(1, 1, 1)\sim (1, 1, z)$ then $z \in g_3^1(\Ker(g_1^3)).$ \end{lemma}
+\begin{proof} By assumption, there exists $(a, b, c)\in W$ such that
+ \[ (a, b, c) \star (1, 1, 1) = ( g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-1}) = (1,1,z). \]
+ By assumption there exists $e \in G_{123}$ such that $f_{12}(e) = a$, $f_{23}(e) = c$, hence
+ \[ 1 = g_1^3(b) \cdot g_1^2(f_{12}(e)) = g_1^3(b \cdot f_{13}(e)),\ z = g_3^2(f_{23}(e))^{-1} \cdot g_3^1(b) = g_3^1(b \cdot f_{13}(e))^{-1}. \qedhere\] \end{proof}
 

### 2018-10-12 paper.tex
Minor

@@
 The above lemma allows us to define an equivalence relation on the set $V$ as follows.
-By definition, two elements $v, v' \in V$ are congruent (denoted $v \sim v'$)
- if $v' = w \star v$ for some triple $(a, b, c) \in W$.
+We declare two elements $v, v' \in V$ congruent (denoted $v \sim v'$) if $v' = w \star v$ for some triple $(a, b, c) \in W$.
 
@@
 If for some $z\in G_3$ holds $(1, 1, 1)\sim (1, 1, z)$ then $z \in g_3^1(\Ker(g_1^3)).$ \end{lemma}
-\begin{proof} By assumption, there exists $(a, b, c)\in W$ such that
+\begin{proof} By the above definition there exists $(a, b, c)\in W$ such that
  \[ (a, b, c) \star (1, 1, 1) = ( g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-1}) = (1,1,z). \]
- By assumption there exists $e \in G_{123}$ such that $f_{12}(e) = a$, $f_{23}(e) = c$, hence
+ By lemma's assumption there exists $e \in G_{123}$ such that $f_{12}(e) = a$, $f_{23}(e) = c$, hence
  \[ 1 = g_1^3(b) \cdot g_1^2(f_{12}(e)) = g_1^3(b \cdot f_{13}(e)),\ z = g_3^2(f_{23}(e))^{-1} \cdot g_3^1(b) = g_3^1(b \cdot f_{13}(e))^{-1}. \qedhere\] \end{proof}

### 2018-10-14 paper.tex
Minor

@@
 
-It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the corresponding map of Steinberg groups by $f_*$.
+It is clear the above construction is functorial in $R$, for a ring map $f\colon R\to S$ we denote the corresponding map of Steinberg groups by $f^*$.
 
-%TODO: define Weyl elements w_{\alpha}(\varepsilon)
-Recall that for $\alpha\in\Phi$, $\varepsilon\in R^*$ the semisimple root elements $h_\alpha(\varepsilon)$ are defined as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
+For $\alpha\in\Phi$ and $\varepsilon \in R^*$ we define the elements $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_\alpha(\varepsilon)$,
+ and $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$ (recall that $h_\alpha(\varepsilon)$ are sometimes called {\it semisimple root elements}).
+%TODO: Write needed identities for w & h here
+\begin{comment} 
+ Let us recall the standard identities which hold for these elements.
+\begin{lemma} \label{lem:Mat5.2}
+ The following identities are true.
+ \begin{lemlist}
+  \item Lol
+  \item Lol2
+ \end{lemlist}
+\end{lemma}
+\end{comment}
+
 Denote by $\StW(\Phi, R)$ the subgroup of $\St(\Phi, R)$ generated by all elements
@@
 \begin{equation}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{I}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{I}} & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
 \end{equation}
@@
 \begin{lemma}\label{lem:bruhat}
-Let $\Phi$ be any irreducible root system.
-Let $\Phi^+$, $\Phi^{+'}$ be two systems of positive roots in $\Phi$.
+Let $A$ be a local ring with maximal ideal $M$ and let $\Phi^+$ be the subset of positive roots of $\Phi$.
 \begin{lemlist}
-\item  The Steinberg group
-$\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
-\begin{equation}\label{eq:bruhat}
-\St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
-\ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right).
-\end{equation}
+\item The Steinberg group $\St(\Phi,A)$ admits the following analogue of the Bruhat decomposition:
+\begin{equation}\label{eq:bruhat} \St(\Phi,A) =\bigsqcup_{w\in W(\Phi)} \left(\UU(\Phi^{+'}, A)\cdot wH(\Phi,A)\cdot\UU(\Phi^+, A) \cdot
+                                  \ker\bigl(\St(\Phi,A) \xrightarrow{\pi^*} \St(\Phi,k)\bigr)\right). \end{equation}
 \item Assume that $uwhvl=u'w'h'v'l'$ for some $u,u'\in \UU(\Phi^{+'}, A)$, $w,w'\in W(\Phi)$,
@@
 $w=w'$,
-$$
-h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr),
-$$
-and
-there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
+$$ h^{-1}h'\in \Sym(\Phi,A)\cdot\ker\bigl(H(\Phi,A) \xrightarrow{\pi^*} H(\Phi,k)\bigr), $$
+and there exist $a\in \UU(\Phi^{+'},m)$ such that $w^{-1}(u^{-1}u'a)w\in \UU(\Phi^+,R)$,
 and $b\in\UU(\Phi^+,m)$ such that
-$$
-b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}.
-$$
+$$ b=v^{-1}(u^{-1}u')^{wh}v'=l(l')^{-1}. $$
 \end{lemlist}

### 2019-01-02 dl-paper.tex
Added stub for Dl paper

\documentclass[oneside, 10pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true]{hyperref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}

\addbibresource{paper.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}

\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\theoremstyle{remark} %\newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}

\theoremstyle{definition}
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\newtheorem{rem}[lemma]{Remark}
\DeclareMathOperator{\St}{St}

\title{On the presentation of orthogonal groups over polynomial rings}
\keywords {Steinberg group, $K_2$-functor, Serre problem
 {\em Mathematical Subject Classification (2010):} 19C20}
\author {Sergey Sinchuk}
\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
\email {sinchukss at gmail.com}
\date {\today}

\begin{document}
\maketitle
\section{Introduction}
\section{Preliminaries}
\subsection{Isogenous forms of the orthogonal group}
\subsection{Grothendieck--Witt groups}
\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}
\subsection{Second injectivity theorem}

Statement \[x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]

$g = x_{-\alpha}(mX)$,

$y := x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1})$,

$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,

$\alpha = h_{ik}^{-1}(X)$.

Using $\pi(z) = 1$ we get 
\begin{multline}z = z^\alpha = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}

We need to introduce notation for certain subgroups of $\St(A[X, X^{-1}])$:
\begin{align}
 G_+   & = \mathrm{Im}(\St(\Phi, A[X], Xm[X]) \to \St(A[X, X^{-1}]))\\
 G_+^0 & = \mathrm{Im}(\St(\Phi, A[X], m[X]) \to \St(A[X, X^{-1}]))
\end{align}
Notice that for $ g\in G_+$ the element $ev_{X=0}(g)^{-1}g$ lies in $G_+^0$.
\begin{lemma} Assume that $\Phi$ is simply-laced.
 For any $a\in A$, $\alpha\in \Phi$, $g_0 \in G^0_+$ there exist $m'\in m$ and $g'\in G_+$ such that 
 \[x_{\alpha}(aX^{-1}) g_0  = g' x_\alpha(-a(1+m')X^{-1}) \cdot \{X, 1+m'\}.\]
\end{lemma}
\begin{proof}
 Choose some parabolic subset $S$ of roots in $\Phi$ in such a way that its special part $\Sigma(S)$ does not contain the root $\alpha$.
 In view of~\cref{lem:Zgen} the subgroup $G_+^0$ is generated by images in $\St(\Phi, A[X, X^{-1}]$ of the elements of the set $\mathcal{Z}(\Sigma(S), A[X], Xm[X])$.

 Without loss of generality we may assume that $g_0$ is either $z_\beta(s, \xi)$ for some $\beta\in \Sigma(S)$ for some $s\in Xm[X]$, $\xi\in A[X]$ or $x_\gamma(s)$ for some $\gamma \in \Phi$.
 \begin{itemize}
  \item {\it Case $\alpha \perp \beta$. } In this case the required statement is obvious (with $m'=0$, $g'=g_0$).
  \item {\it Case $\alpha \not \perp \beta \in \Phi$.} In this case either $\alpha + \beta$ or $\alpha - \beta$ lies in $\Phi$.
  Assume, for example, the former (the argument in the other case is similar).
  The required assertion now follows from the following equality (cf. Sinchuk 16' paper Lemma 9):
  %\[ x_\beta(-aX^{-1}) z_\alpha(s, \xi) x_\beta(aX^{-1}) = x_\beta(-saX^{-1}\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta}saX^{-1})\cdot z_\alpha(s, \xi).\]
  \[ x_\alpha(-aX^{-1}) z_\beta(s, \xi) =  \left( z_\beta(s, \xi) \cdot x_{\alpha+\beta}(N_{\beta,\alpha}saX^{-1}) \cdot x_\alpha(-s\xi aX^{-1}) \right) \cdot x_\alpha(-aX^{-1}).\]
  \item {\it Case $\alpha = \beta$}
  \item {\it Case $\alpha = -\beta$}
 \end{itemize}

\end{proof}

\section{Proof of Rehmann's presentation theorem}

\printbibliography
\end{document}

### 2019-01-07 dl-paper.tex
Fixed notation for symbols

@@
 
-Statement \[x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
+$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
+Our convention for Cartan matrices is 
+$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
 
-$g = x_{-\alpha}(mX)$,
+Then Matsumoto's Lemmas~5.2 and 5.4 assert that:
+\[ {}^{h_\alpha(t)}\!x_\beta(u) = x_\beta(t^{\langle \beta,  \alpha \rangle}u)\]
+\[ {}^{h_\alpha(t)}\!h_\beta(u) = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}. \]
+\[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}\]
 
-$y := x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1})$,
+Definition of Steinberg symbol is:
+\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1} \]
+
+Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book)
+\[ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}. \]
+
+Statement \[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
+
+$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$,
 
@@
 
-$\alpha = h_{ik}^{-1}(X)$.
-
 Using $\pi(z) = 1$ we get 
-\begin{multline}z = z^\alpha = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
+\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
 

### 2019-01-07 dl-paper.tex
Added computation with symbols

@@
 \section{Preliminaries}
+$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
+Our convention for Cartan matrices is 
+$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
+
+\subsection{Steinberg groups}
+Definition of Steinberg symbol is:
+\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1} \]
+
+Then Matsumoto's Lemmas~5.2 and 5.4 assert that:
+\[ {}^{h_\alpha(t)}\!x_\beta(u) = x_\beta(t^{\langle \beta,  \alpha \rangle}u)\]
+\[ {}^{h_\alpha(t)}\!h_\beta(u) = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}. \]
+\[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}\]
+
+Suppose for a moment that $\langle \alpha, \beta \rangle = -1$ and  $\langle \beta, \alpha \rangle = -1$ then
+\[ \{s, t^{-1} \} = \{s,  t^{-1}\}_\alpha = \{t, s^{-1} \}_\beta^{-1} = \{s^{-1}, t\} \]
+In particular, $\{s, s^{-1}\} = \{s, s^{-1}\}^{-1}$
+
 \subsection{Isogenous forms of the orthogonal group}
@@
 
-$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
-Our convention for Cartan matrices is 
-$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
+Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book).
+\[ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}, \]
+where $r, s$ are arbitrary elements of $R$ such that $1 - rs\in R^*$ then
 
-Then Matsumoto's Lemmas~5.2 and 5.4 assert that:
-\[ {}^{h_\alpha(t)}\!x_\beta(u) = x_\beta(t^{\langle \beta,  \alpha \rangle}u)\]
-\[ {}^{h_\alpha(t)}\!h_\beta(u) = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}. \]
-\[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}\]
-
-Definition of Steinberg symbol is:
-\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1} \]
-
-Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book)
-\[ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}. \]
-
-Statement \[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
-
+\begin{comment}
+\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
 $y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
-
 $z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
-
 Using $\pi(z) = 1$ we get 
 \begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
+\end{comment}
+
+For any $\alpha \in \Phi$ one can find $\beta$ such that $\langle \alpha, \beta \rangle = -1$
+(except for the case when $\alpha$ is a long root of a symplectic root system).
+Choose $\beta$ such that $\langle \alpha, \beta \rangle = -1$
+\begin{multline}
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \beta \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \beta \rangle}m) 
+ = {}^{h_\beta(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
+ = {}^{h_\beta(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
+ x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}
+\end{multline}
 

### 2019-01-08 dl-paper.tex
Added more formulas

@@
 \newtheorem{lemma}{Lemma}
-\theoremstyle{remark} %\newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
+\theoremstyle{remark}
 
@@
 
+\begin{comment}
 Suppose for a moment that $\langle \alpha, \beta \rangle = -1$ and  $\langle \beta, \alpha \rangle = -1$ then
@@
 In particular, $\{s, s^{-1}\} = \{s, s^{-1}\}^{-1}$ 
+\end{comment}
 
@@
 Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book).
-\[ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}, \]
+\begin{equation} \label{eq:dennis-stein}
+ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1},
+\end{equation} 
 where $r, s$ are arbitrary elements of $R$ such that $1 - rs\in R^*$ then
@@
 
-For any $\alpha \in \Phi$ one can find $\beta$ such that $\langle \alpha, \beta \rangle = -1$
-(except for the case when $\alpha$ is a long root of a symplectic root system).
-Choose $\beta$ such that $\langle \alpha, \beta \rangle = -1$
-\begin{multline}
- x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \beta \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \beta \rangle}m) 
- = {}^{h_\beta(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
- = {}^{h_\beta(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
- x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}
-\end{multline}
-
 We need to introduce notation for certain subgroups of $\St(A[X, X^{-1}])$:
 \begin{align}
- G_+   & = \mathrm{Im}(\St(\Phi, A[X], Xm[X]) \to \St(A[X, X^{-1}]))\\
- G_+^0 & = \mathrm{Im}(\St(\Phi, A[X], m[X]) \to \St(A[X, X^{-1}]))
+ G_+^0 & = \mathrm{Im}(\St(\Phi, A[X], XM[X]) \to \St(A[X, X^{-1}]))\\
+ G_+   & = \mathrm{Im}(\St(\Phi, A[X], M[X]) \to \St(A[X, X^{-1}]))
 \end{align}
 Notice that for $ g\in G_+$ the element $ev_{X=0}(g)^{-1}g$ lies in $G_+^0$.
+
+\begin{rem} Our goal is to rewrite $x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X))$, where $f_1(X) \in M[X]$, $f_2(X) \in A[X]$ as
+ $g \cdot x_\alpha(\frac{aX^{-1}}{1+am}) \cdot \{ 1 + am, X \}$ for some $g \in G_+$
+ and $m \in M$. At first assume that $\Phi$ is simply-laced. \end{rem}
+\begin{enumerate}
+ \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.} (Is this the same thing as $\alpha \perp \beta$?)
+  Obviously, in this case $g = z_\beta(f_1(X), f_2(X))$, $m=0$.
+ \begin{comment} 
+ \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
+ \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
+ \end{comment}
+ \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
+ Start from this formula (centrality of $K_2$-paper):
+ \begin{multline}
+ x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
+ \end{multline}
+ \item {\it Case $\beta - \alpha \in \Phi$, $f_1(X) = Xf_1'(X)$.}
+ \begin{multline}
+  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1});
+ \end{multline}
+ \item {\it Case $\beta = -\alpha$, $f_1(X) = mX$, $f_2(X)=0$}. %CASE 1
+For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
+(except in the sole case when $\alpha$ is a long root of a symplectic root system).
+Now direct computation using~\eqref{eq:dennis-stein} and centrality of symbols shows that:
+\begin{multline}
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
+ = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
+ = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
+ x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
+\end{multline}
+ \item Essentially this allows one to cover the case $\beta = -\alpha$, $f_1(X) = Xm$ (with the same answer)
+\end{enumerate}
+
 \begin{lemma} Assume that $\Phi$ is simply-laced.

### 2019-01-08 dl-paper.tex
One more case covered

@@
  \end{multline}
- \item {\it Case $\beta - \alpha \in \Phi$, $f_1(X) = Xf_1'(X)$.}
+ \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
  \begin{multline}
@@
  \end{multline}
- \item {\it Case $\beta = -\alpha$, $f_1(X) = mX$, $f_2(X)=0$}. %CASE 1
-For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
+\item {\it Case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$}.
+Suffices to prove the assertion under the assumption $f_2(X)=0$.
+First consider the case $f_1(X) = mX$, where $m\in M$. For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
 (except in the sole case when $\alpha$ is a long root of a symplectic root system).
@@
 \end{multline}
- \item Essentially this allows one to cover the case $\beta = -\alpha$, $f_1(X) = Xm$ (with the same answer)
+
+Now suppose $f_1(X) = X^2f_1'(X)$. Choose $\gamma$ such that $\alpha + \gamma \in \Phi$.
+Then everything we need follows from the computation:
+\begin{multline*}
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X^2 mf_1'(X)) \cdot x_\alpha(-aX^{-1}) = 
+ {}^{x_\alpha(aX^{-1})}[x_{-\alpha - \gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)), x_{\gamma}(X)] = \\
+ = [x_{-\alpha-\gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)) x_{-\gamma}(N_{-\alpha-\gamma, \gamma} N_{-\alpha-\gamma, \alpha} af_1'(X)), x_\gamma(X) x_{\alpha+\gamma}(N_{\alpha,\gamma}a)].
+\end{multline*} 
 \end{enumerate}

### 2019-01-09 dl-paper.tex
More items in references section; cleanup proof of Lemma 3.4

@@
 
-\newtheorem{proposition}{Proposition}
+\newtheorem{prop}{Proposition}
 \newtheorem{theorem}{Theorem}
@@
 \DeclareMathOperator{\St}{St}
+\DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\colim}{colim}
+\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
+\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
+\newcommand{\rA}{\mathsf{A}}
+\newcommand{\rB}{\mathsf{B}}
+\newcommand{\rC}{\mathsf{C}}
+\newcommand{\rD}{\mathsf{D}}
+\newcommand{\rE}{\mathsf{E}}
+\newcommand{\rF}{\mathsf{F}}
+\newcommand{\rG}{\mathsf{G}}
+
+\numberwithin{equation}{section}
 
@@
 \section{Introduction}
+
 \section{Preliminaries}
@@
 \subsection{Steinberg groups}
-Definition of Steinberg symbol is:
-\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1} \]
+Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
+Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(\xi)$ where $\xi\in R, \alpha\in\Phi$ and relations:
+\begin{align}
+& \phantom{[}
+x_\alpha(s) x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
+& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
+ x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
+\end{align}
+The indices $i$, $j$ appearing in the right-hand side of the above relation range over
+all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
+The structure constants $N_{\alpha \beta i j}=\pm 1,2,3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and can be computed explicitly.
 
-Then Matsumoto's Lemmas~5.2 and 5.4 assert that:
-\[ {}^{h_\alpha(t)}\!x_\beta(u) = x_\beta(t^{\langle \beta,  \alpha \rangle}u)\]
-\[ {}^{h_\alpha(t)}\!h_\beta(u) = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}. \]
-\[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}\]
+Recall that for $\alpha\in\Phi$ and $s \in R^*$ the semisimple root elements $h_\alpha(s)$ are defined as follows: \[h_\alpha(s)=w_\alpha(s) \cdot w_\alpha(-1), \text{ where } w_\alpha(s) = x_\alpha(s) \cdot x_{-\alpha}(-s^{-1}) \cdot x_\alpha(s).\]
+
+Recall from~\cite[Lemma~5.2]{Ma69} that the following identities hold for these elements:
+ \begin{align} 
+   \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u) \\
+   \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}.
+ \end{align}
+
+In our computations we will use two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
+\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \]
+
+Recall also that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 - rs \in R^*$ as follows:
+\begin{equation} \label{eq:dennis-stein}
+ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}.
+\end{equation}
+
+%Using~\eqref{eq:conj-h-h} it is easy to verify that \[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}.\] 
+It is easy to show that the above symbols depend only on the length of $\alpha$.
+Moreover, if $\Phi$ is nonsymplectic, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e.
+\begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}.
+\end{equation}
+
+\subsection{Relative Steinberg groups}
+% Generation of relative Steinberg groups
+
+The following result was proved in \cite[Proposition~3.2]{Ste13}.
+\begin{lemma}\label{lem:Zgen} Let $\Phi$ be an irreducible root system of rank $\geq 2$. 
+Let $G$ denote the normal closure in $\St(\Phi, R)$ of the subgroup spanned by elementary root unipotents of level $I$, i.\,e.
+$G=\langle x_\alpha(s) \mid \alpha\in\Phi,\ s\in I\rangle^{\St(\Phi, R)}$.
+
+Let $S$ be a parabolic set of roots of $\Phi$ with special part $\Sigma_S$.
+Then $G$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S, I, R)$ consisting of the following two families of elements:
+\begin{itemize}
+ \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+ \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
+\end{itemize}        
+\end{lemma}
 
@@
 \subsection{Second injectivity theorem}
-
-Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book).
-\begin{equation} \label{eq:dennis-stein}
- \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1},
-\end{equation} 
-where $r, s$ are arbitrary elements of $R$ such that $1 - rs\in R^*$ then
 
@@
  and $m \in M$. At first assume that $\Phi$ is simply-laced. \end{rem}
+
+\begin{lemma} \label{lem:lem34} Assume that $\Phi$ is simply-laced and of rank $\geq 2$.
+ For any $a\in A$, $\alpha\in \Phi$, $g \in G^0_+$ there exists $m = m(g)\in M$ and $g'\in G_+$ such that 
+ \[x_{\alpha}(aX^{-1}) g  = g' Y_\alpha(a,m) \text{ where } Y_\alpha(a,m) = x_\alpha(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\}.\]
+\end{lemma}
+\begin{proof}
+ We can choose some parabolic subset $S$ of roots in $\Phi$ in such a way that its special part $\Sigma_S$ does not contain the root $\alpha$.
+ By~\cref{lem:Zgen} the subgroup $G_+^0$ is generated by images in $\St(\Phi, A[X, X^{-1}]$ of the elements of the set $\mathcal{Z}(\Sigma_S, A[X], XM[X])$.
+ Thus, we can write $g_0$ as a product of elements $z_\beta(f_1(X), f_2(X))$ such that $f_1(X) \in XM[X]$, $f_2(X) \in A[X]$ and, moreover, $f_2(X) = 0$ whenever $\beta \not \in \Sigma_S$.
+
+ It is easy to verify using~\eqref{eq:symbol-properties} that \[x_\alpha(aX^{-1}) \cdot g_0 \cdot g_1 = g_0' \cdot Y_\alpha(a, m(g_0)) \cdot g_1 = g_0' \cdot g_1' \cdot Y_\alpha(a, m(g_0)+m(g_1)),\] therefore it suffices demonstrate the assertion of the lemma in the special case $g = z_\beta(f_1(X), f_2(X))$.
+
+ We proceed by case analysis. Let us first analyze the cases when $\beta \neq -\alpha$. In all these cases $m(g) = 0$.
  \begin{enumerate}
- \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.} (Is this the same thing as $\alpha \perp \beta$?)
-  Obviously, in this case $g = z_\beta(f_1(X), f_2(X))$, $m=0$.
+ \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.}  Obviously, in this case also $g' = g$.
  \begin{comment} 
@@
  \end{comment}
+ \item {\it Case $\alpha = \beta$.} By our choice of $S$ holds $\beta \not \in \Sigma_S$, therefore $f_2(X) = 0$ and $g$ commutes with $x_\alpha(aX^{-1})$.
  \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
- Start from this formula (centrality of $K_2$-paper):
- \begin{multline}
+ Direct computation using formula from~\cite[Lemma~9]{S15} shows that:
+ \begin{multline*}
  x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
- \end{multline}
- \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
- \begin{multline}
-  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1});
- \end{multline}
-\item {\it Case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$}.
-Suffices to prove the assertion under the assumption $f_2(X)=0$.
-First consider the case $f_1(X) = mX$, where $m\in M$. For any $\alpha \in \Phi$ one can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$
-(except in the sole case when $\alpha$ is a long root of a symplectic root system).
-Now direct computation using~\eqref{eq:dennis-stein} and centrality of symbols shows that:
-\begin{multline}
+ \end{multline*}
+ \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.} Similarly to the above case:
+ \begin{multline*}
+  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1}).
+ \end{multline*} \end{enumerate}
+Now we turn to the case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$.
+Since $g$ commutes with $x_\alpha(\pm f_2(X))$, it suffices to prove the assertion in the special case $f_2(X)=0$.
+First consider the case $f_1(X) = mX$, where $m\in M$. Since $\Phi$ is nonsymplectic, we can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
+Now direct computation invoking~\eqref{eq:conj-h-h}--\eqref{eq:dennis-stein} and the centrality of symbols shows that:
+\begin{multline*}
  x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
@@
  = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
-\end{multline}
+\end{multline*}
 
@@
 \end{multline*} 
-\end{enumerate}
-
-\begin{lemma} Assume that $\Phi$ is simply-laced.
- For any $a\in A$, $\alpha\in \Phi$, $g_0 \in G^0_+$ there exist $m'\in m$ and $g'\in G_+$ such that 
- \[x_{\alpha}(aX^{-1}) g_0  = g' x_\alpha(-a(1+m')X^{-1}) \cdot \{X, 1+m'\}.\]
-\end{lemma}
-\begin{proof}
- Choose some parabolic subset $S$ of roots in $\Phi$ in such a way that its special part $\Sigma(S)$ does not contain the root $\alpha$.
- In view of~\cref{lem:Zgen} the subgroup $G_+^0$ is generated by images in $\St(\Phi, A[X, X^{-1}]$ of the elements of the set $\mathcal{Z}(\Sigma(S), A[X], Xm[X])$.
-
- Without loss of generality we may assume that $g_0$ is either $z_\beta(s, \xi)$ for some $\beta\in \Sigma(S)$ for some $s\in Xm[X]$, $\xi\in A[X]$ or $x_\gamma(s)$ for some $\gamma \in \Phi$.
- \begin{itemize}
-  \item {\it Case $\alpha \perp \beta$. } In this case the required statement is obvious (with $m'=0$, $g'=g_0$).
-  \item {\it Case $\alpha \not \perp \beta \in \Phi$.} In this case either $\alpha + \beta$ or $\alpha - \beta$ lies in $\Phi$.
-  Assume, for example, the former (the argument in the other case is similar).
-  The required assertion now follows from the following equality (cf. Sinchuk 16' paper Lemma 9):
-  %\[ x_\beta(-aX^{-1}) z_\alpha(s, \xi) x_\beta(aX^{-1}) = x_\beta(-saX^{-1}\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta}saX^{-1})\cdot z_\alpha(s, \xi).\]
-  \[ x_\alpha(-aX^{-1}) z_\beta(s, \xi) =  \left( z_\beta(s, \xi) \cdot x_{\alpha+\beta}(N_{\beta,\alpha}saX^{-1}) \cdot x_\alpha(-s\xi aX^{-1}) \right) \cdot x_\alpha(-aX^{-1}).\]
-  \item {\it Case $\alpha = \beta$}
-  \item {\it Case $\alpha = -\beta$}
- \end{itemize}
-
 \end{proof}
 
-\section{Proof of Rehmann's presentation theorem}
+\begin{rem}
+ From the proof of the above lemma it is easy to describe the way to compute... 
+\end{rem}
+
+\include{rehmann}
 

### 2019-01-13 dl-paper.tex
Added Lemma

@@
 \DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\GW}{GW}
 \DeclareMathOperator{\colim}{colim}
@@
 \subsection{First injectivity theorem}
+For a commutative ring $A$ with an ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
+It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
+\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$.
+Consider the following commutative square of canonical maps.
+\[ \xymatrix{
+    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]_\mu & \St(\Phi, R)
+   } \]
+Then there exists an arrow $\mu$ which makes the diagram commute.   
+\end{lemma} 
+\begin{proof}
+ Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
+  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
+ Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
+
+ Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
+  (cf.~\cite[\S~4]{LS17} for more details).
+ %TODO: Also give reference on a similar result of Lavrenov
+ %TODO: Rethink the proof of amalgamation theorem...
+\end{proof}
+
+\begin{lemma}
+ For a field $F$ and $\ell \geq 5$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
+\end{lemma}
+\begin{proof}
+ We have defined $\K_3(\rD_\ell, R)$ as 
+\end{proof}
+
 \subsection{Second injectivity theorem}

### 2019-01-15 dl-paper.tex
Added couple of lemmas

@@
 \DeclareMathOperator{\St}{St}
+\DeclareMathOperator{\G}{G}
+\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\HH}{H}
 \DeclareMathOperator{\K}{K}
@@
 \newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
+
+\newcommand{\ZZ}{\mathbb{Z}}
 \newcommand{\rA}{\mathsf{A}}
@@
 % Generation of relative Steinberg groups
+Let us briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups.
+We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
+%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).
+
+Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
+\begin{equation}\label{eq:relative-St}
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
+\end{equation}
+It is not hard to show that $C(\Phi, R, I) = 0$ in the case when $I$ is a splitting ideal of $R$, i.\,e.
+when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
+In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left.
+Thus we need to work with unstable $\K_3$-functors for which we choose the definition a la Quillen (cf.~\cite{Pa89})
+
+\begin{df} Suppose that $\St(\Phi, R)$ is perfect and super-perfect (i.\,e.
+the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$.) Denote by $X$ the result of application of Quillen's $+$-construction to the discrete classifying space $B\G(\Phi, R)$ with respect to the elementary subgroup $\E(\Phi, R)$.
+Now define $\K_3(\Phi, R)$ as the third homotopy group $\pi_3(X)$.
+\end{df}
+%TODO: Give reference on the definition of the plus-construction?
+
+\begin{prop} The group $\K_3(\Phi, R)$ is isomorphic to $\HH_3(\St(\Phi, R), \ZZ)$.
+In particular, it does not depend on the isogeny form of $\G(\Phi, R)$ used to define it.
+Moreover, for a ring epimorphism $R \to R/I$ there is a functorial exact sequence
+\[ \xymatrix{\K_3(\Phi, R) \ar[r] & \K_3(\Phi, R/I) \ar@{->>}[r] & C(\Phi, R, I).} \]
+\end{prop}
+
+\begin{lemma} \label{lem:Panin-stability}
+ Let $R$ be either a field, principal ideal domain or a Dedekind domain. 
+ Then the canonical map $\K_3(\rD_\ell, R) \to \K_3(\rD_\infty, R)$ is an epimorphism for $\ell \geq 6$ 
+ and an isomorphism for $\ell \geq 7$.
+\end{lemma}
+\begin{proof}
+ Stabilization for orthogonal and symplectic K-groups a la Quillen is given by Panin's theorem, see~\cite[Theorem~9.4]{Pa89}.
+More specifically the bounds for surjective (resp.
+injective) stability is
+ $\ell \geq \max(6, a+2)$ (resp. $\ell \geq \max(7,a+3)$) for $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively.
+\end{proof}
 
@@
 \begin{lemma}
- For a field $F$ and $\ell \geq 5$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
+ Let $F$ be a field of characteristic $\neq 2$. Then for $\ell \geq 7$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
 \end{lemma}
@@
 \subsection{Second injectivity theorem}
-
 \begin{comment}

### 2019-01-15 dl-paper.tex
Minor

@@
 \newtheorem{rem}[lemma]{Remark}
+\newtheorem{cond}[lemma]{Condition}
 \DeclareMathOperator{\St}{St}
@@
 \subsection{Relative Steinberg groups}
-% Generation of relative Steinberg groups
-Let us briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups.
+
+The aim of this section is to briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups.
 We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
@@
 
-Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
+...
+
+%Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
 \begin{equation}\label{eq:relative-St}
@@
 \end{equation}
-It is not hard to show that $C(\Phi, R, I) = 0$ in the case when $I$ is a splitting ideal of $R$, i.\,e.
-when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
+It is not hard to show that $C(\Phi, R, I) = 0$ in the special case when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
+
+Unstable relative Steinberg groups share many good properties with their stable counterparts studied in~\cite{Lo78} provided the following assumptions on $\Phi$ hold: \begin{enumerate}
+ \item $\St(\Phi, R)$ is perfect and super-perfect for all commutative $R$ (i.\,e. the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$).
+ \item for all commutative rings $R$ the group $\K_2(\Phi, R)$ is central in $\St(\Phi, R)$.
+\end{enumerate}
+For example, under these assumptions it can be shown that the map $\St(\Phi, R, I) \to \St(\Phi, R)$ is a universal relative central extension of a pair $(\St(\Phi, R/I), \St(\Phi, R))$ in the sense of~\cite{Lo78} (the proof is identical to~\cite[Corollary~3]{S15}).
+
 In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left.
-Thus we need to work with unstable $\K_3$-functors for which we choose the definition a la Quillen (cf.~\cite{Pa89})
-
-\begin{df} Suppose that $\St(\Phi, R)$ is perfect and super-perfect (i.\,e.
-the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$.) Denote by $X$ the result of application of Quillen's $+$-construction to the discrete classifying space $B\G(\Phi, R)$ with respect to the elementary subgroup $\E(\Phi, R)$.
-Now define $\K_3(\Phi, R)$ as the third homotopy group $\pi_3(X)$.
+Thus we need to work with unstable $\K_3$-functors a la Quillen (cf.~\cite{Pa89}).
+\begin{df}  
+Denote by $X$ the topological space obtained from the (discrete) classifying space $B\G(\Phi, R)$ by means of Quillen's $+$-construction with respect to the elementary subgroup $\E(\Phi, R)$ (which is perfect thanks to the first assumption).
+Now set $\K_3(\Phi, R) = \pi_3(X)$.
 \end{df}
@@
 \end{prop}
+\begin{proof}
+ %TODO: First part.
+
+ By~\cite[Th{\'e}or{\`e}me~2]{Lo78} the relative homology group $\HH_3(\St(\Phi, R/I), \St(\Phi, R), \ZZ)$ can be identified with the kernel $C(\Phi, R, I)$ of the relative central extension $\St(\Phi, R, I) \to \St(\Phi, R)$.
+\end{proof}
 

### 2019-01-16 dl-paper.tex
Couple more of lemmas added

@@
 
-The aim of this section is to briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups.
+The aim of this section is to briefly remind the reader definitions of relative Steinberg groups and their basic properties.
 We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
@@
 
-\subsection{Isogenous forms of the orthogonal group}
-\subsection{Grothendieck--Witt groups}
+%\subsection{Isogenous forms of the orthogonal group}
+\subsection{Hermitian K-theory and higher Grothendieck--Witt groups}
+In this section we collect some facts pertaining to Hermitian K-theory that will be of relevance to us. We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for a more detailed introduction.
+
+First of all, recall that in~\cite{Ka80} M.~Karoubi defines higher Grothendieck--Witt groups via Quillen's plus-construction:
+
+Schlichting gave a more general definition which still agrees with the classical one in the affine case.
+In particular one has:
+\begin{equation}
+ \GW_i^{[k]}(R) = \begin{array}{cl} \mathrm{KO}_i(R), & k = 0, \\ U_i(R), & k = 1, \\ \mathrm{KSp}_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}
+\end{equation}
+
+\begin{lemma}\label{lem:bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ one has
+ \[ \GW_i^{[k]}(R[X, X^{-1}]) \cong \GW_i^{[k]}(R) \oplus \GW_{i-1}^{[k-1]}(R). \] \end{lemma}
+\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+
+\begin{lemma}\label{lem:summary} Suppose that $F$ is a field of characteristic $\neq 2$, then
+$\GW_2^{[3]}(F) = 0$. \end{lemma}
+\begin{proof} See~\cite[Lemma~2.2]{FRS12}. \end{proof}
+
 \section{Proof of the main result}
@@
 \subsection{First injectivity theorem}
-For a commutative ring $A$ with an ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
+For a commutative local ring $A$ with the maximal ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
 It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
@@
 
+The following lemma summarizes facts about $\K_2(\Phi, -)$ in the field case.
 \begin{lemma}
@@
 \end{proof}
+
+\begin{theorem} Suppose $A$ is a local ring of characteristic $\neq 2$, then for $\ell \geq 7$
+  the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
+\end{theorem}
+\begin{proof}
+
+\end{proof}
+
+\begin{equation*} \xymatrix{
+ C(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[r] \ar[d] & \St(\Phi, k[t]) \ar[d] \\
+ C(\Phi, R, I) \ar[r]        & \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]& \St(\Phi, R) \ar[r]        & \St(\Phi, k[t, t^{-1}])
+}\end{equation*}
 
@@
 
-\include{rehmann}
+%\include{rehmann}
 

### 2019-01-16 dl-paper.tex
More text added

@@
 \newtheorem{cond}[lemma]{Condition}
+\DeclareMathOperator{\Ker}{Ker}
 \DeclareMathOperator{\St}{St}
@@
 %TODO: Define the category of pairs (so that all constructions below become functorial wrt it).
-
 ...
@@
 
-\begin{prop} The group $\K_3(\Phi, R)$ is isomorphic to $\HH_3(\St(\Phi, R), \ZZ)$.
+\begin{prop}\label{characterization} The group $\K_3(\Phi, R)$ is isomorphic to $\HH_3(\St(\Phi, R), \ZZ)$.
 In particular, it does not depend on the isogeny form of $\G(\Phi, R)$ used to define it.
@@
 \subsection{First injectivity theorem}
-For a commutative local ring $A$ with the maximal ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
+For a commutative local ring $A$ with the maximal ideal $M$ and residue field $k$
+we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
 It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
@@
     \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]_\mu & \St(\Phi, R)
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R)
    } \]
-Then there exists an arrow $\mu$ which makes the diagram commute.   
+Then there exists a diagonal arrow which makes the diagram commute.   
 \end{lemma} 
@@
 The following lemma summarizes facts about $\K_2(\Phi, -)$ in the field case.
-\begin{lemma}
- Let $F$ be a field of characteristic $\neq 2$. Then for $\ell \geq 7$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
+\begin{lemma} \label{lem:field-case}
+ Under certain assumptions the map $\St(\Phi, k[t]) \to \St(\Phi, k[t, t^{-1}])$ is injective.
 \end{lemma}
 \begin{proof}
- We have defined $\K_3(\rD_\ell, R)$ as 
+ %TODO: Add references on Rehmann and Hurrelbrink...
+\end{proof}
+
+\begin{prop}
+ Suppose that the canonical map $C(\Phi, B, I) \to C(\Phi, R, I)$ is surjective,
+  and that Tulenbaev lifting property holds for $\St(\Phi, R)$. 
+ Then the canonical map of Steinberg groups $\St(\Phi, B) \to \St(\Phi, R)$ is injective.
+\end{prop}
+\begin{proof}
+ Consider the following commutative diagram with exact rows: 
+\begin{equation*} \xymatrix{
+ C(\Phi, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\Phi, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
+ \St(\Phi, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\Phi, k[X]) \ar[d]_{i} \\
+ C(\Phi, R, I) \ar[r]^{j_R}         & \St(\Phi, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
+ \St(\Phi, R) \ar[r]^{\pi_R}        & \St(\Phi, k[X, X^{-1}]).
+}\end{equation*}
+Let $a$ be an element of $\Ker(h)$.
+Since $i$ is injective by~\cref{lem:field-case}, the element $a$ also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\Phi, B, I)$ via $\mu_B$.
+Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\Phi, R, I)$ such that $j_R(c) = g(b)$.
+By our assumption, $f$ is surjective, therefore
+ $c = f(d)$ for some $d \in C(\Phi, R, I)$ and we obtain the required assertion:
+ \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
+
 \end{proof}
@@
 \begin{proof}
-
+ In view of the above proposition and~\cref{lem:lemma32} we are left to verify that the map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective.
+Consider the following commutative diagram, whose rows are given by \cref{characterization}:
+ \begin{equation*}\xymatrix{
+  \K_3(\rD_\ell, B) \ar[r] \ar[d] & \K_3(\rD_\ell, k[X]) \ar[d] \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
+  \K_3(\rD_\ell, R) \ar[r]        & \K_3(\rD_\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
+ From~\cref{lem:bass-ft,lem:summary} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
+ In view of~\cref{lem:Panin-stability} the central vertical map is isomorphic to the canonical map
+ $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$ and therefore is surjective. The requred surjectivity of $f$ now follows.
 \end{proof}
-
-\begin{equation*} \xymatrix{
- C(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[r] \ar[d] & \St(\Phi, k[t]) \ar[d] \\
- C(\Phi, R, I) \ar[r]        & \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]& \St(\Phi, R) \ar[r]        & \St(\Phi, k[t, t^{-1}])
-}\end{equation*}
 

### 2019-01-23 dl-paper.tex
Proved injectivity lemma

@@
 \begin{equation}
- \GW_i^{[k]}(R) = \begin{array}{cl} \mathrm{KO}_i(R), & k = 0, \\ U_i(R), & k = 1, \\ \mathrm{KSp}_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}
+ \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \mathrm{KO}_i(R), & k = 0, \\ U_i(R), & k = 1, \\ \mathrm{KSp}_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
 \end{equation}
 
-\begin{lemma}\label{lem:bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ one has
+\begin{lemma}\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ one has
  \[ \GW_i^{[k]}(R[X, X^{-1}]) \cong \GW_i^{[k]}(R) \oplus \GW_{i-1}^{[k-1]}(R). \] \end{lemma}
@@
 
-The following lemma summarizes facts about $\K_2(\Phi, -)$ in the field case.
-\begin{lemma} \label{lem:field-case}
- Under certain assumptions the map $\St(\Phi, k[t]) \to \St(\Phi, k[t, t^{-1}])$ is injective.
-\end{lemma}
-\begin{proof}
- %TODO: Add references on Rehmann and Hurrelbrink...
-\end{proof}
+\begin{lemma} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
+Then $\K_2(\Phi, k[X, X^{-1}]) = \K_2(\Phi, k) \oplus H(\Phi, k)$, where
+\[ H(\Phi, k) = \left\{\begin{array}{ll} k^* & \text{if $\Phi$ is nonsymplectic,} \\ \K_1^\mathrm{MW}(k)& \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+\begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups
+\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
+                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
+Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto's theorem~\cite[Theorem~5.10]{Ma69}.
+The required assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.
+
+In the symplectic case the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
+ which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of~\cref{bass-ft} and~\cite[Lemma~4.1.1]{AF17}. \end{proof}
+
+\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
+\begin{proof} The result follows from consideration of the commutative diagram
+\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
+               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
+in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by the above lemma. \end{proof}
 
@@
 Let $a$ be an element of $\Ker(h)$.
-Since $i$ is injective by~\cref{lem:field-case}, the element $a$ also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\Phi, B, I)$ via $\mu_B$.
+Since $i$ is injective by~\cref{field-injectivity}, the element $a$ also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\Phi, B, I)$ via $\mu_B$.
 Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\Phi, R, I)$ such that $j_R(c) = g(b)$.
@@
   \K_3(\rD_\ell, R) \ar[r]        & \K_3(\rD_\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
- From~\cref{lem:bass-ft,lem:summary} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
+ From~\cref{bass-ft,lem:summary} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
  In view of~\cref{lem:Panin-stability} the central vertical map is isomorphic to the canonical map

### 2019-01-27 dl-paper.tex
Slight rewrite

@@
 
-\begin{lemma}\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ one has
- \[ \GW_i^{[k]}(R[X, X^{-1}]) \cong \GW_i^{[k]}(R) \oplus \GW_{i-1}^{[k-1]}(R). \] \end{lemma}
-\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
-
-\begin{lemma}\label{lem:summary} Suppose that $F$ is a field of characteristic $\neq 2$, then
-$\GW_2^{[3]}(F) = 0$. \end{lemma}
-\begin{proof} See~\cite[Lemma~2.2]{FRS12}. \end{proof}
+\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a split exact sequence of abelian groups
+ \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] &  \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
+\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
 
@@
 \begin{lemma} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
-Then $\K_2(\Phi, k[X, X^{-1}]) = \K_2(\Phi, k) \oplus H(\Phi, k)$, where
-\[ H(\Phi, k) = \left\{\begin{array}{ll} k^* & \text{if $\Phi$ is nonsymplectic,} \\ \K_1^\mathrm{MW}(k)& \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+Then there is a split exact sequence of abelian groups
+\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right \]  \end{lemma}
 \begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups
@@
   \K_3(\rD_\ell, R) \ar[r]        & \K_3(\rD_\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
- From~\cref{bass-ft,lem:summary} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
+ Invoking~\cref{bass-ft} and \cite[Lemma~2.2]{FRS12} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
  In view of~\cref{lem:Panin-stability} the central vertical map is isomorphic to the canonical map

### 2019-01-28 dl-paper.tex
Generalized Proposition 1

@@
 \newtheorem{cond}[lemma]{Condition}
+
+\newlist{proplist}{enumerate}{1} \setlist[proplist]{label=(\roman{proplisti}), ref=\thethm.(\roman{proplisti}),noitemsep} \Crefname{proplisti}{Proposition}{Propositions}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelem.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
+
 \DeclareMathOperator{\Ker}{Ker}
@@
 \newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}} %Category name
 
@@
 
+\subsection{Unstable Quillen K-groups}
 In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left. 
 Thus we need to work with unstable $\K_3$-functors a la Quillen (cf.~\cite{Pa89}).
-\begin{df}  
-Denote by $X$ the topological space obtained from the (discrete) classifying space $B\G(\Phi, R)$ by means of Quillen's $+$-construction with respect to the elementary subgroup $\E(\Phi, R)$ (which is perfect thanks to the first assumption).
-Now set $\K_3(\Phi, R) = \pi_3(X)$.
-\end{df}
-%TODO: Give reference on the definition of the plus-construction?
 
-\begin{prop}\label{characterization} The group $\K_3(\Phi, R)$ is isomorphic to $\HH_3(\St(\Phi, R), \ZZ)$.
-In particular, it does not depend on the isogeny form of $\G(\Phi, R)$ used to define it.
-Moreover, for a ring epimorphism $R \to R/I$ there is a functorial exact sequence
-\[ \xymatrix{\K_3(\Phi, R) \ar[r] & \K_3(\Phi, R/I) \ar@{->>}[r] & C(\Phi, R, I).} \]
+Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor and $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
+
+Thanks to the functoriality of Quillen's plus-construction (see e.\,g.~\cite[Proposition~5.2.4]{Ro95}) one can define a functor 
+$X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define the corresponding K-group functors via $\K_{i}(G, P, R) = \pi_i(X_{G, P}(R))$.
+
+\begin{prop}\label{characterization}
+Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor such that
+ for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
+\begin{proplist}
+ \item There is a natural isomorphism $\K_3(G, P, R) \cong \HH_3(S(R), \ZZ)$.
+ \item For a ring epimorphism $R \to R/I$ there is a natural exact sequence
+ \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
+\end{proplist}
 \end{prop}
 \begin{proof}
- %TODO: First part.
+ Follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook} provided one notices that all the intermediate isomorphisms are natural in $R$.
 
@@
 
-\begin{lemma} \label{lem:Panin-stability}
- Let $R$ be either a field, principal ideal domain or a Dedekind domain. 
- Then the canonical map $\K_3(\rD_\ell, R) \to \K_3(\rD_\infty, R)$ is an epimorphism for $\ell \geq 6$ 
- and an isomorphism for $\ell \geq 7$.
-\end{lemma}
-\begin{proof}
- Stabilization for orthogonal and symplectic K-groups a la Quillen is given by Panin's theorem, see~\cite[Theorem~9.4]{Pa89}.
-More specifically the bounds for surjective (resp.
-injective) stability is
+Stability for orthogonal and symplectic K-theories is given by the following theorem of Panin
+\begin{theorem}[Panin] \label{lem:Panin-stability}
+ Let $R$ be either a field, principal ideal domain or a Dedekind domain and set $a = 1,2,3$ in each of respective cases.
+ Then the canonical map $\K_k(\rD_\ell, R) \to \K_k(\rD_\infty, R)$ is an epimorphism for $\ell \geq \mathrm{max}(2k, a+k-1)$ 
+ and an isomorphism for $\ell \geq \mathrm{max}(2k+1, a+k)$, where $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively \end{theorem}
+\begin{proof} See~\cite[Theorem~9.4]{Pa89}. \end{proof}
+
+\begin{comment}
+ Stabilization for orthogonal and symplectic K-groups a la Quillen is given by Panin's theorem,  More specifically the bounds for surjective (resp. injective) stability is 
  $\ell \geq \max(6, a+2)$ (resp. $\ell \geq \max(7,a+3)$) for $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively.
-\end{proof}
+\end{comment}
 
@@
 \[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right \]  \end{lemma}
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
 \begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups

### 2019-01-29 dl-paper.tex
Writing down Proposition 1

@@
 
-Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor and $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
+Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor preserving binary pullbacks and 
+ $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
 
@@
 \begin{prop}\label{characterization}
-Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor such that
- for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
+Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor equipped with a natural transformation
+ $\varphi \colon S \to P$ such that for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
 \begin{proplist}
  \item There is a natural isomorphism $\K_3(G, P, R) \cong \HH_3(S(R), \ZZ)$.
- \item For a ring epimorphism $R \to R/I$ there is a natural exact sequence
+ \item There is an exact sequence natural in $(R, I)$:
  \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
@@
 \begin{proof}
- Follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook} provided one notices that all the intermediate isomorphisms are natural in $R$.
+ The first claim follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook}. %provided one verifies that all the intermediate isomorphisms are natural in $R$.
 
- By~\cite[Th{\'e}or{\`e}me~2]{Lo78} the relative homology group $\HH_3(\St(\Phi, R/I), \St(\Phi, R), \ZZ)$ can be identified with the kernel $C(\Phi, R, I)$ of the relative central extension $\St(\Phi, R, I) \to \St(\Phi, R)$.
+ Let us verify the second claim.
+ Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
+  and set $d_i = Sp_i$, $s = S\Delta$.
+ Obviously, $d_0s = d_1 s = id_{S(R)}$. Set $G_i = \Ker(d_i)$, $S(R, I) = G_0 / [G_0, G_1]$ and denote by $\mu$ the natural map $S(R, I) \to N$ induced by $d_1$.
+
+ Since $\varphi(G_i) \subseteq \Ker(G(p_i))$ and $G$ preserves pullbacks we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi) \colon S(D_{R, I}) \to G(D_{R, I}))$
+  and hence $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
+ Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal
+  relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$.
+
+ By~\cite[Th{\'e}or{\`e}me~2]{Lo78} the relative homology group $\HH_3(\St(\Phi, R/I), \St(\Phi, R), \ZZ)$ can be identified
+ with the kernel $C(\Phi, R, I)$ of the relative central extension $\St(\Phi, R, I) \to \St(\Phi, R)$.
 \end{proof}

### 2019-01-29 dl-paper.tex
Writing down Proposition 1

@@
 
-\subsection{Relative Steinberg groups}
-
-The aim of this section is to briefly remind the reader definitions of relative Steinberg groups and their basic properties.
-We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
-%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).
-...
-
-%Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
-\begin{equation}\label{eq:relative-St}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
-\end{equation}
-It is not hard to show that $C(\Phi, R, I) = 0$ in the special case when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
-
-Unstable relative Steinberg groups share many good properties with their stable counterparts studied in~\cite{Lo78} provided the following assumptions on $\Phi$ hold: \begin{enumerate}
- \item $\St(\Phi, R)$ is perfect and super-perfect for all commutative $R$ (i.\,e. the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$).
- \item for all commutative rings $R$ the group $\K_2(\Phi, R)$ is central in $\St(\Phi, R)$.
-\end{enumerate}
-For example, under these assumptions it can be shown that the map $\St(\Phi, R, I) \to \St(\Phi, R)$ is a universal relative central extension of a pair $(\St(\Phi, R/I), \St(\Phi, R))$ in the sense of~\cite{Lo78} (the proof is identical to~\cite[Corollary~3]{S15}).
-
 \subsection{Unstable Quillen K-groups}
+\begin{comment}
 In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left. 
 Thus we need to work with unstable $\K_3$-functors a la Quillen (cf.~\cite{Pa89}).
-
-Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor preserving binary pullbacks and 
- $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
+\end{comment}
+Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
+\begin{enumerate}
+ \item\label{req:left-exact} $G$ is left exact;
+ \item $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$;
+ \item There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
+ \item \label{req:coeq} $S$ preserves coqualizers of kernel pairs.
+\end{enumerate}
 
 Thanks to the functoriality of Quillen's plus-construction (see e.\,g.~\cite[Proposition~5.2.4]{Ro95}) one can define a functor 
-$X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define the corresponding K-group functors via $\K_{i}(G, P, R) = \pi_i(X_{G, P}(R))$.
+$X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define for $i \geq 1$ the corresponding K-group functors $\K_{i}(G, P, R)$ as the homotopy groups $\pi_i(X_{G, P}(R))$.
 
 \begin{prop}\label{characterization}
-Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor equipped with a natural transformation
- $\varphi \colon S \to P$ such that for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
+ Then the following holds:
 \begin{proplist}
- \item There is a natural isomorphism $\K_3(G, P, R) \cong \HH_3(S(R), \ZZ)$.
+ \item There are natural isomorphisms
+  \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
  \item There is an exact sequence natural in $(R, I)$:
+ \end{proplist}
  \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
-\end{proplist}
 \end{prop}
@@
 
- Since $\varphi(G_i) \subseteq \Ker(G(p_i))$ and $G$ preserves pullbacks we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi) \colon S(D_{R, I}) \to G(D_{R, I}))$
+ From~\eqref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi) \colon S(D_{R, I}) \to G(D_{R, I})$
   and hence $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
- Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal
-  relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$.
+ Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$, 
+   which coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}.
 
@@
 \end{comment}
+
+\subsection{Relative Steinberg groups}
+
+The aim of this section is to briefly remind the reader definitions of relative Steinberg groups and their basic properties.
+We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
+%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).
+...
+
+%Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
+\begin{equation}\label{eq:relative-St}
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
+\end{equation}
+It is not hard to show that $C(\Phi, R, I) = 0$ in the special case when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
+
+Unstable relative Steinberg groups share many good properties with their stable counterparts studied in~\cite{Lo78} provided the following assumptions on $\Phi$ hold: \begin{enumerate}
+ \item $\St(\Phi, R)$ is perfect and super-perfect for all commutative $R$ (i.\,e. the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$).
+ \item for all commutative rings $R$ the group $\K_2(\Phi, R)$ is central in $\St(\Phi, R)$.
+\end{enumerate}
+For example, under these assumptions it can be shown that the map $\St(\Phi, R, I) \to \St(\Phi, R)$ is a universal relative central extension of a pair $(\St(\Phi, R/I), \St(\Phi, R))$ in the sense of~\cite{Lo78} (the proof is identical to~\cite[Corollary~3]{S15}).
 
@@
 
-\begin{lemma} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
+\begin{prop} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
 Then there is a split exact sequence of abelian groups
 \[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{prop}
 \begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups

### 2019-01-29 dl-paper.tex
More stuff added to Proposition 1

@@
  \item There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
- \item \label{req:coeq} $S$ preserves coqualizers of kernel pairs.
+ \item \label{req:coeq} $S$ preserves coequalizers of kernel pairs.
 \end{enumerate}
@@
 
+Let us also briefly recall Loday's procedure for relativization of $S$, that is,
+ extending $S$ from the category of rings to the category of pairs.
+Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
+  and set $d_i = Sp_i$, $s = S\Delta$.
+ Obviously, $d_0s = d_1 s = id_{S(R)}$. Set $G_i = \Ker(d_i)$, and define $S(R, I)$ as $ G_0 / [G_0, G_1]$, denote by $\mu$ the natural map $S(R, I) \to S(R)$ induced by $d_1$.
+
 \begin{prop}\label{characterization}
- Then the following holds:
 \begin{proplist}
@@
   \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
+ \item The map $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of 
+    $S(R) \to S(R/I)$, whose kernel is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
  \item There is an exact sequence natural in $(R, I)$:
+ \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \Ker(\mu).} \]
  \end{proplist}   
- \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
 \end{prop}
@@
 
- Let us verify the second claim.
- Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
-  and set $d_i = Sp_i$, $s = S\Delta$.
- Obviously, $d_0s = d_1 s = id_{S(R)}$. Set $G_i = \Ker(d_i)$, $S(R, I) = G_0 / [G_0, G_1]$ and denote by $\mu$ the natural map $S(R, I) \to N$ induced by $d_1$.
-
- From~\eqref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi) \colon S(D_{R, I}) \to G(D_{R, I})$
+ Let us verify the second claim. From~\eqref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$
   and hence $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
  Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$, 
-   which coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}.
+   which coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}. The kernel of $\mu$ is isomorphic to $\HH_3(S(R), S(R/I), \ZZ)$ by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
 
- By~\cite[Th{\'e}or{\`e}me~2]{Lo78} the relative homology group $\HH_3(\St(\Phi, R/I), \St(\Phi, R), \ZZ)$ can be identified
- with the kernel $C(\Phi, R, I)$ of the relative central extension $\St(\Phi, R, I) \to \St(\Phi, R)$.
+ The third claim now follows from the starting portion of the homology long exact sequence of the pair $(S(R/I), S(R))$ and the first two assertions.
 \end{proof}

### 2019-01-30 dl-paper.tex
Reorganizing introduction

@@
 
+\begin{comment}
+Suppose for a moment that $\langle \alpha, \beta \rangle = -1$ and  $\langle \beta, \alpha \rangle = -1$ then
+\[ \{s, t^{-1} \} = \{s,  t^{-1}\}_\alpha = \{t, s^{-1} \}_\beta^{-1} = \{s^{-1}, t\} \]
+In particular, $\{s, s^{-1}\} = \{s, s^{-1}\}^{-1}$ 
+\end{comment}
 \subsection{Unstable Quillen K-groups}
@@
 \end{comment}
-Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
+Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following reqirements:
 \begin{enumerate}
- \item\label{req:left-exact} $G$ is left exact;
- \item $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$;
- \item There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
+ \item \label{req:left-exact} $G$ is left exact;
+ \item \label{req:subfunc} $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$;
+ \item \label{req:uce} There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
  \item \label{req:coeq} $S$ preserves coequalizers of kernel pairs.
@@
 Thanks to the functoriality of Quillen's plus-construction (see e.\,g.~\cite[Proposition~5.2.4]{Ro95}) one can define a functor 
+%TODO: can also refer to Weibel's IV.1.5 provided Top is replaced with hTop which apparently does not change anything
 $X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define for $i \geq 1$ the corresponding K-group functors $\K_{i}(G, P, R)$ as the homotopy groups $\pi_i(X_{G, P}(R))$.
@@
 Let us also briefly recall Loday's procedure for relativization of $S$, that is,
- extending $S$ from the category of rings to the category of pairs.
+ a way of extending $S$ from the category of rings to the category of pairs.
 Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
@@
 
+%TODO: Give the definition of $D_{R, I}$ and of 
 \begin{prop}\label{characterization}
-\begin{proplist}
+\begin{enumerate}
  \item There are natural isomorphisms
@@
     $S(R) \to S(R/I)$, whose kernel is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
- \item There is an exact sequence natural in $(R, I)$:
+ \item There is an exact sequence which is natural in $(R, I)$:
  \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \Ker(\mu).} \]
- \end{proplist}   
+ \end{enumerate}   
 \end{prop}
 \begin{proof}
- The first claim follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook}. %provided one verifies that all the intermediate isomorphisms are natural in $R$.
+ The first claim follows from Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook} (here we use~\eqref{req:subfunc}--\eqref{req:uce}).
+%provided one verifies that all the intermediate isomorphisms are natural in $R$.
 
  Let us verify the second claim. From~\eqref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$
-  and hence $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
- Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$, 
-   which coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}. The kernel of $\mu$ is isomorphic to $\HH_3(S(R), S(R/I), \ZZ)$ by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
+  therefore $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
+ From~\eqref{req:uce} we also obtain that $H_1(S(D_{R,I})) = H_2(S(D_{R,I})) = 0$ .
+ The last two assertions allow us to invoke~\cite[Proposition~6]{Lo78} and conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$
+  in the sense of~\cite[\S~3]{Lo78}. 
+ Notice that this coequalizer coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}. 
+ Finally, the kernel of $\mu$ is isomorphic to $\HH_3(S(R), S(R/I), \ZZ)$ by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
 
- The third claim now follows from the starting portion of the homology long exact sequence of the pair $(S(R/I), S(R))$ and the first two assertions.
+ The third claim now follows from the starting portion of the homology long exact sequence of the map $S(R) \to S(R/I)$ and the first two assertions.
 \end{proof}
 
-Stability for orthogonal and symplectic K-theories is given by the following theorem of Panin
+Let us mention the example of a triple $(G,P,S)$ satisfying the above conditions.
+\begin{example} \label{ex:orth}
+ For $n \geq 5$ take the orthogonal group functor $\mathrm{O}_{2n}(-)$ and its elementary subfunctor $\mathrm{EO}_{2n}(-)$ as functors $G_n$ and $P_n$, respectively.
+ Now set $S_n = \St(\rD_n, -)$.
+ From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\eqref{req:uce}.
+ The other requirements can be verified in a straightforward manner.
+\end{example}
+
+In the above definition we could have replaced the orthogonal group with a different isogeneous form of the orthogonal group, e.\,g. 
+ we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then defined $P_n$ as its elementary subfunctor.
+Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
+ it would not change the functors $\K_i(G_n, P_n, -)$ for $i\geq 3$.
+
+Now let $G_n, P_n$ be again as in~\cref{ex:orth}. 
+Let us formulate a stability result for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
 \begin{theorem}[Panin] \label{lem:Panin-stability}
- Let $R$ be either a field, principal ideal domain or a Dedekind domain and set $a = 1,2,3$ in each of respective cases.
- Then the canonical map $\K_k(\rD_\ell, R) \to \K_k(\rD_\infty, R)$ is an epimorphism for $\ell \geq \mathrm{max}(2k, a+k-1)$ 
- and an isomorphism for $\ell \geq \mathrm{max}(2k+1, a+k)$, where $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively \end{theorem}
-\begin{proof} See~\cite[Theorem~9.4]{Pa89}. \end{proof}
+ Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these respective cases.
+ Then the canonical map $\K_i(G_n, P_n, R) \to \K_i(G_{n+1}, P_{n+1}, R)$ is an epimorphism for $n \geq b$ 
+ and an isomorphism for $\ell \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
 
-\begin{comment}
- Stabilization for orthogonal and symplectic K-groups a la Quillen is given by Panin's theorem,  More specifically the bounds for surjective (resp. injective) stability is 
- $\ell \geq \max(6, a+2)$ (resp. $\ell \geq \max(7,a+3)$) for $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively.
-\end{comment}
+Of course, in the limit, the groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ coincide with Karoubi's hermitian groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
+The modern version of hermitian K-theory is the theory of higher Grothendieck--Witt groups of schemes.
+We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for a more detailed introduction to it.
+For our purposes it would be sufficient to think of $\GW_i^{[k]}(R)$ as a shorthand for the following:
+\begin{equation}
+ \GW_i^{[k]}(R) = \left\{\begin{array}{ll} KO_i(R), & k = 0, \\ U_i(R), & k = 1, \\ KSp_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
+\end{equation}
+The notation for the upper index $[k]$ suggests that Grothendieck--Witt groups are $4$-periodic in $k$.
+The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
 
-The following result was proved in \cite[Proposition~3.2]{Ste13}.
-\begin{lemma}\label{lem:Zgen} Let $\Phi$ be an irreducible root system of rank $\geq 2$. 
-Let $G$ denote the normal closure in $\St(\Phi, R)$ of the subgroup spanned by elementary root unipotents of level $I$, i.\,e.
-$G=\langle x_\alpha(s) \mid \alpha\in\Phi,\ s\in I\rangle^{\St(\Phi, R)}$.
-
-Let $S$ be a parabolic set of roots of $\Phi$ with special part $\Sigma_S$.
-Then $G$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S, I, R)$ consisting of the following two families of elements:
-\begin{itemize}
- \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
- \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
-\end{itemize}        
-\end{lemma}
-
-\begin{comment}
-Suppose for a moment that $\langle \alpha, \beta \rangle = -1$ and  $\langle \beta, \alpha \rangle = -1$ then
-\[ \{s, t^{-1} \} = \{s,  t^{-1}\}_\alpha = \{t, s^{-1} \}_\beta^{-1} = \{s^{-1}, t\} \]
-In particular, $\{s, s^{-1}\} = \{s, s^{-1}\}^{-1}$ 
-\end{comment}
+In the sequel we will need the following result.
+\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a split exact sequence of abelian groups
+ \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] &  \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
+\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
 
@@
 
-%\subsection{Isogenous forms of the orthogonal group}
-\subsection{Hermitian K-theory and higher Grothendieck--Witt groups}
-In this section we collect some facts pertaining to Hermitian K-theory that will be of relevance to us. We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for a more detailed introduction.
+The following result was proved in \cite[Proposition~3.2]{Ste13}.
+\begin{lemma}\label{lem:Zgen} Let $\Phi$ be an irreducible root system of rank $\geq 2$. 
+Let $G$ denote the normal closure in $\St(\Phi, R)$ of the subgroup spanned by elementary root unipotents of level $I$, i.\,e.
+$G=\langle x_\alpha(s) \mid \alpha\in\Phi,\ s\in I\rangle^{\St(\Phi, R)}$.
 
-First of all, recall that in~\cite{Ka80} M.~Karoubi defines higher Grothendieck--Witt groups via Quillen's plus-construction:
-
-Schlichting gave a more general definition which still agrees with the classical one in the affine case.
-In particular one has:
-\begin{equation}
- \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \mathrm{KO}_i(R), & k = 0, \\ U_i(R), & k = 1, \\ \mathrm{KSp}_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
-\end{equation}
-
-\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a split exact sequence of abelian groups
- \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] &  \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
-\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+Let $S$ be a parabolic set of roots of $\Phi$ with special part $\Sigma_S$.
+Then $G$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S, I, R)$ consisting of the following two families of elements:
+\begin{itemize}
+ \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+ \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
+\end{itemize}        
+\end{lemma}
 

### 2019-01-30 dl-paper.tex
Thorough rewrite

@@
  {\em Mathematical Subject Classification (2010):} 19C20}
+\author{Andrei Lavrenov}
+\address{Mathematisches Institut der Universit\"at M\"unchen, Theresienstr. 39, D-80333 M\"unchen}
+\email{avlavrenov at gmail.com}
+
 \author {Sergey Sinchuk}
@@
 \subsection{Steinberg groups}
+%TODO: Describe what root systems are sympelctic and which are not
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
@@
 \end{comment}
-\subsection{Unstable Quillen K-groups}
-\begin{comment}
-In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left. 
-Thus we need to work with unstable $\K_3$-functors a la Quillen (cf.~\cite{Pa89}).
-\end{comment}
+\subsection{Unstable Quillen K-groups} \label{sec:quillen}
 Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following reqirements:
@@
 
-%TODO: Give the definition of $D_{R, I}$ and of 
+%TODO: Give the definition of $D_{R, I}$ and of the category of Pairs
 \begin{prop}\label{characterization}
@@
   \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
- \item The map $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of 
-    $S(R) \to S(R/I)$, whose kernel is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
- \item There is an exact sequence which is natural in $(R, I)$:
+ \item The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of 
+    the map $S(R) \to S(R/I)$. The kernel of $\mu$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+ \item There is a natural exact sequence:
  \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \Ker(\mu).} \]
@@
 
-In the above definition we could have replaced the orthogonal group with a different isogeneous form of the orthogonal group, e.\,g. 
- we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then defined $P_n$ as its elementary subfunctor.
-Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
- it would not change the functors $\K_i(G_n, P_n, -)$ for $i\geq 3$.
+In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
+ we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
+Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests %TODO: Does it really change K_2?
+ it would not change $\K_i(G_n, P_n, -)$ for $i\geq 3$.
 
-Now let $G_n, P_n$ be again as in~\cref{ex:orth}. 
-Let us formulate a stability result for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
+Now let $G_n, P_n$ be again as in~\cref{ex:orth}. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
+Let us formulate the stability theorem for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
 \begin{theorem}[Panin] \label{lem:Panin-stability}
  Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these respective cases.
- Then the canonical map $\K_i(G_n, P_n, R) \to \K_i(G_{n+1}, P_{n+1}, R)$ is an epimorphism for $n \geq b$ 
+ Then the canonical map $KO_i(2n, R) \to KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
  and an isomorphism for $\ell \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
 
-Of course, in the limit, the groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ coincide with Karoubi's hermitian groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
-The modern version of hermitian K-theory is the theory of higher Grothendieck--Witt groups of schemes.
-We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for a more detailed introduction to it.
-For our purposes it would be sufficient to think of $\GW_i^{[k]}(R)$ as a shorthand for the following:
+Of course, the limit groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ are exactly hermitian K-groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
+There is a modern version of hermitian K-theory, namely the theory of higher Grothendieck--Witt groups of schemes.
+We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for an introduction to this theory.
+For our purposes it would be sufficient to restrict our attention to to the affine case and to think of $\GW_i^{[k]}(R)$ as a shorthand for
 \begin{equation}
  \GW_i^{[k]}(R) = \left\{\begin{array}{ll} KO_i(R), & k = 0, \\ U_i(R), & k = 1, \\ KSp_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
-\end{equation}
+\end{equation} %TODO: Reference?
+The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
 The notation for the upper index $[k]$ suggests that Grothendieck--Witt groups are $4$-periodic in $k$.
-The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
 
 In the sequel we will need the following result.
-\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a split exact sequence of abelian groups
+\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups
  \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
@@
 \subsection{Relative Steinberg groups}
+Let us briefly recall the definition and basic properties of relative Steinberg groups.
+We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
+By definition, the relative Steinberg group functor $\St(\Phi, R, I)$ is obtained from the functor $\St(\Phi, R)$
+ via the relativization procedure described in~\cref{sec:quillen}.
 
-The aim of this section is to briefly remind the reader definitions of relative Steinberg groups and their basic properties.
-We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
-%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).
-...
+\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
+$A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
+Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
+by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
+Consider the following commutative square of canonical maps.
+\[ \xymatrix{
+    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R)
+   } \]
+Then there exists a diagonal arrow which makes the diagram commute.   
+\end{lemma} 
+\begin{proof}
+ Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
+  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
+ Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
 
-%Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
-\begin{equation}\label{eq:relative-St}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
-\end{equation}
-It is not hard to show that $C(\Phi, R, I) = 0$ in the special case when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}.
+ Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
+  (cf.~\cite[\S~4]{LS17} for more details).
+\end{proof}
+%TODO: Give reference on a similar result of Lavrenov?
 
-Unstable relative Steinberg groups share many good properties with their stable counterparts studied in~\cite{Lo78} provided the following assumptions on $\Phi$ hold: \begin{enumerate}
- \item $\St(\Phi, R)$ is perfect and super-perfect for all commutative $R$ (i.\,e. the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$).
- \item for all commutative rings $R$ the group $\K_2(\Phi, R)$ is central in $\St(\Phi, R)$.
-\end{enumerate}
-For example, under these assumptions it can be shown that the map $\St(\Phi, R, I) \to \St(\Phi, R)$ is a universal relative central extension of a pair $(\St(\Phi, R/I), \St(\Phi, R))$ in the sense of~\cite{Lo78} (the proof is identical to~\cite[Corollary~3]{S15}).
+If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
+\begin{equation*}
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.}
+\end{equation*}
+The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits.
+This immediately follows e.\,g. from the exact sequence of~\cref{characterization}, it is also possible to give a direct proof of this fact, see \cite[Lemma~8]{S15}.
+The following result plays a key role in the proof of~\cref{thm41}.
+\begin{lemma} \label{lem:prop41}
+In the notation of~\cref{lem:lemma32} assume additionally that the residue field $k$ is of characteristic $\neq 2$.
+Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$.
+\end{lemma}
+\begin{proof}
+  Consider the following commutative diagram with rows obtained from~\cref{characterization}:
+\begin{equation*}\xymatrix{
+ KO_3(2\ell, B) \ar[r] \ar[d] & KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
+ KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
+In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is isomorphic to the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+Invoking~\cref{bass-ft} we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
+By \cite[Lemma~2.2]{FRS12} the group $\GW_2^{[3]}(k)$ is trivial, therefore $f'$ (and hence $f$) are surjective.
+\end{proof}
 
+\subsection{Miscellanea}
 The following result was proved in \cite[Proposition~3.2]{Ste13}.
@@
 \subsection{First injectivity theorem}
-For a commutative local ring $A$ with the maximal ideal $M$ and residue field $k$
-we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
-It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
-\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$.
-Consider the following commutative square of canonical maps.
-\[ \xymatrix{
-    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R)
-   } \]
-Then there exists a diagonal arrow which makes the diagram commute.   
-\end{lemma} 
-\begin{proof}
- Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
-  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
- Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
-
- Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
-  (cf.~\cite[\S~4]{LS17} for more details).
- %TODO: Also give reference on a similar result of Lavrenov
- %TODO: Rethink the proof of amalgamation theorem...
-\end{proof}
 
@@
 in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by the above lemma. \end{proof}
-
-\begin{prop}
- Suppose that the canonical map $C(\Phi, B, I) \to C(\Phi, R, I)$ is surjective,
-  and that Tulenbaev lifting property holds for $\St(\Phi, R)$. 
- Then the canonical map of Steinberg groups $\St(\Phi, B) \to \St(\Phi, R)$ is injective.
-\end{prop}
+\begin{theorem} \label{thm41}
+Assume the notation of~\cref{lem:lemma32} and suppose additionally that $2$ is invertible in $A$.
+Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
+\end{theorem}
 \begin{proof}
- Consider the following commutative diagram with exact rows: 
+ Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
 \begin{equation*} \xymatrix{
- C(\Phi, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\Phi, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
- \St(\Phi, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\Phi, k[X]) \ar[d]_{i} \\
- C(\Phi, R, I) \ar[r]^{j_R}         & \St(\Phi, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
- \St(\Phi, R) \ar[r]^{\pi_R}        & \St(\Phi, k[X, X^{-1}]).
+ C(\rD_\ell, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
+ \St(\rD_\ell, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
+ C(\rD_\ell, R, I) \ar[r]^{j_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
+ \St(\rD_\ell, R) \ar[r]^-{\pi_R}        & \St(\rD_\ell, k[X, X^{-1}]).
 }\end{equation*}
-Let $a$ be an element of $\Ker(h)$.
-Since $i$ is injective by~\cref{field-injectivity}, the element $a$ also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\Phi, B, I)$ via $\mu_B$.
-Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\Phi, R, I)$ such that $j_R(c) = g(b)$.
-By our assumption, $f$ is surjective, therefore
- $c = f(d)$ for some $d \in C(\Phi, R, I)$ and we obtain the required assertion:
+Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
+ also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
+Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $j_R(c) = g(b)$. 
+By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$ and we obtain the required assertion:
  \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
 
-\end{proof}
-
-\begin{theorem} Suppose $A$ is a local ring of characteristic $\neq 2$, then for $\ell \geq 7$
-  the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
-\end{theorem}
-\begin{proof}
- In view of the above proposition and~\cref{lem:lemma32} we are left to verify that the map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective.
-Consider the following commutative diagram, whose rows are given by \cref{characterization}:
- \begin{equation*}\xymatrix{
-  \K_3(\rD_\ell, B) \ar[r] \ar[d] & \K_3(\rD_\ell, k[X]) \ar[d] \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
-  \K_3(\rD_\ell, R) \ar[r]        & \K_3(\rD_\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
- Invoking~\cref{bass-ft} and \cite[Lemma~2.2]{FRS12} we obtain that $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k)$.
- In view of~\cref{lem:Panin-stability} the central vertical map is isomorphic to the canonical map
- $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$ and therefore is surjective. The requred surjectivity of $f$ now follows.
 \end{proof}

### 2019-04-26 dl-paper.tex
Added sheet

@@
-\documentclass[oneside, 10pt]{amsart}
+\documentclass[oneside, 8pt]{amsart}
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
@@
 
-\section{Proof of the main result}
-\subsection{Overview of the proof}
-\subsection{First injectivity theorem}
-
+\section{First injectivity theorem}
 \begin{prop} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
@@
 
-\subsection{Second injectivity theorem}
 \begin{comment}
@@
 \begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
-\end{comment}
 
@@
  \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.}  Obviously, in this case also $g' = g$.
- \begin{comment} 
  \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
  \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
- \end{comment}
  \item {\it Case $\alpha = \beta$.} By our choice of $S$ holds $\beta \not \in \Sigma_S$, therefore $f_2(X) = 0$ and $g$ commutes with $x_\alpha(aX^{-1})$.
@@
 \end{rem}
+\include{rehmann}
+\end{comment}
 
-%\include{rehmann}
+\section{Second injectivity theorem}
+\begin{comment} 
+First of all, set $\widetilde{V} = \overline{G}^{\geq 0}_M \times G^{\leq 0} \times (1 + M)^*$
+ and consider it as a pointed set, i.\,e. ignore its structure of the group but retain $\widetilde{v_0} = (1, 1, 1)$ as a choice of a basepoint.
+We let the group $\St(\Phi, R, M)$ act on $\widetilde{V}$ via the formula 
+ $h \cdot (\overline{g}^+, g^-, u) = (\overline{g}^+ \cdot j_+i_+(h), i_-(h)^{-1}\cdot g^-, u)$.
+Denote by $V$ the set of orbits of this action with the fixed basepoint $v_0 = O(\widetilde{v}_0)$.
+We will use the notation $[\overline{g}^+, g^-, u]$ as a shorthand for $O(\overline{g}^+, g^-, u)$.
+
+It is obvious that the map $\widetilde{p} \colon \widetilde{V} \to \St(\Phi, R[t, t^{-1}])$ given by 
+ \[(\overline{g}^+, g^-, u) \mapsto \overline{g}^+ \cdot j_-(g^-) \cdot \{t, u\}\]
+ is constant on the orbits of the above action
+  and therefore gives rise to a well-defined map $p \colon V \to \St(\Phi, R[t, t^{-1}])$ of pointed sets.
+
+We will construct an action of $\St(\Phi, B)$ on the set $V$ with the following additional properties:
+\begin{enumerate}
+\item for $g^- \in \St(\Phi, R[t^{-1}])$ one has $\varphi(g^-) \cdot v_0 = [1, g^-, 1]$, where $\varphi$ is the canonical map
+  $\St(\Phi, R[t^{-1}]) \to \St(\Phi, B)$ induced by the embedding $R[t^{-1}] \to B$.
+\item for $g \in \St(\Phi, B)$ the element $p(g \cdot v_0)$ coincides with the canonical image of $g$ in $\St(\Phi, R[t, t^{-1}])$; 
+\end{enumerate} \end{comment}
+
+Throughout this section $\Phi$ is a simply-laced irreducible root system and $R$ is a local ring with maximal ideal $M$.
+We denote by $B$ the ring $M[t] + R[t^{-1}]$ considered as a graded subring of $R[t, t^{-1}]$.
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[t], M[t]) \to \St(\Phi, R[t, t^{-1}])$ and by
+ $G^{\leq 0}$ the group $\St(\Phi, R[t^{-1}])$.
+
+\[ \xymatrix{ \overline{\St}(\Phi, R, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
+              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, R[t, t^{-1}]), } \]
+
+\subsection{Some elementary lemmas}
+\begin{comment}
+Hall-Witt identity
+\[ [[ y^{-1}, x], z] ^ {y^{-1}}  [[ z^{-1}, y], x] ^ {z^{-1}}  [[ x^{-1}, z], y] ^ {x^{-1}} = 1 \]
+\[ [[ y^{-1}, x], z]  \cdot [[ z^{-1}, y], x] ^ {z^{-1}y} \cdot  [[ x^{-1}, z], y] ^ {x^{-1}y} = 1. \]
+\[ [[ z^{-1}, y^{-1}], x] ^ {z^{-1}y^{-1}} \cdot  [[ x^{-1}, z], y^{-1}] ^ {x^{-1}y^{-1}} = [z, [ y, x]] . \]
+\[  . \]
+\end{comment}
+
+The following lemma summarizes basic properties of structure constants used in our computations below.
+\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta \in \Phi$ are such that $\alpha+\beta = \gamma \in \Phi$.
+\begin{enumerate}
+ \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
+ \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
+ \item $N_{\alpha, \beta} = N_{\beta, \gamma} = N_{\gamma, \alpha}.$
+\end{enumerate}
+\end{lemma}
+\begin{proof} See~\cite[\S~14]{VP}. \end{proof}
+
+Recall that $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$.
+\begin{lemma}\label{Zrels} Let $\Phi$ be a simply laced root system and $\alpha,\beta\in \Phi$ be a pair of roots.
+The elements $z_\alpha(s, \xi)$ satisfy the following relations (everywhere below $\xi, \eta\in R$, $s\in I$):
+\begin{enumerate} 
+\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
+\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
+\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
+\item\label{Z4} $z_{\gamma}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\gamma}(s, \xi)\ \text{if}\ \gamma\perp\alpha$.
+\item\label{Z5} $z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(N_{\alpha,\beta}s) \cdot x_{-\alpha}(N_{\alpha,\beta}st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(N_{\alpha,\beta} s, -N_{\alpha, \beta}t\xi).$
+\end{enumerate} \end{lemma}
+\begin{proof}
+The first four assertions are contained in~\cite[Lemma~9]{S15}. For the proof of the last formula set $\gamma = \alpha + \beta$ and compute:
+\begin{multline} z_{\gamma}(N_{\alpha,\beta}st, \xi) = 
+[x_\alpha(s)^{x_{-\gamma}(\xi)}, x_\beta(t)^{x_{-\gamma}(\xi)}] = [x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s),\ x_{-\alpha}(N_{\beta, -\gamma}t\xi) \cdot x_\beta(t)] = \\ = x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot \left( x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s)\right)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi) \cdot x_\beta(-t)} = \\
+= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi)} \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi)^ {x_\beta(-t)} = \\
+= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(-N_{\alpha, -\gamma}N_{\beta, -\gamma}st^2\xi^2) \cdot x_{-\gamma}(-N_{-\beta, -\alpha} N_{\alpha, -\gamma} N_{\beta, -\gamma}st\xi^2) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t) \cdot \\ \cdot x_{\beta}(-N_{\beta,-\gamma}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi) =\\ = x_{-\beta}(-N_{\alpha, \beta} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(st^2\xi^2) \cdot x_{-\gamma}(-N_{\alpha, \beta} st\xi^2) \cdot z_{-\beta}(-N_{\alpha, \beta} s\xi, -t) \cdot x_{\beta}(-N_{\alpha, \beta}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\alpha, \beta}t\xi).
+\qedhere
+\end{multline}  
+In the last equality we invoked the standard properties of structure constants (see e.\,g.
+formulas in Vavilov-Plotkin \S~14 which imply in our case that $N_{\alpha, \beta} = N_{\beta,-\gamma} = N_{-\gamma, \alpha} = -N_{\alpha, -\gamma}$).
+\end{proof}
+
+Using a variant of Hall-Witt identity: $[x, [ y, z]] = [[ x^{-1}, y^{-1}], z] ^ {x^{-1}y^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}y^{-1}}$ we compute
+\begin{multline}
+ [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
+\end{multline}
+
+\subsection{Computation of the kernel of the map of evaluation at $0$.}
+\begin{lemma} Denote by $C$ the mutual commutator subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$.
+Then one has \[\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot \overline{\St}(\Phi, A[X], XM[X]) \cdot C.\] 
+Consequently, the composite of the two factors in the right-hand side of the above formula coincides with the subgroup $I$ defined as 
+ the intersection $\overline{\St}(\Phi, A[X], M[X]) \cap \overline{\St}(\Phi, A[X], XA[X])$ (or alternatively, as the kernel of the evaluation map $\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$).
+\end{lemma}
+\begin{proof}
+ Take $g \in \overline{\St}(\Phi, A[X], M[X])$ and write it as $g = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+ It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
+
+ Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can written as $z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0))$.
+ Using the fact that the subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\St(\Phi, A, M)$ (this follows e.\,g.
+from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $g(0) = g_1(0)$ modulo $C$, which implies the first assertion.
+
+ Denote by $H$ the composite of $C$ and $\overline{\St}(\Phi, A[X], XM[X])$.
+It is clear that $H \subseteq I$.
+The reverse inclusion follows from the above argument and the fact that for $g \in I$ one has $g(0)=1$.
+\qedhere \end{proof}
+
+ \begin{lemma}
+   If $R$ is a local ring with maximal ideal $M$ then $\overline{\St}(\Phi, R, M) = U(\Phi^+, M) \cdot M(\Phi, R, M) \cdot U(\Phi^-, M)$.
+ \end{lemma}
+ \begin{proof}
+  See Theorem~2.4 of~M. Stein's paper on surjective stability in dimension 0.
+ \end{proof}
+
+\begin{corollary} For $R$, $M$ as above holds
+ $\left[\St(\Phi, XR[X]), \overline{\St}(\Phi, R, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XR[X]), \St(\Phi, M)\right]$.
+\end{corollary}
+\begin{proof}
+ Notice first that the generators of $M(\Phi, R, M)$ normalize both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ (see eq:conj-h-x).
+ Now for $g \in \St(\Phi, XR[X])$, $h \in M(\Phi, R, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+ \[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)]. \qedhere\]
+\end{proof}
+
+\begin{corollary} For $R$ and $M$ as above the subgroup $I$ is generated as a group by its subgroup $\St(\Phi, R[X], XM[X])$ and
+ the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in R[X]$, $\alpha \in \Phi$. 
+\end{corollary}
+\begin{proof}
+By the above lemmata one has $I \subseteq \St(\Phi, R[X], XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)].$
+It is clear that modulo $\St(\Phi, R[X], XM[X])$ the commutator subgroup $[\St(\Phi, XR[X]), \St(\Phi, M)]$ is generated
+ by all $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, $m \in M$, $\xi \in R[X]$, where $g \in \St(\Phi, M + XR[X])$.
+To verify the assertion, therefore, it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, R[X], XM[X])$.
+Moreover, since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a generator of $\St(\Phi, R[X])$,
+i.\,e. $g = x_\beta(\xi)$, $\eta \in R[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.
+
+Set $c_{\alpha,\beta}(m,\xi,\eta) = [[x_{\alpha}(m), x_{-\alpha}(X\xi)], x_\beta(\eta)]$.
+If $\alpha + \beta \not\in \Phi$, $\alpha - \beta \not \in \Phi$ then, obviously, one has $c_{\alpha,\beta}(m,\xi,\eta) = 1$.
+Now suppose $\alpha + \beta \in \Phi$, $\alpha - \beta \in \Phi$. We have:
+\begin{multline} \nonumber c_{\alpha,\beta}(m,\xi,\eta) = [x_{\alpha}(m), x_{-\alpha}(X\xi)] [x_{-\alpha}(X\xi), x_{\alpha}(m)x_{\alpha+\beta}(N_{\beta,\alpha} m\eta)] = \\
+ = {}^{x_\alpha(m)}\![x_{-\alpha}(X\xi), x_{\alpha + \beta}(N_{\beta, \alpha}m\eta)] = x_{\beta}(N_{\beta,\alpha} N_{-\alpha, \alpha+\beta} mX\xi\eta) x_{\alpha+\beta}(N_{\alpha,\beta}N_{\beta,\alpha}N_{-\alpha, \alpha+\beta}m^2X\xi\eta).
+\end{multline}
+It is clear that the expression in the right-hand side belongs to $\St(\Phi, R[X], XM[X])$. In the case $\alpha - \beta \in \Phi$, $\alpha + \beta \not \in \Phi$ the computation is similar.
+{\bf TODO:} we have to consider more cases if we want to make the result valid for nonsimply-laced root systems.
+\end{proof}
+
+\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
+\begin{df} \label{defP0}
+Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, R[X])$ under the
+ map induced by the embedding $R[X] \subseteq R[X, X^{-1}]$:
+\begin{enumerate}
+ \item $z_{\beta}(Xf, g), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
+ \item $z_{\beta}(f, Xg),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
+ \item $z_{\gamma}(f, g),\ \alpha \perp \gamma;$
+ \item $x_{-\alpha}(X^2f),$
+ \item $[x_{\beta}(m), x_{-\beta}(Xg)],\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi$.
+\end{enumerate}
+In the above formulae and below we assume that $f \in M[X]$ and $g \in R[X]$. \end{df}
+
+Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+The following lemma shows that this subgroup is sufficiently large.
+\begin{lemma} The subgroup $P_\alpha(*)$ contains the image of the subgroup $\St(\Phi, R[X], XM[X])$ in $\St(\Phi, R[X, X^{-1}])$. \end{lemma}
+\begin{proof}
+Clearly $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, g)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $g\in R[X]$.
+The assertion now easily follows from Stepanov's theorem. This can also be verified in a straightforward manner without Stepanov theorem.
+
+Now let us verify the assertion for the generators $c_\beta(m, \xi) = [x_\beta(m), x_{-\beta}(X\xi)] = x_\beta(m) \cdot z_{\beta}(-m, -X\xi)$.
+It is clear that $c_\beta(m, \xi)$ are contained in $P_\alpha(*)$ in the cases $\beta \perp \alpha$, $\alpha - \beta \in \Phi \cup \{0\}$.
+There are problems: 1) for the generator $c_{-\alpha}(m, \xi)$, 2) for the generator $c_\beta(m, \xi)$, $\alpha + \beta \in \Phi$.
+
+\begin{comment}
+Let us draw the matrix for $z_\alpha(m, X\xi)$:
+\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) =
+ \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
+Now let us draw the matrix for $c_\alpha(m, \xi)$:
+\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
+ \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
+\end{comment}
+\end{proof}
+
+\begin{comment}
+Useful consequence: $z_{-\alpha}(X^2f(X), g(X)) \in P_\alpha(0)$. Proof: $z_{-\alpha}(X^2f(X), g(X)) = 
+x_{-\beta}(-Xg) \cdot x_{-\alpha-\beta}(\epsilon X) \cdot x_{\alpha+\beta}(\epsilon X^3f^2g^2) \cdot x_{\alpha}(-X^2fg^2) \cdot 
+z_{-\beta}(-Xg, -Xf) \cdot x_{\beta}(-X^3f^2g)  \cdot x_{-\alpha}(-X^2f) \cdot z_{-\alpha-\beta}(\epsilon X, -\epsilon Xfg)$,
+where $\epsilon = N_{-\alpha-\beta,\beta}$. This is a product of generators of types: 1,1,2,2,1,1,4,1.
+\end{comment}
+
+\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence split by the map $m \mapsto x_{-\alpha}(mX)$:
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\]
+\end{lemma}
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator of $P_\alpha(0)$ listed in~Definition~\ref{defP0} still belongs to $P_\alpha(0)$.
+The assertion is obvious for the generators of types (3) and (4).
+
+Let us verify the assertion for the generators of type (1) and (2). In the case $\beta - \alpha \in \Phi$ we obtain from Lemma~\ref{Zrels}:
+\begin{align} z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2fg) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f)     \cdot z_{\beta}(Xf, g), \label{eq3-1} \\
+  z_{\beta}(f, Xg) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2fg ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf)     \cdot z_{\beta}(f, Xg), \label{eq3-2} \\
+  z_{\alpha}(f, Xg) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(g + m)). \end{align}
+The expressions in the right hand side of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
+
+Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
+\[ z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2fg ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2fg^2) \cdot z_{\beta}(Xf, g), \]
+the latter expression, clearly, is a product of generators of types $4, 1, 1$.
+\end{proof}
+
+For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
+From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. 
+The latter fact allows to make the following definition.
+
+\begin{df}
+Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, R[t, t^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] 
+\end{df}
+It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the conjugation map $g \mapsto {}^{x_\alpha(aX^{-1})}\!g$.
+
+\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in R$. \end{lemma}
+\begin{proof} As before, we need to verify that the conjugate of every generator of $P_\alpha(0)$ lies in $P_\alpha(0)$.
+First of all, consider the case $\alpha + \beta \in \Phi$ (only possible for the generator of the first type):
+\[ z_{\beta}(Xf, g) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, g). \]
+Clearly the expression in the right hand side is a product of elements of generators of type 2, 2, 1. 
+Now consider the case $\alpha - \beta \in \Phi$ (possible for generators of type (1) and (2)).
+\begin{align} z_{\beta}(Xf, g) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (afg) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot afg^2) \cdot z_{\beta}(Xf, g), \\
+z_{\beta}(f, Xg) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (afg) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot fXg^2a) \cdot z_{\beta}(f, Xg). \end{align}
+The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.
+
+Let us verify the assertion for the generator of type (4). Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke Lemma~\ref{Zrels}:
+\[z_{-\alpha}(X^2f, aX^{-1}) = x_{-\beta}(-a) \cdot x_{-\alpha-\beta}(\epsilon X) \cdot x_{\alpha+\beta}(\epsilon Xf^2a^2) \cdot x_{\alpha}(-a^2f) \cdot z_{-\beta}(-a, -Xf) \cdot x_{\beta}(-aX^2f^2)  \cdot x_{-\alpha}(-X^2f) \cdot z_{-\alpha-\beta}(\epsilon X, -\epsilon af), \] where $\epsilon = N_{-\alpha-\beta,\beta}$.
+It is clear that the latter expression is a product of generators of types: 2, 1, 1, 2, 2, 1, 1, 1, respectively.
+
+It remains to verify the assertion for the generator $z_\alpha(f, gX)$.
+\begin{comment}
+\[ z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(\epsilon s) \cdot x_{-\alpha}(\epsilon st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(\epsilon s, -\epsilon t\xi) \]
+
+\[ z_{\alpha+\beta}(- s t, \xi) = x_{-\beta}(-\epsilon s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(s t^2\xi^2) \cdot x_{-\alpha-\beta}(s t\xi^2) \cdot z_{-\beta}(-\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(-\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(s t) \cdot z_\alpha( s, t\xi) \]
+
+\[ z_\alpha(-s, t\xi) = z_{\alpha+\beta}(st, \xi) x_{-\beta}(-\epsilon s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(s t^2\xi^2) \cdot x_{-\alpha-\beta}(s t\xi^2) \cdot z_{-\beta}(-\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(-\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(s t) \]
+
+\[ z_\alpha(s, t\xi) = z_{\alpha+\beta}(-st, \xi) x_{-\beta}(\epsilon s\xi) \cdot x_\alpha(-s) \cdot x_{-\alpha}(-s t^2\xi^2) \cdot x_{-\alpha-\beta}(-s t\xi^2) \cdot z_{-\beta}(\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(- s t) \]
+\end{comment}
+Substituting $s := \epsilon f$, $t = -\epsilon g$ and $\xi = X$ in the fifth equality of Lemma~\ref{Zrels} and expressing the rightmost term through others we obtain (here $\beta$ is some other root such that $\alpha + \beta \in \Phi$): \[ z_\alpha(f, gX) = z_{\alpha+\beta}(-fg, X) x_{-\beta}(\epsilon fX) \cdot x_\alpha(-f) \cdot x_{-\alpha}(-f g^2X^2) \cdot x_{-\alpha-\beta}(-f gX^2) \cdot z_{-\beta}(\epsilon fX, \epsilon g) \cdot x_{\beta}(\epsilon fg^2X)  \cdot x_{\alpha+\beta}(- f g),\ \epsilon = N_{\alpha,\beta}.
+\]
+The factors in the right hand side have types: 2, 1, 2, 4, 1, 1, 1, 2. 
+It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the third factor $x_\alpha(-f)$, 
+while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
+\end{proof}
+
+\begin{lemma} \label{lem:Tulenbayev-formula}
+ $x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}$.
+\end{lemma}
+\begin{proof}
+Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
+ \begin{multline*}
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
+ = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
+ = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}. \qedhere
+\end{multline*}
+\end{proof}
+
+\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$. \end{corollary}
+\begin{proof}
+Suppose $g \in P_\alpha(m)$, then $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$ for which we already know that $S_\alpha(a, g_0) \in P(\alpha, 0)$.
+We need to verify that $h = S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)$ lies in $P\left(\alpha, \frac{m}{1 + am}\right)$, but from Lemmas~\ref{P0_conj}--\ref{lem:Tulenbayev-formula} and the antisymmetry of Steinberg symbols we obtain that:
+\begin{multline} h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
+= S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right).\qedhere \end{multline}
+\end{proof}
+
+\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P(\beta, 0)$. \end{lemma}
+\begin{proof}
+It suffices to verify the assertion for the generators $z_\gamma(Xf, g)$, $\gamma \in \Phi$.
+By our assumption $(\alpha, \beta) \geq 0$. 
+\end{proof}
+
+\subsection{The proof of the injectivity theorem}
+
+ \begin{comment}
+\begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
+\begin{proof}
+ Lol
+\end{proof}
+\end{comment}
+
+Let $P(\alpha, m)$ be a collection of subsets of $\overline{G}^{\geq 0}_M$ with the following properties:
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ \ g \in P(\alpha, m)\text{ for some $m \in M$}.\]
+
+$P(\alpha, a) P(\alpha, b) \subseteq P(\alpha, a + b)$.
+In particular, $P(\alpha, 0)$ is a subgroup.
+This hints us that there is a well-defined map $map_\alpha \colon G_M^{\geq 0} \to M$
+
+Let us show that this suffices to verify Steinberg additivity relation:
+
+Consider the set $V' = \St(\Phi, R[X, X^{-1}]) \times \St(\Phi, R[X^{-1}]) \times (1 + M)^*$.
+Denote by $V'_0$ the subset of $V'$ consisting of those $(g, h, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
+The the following operator is defined for those $(g, h, u)$, for which $\pi(g, h, u) \in P(\alpha, m)$
+\[ T_\alpha(aX^{-1})(g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
+                                         h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right),\ 
+                                         u(1 + am)\right).\]
+We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
+ (this operation is well defined for $V'_0$).
+
+\begin{multline}
+ T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim
+T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
+ = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
+ \begin{multline}
+h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\frac{bX^{-1}}{1 + \frac{bm}{1+am}}\right) = \\ = 
+ h \cdot x_\alpha\left(- \frac{aX^{-1}}{1 + am} - \frac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
+  h \cdot x_\alpha\left(- \frac{(a+b)X^{-1}}{1 + am + bm}\right).
+\end{multline}
+
+If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
+$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am})$
+%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
+\begin{multline}
+ T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
+ T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
+ \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
+ = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
+ \begin{multline}
+ h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
+    \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\frac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
+ = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am} + \frac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
+ \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}}{1 + am + bm'}\right).
+\end{multline}
+The latter expression is symmetric.
+
+If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
+\[x_\alpha(-a) \cdot S_\beta(-b, \pi(g, h, u)) h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')) \in P\left(\beta, \frac{m + am'}{1-bm}\right)\]
+
+\begin{comment}
+($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
+($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
+\begin{multline}
+\left(\begin{array}{ccc} 
+ 1 & 0 & -bX^{-1} \\
+ 0 & 1 & 0 \\
+ 0 & 0 & 1 
+ \end{array}\right)
+\left(\begin{array}{ccc} 
+ 1 & 0 & * \\
+ 0 & 1 & * \\
+ mX & m'X & 1 
+ \end{array}\right)
+ \left(\begin{array}{ccc} 
+ 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
+ 0 & 1 & 0 \\
+ 0 & 0 & 1 
+ \end{array}\right) = 
+ \left(\begin{array}{ccc} 
+ 1 - bm & -bm' & * \\
+ 0 & 1 & * \\
+ mX & m'X & (1 - mb)^{-1} 
+ \end{array}\right) = S_\beta(-b, g^+).
+\end{multline}
+\begin{multline}
+\left(\begin{array}{ccc} 
+ 1 & 0 & 0 \\
+ -a & 1 & 0 \\
+ 0 & 0 & 1 
+ \end{array}\right)
+ \left(\begin{array}{ccc} 
+ 1 - bm & - bm' & * \\
+ 0 & 1 & * \\
+ mX & m'X & (1 - bm)^{-1} 
+ \end{array}\right) = 
+ \left(\begin{array}{ccc} 
+ 1 - bm & - bm' & * \\
+ - a + abm & 1 + abm' & * \\
+ mX & m'X & (1 - bm)^{-1} 
+ \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
+\end{multline}
+\begin{multline}
+ \left(\begin{array}{ccc} 
+ 1 - bm & - bm' & * \\
+ - a + abm & 1 + abm' & * \\
+ mX & m'X & (1 - bm)^{-1} 
+ \end{array}\right)
+ \left(\begin{array}{ccc} 
+ (1  - bm)^{-1} & 0 & 0 \\
+ 0 & 1 & 0 \\
+ 0 & 0 & 1 - bm 
+ \end{array}\right)
+\left(\begin{array}{ccc} 
+ 1 + abm' & 0 & 0 \\
+ 0 & (1 + abm')^{-1} & 0 \\
+ 0 & 0 & 1 
+ \end{array}\right)
+ \left(\begin{array}{ccc} 
+ 1 & 0 & 0 \\
+ a(1 + abm') & 1 & 0 \\
+ 0 & 0 & 1 
+ \end{array}\right) = \\
+ = 
+ \left(\begin{array}{ccc} 
+ 1 & - \frac{bm'}{1 + abm'} & * \\
+ 0 & 1 & * \\
+ \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
+ \end{array}\right)
+\end{multline}
+
+There is still a mistake in the last implication :(
+\end{comment}
+Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
+\begin{multline}
+[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
+ T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
+ \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
+ = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
+ \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
+ \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
+ = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
+ h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
+\end{multline}
+
+Full axioms
+\begin{enumerate}
+ \item $(+)$ $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
+ \item $(+)$ if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
+ %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
+ \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then
+$S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
+ \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
+ $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
+ \item if $\alpha + \beta \not \in \Phi$ then ???;
+\end{enumerate}
+
+Restricted axioms:
+\begin{enumerate}
+ \item $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
+ \item if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
+% \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
+ \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
+$S_\alpha(a, g) \in P(\beta, 0);$
+ \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
+ $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
+ \item if $\alpha + \beta \not \in \Phi$ then ???;
+\end{enumerate}
+
+Some implication: suppose $g \in P(\alpha, 0)$, then $g x_{-\alpha}(mX) \in P(\alpha, m)$ by the definition of the latter.
+\begin{multline}S(\alpha, g \cdot x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot g \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
+= S(\alpha, g) \cdot x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha % = \\
+%= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\} \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
+= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am). 
+\end{multline}
+
+Let us show that F3 and F4 hold automatically.
+Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
+$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
+Then 
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
+  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
+We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
 

### 2019-04-26 dl-paper.tex
Added Lemma on properties of elements C

@@
 
-\subsection{Miscellanea}
+\subsection{Some elementary lemmas}
+\begin{comment}
 The following result was proved in \cite[Proposition~3.2]{Ste13}.
@@
 \end{lemma}
+\end{comment}
+
+\begin{comment}
+Hall-Witt identity
+\[ [[ y^{-1}, x], z] ^ {y^{-1}}  [[ z^{-1}, y], x] ^ {z^{-1}}  [[ x^{-1}, z], y] ^ {x^{-1}} = 1 \]
+\[ [[ y^{-1}, x], z]  \cdot [[ z^{-1}, y], x] ^ {z^{-1}y} \cdot  [[ x^{-1}, z], y] ^ {x^{-1}y} = 1. \]
+\[ [[ z^{-1}, y^{-1}], x] ^ {z^{-1}y^{-1}} \cdot  [[ x^{-1}, z], y^{-1}] ^ {x^{-1}y^{-1}} = [z, [ y, x]] . \]
+\[  . \]
+\end{comment}
+Throughtout this section $A$ denotes an arbitary ring and $I, J$ two its ideals and $\Phi$ a simply laced root system.
+
+The following lemma summarizes basic properties of structure constants used in the computations below.
+\begin{lemma} Suppose $\alpha, \beta \in \Phi$ are such that $\alpha+\beta \in \Phi$.
+\begin{enumerate}\label{lem:structure-constants}
+ \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
+ \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
+ \item $N_{\alpha, \beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}.$
+\end{enumerate}
+\end{lemma}
+\begin{proof} See~\cite[\S~14]{VP}. \end{proof}
+
+We define the following two families of elements of $\St(\Phi, A)$:
+\begin{itemize}
+ \item $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$ defined for $\xi \in A$, $s \in I$;
+ \item $c_\alpha(s, t) = [x_\alpha(s), x_{-\alpha}(t)]$ defined for $s \in I$, $t \in J$.
+\end{itemize}
+
+\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in A$, $s\in I$:
+\begin{enumerate} 
+\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
+\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
+\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
+\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
+\item\label{Z5} $z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(N_{\alpha,\beta}s) \cdot x_{-\alpha}(N_{\alpha,\beta}st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(N_{\alpha,\beta} s, -N_{\alpha, \beta}t\xi)$ for any $\alpha, \beta$ such that $\alpha+\beta\in\Phi$.
+\end{enumerate} \end{lemma}
+\begin{proof}
+The first four assertions are contained in~\cite[Lemma~9]{S15}. For the proof of the last formula set $\gamma = \alpha + \beta$.
+Now direct computation using~\cref{lem:structure-constants} shows that:
+\begin{multline} \nonumber z_{\gamma}(N_{\alpha,\beta}st, \xi) = 
+[x_\alpha(s)^{x_{-\gamma}(\xi)}, x_\beta(t)^{x_{-\gamma}(\xi)}] = [x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s),\ x_{-\alpha}(N_{\beta, -\gamma}t\xi) \cdot x_\beta(t)] = \\ = x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot \left( x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s)\right)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi) \cdot x_\beta(-t)} = \\
+= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi)} \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi)^ {x_\beta(-t)} = \\
+= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(-N_{\alpha, -\gamma}N_{\beta, -\gamma}st^2\xi^2) \cdot x_{-\gamma}(-N_{-\beta, -\alpha} N_{\alpha, -\gamma} N_{\beta, -\gamma}st\xi^2) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t) \cdot \\ \cdot x_{\beta}(-N_{\beta,-\gamma}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi) =\\ = x_{-\beta}(-N_{\alpha, \beta} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(st^2\xi^2) \cdot x_{-\gamma}(-N_{\alpha, \beta} st\xi^2) \cdot z_{-\beta}(-N_{\alpha, \beta} s\xi, -t) \cdot x_{\beta}(-N_{\alpha, \beta}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\alpha, \beta}t\xi).
+\qedhere
+\end{multline} \end{proof}
+
+In the following lemma we will need the following variant of Hall--Witt identity:
+\begin{equation} \label{HW-variant} [x, [ y, z]] = \left([[ x^{-1}, y^{-1}], z] ^ {x^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}}\right)^{y^{-1}}.\end{equation}
+
+\begin{lemma} \label{Crels}
+The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in A$.
+ \begin{enumerate}
+  \item \label{C1} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi)$ if $\alpha-\beta \in \Phi$;
+  \item \label{C2} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(st\xi + s^2t^2\xi) \cdot x_{-\alpha-\beta}(N_{\alpha, \beta}st^2\xi)$ if $\alpha+\beta \in \Phi$;
+  \item \label{C3} $[c_\beta(s, t), x_{-\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;
+  \item \label{C4} $c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot c_{\alpha}(N_{\alpha, \beta}s\xi, -N_{\alpha,\beta}t)^{-1} \cdot x_{-\beta}(-st\xi^2)$ if $\alpha+\beta\in\Phi$.
+ \end{enumerate}
+\end{lemma}
+\begin{proof}
+To verify~\eqref{C1} suppose $\alpha - \beta \in \Phi$ and compute
+\begin{multline} \nonumber [c_{\beta}(s, t), x_{-\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta-\alpha}(N_{-\alpha, \beta} s\xi)] = \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\beta-\alpha}(N_{-\alpha, \beta}s\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi). \end{multline}
+
+Now suppose $\alpha+\beta \in \Phi$. Using~\eqref{HW-variant} we obtain:
+\begin{multline} \nonumber
+[x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = 
+\left([[ x_{-\alpha}(-\xi), x_\beta(-s)], x_{-\beta}(t)] ^ {x_{-\alpha}(-\xi)} \cdot  [[ x_{-\beta}(-t), x_{-\alpha}(\xi)], x_\beta(-s)] ^ {x_{-\beta}(-t)}\right)^{x_\beta(-s)} =  \\ = [x_{-\beta-\alpha}(-N_{-\beta,-\alpha}t\xi), x_\beta(-s)] ^ {x_{-\beta}(-t) x_\beta(-s)} = x_{-\alpha}(-st\xi) ^ {x_{-\beta}(-t) x_\beta(-s)} = \\
+= (x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi))^{x_\beta(-s)} = x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi - s^2t^2\xi),
+\end{multline} which implies~\eqref{C2}.
+
+Finally, relation~\eqref{C4} can be verified by the following computation involving identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$:
+\begin{multline} \nonumber
+ [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(N_{-\alpha,-\beta}t), x_{-\beta}(\xi)]] = \\
+  = \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(-N_{-\alpha,-\beta}t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(N_{\alpha,\beta}t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(N_{\alpha,\beta}t)} = \\ =
+  [ x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [ x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha}(N_{\alpha,\beta}t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(N_{\alpha,\beta}t)}  = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [ x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha}(N_{\alpha,\beta}t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(N_{\alpha,\beta}t)} = \\ =
+  [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [x_{-\alpha}(-N_{\alpha,\beta}t), x_{\alpha}(N_{\alpha,\beta}s\xi)] \cdot [x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha-\beta}(t\xi)] = \\
+  [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot c_{\alpha}(N_{\alpha, \beta}s\xi, -N_{\alpha,\beta}t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
+\end{multline}
+
+\begin{comment}
+\begin{multline} 
+ [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
+\end{multline}
+\end{comment}
+\end{proof}
 
@@
 
-\subsection{Some elementary lemmas}
-\begin{comment}
-Hall-Witt identity
-\[ [[ y^{-1}, x], z] ^ {y^{-1}}  [[ z^{-1}, y], x] ^ {z^{-1}}  [[ x^{-1}, z], y] ^ {x^{-1}} = 1 \]
-\[ [[ y^{-1}, x], z]  \cdot [[ z^{-1}, y], x] ^ {z^{-1}y} \cdot  [[ x^{-1}, z], y] ^ {x^{-1}y} = 1. \]
-\[ [[ z^{-1}, y^{-1}], x] ^ {z^{-1}y^{-1}} \cdot  [[ x^{-1}, z], y^{-1}] ^ {x^{-1}y^{-1}} = [z, [ y, x]] . \]
-\[  . \]
-\end{comment}
-
-The following lemma summarizes basic properties of structure constants used in our computations below.
-\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta \in \Phi$ are such that $\alpha+\beta = \gamma \in \Phi$.
-\begin{enumerate}
- \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
- \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
- \item $N_{\alpha, \beta} = N_{\beta, \gamma} = N_{\gamma, \alpha}.$
-\end{enumerate}
-\end{lemma}
-\begin{proof} See~\cite[\S~14]{VP}. \end{proof}
-
-Recall that $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$.
-\begin{lemma}\label{Zrels} Let $\Phi$ be a simply laced root system and $\alpha,\beta\in \Phi$ be a pair of roots.
-The elements $z_\alpha(s, \xi)$ satisfy the following relations (everywhere below $\xi, \eta\in R$, $s\in I$):
-\begin{enumerate} 
-\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
-\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
-\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
-\item\label{Z4} $z_{\gamma}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\gamma}(s, \xi)\ \text{if}\ \gamma\perp\alpha$.
-\item\label{Z5} $z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(N_{\alpha,\beta}s) \cdot x_{-\alpha}(N_{\alpha,\beta}st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(N_{\alpha,\beta} s, -N_{\alpha, \beta}t\xi).$
-\end{enumerate} \end{lemma}
-\begin{proof}
-The first four assertions are contained in~\cite[Lemma~9]{S15}. For the proof of the last formula set $\gamma = \alpha + \beta$ and compute:
-\begin{multline} z_{\gamma}(N_{\alpha,\beta}st, \xi) = 
-[x_\alpha(s)^{x_{-\gamma}(\xi)}, x_\beta(t)^{x_{-\gamma}(\xi)}] = [x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s),\ x_{-\alpha}(N_{\beta, -\gamma}t\xi) \cdot x_\beta(t)] = \\ = x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot \left( x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s)\right)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi) \cdot x_\beta(-t)} = \\
-= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi)} \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi)^ {x_\beta(-t)} = \\
-= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(-N_{\alpha, -\gamma}N_{\beta, -\gamma}st^2\xi^2) \cdot x_{-\gamma}(-N_{-\beta, -\alpha} N_{\alpha, -\gamma} N_{\beta, -\gamma}st\xi^2) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t) \cdot \\ \cdot x_{\beta}(-N_{\beta,-\gamma}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi) =\\ = x_{-\beta}(-N_{\alpha, \beta} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(st^2\xi^2) \cdot x_{-\gamma}(-N_{\alpha, \beta} st\xi^2) \cdot z_{-\beta}(-N_{\alpha, \beta} s\xi, -t) \cdot x_{\beta}(-N_{\alpha, \beta}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\alpha, \beta}t\xi).
-\qedhere
-\end{multline}  
-In the last equality we invoked the standard properties of structure constants (see e.\,g.
-formulas in Vavilov-Plotkin \S~14 which imply in our case that $N_{\alpha, \beta} = N_{\beta,-\gamma} = N_{-\gamma, \alpha} = -N_{\alpha, -\gamma}$).
-\end{proof}
-
-Using a variant of Hall-Witt identity: $[x, [ y, z]] = [[ x^{-1}, y^{-1}], z] ^ {x^{-1}y^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}y^{-1}}$ we compute
-\begin{multline}
- [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
-\end{multline}
-
 \subsection{Computation of the kernel of the map of evaluation at $0$.}
@@
 i.\,e. $g = x_\beta(\xi)$, $\eta \in R[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.
-
-Set $c_{\alpha,\beta}(m,\xi,\eta) = [[x_{\alpha}(m), x_{-\alpha}(X\xi)], x_\beta(\eta)]$.
-If $\alpha + \beta \not\in \Phi$, $\alpha - \beta \not \in \Phi$ then, obviously, one has $c_{\alpha,\beta}(m,\xi,\eta) = 1$.
-Now suppose $\alpha + \beta \in \Phi$, $\alpha - \beta \in \Phi$. We have:
-\begin{multline} \nonumber c_{\alpha,\beta}(m,\xi,\eta) = [x_{\alpha}(m), x_{-\alpha}(X\xi)] [x_{-\alpha}(X\xi), x_{\alpha}(m)x_{\alpha+\beta}(N_{\beta,\alpha} m\eta)] = \\
- = {}^{x_\alpha(m)}\![x_{-\alpha}(X\xi), x_{\alpha + \beta}(N_{\beta, \alpha}m\eta)] = x_{\beta}(N_{\beta,\alpha} N_{-\alpha, \alpha+\beta} mX\xi\eta) x_{\alpha+\beta}(N_{\alpha,\beta}N_{\beta,\alpha}N_{-\alpha, \alpha+\beta}m^2X\xi\eta).
-\end{multline}
-It is clear that the expression in the right-hand side belongs to $\St(\Phi, R[X], XM[X])$. In the case $\alpha - \beta \in \Phi$, $\alpha + \beta \not \in \Phi$ the computation is similar.
-{\bf TODO:} we have to consider more cases if we want to make the result valid for nonsimply-laced root systems.
 \end{proof}

### 2019-04-26 dl-paper.tex
Beautify identities in Lemmas 5-6

@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item\label{Z5} $z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(N_{\alpha,\beta}s) \cdot x_{-\alpha}(N_{\alpha,\beta}st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(N_{\alpha,\beta} s, -N_{\alpha, \beta}t\xi)$ for any $\alpha, \beta$ such that $\alpha+\beta\in\Phi$.
+\item\label{Z5} If $\alpha+\beta\in\Phi$, then the following relation holds (in which $\epsilon = N_{\alpha,\beta}$):
+\begin{multline} \nonumber z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(\epsilon s) \cdot x_{-\alpha}(\epsilon st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t)\cdot \\ \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(\epsilon s, -\epsilon t\xi).\end{multline}
 \end{enumerate} \end{lemma}
 \begin{proof}
-The first four assertions are contained in~\cite[Lemma~9]{S15}. For the proof of the last formula set $\gamma = \alpha + \beta$.
+The first four assertions are contained in~\cite[Lemma~9]{S15}.
+To prove the remaining assertion use direct computation (in which $\epsilon = N_{}$):
+\begin{multline} \nonumber
+  z_{\alpha+\beta}(s\eta, \xi) = 
+\end{multline}
+
+For the proof of the last formula set $\gamma = \alpha + \beta$.
 Now direct computation using~\cref{lem:structure-constants} shows that:
@@
   \item \label{C3} $[c_\beta(s, t), x_{-\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;
-  \item \label{C4} $c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot c_{\alpha}(N_{\alpha, \beta}s\xi, -N_{\alpha,\beta}t)^{-1} \cdot x_{-\beta}(-st\xi^2)$ if $\alpha+\beta\in\Phi$.
+  \item \label{C4} If $\alpha+\beta\in\Phi$ then the following relation holds (in which $\epsilon = N_{\alpha,\beta}$):
+  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2).\]
  \end{enumerate}
@@
 
-Now suppose $\alpha+\beta \in \Phi$. Using~\eqref{HW-variant} we obtain:
-\begin{multline} \nonumber
+Now suppose $\alpha+\beta \in \Phi$, from~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
 [x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = 
@@
 
-Finally, relation~\eqref{C4} can be verified by the following computation involving identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$:
-\begin{multline} \nonumber
- [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(N_{-\alpha,-\beta}t), x_{-\beta}(\xi)]] = \\
-  = \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(-N_{-\alpha,-\beta}t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(N_{\alpha,\beta}t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(N_{\alpha,\beta}t)} = \\ =
-  [ x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [ x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha}(N_{\alpha,\beta}t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(N_{\alpha,\beta}t)}  = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [ x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha}(N_{\alpha,\beta}t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(N_{\alpha,\beta}t)} = \\ =
-  [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot  [x_{-\alpha}(-N_{\alpha,\beta}t), x_{\alpha}(N_{\alpha,\beta}s\xi)] \cdot [x_{\alpha}(N_{\alpha,\beta}s\xi), x_{-\alpha-\beta}(t\xi)] = \\
-  [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(N_{\alpha,\beta}t)} \cdot c_{\alpha}(N_{\alpha, \beta}s\xi, -N_{\alpha,\beta}t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
+Finally, relation~\eqref{C4} can be verified by the direct computation involving identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ (everywhere below $\epsilon = N_{\alpha, \beta}$):
+\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ = \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\ = [ x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2).
+\qedhere
 \end{multline}

### 2019-04-27 dl-paper.tex
Fixed Lemma 5

@@
 \item\label{Z5} If $\alpha+\beta\in\Phi$, then the following relation holds (in which $\epsilon = N_{\alpha,\beta}$):
-\begin{multline} \nonumber z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(\epsilon s) \cdot x_{-\alpha}(\epsilon st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t)\cdot \\ \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(\epsilon s, -\epsilon t\xi).\end{multline}
+\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
+  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta).\end{multline}
 \end{enumerate} \end{lemma}
 \begin{proof}
-The first four assertions are contained in~\cite[Lemma~9]{S15}.
-To prove the remaining assertion use direct computation (in which $\epsilon = N_{}$):
+The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
+Direct computation shows that
 \begin{multline} \nonumber
-  z_{\alpha+\beta}(s\eta, \xi) = 
+  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
+  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
+  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
 \end{multline} 
-
-For the proof of the last formula set $\gamma = \alpha + \beta$.
-Now direct computation using~\cref{lem:structure-constants} shows that:
-\begin{multline} \nonumber z_{\gamma}(N_{\alpha,\beta}st, \xi) = 
-[x_\alpha(s)^{x_{-\gamma}(\xi)}, x_\beta(t)^{x_{-\gamma}(\xi)}] = [x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s),\ x_{-\alpha}(N_{\beta, -\gamma}t\xi) \cdot x_\beta(t)] = \\ = x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot \left( x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s)\right)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi) \cdot x_\beta(-t)} = \\
-= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi)} \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi)^ {x_\beta(-t)} = \\
-= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(-N_{\alpha, -\gamma}N_{\beta, -\gamma}st^2\xi^2) \cdot x_{-\gamma}(-N_{-\beta, -\alpha} N_{\alpha, -\gamma} N_{\beta, -\gamma}st\xi^2) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t) \cdot \\ \cdot x_{\beta}(-N_{\beta,-\gamma}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi) =\\ = x_{-\beta}(-N_{\alpha, \beta} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(st^2\xi^2) \cdot x_{-\gamma}(-N_{\alpha, \beta} st\xi^2) \cdot z_{-\beta}(-N_{\alpha, \beta} s\xi, -t) \cdot x_{\beta}(-N_{\alpha, \beta}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\alpha, \beta}t\xi).
-\qedhere
-\end{multline} \end{proof}
+and the required assertion follows from~\eqref{Z2}.
+\end{proof}
 
@@
   \item \label{C3} $[c_\beta(s, t), x_{-\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;
-  \item \label{C4} If $\alpha+\beta\in\Phi$ then the following relation holds (in which $\epsilon = N_{\alpha,\beta}$):
-  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2).\]
+  \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
+  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
+  where $\epsilon = N_{\alpha,\beta}$.
  \end{enumerate}
@@
 Now suppose $\alpha+\beta \in \Phi$, from~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
-[x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = 
-\left([[ x_{-\alpha}(-\xi), x_\beta(-s)], x_{-\beta}(t)] ^ {x_{-\alpha}(-\xi)} \cdot  [[ x_{-\beta}(-t), x_{-\alpha}(\xi)], x_\beta(-s)] ^ {x_{-\beta}(-t)}\right)^{x_\beta(-s)} =  \\ = [x_{-\beta-\alpha}(-N_{-\beta,-\alpha}t\xi), x_\beta(-s)] ^ {x_{-\beta}(-t) x_\beta(-s)} = x_{-\alpha}(-st\xi) ^ {x_{-\beta}(-t) x_\beta(-s)} = \\
+[x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = \\ 
+= \left([[ x_{-\alpha}(-\xi), x_\beta(-s)], x_{-\beta}(t)] ^ {x_{-\alpha}(-\xi)} \cdot  [[ x_{-\beta}(-t), x_{-\alpha}(\xi)], x_\beta(-s)] ^ {x_{-\beta}(-t)}\right)^{x_\beta(-s)} =  \\ = [x_{-\beta-\alpha}(-N_{-\beta,-\alpha}t\xi), x_\beta(-s)] ^ {x_{-\beta}(-t) x_\beta(-s)} = x_{-\alpha}(-st\xi) ^ {x_{-\beta}(-t) x_\beta(-s)} = \\
 = (x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi))^{x_\beta(-s)} = x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi - s^2t^2\xi),

### 2019-04-28 dl-paper.tex
Fixed signs in Lemma 6

@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item\label{Z5} If $\alpha+\beta\in\Phi$, then the following relation holds (in which $\epsilon = N_{\alpha,\beta}$):
+\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
 \begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
-  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta).\end{multline}
+  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
 \end{enumerate} \end{lemma}
@@
   \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
-  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
+  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
   where $\epsilon = N_{\alpha,\beta}$.
@@
 
-Now suppose $\alpha+\beta \in \Phi$, from~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
+Now suppose $\alpha+\beta \in \Phi$. From~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
 [x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = \\ 
@@
 
-Finally, relation~\eqref{C4} can be verified by the direct computation involving identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ (everywhere below $\epsilon = N_{\alpha, \beta}$):
-\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ = \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\ = [ x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\ = [x_{\beta}(-st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2).
-\qedhere
+Finally, relation~\eqref{C4} can be verified by the following direct computation, which involves identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$:
+\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
+= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
+= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
+= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
+= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
+= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
 \end{multline}

### 2019-04-28 dl-paper.tex
Editing 4.1

@@
 If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
-\begin{equation*}
+\begin{equation} \label{relSteinberg-def}
  \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.}
-\end{equation*}
+\end{equation}
 The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits.
@@
 
-Throughout this section $\Phi$ is a simply-laced irreducible root system and $R$ is a local ring with maximal ideal $M$.
-We denote by $B$ the ring $M[t] + R[t^{-1}]$ considered as a graded subring of $R[t, t^{-1}]$.
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[t], M[t]) \to \St(\Phi, R[t, t^{-1}])$ and by
- $G^{\leq 0}$ the group $\St(\Phi, R[t^{-1}])$.
+Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.
+We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
+ $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
 
-\[ \xymatrix{ \overline{\St}(\Phi, R, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
-              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, R[t, t^{-1}]), } \]
+\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
+              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \]
 
 \subsection{Computation of the kernel of the map of evaluation at $0$.}
-\begin{lemma} Denote by $C$ the mutual commutator subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$.
-Then one has \[\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot \overline{\St}(\Phi, A[X], XM[X]) \cdot C.\] 
-Consequently, the composite of the two factors in the right-hand side of the above formula coincides with the subgroup $I$ defined as 
- the intersection $\overline{\St}(\Phi, A[X], M[X]) \cap \overline{\St}(\Phi, A[X], XA[X])$ (or alternatively, as the kernel of the evaluation map $\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$).
+%TODO: Do we need any specific conditions on \Phi? Specify them.
+For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
+We also denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
+It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
+
+The aim of this subsection is to describe the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
+induced by the ring homomorphism of evaluation at $0$. Clearly, this kernel, denote it by $K$, contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$, however, apriori it may be larger,
+ so our goal will be to describe the explicit extra elements sufficient to generate it.
+
+Obviously, $ev_{X=0}^*$ admits a section hence we can consider $\overline{\St}(\Phi, A, M)$ as a subgroup of $\overline{\St}(\Phi, A[X], M[X])$,
+ moreover, the following decomposition holds:
+\begin{equation} \label{relZero-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K.\end{equation}
+\begin{lemma} 
+The following decomposition holds
+ \[ K = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] 
 \end{lemma}
 \begin{proof}
- Take $g \in \overline{\St}(\Phi, A[X], M[X])$ and write it as $g = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
- It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
+ Fix $g \in K$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+ It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
 
- Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can written as $z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0))$.
- Using the fact that the subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\St(\Phi, A, M)$ (this follows e.\,g.
-from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $g(0) = g_1(0)$ modulo $C$, which implies the first assertion.
+ Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
+ Since the subgroup $C = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
+ (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C$,
+ which implies the assertion. \qedhere
 
- Denote by $H$ the composite of $C$ and $\overline{\St}(\Phi, A[X], XM[X])$.
+ %Denote by $H$ the composite of $C$ and $\overline{\St}(\Phi, A[X], XM[X])$.
 It is clear that $H \subseteq I$.
 The reverse inclusion follows from the above argument and the fact that for $g \in I$ one has $g(0)=1$.
-\qedhere \end{proof}
+\qedhere
+\end{proof}
+ \begin{lemma} If $A$ is a local ring with maximal ideal $M$ then \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot M(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{lemma}
+ \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}
 
- \begin{lemma}
-   If $R$ is a local ring with maximal ideal $M$ then $\overline{\St}(\Phi, R, M) = U(\Phi^+, M) \cdot M(\Phi, R, M) \cdot U(\Phi^-, M)$.
- \end{lemma}
+\begin{corollary} For $A$, $M$ as above holds
+ \[\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right].\]
+\end{corollary}
 \begin{proof}
-  See Theorem~2.4 of~M. Stein's paper on surjective stability in dimension 0.
+ Notice first that the generators of $M(\Phi, A, M)$ normalize both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$, see~\eqref{eq:conj-h-x}.
+ Now for $g \in \St(\Phi, XR[X])$, $h \in M(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+ \[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)]. \qedhere\]
 \end{proof}
 
-\begin{corollary} For $R$, $M$ as above holds
- $\left[\St(\Phi, XR[X]), \overline{\St}(\Phi, R, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XR[X]), \St(\Phi, M)\right]$.
+\begin{corollary} For $A$ and $M$ as above the subgroup $K$ is generated as a group by its subgroup $\St(\Phi, A[X], XM[X])$ and
+ the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. 
 \end{corollary}
 \begin{proof}
- Notice first that the generators of $M(\Phi, R, M)$ normalize both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ (see eq:conj-h-x).
- Now for $g \in \St(\Phi, XR[X])$, $h \in M(\Phi, R, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
- \[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)]. \qedhere\]
-\end{proof}
-
-\begin{corollary} For $R$ and $M$ as above the subgroup $I$ is generated as a group by its subgroup $\St(\Phi, R[X], XM[X])$ and
- the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in R[X]$, $\alpha \in \Phi$. 
-\end{corollary}
-\begin{proof}
-By the above lemmata one has $I \subseteq \St(\Phi, R[X], XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)].$
-It is clear that modulo $\St(\Phi, R[X], XM[X])$ the commutator subgroup $[\St(\Phi, XR[X]), \St(\Phi, M)]$ is generated
- by all $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, $m \in M$, $\xi \in R[X]$, where $g \in \St(\Phi, M + XR[X])$.
-To verify the assertion, therefore, it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, R[X], XM[X])$.
-Moreover, since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a generator of $\St(\Phi, R[X])$,
-i.\,e. $g = x_\beta(\xi)$, $\eta \in R[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.
+By the above lemmata one has $K \subseteq \St(\Phi, A[X], XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)].$
+It is clear that modulo $\St(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated
+ by all $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, $m \in M$, $\xi \in A[X]$, where $g \in \St(\Phi, M + XA[X])$.
+To verify the assertion, therefore, it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, A[X], XM[X])$.
+Moreover, since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a generator of $\St(\Phi, A[X])$,
+i.\,e. $g = x_\beta(\xi)$, $\eta \in A[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.
 \end{proof}

### 2019-04-29 dl-paper.tex
Finished rewriting 4.1

@@
 \subsection{Computation of the kernel of the map of evaluation at $0$.}
-%TODO: Do we need any specific conditions on \Phi? Specify them.
 For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
@@
 It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
+We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^*$, $v \in R^*$, $\alpha\in \Phi$.
 
 The aim of this subsection is to describe the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
-induced by the ring homomorphism of evaluation at $0$. Clearly, this kernel, denote it by $K$, contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$, however, apriori it may be larger,
- so our goal will be to describe the explicit extra elements sufficient to generate it.
+induced by the ring homomorphism of evaluation at $0$.
+Clearly, this kernel, denote it by $K(A[X], M[X])$, contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$, however, apriori it may be larger, so our goal will be to describe the explicit extra elements sufficient to generate it.
 
-Obviously, $ev_{X=0}^*$ admits a section hence we can consider $\overline{\St}(\Phi, A, M)$ as a subgroup of $\overline{\St}(\Phi, A[X], M[X])$,
+Obviously, $ev_{X=0}^*$ admits a section hence we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
  moreover, the following decomposition holds:
-\begin{equation} \label{relZero-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K.\end{equation}
+\begin{equation} \label{relZero-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).\end{equation}
 \begin{lemma} 
 The following decomposition holds
- \[ K = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] 
+ \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] 
 \end{lemma}
 \begin{proof}
- Fix $g \in K$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+ Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
  It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
@@
  which implies the assertion. \qedhere
+\end{proof}
 
- %Denote by $H$ the composite of $C$ and $\overline{\St}(\Phi, A[X], XM[X])$.
-It is clear that $H \subseteq I$.
-The reverse inclusion follows from the above argument and the fact that for $g \in I$ one has $g(0)=1$.
-\qedhere
+ \begin{theorem}[Stein] \label{thmStein} For a local ring $A$ with maximal ideal $M$ holds \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
 \end{proof}
- \begin{lemma} If $A$ is a local ring with maximal ideal $M$ then \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot M(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{lemma}
- \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}
 
-\begin{corollary} For $A$, $M$ as above holds
- \[\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right].\]
+\begin{prop} \label{Kgen}
+For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\St(\Phi, A[X], XM[X])$ and
+ the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
+\begin{proof}
+ Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \St(\Phi, XM[X])$.
+
+Now for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)],\]
+hence $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right]$ and therefore \[K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \St(\Phi, M)\right].\]
+
+It is clear that modulo $\St(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
+Thus, to verify the assertion it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, A[X], XM[X])$.
+Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
+Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, but in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}.
+\end{proof}
+
+\begin{corollary} \label{Kgen-strong}
+ For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\St(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(f, \eta)$, $f \in M[X]$, $\eta \in XA[X]$.
 \end{corollary}
 \begin{proof}
- Notice first that the generators of $M(\Phi, A, M)$ normalize both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$, see~\eqref{eq:conj-h-x}.
- Now for $g \in \St(\Phi, XR[X])$, $h \in M(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
- \[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)]. \qedhere\]
-\end{proof}
-
-\begin{corollary} For $A$ and $M$ as above the subgroup $K$ is generated as a group by its subgroup $\St(\Phi, A[X], XM[X])$ and
- the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. 
-\end{corollary}
-\begin{proof}
-By the above lemmata one has $K \subseteq \St(\Phi, A[X], XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)].$
-It is clear that modulo $\St(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated
- by all $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, $m \in M$, $\xi \in A[X]$, where $g \in \St(\Phi, M + XA[X])$.
-To verify the assertion, therefore, it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, A[X], XM[X])$.
-Moreover, since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a generator of $\St(\Phi, A[X])$,
-i.\,e. $g = x_\beta(\xi)$, $\eta \in A[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.
+ Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root.
+Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
+Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$ belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
+Similar argument also works for the negative roots.
+The required assertion now follows from the above proposition.
 \end{proof}

### 2019-04-29 dl-paper.tex
Fixed Lemma 9

@@
 \begin{df} \label{defP0}
-Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, R[X])$ under the
- map induced by the embedding $R[X] \subseteq R[X, X^{-1}]$:
+Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
+ map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
 \begin{enumerate}
- \item $z_{\beta}(Xf, g), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, Xg),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
- \item $z_{\gamma}(f, g),\ \alpha \perp \gamma;$
+ \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
+ \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
+ \item $z_{\gamma}(f, \xi),\ \alpha \perp \gamma;$
  \item $x_{-\alpha}(X^2f),$
- \item $[x_{\beta}(m), x_{-\beta}(Xg)],\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi$.
 \end{enumerate}
-In the above formulae and below we assume that $f \in M[X]$ and $g \in R[X]$. \end{df}
+In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$. \end{df}
 
-Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
 The following lemma shows that this subgroup is sufficiently large.
-\begin{lemma} The subgroup $P_\alpha(*)$ contains the image of the subgroup $\St(\Phi, R[X], XM[X])$ in $\St(\Phi, R[X, X^{-1}])$. \end{lemma}
+\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
 \begin{proof}
-Clearly $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, g)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $g\in R[X]$.
-The assertion now easily follows from Stepanov's theorem. This can also be verified in a straightforward manner without Stepanov theorem.
+Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$.
+Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we conclude from this that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
+Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.
 
-Now let us verify the assertion for the generators $c_\beta(m, \xi) = [x_\beta(m), x_{-\beta}(X\xi)] = x_\beta(m) \cdot z_{\beta}(-m, -X\xi)$.
-It is clear that $c_\beta(m, \xi)$ are contained in $P_\alpha(*)$ in the cases $\beta \perp \alpha$, $\alpha - \beta \in \Phi \cup \{0\}$.
-There are problems: 1) for the generator $c_{-\alpha}(m, \xi)$, 2) for the generator $c_\beta(m, \xi)$, $\alpha + \beta \in \Phi$.
-
+Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
+But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3.
 \begin{comment}

### 2019-04-29 dl-paper.tex
Fixed signs in the proof of Lemma 12

@@
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator of $P_\alpha(0)$ listed in~Definition~\ref{defP0} still belongs to $P_\alpha(0)$.
-The assertion is obvious for the generators of types (3) and (4).
+The assertion is obvious for the generators of type (3) and (4).
 
@@
 \[ z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2fg ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2fg^2) \cdot z_{\beta}(Xf, g), \]
-the latter expression, clearly, is a product of generators of types $4, 1, 1$.
+the latter expression, clearly, is a product of generators of type $4, 1, 1$.
 \end{proof}
@@
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. 
-The latter fact allows to make the following definition.
+From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
 
 \begin{df}
-Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, R[t, t^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
 \[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] 
@@
 
-\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in R$. \end{lemma}
-\begin{proof} As before, we need to verify that the conjugate of every generator of $P_\alpha(0)$ lies in $P_\alpha(0)$.
+\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
+\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator of $P_\alpha(0)$ lies in $P_\alpha(0)$.
 First of all, consider the case $\alpha + \beta \in \Phi$ (only possible for the generator of the first type):
@@
 
-Let us verify the assertion for the generator of type (4). Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke Lemma~\ref{Zrels}:
-\[z_{-\alpha}(X^2f, aX^{-1}) = x_{-\beta}(-a) \cdot x_{-\alpha-\beta}(\epsilon X) \cdot x_{\alpha+\beta}(\epsilon Xf^2a^2) \cdot x_{\alpha}(-a^2f) \cdot z_{-\beta}(-a, -Xf) \cdot x_{\beta}(-aX^2f^2)  \cdot x_{-\alpha}(-X^2f) \cdot z_{-\alpha-\beta}(\epsilon X, -\epsilon af), \] where $\epsilon = N_{-\alpha-\beta,\beta}$.
-It is clear that the latter expression is a product of generators of types: 2, 1, 1, 2, 2, 1, 1, 1, respectively.
+Let us verify the assertion for the generator of type (4).
+Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke~\eqref{Z5} of~\cref{Zrels} substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$:
+\begin{multline} \nonumber
+ z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(f a X^2) \cdot x_{-\alpha}(X^2f) \cdot \\ \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon Xf a^2) \cdot x_{\alpha}(- f a^2) \cdot z_{-\beta}(f a, -X),
+\end{multline}
+where $\epsilon = N_{-\alpha-\beta,\beta}$. Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.
 
-It remains to verify the assertion for the generator $z_\alpha(f, gX)$.
-\begin{comment}
-\[ z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(\epsilon s) \cdot x_{-\alpha}(\epsilon st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(\epsilon s, -\epsilon t\xi) \]
-
-\[ z_{\alpha+\beta}(- s t, \xi) = x_{-\beta}(-\epsilon s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(s t^2\xi^2) \cdot x_{-\alpha-\beta}(s t\xi^2) \cdot z_{-\beta}(-\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(-\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(s t) \cdot z_\alpha( s, t\xi) \]
-
-\[ z_\alpha(-s, t\xi) = z_{\alpha+\beta}(st, \xi) x_{-\beta}(-\epsilon s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(s t^2\xi^2) \cdot x_{-\alpha-\beta}(s t\xi^2) \cdot z_{-\beta}(-\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(-\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(s t) \]
-
-\[ z_\alpha(s, t\xi) = z_{\alpha+\beta}(-st, \xi) x_{-\beta}(\epsilon s\xi) \cdot x_\alpha(-s) \cdot x_{-\alpha}(-s t^2\xi^2) \cdot x_{-\alpha-\beta}(-s t\xi^2) \cdot z_{-\beta}(\epsilon s\xi, \epsilon t)) \cdot x_{\beta}(\epsilon st^2\xi)  \cdot x_{\alpha+\beta}(- s t) \]
-\end{comment}
-Substituting $s := \epsilon f$, $t = -\epsilon g$ and $\xi = X$ in the fifth equality of Lemma~\ref{Zrels} and expressing the rightmost term through others we obtain (here $\beta$ is some other root such that $\alpha + \beta \in \Phi$): \[ z_\alpha(f, gX) = z_{\alpha+\beta}(-fg, X) x_{-\beta}(\epsilon fX) \cdot x_\alpha(-f) \cdot x_{-\alpha}(-f g^2X^2) \cdot x_{-\alpha-\beta}(-f gX^2) \cdot z_{-\beta}(\epsilon fX, \epsilon g) \cdot x_{\beta}(\epsilon fg^2X)  \cdot x_{\alpha+\beta}(- f g),\ \epsilon = N_{\alpha,\beta}.
-\]
-The factors in the right hand side have types: 2, 1, 2, 4, 1, 1, 1, 2. 
-It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the third factor $x_\alpha(-f)$, 
-while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
+It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2. Substituting in~\eqref{Z5} of~\cref{Crels} $s := -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ we obtain that
+\begin{multline} \nonumber
+ z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) = x_\alpha( -f) x_{-\beta}(- f g) \cdot x_{\beta}( f gX^2) \cdot x_{\alpha+\beta}(-\epsilon f X) \cdot \\ \cdot z_\alpha(f,  gX) \cdot x_{-\alpha}(fg^2X^2) \cdot x_{-\alpha-\beta}(\epsilon f g^2 X) \cdot z_{-\beta}(fg, -X),
+\end{multline}
+where $\epsilon = N_{\alpha,\beta}$. 
+Expressing $z_{\alpha}(f, gX)$ through other terms
+\begin{multline} \nonumber
+ z_\alpha(f, gX) = 
+ x_{\alpha+\beta}(\epsilon f X) \cdot
+ x_{\beta}(-f gX^2) \cdot
+ x_{-\beta}(f g) \cdot
+ x_\alpha(f) \cdot \\ \cdot
+ z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) \cdot 
+ z_{-\beta}(-fg, -X) \cdot
+ x_{-\alpha-\beta}(-\epsilon f g^2 X) \cdot
+ x_{-\alpha}(-fg^2X^2) \cdot
+\end{multline}
+we conclude that the factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4.
+It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$.
 \end{proof}

### 2019-04-30 dl-paper.tex
Abridged Lemma 12

@@
 
-It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2. Substituting in~\eqref{Z5} of~\cref{Crels} $s := -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ we obtain that
-\begin{multline} \nonumber
- z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) = x_\alpha( -f) x_{-\beta}(- f g) \cdot x_{\beta}( f gX^2) \cdot x_{\alpha+\beta}(-\epsilon f X) \cdot \\ \cdot z_\alpha(f,  gX) \cdot x_{-\alpha}(fg^2X^2) \cdot x_{-\alpha-\beta}(\epsilon f g^2 X) \cdot z_{-\beta}(fg, -X),
-\end{multline}
-where $\epsilon = N_{\alpha,\beta}$. 
-Expressing $z_{\alpha}(f, gX)$ through other terms
+It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2.
+Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ and expressing $z_\alpha(f, gX)$ through other terms we obtain that
 \begin{multline} \nonumber
@@
  x_{-\alpha-\beta}(-\epsilon f g^2 X) \cdot
- x_{-\alpha}(-fg^2X^2) \cdot
+ x_{-\alpha}(-fg^2X^2),
 \end{multline}
-we conclude that the factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4.
+where $\epsilon = N_{\alpha,\beta}$. 
+The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4.
 It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$.

### 2019-04-30 dl-paper.tex
Finished editing 4.2

@@
 Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$.
-Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we conclude from this that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
-Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.
+Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we obtain that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$ and hence that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.
 
 Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
-But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3.
-\begin{comment}
-Let us draw the matrix for $z_\alpha(m, X\xi)$:
-\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) =
- \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
-Now let us draw the matrix for $c_\alpha(m, \xi)$:
-\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
- \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
-\end{comment}
+But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of $P_\alpha(0)$ of type 3.
 \end{proof}
 
-\begin{comment}
-Useful consequence: $z_{-\alpha}(X^2f(X), g(X)) \in P_\alpha(0)$. Proof: $z_{-\alpha}(X^2f(X), g(X)) = 
-x_{-\beta}(-Xg) \cdot x_{-\alpha-\beta}(\epsilon X) \cdot x_{\alpha+\beta}(\epsilon X^3f^2g^2) \cdot x_{\alpha}(-X^2fg^2) \cdot 
-z_{-\beta}(-Xg, -Xf) \cdot x_{\beta}(-X^3f^2g)  \cdot x_{-\alpha}(-X^2f) \cdot z_{-\alpha-\beta}(\epsilon X, -\epsilon Xfg)$,
-where $\epsilon = N_{-\alpha-\beta,\beta}$. This is a product of generators of types: 1,1,2,2,1,1,4,1.
-\end{comment}
-
-\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence split by the map $m \mapsto x_{-\alpha}(mX)$:
+\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
 \[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\]
 \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator of $P_\alpha(0)$ listed in~Definition~\ref{defP0} still belongs to $P_\alpha(0)$.
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to the generators of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
 The assertion is obvious for the generators of type (3) and (4).
@@
 Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
-\[ z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2fg ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2fg^2) \cdot z_{\beta}(Xf, g), \]
-the latter expression, clearly, is a product of generators of type $4, 1, 1$.
+\[ z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2fg ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2fg^2) \cdot z_{\beta}(Xf, g). \]
+It is clear that the latter expression is a product of generators of type $4, 1, 1$.
 \end{proof}
@@
 Let us verify the assertion for the generator of type (4).
-Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke~\eqref{Z5} of~\cref{Zrels} substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$:
+Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$.
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
 \begin{multline} \nonumber
@@
 We need to verify that $h = S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)$ lies in $P\left(\alpha, \frac{m}{1 + am}\right)$, but from Lemmas~\ref{P0_conj}--\ref{lem:Tulenbayev-formula} and the antisymmetry of Steinberg symbols we obtain that:
-\begin{multline} h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
+\begin{multline} \nonumber h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
 = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right).\qedhere \end{multline}
@@
 
-\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P(\beta, 0)$. \end{lemma}
+\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P_\beta(0)$. \end{lemma}
 \begin{proof}

### 2019-04-30 dl-paper.tex
Minor fix

@@
 Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.
-We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
- $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
-
-\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
-              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \]
 
@@
 \subsection{The proof of the injectivity theorem}
+We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
+ $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
 
- \begin{comment}
+\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
+              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \]
+
 \begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
@@
 \end{proof}
-\end{comment}
 
@@
 \end{multline}
+\end{comment}
 
 There is still a mistake in the last implication :(
-\end{comment}
 Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.

### 2019-05-02 dl-paper.tex
More coherent notation, added couple of easy formulas

--- 2019-04-30 dl-paper.tex
@@
 
+{\bf Warning}: This definition is somewhat incomplete, $P_\alpha(0)$ should also contain certain symbols, e.\,g. those from~\cref{lem:Tulenbayev-formula} below. 
+I'll fix this later.
+
 Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
@@
 \begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof}
-Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$.
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$.
 Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we conclude from this that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
@@
 Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
-But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3.
-\begin{comment}
-Let us draw the matrix for $z_\alpha(m, X\xi)$:
-\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) =
- \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
-Now let us draw the matrix for $c_\alpha(m, \xi)$:
-\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
- \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
-\end{comment}
-\end{proof}
+But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3. \end{proof}
 
-\begin{comment}
-Useful consequence: $z_{-\alpha}(X^2f(X), g(X)) \in P_\alpha(0)$. Proof: $z_{-\alpha}(X^2f(X), g(X)) = 
-x_{-\beta}(-Xg) \cdot x_{-\alpha-\beta}(\epsilon X) \cdot x_{\alpha+\beta}(\epsilon X^3f^2g^2) \cdot x_{\alpha}(-X^2fg^2) \cdot 
-z_{-\beta}(-Xg, -Xf) \cdot x_{\beta}(-X^3f^2g)  \cdot x_{-\alpha}(-X^2f) \cdot z_{-\alpha-\beta}(\epsilon X, -\epsilon Xfg)$,
-where $\epsilon = N_{-\alpha-\beta,\beta}$. This is a product of generators of types: 1,1,2,2,1,1,4,1.
-\end{comment}
+The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
+ it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $g(0)$ lies in the subgroup generated by
+ elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
+ and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.
 
 \begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence split by the map $m \mapsto x_{-\alpha}(mX)$:
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\]
-\end{lemma}
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator of $P_\alpha(0)$ listed in~Definition~\ref{defP0} still belongs to $P_\alpha(0)$.
@@
 Let us verify the assertion for the generators of type (1) and (2). In the case $\beta - \alpha \in \Phi$ we obtain from Lemma~\ref{Zrels}:
-\begin{align} z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2fg) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f)     \cdot z_{\beta}(Xf, g), \label{eq3-1} \\
-  z_{\beta}(f, Xg) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2fg ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf)     \cdot z_{\beta}(f, Xg), \label{eq3-2} \\
-  z_{\alpha}(f, Xg) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(g + m)). \end{align}
+\begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
+  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \\
+  z_{\alpha}(f, X\xi) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(\xi + m)). \end{align}
 The expressions in the right hand side of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
@@
 Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
-\[ z_{\beta}(Xf, g) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2fg ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2fg^2) \cdot z_{\beta}(Xf, g), \]
+\[ z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \]
 the latter expression, clearly, is a product of generators of type $4, 1, 1$.
@@
 
-\begin{df}
-Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] 
-\end{df}
+\begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] \end{df}
+Right from the definition of $S_\alpha(a, -)$ it is easy to verify that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
+\[ S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\]
+
 It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the conjugation map $g \mapsto {}^{x_\alpha(aX^{-1})}\!g$.
@@
 First of all, consider the case $\alpha + \beta \in \Phi$ (only possible for the generator of the first type):
-\[ z_{\beta}(Xf, g) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, g). \]
+\[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
 Clearly the expression in the right hand side is a product of elements of generators of type 2, 2, 1. 
 Now consider the case $\alpha - \beta \in \Phi$ (possible for generators of type (1) and (2)).
-\begin{align} z_{\beta}(Xf, g) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (afg) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot afg^2) \cdot z_{\beta}(Xf, g), \\
-z_{\beta}(f, Xg) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (afg) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot fXg^2a) \cdot z_{\beta}(f, Xg). \end{align}
+\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
+z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot Xf\xi^2a) \cdot z_{\beta}(f, X\xi). \end{align}
 The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.
@@
 Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke~\eqref{Z5} of~\cref{Zrels} substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$:
-\begin{multline} \nonumber
- z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(f a X^2) \cdot x_{-\alpha}(X^2f) \cdot \\ \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon Xf a^2) \cdot x_{\alpha}(- f a^2) \cdot z_{-\beta}(f a, -X),
-\end{multline}
-where $\epsilon = N_{-\alpha-\beta,\beta}$. Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.
+\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(X^2 f a) \cdot x_{-\alpha}(X^2f) \cdot \\
+ \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon Xf a^2) \cdot x_{\alpha}(- f a^2) \cdot z_{-\beta}(f a, -X), \end{multline}
+where $\epsilon = N_{-\alpha-\beta,\beta}$. 
+Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.
 
 It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2.
-Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ and expressing $z_\alpha(f, gX)$ through other terms we obtain that
-\begin{multline} \nonumber
- z_\alpha(f, gX) = 
- x_{\alpha+\beta}(\epsilon f X) \cdot
- x_{\beta}(-f gX^2) \cdot
- x_{-\beta}(f g) \cdot
- x_\alpha(f) \cdot \\ \cdot
- z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) \cdot 
- z_{-\beta}(-fg, -X) \cdot
- x_{-\alpha-\beta}(-\epsilon f g^2 X) \cdot
- x_{-\alpha}(-fg^2X^2),
-\end{multline}
+Substituting in~\eqref{Z5} of~\cref{Crels} $s := -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ we obtain that
+\begin{multline} \nonumber z_{\alpha+\beta}(-\epsilon fX, -\epsilon \xi) = x_\alpha( -f) x_{-\beta}(- f \xi) \cdot x_{\beta}( X^2f \xi) \cdot x_{\alpha+\beta}(-X\epsilon f) \cdot \\
+ \cdot z_\alpha(f,  X\xi) \cdot x_{-\alpha}(X^2f\xi^2) \cdot x_{-\alpha-\beta}(\epsilon Xf \xi^2) \cdot z_{-\beta}(f\xi, -X), \end{multline}
 where $\epsilon = N_{\alpha,\beta}$. 
+We can express $z_{\alpha}(f, X\xi)$ through other terms and obtain that
+\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
+ \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2) \cdot \end{multline}
 The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
-It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$.
-\end{proof}
+It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
+while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
 
-\begin{lemma} \label{lem:Tulenbayev-formula}
- $x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}$.
-\end{lemma}
-\begin{proof}
-Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
+\begin{lemma} \label{lem:Tulenbayev-formula} One has
+ \[x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot 
+ x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.\] \end{lemma}
+\begin{proof} Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
  \begin{multline*}
@@
 
-\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$. \end{corollary}
+\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$.
+Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary}
 \begin{proof}
@@
 \begin{multline} h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
-= S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right).\qedhere \end{multline}
-\end{proof}
+= S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right). \end{multline}
+The second assertion can be verified in a straightforward manner. \end{proof}
 

### 2019-05-02 dl-paper.tex

@@
 \begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$. 
-Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we conclude from this that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
+Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we obtain that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
 Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.
@@
 Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
-But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of type 3. \end{proof}
+But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of $P_\alpha(0)$ of type 3. \end{proof}
 
@@
 
-\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence split by the map $m \mapsto x_{-\alpha}(mX)$:
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator of $P_\alpha(0)$ listed in~Definition~\ref{defP0} still belongs to $P_\alpha(0)$.
+\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\]
+\end{lemma}
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to the generators of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
 The assertion is obvious for the generators of type (3) and (4).
@@
 Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
-\[ z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \]
-the latter expression, clearly, is a product of generators of type $4, 1, 1$.
+\[ z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \]
+It is clear that the latter expression is a product of generators of type $4, 1, 1$.
 \end{proof}
@@
 Let us verify the assertion for the generator of type (4).
-Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$ and invoke~\eqref{Z5} of~\cref{Zrels} substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$:
+Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
 \begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(X^2 f a) \cdot x_{-\alpha}(X^2f) \cdot \\
@@
 
-It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2.
-Substituting in~\eqref{Z5} of~\cref{Crels} $s := -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ we obtain that
-\begin{multline} \nonumber z_{\alpha+\beta}(-\epsilon fX, -\epsilon \xi) = x_\alpha( -f) x_{-\beta}(- f \xi) \cdot x_{\beta}( X^2f \xi) \cdot x_{\alpha+\beta}(-X\epsilon f) \cdot \\
- \cdot z_\alpha(f,  X\xi) \cdot x_{-\alpha}(X^2f\xi^2) \cdot x_{-\alpha-\beta}(\epsilon Xf \xi^2) \cdot z_{-\beta}(f\xi, -X), \end{multline}
+It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
+Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
+\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
+ \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
 where $\epsilon = N_{\alpha,\beta}$.  
-We can express $z_{\alpha}(f, X\xi)$ through other terms and obtain that
-\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
- \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2) \cdot \end{multline}
 The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
@@
 We need to verify that $h = S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)$ lies in $P\left(\alpha, \frac{m}{1 + am}\right)$, but from Lemmas~\ref{P0_conj}--\ref{lem:Tulenbayev-formula} and the antisymmetry of Steinberg symbols we obtain that:
-\begin{multline} h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
+\begin{multline} \nonumber h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
 = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right). \end{multline}

### 2019-05-02 dl-paper.tex
Minor fix

@@
  Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
-Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
-Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$ belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
-Similar argument also works for the negative roots.
-The required assertion now follows from the above proposition.
+ Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo 
+ $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to 
+ $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
+ Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$
+ belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
+ Similar argument also works for the negative roots, and the required assertion now follows.
 \end{proof}
@@
 It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
-Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
+Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
 \begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 

### 2019-05-02 dl-paper.tex
Minor fix

--- 2019-05-02 dl-paper.tex
@@
 \[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
-Clearly the expression in the right hand side is a product of elements of generators of type 2, 2, 1. 
+Clearly the expression in the right hand side is a product of generators of type 2, 2, 1. 
 Now consider the case $\alpha - \beta \in \Phi$ (possible for generators of type (1) and (2)).

### 2019-05-02 dl-paper.tex
Minor fix

--- 2019-05-02 dl-paper.tex
@@
  \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
- \item $z_{\gamma}(f, \xi),\ \alpha \perp \gamma;$
+ \item $z_{\beta}(f, \xi),\ \alpha \perp \beta;$
  \item $x_{-\alpha}(X^2f),$
@@
 \begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator of $P_\alpha(0)$ lies in $P_\alpha(0)$. 
-First of all, consider the case $\alpha + \beta \in \Phi$ (only possible for the generator of the first type):
+\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
+First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
 \[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
-Clearly the expression in the right hand side is a product of elements of generators of type 2, 2, 1. 
-Now consider the case $\alpha - \beta \in \Phi$ (possible for generators of type (1) and (2)).
+Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
+Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
+Computing the conjugates of these generators using~\cref{Zrels} we obtain that
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
-z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot Xf\xi^2a) \cdot z_{\beta}(f, X\xi). \end{align}
+z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \end{align}
 The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.
 
-Let us verify the assertion for the generator of type (4).
+Let us verify the assertion for the generator of type 4.
 Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
 Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
-\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(X^2 f a) \cdot x_{-\alpha}(X^2f) \cdot \\
- \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon Xf a^2) \cdot x_{\alpha}(- f a^2) \cdot z_{-\beta}(f a, -X), \end{multline}
+\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
+ \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
 where $\epsilon = N_{-\alpha-\beta,\beta}$. 
@@
 It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
+Again choose $\beta$ to be any root such that $\alpha+\beta \in \Phi$.
 Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that

### 2019-05-03 dl-paper.tex
Minor

@@
 \[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] \end{df}
-Right from the definition of $S_\alpha(a, -)$ it is easy to verify that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
+It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
 \[ S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\]
@@
 
+Our next goal is to determine what happens with the generators of $K(A[X], M[X])$ under the map $S_\alpha(a, -)$.
+At first we could look at what happens with $K(A[X], M[X]) \cap P_\alpha(0)$ under $S_\alpha(a, -)$.
+We notice the following elements:
+\begin{itemize}
+ \item $x_\alpha(c)$, $c \in A$;
+ \item $x_{\alpha+\beta}(d)$, $\alpha+\beta \in \Phi$
+\end{itemize}
+
+\[ x_\alpha(c), , x_{\alpha-\beta}(d) \]
+
+\begin{comment}
 \begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P_\beta(0)$. \end{lemma}
@@
 \end{proof}
+\end{comment}
 
@@
 
-\begin{comment}
 ($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
@@
  0 & 0 & 1 - bm 
- \end{array}\right)
+ \end{array}\right) \cdot \\ \cdot
 \left(\begin{array}{ccc} 
@@
 \end{multline}
-\end{comment}
 

### 2019-05-03 dl-paper.tex
Added Corollary 3

@@
 The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
- it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $g(0)$ lies in the subgroup generated by
+ it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
  elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
@@
 First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
-\[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
+\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
 Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
@@
 Computing the conjugates of these generators using~\cref{Zrels} we obtain that
-\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
-z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \end{align}
+\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \\
+z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \nonumber \end{align}
 The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.
@@
 Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
-\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
+\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
  \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
@@
 while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
+
+\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
+\begin{proof}
+ By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
+ $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.
+
+ It remains to notice that in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} after evaluating at $X=0$ the only terms that remain 
+  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
+\end{proof}
 

### 2019-05-04 dl-paper.tex
Added Lemma 13

@@
 \begin{comment}
-The following result was proved in \cite[Proposition~3.2]{Ste13}.
-\begin{lemma}\label{lem:Zgen} Let $\Phi$ be an irreducible root system of rank $\geq 2$. 
-Let $G$ denote the normal closure in $\St(\Phi, R)$ of the subgroup spanned by elementary root unipotents of level $I$, i.\,e.
-$G=\langle x_\alpha(s) \mid \alpha\in\Phi,\ s\in I\rangle^{\St(\Phi, R)}$.
-
-Let $S$ be a parabolic set of roots of $\Phi$ with special part $\Sigma_S$.
-Then $G$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S, I, R)$ consisting of the following two families of elements:
-\begin{itemize}
- \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
- \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
-\end{itemize}        
-\end{lemma}
-\end{comment}
-
-\begin{comment}
 Hall-Witt identity
@@
 
-In the following lemma we will need the following variant of Hall--Witt identity:
+\begin{comment}
+For a subset of roots $S \subseteq \Phi$ denote by $\mathcal{Z}(S, R, I)$ the subset of $\overline{\St}(\Phi, R, I)$ consisting of the following two families of elements:
+\begin{itemize}
+ \item $x_\alpha(s)$, $\alpha \in \Phi$, $s\in I$;
+ \item $z_\alpha(s, \xi)$, $\alpha \in S$, $s\in I$, $\xi \in R$.
+\end{itemize}
+
+\begin{lemma} \label{weak-Stepanov} For any $\Phi$ of rank $\geq 2$ the set $\mathcal{Z}(\Phi, R, I)$ generates $\overline{\St}(\Phi, R, I)$ as a group.
+ Further, if $\Phi$ is simply laced $\overline{\St}(\Phi, R, I)$ is generated by even smaller set $\mathcal{Z}(\Phi\setminus\{\alpha, \beta\}, R, I)$, 
+  where $\alpha, \beta \in \Phi$ are arbitrary roots of $\Phi$. \end{lemma}
+\begin{proof}
+ The first assertion is well-known, see the first part of~\cite[Lemma~4]{S15}.
+ Notice that it follows from relation~\eqref{Z5} that $\mathcal{Z}(S, R, I)$ generates the same group as $\mathcal{Z}(S \cup (S - S), R, I)$.
+ The second assertion then follows from the first one and the fact that for $S := \Phi \setminus \{ \alpha, \beta \}$ one has $S \cup (S - S) = \Phi$.
+\end{proof}
+{\bf TODO:} Probably, in the same fashion we could reprove Stepanov's theorem in the simply laced case.
+\end{comment}
+
+\begin{theorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated 
+by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+
+In fact, it is generated by even smaller set of elements defined as follows.
+Choose any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$. Then the generating set consists of the following two families of elements:
+$x_\alpha(s)$, $s \in I$ and $z_\alpha(s, \xi)$, $\alpha \in \Sigma_S$, $s \in I$, $\xi \in R$. \end{theorem}
+\begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+
+{\bf TODO:} Perhaps we could deduce the second assertion of Stepanov's theorem from the first one using relation~\eqref{Z5}.
+
+For the proof of the following lemma we will need the following variant of Hall--Witt identity:
 \begin{equation} \label{HW-variant} [x, [ y, z]] = \left([[ x^{-1}, y^{-1}], z] ^ {x^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}}\right)^{y^{-1}}.\end{equation}
@@
 \end{enumerate}
-In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$. \end{df}
-
-{\bf Warning}: This definition is somewhat incomplete, $P_\alpha(0)$ should also contain certain symbols, e.\,g. those from~\cref{lem:Tulenbayev-formula} below. 
-I'll fix this later.
+In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$.
+{\bf TODO:} the above definition is somewhat incomplete, $P_\alpha(0)$ should also contain certain symbols, e.\,g. those from~\cref{lem:Tulenbayev-formula} below. \end{df}
 
@@
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
-  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \\
-  z_{\alpha}(f, X\xi) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(\xi + m)). \end{align}
+  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \nonumber \\
+  z_{\alpha}(f, X\xi) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(\xi + m)). \nonumber \end{align}
 The expressions in the right hand side of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
@@
 Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
-\[ z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \]
+\begin{equation} \label{eq3-2} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
 It is clear that the latter expression is a product of generators of type $4, 1, 1$.
@@
 
- It remains to notice that in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} after evaluating at $X=0$ the only terms that remain 
+ It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
   are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
 \end{proof}
+
+In fact, we could prove something a little bit stronger.
+\begin{lemma}
+ Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
+ the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
+  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.
+
+ The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
+ \begin{itemize}
+  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
+ \end{itemize}
+\end{lemma}
+\begin{proof}
+ %Follows from~\cref{Kgen-strong}, \cref{P0_normal} and Stepanov's theorem.
+ Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
+ Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
+  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
+
+ Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
+  generators of the form $c_{\pm \delta}(f, X\xi)$.
+
+ The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
+ $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
+  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
+ Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates.
+ Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
+  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
+   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$ for some $\xi \in A[X]$.
+ After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+  we obtain the desired decomposition for $g$. \end{proof}
 
@@
 The second assertion can be verified in a straightforward manner. \end{proof}
-
-Our next goal is to determine what happens with the generators of $K(A[X], M[X])$ under the map $S_\alpha(a, -)$.
-At first we could look at what happens with $K(A[X], M[X]) \cap P_\alpha(0)$ under $S_\alpha(a, -)$.
-We notice the following elements:
-\begin{itemize}
- \item $x_\alpha(c)$, $c \in A$;
- \item $x_{\alpha+\beta}(d)$, $\alpha+\beta \in \Phi$
-\end{itemize}
-
-\[ x_\alpha(c), , x_{\alpha-\beta}(d) \]
 

### 2019-05-04 dl-paper.tex
Minor fix

@@
 
+In fact, we could prove something a little bit stronger.
+\begin{lemma} \label{K-a-b}
+ Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
+ the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
+  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.
+
+ The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
+ \begin{itemize}
+  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
+ \end{itemize}
+\end{lemma}
+\begin{proof}
+
+ Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
+ Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
+  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
+
+ Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
+  generators of the form $c_{\pm \delta}(f, X\xi)$.
+
+ The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
+ $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
+  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
+ Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
+  so this process is guaranteered to end.
+ Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
+  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
+   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
+ After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+  we obtain the desired decomposition for $g$. \end{proof}
+
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
@@
 \end{proof}
-
-In fact, we could prove something a little bit stronger.
-\begin{lemma}
- Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
- the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
-  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.
-
- The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
- \begin{itemize}
-  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
-  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
- \end{itemize}
-\end{lemma}
-\begin{proof}
- %Follows from~\cref{Kgen-strong}, \cref{P0_normal} and Stepanov's theorem.
- Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
- Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
-  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
-
- Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
-  generators of the form $c_{\pm \delta}(f, X\xi)$.
-
- The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
- $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
-  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
- Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates.
- Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
-  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
-   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$ for some $\xi \in A[X]$.
- After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
-  we obtain the desired decomposition for $g$. \end{proof}
 

### 2019-05-05 dl-paper.tex
Added root-theoretic lemma

@@
 
+\begin{lemma} \label{root-lemma}
+ For any $\alpha, \beta$ in a system of type $A_3$ there exist $\alpha_1, \alpha_2, \beta_1, \beta_2 \in \Phi$ such that
+ $\alpha = \alpha_1 - \alpha_2$, $\beta = \beta_1 - \beta_2$ and root sets $\{ \pm \alpha, \pm \beta \}$ and $\{ \alpha_1, \alpha_2, \beta_1, \beta_2 \}$ have empty intersection.
+\end{lemma}
+\begin{proof} Direct calculation. \end{proof}
+
 In fact, we could prove something a little bit stronger.
@@
   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
-  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
+  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
  \end{itemize}
@@
  Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
-  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
+  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
 
@@
 
- The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
+ The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
  $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
@@
  Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
-  so this process is guaranteered to end.
+  so this process is guaranteed to terminate.
  Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
-  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
-   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
- After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into it)
+  have terms of degree at least $2$ in $X$.
+
+ As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could be transformed into terms of the form
+   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
+    $\beta = \beta_1 - \beta_2$ with the additional property $\{ \pm \alpha, \pm \beta \} \cap \{ \alpha_1, \alpha_2, \beta_1, \beta_2 \} = \emptyset$.
+ Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
+  $z_\alpha(Xf, X\xi)$ as a product of terms from the statement of the lemma. Similar argument also applies to $z_\beta(Xf, X\xi)$.
+
+ Finally, after collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
   we obtain the desired decomposition for $g$. \end{proof}
@@
 while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
+
+\begin{lemma}
+ Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha,\beta \rangle = 0$ or $1$.
+ Then the image of $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$
+  generated by the following elements:
+  \begin{enumerate}
+   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
+   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
+  \end{enumerate}
+ In particular, this image is contained in $P_\beta(0)$.
+\end{lemma}
+\begin{proof}
+Lol
+\end{proof}
 

### 2019-05-05 dl-paper.tex
Moved K-a-b to a separate subsection

@@
 
-\begin{lemma} \label{root-lemma}
- For any $\alpha, \beta$ in a system of type $A_3$ there exist $\alpha_1, \alpha_2, \beta_1, \beta_2 \in \Phi$ such that
- $\alpha = \alpha_1 - \alpha_2$, $\beta = \beta_1 - \beta_2$ and root sets $\{ \pm \alpha, \pm \beta \}$ and $\{ \alpha_1, \alpha_2, \beta_1, \beta_2 \}$ have empty intersection.
-\end{lemma}
-\begin{proof} Direct calculation. \end{proof}
-
-In fact, we could prove something a little bit stronger.
-\begin{lemma} \label{K-a-b}
- Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
- the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
-  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.
-
- The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
- \begin{itemize}
-  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
-  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
- \end{itemize}
-\end{lemma}
-\begin{proof}
-
- Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
- Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
-  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
-
- Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
-  generators of the form $c_{\pm \delta}(f, X\xi)$.
-
- The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
- $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
-  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
- Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
-  so this process is guaranteed to terminate.
- Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into it)
-  have terms of degree at least $2$ in $X$.
-
- As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could be transformed into terms of the form
-   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
-    $\beta = \beta_1 - \beta_2$ with the additional property $\{ \pm \alpha, \pm \beta \} \cap \{ \alpha_1, \alpha_2, \beta_1, \beta_2 \} = \emptyset$.
- Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
-  $z_\alpha(Xf, X\xi)$ as a product of terms from the statement of the lemma. Similar argument also applies to $z_\beta(Xf, X\xi)$.
-
- Finally, after collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
-  we obtain the desired decomposition for $g$. \end{proof}
-
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
@@
 
-\begin{lemma}
- Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha,\beta \rangle = 0$ or $1$.
- Then the image of $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$
-  generated by the following elements:
-  \begin{enumerate}
-   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
-   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
-   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
-  \end{enumerate}
- In particular, this image is contained in $P_\beta(0)$.
-\end{lemma}
-\begin{proof}
-Lol
-\end{proof}
-
+\begin{comment}
 \begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
@@
 \end{comment}
+
+\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
+\begin{df}
+ Let $\alpha, \beta$ be a pair of nonopposite roots of $\Phi$. Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
+ generated by the following elements:
+ \begin{enumerate}
+  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
+  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
+ \end{enumerate}
+\end{df}
+It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
+In fact, as the proposition below shows the opposite inclusion is also true.
+
+\begin{lemma} \label{root-lemma}
+ For any $\alpha, \beta$ in a system of type $A_3$ there exist $\alpha_1, \alpha_2, \beta_1, \beta_2 \in \Phi$ such that
+ $\alpha = \alpha_1 - \alpha_2$, $\beta = \beta_1 - \beta_2$ and root sets $\{ \pm \alpha, \pm \beta \}$ and $\{ \alpha_1, \alpha_2, \beta_1, \beta_2 \}$ have empty intersection.
+\end{lemma}
+\begin{proof} Direct calculation. \end{proof}
+
+\begin{prop} \label{K-a-b}
+ Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
+ the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
+\end{prop}
+\begin{proof}
+ Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
+ Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
+  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
+
+ Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
+  generators of the form $c_{\pm \delta}(f, X\xi)$.
+
+ The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
+ $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
+  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
+ Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
+  so this process is guaranteed to terminate.
+ Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into it)
+  have terms of degree at least $2$ in $X$.
+
+ As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could be transformed into terms of the form
+   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
+    $\beta = \beta_1 - \beta_2$ with the additional property $\{ \pm \alpha, \pm \beta \} \cap \{ \alpha_1, \alpha_2, \beta_1, \beta_2 \} = \emptyset$.
+ Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
+  $z_\alpha(Xf, X\xi)$ as a product of terms from the statement of the lemma. Similar argument also applies to $z_\beta(Xf, X\xi)$.
+
+ Finally, after collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+  we obtain the desired decomposition for $g$. \end{proof}
+
+\begin{lemma}
+ Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha,\beta \rangle = 0$ or $1$.
+ Then the image of $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$
+  generated by the following elements:
+  \begin{enumerate}
+   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
+   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
+  \end{enumerate}
+ In particular, this image is contained in $P_\beta(0)$.
+\end{lemma}
+\begin{proof}
+Lol
+\end{proof}
 

### 2019-05-05 dl-paper.tex
Added some corollary

@@
 
-\begin{comment}
-\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
-\begin{proof}
- By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
- $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.
-
- It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
-  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
-\end{proof}
-\end{comment}
-
 \begin{lemma} \label{lem:Tulenbayev-formula} One has
@@
   \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$ forming a sharp angle with both $\alpha$ and $\beta$.
  \end{enumerate}
 \end{df}
-It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
-In fact, as the proposition below shows the opposite inclusion is also true.
-
 \begin{lemma} \label{root-lemma}
@@
 
- Now choose arbitrary $\delta \neq \pm \alpha, \pm \beta$. By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and
-  generators of the form $c_{\pm \delta}(f, X\xi)$.
+ By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and generators of the form $c_{\pm \delta}(f, X\xi)$ for $\delta$
+  as in the above definition.
 
@@
  Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into it)
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them)
   have terms of degree at least $2$ in $X$.
 
- As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could be transformed into terms of the form
+ As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ might be transformed into terms of the form
    $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
@@
  Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
-  $z_\alpha(Xf, X\xi)$ as a product of terms from the statement of the lemma. Similar argument also applies to $z_\beta(Xf, X\xi)$.
+  $z_\alpha(Xf, X\xi)$ as a product of generators of type 1,2,3. Similar argument also applies to $z_\beta(Xf, X\xi)$.
 
- Finally, after collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+ Finally, after collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
   we obtain the desired decomposition for $g$. \end{proof}
 
+It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
+The above proposition shows that this inlusion is, in fact, an equality.
+
 \begin{lemma}
- Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha,\beta \rangle = 0$ or $1$.
- Then the image of $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$
-  generated by the following elements:
-  \begin{enumerate}
-   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
-   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
-   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
-  \end{enumerate}
- In particular, this image is contained in $P_\beta(0)$.
+ Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha, \beta \rangle = 0\text{ or }1$.
+ Then the image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
+ generated by $K(\alpha, \beta)$ and the subgroup $U$, by definition, generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+ We call these elements generators of type 5.
 \end{lemma}
 \begin{proof}
-Lol
+By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 5, 5, 1.
+By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 5, 1, 2, 1, 1, 5, 5.
+$S(\alpha, -)$ either fixes $x_{-\beta}(X^2f)$, the other generator of type 2, or transforms them into products of generators of type 2, 1.
+Clearly, $S(\alpha, -)$ fixes both generators of type 3. 
+As for the remaining generators type 4, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 5, 5, 4.
 \end{proof}
+
+\begin{corollary} If $\alpha$ and $\beta$ form a sharp angle, then the image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{proof} Follows from the above lemma and the fact that the generators of $U$ are generators of the second type for $P_\beta(0)$ in the sense of~\cref{defP0}.
+ Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
+  $\gamma = \alpha - \beta$, a contradiction. \end{proof}
+
+\begin{comment}
+\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
+\begin{proof}
+ By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
+ $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.
+
+ It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
+  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
+\end{proof}
+\end{comment}
 

### 2019-05-06 dl-paper.tex
Modified definition 8

@@
  \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
+ \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
  \item $z_{\beta}(f, \xi),\ \alpha \perp \beta;$
- \item $x_{-\alpha}(X^2f),$
+ \item $x_{-\alpha}(X^2f);$
+ \item $x_{\alpha}(f).$ 
+ \item Dennis--Stein symbols $\langle a, m \rangle$, $a\in A$, $m\in M$.
 \end{enumerate}
-In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$.
-{\bf TODO:} the above definition is somewhat incomplete, $P_\alpha(0)$ should also contain certain symbols, e.\,g. those from~\cref{lem:Tulenbayev-formula} below. \end{df}
+In the above formulae and for the rest of this subsection we assume $f \in M[X]$ and $\xi \in A[X]$.
+\end{df}
 
-Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$.
 The following lemma shows that this subgroup is sufficiently large.
@@
 \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to the generators of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
-The assertion is obvious for the generators of type (3) and (4).
+\begin{proof} 
+We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
+The assertion is obvious for the generators of type 3, 4 and 6.
 
-Let us verify the assertion for the generators of type (1) and (2). In the case $\beta - \alpha \in \Phi$ we obtain from Lemma~\ref{Zrels}:
+Suppose $g$ has type 1 or 2 and $\beta - \alpha \in \Phi$. By~\cref{Zrels} we obtain that
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
-  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \nonumber \\
-  z_{\alpha}(f, X\xi) ^ {x_{-\alpha}(mX)} = & z_{\alpha}(f, X(\xi + m)). \nonumber \end{align}
-The expressions in the right hand side of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
+  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \nonumber \end{align}
+The expressions in the right hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
 
-Finally, in the case $\alpha + \beta \in \Phi$ (only possible for the generator of type (1)) we have:
+Suppose $g$ has type 1 and  $\alpha + \beta \in \Phi$. By~\cref{Zrels} 
 \begin{equation} \label{eq3-2} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
-It is clear that the latter expression is a product of generators of type $4, 1, 1$.
+and the latter expression is a product of generators of type $4, 1, 1$.
+
+Finally, suppose $g$ has type $5$.
+Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
+\begin{multline} \nonumber z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
+ \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
+and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4.
 \end{proof}
@@
 \begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
+\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
+The assertion is clear for generators of type 3, 5 and 6.
 First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
 \begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
-Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
+Clearly, the expression in the right hand side is a product of generators of type 5, 2, 1.
+
 Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
@@
 z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \nonumber \end{align}
-The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.
+The expressions in the right-hand side are products of generators of type 5, 2, 1 and 5, 1, 2.
 
@@
 where $\epsilon = N_{-\alpha-\beta,\beta}$. 
-Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.
+Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2.
 
+\begin{comment}
 It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
@@
 It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
-while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
+while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
+\end{comment}
+\end{proof}
 

### 2019-05-06 dl-paper.tex
Added Lemma 17

@@
 Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we obtain that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
-Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], M[X])$.
+Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], XM[X])$.
 
@@
 \begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r] & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\]
-\end{lemma}
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
 \begin{proof} 
@@
 \end{proof}
-
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
@@
  Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
-  $z_\alpha(Xf, X\xi)$ as a product of generators of type 1,2,3. Similar argument also applies to $z_\beta(Xf, X\xi)$.
+  $z_\alpha(Xf, X\xi)$ as a product of generators of type 1, 2, 3. Similar argument also applies to $z_\beta(Xf, X\xi)$.
 
@@
   $\gamma = \alpha - \beta$, a contradiction. \end{proof}
+
+\begin{lemma}
+ If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$ for $a \in A$.
+\end{lemma}
 

### 2019-05-07 dl-paper.tex
Added one more assertion

@@
 
+\begin{lemma} Suppose $\alpha$ and $\beta$ form a sharp angle, then $g \in K(A[X], M[X])$ then 
+\[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
+\begin{proof}
+ By~\cref{K-a-b} $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
+ \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
+  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\frac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
+The assertion now follows from the preceding corollary.
+\end{proof}
+
 \begin{lemma}
- If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$ for $a \in A$.
+ If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq P_\alpha(0)$ for $a \in A$.
 \end{lemma}
+\begin{proof}
+ It is clear that $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(A[X], M[X]) \subseteq P_\alpha(*)$.
+\end{proof}
 
@@
 \begin{enumerate}
- \item $(+)$ $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
- \item $(+)$ if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
+ \item (+) $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
+ \item (+) if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
  %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
- \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then
-$S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
+ \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then $S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
  \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
@@
 \begin{enumerate}
- \item $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
- \item if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
+ \item (+) $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
+ \item (+) if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
 % \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
- \item if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
+ \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
 $S_\alpha(a, g) \in P(\beta, 0);$

### 2019-05-07 dl-paper.tex
Added sketch of the proof for Stepanov's theorem; inserted Andrei's piece of text

@@
 \DeclareMathOperator{\colim}{colim}
+\newcommand{\inv}{^{-1}}
+
 \newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
@@
 
-\begin{theorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated 
-by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
-
-In fact, it is generated by even smaller set of elements defined as follows.
-Choose any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$. Then the generating set consists of the following two families of elements:
-$x_\alpha(s)$, $s \in I$ and $z_\alpha(s, \xi)$, $\alpha \in \Sigma_S$, $s \in I$, $\xi \in R$. \end{theorem}
-\begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
-
-{\bf TODO:} Perhaps we could deduce the second assertion of Stepanov's theorem from the first one using relation~\eqref{Z5}.
+For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
+
+\begin{theorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+
+In fact, it is generated as a group by even smaller subset $\mathcal{Z}(\Sigma_S, R, I)$. Here $\Sigma_S$ denotes the special part of arbitrary parabolic subset of roots $S \subseteq \Phi$.
+\end{theorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+
+\begin{rem}
+ For a simply-laced $\Phi$ the second assertion of~\cref{thm:Stepanov} can be deduced from the first one by means of~\cref{Zrels}.
+Indeed, for a root subset $U\subseteq \Phi$ consider the following operation:
+ \[dU := U \cup (U - U)\cap \Phi.\]
+ In other words $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
+It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n$ (in fact, $n=2$).
+It remains to see that relation~\eqref{Z5} immediately implies the following assertion: every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
+\end{rem}
+
+{\bf TODO:} One can write analogue of~\eqref{Z5} in the nonsimply-laced case and the above argument still applies.
 
@@
 
+\subsection{Lemma33}
 Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.
+
+For a simply-laced root system $\Phi$ and a commutative ring $R$, the Steinberg group $\St(\Phi,\,R)$ is generated by the formal symbols $x_{\alpha}(a)$ for $\alpha\in\Phi$, $a\in R$ subject to the Steinberg relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{R\arabic{equation}}
+\begin{align}
+&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b),\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi,\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0.
+\end{align}
+
+Let $I\trianglelefteq A$ be an ideal in a commutative ring $A$ (not neccesarily proper), denote $R=\oplus_{d\in\mathbb Z}R_d\subseteq A[t,t\inv]$, where $R_d=It^d$, $d<0$, and $R_d=At^d$, $d\geq0$.
+
+For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
+
+Consider the root system $\rD_l$ for $l\geq5$. It can be naturally embedded into the root system of type $\rC_l$ as a set of short roots.
+
+Define trancated Steinberg groups $G_n$ for $n\geq1$ by the set of generators $x_\alpha(a)$, $\alpha\in\rD_l$, $a\in R_d$, $d\leq n$, and relations
+
+\vspace{-15pt}
+\setcounter{equation}{0}
+\renewcommand{\theequation}{R\arabic{equation}$\!\,_n$}
+\begin{align}
+&\,\,x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b),\ a,b\in R_d,\ d\leq n,\\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n,\phantom{tttttttt}
+\end{align}
+\vspace{-35pt}
+\setcounter{equation}{0}
+\renewcommand{\theequation}{R3.\arabic{equation}$\!\,_n$}
+\begin{align}
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\ \alpha+\beta\not\in\rC_l\cup0,\ a\in R_d,\ b\in R_e,\ d,e\leq n,\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\ \alpha+\beta\in\rC_l\setminus\rD_l,\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n.
+\end{align}
+
+\begin{rem}
+We can take $\mathbb R^l$ with a base $\chi_1,\ldots,\chi_l$ and visualise root systems
+$$
+\rD_l=\{\pm\chi_i\pm\chi_j\mid1\leq i\neq j\leq l\}
+$$
+and $\rC_l=\rD_l\cup\{\pm2\chi_i\mid1\leq i\leq l\}$.
+Then we immediately see that $\alpha+\beta\in\rC_l\setminus\rD_l$ exactly means that either $\{\alpha,\beta\}$ or $\{-\alpha,-\beta\}$ equals $\{\chi_i-\chi_j,\chi_i+\chi_j\}$.
+Then for some $\sigma$ from the Weyl group of $\rD_l$ we get
+$$
+\{\sigma\alpha,\sigma\beta\}=\{\chi_{l-1}-\chi_l, \chi_{l-1}+\chi_l\}=\{\alpha_{l-1},\alpha_l\}
+$$ 
+(the horns of the Dynkin diagram $\rD_l$).
+Another condition on $\alpha$ and $\beta$ equivalent to $\alpha+\beta\in\rC_l\setminus\rD_l$ is that they do not lie in any subsystem of $\rD_l$ of type $\rA_m$ for $m\geq4$.
+\end{rem}
+
+We claim that $G_n\cong G_{n+1}$, more precisely, we construct an inverse homomorhism to the natural map $G_n\rightarrow G_{n+1}$.
+With this end we define elements $s_\alpha(a)\in G_n$ for $a\in R_{n+1}$ and prove the above relations for these elements.
+We start with the following easy fact.
+
+\begin{lemma}
+\label{welldef}
+Take $d$, $e\leq n$, $d+e=n+1$, $a\in R_d$, $b\in R_e$, and consider an embedding $\iota\colon\rA_4\hookrightarrow\rD_l$.
+For the chosen simple roots $\alpha_k$ of $\rA_4$ denote $\beta_k=\iota(\alpha_k)$.
+Then holds
+$$
+[x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)],
+$$
+where $N=N_{\beta_1,\beta_2}N_{\beta_2,\beta_3}$.
+\end{lemma}
+\begin{proof}
+Observe that $d$, $e\geq1$.
+Take $x=x_{\beta_1}(a)$, $y=x_{\beta_2}(N_{\beta_3,\beta_2}bt\inv)$, $z=x_{\beta_3}(t)$.
+Since $x$ and $z$ lie in the subsystem of type $\rA_4$, we get by R3.1$\!\,_n$ that they commute.
+Then Hall--Witt identity gives us
+$$
+\,^y[x,\,[y\inv,\,z]]=\,^x[[x\inv,\,y],\,z],
+$$
+where $[x,\,[y\inv,z]]=[x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]$ and $[[x\inv,y],\,z]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)]$ by R2$\!\,_n$.
+Here $x$ commutes with $x_{\beta_1+\beta_2}(Nabt\inv)$ and $x_{\beta_3}(t)$, and $y$ commutes with $x_{\beta_2+\beta_3}(b)$ by R3.1$\!\,_n$.
+Finally, $[x_{\beta_1}(-a),\,y]=x_{\beta_1+\beta_2}(Nabt\inv)$ also commutes with $x_{\beta_2+\beta_3}(b)$, what finishes the proof.
+\end{proof}
+
+The above lemma allows us for $a\in R_{n+1}$ and $\alpha\in\rD_l$ chose an arbitrary decomposition $\alpha=\beta+\gamma$ and define $s_\alpha(a)=[x_\beta(N_{\beta,\gamma}\,at\inv),\,x_\gamma(t)]$.
+Indeed, take another decomposition $\alpha=\beta'+\gamma'$, we may assume that subsystem $\Psi$ generated by $\beta$, $\beta'$, $\gamma$, $\gamma'$ has type $\rA_3$ If it is contained in the subsystem of type $\rA_4$, we are done by Lemma~\ref{welldef}.
+If not, we may assume $\Psi=\langle\alpha_{l-2},\alpha_{l-1},\alpha_l\rangle$ and since $l\geq5$ take two subsystems of type $\rA_4$, say, $\Psi_1$ and $\Psi_2$, which overlap by $\rA_3$, and $\beta$, $\gamma\in\Psi_1$, $\beta'$, $\gamma'\in\Psi_2$.
+Therefore, there exist $\beta''$, $\gamma''\in\Psi_1\cap\Psi_2$ with $\alpha=\beta''+\gamma''$ and we can again apply Lemma~\ref{welldef} to get the claim.
+
+Moreover, with the assumption of Lemma~\ref{welldef} on $a$ and $b$ we have
+$$
+[x_{\beta}(a),\,x_{\gamma}(b)]=s_{\alpha}(N_{\beta,\gamma}\,ab).
+$$
+
+The following observation is obvious.
+
+\begin{lemma}
+\label{commute}
+Consider an embedding $\iota\colon\rA_4\hookrightarrow\rD_l$ and denote $\beta_k=\iota(\alpha_k)$ for simple roots $\alpha_k$ of $\rA_4$.
+Then for any $a\in R_d$, $b\in R_e$, $c\in R_f$ with $d$, $e$, $f\leq n$ holds
+$$
+[[x_{\beta_1}(a),\,x_{\beta_2}(b)],\,x_{\beta_4}(c)]=1.
+$$
+\end{lemma}
+
+Consider now any two roots $\alpha$, $\beta\in\rD_l$ such that $\alpha+\beta\not\in\rC_l\cup0$.
+Since $l\geq5$, there exists a subsystem $\Psi$ of type $\rA_4$, containing $\alpha$ and $\beta$.
+Then we can take any $a\in R_{n+1}$ and $b\in R_d$ for $d\leq n$ and apply Lemma~\ref{commute} for $\Psi$ to get
+\setcounter{equation}{0}
+\renewcommand{\theequation}{\arabic{equation}}
+\begin{align}
+\label{sx}
+[s_\alpha(a),\,x_\beta(b)]=1.
+\end{align}
+Next, using this fact we can apply again Lemma~\ref{commute} for $\Psi$ and get
+$$
+[s_\alpha(a),\,s_\beta(c)]=1
+$$
+for any $c\in R_{n+1}$. Therefore, R3.1$\!\,_{n+1}$ holds for $s_\alpha$'s.
+
+Now one can take $a\in R_d$ for $d\leq0$ and $b\in R_{n+1}$, and repeat the proof of Lemma~\ref{welldef} using~(\ref{sx}) to get
+$$
+[x_\beta(a),\,s_\gamma(b)]=\begin{cases}s_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d=0,\\x_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d<0.\end{cases}
+$$
+This finishes the proof of R2$\!\,_{n+1}$.
+
+The proof of R1$\!\,_{n+1}$ is left to the reader. The next lemma is devoted to R3.2$\!\,_{n+1}$.
+
+\begin{lemma}
+For $a\in R_d$, $b\in R_e$, $d$, $e\leq n$, $d+e=n+1$ holds
+$$
+[x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1.
+$$
+\end{lemma}
+\begin{proof}
+Take $x=x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)$, $y=x_{\alpha_{l-1}-\alpha_{l-2}}(N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}at\inv)$, and $z=x_{\alpha_{l-2}}(t)$.
+Then
+$$
+[x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=[[y\inv,\,z],\,[x,\,z]]=\,^{y\inv z}[y,\,[z\inv,\,x]]\cdot[y\inv,\,[x,\,z]].
+$$
+Next, by R3.2$\!\,_n$ we know that $x$ and $y$ commute, and therefore 
+$$
+\,^{y\inv z}[y,\,[z\inv,\,x]]=[[y\inv,\,z],\,x]=x_{\alpha_{l-1}+\alpha_{l}-\alpha_{l-2}}(Nabt\inv)
+%[x_{\alpha_{l-1}}(a),\,x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)].
+$$
+for $N=N_{\alpha_{l-1},\alpha_{l}-\alpha_{l-2}}N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}$. Finally,
+$$
+[y\inv,\,[x,\,z]]=x_{\alpha_{l-1}-\alpha_{l-2}+\alpha_l}(N'abt\inv)
+$$
+for $N'=-N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}N_{{\alpha_{l-1}-\alpha_{l-2}},\alpha_l}$.
+Since $N_{\alpha,\beta}$ are the structure constants of the Lie algebra, it follows $N=-N'$ from the Jacobi identity.
+\end{proof}
+
+Now the same argument as in Lemma~\ref{welldef} allows to prove that $[s_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1$ for $b\in R_e$, $e\leq0$, what finishes the proof of R3.2$\!\,_{n+1}$.
 

### 2019-05-09 dl-paper.tex
Fixed bugs found by Andrei in 4.1

@@
  Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
  Since the subgroup $C = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
@@
 \begin{prop} \label{Kgen}
-For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\St(\Phi, A[X], XM[X])$ and
+For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\overline{\St}(\Phi, A[X], XM[X])$ and
  the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
 \begin{proof}
- Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \St(\Phi, XM[X])$.
+ Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
 
 Now for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
-\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)],\]
-hence $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right]$ and therefore \[K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \St(\Phi, M)\right].\]
-
-It is clear that modulo $\St(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
-Thus, to verify the assertion it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, A[X], XM[X])$.
+\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)],\]
+hence $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right]$ and therefore \[K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \St(\Phi, M)\right].\]
+
+It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
+Thus, to verify the assertion it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
 Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.

### 2019-05-13 dl-paper.tex
Rewritten Proposition 4

@@
  \[dU := U \cup (U - U)\cap \Phi.\]
- In other words $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
-It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n$ (in fact, $n=2$).
+ In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
+It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n$ (in fact, for $n=2$).
 It remains to see that relation~\eqref{Z5} immediately implies the following assertion: every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
@@
 Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
-\begin{multline} \nonumber z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
+\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
  \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
@@
 \subsection{The subgroups $K(\alpha, \beta)$ and their properties}
+Throughout this section $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
+$\langle \alpha, \beta \rangle = 1$).
+We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
 \begin{df}
- Let $\alpha, \beta$ be a pair of nonopposite roots of $\Phi$. Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
- generated by the following elements:
+ Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
  \begin{enumerate}
-  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
+  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi,$ and $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
   \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$ forming a sharp angle with both $\alpha$ and $\beta$.
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$.
  \end{enumerate}
 \end{df}
-\begin{lemma} \label{root-lemma}
- For any $\alpha, \beta$ in a system of type $A_3$ there exist $\alpha_1, \alpha_2, \beta_1, \beta_2 \in \Phi$ such that
- $\alpha = \alpha_1 - \alpha_2$, $\beta = \beta_1 - \beta_2$ and root sets $\{ \pm \alpha, \pm \beta \}$ and $\{ \alpha_1, \alpha_2, \beta_1, \beta_2 \}$ have empty intersection.
-\end{lemma}
-\begin{proof} Direct calculation. \end{proof}
 
 \begin{prop} \label{K-a-b}
- Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
- the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
+ Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
 \end{prop}
 \begin{proof}
- Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
+ Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
  Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
-  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.
-
- By~\cref{Kgen-strong} we can write $g$ as a product of elements of the above family and generators of the form $c_{\pm \delta}(f, X\xi)$ for $\delta$
-  as in the above definition.
+  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
+ By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 4.
 
@@
   so this process is guaranteed to terminate.
- Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
+ To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
  (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them)
@@
 
- As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ might be transformed into terms of the form
-   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
-    $\beta = \beta_1 - \beta_2$ with the additional property $\{ \pm \alpha, \pm \beta \} \cap \{ \alpha_1, \alpha_2, \beta_1, \beta_2 \} = \emptyset$.
- Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
-  $z_\alpha(Xf, X\xi)$ as a product of generators of type 1, 2, 3. Similar argument also applies to $z_\beta(Xf, X\xi)$.
+ As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ might transform into factors of the form $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
+We can express each factor $z_\alpha(Xf, X\xi)$ through the generators of $K(\alpha, \beta)$ as follows.
+Pick a root $\gamma \in \Phi\setminus \Psi$ forming an obtuse angle with $\alpha$ and then invoke~\eqref{eq:zalpha}:
+ \begin{multline}
+  z_\alpha(Xf, X\xi) = x_{\alpha+\gamma}(\epsilon X^2f) \cdot x_{\gamma}(-X^3 \xi f) \cdot x_{-\gamma}(Xf\xi) \cdot x_\alpha(Xf) \cdot \\ \cdot z_{\alpha+\gamma}(-\epsilon X^2 f, -\epsilon \xi) \cdot z_{-\gamma}(-Xf\xi, -X) \cdot x_{-\alpha-\gamma}(-\epsilon X^2\xi^2 f) \cdot x_{-\alpha}(-X^3 f \xi^2),\ \text{for } \epsilon = N_{\alpha, \gamma}.
+ \end{multline}
+ The expression in the right-hand side is a product of generators of type 1, 1, 1, 3, 1, 1, 1, 2. Similar argument also applies to $z_\beta(Xf, X\xi)$.
 
@@
 \begin{lemma}
- Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha, \beta \rangle = 0\text{ or }1$.
- Then the image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
- generated by $K(\alpha, \beta)$ and the subgroup $U$, by definition, generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+ The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
+ generated by $K(\alpha, \beta)$ and the subgroup $U$, which, by definition, is generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
  We call these elements generators of type 5.

### 2019-05-13 dl-paper.tex
Improved typesetting of Andrei's piece

@@
 For a simply-laced root system $\Phi$ and a commutative ring $R$, the Steinberg group $\St(\Phi,\,R)$ is generated by the formal symbols $x_{\alpha}(a)$ for $\alpha\in\Phi$, $a\in R$ subject to the Steinberg relations
-\setcounter{equation}{0}
-\renewcommand{\theequation}{R\arabic{equation}}
 \begin{align}
-&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b),\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi,\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0.
+&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
 \end{align}
 
-Let $I\trianglelefteq A$ be an ideal in a commutative ring $A$ (not neccesarily proper), denote $R=\oplus_{d\in\mathbb Z}R_d\subseteq A[t,t\inv]$, where $R_d=It^d$, $d<0$, and $R_d=At^d$, $d\geq0$.
+Let $I\trianglelefteq A$ be a (not neccesarily proper) ideal of a commutative ring $A$. Denote $R=\oplus_{d\in\mathbb Z}R_d\subseteq A[t,t\inv]$, where $R_d=It^d$, $d<0$, and $R_d=At^d$, $d\geq0$.
 
@@
 
-Define trancated Steinberg groups $G_n$ for $n\geq1$ by the set of generators $x_\alpha(a)$, $\alpha\in\rD_l$, $a\in R_d$, $d\leq n$, and relations
-
-\vspace{-15pt}
-\setcounter{equation}{0}
-\renewcommand{\theequation}{R\arabic{equation}$\!\,_n$}
+Define truncated Steinberg groups $G_n$ for $n\geq1$ by the set of generators $x_\alpha(a)$, $\alpha\in\rD_l$, $a\in R_d$, $d\leq n$, and relations
+
 \begin{align}
-&\,\,x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b),\ a,b\in R_d,\ d\leq n,\\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n,\phantom{tttttttt}
-\end{align}
-\vspace{-35pt}
-\setcounter{equation}{0}
-\renewcommand{\theequation}{R3.\arabic{equation}$\!\,_n$}
-\begin{align}
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\ \alpha+\beta\not\in\rC_l\cup0,\ a\in R_d,\ b\in R_e,\ d,e\leq n,\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\ \alpha+\beta\in\rC_l\setminus\rD_l,\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n.
+&\,\,x_{\alpha}(a)x_{\alpha}(b) =  x_{\alpha}(a+b),& a,b\in R_d,\ d\leq n, \tag{R$1_n$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha\beta}\,ab),& a\in R_d,\ b\in R_e,\ d,e,d+e\leq n, \tag{R$2_n$} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha+\beta\not\in\rC_l\cup0,\ a\in R_d,\ b\in R_e,\ d,e\leq n, \tag{R$3.1_n$} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha+\beta\in\rC_l\setminus\rD_l,\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n. \tag{R$3.2_n$}
 \end{align}
@@
 We can take $\mathbb R^l$ with a base $\chi_1,\ldots,\chi_l$ and visualise root systems
-$$
-\rD_l=\{\pm\chi_i\pm\chi_j\mid1\leq i\neq j\leq l\}
-$$
+\[\rD_l=\{\pm\chi_i\pm\chi_j\mid1\leq i\neq j\leq l\}\]
 and $\rC_l=\rD_l\cup\{\pm2\chi_i\mid1\leq i\leq l\}$.
@@
 Then for some $\sigma$ from the Weyl group of $\rD_l$ we get
-$$
-\{\sigma\alpha,\sigma\beta\}=\{\chi_{l-1}-\chi_l, \chi_{l-1}+\chi_l\}=\{\alpha_{l-1},\alpha_l\}
-$$ 
+\[ \{\sigma\alpha,\sigma\beta\}=\{\chi_{l-1}-\chi_l, \chi_{l-1}+\chi_l\}=\{\alpha_{l-1},\alpha_l\} \]
 (the horns of the Dynkin diagram $\rD_l$).
@@
 Then holds
-$$
-[x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)],
-$$
+\[ [x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)], \]
 where $N=N_{\beta_1,\beta_2}N_{\beta_2,\beta_3}$.
@@
 Then Hall--Witt identity gives us
-$$
-\,^y[x,\,[y\inv,\,z]]=\,^x[[x\inv,\,y],\,z],
-$$
+\[ \,^y[x,\,[y\inv,\,z]]=\,^x[[x\inv,\,y],\,z], \]
 where $[x,\,[y\inv,z]]=[x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]$ and $[[x\inv,y],\,z]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)]$ by R2$\!\,_n$.
@@
 Moreover, with the assumption of Lemma~\ref{welldef} on $a$ and $b$ we have
-$$
-[x_{\beta}(a),\,x_{\gamma}(b)]=s_{\alpha}(N_{\beta,\gamma}\,ab).
-$$
+\[ [x_{\beta}(a),\,x_{\gamma}(b)]=s_{\alpha}(N_{\beta,\gamma}\,ab). \]
 
 The following observation is obvious.
-
-\begin{lemma}
-\label{commute}
+\begin{lemma} \label{commute}
 Consider an embedding $\iota\colon\rA_4\hookrightarrow\rD_l$ and denote $\beta_k=\iota(\alpha_k)$ for simple roots $\alpha_k$ of $\rA_4$.
 Then for any $a\in R_d$, $b\in R_e$, $c\in R_f$ with $d$, $e$, $f\leq n$ holds
-$$
-[[x_{\beta_1}(a),\,x_{\beta_2}(b)],\,x_{\beta_4}(c)]=1.
-$$
+\[ [[x_{\beta_1}(a),\,x_{\beta_2}(b)],\,x_{\beta_4}(c)]=1. \]
 \end{lemma}
@@
 Then we can take any $a\in R_{n+1}$ and $b\in R_d$ for $d\leq n$ and apply Lemma~\ref{commute} for $\Psi$ to get
-\setcounter{equation}{0}
-\renewcommand{\theequation}{\arabic{equation}}
-\begin{align}
-\label{sx}
-[s_\alpha(a),\,x_\beta(b)]=1.
-\end{align}
+\begin{equation} \label{sx} [s_\alpha(a),\,x_\beta(b)]=1. \end{equation}
 Next, using this fact we can apply again Lemma~\ref{commute} for $\Psi$ and get
-$$
-[s_\alpha(a),\,s_\beta(c)]=1
-$$
+\[ [s_\alpha(a),\,s_\beta(c)]=1 \]
 for any $c\in R_{n+1}$. Therefore, R3.1$\!\,_{n+1}$ holds for $s_\alpha$'s.
@@
 Now one can take $a\in R_d$ for $d\leq0$ and $b\in R_{n+1}$, and repeat the proof of Lemma~\ref{welldef} using~(\ref{sx}) to get
-$$
-[x_\beta(a),\,s_\gamma(b)]=\begin{cases}s_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d=0,\\x_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d<0.\end{cases}
-$$
+\[ [x_\beta(a),\,s_\gamma(b)]=\begin{cases}s_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d=0,\\x_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d<0.\end{cases} \]
 This finishes the proof of R2$\!\,_{n+1}$.
@@
 For $a\in R_d$, $b\in R_e$, $d$, $e\leq n$, $d+e=n+1$ holds
-$$
-[x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1.
-$$
+\[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1. \]
 \end{lemma}
@@
 Then
-$$
-[x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=[[y\inv,\,z],\,[x,\,z]]=\,^{y\inv z}[y,\,[z\inv,\,x]]\cdot[y\inv,\,[x,\,z]].
-$$
+\[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=[[y\inv,\,z],\,[x,\,z]]=\,^{y\inv z}[y,\,[z\inv,\,x]]\cdot[y\inv,\,[x,\,z]]. \]
 Next, by R3.2$\!\,_n$ we know that $x$ and $y$ commute, and therefore 
-$$
-\,^{y\inv z}[y,\,[z\inv,\,x]]=[[y\inv,\,z],\,x]=x_{\alpha_{l-1}+\alpha_{l}-\alpha_{l-2}}(Nabt\inv)
-%[x_{\alpha_{l-1}}(a),\,x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)].
-$$
+\[ \,^{y\inv z}[y,\,[z\inv,\,x]]=[[y\inv,\,z],\,x]=x_{\alpha_{l-1}+\alpha_{l}-\alpha_{l-2}}(Nabt\inv) \]
 for $N=N_{\alpha_{l-1},\alpha_{l}-\alpha_{l-2}}N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}$. Finally,
-$$
-[y\inv,\,[x,\,z]]=x_{\alpha_{l-1}-\alpha_{l-2}+\alpha_l}(N'abt\inv)
-$$
+\[ [y\inv,\,[x,\,z]]=x_{\alpha_{l-1}-\alpha_{l-2}+\alpha_l}(N'abt\inv) \]
 for $N'=-N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}N_{{\alpha_{l-1}-\alpha_{l-2}},\alpha_l}$.

### 2019-05-13 dl-paper.tex
Proved the last restricted axiom

@@
 \end{proof}
+
+\begin{rem} \label{rem:palpha} From the above two lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows.
+Express $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta \perp \alpha$.
+Now $p_\alpha(g)$ coincides with the sum of constant terms of the polynomials $f$ corresponding to the factors of the form $z_{-\alpha}(Xf, \xi)$ occuring in this expression.
+\end{rem}
+
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
@@
 \subsection{The subgroups $K(\alpha, \beta)$ and their properties}
-Throughout this section $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
+Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
 $\langle \alpha, \beta \rangle = 1$).
@@
  \begin{enumerate}
-  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi,$ and $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
+  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
   \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
+  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$.
@@
  Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
+Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$.
 \end{prop}
@@
 
- Finally, after collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
-  we obtain the desired decomposition for $g$. \end{proof}
+ After collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
+ we obtain the desired decomposition for $g$.
 
  It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
-The above proposition shows that this inlusion is, in fact, an equality.
-
-\begin{lemma}
- The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
+The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ by~\cref{rem:palpha} one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$.
+\end{proof}
+
+\begin{lemma} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
  generated by $K(\alpha, \beta)$ and the subgroup $U$, which, by definition, is generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
- We call these elements generators of type 5.
+We call these elements generators of type 6.
 \end{lemma}
-\begin{proof}
-By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 5, 5, 1.
-By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 5, 1, 2, 1, 1, 5, 5.
-$S(\alpha, -)$ either fixes $x_{-\beta}(X^2f)$, the other generator of type 2, or transforms them into products of generators of type 2, 1.
+\begin{proof} By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of types 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
+By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
+Clearly, $S(\alpha, -)$ transforms $x_{-\beta}(X^2f)$ into the products of generators of type 2, 1.
 Clearly, $S(\alpha, -)$ fixes both generators of type 3. 
-As for the remaining generators type 4, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 5, 5, 4.
-\end{proof}
-
-\begin{corollary} If $\alpha$ and $\beta$ form a sharp angle, then the image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
+As for the remaining generators type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5. \end{proof}
+
+\begin{corollary} The image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
 \begin{proof} Follows from the above lemma and the fact that the generators of $U$ are generators of the second type for $P_\beta(0)$ in the sense of~\cref{defP0}.
@@
 
-\begin{lemma} Suppose $\alpha$ and $\beta$ form a sharp angle, then $g \in K(A[X], M[X])$ then 
-\[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
+\begin{lemma} Suppose $g \in K(A[X], M[X])$ then \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
 \begin{proof}
@@
 
-\begin{lemma}
- If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq P_\alpha(0)$ for $a \in A$.
-\end{lemma}
-\begin{proof}
- It is clear that $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(A[X], M[X]) \subseteq P_\alpha(*)$.
-\end{proof}
+\begin{lemma} For $a \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$. \end{lemma}
+\begin{proof}
+ By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(a)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
+
+ Now let $g$ be a generator of type 2 or 3. It is clear that conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two elements of type 2 or 3.
+
+ By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
+
+ Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, a) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
 

### 2019-05-13 dl-paper.tex
Minor fix
Abridged Lemma 19 and Corollary 3

@@
 
-\begin{rem} \label{rem:palpha} From the above two lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows.
+\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows.
 Express $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta \perp \alpha$.
@@
 It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
-\[ S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\]
-
-It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the conjugation map $g \mapsto {}^{x_\alpha(aX^{-1})}\!g$.
+\begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\end{equation}
+
+It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the map of left conjugation by $x_\alpha(aX^{-1})$.
 
@@
 where $\epsilon = N_{-\alpha-\beta,\beta}$. 
-Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2.
-
-\begin{comment}
-It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
-Again choose $\beta$ to be any root such that $\alpha+\beta \in \Phi$.
-Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
-\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
- \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
-where $\epsilon = N_{\alpha,\beta}$.  
-The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
-It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
-while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
-\end{comment}
-\end{proof}
-
-\begin{lemma} \label{lem:Tulenbayev-formula} One has
- \[x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot 
- x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.\] \end{lemma}
+Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}
+
+\begin{lemma} \label{lem:Tulenbayev-formula} 
+One has 
+$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
+\end{lemma}
 \begin{proof} Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
@@
  = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}. \qedhere
+ = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
 \end{multline*}
+which implies the assertion.
 \end{proof}
@@
 \begin{proof}
-Suppose $g \in P_\alpha(m)$, then $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$ for which we already know that $S_\alpha(a, g_0) \in P(\alpha, 0)$.
-We need to verify that $h = S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)$ lies in $P\left(\alpha, \frac{m}{1 + am}\right)$, but from Lemmas~\ref{P0_conj}--\ref{lem:Tulenbayev-formula} and the antisymmetry of Steinberg symbols we obtain that:
-\begin{multline} \nonumber h = {}^{x_\alpha(aX^{-1})}\!g_0 \cdot \left(x_{\alpha}(aX^{-1}) \cdot x_{-\alpha}(mX)\right) \cdot x_{\alpha}\left(-\frac{aX^{-1}}{1+am}\right) \cdot \{X, 1+am\} \cdot h_\alpha^{-1}(1 + am) = \\
-= S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \in P_\alpha\left(\frac{m}{1+am}\right). \end{multline}
+Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
+Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
+\begin{multline} \nonumber
+S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
+\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot\langle -a, m \rangle \in P_\alpha\left(\frac{m}{1+am}\right).
+\end{multline}
+
 The second assertion can be verified in a straightforward manner. \end{proof}
-
-\begin{comment}
-\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P_\beta(0)$. \end{lemma}
-\begin{proof}
-It suffices to verify the assertion for the generators $z_\gamma(Xf, g)$, $\gamma \in \Phi$.
-By our assumption $(\alpha, \beta) \geq 0$. 
-\end{proof}
-\end{comment}
 
@@
   $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
- By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 4.
+ By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
 
@@
  By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(a)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
-
- Now let $g$ be a generator of type 2 or 3. It is clear that conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two elements of type 2 or 3.
-
- By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
-
- Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, a) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
+Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of either two elements of type 2 or two elements of type 3.
+By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
+Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, a) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
+\end{proof}
 

### 2019-05-14 dl-paper.tex
Proved the last restricted axio

@@
  $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
-  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
- Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
-  so this process is guaranteed to terminate.
+  conjugating by $x_{\epsilon}(mX)$ all factors along the way.
+ Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
  To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
@@
 
-\begin{lemma} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
- generated by $K(\alpha, \beta)$ and the subgroup $U$, which, by definition, is generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
-We call these elements generators of type 6.
-\end{lemma}
-\begin{proof} By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of types 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
+ We need one more technical definition.
+ \begin{df} Denote by $Z$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+ \end{df}
+
+\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z$.
+\end{lemma}
+\begin{proof} 
+To simplify notation we call the generators of the subgroup $Z$ ``generators of type 6``, despite the fact that these elements are not always contained in $K(\alpha, \beta)$ (or even $K(A[X], M[X])$).
+
+By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
 By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
@@
 \begin{corollary} The image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} Follows from the above lemma and the fact that the generators of $U$ are generators of the second type for $P_\beta(0)$ in the sense of~\cref{defP0}.
+\begin{proof} Follows from the above lemma and the fact that the generators of $Z$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
  Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
@@
 
-\begin{lemma} Suppose $g \in K(A[X], M[X])$ then \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
-\begin{proof}
- By~\cref{K-a-b} $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
+\begin{lemma} For $g \in K(A[X], M[X])$ there exist $m, m' \in M$ such that \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).
+\] \end{lemma}
+\begin{proof}
+ By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that
  \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
@@
 
-\begin{lemma} For $a \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof}
- By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(a)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
+\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
+\begin{proof}
+ By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
 Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of either two elements of type 2 or two elements of type 3.
-By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
-Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, a) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
-\end{proof}
+By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
+Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
+\end{proof}
+
+\begin{lemma} 
+ For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to
+ $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+\end{lemma}
+\begin{proof}
+ By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+
+ Throughout this proof we understand generator types according to~\cref{defP0}.
+It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
+
+ In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
+\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\gamma + \beta -\alpha} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi.
+\]
+Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = 
+  \langle \gamma , \alpha \rangle + \langle \beta , \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.
+{\bf TODO: } Double check that both possibilities actually occur.
+
+Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
+Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$ we obtain that $\beta - \gamma - \alpha = -\alpha$.
+Thus, by \eqref{Z3} of~\cref{Zrels}
+\[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
+The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
 
@@
  $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
- \item if $\alpha + \beta \not \in \Phi$ then ???;
 \end{enumerate}
@@
 $S_\alpha(a, g) \in P(\beta, 0);$
- \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
+ \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
  $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
- \item if $\alpha + \beta \not \in \Phi$ then ???;
 \end{enumerate}

### 2019-05-14 dl-paper.tex
Proving Lemma 26

@@
  By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
-Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
-\end{proof}
+ Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
 
@@
 \]
-Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = 
-  \langle \gamma , \alpha \rangle + \langle \beta , \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.
-{\bf TODO: } Double check that both possibilities actually occur.
+ Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = \langle \gamma , \alpha \rangle + \langle \beta, 
+ \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, 
+ therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.
 
 Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
-Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$ we obtain that $\beta - \gamma - \alpha = -\alpha$.
-Thus, by \eqref{Z3} of~\cref{Zrels}
+Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$
+we obtain that $\beta - \gamma - \alpha = -\alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
 \[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
 The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
+
+\begin{lemma}
+ For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ holds 
+ \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + N_{\alpha,-\beta} \cdot abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + N_{\alpha,-\beta} \cdot abm')) \in P\left(\alpha, \frac{m - bm'}{1+am}\right).
+\]
+\end{lemma}
+\begin{proof}
+Set $\epsilon = N_{\alpha, -\beta}$, $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
+By~\cref{K-a-b} we can write $g = g_0 \cdot $ for some $m, m' \in M$ hence by ??? we obtain that
+ \begin{multline} \nonumber 
+ S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
+ = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
+ = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
+ = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
+ =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\frac{cmX}{1+am}\right) \cdot s_0 =
+\end{multline}
+
+\end{proof}
 

### 2019-05-16 dl-paper.tex
Proved full axiom for obtuse angles

--- 2019-05-14 dl-paper.tex
@@
  \item $x_{-\alpha}(X^2f);$
- \item $x_{\alpha}(f).$ 
+ \item $x_{\alpha}(f);$
  \item Dennis--Stein symbols $\langle a, m \rangle$, $a\in A$, $m\in M$.
@@
 One has 
-$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
+$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
 \end{lemma}
@@
  = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
- = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
+ = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
 \end{multline*}
@@
 
-\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$.
+\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
 Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary}
@@
 S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
-\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot\langle -a, m \rangle \in P_\alpha\left(\frac{m}{1+am}\right).
+\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle -a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right).
 \end{multline}
@@
  We need one more technical definition.
- \begin{df} Denote by $Z$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+ \begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
  \end{df}
 
-\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z$.
+\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
 \end{lemma}
@@
 By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
-Clearly, $S(\alpha, -)$ transforms $x_{-\beta}(X^2f)$ into the products of generators of type 2, 1.
-Clearly, $S(\alpha, -)$ fixes both generators of type 3. 
-As for the remaining generators type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5. \end{proof}
+The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1.
+As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5.
+\end{proof}
 
@@
 
-\begin{lemma} For $g \in K(A[X], M[X])$ there exist $m, m' \in M$ such that \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).
+\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right).
 \] \end{lemma}
@@
  By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that
- \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
-  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\frac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
+ \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
+  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
 The assertion now follows from the preceding corollary.
@@
 \begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof}
- By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
+\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
  Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of either two elements of type 2 or two elements of type 3.
  By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
-Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
-\end{proof}
-
-\begin{lemma} 
- For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to
- $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
-\end{lemma}
-\begin{proof}
- By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+ Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
+
+\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
+\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
 
@@
 \]
-Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = 
-  \langle \gamma , \alpha \rangle + \langle \beta , \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.
-{\bf TODO: } Double check that both possibilities actually occur.
+ Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = \langle \gamma , \alpha \rangle + \langle \beta, 
+ \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, 
+ therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.
 
 Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
-Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$ we obtain that $\beta - \gamma - \alpha = -\alpha$.
-Thus, by \eqref{Z3} of~\cref{Zrels}
+Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$
+we obtain that $\beta - \gamma - \alpha = -\alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
 \[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
 The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
+
+\begin{lemma} \label{lem:SRobtuse}
+ For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ the element
+ \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
+ belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
+\end{lemma}
+\begin{proof}
+Set $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
+From the definition of $S_\alpha(a, -)$ we obtain that
+ \begin{multline} \label{eq:SRobtuse-computation}
+ S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
+ = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
+ = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
+ = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
+ =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
+ = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
+\end{multline}
+Denote by $h_0$ the product of all terms except the first and the last one in the above formula.
+Clearly, $h_0$ is a product of generators of $P_\alpha(0)$ of type 1, 2, 6, 6.
+Now by~\cref{K-a-b} we can write $g = g_0 x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for $g_0 \in K(\alpha, \beta)$.
+The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
+\begin{multline} \nonumber
+ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
+  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
+\end{multline}
+
+\end{proof}
 
@@
  \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then $S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
- \item If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
+ \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
  $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$

### 2019-05-16 dl-paper.tex
Small fixes

@@
 \begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] \end{df}
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha.\] \end{df}
 It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
-\begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\end{equation}
+\begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\end{equation}
 
@@
 Clearly, $h_0$ is a product of generators of $P_\alpha(0)$ of type 1, 2, 6, 6.
-Now by~\cref{K-a-b} we can write $g = g_0 x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for $g_0 \in K(\alpha, \beta)$.
+Now by~\cref{K-a-b} we can write $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for $g_0 \in K(\alpha, \beta)$.
 The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
@@
 \end{multline}
-
-\end{proof}
-
-\begin{comment}
-\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
-\begin{proof}
- By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
- $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.
-
- It remains to notice that the only factors in the right-hand sides of in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} which do not vanish after evaluation at $X=0$
-  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
-\end{proof}
-\end{comment}
+\end{proof}
 

### 2019-05-17 dl-paper.tex
Many minor fixes

@@
 In our computations we will use two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
-\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \]
+\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \end{equation}
 
@@
  \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
-
 \end{proof}
@@
 
-\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
+\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
 \begin{df} \label{defP0}
@@
  \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, \xi),\ \alpha \perp \beta;$
+ \item $z_{\beta}(f, \xi),\ \beta \in Z_0(\alpha);$
  \item $x_{-\alpha}(X^2f);$
- \item $x_{\alpha}(f);$
- \item Dennis--Stein symbols $\langle a, m \rangle$, $a\in A$, $m\in M$.
+ \item $x_{\alpha}(f)$.
 \end{enumerate}
-In the above formulae and for the rest of this subsection we assume $f \in M[X]$ and $\xi \in A[X]$.
-\end{df}
+In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}
+
+\begin{rem}\label{rem:c-DS}
+From our assumptions on $\Phi$ it follows that $Z_0(\alpha)$ is nonempty, hence $P_\alpha(0)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ ($a\in A$, $m\in M$) and elements $c_{\pm \gamma}(f, X\xi)$ for $\gamma \in Z_0(\alpha)$ (both can be expressed as products of generators of type 3).
+\end{rem}
 
 Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$.
-The following lemma shows that this subgroup is sufficiently large.
+The following lemma shows that the resulting subgroup is sufficiently large.
 \begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$. 
-Invoking~\eqref{Z5} of~\cref{Zrels} with $s = Xf$, $\eta = 1$ we obtain that $z_{\pm\alpha}(Xf, \xi)$ also belong to $P_{\alpha}(*)$.
-Thus, we have shown that $P_\alpha(*)$ contains $\St(\Phi, A[X], XM[X])$.
-
-Now choose $\gamma$ to be arbitrary root orthogonal to $\alpha$. By~\cref{Kgen-strong} we are left to prove that $c_{\pm \gamma}(f, X\xi)$ lies in $P_\alpha(*)$. 
-But $c_{\pm \gamma}(f, X\xi) = x_{\pm \gamma}(f) \cdot z_{\pm \gamma}(-f, -X\xi)$ is a product of two generators of $P_\alpha(0)$ of type 3. \end{proof}
-
-The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
- it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $\St(\Phi, A[X], XM[X])$.
+The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
+\end{proof}
+
+The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
  elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
@@
 We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
-The assertion is obvious for the generators of type 3, 4 and 6.
+The assertion is obvious for the generators of type 3 and 4.
 
@@
 
-\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows.
-Express $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta \perp \alpha$.
-Now $p_\alpha(g)$ coincides with the sum of constant terms of the polynomials $f$ corresponding to the factors of the form $z_{-\alpha}(Xf, \xi)$ occuring in this expression.
+\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed via the following procedure.
+Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$.
+Now pick among these factors those that correspond to the root $\beta = -\alpha$ (i.\,e.
+pick all factors $z_{-\alpha}(Xf_i, \xi_i)$).
+Now $p_\alpha(g)$ is precisely the sum of constant terms of the polynomials $f_i$.
 \end{rem}
@@
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
+From the preceding lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
 
@@
 \begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
-The assertion is clear for generators of type 3, 5 and 6.
+The assertion is clear for generators of type 3 and 5.
 First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
@@
 \end{lemma}
-\begin{proof} Since $\Phi$ is nonsymplectic, we can choose some $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
+\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$.
+Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein} shows that
  \begin{multline*}
- x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
- = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
  = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
@@
 
-\begin{prop} \label{K-a-b}
- Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
+\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
 Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$.
 \end{prop}
-\begin{proof}
- Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
- Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
-  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
+\begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
+Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
 By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
@@
  The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
- $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
-  conjugating by $x_{\epsilon}(mX)$ all factors along the way.
+ $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position conjugating by $x_{\epsilon}(mX)$ all factors along the way.
  Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
  To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them)
-  have terms of degree at least $2$ in $X$.
+ (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them) have terms of degree at least $2$ in $X$.
 
@@
 
- After collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
- we obtain the desired decomposition for $g$.
+ After collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression we obtain the desired decomposition for $g$.
 
  It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
-The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ by~\cref{rem:palpha} one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$.
+The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
 \end{proof}
@@
  We need one more technical definition.
- \begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
- \end{df}
+ \begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.\end{df}
 
@@
 \end{lemma}
-\begin{proof} 
-To simplify notation we call the generators of the subgroup $Z$ ``generators of type 6``, despite the fact that these elements are not always contained in $K(\alpha, \beta)$ (or even $K(A[X], M[X])$).
-
-By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
-By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
+\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
+By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
+By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
 The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1.
-As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5.
-\end{proof}
-
-\begin{corollary} The image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} Follows from the above lemma and the fact that the generators of $Z$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
+As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5.
+\end{proof}
+
+\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
  Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
@@
 
-\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right).
+\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right).
 \] \end{lemma}
-\begin{proof}
- By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that
- \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
   S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
@@
 By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
- Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
+Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
+\end{proof}
 
@@
 \begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
-
- Throughout this proof we understand generator types according to~\cref{defP0}.
+Throughout the proof we understand generator types according to~\cref{defP0}.
 It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
@@
  In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
-\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\gamma + \beta -\alpha} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi.
-\]
- Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = \langle \gamma , \alpha \rangle + \langle \beta, 
- \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, 
- therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.
+\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{-\alpha + \gamma + \beta} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi.
+\] Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
+ hence $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$ and the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.
 
 Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
-Since $\langle \beta - \gamma - \alpha , \alpha \rangle = \langle \beta , \alpha \rangle - \langle \gamma , \alpha \rangle - \langle \alpha, \alpha \rangle \leq 1 - 1 - 2 = -2$
-we obtain that $\beta - \gamma - \alpha = -\alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
+Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
+we obtain that $\alpha - \beta + \gamma = \alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
 \[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
@@
 
-\begin{lemma} \label{lem:SRobtuse}
- For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ the element
- \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
+\begin{lemma} \label{lem:SRobtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
  belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
 \end{lemma}
-\begin{proof}
-Set $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
+\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
 From the definition of $S_\alpha(a, -)$ we obtain that
@@
 Denote by $h_0$ the product of all terms except the first and the last one in the above formula.
-Clearly, $h_0$ is a product of generators of $P_\alpha(0)$ of type 1, 2, 6, 6.
-Now by~\cref{K-a-b} we can write $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for $g_0 \in K(\alpha, \beta)$.
+It is clear that $h_0$ lies in $P_\alpha(0)$.
+Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$.
 The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:

### 2019-05-17 dl-paper.tex
Fixed Andrei's remarks

@@
 
-The following lemma summarizes basic properties of structure constants used in the computations below.
+The following lemma summarizes basic properties of structure constants which will be used in the computations below, often without explicit reference.
 \begin{lemma} Suppose $\alpha, \beta \in \Phi$ are such that $\alpha+\beta \in \Phi$.
@@
 \item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
-\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
-\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
-\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
+\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = x_{\alpha} (- s\xi \eta) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
+\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = x_{\alpha} (s\xi \eta) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
+
+\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
 \item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
@@
 
-\begin{comment}
-For a subset of roots $S \subseteq \Phi$ denote by $\mathcal{Z}(S, R, I)$ the subset of $\overline{\St}(\Phi, R, I)$ consisting of the following two families of elements:
-\begin{itemize}
- \item $x_\alpha(s)$, $\alpha \in \Phi$, $s\in I$;
- \item $z_\alpha(s, \xi)$, $\alpha \in S$, $s\in I$, $\xi \in R$.
-\end{itemize}
-
-\begin{lemma} \label{weak-Stepanov} For any $\Phi$ of rank $\geq 2$ the set $\mathcal{Z}(\Phi, R, I)$ generates $\overline{\St}(\Phi, R, I)$ as a group.
- Further, if $\Phi$ is simply laced $\overline{\St}(\Phi, R, I)$ is generated by even smaller set $\mathcal{Z}(\Phi\setminus\{\alpha, \beta\}, R, I)$, 
-  where $\alpha, \beta \in \Phi$ are arbitrary roots of $\Phi$. \end{lemma}
-\begin{proof}
- The first assertion is well-known, see the first part of~\cite[Lemma~4]{S15}.
- Notice that it follows from relation~\eqref{Z5} that $\mathcal{Z}(S, R, I)$ generates the same group as $\mathcal{Z}(S \cup (S - S), R, I)$.
- The second assertion then follows from the first one and the fact that for $S := \Phi \setminus \{ \alpha, \beta \}$ one has $S \cup (S - S) = \Phi$.
-\end{proof}
-{\bf TODO:} Probably, in the same fashion we could reprove Stepanov's theorem in the simply laced case.
-\end{comment}
-
 For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
@@
 
-\begin{rem}
- For a simply-laced $\Phi$ the second assertion of~\cref{thm:Stepanov} can be deduced from the first one by means of~\cref{Zrels}.
-Indeed, for a root subset $U\subseteq \Phi$ consider the following operation:
- \[dU := U \cup (U - U)\cap \Phi.\]
- In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
+\begin{rem} For a simply-laced $\Phi$ the second assertion of~\cref{thm:Stepanov} can be deduced from the first one by means of~\cref{Zrels}.
+Indeed, for a root subset $U\subseteq \Phi$ consider the following operation: \[dU := U \cup (U - U)\cap \Phi.\] In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
 It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n$ (in fact, for $n=2$).
@@
 
-{\bf TODO:} One can write analogue of~\eqref{Z5} in the nonsimply-laced case and the above argument still applies.
-
 For the proof of the following lemma we will need the following variant of Hall--Witt identity:
-\begin{equation} \label{HW-variant} [x, [ y, z]] = \left([[ x^{-1}, y^{-1}], z] ^ {x^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}}\right)^{y^{-1}}.\end{equation}
+\begin{equation} \label{HW-variant} [[x, y], z] = \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}.\end{equation}
 
@@
  \begin{enumerate}
-  \item \label{C1} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi)$ if $\alpha-\beta \in \Phi$;
-  \item \label{C2} $[c_\beta(s, t), x_{-\alpha}(\xi)] = x_{-\alpha}(st\xi + s^2t^2\xi) \cdot x_{-\alpha-\beta}(N_{\alpha, \beta}st^2\xi)$ if $\alpha+\beta \in \Phi$;
-  \item \label{C3} $[c_\beta(s, t), x_{-\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;
+ \item \label{C1} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(- st\xi) \cdot x_{\beta+\alpha}(N_{\alpha,\beta}s^2t\xi)$ if $\alpha+\beta \in \Phi$;
+ \item \label{C2} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(st\xi + s^2t^2\xi) \cdot x_{\alpha-\beta}(N_{-\alpha, \beta}st^2\xi)$ if $\alpha-\beta \in \Phi$;  
+ \item \label{C3} $[c_\beta(s, t), x_{\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;  
  \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
@@
 \begin{proof}
-To verify~\eqref{C1} suppose $\alpha - \beta \in \Phi$ and compute
-\begin{multline} \nonumber [c_{\beta}(s, t), x_{-\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta-\alpha}(N_{-\alpha, \beta} s\xi)] = \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\beta-\alpha}(N_{-\alpha, \beta}s\xi)] = x_{-\alpha}(- st\xi) \cdot x_{\beta-\alpha}(N_{-\alpha,\beta}s^2t\xi). \end{multline}
-
-Now suppose $\alpha+\beta \in \Phi$. From~\eqref{HW-variant} we obtain that \begin{multline} \nonumber
-[x_{-\alpha}(\xi), [x_\beta(s), x_{-\beta}(t)]] = \\ 
-= \left([[ x_{-\alpha}(-\xi), x_\beta(-s)], x_{-\beta}(t)] ^ {x_{-\alpha}(-\xi)} \cdot  [[ x_{-\beta}(-t), x_{-\alpha}(\xi)], x_\beta(-s)] ^ {x_{-\beta}(-t)}\right)^{x_\beta(-s)} =  \\ = [x_{-\beta-\alpha}(-N_{-\beta,-\alpha}t\xi), x_\beta(-s)] ^ {x_{-\beta}(-t) x_\beta(-s)} = x_{-\alpha}(-st\xi) ^ {x_{-\beta}(-t) x_\beta(-s)} = \\
-= (x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi))^{x_\beta(-s)} = x_{-\alpha-\beta}(-N_{\alpha, \beta}st^2\xi) \cdot x_{-\alpha}(-st\xi - s^2t^2\xi),
-\end{multline} which implies~\eqref{C2}.
-
-Finally, relation~\eqref{C4} can be verified by the following direct computation, which involves identities~\eqref{HW-variant} and $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$:
+To verify~\eqref{C1} suppose $\alpha + \beta \in \Phi$ and compute
+\begin{multline} \nonumber [c_{\beta}(s, t), x_{\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] \cdot [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta+\alpha}(N_{\alpha, \beta} \cdot s\xi)] = \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
+
+In the case $\alpha-\beta \in \Phi$ the second assertion directly follows from~\eqref{HW-variant}:
+\begin{multline} \nonumber
+[[x_\beta(s), x_{-\beta}(t)], x_{\alpha}(\xi)] = \\
+= \left([x_\beta(-s), [ x_{-\beta}(-t), x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot [x_{-\beta}(t), [ x_{\alpha}(-\xi), x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\right)^{x_\beta(-s)} = \\
+= x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = \\
+= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi). \end{multline}
+
+Finally, the final relation can be verified by the following direct computation, which involves identity $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ and \eqref{HW-variant} with both sides of the equation inverted:
 \begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
@@
 By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
-The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a products of generators of type 2, 1.
+The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 1.
 As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5.
@@
 \begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.
-Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of either two elements of type 2 or two elements of type 3.
+\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of generators of type 4, 1, 1.
+Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
 By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.

### 2019-05-18 dl-paper.tex
Writing proof of the injectivity theorem

@@
 We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
- $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
 
@@
               G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \] 
-
-\begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
-\begin{proof}
- Lol
-\end{proof}
-
-Let $P(\alpha, m)$ be a collection of subsets of $\overline{G}^{\geq 0}_M$ with the following properties:
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ \ g \in P(\alpha, m)\text{ for some $m \in M$}.\]
-
-$P(\alpha, a) P(\alpha, b) \subseteq P(\alpha, a + b)$.
-In particular, $P(\alpha, 0)$ is a subgroup.
-This hints us that there is a well-defined map $map_\alpha \colon G_M^{\geq 0} \to M$
-
-Let us show that this suffices to verify Steinberg additivity relation:
-
-Consider the set $V' = \St(\Phi, R[X, X^{-1}]) \times \St(\Phi, R[X^{-1}]) \times (1 + M)^*$.
-Denote by $V'_0$ the subset of $V'$ consisting of those $(g, h, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
-The the following operator is defined for those $(g, h, u)$, for which $\pi(g, h, u) \in P(\alpha, m)$
-\[ T_\alpha(aX^{-1})(g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
-                                         h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right),\ 
-                                         u(1 + am)\right).\]
+Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$ and by $C$ the set of left cosets of $\overline{G}_M^0$ in $G^{\leq 0}$, i.\,e.
+$C = \{ g\overline{G}^0_M \mid g \in G^{\leq 0} \}.$
+
+Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$ consisting of those triples $(g, h \overline{G}^0_M, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
+The correctness of this definition is clear from the above commutative diagram.
+
+The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a  function $T_\alpha(aX^{-1}) \colon V \to V$.
+This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
+If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is defined via the following identity:
+\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
+                                         h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ 
+                                         u \cdot (1 + am)\right).\]
+It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$
+
+The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
 We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
@@
 The latter expression is symmetric.
-
+\begin{comment}
 If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
@@
 Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
+
 \begin{multline}
@@
 We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
-
+\end{comment}
 \printbibliography

### 2019-05-18 dl-paper.tex
Proving one more lemma

@@
 \[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
-\begin{proof} 
-We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
 The assertion is obvious for the generators of type 3 and 4.
@@
 
-Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$ consisting of those triples $(g, h \overline{G}^0_M, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
-The correctness of this definition is clear from the above commutative diagram.
-
-The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a  function $T_\alpha(aX^{-1}) \colon V \to V$.
+Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times G^{\leq 0} \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
+$\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
+Denote by $\overline{V}$ the image of $V$ in $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$
+under the obvious map induced by the projection $G^{\leq 0} \to C$
+ (of course, these triples still can be characterized by the property that $(g, h \overline{G}^0_M, u) \in \overline{V}$ iff $\pi(g, h, u) \in \overline{G}_M^{\geq 0}$).
+
+The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $T_\alpha(aX^{-1}) \colon V \not\to V$.
 This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is defined via the following identity:
+If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is given by the following identity:
 \[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
@@
 It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$
+
+\begin{lemma} $T_\alpha(aX^{-1})$ descends to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
+\begin{proof}
+ First of all, let us show that the resulting function is total. 
+ We need to show that for every $(g, h\overline{G}^0_M, u) \in \overline{V}$ we can find a representative $h' \in h\overline{G}^0_M$
+ such that $\pi(g, h', u) \in P_\alpha(*)$. Set $h' = h \cdot ev_{X=0}(\pi(g, h, u))^{-1}$, then
+  \[\pi(g, h', u) = g \cdot j_-(h) \cdot \{ X, u \} \cdot \left(ev_{X=0}(g \cdot j_-(h))\right)^{-1} \in Im(K(A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])) \subseteq P_\alpha(*).\]
+
+ Next, we have to show that the value of $T_\alpha(aX^{-1})$ is well-defined. Suppose $(g, h_1, u), (g, h_2, u) \in V$ are such that 
+  both $\pi(g, h_1, u)$ and $\pi(g, h_2, u)$ lie in $P_\alpha(*)$. Consequently, $j_-(h_1 h_2^{-1}) \in P_\alpha(*)$.
+
+\end{proof}
 

### 2019-05-18 dl-paper.tex
Written down formulas deducing the claim for orthogonal roots

@@
 \end{comment}
+\begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
+ = [x_{-\beta}(b'X^{-1}), {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$3_1$ for sharp angles}\\
+ = [[x_{-\beta-\gamma}(b''), x_\gamma(X^{-1})], {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
+ = [x_{-\beta-\gamma}(b''), [x_\gamma(X^{-1}), x_{\alpha+\beta}(1)]] & \text{ by R$3_0$}\\
+ = x_{\alpha}(b'''X^{-1}) & \text{ by R$2_1$.} \end{align*}
+
+\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
+ = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
+ = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
+ = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
+ = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
+
 \printbibliography

### 2019-05-20 dl-paper.tex
Minor

@@
 \DeclareMathOperator{\Ker}{Ker}
+\DeclareMathOperator{\Img}{Im}
 \DeclareMathOperator{\St}{St}
@@
 Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
- map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
+ map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
 \begin{enumerate}
@@
 \begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $\St(\Phi, A[X], XM[X])$.
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
 The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
@@
 
-The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
- elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
- and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.
+\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists of images under $j_+$ of those elements 
+ $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $C_\alpha(A, M) := \Img(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)) \ltimes \hat{U}(Z_+(\alpha), M)$
+ (i.\,e. the subgroup generated by elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
+ and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}). \end{rem}
 
@@
               G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \] 
-Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$ and by $C$ the set of left cosets of $\overline{G}_M^0$ in $G^{\leq 0}$, i.\,e.
-$C = \{ g\overline{G}^0_M \mid g \in G^{\leq 0} \}.$
+Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$.
 
 Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times G^{\leq 0} \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
-$\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
-Denote by $\overline{V}$ the image of $V$ in $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$
-under the obvious map induced by the projection $G^{\leq 0} \to C$
- (of course, these triples still can be characterized by the property that $(g, h \overline{G}^0_M, u) \in \overline{V}$ iff $\pi(g, h, u) \in \overline{G}_M^{\geq 0}$).
+$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
+We let $\overline{G}_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot h_0, u)$, $h_0 \in \overline{G}_M^0$.
+It is clear that this action is well defined. Denote by $\overline{V}$ the quotient set $V / \overline{G}_M^0$.
 
 The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $T_\alpha(aX^{-1}) \colon V \not\to V$.
-This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is given by the following identity:
-\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
-                                         h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ 
-                                         u \cdot (1 + am)\right).\]
-It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$
+This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
+If $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is given by the following identity:
+\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
+It is easy to verify that $p(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, p(g, h, u)).$
 
@@
  First of all, let us show that the resulting function is total. 
- We need to show that for every $(g, h\overline{G}^0_M, u) \in \overline{V}$ we can find a representative $h' \in h\overline{G}^0_M$
- such that $\pi(g, h', u) \in P_\alpha(*)$. Set $h' = h \cdot ev_{X=0}(\pi(g, h, u))^{-1}$, then
-  \[\pi(g, h', u) = g \cdot j_-(h) \cdot \{ X, u \} \cdot \left(ev_{X=0}(g \cdot j_-(h))\right)^{-1} \in Im(K(A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])) \subseteq P_\alpha(*).\]
-
- Next, we have to show that the value of $T_\alpha(aX^{-1})$ is well-defined. Suppose $(g, h_1, u), (g, h_2, u) \in V$ are such that 
-  both $\pi(g, h_1, u)$ and $\pi(g, h_2, u)$ lie in $P_\alpha(*)$. Consequently, $j_-(h_1 h_2^{-1}) \in P_\alpha(*)$.
-
+ Fix $c = [(g, h, u)] \in \overline{V}$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
+ Set $h_0 = ev_{X=0}(g_1))^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
+ $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
+  which shows that $(g, h \cdot i_+(h_0), u)$ is the representative of $c$ on which $T_\alpha(aX^{-1})$ is defined.
+
+ Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
+ Let $(g, h_1, u), (g, h_2, u)$ be a pair of representatives of the same $c \in \overline{V}$ for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ lie in $P_\alpha(*)$.
+ By definition, $h_1 h_2^{-1} = i_-(h_0)$, for $h_0 \in \overline{\St}(\Phi, A, M)$, moreover, $p(g, h_1, u) \cdot p(g, h_2, u)^{-1} = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$,
+ Clearly, $ev_{X=1}(j_+ i_+ (h_0)) = ev_{X=1}(i_+(h_0)) = ev_{X=0}(i_+(h_0)) = h_0$.
+ On the other hand, by~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $ev_{X=0}(g_1) \in C_\alpha(A, M)$
+  and $j_+(g_1) = j_+ i_+ (h_0)$.
+ Now we have: $h_0 = ev_{X=1}(j_+(g_1)) = ev_{X=1}(g_1)$
+
+ %Invoking injective stability for $\K_1(\Phi, -)$ and surjective stability $\K_2(\Phi, -)$ we can find $h_0 \in \overline{\St}(Z_0(\alpha), A, M) \ltimes U(Z_+(\alpha), M)$ such that $\pi(h_0) = \pi(j_-(h_1 h_2^{-1}))$.
 \end{proof}

### 2019-05-21 dl-paper.tex
Sketched the proof of Lemma on descent

@@
 \begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists of images under $j_+$ of those elements 
- $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $C_\alpha(A, M) := \Img(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)) \ltimes \hat{U}(Z_+(\alpha), M)$
+ $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M) := \Img(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)) \ltimes \hat{U}(Z_+(\alpha), M)$
  (i.\,e. the subgroup generated by elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
@@
 
-The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $T_\alpha(aX^{-1}) \colon V \not\to V$.
+The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
 This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is given by the following identity:
-\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
-It is easy to verify that $p(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, p(g, h, u)).$
-
-\begin{lemma} $T_\alpha(aX^{-1})$ descends to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
+If $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
+\[ t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
+It is easy to verify that $p(t_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, p(g, h, u)).$
+
+\begin{lemma} Let $\Phi$ be any root system of rank $\geq 3$, $\alpha \in \Phi$ and $(A, M)$ be a local pair.
+ Then the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
+  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
 \begin{proof}
  First of all, let us show that the resulting function is total. 
- Fix $c = [(g, h, u)] \in \overline{V}$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
- Set $h_0 = ev_{X=0}(g_1))^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
+ Fix $c = [g, h, u] \in \overline{V}$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
+ Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $(g, h \cdot i_+(h_0), u)$ is the representative of $c$ on which $T_\alpha(aX^{-1})$ is defined.
+  which shows that $(g, h \cdot i_+(h_0), u)$ is the representative of $c$ on which $t_\alpha(aX^{-1})$ is defined.
 
@@
  Let $(g, h_1, u), (g, h_2, u)$ be a pair of representatives of the same $c \in \overline{V}$ for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ lie in $P_\alpha(*)$.
- By definition, $h_1 h_2^{-1} = i_-(h_0)$, for $h_0 \in \overline{\St}(\Phi, A, M)$, moreover, $p(g, h_1, u) \cdot p(g, h_2, u)^{-1} = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$,
- Clearly, $ev_{X=1}(j_+ i_+ (h_0)) = ev_{X=1}(i_+(h_0)) = ev_{X=0}(i_+(h_0)) = h_0$.
- On the other hand, by~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $ev_{X=0}(g_1) \in C_\alpha(A, M)$
-  and $j_+(g_1) = j_+ i_+ (h_0)$.
- Now we have: $h_0 = ev_{X=1}(j_+(g_1)) = ev_{X=1}(g_1)$
-
- %Invoking injective stability for $\K_1(\Phi, -)$ and surjective stability $\K_2(\Phi, -)$ we can find $h_0 \in \overline{\St}(Z_0(\alpha), A, M) \ltimes U(Z_+(\alpha), M)$ such that $\pi(h_0) = \pi(j_-(h_1 h_2^{-1}))$.
-\end{proof}
+ By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in \overline{\St}(\Phi, A, M)$, moreover, 
+  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
+ By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
+ From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
+ the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, therefore $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
+ By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$.
+ It is not hard to check using e.\,g. the table on p.~986 of~\cite{St71} that $Z_0(\alpha)$ always contains a long root, therefore
+  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by ??? hence $h_0 \in Z_\alpha(A, M)$.
+ Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$ therefore
+ \begin{multline} \nonumber
+  T_\alpha(aX^{-1})[g, h_1, u] = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = \\
+  = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = T_\alpha(aX^{-1})[g, h_2, u]. \qedhere
+ \end{multline} \end{proof}
 

### 2019-05-21 dl-paper.tex
Changed notation for Dennis--Stein symbols

@@
 
-Recall also that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 - rs \in R^*$ as follows:
+Recall also that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^*$ as follows:
 \begin{equation} \label{eq:dennis-stein}
- \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}.
+ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- s}{1 + rs}\right) \cdot x_{\alpha}(r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\tfrac{- r}{1+rs}\right) \cdot h_{\alpha}(1 + rs)^{-1}.
 \end{equation} 
+Notice that our notation follows~\cite{DS73} and {\it not}~III.5.11 of~\cite{Kbook}.
+
+Dennis--Stein symbols and Steinberg symbols are related to each other via the following identities:
+\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^*,\ \
+ \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^* \end{equation}
 
@@
     \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R)
-   } \]
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
 Then there exists a diagonal arrow which makes the diagram commute.   
@@
 One has 
-$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am).$
+$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
 \end{lemma}
@@
  x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
- = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
+ = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
 \end{multline*}
@@
 S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
-\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle -a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right).
+\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right).
 \end{multline}
@@
 \] \end{lemma}
-\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
-  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
+  S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
 The assertion now follows from the preceding corollary.
@@
 \end{lemma}
-\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
+\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
 From the definition of $S_\alpha(a, -)$ we obtain that

### 2019-05-22 dl-paper.tex
Fixed some issues

@@
 
-\begin{lemma}
-For $a\in R_d$, $b\in R_e$, $d$, $e\leq n$, $d+e=n+1$ holds
-\[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1. \]
-\end{lemma}
-\begin{proof}
-Take $x=x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)$, $y=x_{\alpha_{l-1}-\alpha_{l-2}}(N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}at\inv)$, and $z=x_{\alpha_{l-2}}(t)$.
+\begin{lemma} For $a\in R_d$, $b\in R_e$, $d$, $e\leq n$, $d+e=n+1$ holds \[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1. \] \end{lemma}
+\begin{proof} Take $x=x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)$, $y=x_{\alpha_{l-1}-\alpha_{l-2}}(N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}at\inv)$, and $z=x_{\alpha_{l-2}}(t)$.
 Then
@@
 \begin{equation} \label{relZero-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).\end{equation}
-\begin{lemma} 
-The following decomposition holds
- \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] 
-\end{lemma}
-\begin{proof}
- Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+\begin{lemma} The following decomposition holds
+ \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
+\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
  It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
@@
  (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C$,
- which implies the assertion. \qedhere
-\end{proof}
+ which implies the assertion. \qedhere \end{proof}
 
@@
 
-\begin{prop} \label{Kgen}
-For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\overline{\St}(\Phi, A[X], XM[X])$ and
+\begin{prop} \label{Kgen} For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\overline{\St}(\Phi, A[X], XM[X])$ and
  the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
-\begin{proof}
- Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
+\begin{proof} Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
 
@@
 
-\begin{corollary} \label{Kgen-strong}
- For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\St(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(f, \eta)$, $f \in M[X]$, $\eta \in XA[X]$.
-\end{corollary}
-\begin{proof}
- Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
- Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo 
- $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to 
- $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
- Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$
- belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
- Similar argument also works for the negative roots, and the required assertion now follows.
-\end{proof}
-
-\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
-\begin{df} \label{defP0}
-Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
+\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by
+ $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
+\begin{proof} Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
+ Invoking~\eqref{C4} of~\cref{Crels} with $\xi = 1$, $s = m$, $t = X\eta$ we obtain that modulo 
+ $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to 
+ $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
+ Arguing by induction on the height of $\alpha$ we conclude that $c_\alpha(m, X\eta)$ for all $\alpha \in \Phi^+$
+ belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(m, X\eta)$.
+ Similar argument also works for the negative roots, and the required assertion now follows. \end{proof}
+
+\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} 
+Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
+
+Consider the following root subsets of $\Phi$ (cf.~\cite[Proposition~5.7]{St71}):
+\begin{equation} \nonumber \begin{align}
+   Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
+   Z_0(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle = 0 \}, \\
+   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} \end{equation}
+
+We denote by $Z_\alpha(A, M)$ the subgroup of $\overline{\St}(\Phi, A, M)$ generated by elements
+ $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$.
+It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes \hat{U}(Z_+(\alpha), M). \]
+Notice that the subgroup $Z_\alpha(A, A)$ coincides with $Z(\hat{U}_\alpha)$ defined in~\cite[984]{St71}.
+
+\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, 
+hence $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
+By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^*$, $m\in M$. \end{rem}
+
+\begin{df} \label{defP0} Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
  map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
-\begin{enumerate}
- \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, \xi),\ \beta \in Z_0(\alpha);$
+\begin{enumerate} \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
+ \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
+ \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
  \item $x_{-\alpha}(X^2f);$
- \item $x_{\alpha}(f)$.
-\end{enumerate}
+ \item $x_{\alpha}(f)$. \end{enumerate}
 In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}
 
-\begin{rem}\label{rem:c-DS}
-From our assumptions on $\Phi$ it follows that $Z_0(\alpha)$ is nonempty, hence $P_\alpha(0)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ ($a\in A$, $m\in M$) and elements $c_{\pm \gamma}(f, X\xi)$ for $\gamma \in Z_0(\alpha)$ (both can be expressed as products of generators of type 3).
-\end{rem}
-
-Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(Xm)$, $m \in M$.
+\begin{rem}\label{rem:c-DS} It is easy to check that $P_\alpha(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
+In particular, it contains the relative Dennis--Stein and Steinberg symbols.
+It is also clear that $P_\alpha(0)$ contains the elements $c_{\pm \beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
+ (they can be factored as products of two elements of type 2 or 3). \end{rem}
+
+Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
 The following lemma shows that the resulting subgroup is sufficiently large.
@@
 
-\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists of images under $j_+$ of those elements 
- $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M) := \Img(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)) \ltimes \hat{U}(Z_+(\alpha), M)$
- (i.\,e. the subgroup generated by elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
- and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}). \end{rem}
+\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of images under $j_+$ of all elements 
+ $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
 
@@
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
-  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \nonumber \end{align}
+  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \end{align}
 The expressions in the right hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
@@
 Suppose $g$ has type 1 and  $\alpha + \beta \in \Phi$. By~\cref{Zrels} 
-\begin{equation} \label{eq3-2} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
+\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
 and the latter expression is a product of generators of type $4, 1, 1$.
@@
  \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
-and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4.
-\end{proof}
+and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}
 
@@
 Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. 
-Now pick among these factors those that correspond to the root $\beta = -\alpha$ (i.\,e.
-pick all factors $z_{-\alpha}(Xf_i, \xi_i)$).
-Now $p_\alpha(g)$ is precisely the sum of constant terms of the polynomials $f_i$.
-\end{rem}
+Now pick among these factors those that correspond to the root $\beta = -\alpha$ (i.\,e. pick all factors $z_{-\alpha}(Xf_i, \xi_i)$). 
+Now $p_\alpha(g)$ is precisely the sum of constant terms of the polynomials $f_i$. \end{rem}
 
@@
 \begin{lemma} \label{lem:Tulenbayev-formula} 
-One has 
-$ S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
+One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
 \end{lemma}
@@
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\},
-\end{multline*}
-which implies the assertion.
-\end{proof}
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}, \end{multline*}
+which implies the assertion. \end{proof}
 
 \begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
-Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary}
-\begin{proof}
+Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
 Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
 Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
-\begin{multline} \nonumber
-S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
-\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right).
-\end{multline}
+\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
+\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}
 
@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df}
- Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
+\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
  \begin{enumerate}
@@
   \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$.
- \end{enumerate}
-\end{df}
+  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
 
@@
  Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
- To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
+ To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-3} 
  (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them) have terms of degree at least $2$ in $X$.
@@
 Pick a root $\gamma \in \Phi\setminus \Psi$ forming an obtuse angle with $\alpha$ and then invoke~\eqref{eq:zalpha}:
- \begin{multline}
-  z_\alpha(Xf, X\xi) = x_{\alpha+\gamma}(\epsilon X^2f) \cdot x_{\gamma}(-X^3 \xi f) \cdot x_{-\gamma}(Xf\xi) \cdot x_\alpha(Xf) \cdot \\ \cdot z_{\alpha+\gamma}(-\epsilon X^2 f, -\epsilon \xi) \cdot z_{-\gamma}(-Xf\xi, -X) \cdot x_{-\alpha-\gamma}(-\epsilon X^2\xi^2 f) \cdot x_{-\alpha}(-X^3 f \xi^2),\ \text{for } \epsilon = N_{\alpha, \gamma}.
+ \begin{multline} z_\alpha(Xf, X\xi) = x_{\alpha+\gamma}(\epsilon X^2f) \cdot x_{\gamma}(-X^3 \xi f) \cdot x_{-\gamma}(Xf\xi) \cdot x_\alpha(Xf) \cdot \\ 
+ \cdot z_{\alpha+\gamma}(-\epsilon X^2 f, -\epsilon \xi) \cdot z_{-\gamma}(-Xf\xi, -X) \cdot x_{-\alpha-\gamma}(-\epsilon X^2\xi^2 f) \cdot x_{-\alpha}(-X^3 f \xi^2),\ \text{for } \epsilon = N_{\alpha, \gamma}.
 \end{multline}
@@
 We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.
-
-\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
-              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \] 
-Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$.
-
-Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times G^{\leq 0} \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
+For shortness we also write $G_M^0$ instead of $\overline{\St}(\Phi, A, M)$.
+\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
+              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
+Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
 $p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
-We let $\overline{G}_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot h_0, u)$, $h_0 \in \overline{G}_M^0$.
-It is clear that this action is well defined. Denote by $\overline{V}$ the quotient set $V / \overline{G}_M^0$.
+We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
+It is clear that this action is well defined.
+Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
+Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$.
 
@@
  First of all, let us show that the resulting function is total. 
- Fix $c = [g, h, u] \in \overline{V}$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
+ Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $(g, h \cdot i_+(h_0), u)$ is the representative of $c$ on which $t_\alpha(aX^{-1})$ is defined.
+  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, while the latter triple also lies in the same orbit as $(g, h, u)$.
 
  Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
- Let $(g, h_1, u), (g, h_2, u)$ be a pair of representatives of the same $c \in \overline{V}$ for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ lie in $P_\alpha(*)$.
- By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in \overline{\St}(\Phi, A, M)$, moreover, 
+ Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
+ By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
   $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
@@
  From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
- the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, therefore $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
- By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$.
+ the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
+ By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$,
  It is not hard to check using e.\,g. the table on p.~986 of~\cite{St71} that $Z_0(\alpha)$ always contains a long root, therefore
-  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by ??? hence $h_0 \in Z_\alpha(A, M)$.
- Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$ therefore
+  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS} hence $h_0 \in Z_\alpha(A, M)$.
+ Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
  \begin{multline} \nonumber
-  T_\alpha(aX^{-1})[g, h_1, u] = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = \\
-  = \left[ x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right] = T_\alpha(aX^{-1})[g, h_2, u]. \qedhere
+  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
+  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
  \end{multline} \end{proof}

### 2019-05-23 dl-paper.tex
Fixed some issues

@@
 \end{comment}
+
 \subsection{Unstable Quillen K-groups} \label{sec:quillen}
@@
 \subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} 
-Throughout this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ denotes some fixed root of $\Phi$.
-
-Consider the following root subsets of $\Phi$ (cf.~\cite[Proposition~5.7]{St71}):
+Assume for a moment that $\Phi$ is an arbitrary root system and consider the following subsets of $\Phi$:
 \begin{equation} \nonumber \begin{align}
    Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
-   Z_0(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle = 0 \}, \\
+   Z_0(\alpha) & = \{ \beta \in \Phi \mid \alpha + \beta \not\in \Phi,\ \langle \alpha, \beta \rangle = 0 \}, \\
    Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} \end{equation}
+Clearly, $Z_0(\alpha)$ (resp.
+$Z_+(\alpha)$) is a reductive (resp.
+special) subset of $\Phi$, moreover, in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.
+$Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
+(cf.~\cite[Proposition~5.7]{St71}).
 
@@
 It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes \hat{U}(Z_+(\alpha), M). \]
-Notice that the subgroup $Z_\alpha(A, A)$ coincides with $Z(\hat{U}_\alpha)$ defined in~\cite[984]{St71}.
-
-\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, 
-hence $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
+It is clear, that $Z_\alpha(A, M)$ centralizes the root subgroup $X_\alpha(A)$ (cf. \cite[984]{St71}).
+
+For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a root of $\Phi$.
+
+\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, hence the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
 By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^*$, $m\in M$. \end{rem}
@@
 
-Suppose $g$ has type 1 or 2 and $\beta - \alpha \in \Phi$. By~\cref{Zrels} we obtain that
+Suppose $g$ has type 1 or 2 and $\alpha - \beta \in \Phi$. By~\cref{Zrels} we obtain that
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
@@
 
-\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed via the following procedure. 
+\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of the function $p_\alpha$ from the statement of~\cref{P0_normal} on an element $g\in K(A[X], M[X])$ can be computed via the following procedure.
 Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. 
@@
 
-\begin{lemma} Let $\Phi$ be any root system of rank $\geq 3$, $\alpha \in \Phi$ and $(A, M)$ be a local pair.
- Then the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
+\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$, $(A, M)$ be a local pair.
+Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function
   $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
@@
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, while the latter triple also lies in the same orbit as $(g, h, u)$.
+  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.
 
@@
  the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
- By~\cite[Theorem~2.5]{Ste73} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}_\beta$, where $\beta$ is any fixed long root of $\Phi$,
- It is not hard to check using e.\,g. the table on p.~986 of~\cite{St71} that $Z_0(\alpha)$ always contains a long root, therefore
-  $\overline{\K_2}(\Phi, A, M)$ is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS} hence $h_0 \in Z_\alpha(A, M)$.
- Thus, we have shown that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
+ By~\cref{thmStein} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}.
+Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
  \begin{multline} \nonumber

### 2019-05-24 dl-paper.tex
Switched to biber, restored correct operation of live preview, fixed some warnings

@@
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
-\usepackage[breaklinks=true]{hyperref}
-\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\usepackage[breaklinks=true,unicode]{hyperref}
+\usepackage[hyperref=true, backend=biber, bibencoding=utf8, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 \DeclareMathOperator{\St}{St}
-\DeclareMathOperator{\G}{G}
+\DeclareMathOperator{\GG}{G}
 \DeclareMathOperator{\E}{E}
@@
 
-\subsection{Computation of the kernel of the map of evaluation at $0$.}
+\subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}
 For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
@@
 
-\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} 
-Assume for a moment that $\Phi$ is an arbitrary root system and consider the following subsets of $\Phi$:
-\begin{equation} \nonumber \begin{align}
-   Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} 
+For a root system $\Phi$ consider the following subsets of $\Phi$:
+\begin{align} Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
    Z_0(\alpha) & = \{ \beta \in \Phi \mid \alpha + \beta \not\in \Phi,\ \langle \alpha, \beta \rangle = 0 \}, \\
-   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} \end{equation}
-Clearly, $Z_0(\alpha)$ (resp.
-$Z_+(\alpha)$) is a reductive (resp.
-special) subset of $\Phi$, moreover, in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.
-$Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
-(cf.~\cite[Proposition~5.7]{St71}).
+   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} 
+Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$.
 
@@
 For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a root of $\Phi$.
+Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.
+$Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
+(cf.~\cite[Proposition~5.7]{St71}).
 
@@
 
-\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
+\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
 Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
@@
 
+\begin{comment}
 The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
@@
 \begin{multline}
- T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim
-T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
+ T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
+T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
  = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
  \begin{multline}
-h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\frac{bX^{-1}}{1 + \frac{bm}{1+am}}\right) = \\ = 
- h \cdot x_\alpha\left(- \frac{aX^{-1}}{1 + am} - \frac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
-  h \cdot x_\alpha\left(- \frac{(a+b)X^{-1}}{1 + am + bm}\right).
+h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm}{1+am}}\right) = \\ = 
+ h \cdot x_\alpha\left(- \tfrac{aX^{-1}}{1 + am} - \tfrac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
+  h \cdot x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + am + bm}\right).
 \end{multline}
@@
 If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
-$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am})$
+$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \tfrac{m'}{1 + am})$
 %($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
@@
  T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
- T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
- \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
+ T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
+ \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
  = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
  \begin{multline}
- h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
-    \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\frac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
- = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am} + \frac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
- \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}}{1 + am + bm'}\right).
+ h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
+    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
+ = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
+ \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
 \end{multline}
 The latter expression is symmetric.
-\begin{comment}
-If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
-\[x_\alpha(-a) \cdot S_\beta(-b, \pi(g, h, u)) h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')) \in P\left(\beta, \frac{m + am'}{1-bm}\right)\]
-
-($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
-($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
-\begin{multline}
-\left(\begin{array}{ccc} 
- 1 & 0 & -bX^{-1} \\
- 0 & 1 & 0 \\
- 0 & 0 & 1 
- \end{array}\right)
-\left(\begin{array}{ccc} 
- 1 & 0 & * \\
- 0 & 1 & * \\
- mX & m'X & 1 
- \end{array}\right)
- \left(\begin{array}{ccc} 
- 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
- 0 & 1 & 0 \\
- 0 & 0 & 1 
- \end{array}\right) = 
- \left(\begin{array}{ccc} 
- 1 - bm & -bm' & * \\
- 0 & 1 & * \\
- mX & m'X & (1 - mb)^{-1} 
- \end{array}\right) = S_\beta(-b, g^+).
-\end{multline}
-\begin{multline}
-\left(\begin{array}{ccc} 
- 1 & 0 & 0 \\
- -a & 1 & 0 \\
- 0 & 0 & 1 
- \end{array}\right)
- \left(\begin{array}{ccc} 
- 1 - bm & - bm' & * \\
- 0 & 1 & * \\
- mX & m'X & (1 - bm)^{-1} 
- \end{array}\right) = 
- \left(\begin{array}{ccc} 
- 1 - bm & - bm' & * \\
- - a + abm & 1 + abm' & * \\
- mX & m'X & (1 - bm)^{-1} 
- \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
-\end{multline}
-\begin{multline}
- \left(\begin{array}{ccc} 
- 1 - bm & - bm' & * \\
- - a + abm & 1 + abm' & * \\
- mX & m'X & (1 - bm)^{-1} 
- \end{array}\right)
- \left(\begin{array}{ccc} 
- (1  - bm)^{-1} & 0 & 0 \\
- 0 & 1 & 0 \\
- 0 & 0 & 1 - bm 
- \end{array}\right) \cdot \\ \cdot
-\left(\begin{array}{ccc} 
- 1 + abm' & 0 & 0 \\
- 0 & (1 + abm')^{-1} & 0 \\
- 0 & 0 & 1 
- \end{array}\right)
- \left(\begin{array}{ccc} 
- 1 & 0 & 0 \\
- a(1 + abm') & 1 & 0 \\
- 0 & 0 & 1 
- \end{array}\right) = \\
- = 
- \left(\begin{array}{ccc} 
- 1 & - \frac{bm'}{1 + abm'} & * \\
- 0 & 1 & * \\
- \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
- \end{array}\right)
-\end{multline}
-
-There is still a mistake in the last implication :(
-Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
-
-\begin{multline}
-[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
- T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
- \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
- = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
- \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
- \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
- = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
- h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
-\end{multline}
-
-Full axioms
-\begin{enumerate}
- \item (+) $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
- \item (+) if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
- %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
- \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then $S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
- \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
- $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
-\end{enumerate}
-
-Restricted axioms:
-\begin{enumerate}
- \item (+) $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
- \item (+) if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
-% \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
- \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
-$S_\alpha(a, g) \in P(\beta, 0);$
- \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
- $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
-\end{enumerate}
-
-Some implication: suppose $g \in P(\alpha, 0)$, then $g x_{-\alpha}(mX) \in P(\alpha, m)$ by the definition of the latter.
-\begin{multline}S(\alpha, g \cdot x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot g \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
-= S(\alpha, g) \cdot x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha % = \\
-%= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\} \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
-= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am). 
-\end{multline}
-
-Let us show that F3 and F4 hold automatically.
-Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
-$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
-Then 
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
-  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
-We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
-\end{comment}
+
 \begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
@@
  = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
-
+\end{comment}
 \printbibliography

### 2019-05-24 dl-paper.tex
Strengthened statement of Corollary 2

@@
 
-\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by
- $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
-\begin{proof} Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
- Invoking~\eqref{C4} of~\cref{Crels} with $\xi = 1$, $s = m$, $t = X\eta$ we obtain that modulo 
- $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to 
- $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
- Arguing by induction on the height of $\alpha$ we conclude that $c_\alpha(m, X\eta)$ for all $\alpha \in \Phi^+$
- belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(m, X\eta)$.
- Similar argument also works for the negative roots, and the required assertion now follows. \end{proof}
+\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$.
+\end{corollary}
+\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
+ $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
+The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
+\end{proof}
 
@@
 In particular, it contains the relative Dennis--Stein and Steinberg symbols.
-It is also clear that $P_\alpha(0)$ contains the elements $c_{\pm \beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
+It is also clear that $P_\alpha(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
  (they can be factored as products of two elements of type 2 or 3). \end{rem}
@@
 
-The second assertion can be verified in a straightforward manner. \end{proof}
+The second assertion can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}
 
@@
   \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
-  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
+  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
 

### 2019-05-26 dl-paper.tex
Minor fixes

@@
 
-\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$.
+\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$.
 \end{corollary}
@@
   \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
+Notice that a priori $K(\alpha, \beta)$ depends on a choice of $\delta$, however as the next proposition shows, there is no such dependence.
 
@@
 
-\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$, $(A, M)$ be a local pair.
+\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair.
 Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function
@@
 
-\begin{comment}
 The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
@@
  = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
-\end{comment}
+
+\include{rehmann}
+
 \printbibliography
+
 \end{document}

### 2019-05-27 dl-paper.tex
Added Proposition 5

@@
 
-\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
+\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
 Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
@@
 This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
+If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
 \[ t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
-It is easy to verify that $p(t_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, p(g, h, u)).$
 
-\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair.
-Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function
-  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
+From~\cref{SR:additivity} it follows that
+\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
+therefore the operation $t_\alpha(aX^{-1})$ is well-defined.
+
+\begin{lemma}\label{lem:orbit-action} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. 
+Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
+\end{lemma}
 \begin{proof}
@@
 
-The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
-We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
- (this operation is well defined for $V'_0$).
+\begin{prop}
+ The operators $T_\alpha(aX^{-1})$ satisfy relations $\text{R1}_1, $ $\text{R2}_1$.
+\end{prop}
+\begin{proof}
+Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
+  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
+Invoking~\cref{SR:additivity} once again we obtain that
+\begin{multline} \nonumber t_\alpha(bX^{-1}) t_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
+t_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
+ = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim t_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
+which implies the assertion for $\text{R1}_1$.
 
-\begin{multline}
- T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
-T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
- = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
- \begin{multline}
-h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm}{1+am}}\right) = \\ = 
- h \cdot x_\alpha\left(- \tfrac{aX^{-1}}{1 + am} - \tfrac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
-  h \cdot x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + am + bm}\right).
+Now let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. 
+Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf.
+the first part of the proof of~\cref{lem:orbit-action}).
+Now for $a, b \in A$ set $\epsilon = N_{?, ?}$ and $c = 1 + \epsilon abm'$.
+It is clear that $\alpha$ and $\alpha+\beta$ form a sharp angle.
+\begin{multline} \nonumber
+[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
+ T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\tfrac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
+ \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
+ = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
+ \begin{multline} \nonumber
+ h' = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\ \sim  h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
+ = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\tfrac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
+ h\cdot x_{\alpha + \beta}\left(\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
 \end{multline}
+\end{proof}
 

### 2019-05-27 dl-paper.tex
Proved 4.3

@@
 
-\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right).
+\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
 \] \end{lemma}
-\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
-  S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
+\end{multline}
 The assertion now follows from the preceding corollary.
@@
 
-\begin{lemma} \label{lem:SRobtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
+\begin{lemma} \label{SR:obtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
  belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
@@
 \subsection{The proof of the injectivity theorem}
+Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
 We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
@@
 
-\begin{lemma}\label{lem:orbit-action} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. 
+\begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
 Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
@@
 
- Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
+ Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of representative.
  Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
@@
 
-\begin{prop}
- The operators $T_\alpha(aX^{-1})$ satisfy relations $\text{R1}_1, $ $\text{R2}_1$.
+The following proposition is directly inspired by~\cite[Proposition~4.3]{Tu83}.
+\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
 \end{prop}
@@
   x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
-Invoking~\cref{SR:additivity} once again we obtain that
-\begin{multline} \nonumber t_\alpha(bX^{-1}) t_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
-t_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
- = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim t_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
-which implies the assertion for $\text{R1}_1$.
+The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
+\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
+T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
+ = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}
 
-Now let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. 
+Let us verify $\text{R2}_1$.
+Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
 Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf.
 the first part of the proof of~\cref{lem:orbit-action}).
-Now for $a, b \in A$ set $\epsilon = N_{?, ?}$ and $c = 1 + \epsilon abm'$.
-It is clear that $\alpha$ and $\alpha+\beta$ form a sharp angle.
+Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta}$ and $c = 1 - \epsilon abm'$.
+Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
 \begin{multline} \nonumber
-[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
- T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\tfrac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
- \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
- = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
+[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
+ = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right) , u (1 - am) \right) \sim \\ \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h \cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc), u (1 - am) \right) = \\ = \left([x_\beta(b), x_\alpha(aX^{-1})] g, h', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline}
+ where the last equivalence is obtained as follows:
  \begin{multline} \nonumber
- h' = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\ \sim  h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
- = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\tfrac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
- h\cdot x_{\alpha + \beta}\left(\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
+ h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim \\ \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
 \end{multline}
-\end{proof}
 
-If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
-$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \tfrac{m'}{1 + am})$
-%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
-\begin{multline}
+Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle.
+As before, we can assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
+Set $\epsilon = N_{\alpha,-\beta}$.
+Applying~\cref{SR:sharp} we obtain that
+\begin{multline} \label{eq:sharp-formula1}
  T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
  T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
- \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
+ \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
  = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
- \begin{multline}
- h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
+ \begin{multline} \label{eq:sharp-formula2}
+ h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
     \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
- = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
+ = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
  \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
 \end{multline}
-The latter expression is symmetric.
+The expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are clearly symmetric under transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies $\text{R3}_{1,1}$.
+\end{proof}
 

### 2019-05-27 dl-paper.tex
Some fixes

@@
  \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
- Since the subgroup $C = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
- (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C$,
+ Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
+ (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
  which implies the assertion. \qedhere \end{proof}
@@
 
-Now for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
-\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot [\St(\Phi, XA[X]), \St(\Phi, M)],\]
-hence $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right] \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]), \St(\Phi, M)\right]$ and therefore \[K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \St(\Phi, M)\right].\]
+Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$.
+It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
+Since $C_0$ is generated by the above commutators and $\overline{\St}(\Phi, A[X], XM[X])$ is a normal subgroup of $\St(\Phi, A[X])$
+we obtain that $C_0 \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1$ and consequently that
+$K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1.$
 
-It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
-Thus, to verify the assertion it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
+It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
+Thus, it remains to show that commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
 Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
-Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, but in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}.
-\end{proof}
+Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, 
+ and in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}
 
@@
   \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
-Notice that a priori $K(\alpha, \beta)$ depends on a choice of $\delta$, however as the next proposition shows, there is no such dependence.
 
@@
 Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$. 
-\end{prop}
+In particular, $K(\alpha, \beta)$ does not depend on a choice of the root $\delta$. \end{prop}
 \begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
@@
 
-The following proposition is directly inspired by~\cite[Proposition~4.3]{Tu83}.
+The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
 \begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
@@
 the first part of the proof of~\cref{lem:orbit-action}).
-Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta}$ and $c = 1 - \epsilon abm'$.
+Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
 Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
@@
 [T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
- = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right) , u (1 - am) \right) \sim \\ \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h \cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc), u (1 - am) \right) = \\ = \left([x_\beta(b), x_\alpha(aX^{-1})] g, h', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline}
- where the last equivalence is obtained as follows:
+ = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
+ \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h', u (1 - am) \right) = \\
+ = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g, h'', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
+ where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot$ 
+  and the last congruence is obtained as follows:
  \begin{multline} \nonumber
- h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim \\ \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
+ h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
+ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
+ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
 \end{multline}
@@
 Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle.
-As before, we can assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
-Set $\epsilon = N_{\alpha,-\beta}$.
-Applying~\cref{SR:sharp} we obtain that
+As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
+Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
 \begin{multline} \label{eq:sharp-formula1}
@@
  = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline}
+
 \begin{multline} \label{eq:sharp-formula2}
@@
 \end{multline}
-The expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are clearly symmetric under transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies $\text{R3}_{1,1}$.
+Relation $\text{R3}_{1,1}$ now follows from the fact that expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are symmetric under
+ the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$.
 \end{proof}

### 2019-05-28 dl-paper.tex
Added couple of more lemmas

@@
 \usepackage{enumitem}
-\usepackage[notref,notcite]{showkeys}
+%\usepackage[notref,notcite]{showkeys}
 
@@
 Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
-Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$.
+Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$ and say that these triples are congruent.
 
 The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
-This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
+This function is defined for the triples $(g, h, u)$ satisfying $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
 If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
@@
 \begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
-Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
+Then for any $\alpha \in \Phi$ and $a \in A$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined (total) function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
 \end{lemma}
@@
 
+For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
+\[ T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h\cdot x_{\alpha}(-a), u).  \]
+It is easy to see that this definition is correct.
+
+\begin{lemma}
+ The operators $T_\alpha$ satisfy $\text{R3}_{1,0}$.
+\end{lemma}
+\begin{proof}
+ We have to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a, b\in A$.
+ \begin{multline}
+  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) = \\
+  = T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot x_\beta(b), u(1-am)\right)
+ \end{multline}
+\end{proof}
+
+\begin{lemma}
+ For $a, b\in A$, $f, g \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
+ \[ T_\beta(f) T_\alpha(aX^{-1})  T_\beta(g) T_\alpha(bX^{-1})(g, h, u) \]
+\end{lemma}
+\begin{proof}
+Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
+  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
+The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
+\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
+T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
+ = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}
+
+\end{proof}
+
 The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
+\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
 \end{prop}
@@
 Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
-Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
+Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
 \begin{multline} \nonumber

### 2019-05-31 dl-paper.tex
Proved R3_{1,0}

@@
 \usepackage{enumitem}
-%\usepackage[notref,notcite]{showkeys}
+\usepackage[notref,notcite]{showkeys}
 
@@
 
-\begin{df} \label{defP0} Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
+\begin{df} \label{defP0}
+Let $M$ be an ideal of a local ring $A$. We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
  map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
@@
  \item $x_{\alpha}(f)$. \end{enumerate}
-In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. \end{df}
-
-\begin{rem}\label{rem:c-DS} It is easy to check that $P_\alpha(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
-In particular, it contains the relative Dennis--Stein and Steinberg symbols.
-It is also clear that $P_\alpha(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$
- (they can be factored as products of two elements of type 2 or 3). \end{rem}
-
-Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
-The following lemma shows that the resulting subgroup is sufficiently large.
-\begin{lemma} \label{Pstar-large} The subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
-The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
-\end{proof}
-
-\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_\alpha(*)$ as follows: it consists precisely of images under $j_+$ of all elements 
- $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
-
-\begin{lemma}\label{P0_normal} The subgroup $P_\alpha(0)$ is normal in $P_\alpha(*)$. In particular, there is an exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
+In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$.
+
+We also denote by $P_{\alpha, M}(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_{\alpha, M}(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+\end{df}
+
+Typically, the ideal $M$ from the above definition is precisely the maximal ideal of $A$, however, sometimes (e.\,g. in~\cref{P0-conj-invariant}) we also use the subgroups defined above for $M=A$.
+
+\begin{lemma}\label{P0_normal} The subgroup $P_{\alpha, M}(0)$ is normal in $P_{\alpha, M}(*)$. In particular, there is a short exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar@{->>}[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
@@
 
-\begin{rem} \label{rem:palpha} From the two preceding lemmas it follows that the value of the function $p_\alpha$ from the statement of~\cref{P0_normal} on an element $g\in K(A[X], M[X])$ can be computed via the following procedure.
+\begin{rem}\label{rem:c-DS} It is easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
+In particular, it contains the relative Dennis--Stein and Steinberg symbols.
+Notice that $P_\alpha(0)$ also contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3). \end{rem}
+
+The following lemma shows that $P_{\alpha, M}(*)$ is sufficiently large.
+\begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. Then the subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
+The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
+\end{proof}
+
+\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it consists precisely of images under $j_+$ of the elements 
+ $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
+
+\begin{rem} \label{rem:palpha} It follows from~\cref{P0_normal} and~\cref{Pstar-large} that the value of the function $p_\alpha$ from the statement of~\cref{P0_normal} on an element $g\in K(A[X], M[X])$ can be computed via the following procedure.
 Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. 
@@
 
+\begin{lemma} \label{P0-conj-invariant} Suppose $(A, M)$ is a local pair.
+Then for any $\beta \in Z(\alpha)$ and $b \in A$ the subgroups $P_{\alpha, M}(0)$ and $P_{\alpha, M}(*)$ are stable under conjugation by $x_\beta(b)$.
+\end{lemma}
+\begin{proof}
+Notice that both $Z_\alpha(A, M)$ and $K(A[X], M[X])$ are stable under the specified conjugation, which implies the assertion for $P_{\alpha, M}(*)$. 
+To obtain the assertion for $P_{\alpha, M}(0)$ consider the following commutative diagram.
+\[ \xymatrix{ P_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & P_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & M^+ \ar@{^{(}->}[d] \\ P_{\alpha, A}(0) \ar@{^{(}->}[r] & P_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & A^+} \]
+Notice that $x_\beta(b) \in P_{\alpha, A}(0)$ therefore for $g \in P_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
+
+For the rest of this section $M$ denotes the maximal ideal of $A$, so everywhere below we abridge $P_{\alpha, M}(*)$ (resp.
+$P_{\alpha, M}(0)$) to just $P_{\alpha}(*)$ (resp.
+$P_{\alpha}(0)$).
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-From the preceding lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
+From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
 
@@
 We have to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a, b\in A$.
- \begin{multline}
-  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) = \\
-  = T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot x_\beta(b), u(1-am)\right)
- \end{multline}
+Suppose $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that
+\begin{gather*}
+\begin{multlined} \nonumber
+  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) \sim \\
+  \sim T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b), u(1-am)\right) = \\ =
+  \left( [x_\beta(b), x_{\alpha}(aX^{-1}] \cdot g, h \cdot h', u] \right) \sim \left( g, h, u\right), \end{multlined} \\
+\begin{multlined} \nonumber \text{ where }
+ h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\ = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am).
+\qedhere \end{multlined} \end{gather*}
+
 \end{proof}

### 2019-06-01 dl-paper.tex
Added more text to lemma 33

@@
 \begin{multlined} \nonumber \text{ where }
- h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\ = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am).
-\qedhere \end{multlined} \end{gather*}
-
-\end{proof}
-
-\begin{lemma}
- For $a, b\in A$, $f, g \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
- \[ T_\beta(f) T_\alpha(aX^{-1})  T_\beta(g) T_\alpha(bX^{-1})(g, h, u) \]
+ h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\
+ = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}
+\end{proof}
+
+\begin{lemma} For $a, b\in A$, $f_1, f_2 \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
+ \[ T_\beta(Xf_1) T_\alpha(bX^{-1})  T_\beta(Xf_2) T_\alpha(aX^{-1})(g, h, u) = \left(g' \cdot g, h \cdot h', u(1+(a+b)m)\right), \]
+where $h' = x_\alpha\left(\tfrac{(a+b)X^{-1}}{1+(a+b)m}\right)$, $g' = x_\beta(Xf_1) \cdot x_\alpha\left(bX^{-1}\right) \cdot x_\beta(Xf_2) \cdot x_\alpha\left( aX^{-1}\right)$.
  \end{lemma}
@@
   x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
-The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
-\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
-T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
- = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}
-
+Notice that $x_\beta(Xf)$, $x_\beta(Xg)$ belong to $P_\alpha(0)$ therefore from~\cref{SR:additivity} we obtain that:
+\begin{multline} \nonumber T_\beta(Xf_1) \cdot T_\alpha(bX^{-1}) \cdot T_\beta(Xf_2) \cdot T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ 
+\sim T_\beta(Xf_1) \cdot T_\alpha(bX^{-1}) \left(x_{\beta}(Xf_2) \cdot x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) \sim \\
+ \sim \left( g' \cdot g,\ h \cdot x_\alpha\left(-\tfrac{(a+b)X^{-1}}{1+(a+b)m}\right),\ u(1 + am + bm) \right). \end{multline}  
 \end{proof}

### 2019-06-03 dl-paper.tex
Cleaner case analysis

--- 2019-05-31 dl-paper.tex
@@
 \begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
-Then for any $\alpha \in \Phi$ and $a \in A$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined (total) function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
+Then for any $\alpha \in \Phi$ and $a \in A$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$.
 \end{lemma}
@@
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.
+  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
 
@@
 
-\begin{lemma}
- The operators $T_\alpha$ satisfy $\text{R3}_{1,0}$.
-\end{lemma}
-\begin{proof}
-We have to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a, b\in A$.
-Suppose $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+\begin{lemma} The operators $T_\alpha$ satisfy $\text{R3}_{\leq 0, 1}$. \end{lemma}
+\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
+Write $b = b_0 + Xf$ for some $f \in M[X]$.
+We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
 It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that 
@@
 \begin{multlined} \nonumber
-  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) \sim \\
-  \sim T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b), u(1-am)\right) = \\ =
-  \left( [x_\beta(b), x_{\alpha}(aX^{-1}] \cdot g, h \cdot h', u] \right) \sim \left( g, h, u\right), \end{multlined} \\
+  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, h, u) \sim \\
+  \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0), u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, h \cdot h', u] \right) \sim \left(g, h, u\right), \end{multlined} \\
 \begin{multlined} \nonumber \text{ where }
- h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\ = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am).
-\qedhere \end{multlined} \end{gather*}
-
-\end{proof}
-
-\begin{lemma}
- For $a, b\in A$, $f, g \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
- \[ T_\beta(f) T_\alpha(aX^{-1})  T_\beta(g) T_\alpha(bX^{-1})(g, h, u) \]
-\end{lemma}
+ h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b_0) = \\
+ = h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right),\ x_\beta(b_0)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}
+\end{proof}
+
+\begin{lemma} The operators $T_\alpha$ satisfy $\text{R2}_{\leq -1, 1}$. \end{lemma}
+\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
+ \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, h, u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, h, u\right). \]
+
+As before, we may assume that $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+Since $x_\beta(Xf)$ belongs to $P_\alpha(0)$ we obtain from~\cref{SR:additivity} that:
+\begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ h,\ u\right) \sim \\ 
+\sim T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am),\ u(1-am)\right) = \\ = \left( [x_\beta(Xf), x_\alpha(aX^{-1})] \cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right),\ u \right) \sim \\ \sim (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ h,\ u).
+\qedhere \end{multline} \end{proof}
+
+The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle. \end{prop}
 \begin{proof} 
+\begin{comment}
 Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
@@
  = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
-
-\end{proof}
-
-The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
-\end{prop}
-\begin{proof}
-Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
-Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
-  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
-The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
-\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
-T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
- = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}
-
-Let us verify $\text{R2}_1$. 
-Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
-Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf.
-the first part of the proof of~\cref{lem:orbit-action}).
+\end{comment}
+Let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
+Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$.
 Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
@@
 [T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
- = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
+ = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
  \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h', u (1 - am) \right) = \\
@@
 Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
-\begin{multline} \label{eq:sharp-formula1}
- T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
+\begin{gather*} \begin{multlined} \nonumber
+ T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, h, u\right) = 
  T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
  \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
- = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline}
-
-\begin{multline} \label{eq:sharp-formula2}
+ = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multlined} \\
+\begin{multlined} \nonumber
  h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
@@
  \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
-\end{multline}
-Relation $\text{R3}_{1,1}$ now follows from the fact that expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are symmetric under
- the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$.
-\end{proof}
+\end{multlined}
+\end{gather*}
+The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$,
+ which implies the relation $\text{R3}_{1,1}$.
+\end{proof}
+
+\begin{corollary}
+  $T_\alpha$ satisfy the relations $\text{R3}_{1,1}$ in the remaining case when $\alpha$ is perpendicular to $\beta$.
+\end{corollary}
 

### 2019-06-05 dl-paper.tex
Added Lemma 34

@@
 
+\begin{comment}
+$n \geq m$
+$b = \epsilon  X^{-m}$
+$\epsilon \in R^*$, $d \in R$
+$abc = d X^{-n}$
+
+$|a| = n-m$, $|b| = m$, $|c| = 0$
+
+\begin{align*}
+[x_{il}(abc), x_{jk}(b)] &= 1 & \text{R3}_{n,m} \\
+[x_{ij}(a), x_{kl}(c)] &= 1 & \text{R3}_{n-m, 0}\\
+[x_{ik}(ab), x_{kl}(c)] &= x_{il}(abc), & \text{R2}_{n, 0} \\
+[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
+[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab), & \text{R2}_{n-m, m}\\
+[x_{ij}(a), x_{jl}(bc)] &= x_{il}(abc),& \text{R2}_{n-m, m}\\
+[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
+[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab) & \text{R2}_{n-m, m}
+\end{align*}
+\end{comment}
+
+\begin{lemma} For any simply laced root system $\Phi$ of rank $\geq 3$, a local ring $A$ and any $1 \leq m \leq n$ the relation $\text{R3}_{n,m}^\perp$ follows from $\text{R1}_n$, $\text{R2}_{n,0}$, $\text{R2}_{m,0}$ and $\text{R2}_{n-m,m}$ and $\text{R3}_{n-m, 0}^\perp$.
+\end{lemma}
+\begin{proof}
+We need to show that $[x_{\alpha}(cX^{n}), x_{\beta}(dX^{m})] = 1$ for all $c, d\in A$, $\alpha \perp \beta$.
+Notice that in the special case $c = \epsilon \in A^*$ the assertion follows from a consideration of \cite[Fig.~4]{KS99} in which one substitutes $a = \epsilon^{-1} d \cdot X^{-(n-m)}$, $b = \epsilon X^{-m}$, $c = 1$.
+
+Now if $c \in M$ we can express it as a difference $c = \epsilon_1 - \epsilon_2$ of two invertible elements.
+The required assertion now follows from $\text{R1}_{n}$, the standard commutator identity $[ab, c] = {}^a[b, c] [a, c]$ and the special case considered above.
+\end{proof}
+
+\begin{comment}
 \begin{corollary}
@@
  = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
+ \end{comment}
 

### 2019-06-05 dl-paper.tex
Minor

@@
 
-For the rest of this section $M$ denotes the maximal ideal of $A$, so everywhere below we abridge $P_{\alpha, M}(*)$ (resp.
+For the rest of this section $M$ denotes the maximal ideal of $A$, so everywhere below we shorten the notation for $P_{\alpha, M}(*)$ (resp.
 $P_{\alpha, M}(0)$) to just $P_{\alpha}(*)$ (resp.
@@
 The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle. \end{prop}
+\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}^{\angle}$ in the special case when $\alpha, \beta$ form a sharp angle. \end{prop}
 \begin{proof} 
@@
 \end{comment}
-Let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
+Let us verify $\text{R2}_{0,1}$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
 Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$.
@@
 
-Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle.
-As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
+Now let us prove $\text{R3}_{1,1}^\angle$. As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
 Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
@@
 \end{gather*}
-The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$,
- which implies the relation $\text{R3}_{1,1}$.
+The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies the desired relation.
 \end{proof}
@@
 
-\begin{lemma} For any simply laced root system $\Phi$ of rank $\geq 3$, a local ring $A$ and any $1 \leq m \leq n$ the relation $\text{R3}_{n,m}^\perp$ follows from $\text{R1}_n$, $\text{R2}_{n,0}$, $\text{R2}_{m,0}$ and $\text{R2}_{n-m,m}$ and $\text{R3}_{n-m, 0}^\perp$.
+\begin{lemma} For any simply laced root system $\Phi$ of rank $\geq 3$, a local ring $A$ and any $1 \leq m \leq n$ the relation $\text{R3}_{n,m}^\bot$ follows from $\text{R1}_n$, $\text{R2}_{n,0}$, $\text{R2}_{m,0}$ and $\text{R2}_{n-m,m}$ and $\text{R3}_{n-m, 0}^\bot$.
 \end{lemma}
@@
 Now if $c \in M$ we can express it as a difference $c = \epsilon_1 - \epsilon_2$ of two invertible elements.
-The required assertion now follows from $\text{R1}_{n}$, the standard commutator identity $[ab, c] = {}^a[b, c] [a, c]$ and the special case considered above.
+The required assertion now follows from $\text{R1}_{n}$, the standard commutator identity $[ab, c] = {}^a[b, c] [a, c]$ and the just considered case.
 \end{proof}
@@
 
-%\include{rehmann}
+\include{rehmann}
 

### 2019-06-06 dl-paper.tex
More material

@@
 The structure constants $N_{\alpha \beta i j}=\pm 1,2,3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and can be computed explicitly.
+
+In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is simply-laced, in which case the above relations further simplify to
+\begin{align}
+&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
+\end{align}
 
@@
 
-\subsection{Lemma33}
-Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.
-
-For a simply-laced root system $\Phi$ and a commutative ring $R$, the Steinberg group $\St(\Phi,\,R)$ is generated by the formal symbols $x_{\alpha}(a)$ for $\alpha\in\Phi$, $a\in R$ subject to the Steinberg relations
+\subsection{Lemma on the presentation of Steinberg groups}
+%Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
+Let $I\trianglelefteq A$ be an ideal of a commutative ring $A$.
+We consider $A[X, X\inv]$ as a graded ring in which $X^{-1}$ has degree $1$.
+We denote by $B = B(A, I)$ the subring $A[X^{-1}] + I[X] \subseteq A[X, X\inv]$ with the induced grading.
+As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot X^d$ for $d<0$, and $B_d=A \cdot X^d$ for $d\geq0$.
+
+We need to introduce notation for certain relations of $\St(\Phi, B)$.
 \begin{align}
-&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
+&\,\,x_{\alpha}(a)x_{\alpha}(b) =  x_{\alpha}(a+b),& a,b\in B_d, \tag{R$1_d$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),& a\in B_d,\ b\in B_e, \tag{R$2_{d,e}$} \\
+&[x_{\alpha}(a),\,x_{\gamma}(b)]= 1,& \alpha \perp \beta,\ a\in B_d,\ b\in B_e, \tag{R$3^\bot_{d,e}$} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ a\in B_d,\ b\in B_e. \tag{R$3^\angle_{d,e}$}
 \end{align}
-
-Let $I\trianglelefteq A$ be a (not neccesarily proper) ideal of a commutative ring $A$. Denote $R=\oplus_{d\in\mathbb Z}R_d\subseteq A[t,t\inv]$, where $R_d=It^d$, $d<0$, and $R_d=At^d$, $d\geq0$.
-
-For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
-
-Consider the root system $\rD_l$ for $l\geq5$. It can be naturally embedded into the root system of type $\rC_l$ as a set of short roots.
-
-Define truncated Steinberg groups $G_n$ for $n\geq1$ by the set of generators $x_\alpha(a)$, $\alpha\in\rD_l$, $a\in R_d$, $d\leq n$, and relations
-
-\begin{align}
-&\,\,x_{\alpha}(a)x_{\alpha}(b) =  x_{\alpha}(a+b),& a,b\in R_d,\ d\leq n, \tag{R$1_n$} \\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha\beta}\,ab),& a\in R_d,\ b\in R_e,\ d,e,d+e\leq n, \tag{R$2_n$} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha+\beta\not\in\rC_l\cup0,\ a\in R_d,\ b\in R_e,\ d,e\leq n, \tag{R$3.1_n$} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha+\beta\in\rC_l\setminus\rD_l,\ a\in R_d,\ b\in R_e,\ d,e,d+e\leq n. \tag{R$3.2_n$}
-\end{align}
-
+%For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
+
+For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of generators $x_\alpha(a)$, $\alpha\in \Phi$, $a\in B_d$, $d\leq n$, and relations 
+\begin{itemize}
+ \item $\text{R}1_{d}$ for $d\leq n$;
+ \item $\text{R2}_{d,e}$ for $d,e \leq n$ such that $d+e \leq n$;
+ \item $\text{R3}^\angle_{d, e}$ for $d, e\leq n$;
+ \item $\text{R3}^\bot_{d, 0}$ for $d \leq n$.
+ \end{itemize}
+
+\begin{comment}
 \begin{rem}
@@
 \end{rem}
+
+Everywhere below we set $t = X^{-1}$.
+\begin{lemma} \label{claim2} In $\St^{\leq n}(\Phi, B)$ relations $\text{R3}^\angle_{d, e}$ imply $\text{R3}^{\bot,0}_{d, e}$ for $1\leq d\leq e \leq n$. \end{lemma}
+\begin{proof}
+Without loss of generality we may assume that $\alpha, \gamma$ fit into some $\mathsf{A}_3$-triple $(\alpha, \beta, \gamma)$.
+ \begin{align*}
+ {}^{x_\gamma(t^d)}x_\alpha(bt^{e}) = {}^{x_\gamma(t^d)}[x_{-\beta}(b't^{e}), x_{\alpha+\beta}(1)] & \text{ by $\text{R2}_{e,0}$}\\
+ = [x_{-\beta}(b't^{e}), {}^{x_\gamma(t^d)}x_{\alpha+\beta}(1)] & \text{ by $\text{R3}^\angle_{d, e}$}\\
+ = [[x_{-\beta-\gamma}(b''t^{e-d}), x_\gamma(t^d)], {}^{x_\gamma(t^d)}x_{\alpha+\beta}(1)] & \text{ by $\text{R2}_{e-d,d}$}\\
+ = [x_{-\beta-\gamma}(b''t^{e-d)}), [x_\gamma(t^d), x_{\alpha+\beta}(1)]] & \text{ by~\eqref{eq:H1iii} and $\text{R3}^\bot_{e-d,0}$}\\
+ = x_{\alpha}(b'''t^{e}) & \text{ by $\text{R2}_{0,d}$ and $\text{R2}_{e-d,d}$.} \end{align*}
+Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
+ $b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b,$ from which the claim follows.
+\end{proof}
+
+\begin{lemma} \label{claim3}
+ In $\St^{\leq n}(\Phi, B)$ relations $\bot_0(d, e)$, $\angle(d, d)$ and $\angle(e, e)$ imply $\bot(d, e)$ for $d\leq e \leq n$.
+\end{lemma}
+\begin{proof}
+ \begin{align*} 
+ x_{\alpha+\beta+\gamma}(abt^{e}) = {}^{x_{-\beta}(t^d)}\!x_{\alpha+\beta+\gamma}(abt^{e}) & \text{ by $\text{R3}^{\bot, 0}_{d, e}$}\\
+ = {}^{x_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{e-d}), x_\gamma(at^d)] & \text{ by $\text{R2}_{e-d,d}$} \\
+ = [x_{\alpha}(b't^{e}) \cdot x_{\alpha+\beta}(b't^{e-d}), x_\gamma(at^d)] & \text{ by $\text{R2}_{e-d,d}$ and $\text{R3}^\angle_{d, d}$ }\\
+ = {}^{x_{\alpha}(b't^{e})}\!x_{\alpha+\beta+\gamma}(abt^{e}) [x_{\alpha}(b't^{e}), x_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and $\text{R2}_{e-d,d}$} \\ = x_{\alpha+\beta+\gamma}(abt^{e}) [x_{\alpha}(b't^{e}), x_\gamma(at^d)] & \text{ by $\text{R3}^\angle_{e, e}$.
+\qedhere}
+\end{align*}
+\end{proof}
+\end{comment}
+
+\begin{align}
+ \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
+ \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].&
+\end{align}
+
+\begin{align*} 
+ [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$} \\
+ = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{0,1}$} \\
+ = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{0,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$} \\
+ = 1 & \text{ by $\text{R3}^\bot_{e-1,1}$.}
+\end{align*}
 
@@
 \begin{comment}
-\begin{corollary}
-  $T_\alpha$ satisfy the relations $\text{R3}_{1,1}$ in the remaining case when $\alpha$ is perpendicular to $\beta$.
-\end{corollary}
-
 \begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\

### 2019-06-06 dl-paper.tex
Added Lemma 8

@@
 
-For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of generators $x_\alpha(a)$, $\alpha\in \Phi$, $a\in B_d$, $d\leq n$, and relations 
-\begin{itemize}
- \item $\text{R}1_{d}$ for $d\leq n$;
- \item $\text{R2}_{d,e}$ for $d,e \leq n$ such that $d+e \leq n$;
- \item $\text{R3}^\angle_{d, e}$ for $d, e\leq n$;
- \item $\text{R3}^\bot_{d, 0}$ for $d \leq n$.
- \end{itemize}
+For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of generators $x_\alpha(a)$, $\alpha\in \Phi$, $a\in B_d$, $d\leq n$, and relations $\text{R}1_{d}$, $\text{R3}^\angle_{d, e}$ and $\text{R3}^\bot_{d, e}$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for those $d,e \leq n$ for which $d+e \leq n$.
+
+\begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_\Phi\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
+In particular, the natural map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
+\end{lemma}
+\begin{proof}
+ The special case $\Phi=\rA_{\geq 4}$ of the assertion is due to Tulenbayev, see~\cite[Lemma~3.3]{Tu83}. Thus, it remains to deduce from it the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
+
+ Denote by $A_4(\Phi)$ the set consisting of all root subsystems of $\Phi$ of type $\rA_4$ and by $G_n$ the free product of groups $\coprod\limits_{\Psi \in A_4(\Phi)} \St^{\leq n}(\Psi, B)$ amalgamated over relations $x^{\Psi_1}_\alpha(a) = x^{\Psi_2}_\alpha(a)$ for all $a \in B_d$, $d \leq n$, $\alpha \in \Psi_1\cap\Psi_2$, $\Psi_1, \Psi_2 \in A_4(\Phi)$.
+
+ Let us show that the obvious map $i_n \colon G_n \to G_{n+1}$ has an inverse $j_n$.
+Notice first that the maps $j_\Psi$ constructed by Tulenbaev agree on the generators of $G_{n+1}$ and hence, by the universal property of colimits, give rise to the well-defined map $j\colon G_{n+1}\to G_n$, which is easily seen to be  inverse to $i$.
+  \begin{equation} \nonumber \xymatrix{
+ \St^{\leq n+1}(\Psi, B) \ar[r]^{j_\Psi} \ar[d] & \St^{\leq n}(\Psi, B) \ar[d] \\
+ G_{n+1} \ar[r]^{j_n} & G_{n} }
+ \end{equation}
+Notice that in the case $\Phi = \rE_\ell$ the natural homomorphisms $G_k \to \St^{\leq k}(\rE_\ell, B)$ are isomorphisms for $k=n,n+1$ (cf.\cite[Corollary 10]{S15}), therefore the proof is already complete in this case.
+
+We are left to consider the case $\Phi = \rD_\ell$.
+Notice that any pair of nonperpendicular roots  $\alpha, \beta$ is contained in some subsystem $\Psi \subseteq \Phi$ of type $\rA_4$, hence the only defining relations of $\St^{\leq n+1}(\Phi, B)$ which do not occur already in $G_{n+1},$ are $\text{R3}^\bot_{d, n+1}$ for $d \leq n+1$ (more precisely, the relations for which $\alpha$ and $\gamma$ are orthogonal and lie in a root subsystem of type $\rD_3$, cf.~\cite[Remark~2.1]{S15}).
+\end{proof}
 

### 2019-06-07 dl-paper.tex
Added slicker relations

@@
 Let $I\trianglelefteq A$ be an ideal of a commutative ring $A$.
-We consider $A[X, X\inv]$ as a graded ring in which $X^{-1}$ has degree $1$.
+We consider $A[X, X\inv]$ as a $\mathbb{Z}$-graded ring in which $X^{-1}$ has degree $1$.
 We denote by $B = B(A, I)$ the subring $A[X^{-1}] + I[X] \subseteq A[X, X\inv]$ with the induced grading.
-As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot X^d$ for $d<0$, and $B_d=A \cdot X^d$ for $d\geq0$.
+As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot X^d$ for $d>0$, and $B_d=A \cdot X^d$ for $d\leq0$.
+Obviously, $B = A[X^{-1}]$ in the case $I=0$ and $B = A[X, X^{-1}]$ in the case $I=A$.
 
@@
 \begin{align}
-&\,\,x_{\alpha}(a)x_{\alpha}(b) =  x_{\alpha}(a+b),& a,b\in B_d, \tag{R$1_d$} \\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),& a\in B_d,\ b\in B_e, \tag{R$2_{d,e}$} \\
-&[x_{\alpha}(a),\,x_{\gamma}(b)]= 1,& \alpha \perp \beta,\ a\in B_d,\ b\in B_e, \tag{R$3^\bot_{d,e}$} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ a\in B_d,\ b\in B_e. \tag{R$3^\angle_{d,e}$}
+&\,\,x_{\alpha}(a)x_{\alpha}(a') =  x_{\alpha}(a+a'),& \tag{R$1_d$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),& \tag{R$2_{d,e}$} \\
+&[x_{\alpha}(a),\,x_{\gamma}(b)]= 1,& \alpha \perp \beta,\ \tag{R$3^\bot_{d,e}$} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$}
 \end{align}
+where $a, a' \in B_d$, $b\in R_e$. 
 %For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
@@
 \end{rem}
-
 Everywhere below we set $t = X^{-1}$.
@@
 \end{comment}
-
 \begin{align}
@@
 
+In the case $1\leq d \leq e \leq n$ the assertion follows from the following computation:
+\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$  } \\ 
+ = [[x_{\alpha+\beta}(at^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\beta+\gamma}(b)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\alpha}(at^e), x_{\beta+\gamma}(b)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \\ 
+ = [x_{\alpha}(at^e) \cdot x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \\ 
+ = {}^{x_\alpha(at^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \\
+ = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \end{align*}
+
+In the case $d < 1\leq e \leq n$
 \begin{align*} 
- [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$} \\
- = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{0,1}$} \\
- = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{0,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$} \\
- = 1 & \text{ by $\text{R3}^\bot_{e-1,1}$.}
-\end{align*}
+ [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+ = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
+ = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$.} \end{align*}
 
@@
 \end{align*}
-\end{comment}
 
@@
 
-\begin{comment}
 \begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
@@
  = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
+
+\include{rehmann}
 \end{comment}
 
-\include{rehmann}
-
 \printbibliography

### 2019-06-08 dl-paper.tex
Reorganizing proof

@@
 
-We need to introduce notation for certain relations of $\St(\Phi, B)$. 
+Whenever the coefficient $\xi$ of a Steinberg generator $g = x_\alpha(\xi)$ of $\St(\Phi, B)$ is a homogeneous element of $B$, i.\,e. $\xi \in B_d$ for some $d \in \mathbb{Z}$,
+ we call the corresponding generator $g$ homogeneous of degree $d$.
+It is not hard to show that $\St(\Phi, B)$ can be presented by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations
+ between them (below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
 \begin{align}
 &\,\,x_{\alpha}(a)x_{\alpha}(a') =  x_{\alpha}(a+a'),& \tag{R$1_d$} \\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),& \tag{R$2_{d,e}$} \\
-&[x_{\alpha}(a),\,x_{\gamma}(b)]= 1,& \alpha \perp \beta,\ \tag{R$3^\bot_{d,e}$} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$}
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),& \alpha + \beta \in \Phi \tag{R$2_{d,e}$} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha + \beta \not \in \Phi\cup\{0\}.\ \tag{R$3_{d,e}$}
+%&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$}
 \end{align}
-where $a, a' \in B_d$, $b\in R_e$. 
 %For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
 
-For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of generators $x_\alpha(a)$, $\alpha\in \Phi$, $a\in B_d$, $d\leq n$, and relations $\text{R}1_{d}$, $\text{R3}^\angle_{d, e}$ and $\text{R3}^\bot_{d, e}$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for those $d,e \leq n$ for which $d+e \leq n$.
+For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$
+modulo relations $\text{R}1_{d}$, $\text{R3}_{d, e}$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for those $d,e \leq n$ for which $d+e \leq n$.
+
+It will be convenient for us to distinguish between the cases when depending on whether the roots $\alpha, \beta$ appearing in $\text{R3}_{d,e}$ are orthogonal to each other or form a sharp angle.
+In the former case we denote such relator by $\text{R3}^\bot_{d,e}$, and in the latter case by $\text{R3}^\angle_{d,e}$.
+
+The following lemma is inspired by the proof of the main result in ???.
+Basically, it says that most of the relators $\text{R3}^\bot_{d,e}$ in the presentation of $\St^{\leq n}(\Phi, B)$ are superflous.
+\begin{lemma}\label{superfluous-relations}
+
+\end{lemma}
+\begin{proof}
+We will use the following commutator identities (cf Rehmann-Soule).
+\begin{align} \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
+ \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].& \end{align}
+
+In the case $0 < d \leq e \leq n$ the assertion follows from the following computation:
+\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$  } \\ 
+ = [[x_{\alpha+\beta}(at^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\beta+\gamma}(b)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\alpha}(at^e), x_{\beta+\gamma}(b)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \\ 
+ = [x_{\alpha}(at^e) \cdot x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \\ 
+ = {}^{x_\alpha(at^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \\
+ = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \end{align*}
+
+In the case $d \leq 0 \leq e \leq n$
+\begin{align*} 
+ [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+ = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
+ = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$. \qedhere} \end{align*}
+\end{proof}
 
@@
 \end{proof}
-\end{comment}
-\begin{align}
- \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
- \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].&
-\end{align}
-
-In the case $1\leq d \leq e \leq n$ the assertion follows from the following computation:
-\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$  } \\ 
- = [[x_{\alpha+\beta}(at^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\beta+\gamma}(b)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\alpha}(at^e), x_{\beta+\gamma}(b)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \\ 
- = [x_{\alpha}(at^e) \cdot x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \\ 
- = {}^{x_\alpha(at^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \\
- = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \end{align*}
-
-In the case $d < 1\leq e \leq n$
-\begin{align*} 
- [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
- = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
- = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$.} \end{align*}
 
@@
 Now the same argument as in Lemma~\ref{welldef} allows to prove that $[s_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1$ for $b\in R_e$, $e\leq0$, what finishes the proof of R3.2$\!\,_{n+1}$.
-
+\end{comment}
 \subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}

### 2019-06-08 dl-paper.tex
Added statement of Lemma 8

@@
 
-\subsection{Lemma on the presentation of Steinberg groups}
+\subsection{Presentation by Homogeneous elements}
 %Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
@@
 \begin{align}
-&\,\,x_{\alpha}(a)x_{\alpha}(a') =  x_{\alpha}(a+a'),& \tag{R$1_d$} \\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),& \alpha + \beta \in \Phi \tag{R$2_{d,e}$} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha + \beta \not \in \Phi\cup\{0\}.\ \tag{R$3_{d,e}$}
-%&[x_{\alpha}(a),\,x_{\beta}(b)]= 1,& \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$}
+&\,\,x_{\alpha}(a)\cdot x_{\alpha}(a') =  x_{\alpha}(a+a'),                        & \tag{R$1_d$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),   & \alpha + \beta \in \Phi,\ \tag{R$2_{d,e}$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$} \\
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha \perp \beta \in \Phi.\ \tag{R$3^\bot_{d,e}$}
 \end{align}
@@
 For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$
-modulo relations $\text{R}1_{d}$, $\text{R3}_{d, e}$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for those $d,e \leq n$ for which $d+e \leq n$.
-
-It will be convenient for us to distinguish between the cases when depending on whether the roots $\alpha, \beta$ appearing in $\text{R3}_{d,e}$ are orthogonal to each other or form a sharp angle.
-In the former case we denote such relator by $\text{R3}^\bot_{d,e}$, and in the latter case by $\text{R3}^\angle_{d,e}$.
-
-The following lemma is inspired by the proof of the main result in ???.
-Basically, it says that most of the relators $\text{R3}^\bot_{d,e}$ in the presentation of $\St^{\leq n}(\Phi, B)$ are superflous.
+modulo relations $\text{R}1_{d}$, $\text{R3}^\angle_{d, e}$, $\text{R3}_{d,e}^\bot$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for $d,e,d+e \leq n$.
+The following lemma asserts that most of the relators $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ can be omitted.
 \begin{lemma}\label{superfluous-relations}
-
+ One can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ all the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
 \end{lemma}
@@
 
-In the case $d \leq 0 \leq e \leq n$
+In the case $d \leq 0 \leq e \leq n$ for $\xi \in B_d$ one has
 \begin{align*} 
@@
 \end{gather*}
-The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies the desired relation.
+The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which shows that the desired relation holds.
 \end{proof}
@@
 
+\end{comment}
 \include{rehmann}
-\end{comment}
 

### 2019-06-09 dl-paper.tex
Rewritten Lemma 8

@@
 
-In our computations we will use two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
+For our computations we will need two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
 \begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \end{equation}
 
-Recall also that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^*$ as follows:
-\begin{equation} \label{eq:dennis-stein}
- \langle r,s \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- s}{1 + rs}\right) \cdot x_{\alpha}(r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\tfrac{- r}{1+rs}\right) \cdot h_{\alpha}(1 + rs)^{-1}.
+Our convention for Dennis--Stein symbols follows~\cite{DS73} (and {\it not} III.5.11 of ~\cite{Kbook}).
+Recall that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^*$ as follows:
+\begin{equation} \label{eq:dennis-stein}  \langle r,s \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- s}{1 + rs}\right) \cdot x_{\alpha}(r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\tfrac{- r}{1+rs}\right) \cdot h_{\alpha}(1 + rs)^{-1}.
 \end{equation}
-Notice that our notation follows~\cite{DS73} and {\it not}~III.5.11 of~\cite{Kbook}.
 
@@
 \begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^*,\ \
- \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^* \end{equation}
+ \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^*. \end{equation}
 
@@
 
-\subsection{Presentation by Homogeneous elements}
+\subsection{Presentation of Steinberg groups by homogeneous generators}
 %Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
 Let $I\trianglelefteq A$ be an ideal of a commutative ring $A$.
-We consider $A[X, X\inv]$ as a $\mathbb{Z}$-graded ring in which $X^{-1}$ has degree $1$.
-We denote by $B = B(A, I)$ the subring $A[X^{-1}] + I[X] \subseteq A[X, X\inv]$ with the induced grading.
-As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot X^d$ for $d>0$, and $B_d=A \cdot X^d$ for $d\leq0$.
-Obviously, $B = A[X^{-1}]$ in the case $I=0$ and $B = A[X, X^{-1}]$ in the case $I=A$.
+We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
+We denote by $B = B(A, I)$ the subring $A[t^{-1}] + I[t] \subseteq A[t, t\inv]$ with the induced grading.
+As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\leq0$.
+Obviously, $B = A[t]$ in the case $I=0$ and $B = A[t, t\inv]$ in the case $I=A$.
 
 Whenever the coefficient $\xi$ of a Steinberg generator $g = x_\alpha(\xi)$ of $\St(\Phi, B)$ is a homogeneous element of $B$, i.\,e. $\xi \in B_d$ for some $d \in \mathbb{Z}$,
- we call the corresponding generator $g$ homogeneous of degree $d$.
+ we call the corresponding generator $g$ {\it homogeneous of degree $d$}.
 It is not hard to show that $\St(\Phi, B)$ can be presented by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations
@@
 \end{align}
+By the degree of a relation we mean the maximum of the degrees of generators that appear in it.
+For example, the degree of $\text{R2}_{d,e}$ is $\max(d,e,d+e)$ while the degree of $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
 %For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
 
-For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$
-modulo relations $\text{R}1_{d}$, $\text{R3}^\angle_{d, e}$, $\text{R3}_{d,e}^\bot$ for all $d,e \leq n$ and $\text{R2}_{d,e}$ for $d,e,d+e \leq n$.
+For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$ modulo Steinberg relations of degree $\leq n$.
 The following lemma asserts that most of the relators $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ can be omitted.
 \begin{lemma}\label{superfluous-relations}
- One can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ all the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
-\end{lemma}
-\begin{proof}
-We will use the following commutator identities (cf Rehmann-Soule).
-\begin{align} \label{eq:H1ii}  [ab, c] = {}^a[b, c] \cdot [a,c];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
- \label{eq:H1iii} [a,c]   = 1    \text{ implies } [a, [b,c]] = [[a,b],{}^bc].& \end{align}
-
-In the case $0 < d \leq e \leq n$ the assertion follows from the following computation:
-\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$  } \\ 
+ For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ all the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
+\end{lemma}
+\begin{proof}
+For the proof we will need the following commutator identities:
+\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
+ \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}
+Without loss of generality we may assume $e \geq d$ and $e > 0$. Let $\alpha$ and $\gamma$ be a pair of orthogonal roots of $\Phi$.
+We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
+
+We start with the following two observations inspired by the proof of the main result of~\cite{RS76}.
+\begin{enumerate}
+\item In the case $0 < d \leq e \leq n$ the relation $\text{R3}^\bot_{d,e}$ is a consequence of $\text{R3}^\bot_{0,e-d}$:
+\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \\ 
  = [[x_{\alpha+\beta}(at^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\beta+\gamma}(b)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \\ 
@@
 
-In the case $d \leq 0 \leq e \leq n$ for $\xi \in B_d$ one has
-\begin{align*} 
- [x_\alpha(\xi), x_{\gamma}(bt^{e})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
- = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
- = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(b't^{e-1}\xi), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$. \qedhere} \end{align*}
+\item In the case $d \leq 0 \leq e \leq n$ the relation $\text{R3}^\bot_{d,e}$ is a consequence of $\text{R3}^\bot_{1,d+e-1}$:
+\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+ = [[x_\alpha(at^d), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
+ = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(ab't^{e-1}t^d), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$.} \end{align*} \end{enumerate}
+
+To see that $\text{R3}^\bot_{d,e}$ is superfluous one must iteratively apply one of the above observations.
+Notice that the value $\max(0,d,e)$ decreases strictly whenever $e > 1$. 
+Finally, by the first observation $\text{R3}^\bot_{1,1}$ follows from $\text{R3}^\bot_{0,0}$.
 \end{proof}

### 2019-06-09 dl-paper.tex
Minor fix

@@
 \begin{lemma}\label{superfluous-relations}
- For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ all the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
+ For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
 \end{lemma}
@@
  = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$.} \end{align*} \end{enumerate}                                                           
-
-To see that $\text{R3}^\bot_{d,e}$ is superfluous one must iteratively apply one of the above observations.
-Notice that the value $\max(0,d,e)$ decreases strictly whenever $e > 1$. 
-Finally, by the first observation $\text{R3}^\bot_{1,1}$ follows from $\text{R3}^\bot_{0,0}$.
-\end{proof}
-
-\begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_\Phi\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
+Together the above observation show that if the degree of the relator $\text{R3}^\bot_{d,e}$ is $\geq 2$ then it is a consequence of some relator $\text{R3}^\bot_{d',e'}$ of strictly smaller degree.
+Finally, by the first observation, $\text{R3}^\bot_{1,1}$ is a consequence of $\text{R3}^\bot_{0,0}$.
+\end{proof}
+
+\begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
 In particular, the natural map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
@@
 \begin{proof}
- The special case $\Phi=\rA_{\geq 4}$ of the assertion is due to Tulenbayev, see~\cite[Lemma~3.3]{Tu83}. Thus, it remains to deduce from it the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
-
- Denote by $A_4(\Phi)$ the set consisting of all root subsystems of $\Phi$ of type $\rA_4$ and by $G_n$ the free product of groups $\coprod\limits_{\Psi \in A_4(\Phi)} \St^{\leq n}(\Psi, B)$ amalgamated over relations $x^{\Psi_1}_\alpha(a) = x^{\Psi_2}_\alpha(a)$ for all $a \in B_d$, $d \leq n$, $\alpha \in \Psi_1\cap\Psi_2$, $\Psi_1, \Psi_2 \in A_4(\Phi)$.
+ The special case $\Phi=\rA_{\geq 4}$ of the assertion is due to Tulenbayev, see~\cite[Lemma~3.3]{Tu83}. 
+ Therefore it can be used to deduce our assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
+
+ %Denote by $A_4(\Phi)$ the set consisting of all root subsystems of $\Phi$ of type $\rA_4$ and by $G_n$ the free product of groups $\coprod\limits_{\Psi \in A_4(\Phi)} \St^{\leq n}(\Psi, B)$ amalgamated over relations $x^{\Psi_1}_\alpha(a) = x^{\Psi_2}_\alpha(a)$ for all $a \in B_d$, $d \leq n$, $\alpha \in \Psi_1\cap\Psi_2$, $\Psi_1, \Psi_2 \in A_4(\Phi)$.
 

### 2019-06-10 dl-paper.tex
Many fixes in Lemma 8

@@
 \end{align}
-By the degree of a relation we mean the maximum of the degrees of generators that appear in it.
-For example, the degree of $\text{R2}_{d,e}$ is $\max(d,e,d+e)$ while the degree of $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
+By the degree of a Steinberg relation we mean the maximum of degrees of generators that appear in it.
+For example, the degree of every relation of type $\text{R2}_{d,e}$ is $\max(d,e,d+e)$ 
+ while the degree of a relation of type $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
 %For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
@@
 For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$ modulo Steinberg relations of degree $\leq n$.
-The following lemma asserts that most of the relators $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ can be omitted.
+The following lemma asserts that most of the relations of type $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ 
+ are superfluous and can be omitted.
 \begin{lemma}\label{superfluous-relations}
- For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from the presentation of $\St^{\leq n}(\Phi, B)$ the relators $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
+ For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from
+ the presentation of $\St^{\leq n}(\Phi, B)$ all relations of type $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
 \end{lemma}
@@
  \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}
-Without loss of generality we may assume $e \geq d$ and $e > 0$. Let $\alpha$ and $\gamma$ be a pair of orthogonal roots of $\Phi$.
+
+The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree
+ $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot_{d',e'}$ of strictly smaller degree.
+Let $R=[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ be such a relation for some $\alpha\perp\gamma$.
 We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
-
-We start with the following two observations inspired by the proof of the main result of~\cite{RS76}.
+Without loss of generality we may assume $e \geq d$ and $e > 0$. We need to consider two cases.
 \begin{enumerate}
-\item In the case $0 < d \leq e \leq n$ the relation $\text{R3}^\bot_{d,e}$ is a consequence of $\text{R3}^\bot_{0,e-d}$:
-\begin{align*} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\alpha+\beta}(at^{e-d}), [x_{-\beta}(t^d), x_{\beta+\gamma}(b)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \\ 
- = [[x_{\alpha+\beta}(at^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\beta+\gamma}(b)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\alpha}(at^e), x_{\beta+\gamma}(b)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \\ 
- = [x_{\alpha}(at^e) \cdot x_{\alpha + \beta}(at^{e-d}), x_{\gamma}(bt^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \\ 
- = {}^{x_\alpha(at^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \\
- = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\alpha(at^e), x_\gamma(bt^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \end{align*}
-
-\item In the case $d \leq 0 \leq e \leq n$ the relation $\text{R3}^\bot_{d,e}$ is a consequence of $\text{R3}^\bot_{1,d+e-1}$:
-\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b't^{e-1}), x_{-\beta}(t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
- = [[x_\alpha(at^d), x_{\beta+\gamma}(b't^{e-1})], {}^{x_{\beta+\gamma}(b't^{e-1})}\!x_{-\beta}(t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
- = {}^{x_{\beta+\gamma}(b't^{e-1})}\![x_{\alpha+\beta+\gamma}(ab't^{e-1}t^d), x_{-\beta}(t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$.} \end{align*} \end{enumerate}                                                           
-Together the above observation show that if the degree of the relator $\text{R3}^\bot_{d,e}$ is $\geq 2$ then it is a consequence of some relator $\text{R3}^\bot_{d',e'}$ of strictly smaller degree.
-Finally, by the first observation, $\text{R3}^\bot_{1,1}$ is a consequence of $\text{R3}^\bot_{0,0}$.
+\item In the case $0 < d \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
+\begin{align} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\beta+\gamma}(bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
+ = [[x_{\beta+\gamma}(bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\gamma}(bt^e), x_{\alpha+\beta}(a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
+ = [x_{\gamma}(bt^e) \cdot x_{\beta + \gamma}(bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \nonumber \\ 
+ = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
+ = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \nonumber \end{align}
+
+\item In the case $d \leq 0 \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
+\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+ = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
+ = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{e+d-1}), x_{-\beta}(\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$,} \end{align*} where $\epsilon_1 = N_{\beta+\gamma,-\beta}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
+ \end{enumerate}
+
+The assertion of the lemma now follows from the above observation by induction on the degree of $R$ and the fact
+ that by~\eqref{first-computation} relation $\text{R3}^\bot_{1,1}$ is a consequence of $\text{R3}^\bot_{0,0}$.
 \end{proof}

### 2019-06-12 dl-paper.tex
Fixed signs of structure constants; fixed minor bugs; added reference on affine result

@@
  \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
-\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+\begin{proof} See~\cite[Corollary~5.3]{Ho05}. 
+%This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. 
+\end{proof}
 
@@
 
-The following lemma summarizes basic properties of structure constants which will be used in the computations below, often without explicit reference.
-\begin{lemma} Suppose $\alpha, \beta \in \Phi$ are such that $\alpha+\beta \in \Phi$.
-\begin{enumerate}\label{lem:structure-constants}
- \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
- \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
- \item $N_{\alpha, \beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}.$
-\end{enumerate}
-\end{lemma}
-\begin{proof} See~\cite[\S~14]{VP}. \end{proof}
+The following lemma summarizes basic properties of structure constants which will be used in our computations below, often without further reference.
+\begin{lemma} Suppose $(\alpha, \beta, \gamma)$ is a triple of roots forming a basis of root subsystem of type $\rA_3$
+ (i.\,e. such that $\alpha+\beta, \beta + \gamma \in \Phi$ and $\alpha \perp \beta$), then holds:
+\begin{equation} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
+\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation}
+\end{lemma} \begin{proof} See~\cite[\S~14]{VP}. \end{proof}
 
@@
 We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
-We denote by $B = B(A, I)$ the subring $A[t^{-1}] + I[t] \subseteq A[t, t\inv]$ with the induced grading.
-As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\leq0$.
+We denote by $B = B(A, I)$ the subring $A[t] + I[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
+As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$.
 Obviously, $B = A[t]$ in the case $I=0$ and $B = A[t, t\inv]$ in the case $I=A$.
@@
 \item In the case $0 < d \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
-\begin{align} x_{\alpha+\beta+\gamma}(abt^e) = [x_{\beta+\gamma}(bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
- = [[x_{\beta+\gamma}(bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\gamma}(bt^e), x_{\alpha+\beta}(a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
- = [x_{\gamma}(bt^e) \cdot x_{\beta + \gamma}(bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \nonumber \\ 
- = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
- = x_{\alpha+\beta+\gamma}(abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}. \nonumber \end{align}
+\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
+[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_2 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
+ = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_2 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\gamma}(- bt^e), x_{\alpha+\beta}(-\delta_2 \cdot a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
+ = [x_{\gamma}(bt^e) \cdot x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,d}$} \nonumber \\ 
+ = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
+ = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
+ where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha+\beta,\gamma}$, $\delta_2 = N_{\alpha,\beta}$
+ and in the fourth equality we use~\eqref{eq:cocycle}.
 
 \item In the case $d \leq 0 \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
-\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
- = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
- = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{e+d-1}), x_{-\beta}(\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$,} \end{align*} where $\epsilon_1 = N_{\beta+\gamma,-\beta}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
+\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+ = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
+ = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{e+d-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$,} \end{align*} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
  \end{enumerate}
@@
 
-\begin{lemma} The operators $T_\alpha$ satisfy $\text{R3}_{\leq 0, 1}$. \end{lemma}
+\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\text{R3}_{\leq 0, 1}$. \end{lemma}
 \begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
@@
 
-\begin{lemma} The operators $T_\alpha$ satisfy $\text{R2}_{\leq -1, 1}$. \end{lemma}
+\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\text{R2}_{\leq -1, 1}$. \end{lemma}
 \begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
@@
 The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R2}_{0,1}$ and relations $\text{R3}_{1,1}^{\angle}$ in the special case when $\alpha, \beta$ form a sharp angle. \end{prop}
+\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations of types $\text{R2}_{0,1}$ and $\text{R3}_{1,1}^{\angle}$. \end{prop}
 \begin{proof} 

### 2019-06-13 dl-paper.tex
Many small fixes

@@
 all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The structure constants $N_{\alpha \beta i j}=\pm 1,2,3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and can be computed explicitly.
+The structure constants $N_{\alpha \beta i j}=\pm 1,\pm 2,\pm 3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and {\bf TODO}:
+% в литературе описываются способы выбрать эти константы ссылка на третий взгляд.
 
@@
 
-Recall that for $\alpha\in\Phi$ and $s \in R^*$ the semisimple root elements $h_\alpha(s)$ are defined as follows: \[h_\alpha(s)=w_\alpha(s) \cdot w_\alpha(-1), \text{ where } w_\alpha(s) = x_\alpha(s) \cdot x_{-\alpha}(-s^{-1}) \cdot x_\alpha(s).\]
+Recall that for $\alpha\in\Phi$ and $s \in R^\times$ the semisimple root elements $h_\alpha(s)$ are defined as follows: 
+\[h_\alpha(s)=w_\alpha(s) \cdot w_\alpha(-1), \text{ where } w_\alpha(s) = x_\alpha(s) \cdot x_{-\alpha}(-s^{-1}) \cdot x_\alpha(s).\]
 
@@
 
-For our computations we will need two explicit elements of $\K_2(\Phi, R)$. Recall that Steinberg symbols are defined for any $s, t \in R^*$ by the identity
+In our computations we use two explicit families of elements of $\K_2(\Phi, R)$: Steinberg and Dennis--Stein symbols.
+Recall that Steinberg symbols are defined for any $s, t \in R^\times$ by the identity
 \begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \end{equation}
@@
 Our convention for Dennis--Stein symbols follows~\cite{DS73} (and {\it not} III.5.11 of ~\cite{Kbook}).
-Recall that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^*$ as follows:
+Recall that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^\times$ as follows:
 \begin{equation} \label{eq:dennis-stein}  \langle r,s \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- s}{1 + rs}\right) \cdot x_{\alpha}(r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\tfrac{- r}{1+rs}\right) \cdot h_{\alpha}(1 + rs)^{-1}.
@@
 Dennis--Stein symbols and Steinberg symbols are related to each other via the following identities:
-\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^*,\ \
- \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^*. \end{equation}
+\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
+ \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
 
@@
 \subsection{Unstable Quillen K-groups} \label{sec:quillen}
-Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following reqirements:
+Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
 \begin{enumerate}
@@
   \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
- \item The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of 
-    the map $S(R) \to S(R/I)$. The kernel of $\mu$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+ \item The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of the map $S(R) \to S(R/I)$.
+       Denote the kernel of $\mu$ by $C(R, I)$.
+       Then $C(R, I)$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
  \item There is a natural exact sequence:
- \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \Ker(\mu).} \]
+ \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C(R, I).} \]
  \end{enumerate}   
@@
 \begin{proof}
- The first claim follows from Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook} (here we use~\eqref{req:subfunc}--\eqref{req:uce}).
+ The first claim follows from \cite[Chapter~IV]{Kbook} (cf.
+Exercises~1.8--1.9 ibid, here we use assumptions~\eqref{req:subfunc}--\eqref{req:uce}).
 %provided one verifies that all the intermediate isomorphisms are natural in $R$.
@@
 
-Let us mention the example of a triple $(G,P,S)$ satisfying the above conditions.
-\begin{example} \label{ex:orth}
+The principal example of a triple $(G,P,S)$ satisfying the above conditions is as follows.
 For $n \geq 5$ take the orthogonal group functor $\mathrm{O}_{2n}(-)$ and its elementary subfunctor $\mathrm{EO}_{2n}(-)$ as functors $G_n$ and $P_n$, respectively.
@@
 From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\eqref{req:uce}.
- The other requirements can be verified in a straightforward manner.
-\end{example}
+ The other requirements can be verified in a straightforward manner. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
 
@@
  we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
-Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests %TODO: Does it really change K_2?
- it would not change $\K_i(G_n, P_n, -)$ for $i\geq 3$.
-
-Now let $G_n, P_n$ be again as in~\cref{ex:orth}. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
+Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
+ it would not change $\K_3(G_n, P_n, -)$.
+
 Let us formulate the stability theorem for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
@@
  \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
-\begin{proof} See~\cite[Corollary~5.3]{Ho05}. 
-%This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. 
-\end{proof}
+\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
 
@@
 \end{equation}
-The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits.
-This immediately follows e.\,g. from the exact sequence of~\cref{characterization}, it is also possible to give a direct proof of this fact, see \cite[Lemma~8]{S15}.
+The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
 The following result plays a key role in the proof of~\cref{thm41}.
@@
  KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is isomorphic to the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
-Invoking~\cref{bass-ft} we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
+In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+Invoking~\cref{bass-ft} (or~\cite[Corollary~5.3]{Ho05}) we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
 By \cite[Lemma~2.2]{FRS12} the group $\GW_2^{[3]}(k)$ is trivial, therefore $f'$ (and hence $f$) are surjective.
@@
 \end{comment}
-Throughtout this section $A$ denotes an arbitary ring and $I, J$ two its ideals and $\Phi$ a simply laced root system.
-
-The following lemma summarizes basic properties of structure constants which will be used in our computations below, often without further reference.
+Throughtout this section $A$ denotes an arbitary ring, and $I, J$ two its ideals, and $\Phi$ a simply laced root system.
+
+The following lemma summarizes basic properties of structure constants which will be used in our computations below, often without further reference (cf.~\cite[\S~14]{VP}).
 \begin{lemma} Suppose $(\alpha, \beta, \gamma)$ is a triple of roots forming a basis of root subsystem of type $\rA_3$
@@
 \begin{equation} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
-\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation}
-\end{lemma} \begin{proof} See~\cite[\S~14]{VP}. \end{proof}
+\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
 
@@
 It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
-We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^*$, $v \in R^*$, $\alpha\in \Phi$.
+We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^\times$, $v \in R^\times$, $\alpha\in \Phi$.
 
@@
 \begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, hence the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
-By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^*$, $m\in M$. \end{rem}
+By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^\times$, $m\in M$. \end{rem}
 
@@
 Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
-Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
+Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times$ consisting of those triples $(g, h, u)$ for which 
 $p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.

### 2019-06-17 dl-paper.tex
Fixed problem with symbols

@@
 \subsection{Steinberg groups}
-%TODO: Describe what root systems are sympelctic and which are not
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
@@
 
-In our computations we use two explicit families of elements of $\K_2(\Phi, R)$: Steinberg and Dennis--Stein symbols.
+\subsection{$\K_2$-groups and symbols}
+
+In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+Notice that our definition of these symbols follows~\cite{DS73}, rather than more modern textbooks such as~\cite{Kbook}.
 Recall that Steinberg symbols are defined for any $s, t \in R^\times$ by the identity
-\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1}. \end{equation}
-
-Our convention for Dennis--Stein symbols follows~\cite{DS73} (and {\it not} III.5.11 of ~\cite{Kbook}).
-Recall that Dennis--Stein symbols are defined for arbitrary $r, s\in R$ satisfying $1 + rs \in R^\times$ as follows:
-\begin{equation} \label{eq:dennis-stein}  \langle r,s \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- s}{1 + rs}\right) \cdot x_{\alpha}(r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\tfrac{- r}{1+rs}\right) \cdot h_{\alpha}(1 + rs)^{-1}.
+\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
+In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$ by the following formula:
+\begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab).
 \end{equation}
-
-Dennis--Stein symbols and Steinberg symbols are related to each other via the following identities:
+Dennis--Stein symbol $\langle a, b \rangle_\alpha$ can be expressed through Steinberg symbols in the special case when either $a$ or $b$ is an invertible element of $R$.
+More specifically, the following formulae hold (cf.~\cite[p.~250]{DS73}).
 \begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
  \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
-
 %Using~\eqref{eq:conj-h-h} it is easy to verify that \[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}.\] 
-It is easy to show that the above symbols depend only on the length of $\alpha$.
-Moreover, if $\Phi$ is nonsymplectic, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e.
-\begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}.
+Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced.
+If $\Phi$ happens to be {\it nonsymplectic}, i.\,e.
+$\Phi \neq \rA_1, \rB_2, \rC_{\geq 3}$, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e.
+they satisfy the following identities: \begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}.
 \end{equation}
+For these and other properties of symbols we refer the reader to~\cite{DS73}.
 
@@
 \end{comment}
+The classical Matsumoto theorem (see~\cite[Theorem~5.10]{Ma69}) allows one to compute the group $\K_2(\Phi, R)$ in the special case when $R=k$ is a field.
+More concretely, it asserts that $\K_2(\Phi, k) \cong \K_2^\mathrm{MW}(k)$ provided $\Phi$ is symplectic and  $\K_2(\Phi, k) \cong \K_2^\mathrm{M}(k)$ otherwise.
+In the following lemma we compute the group $\K_2(\Phi, R)$ in yet another case when $R=k[X, X\inv]$.
+\begin{lemma}\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
+\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ in which} \]
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+\begin{proof} If $\Phi$ is nonsymplectic one can choose a long simple root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
+\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
+                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
+Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto theorem.
+The assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.
+
+If $\Phi$ is symplectic the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
+ which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of~\cref{bass-ft} and~\cite[Lemma~4.1.1]{AF17}. \end{proof}
 
@@
 \section{First injectivity theorem}
-\begin{prop} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
-Then there is a split exact sequence of abelian groups
-\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{prop}
-\begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
-                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
-Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto's theorem~\cite[Theorem~5.10]{Ma69}.
-The required assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.
-
-In the symplectic case the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
- which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of~\cref{bass-ft} and~\cite[Lemma~4.1.1]{AF17}. \end{proof}
-
 \begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
@@
                \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
-in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by the above lemma. \end{proof}
+in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
 \begin{theorem} \label{thm41}
@@
 \begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha.\] \end{df}
+\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}
 It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
@@
 \begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$.
-Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein} shows that
+Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein},\eqref{eq:symbol-properties} shows that
  \begin{multline*}
@@
  = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}, \end{multline*}
@@
 
+\include{rehmann}
 \end{comment}
-\include{rehmann}
 

### 2019-06-17 dl-paper.tex
Moved lemmas

@@
 \[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
-\begin{proof} If $\Phi$ is nonsymplectic one can choose a long simple root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
+\begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
 \[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
@@
 
-If $\Phi$ is symplectic the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
- which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of~\cref{bass-ft} and~\cite[Lemma~4.1.1]{AF17}. \end{proof}
+In the symplectic case the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
+ which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of and~\cite[Lemma~4.1.1]{AF17} and \cref{bass-ft} below. \end{proof}
+
+\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
+\begin{proof} The result follows from consideration of the commutative diagram
+\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
+               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
+in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
 
@@
 
-If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
-\begin{equation} \label{relSteinberg-def}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.}
-\end{equation}
-The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
-The following result plays a key role in the proof of~\cref{thm41}.
-\begin{lemma} \label{lem:prop41}
-In the notation of~\cref{lem:lemma32} assume additionally that the residue field $k$ is of characteristic $\neq 2$.
-Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$.
-\end{lemma}
-\begin{proof}
-  Consider the following commutative diagram with rows obtained from~\cref{characterization}:
-\begin{equation*}\xymatrix{
- KO_3(2\ell, B) \ar[r] \ar[d] & KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
- KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
-Invoking~\cref{bass-ft} (or~\cite[Corollary~5.3]{Ho05}) we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
-By \cite[Lemma~2.2]{FRS12} the group $\GW_2^{[3]}(k)$ is trivial, therefore $f'$ (and hence $f$) are surjective.
-\end{proof}
-
 \subsection{Some elementary lemmas}
@@
 \section{First injectivity theorem}
-\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
-\begin{proof} The result follows from consideration of the commutative diagram
-\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
-               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
-in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
+
+If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
+\begin{equation} \label{relSteinberg-def}
+ \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.}
+\end{equation}
+The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
+The following result plays a key role in the proof of~\cref{thm41}.
+\begin{lemma} \label{lem:prop41}
+In the notation of~\cref{lem:lemma32} assume additionally that the residue field $k$ is of characteristic $\neq 2$.
+Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$.
+\end{lemma}
+\begin{proof}
+  Consider the following commutative diagram with rows obtained from~\cref{characterization}:
+\begin{equation*}\xymatrix{
+ KO_3(2\ell, B) \ar[r] \ar[d] & KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
+ KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
+In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+Invoking~\cref{bass-ft} (or~\cite[Corollary~5.3]{Ho05}) we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
+By \cite[Lemma~2.2]{FRS12} the group $\GW_2^{[3]}(k)$ is trivial, therefore $f'$ (and hence $f$) are surjective.
+\end{proof}
+
 \begin{theorem} \label{thm41}
@@
 
-\begin{comment}
-\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
-$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
-$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
-Using $\pi(z) = 1$ we get 
-\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
-
-We need to introduce notation for certain subgroups of $\St(A[X, X^{-1}])$:
-\begin{align}
- G_+^0 & = \mathrm{Im}(\St(\Phi, A[X], XM[X]) \to \St(A[X, X^{-1}]))\\
- G_+   & = \mathrm{Im}(\St(\Phi, A[X], M[X]) \to \St(A[X, X^{-1}]))
-\end{align}
-Notice that for $ g\in G_+$ the element $ev_{X=0}(g)^{-1}g$ lies in $G_+^0$.
-
-\begin{rem} Our goal is to rewrite $x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X))$, where $f_1(X) \in M[X]$, $f_2(X) \in A[X]$ as
- $g \cdot x_\alpha(\frac{aX^{-1}}{1+am}) \cdot \{ 1 + am, X \}$ for some $g \in G_+$
- and $m \in M$. At first assume that $\Phi$ is simply-laced. \end{rem}
-
-\begin{lemma} \label{lem:lem34} Assume that $\Phi$ is simply-laced and of rank $\geq 2$.
- For any $a\in A$, $\alpha\in \Phi$, $g \in G^0_+$ there exists $m = m(g)\in M$ and $g'\in G_+$ such that 
- \[x_{\alpha}(aX^{-1}) g  = g' Y_\alpha(a,m) \text{ where } Y_\alpha(a,m) = x_\alpha(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\}.\]
-\end{lemma}
-\begin{proof}
- We can choose some parabolic subset $S$ of roots in $\Phi$ in such a way that its special part $\Sigma_S$ does not contain the root $\alpha$.
- By~\cref{lem:Zgen} the subgroup $G_+^0$ is generated by images in $\St(\Phi, A[X, X^{-1}]$ of the elements of the set $\mathcal{Z}(\Sigma_S, A[X], XM[X])$.
- Thus, we can write $g_0$ as a product of elements $z_\beta(f_1(X), f_2(X))$ such that $f_1(X) \in XM[X]$, $f_2(X) \in A[X]$ and, moreover, $f_2(X) = 0$ whenever $\beta \not \in \Sigma_S$.
-
- It is easy to verify using~\eqref{eq:symbol-properties} that \[x_\alpha(aX^{-1}) \cdot g_0 \cdot g_1 = g_0' \cdot Y_\alpha(a, m(g_0)) \cdot g_1 = g_0' \cdot g_1' \cdot Y_\alpha(a, m(g_0)+m(g_1)),\] therefore it suffices demonstrate the assertion of the lemma in the special case $g = z_\beta(f_1(X), f_2(X))$.
-
- We proceed by case analysis. Let us first analyze the cases when $\beta \neq -\alpha$. In all these cases $m(g) = 0$.
- \begin{enumerate}
- \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.}  Obviously, in this case also $g' = g$.
- \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
- \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
- \item {\it Case $\alpha = \beta$.} By our choice of $S$ holds $\beta \not \in \Sigma_S$, therefore $f_2(X) = 0$ and $g$ commutes with $x_\alpha(aX^{-1})$.
- \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
- Direct computation using formula from~\cite[Lemma~9]{S15} shows that:
- \begin{multline*}
- x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
- \end{multline*}
- \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.} Similarly to the above case:
- \begin{multline*}
-  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1}).
- \end{multline*} \end{enumerate}
-Now we turn to the case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$.
-Since $g$ commutes with $x_\alpha(\pm f_2(X))$, it suffices to prove the assertion in the special case $f_2(X)=0$.
-First consider the case $f_1(X) = mX$, where $m\in M$. Since $\Phi$ is nonsymplectic, we can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
-Now direct computation invoking~\eqref{eq:conj-h-h}--\eqref{eq:dennis-stein} and the centrality of symbols shows that:
-\begin{multline*}
- x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
- = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
- = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
- x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
-\end{multline*}
-
-Now suppose $f_1(X) = X^2f_1'(X)$. Choose $\gamma$ such that $\alpha + \gamma \in \Phi$.
-Then everything we need follows from the computation:
-\begin{multline*}
- x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X^2 mf_1'(X)) \cdot x_\alpha(-aX^{-1}) = 
- {}^{x_\alpha(aX^{-1})}[x_{-\alpha - \gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)), x_{\gamma}(X)] = \\
- = [x_{-\alpha-\gamma}(N_{-\alpha-\gamma, \gamma}Xf_1'(X)) x_{-\gamma}(N_{-\alpha-\gamma, \gamma} N_{-\alpha-\gamma, \alpha} af_1'(X)), x_\gamma(X) x_{\alpha+\gamma}(N_{\alpha,\gamma}a)].
-\end{multline*} 
-\end{proof}
-
-\begin{rem}
- From the proof of the above lemma it is easy to describe the way to compute... 
-\end{rem}
-\include{rehmann}
-\end{comment}
-
 \section{Second injectivity theorem}
-\begin{comment} 
-First of all, set $\widetilde{V} = \overline{G}^{\geq 0}_M \times G^{\leq 0} \times (1 + M)^*$
- and consider it as a pointed set, i.\,e. ignore its structure of the group but retain $\widetilde{v_0} = (1, 1, 1)$ as a choice of a basepoint.
-We let the group $\St(\Phi, R, M)$ act on $\widetilde{V}$ via the formula 
- $h \cdot (\overline{g}^+, g^-, u) = (\overline{g}^+ \cdot j_+i_+(h), i_-(h)^{-1}\cdot g^-, u)$.
-Denote by $V$ the set of orbits of this action with the fixed basepoint $v_0 = O(\widetilde{v}_0)$.
-We will use the notation $[\overline{g}^+, g^-, u]$ as a shorthand for $O(\overline{g}^+, g^-, u)$.
-
-It is obvious that the map $\widetilde{p} \colon \widetilde{V} \to \St(\Phi, R[t, t^{-1}])$ given by 
- \[(\overline{g}^+, g^-, u) \mapsto \overline{g}^+ \cdot j_-(g^-) \cdot \{t, u\}\]
- is constant on the orbits of the above action
-  and therefore gives rise to a well-defined map $p \colon V \to \St(\Phi, R[t, t^{-1}])$ of pointed sets.
-
-We will construct an action of $\St(\Phi, B)$ on the set $V$ with the following additional properties:
-\begin{enumerate}
-\item for $g^- \in \St(\Phi, R[t^{-1}])$ one has $\varphi(g^-) \cdot v_0 = [1, g^-, 1]$, where $\varphi$ is the canonical map
-  $\St(\Phi, R[t^{-1}]) \to \St(\Phi, B)$ induced by the embedding $R[t^{-1}] \to B$.
-\item for $g \in \St(\Phi, B)$ the element $p(g \cdot v_0)$ coincides with the canonical image of $g$ in $\St(\Phi, R[t, t^{-1}])$; 
-\end{enumerate} \end{comment}
 

### 2019-06-17 dl-paper.tex
More text on structure constants

@@
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
-Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(\xi)$ where $\xi\in R, \alpha\in\Phi$ and relations:
+Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ (where $\alpha\in\Phi, s\in R$) and relations:
 \begin{align}
 & \phantom{[}
-x_\alpha(s) x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
+x_\alpha(s) \cdot x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
 & [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
@@
 all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The structure constants $N_{\alpha \beta i j}=\pm 1,\pm 2,\pm 3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and {\bf TODO}:
-% в литературе описываются способы выбрать эти константы ссылка на третий взгляд.
-
-In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is simply-laced, in which case the above relations further simplify to
+The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$.
+There is a degree of freedom in the choice of these constants, for example, in the literature there are several methods of choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
+
+In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is simply-laced, i.\,e.
+does not contain double bonds, in which case Steinberg relations further simplify to the following relations:
 \begin{align}
-&x_{\alpha}(a)x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta}\,ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
+&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
 &[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
 \end{align}
-
-Recall that for $\alpha\in\Phi$ and $s \in R^\times$ the semisimple root elements $h_\alpha(s)$ are defined as follows: 
-\[h_\alpha(s)=w_\alpha(s) \cdot w_\alpha(-1), \text{ where } w_\alpha(s) = x_\alpha(s) \cdot x_{-\alpha}(-s^{-1}) \cdot x_\alpha(s).\]
-
-Recall from~\cite[Lemma~5.2]{Ma69} that the following identities hold for these elements:
+In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta, 1, 1} = N_{\alpha, \beta} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
+Although there is still some degree of freedom in their choice, these constants always must satisfy certain relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
+\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
+\begin{equation} \label{eq:simplest} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
+If, moreover, $\gamma \in \Phi$ is such that $\alpha,\beta,\gamma$ form a basis of a root subsystem of type $\rA_3$ then holds
+\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
+In the computations below we will be using identities~\eqref{eq:simplest} without explicit reference.
+
+For $\alpha\in\Phi$ and $s \in R^\times$ we define certain elements $w_\alpha(s), h_\alpha(s)$ of $\St(\Phi, R)$ (the latter ones are sometimes called {\it semisimple root elements}):
+\begin{align*} w_\alpha(s) & =  x_\alpha(s) \cdot x_{-\alpha}(-s^{-1}) \cdot x_\alpha(s), \\ h_\alpha(s) & =  w_\alpha(s) \cdot w_\alpha(-1).  \end{align*}
+
+Recall from~\cite[Lemma~5.2]{Ma69} that the following relations hold for semisimple root elements:
  \begin{align} 
-   \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u) \\
+   \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u), \\
    \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}.
@@
 In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
-Notice that our definition of these symbols follows~\cite{DS73}, rather than more modern textbooks such as~\cite{Kbook}.
-Recall that Steinberg symbols are defined for any $s, t \in R^\times$ by the identity
+Notice that our treatment of symbols follows~\cite{DS73}.
+Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
 \begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
-In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$ by the following formula:
+In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$:
 \begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab).
@@
 More concretely, it asserts that $\K_2(\Phi, k) \cong \K_2^\mathrm{MW}(k)$ provided $\Phi$ is symplectic and  $\K_2(\Phi, k) \cong \K_2^\mathrm{M}(k)$ otherwise.
-In the following lemma we compute the group $\K_2(\Phi, R)$ in yet another case when $R=k[X, X\inv]$.
+In the following lemma we compute the group $\K_2(\Phi, R)$ in yet another case $R=k[X, X\inv]$.
 \begin{lemma}\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
@@
 \begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
-\begin{proof} The result follows from consideration of the commutative diagram
+\begin{proof} Follows from consideration of the following commutative diagram:
 \[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
-               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
-in which the left arrow is an isomorphism by the corollary of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
+               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}]),} \]
+in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
 
@@
 Throughtout this section $A$ denotes an arbitary ring, and $I, J$ two its ideals, and $\Phi$ a simply laced root system.
-
-The following lemma summarizes basic properties of structure constants which will be used in our computations below, often without further reference (cf.~\cite[\S~14]{VP}).
-\begin{lemma} Suppose $(\alpha, \beta, \gamma)$ is a triple of roots forming a basis of root subsystem of type $\rA_3$
- (i.\,e. such that $\alpha+\beta, \beta + \gamma \in \Phi$ and $\alpha \perp \beta$), then holds:
-\begin{equation} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
-\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
 

### 2019-06-17 dl-paper.tex
Minor fix

@@
 In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta, 1, 1} = N_{\alpha, \beta} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
-Although there is still some degree of freedom in their choice, these constants always must satisfy certain relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
+Although there is still some degree of freedom in their choice, these constants always must satisfy the relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
 \begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds

### 2019-06-17 dl-paper.tex
Minor fixes

@@
 Recall from~\cite[Lemma~5.2]{Ma69} that the following relations hold for semisimple root elements:
- \begin{align} 
-   \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u), \\
-   \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}.
+\begin{align} \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u), \\ \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}.
 \end{align}
 
-\subsection{$\K_2$-groups and symbols}
-
-In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{$\K_2$-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our treatment of symbols follows~\cite{DS73}.
@@
 Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
-\begin{enumerate}
+\begin{enumerate} [label=(A\arabic*)]
  \item \label{req:left-exact} $G$ is left exact;
@@
  \item \label{req:uce} There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
- \item \label{req:coeq} $S$ preserves coequalizers of kernel pairs.
+ \item \label{req:coeq} For every pair $(R, I)$ the functor $S$ has the property that \[S(R \times_{R/I} R) \cong S(R) \times_{S(R/I)} S(R).\]
 \end{enumerate}
@@
 \begin{prop}\label{characterization}
+For $(G, P, R)$ as above the following statements are true.
 \begin{enumerate}
@@
 \begin{proof}
- The first claim follows from \cite[Chapter~IV]{Kbook} (cf.
-Exercises~1.8--1.9 ibid, here we use assumptions~\eqref{req:subfunc}--\eqref{req:uce}).
+ The first claim follows from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
+Exercises~1.8--1.9 ibid.).
 %provided one verifies that all the intermediate isomorphisms are natural in $R$.
 
- Let us verify the second claim. From~\eqref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$
+ Let us verify the second claim. From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$
   therefore $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
- From~\eqref{req:uce} we also obtain that $H_1(S(D_{R,I})) = H_2(S(D_{R,I})) = 0$ .
+ From~\ref{req:uce} we also obtain that $\HH_1(S(D_{R,I})) = \HH_2(S(D_{R,I})) = 0$ .
  The last two assertions allow us to invoke~\cite[Proposition~6]{Lo78} and conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$
   in the sense of~\cite[\S~3]{Lo78}. 
- Notice that this coequalizer coincides with $S(R) \to S(R/I)$ by~\eqref{req:coeq}. 
+ Notice that this coequalizer coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}. 
  Finally, the kernel of $\mu$ is isomorphic to $\HH_3(S(R), S(R/I), \ZZ)$ by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
@@
 Now set $S_n = \St(\rD_n, -)$.
-From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\eqref{req:uce}.
+From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce}.
  The other requirements can be verified in a straightforward manner. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
@@
 \section{First injectivity theorem}
-
 If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
@@
 
-\begin{comment}
-\begin{rem}
-We can take $\mathbb R^l$ with a base $\chi_1,\ldots,\chi_l$ and visualise root systems
-\[\rD_l=\{\pm\chi_i\pm\chi_j\mid1\leq i\neq j\leq l\}\]
-and $\rC_l=\rD_l\cup\{\pm2\chi_i\mid1\leq i\leq l\}$.
-Then we immediately see that $\alpha+\beta\in\rC_l\setminus\rD_l$ exactly means that either $\{\alpha,\beta\}$ or $\{-\alpha,-\beta\}$ equals $\{\chi_i-\chi_j,\chi_i+\chi_j\}$.
-Then for some $\sigma$ from the Weyl group of $\rD_l$ we get
-\[ \{\sigma\alpha,\sigma\beta\}=\{\chi_{l-1}-\chi_l, \chi_{l-1}+\chi_l\}=\{\alpha_{l-1},\alpha_l\} \]
-(the horns of the Dynkin diagram $\rD_l$).
-Another condition on $\alpha$ and $\beta$ equivalent to $\alpha+\beta\in\rC_l\setminus\rD_l$ is that they do not lie in any subsystem of $\rD_l$ of type $\rA_m$ for $m\geq4$.
-\end{rem}
-Everywhere below we set $t = X^{-1}$.
-\begin{lemma} \label{claim2} In $\St^{\leq n}(\Phi, B)$ relations $\text{R3}^\angle_{d, e}$ imply $\text{R3}^{\bot,0}_{d, e}$ for $1\leq d\leq e \leq n$. \end{lemma}
-\begin{proof}
-Without loss of generality we may assume that $\alpha, \gamma$ fit into some $\mathsf{A}_3$-triple $(\alpha, \beta, \gamma)$.
- \begin{align*}
- {}^{x_\gamma(t^d)}x_\alpha(bt^{e}) = {}^{x_\gamma(t^d)}[x_{-\beta}(b't^{e}), x_{\alpha+\beta}(1)] & \text{ by $\text{R2}_{e,0}$}\\
- = [x_{-\beta}(b't^{e}), {}^{x_\gamma(t^d)}x_{\alpha+\beta}(1)] & \text{ by $\text{R3}^\angle_{d, e}$}\\
- = [[x_{-\beta-\gamma}(b''t^{e-d}), x_\gamma(t^d)], {}^{x_\gamma(t^d)}x_{\alpha+\beta}(1)] & \text{ by $\text{R2}_{e-d,d}$}\\
- = [x_{-\beta-\gamma}(b''t^{e-d)}), [x_\gamma(t^d), x_{\alpha+\beta}(1)]] & \text{ by~\eqref{eq:H1iii} and $\text{R3}^\bot_{e-d,0}$}\\
- = x_{\alpha}(b'''t^{e}) & \text{ by $\text{R2}_{0,d}$ and $\text{R2}_{e-d,d}$.} \end{align*}
-Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
- $b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b,$ from which the claim follows.
-\end{proof}
-
-\begin{lemma} \label{claim3}
- In $\St^{\leq n}(\Phi, B)$ relations $\bot_0(d, e)$, $\angle(d, d)$ and $\angle(e, e)$ imply $\bot(d, e)$ for $d\leq e \leq n$.
-\end{lemma}
-\begin{proof}
- \begin{align*} 
- x_{\alpha+\beta+\gamma}(abt^{e}) = {}^{x_{-\beta}(t^d)}\!x_{\alpha+\beta+\gamma}(abt^{e}) & \text{ by $\text{R3}^{\bot, 0}_{d, e}$}\\
- = {}^{x_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{e-d}), x_\gamma(at^d)] & \text{ by $\text{R2}_{e-d,d}$} \\
- = [x_{\alpha}(b't^{e}) \cdot x_{\alpha+\beta}(b't^{e-d}), x_\gamma(at^d)] & \text{ by $\text{R2}_{e-d,d}$ and $\text{R3}^\angle_{d, d}$ }\\
- = {}^{x_{\alpha}(b't^{e})}\!x_{\alpha+\beta+\gamma}(abt^{e}) [x_{\alpha}(b't^{e}), x_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and $\text{R2}_{e-d,d}$} \\ = x_{\alpha+\beta+\gamma}(abt^{e}) [x_{\alpha}(b't^{e}), x_\gamma(at^d)] & \text{ by $\text{R3}^\angle_{e, e}$.
-\qedhere}
-\end{align*}
-\end{proof}
-
-We claim that $G_n\cong G_{n+1}$, more precisely, we construct an inverse homomorhism to the natural map $G_n\rightarrow G_{n+1}$.
-With this end we define elements $s_\alpha(a)\in G_n$ for $a\in R_{n+1}$ and prove the above relations for these elements.
-We start with the following easy fact.
-
-\begin{lemma}
-\label{welldef}
-Take $d$, $e\leq n$, $d+e=n+1$, $a\in R_d$, $b\in R_e$, and consider an embedding $\iota\colon\rA_4\hookrightarrow\rD_l$.
-For the chosen simple roots $\alpha_k$ of $\rA_4$ denote $\beta_k=\iota(\alpha_k)$.
-Then holds
-\[ [x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)], \]
-where $N=N_{\beta_1,\beta_2}N_{\beta_2,\beta_3}$.
-\end{lemma}
-\begin{proof}
-Observe that $d$, $e\geq1$.
-Take $x=x_{\beta_1}(a)$, $y=x_{\beta_2}(N_{\beta_3,\beta_2}bt\inv)$, $z=x_{\beta_3}(t)$.
-Since $x$ and $z$ lie in the subsystem of type $\rA_4$, we get by R3.1$\!\,_n$ that they commute.
-Then Hall--Witt identity gives us
-\[ \,^y[x,\,[y\inv,\,z]]=\,^x[[x\inv,\,y],\,z], \]
-where $[x,\,[y\inv,z]]=[x_{\beta_1}(a),\,x_{\beta_2+\beta_3}(b)]$ and $[[x\inv,y],\,z]=[x_{\beta_1+\beta_2}(Nabt\inv),\,x_{\beta_3}(t)]$ by R2$\!\,_n$.
-Here $x$ commutes with $x_{\beta_1+\beta_2}(Nabt\inv)$ and $x_{\beta_3}(t)$, and $y$ commutes with $x_{\beta_2+\beta_3}(b)$ by R3.1$\!\,_n$.
-Finally, $[x_{\beta_1}(-a),\,y]=x_{\beta_1+\beta_2}(Nabt\inv)$ also commutes with $x_{\beta_2+\beta_3}(b)$, what finishes the proof.
-\end{proof}
-
-The above lemma allows us for $a\in R_{n+1}$ and $\alpha\in\rD_l$ chose an arbitrary decomposition $\alpha=\beta+\gamma$ and define $s_\alpha(a)=[x_\beta(N_{\beta,\gamma}\,at\inv),\,x_\gamma(t)]$.
-Indeed, take another decomposition $\alpha=\beta'+\gamma'$, we may assume that subsystem $\Psi$ generated by $\beta$, $\beta'$, $\gamma$, $\gamma'$ has type $\rA_3$ If it is contained in the subsystem of type $\rA_4$, we are done by Lemma~\ref{welldef}.
-If not, we may assume $\Psi=\langle\alpha_{l-2},\alpha_{l-1},\alpha_l\rangle$ and since $l\geq5$ take two subsystems of type $\rA_4$, say, $\Psi_1$ and $\Psi_2$, which overlap by $\rA_3$, and $\beta$, $\gamma\in\Psi_1$, $\beta'$, $\gamma'\in\Psi_2$.
-Therefore, there exist $\beta''$, $\gamma''\in\Psi_1\cap\Psi_2$ with $\alpha=\beta''+\gamma''$ and we can again apply Lemma~\ref{welldef} to get the claim.
-
-Moreover, with the assumption of Lemma~\ref{welldef} on $a$ and $b$ we have
-\[ [x_{\beta}(a),\,x_{\gamma}(b)]=s_{\alpha}(N_{\beta,\gamma}\,ab). \]
-
-The following observation is obvious.
-\begin{lemma} \label{commute}
-Consider an embedding $\iota\colon\rA_4\hookrightarrow\rD_l$ and denote $\beta_k=\iota(\alpha_k)$ for simple roots $\alpha_k$ of $\rA_4$.
-Then for any $a\in R_d$, $b\in R_e$, $c\in R_f$ with $d$, $e$, $f\leq n$ holds
-\[ [[x_{\beta_1}(a),\,x_{\beta_2}(b)],\,x_{\beta_4}(c)]=1. \]
-\end{lemma}
-
-Consider now any two roots $\alpha$, $\beta\in\rD_l$ such that $\alpha+\beta\not\in\rC_l\cup0$.
-Since $l\geq5$, there exists a subsystem $\Psi$ of type $\rA_4$, containing $\alpha$ and $\beta$.
-Then we can take any $a\in R_{n+1}$ and $b\in R_d$ for $d\leq n$ and apply Lemma~\ref{commute} for $\Psi$ to get
-\begin{equation} \label{sx} [s_\alpha(a),\,x_\beta(b)]=1. \end{equation}
-Next, using this fact we can apply again Lemma~\ref{commute} for $\Psi$ and get
-\[ [s_\alpha(a),\,s_\beta(c)]=1 \]
-for any $c\in R_{n+1}$. Therefore, R3.1$\!\,_{n+1}$ holds for $s_\alpha$'s.
-
-Now one can take $a\in R_d$ for $d\leq0$ and $b\in R_{n+1}$, and repeat the proof of Lemma~\ref{welldef} using~(\ref{sx}) to get
-\[ [x_\beta(a),\,s_\gamma(b)]=\begin{cases}s_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d=0,\\x_{\beta+\gamma}(N_{\beta\gamma}\,ab),&d<0.\end{cases} \]
-This finishes the proof of R2$\!\,_{n+1}$.
-
-The proof of R1$\!\,_{n+1}$ is left to the reader. The next lemma is devoted to R3.2$\!\,_{n+1}$.
-
-\begin{lemma} For $a\in R_d$, $b\in R_e$, $d$, $e\leq n$, $d+e=n+1$ holds \[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1. \] \end{lemma}
-\begin{proof} Take $x=x_{\alpha_{l}-\alpha_{l-2}}(N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}bt\inv)$, $y=x_{\alpha_{l-1}-\alpha_{l-2}}(N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}at\inv)$, and $z=x_{\alpha_{l-2}}(t)$.
-Then
-\[ [x_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=[[y\inv,\,z],\,[x,\,z]]=\,^{y\inv z}[y,\,[z\inv,\,x]]\cdot[y\inv,\,[x,\,z]]. \]
-Next, by R3.2$\!\,_n$ we know that $x$ and $y$ commute, and therefore 
-\[ \,^{y\inv z}[y,\,[z\inv,\,x]]=[[y\inv,\,z],\,x]=x_{\alpha_{l-1}+\alpha_{l}-\alpha_{l-2}}(Nabt\inv) \]
-for $N=N_{\alpha_{l-1},\alpha_{l}-\alpha_{l-2}}N_{\alpha_{l}-\alpha_{l-2},\alpha_{l-2}}$. Finally,
-\[ [y\inv,\,[x,\,z]]=x_{\alpha_{l-1}-\alpha_{l-2}+\alpha_l}(N'abt\inv) \]
-for $N'=-N_{\alpha_{l-2},\alpha_{l-1}-\alpha_{l-2}}N_{{\alpha_{l-1}-\alpha_{l-2}},\alpha_l}$.
-Since $N_{\alpha,\beta}$ are the structure constants of the Lie algebra, it follows $N=-N'$ from the Jacobi identity.
-\end{proof}
-
-Now the same argument as in Lemma~\ref{welldef} allows to prove that $[s_{\alpha_{l-1}}(a),\,x_{\alpha_l}(b)]=1$ for $b\in R_e$, $e\leq0$, what finishes the proof of R3.2$\!\,_{n+1}$.
-\end{comment}
 \subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}

### 2019-07-01 dl-paper.tex
Minor fixes

@@
 & [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
- x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
+ x_{i\alpha + j\beta}\left(N_{\alpha,\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
 \end{align}
@@
 The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$.
-There is a degree of freedom in the choice of these constants, for example, in the literature there are several methods of choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
+There is a degree of freedom in the choice of signs of the structure constants.
+Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
 
-In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is simply-laced, i.\,e.
-does not contain double bonds, in which case Steinberg relations further simplify to the following relations:
+In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is {\it simply-laced}, i.\,e.
+does not contain double bonds.
+In this case the defining relations of $\St(\Phi, R)$ have the following simpler form:
 \begin{align}
@@
 \end{align}
-In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta, 1, 1} = N_{\alpha, \beta} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
+In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta} = N_{\alpha, \beta, 1, 1} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
 Although there is still some degree of freedom in their choice, these constants always must satisfy the relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
@@
  For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from
- the presentation of $\St^{\leq n}(\Phi, B)$ all relations of type $\text{R3}_{d,e}^\bot$ for which $\max(0,d) + \max(0,e) > 1$.
+ the presentation of $\St^{\leq n}(\Phi, B)$ all relations of type $\text{R3}_{d,e}^\bot$ whenever $\max(0,d) + \max(0,e) > 1$.
 \end{lemma}
@@
 The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree
- $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot_{d',e'}$ of strictly smaller degree.
-Let $R=[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ be such a relation for some $\alpha\perp\gamma$.
+ $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree.
+Let $R=[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ be a relation of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$.
 We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
@@
 \begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
-In particular, the natural map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
+In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
 \end{lemma}
 \begin{proof}
- The special case $\Phi=\rA_{\geq 4}$ of the assertion is due to Tulenbayev, see~\cite[Lemma~3.3]{Tu83}. 
- Therefore it can be used to deduce our assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
+ The special case $\Phi=\rA_{\geq 4}$ of the assertion has been proved by Tulenbayev (see~\cite[Lemma~3.3]{Tu83}) 
+ and therefore can be used to deduce the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
 

### 2019-07-02 dl-paper.tex
Minor fix

@@
 
-For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$ modulo Steinberg relations of degree $\leq n$.
-The following lemma asserts that most of the relations of type $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ 
+For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ as the quotient of the free group generated by the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ modulo the normal subgroup $\mathcal{R}_{\leq n}^\Phi$ generated by the set of Steinberg relations of degree $\leq n$.
+
+The following lemma asserts that most of the relations of type $\text{R3}^\bot_{d,e}$ of positive degree in this presentation of $\St^{\leq n}(\Phi, B)$ 
  are superfluous and can be omitted.
@@
 
-\begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
+\begin{prop} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
 In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
-\end{lemma}
+\end{prop}
 \begin{proof}

### 2019-07-03 dl-paper.tex
Rewritten Lemma 3.3

@@
 
-For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ as the quotient of the free group generated by the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ modulo the normal subgroup $\mathcal{R}_{\leq n}^\Phi$ generated by the set of Steinberg relations of degree $\leq n$.
+For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
 
@@
 \begin{proof}
- The special case $\Phi=\rA_{\geq 4}$ of the assertion has been proved by Tulenbayev (see~\cite[Lemma~3.3]{Tu83}) 
- and therefore can be used to deduce the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
+ We need to construct a map $j_n$ which would be the inverse of $i_n$. 
+ We start with a word map $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
+ \[ \widetilde{j}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
+      [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
+ where $\beta$ is an arbitrary root of $\Phi$ forming a sharp angle with $\alpha$.
+ Standard argument (cf.~\cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}_n$ does not depend on the choice of $\beta$.
 
- %Denote by $A_4(\Phi)$ the set consisting of all root subsystems of $\Phi$ of type $\rA_4$ and by $G_n$ the free product of groups $\coprod\limits_{\Psi \in A_4(\Phi)} \St^{\leq n}(\Psi, B)$ amalgamated over relations $x^{\Psi_1}_\alpha(a) = x^{\Psi_2}_\alpha(a)$ for all $a \in B_d$, $d \leq n$, $\alpha \in \Psi_1\cap\Psi_2$, $\Psi_1, \Psi_2 \in A_4(\Phi)$.
+ Set $\mathcal{R}^\Phi_{n+1} = \mathcal{R}^\Phi_{\leq n+1} \setminus \mathcal{R}^\Phi_{\leq n}$.
+ We need to verify that the image of every relator $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
+In the special case $\Phi=\rA_{\geq 4}$ this assertion has already been demonstrated by Tulenbayev in~\cite[Lemma~3.3]{Tu83}.
+We will deduce the assertion in the remaining cases $\Phi=\rD_\ell,\rE_\ell$ from this Tulebayev's result.
 
- Let us show that the obvious map $i_n \colon G_n \to G_{n+1}$ has an inverse $j_n$.
-Notice first that the maps $j_\Psi$ constructed by Tulenbaev agree on the generators of $G_{n+1}$ and hence, by the universal property of colimits, give rise to the well-defined map $j\colon G_{n+1}\to G_n$, which is easily seen to be  inverse to $i$.
+ Fix a relator $R \in \mathcal{R}^\Phi_{n+1}$.
+By~\cref{superfluous-relations} we may assume that $R$ is not of type $\text{R3}^\bot$, hence the roots $\alpha, \beta$ appearing in $R$ are contained in a root subsystem of $\Phi$ of type $\rA_2$.
+Our assumptions on $\Phi$ guarantee that there exists some root subsystem $\Psi$ of type $\rA_4$ containing $\alpha$ and $\beta$.
+Consider the following commutative diagram in which the vertical arrows are induced by the embedding $\Psi\subseteq\Phi$.
   \begin{equation} \nonumber \xymatrix{
- \St^{\leq n+1}(\Psi, B) \ar[r]^{j_\Psi} \ar[d] & \St^{\leq n}(\Psi, B) \ar[d] \\
- G_{n+1} \ar[r]^{j_n} & G_{n} }
+ F(\mathcal{X}_{\leq n+1}^\Psi) \ar[r]^{j_n^\Psi} \ar[d] & \St^{\leq n}(\Psi, B) \ar[d] \\
+ F(\mathcal{X}_{\leq n+1}^\Phi) \ar[r]^{j_n^\Phi} & \St^{\leq n}(\Phi, B) }
  \end{equation}
-Notice that in the case $\Phi = \rE_\ell$ the natural homomorphisms $G_k \to \St^{\leq k}(\rE_\ell, B)$ are isomorphisms for $k=n,n+1$ (cf.\cite[Corollary 10]{S15}), therefore the proof is already complete in this case.
-
-We are left to consider the case $\Phi = \rD_\ell$.
-Notice that any pair of nonperpendicular roots  $\alpha, \beta$ is contained in some subsystem $\Psi \subseteq \Phi$ of type $\rA_4$, hence the only defining relations of $\St^{\leq n+1}(\Phi, B)$ which do not occur already in $G_{n+1},$ are $\text{R3}^\bot_{d, n+1}$ for $d \leq n+1$ (more precisely, the relations for which $\alpha$ and $\gamma$ are orthogonal and lie in a root subsystem of type $\rD_3$, cf.~\cite[Remark~2.1]{S15}).
+The relation $R$ lies in the image of the left arrow, therefore it comes from some relation $R' \in \mathcal{R}^\Psi_{n+1}$.
+The image of $R'$ in $\St^{\leq n}(\Psi, B)$ under $j_n^\Psi$ is trivial by Tulenbayev's result.
+But this implies that the image of $R$ under $\widetilde{j}_n^\Phi$ is also trivial and hence that $\widetilde{j}_n^\Phi$ gives rise to the desired map $j_n$.
 \end{proof}

### 2019-07-03 dl-paper.tex
Added remark to Lemma 3.3

@@
 The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$.
-There is a degree of freedom in the choice of signs of the structure constants.
 Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
@@
  Set $\mathcal{R}^\Phi_{n+1} = \mathcal{R}^\Phi_{\leq n+1} \setminus \mathcal{R}^\Phi_{\leq n}$.
- We need to verify that the image of every relator $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
-In the special case $\Phi=\rA_{\geq 4}$ this assertion has already been demonstrated by Tulenbayev in~\cite[Lemma~3.3]{Tu83}.
-We will deduce the assertion in the remaining cases $\Phi=\rD_\ell,\rE_\ell$ from this Tulebayev's result.
+It suffices to verify that the image of every relator $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
+In the special case $\Phi=\rA_{\geq 4}$ this has already been demonstrated by Tulenbayev in~\cite[Lemma~3.3]{Tu83}, so in this case the proof of the proposition is complete.
+We will deduce the assertion in the remaining cases $\Phi=\rD_\ell,\rE_\ell$ from the special case $\Phi=\rA_4$ of Tulenbayev's result.
 
- Fix a relator $R \in \mathcal{R}^\Phi_{n+1}$.
+ Let $R$ be a relation from $\mathcal{R}^\Phi_{n+1}$.
 By~\cref{superfluous-relations} we may assume that $R$ is not of type $\text{R3}^\bot$, hence the roots $\alpha, \beta$ appearing in $R$ are contained in a root subsystem of $\Phi$ of type $\rA_2$.
@@
 \end{proof}
+
+\begin{rem}
+ We needed to exclude relations of type $\text{R3}^\bot$ from the presentation of $\St^{\leq n}(\Phi, B)$ in the proof of the above proposition because already in the case $\Phi=\rD_\ell$ the pair of simple roots $\alpha_{\ell-1}$, $\alpha_{\ell}$ cannot be embedded into a root subsystem of type $\rA_4$.
+
+ In the special case $M=A$, $B = A[t, t\inv]$ the assertion of the above proposition also holds in the cases $\Phi=\rA_2, \rA_3, \rD_4$.
+This is an easy consequence of the presentation of D.~Allcock applied to the affine Steinberg group $\St(\Phi, A[t, t\inv]) \cong \St(\widetilde{\Phi}^{(1)}, A)$ (Allcock's presentation implies that $\St(\Phi, A[t, t\inv])$ can be presented using only generators and relations of degree $\leq 1$ with respect to both $t$ and $t^{-1}$, see~\cite[Corollary~1.3]{A13}).
+
+ In the cases $\Phi = \rA_3, \rD_4$, $M \neq A$ it is still possible to prove the injectivity of $i_n$ starting from $n\geq 2$ using a variation of the argument of Rehmann--Soul{\'e} (cf.
+the lower bound for $m$ in~\cite[3.2.1]{RS76}).
+However, apparently, it is not possible to establish the injectivity of $i_1$ in the specified cases using arguments similar to~\cite{RS76}.
+\end{rem}
 

### 2019-07-05 dl-paper.tex
Minor fixes

@@
 &\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$} \\
-&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha \perp \beta \in \Phi.\ \tag{R$3^\bot_{d,e}$}
+&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha \perp \beta.\ \tag{R$3^\bot_{d,e}$}
 \end{align}
@@
  $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree.
-Let $R=[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ be a relation of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$.
+Let us fix some relation $[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$. Denote this relation by $R$.
+
 We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
@@
 \begin{enumerate}
-\item In the case $0 < d \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
+\item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
 \begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 

### 2019-07-08 dl-paper.tex
Expanded Lemma 2

@@
 More concretely, it asserts that $\K_2(\Phi, k) \cong \K_2^\mathrm{MW}(k)$ provided $\Phi$ is symplectic and  $\K_2(\Phi, k) \cong \K_2^\mathrm{M}(k)$ otherwise.
-In the following lemma we compute the group $\K_2(\Phi, R)$ in yet another case $R=k[X, X\inv]$.
+In the following lemma we
+recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
 \begin{lemma}\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
@@
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
-                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
-Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto theorem.
-The assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.
+\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{h} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
+                                                                                      &                                 & \K_2^\mathrm{M}(k(X)),} \]
+in which $h = \{ -, X \}_{\alpha}$ and the vertical map is an isomorphism by Matsumoto theorem.
+Notice that the diagonal map is split by the obvious residue homomorphism and therefore is injective. This, in turn, implies that $h$ is also injective.
+The assertion of the lemma now follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi$ holds $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
 
-In the symplectic case the assertion follows from~\cite[Theorem~B]{MR91}, provided one verifies that Morita--Rehmann's group $P(F)$ is isomorphic to $\K_1^\mathrm{MW}(F)$,
- which is an easy exercise. Alternatively, this isomorphism can be obtained as a corollary of and~\cite[Lemma~4.1.1]{AF17} and \cref{bass-ft} below. \end{proof}
+Consider now the case when $\Phi$ is symplectic. In this case the assertion of the lemma is just a reformulation of~\cite[Theorem~B]{MR91},
+which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv] \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
+$P(k)$ is the set $k^* \times I_2(k)$ with the group structure given by
+\[ (u, y) \cdot (v, z) = (uv, y + z - \langle\langle u, v\rangle\rangle).\]
+Here $I^2(k)$ stands for the second power of the fundamental ideal $I(k)$ in the Witt ring $W(k)$ of $k$.
+Recall that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
+\[ \xymatrix{ \K_1^\mathrm{MW}(k) \ar[r] \ar[d] & I(k) \ar[d] \\ \K_1(k) \ar[r] & I(k)/I^2(k), } \]
+in other words, it consists of pairs $[u, x]$ such that $x - \langle \langle u \rangle \rangle \in I^2(k)$.
+It is not hard to verify that tha map $[u, x] \mapsto (u, x - \langle\langle u \rangle\rangle)$ defines an isomorphism of $P(k)$ and $\K_1^\mathrm{MW}(k)$.
+
+\begin{comment}
+Under additonal assumption $\mathrm{char}(k)\neq 2$ the assertion of the lemma in the symplectic case can be obtained as a chain of isomorphisms
+\[ \K_2(\rC_\ell, k[X, X\inv]) \cong \GW_2^2(\Phi, k[X, X\inv]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k). \]
+Here the first 
+corollary of~\cite[Lemma~4.1.1]{AF17} and \cref{bass-ft} below. 
+\end{comment}
+\end{proof}
 

### 2019-07-08 dl-paper.tex
Fix signs

@@
 in other words, it consists of pairs $[u, x]$ such that $x - \langle \langle u \rangle \rangle \in I^2(k)$.
-It is not hard to verify that tha map $[u, x] \mapsto (u, x - \langle\langle u \rangle\rangle)$ defines an isomorphism of $P(k)$ and $\K_1^\mathrm{MW}(k)$.
-
-\begin{comment}
-Under additonal assumption $\mathrm{char}(k)\neq 2$ the assertion of the lemma in the symplectic case can be obtained as a chain of isomorphisms
-\[ \K_2(\rC_\ell, k[X, X\inv]) \cong \GW_2^2(\Phi, k[X, X\inv]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k). \]
-Here the first 
-corollary of~\cite[Lemma~4.1.1]{AF17} and \cref{bass-ft} below. 
-\end{comment}
-\end{proof}
+It is easy to verify that the map $[u, x] \mapsto (u, \langle\langle u \rangle\rangle - x)$ defines an isomorphism of $\K_1^\mathrm{MW}(k)$ and $P(k)$. \end{proof}
 

### 2019-07-22 dl-paper.tex
Expanding preliminaries

@@
 
-\subsection{Unstable Quillen K-groups} \label{sec:quillen}
-Throughout this section $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
+\subsection{Relative Steinberg groups} \label{sec:quillen}
+In this subsection we recall the definitions and basic facts pertaining to relative Steinberg groups as defined by J.-L.~Loday in~\cite{Lo78},
+ where a theory of relative central extensions is developed and then applied to the usual (stable) Steinberg group $\St(R)$ from algebraic K-theory (see e.\,g.~\cite[Ch. III \S~5]{Kbook}).
+The main goal of this subsection is to show that Loday's result can be applied to the unstable Steinberg groups, and that
+ the resulting relative groups enjoy the same good properties as their stable counterparts.
+
+%Some of the results of this subsection have been already mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
+%Nevertheless, we chose to reproduce them with greater amount of detail for the reason that~\cref{lem:prop41} depends on the unstable exact sequence of.
+
+First of all, let us recall the definition of the category of (commutative) pairs $\catname{Pairs}$.
+The objects of $\catname{Pairs}$ are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ its ideal.
+By definition, a morphism $f \colon (R, I) \to (R', I')$ in the category of pairs corresponds to a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
+Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ the morphism category $\catname{CRings}^\rightarrow$.
+
+There is an obvious fully faithful embedding $\catname{CRings} \to \catname{Pairs}$ sending $R$ to $(R, R)$.
+For a given functor $S \colon \catname{CRings} \to \catname{Groups}$ a {\it relativization} of $S$ is any functor $\widetilde{S} \colon \catname{Pairs} \to \catname{Groups}$
+ extending $S$ in the obvious sense. Relativization of a functor is not unique.
+
+Recall that {\it the double ring} $D_{R, I}$ of a pair $(R, I)$ is, by definition, the pullback ring $R \times_{R/I} R$.
+In other words, it is the ring consisting of pairs of elements of $R$ congruent modulo $I$.
+Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$.
+
+Let us describe the procedure for relativization as specified by Loday.
+Let $S \colon \catname{CRings} \to \catname{Groups}$ be a functor.
+Set $G_i = \Ker(S(p_i))$ and define Loday's relativization $S(R, I)$ as $ G_0 / [G_0, G_1]$. The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$. 
+For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. In fact, there is a natural exact sequence:
+\begin{equation}
+ \xymatrix{ 1 \ar[r] & C(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
+\end{equation}
+\begin{example}
+ If one applies Loday's relativization to the functor $S(R) = \St(R)$ one recovers the usual relative Steinberg group $\St(R, I)$
+  as defined in~\cite{Kbook}[Ch. III, Definition~5.7]. Notice that $\St(R, I)$ is not a subgroup of $\St(R)$ but rather its central extension.
+\end{example}
+
+For the rest of this subsection $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
 \begin{enumerate} [label=(A\arabic*)]
- \item \label{req:left-exact} $G$ is left exact;
- \item \label{req:subfunc} $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$;
- \item \label{req:uce} There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi \colon S(R) \to P(R)$ is a universal central extension for all $R$;
- \item \label{req:coeq} For every pair $(R, I)$ the functor $S$ has the property that \[S(R \times_{R/I} R) \cong S(R) \times_{S(R/I)} S(R).\]
+ \item \label{req:left-exact} $G$ is left exact.
+ \item \label{req:subfunc} $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
+ \item \label{req:uce} There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$.
+ %This means that $\varphi_R$ is a certain surjective and that its kernel is contained in the center of $S(R)$.
+ \item \label{req:coeq} For every ring $R$ and an ideal $I \trianglelefteq R$ the functor $S$ has the property that \[S(R \times_{R/I} R) \cong S(R) \times_{S(R/I)} S(R).\]
 \end{enumerate}
+\begin{example}
+ The obvious triple of functors satisfying the above assumptions is as follows.
+ Take the infinite general linear group functor $\mathrm{GL}(-)$ as $G$, its infinite elementary subfunctor $E(-)$ as $P$
+  and the infinite Steinberg group functor $\St(-)$ as $S$. %TODO: Why these 4 propeties hold? What is a relative central extension.
+\end{example}
 
@@
 $X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define for $i \geq 1$ the corresponding K-group functors $\K_{i}(G, P, R)$ as the homotopy groups $\pi_i(X_{G, P}(R))$.
-
-Let us also briefly recall Loday's procedure for relativization of $S$, that is,
- a way of extending $S$ from the category of rings to the category of pairs.
-Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
-  and set $d_i = Sp_i$, $s = S\Delta$.
- Obviously, $d_0s = d_1 s = id_{S(R)}$. Set $G_i = \Ker(d_i)$, and define $S(R, I)$ as $ G_0 / [G_0, G_1]$, denote by $\mu$ the natural map $S(R, I) \to S(R)$ induced by $d_1$.
 
@@
  \item The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of the map $S(R) \to S(R/I)$.
-       Denote the kernel of $\mu$ by $C(R, I)$.
-       Then $C(R, I)$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+       The kernel $C(R, I)$ of $\mu$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
  \item There is a natural exact sequence:

### 2019-07-23 dl-paper.tex
Added definition of crossed modules

@@
 Set $G_i = \Ker(S(p_i))$ and define Loday's relativization $S(R, I)$ as $ G_0 / [G_0, G_1]$. The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$. 
-For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. In fact, there is a natural exact sequence:
-\begin{equation}
+For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. We also introduce the notation for the kernel of $\mu$.
+\begin{equation} \label{LodayRelativization}
  \xymatrix{ 1 \ar[r] & C(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
@@
 \end{example}
+
+The exact sequence in~\eqref{LodayRelativization} often is an example of a {\it relative central extension}.
+Let us briefly recall the relevant terminology. 
+First of all, recall that a {\it central extension} of a group $G$ is a surjective map $\widetilde{G} \to G$, whose kernel is contained in the center of $\widetilde{G}$. 
+A central extension is said to be {\it universal} if it is an initial object of the category of central extensions of $G$.
+
+Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of a group $N$ acting on itself by left conjugation, an $N$-group $M$ and a map
+ $\mu \colon M\to N$ of $N$-groups satisfying {\it Peiffer identity} $\mu(m) \cdot m' = m m' m^{-1}$. It can be shown that the image of $\mu$ is always
+  a normal subgroup of $N$ and that the kernel of $\mu$ is always contained in the center of $M$.
+
+Now if $\nu \colon N \twoheadrightarrow Q$ is a surjective map of groups, a {\it relative central extension of $\nu$} is, by definition,
+a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is precisely $\nu$. Thus, we have the following diagram
+\begin{equation} \label{RelativeCentralExtension}
+ \xymatrix{ 1 \ar[r] & C \ar^{\lambda}[r] & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1}
+\end{equation}
 

### 2019-07-23 dl-paper.tex
Writing stuff

--- 2019-07-22 dl-paper.tex
@@
 
-Let us describe the procedure for relativization as specified by Loday.
 Let $S \colon \catname{CRings} \to \catname{Groups}$ be a functor.
-Set $G_i = \Ker(S(p_i))$ and define Loday's relativization $S(R, I)$ as $ G_0 / [G_0, G_1]$. The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$. 
-For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. In fact, there is a natural exact sequence:
-\begin{equation}
- \xymatrix{ 1 \ar[r] & C(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
+Set $G_i = \Ker(S(p_i))$ and define {\it Loday's relativization} $S(R, I)$ as $ G_0 / [G_0, G_1]$.
+The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$.
+We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$.
+\begin{equation} \label{LodayRelativization}
+ \xymatrix{ 1 \ar[r] & C_S(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
 \end{equation}
-\begin{example}
- If one applies Loday's relativization to the functor $S(R) = \St(R)$ one recovers the usual relative Steinberg group $\St(R, I)$
-  as defined in~\cite{Kbook}[Ch. III, Definition~5.7]. Notice that $\St(R, I)$ is not a subgroup of $\St(R)$ but rather its central extension.
-\end{example}
+
+\begin{df}
+By definition, the {\it relative Steinberg group} $\St(\Phi, R, I)$ is the result of application of Loday's relativization to the functor $\St(\Phi, -)$.
+Notice that $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ but rather its central extension by the abelian group $C_{\St(\Phi, -)}(R, I)$.
+For shortness we rename the latter group to $C(\Phi, R, I)$.
+\end{df}
+
+Our next goal is to obtain a more concrete description of the group $C(\Phi, R, I)$.
+We need to recall some additional notation and terminology.
+
+First of all, recall that a {\it central extension} of a group $G$ is a surjective map $\widetilde{G} \to G$, whose kernel is contained in the center of $\widetilde{G}$. 
+A morphism of central extensions is a group-theoretic map $\widetilde{G} \to \widetilde{G}'$ over $G$.
+A central extension is said to be {\it universal} if it is an initial object of the category of central extensions of $G$.
+
+Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of a group $N$ acting on itself by left conjugation, an $N$-group $M$ and a map
+ $\mu \colon M\to N$ of $N$-groups satisfying {\it Peiffer identity} $\mu(m) \cdot m' = m m' m^{-1}$. It can be shown that the image of $\mu$ is always
+  a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$. %TODO: There's a problem with the side of the action :(
+
+Now if $\nu \colon N \twoheadrightarrow Q$ is a surjective map of groups, a {\it relative central extension of $\nu$} is, by definition,
+a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is $\nu$.
+The mentioned groups and morphisms fit into the following diagram.
+\begin{equation} \label{RelativeCentralExtension}
+ \xymatrix{ 1 \ar[r] & L \ar[r]^{\ker(\mu)} & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1} \end{equation}
+
+A morphism $(M, \mu) \to (M', \mu')$ between two relative central extensions of $\nu$ is, by definition, an $N$-group homomorphism $f\colon M \to M'$ such that $\mu' f = \mu$.
+Denote by $Ext(Q, N, L)$ the set of isomorphism classes of relative central extensions of $\nu$ by an abelian group $L$.
+It turns out that there is a well-defined bijection $\xi \colon Ext(Q, N, L) \to \HH^3(Q, N; L)$ which is called {\it characteristic class} (see~\cite[Th{\'e}or{\`e}me~1]{Lo78}).
 
@@
  %This means that $\varphi_R$ is a certain surjective and that its kernel is contained in the center of $S(R)$.
- \item \label{req:coeq} For every ring $R$ and an ideal $I \trianglelefteq R$ the functor $S$ has the property that \[S(R \times_{R/I} R) \cong S(R) \times_{S(R/I)} S(R).\]
+ \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of the pair of maps $S(p_0), S(p_1) \colon S(D_{R, I}) \to S(R)$ is precisely the map $S(R) \to S(R/I)$.
 \end{enumerate}
@@
 
+\begin{lemma}
+ Suppose $(G, P, S)$ is a triple satisfying properties \text{A1}--\text{A4}.
+ The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of $\nu \colon S(R) \to S(R/I)$, i.\,e. the initial object of the category of relative central extensions.
+
+ There is a natural isomorphism between the kernel $C_S(R, I)$ of $\mu$ and the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+\end{lemma}
+\begin{proof}
+From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$ therefore $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
+From~\ref{req:uce} and~\cite[Ch.~III, Theorem~5.4]{Kbook} we conclude that $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$ for all rings $R$.
+
+Using~\cite[Proposition~6]{Lo78} we obtain that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$, which coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}.
+
+Now set $C = \HH_3(S(R/I), S(R), \ZZ)$, $L = C_S(R, I)$.
+Since 
+Recall from the proof of \cite[Th{\'e}or{\`e}me~2]{Lo78} that there is a map $\alpha \colon C \to L.$
+Under t
+
+of~. To see that this isomorphism is natural in $(R, I)$ notice that the map $ $
+\end{proof}
+
 Thanks to the functoriality of Quillen's plus-construction (see e.\,g.~\cite[Proposition~5.2.4]{Ro95}) one can define a functor 
@@
   \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
- \item The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of the map $S(R) \to S(R/I)$.
-       The kernel $C(R, I)$ of $\mu$ is naturally isomorphic to the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+ \item 
  \item There is a natural exact sequence:
@@
 %provided one verifies that all the intermediate isomorphisms are natural in $R$.
-
- Let us verify the second claim. From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$
-  therefore $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
- From~\ref{req:uce} we also obtain that $\HH_1(S(D_{R,I})) = \HH_2(S(D_{R,I})) = 0$ .
- The last two assertions allow us to invoke~\cite[Proposition~6]{Lo78} and conclude that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$
-  in the sense of~\cite[\S~3]{Lo78}. 
- Notice that this coequalizer coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}. 
- Finally, the kernel of $\mu$ is isomorphic to $\HH_3(S(R), S(R/I), \ZZ)$ by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
 

### 2019-07-23 dl-paper.tex
Minor fix

@@
 First of all, let us recall the definition of the category of (commutative) pairs $\catname{Pairs}$.
-The objects of $\catname{Pairs}$ are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ its ideal.
+The objects of $\catname{Pairs}$ are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ is an ideal of $R$.
 By definition, a morphism $f \colon (R, I) \to (R', I')$ in the category of pairs corresponds to a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
@@
 
-Now if $\nu \colon N \twoheadrightarrow Q$ is a surjective map of groups, a {\it relative central extension of $\nu$} is, by definition,
+Let $\nu \colon N \twoheadrightarrow Q$ be a surjective group-theoretic map.
+A {\it relative central extension of $\nu$} is, by definition,
 a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is $\nu$.
@@
 
-A morphism $(M, \mu) \to (M', \mu')$ between two relative central extensions of $\nu$ is, by definition, an $N$-group homomorphism $f\colon M \to M'$ such that $\mu' f = \mu$.
-Denote by $Ext(Q, N, L)$ the set of isomorphism classes of relative central extensions of $\nu$ by an abelian group $L$.
-It turns out that there is a well-defined bijection $\xi \colon Ext(Q, N, L) \to \HH^3(Q, N; L)$ which is called {\it characteristic class} (see~\cite[Th{\'e}or{\`e}me~1]{Lo78}).
-
-For the rest of this subsection $G, P, S$ denote three group-valued functors on the category of commutative rings satisfying the following assumptions:
+A morphism $(M, \mu) \to (M', \mu')$ of two relative central extensions of $\nu$ is, by definition, an $N$-group homomorphism $f\colon M \to M'$ such that $\mu' f = \mu$. 
+It turns out that the set  $Ext(Q, N; L)$  of isomoprhism classes of relative central extensions of $\nu$ by an abelian group $L$ can be classified by means of a certain cohomological invariant called {\it characteristic class}.
+More precisely, \cite[Th{\'e}or{\`e}me~1]{Lo78} asserts that there is a well-defined bijection $\xi \colon Ext(Q, N; L) \to \HH^3(Q, N; L)$.
+
+For the rest of this subsection $S \xrightarrow{\varphi} P \subseteq G$ is a triple of group-valued functors on the category of commutative rings satisfying the following assumptions:
 \begin{enumerate} [label=(A\arabic*)]
- \item \label{req:left-exact} $G$ is left exact.
- \item \label{req:subfunc} $P$ is a subfunctor of $G$ such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
- \item \label{req:uce} There is a natural transformation $\varphi \colon S \to P$ such that $ \varphi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$.
+ \item \label{req:left-exact} $G(D_{R, I}) \cong G(R) \times_{G(R/I)} G(R)$.
+ \item \label{req:subfunc} For every $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
+ \item \label{req:uce} For every $R$ the map $ \varphi_R \colon S(R) \to P(R)$ is a universal central extension.
  %This means that $\varphi_R$ is a certain surjective and that its kernel is contained in the center of $S(R)$.
- \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of the pair of maps $S(p_0), S(p_1) \colon S(D_{R, I}) \to S(R)$ is precisely the map $S(R) \to S(R/I)$.
+ \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of $S(p_0), S(p_1)$ is precisely $S(R) \to S(R/I)$.
 \end{enumerate}
+\begin{comment}
 \begin{example}
@@
 \end{example}
-
+\end{comment}
 \begin{lemma}
- Suppose $(G, P, S)$ is a triple satisfying properties \text{A1}--\text{A4}.
- The map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of $\nu \colon S(R) \to S(R/I)$, i.\,e. the initial object of the category of relative central extensions.
-
- There is a natural isomorphism between the kernel $C_S(R, I)$ of $\mu$ and the third relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+ Suppose  for every pair $(R, I)$ the map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of $\nu \colon S(R) \to S(R/I)$, i.\,e.
+the initial object of the category of relative central extensions of $\nu$.
+ Moreover, $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
 \end{lemma}

### 2019-07-24 dl-paper.tex
Reorganized introduction

@@
 
-\subsection{Relative Steinberg groups} \label{sec:quillen}
-In this subsection we recall the definitions and basic facts pertaining to relative Steinberg groups as defined by J.-L.~Loday in~\cite{Lo78},
- where a theory of relative central extensions is developed and then applied to the usual (stable) Steinberg group $\St(R)$ from algebraic K-theory (see e.\,g.~\cite[Ch. III \S~5]{Kbook}).
-The main goal of this subsection is to show that Loday's result can be applied to the unstable Steinberg groups, and that
- the resulting relative groups enjoy the same good properties as their stable counterparts.
-
-%Some of the results of this subsection have been already mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
-%Nevertheless, we chose to reproduce them with greater amount of detail for the reason that~\cref{lem:prop41} depends on the unstable exact sequence of.
-
-First of all, let us recall the definition of the category of (commutative) pairs $\catname{Pairs}$.
-The objects of $\catname{Pairs}$ are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ is an ideal of $R$.
-By definition, a morphism $f \colon (R, I) \to (R', I')$ in the category of pairs corresponds to a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
+\subsection{Relative Steinberg groups and unstable K-groups} \label{sec:quillen}
+In this subsection we recall the definitions and basic facts pertaining to relative Steinberg groups as defined by J.-L.~Loday in~\cite{Lo78}, where a theory of relative central extensions was developed and then applied to the stable Steinberg group $\St(R)$ from algebraic K-theory.
+The main goal of this subsection is to show that Loday's results can be applied to unstable Steinberg groups, and that the resulting relative groups enjoy many good properties of their stable counterparts.
+Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
+
+Recall that the category of (commutative) pairs $\catname{Pairs}$ is defined as follows.
+Its objects are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ is an ideal of $R$.
+A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
 Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ the morphism category $\catname{CRings}^\rightarrow$.
@@
 There is an obvious fully faithful embedding $\catname{CRings} \to \catname{Pairs}$ sending $R$ to $(R, R)$.
-For a given functor $S \colon \catname{CRings} \to \catname{Groups}$ a {\it relativization} of $S$ is any functor $\widetilde{S} \colon \catname{Pairs} \to \catname{Groups}$
- extending $S$ in the obvious sense. Relativization of a functor is not unique.
+For a given functor $S \colon \catname{CRings} \to \catname{Groups}$ a {\it relativization} of $S$ is any functor $\widetilde{S} \colon \catname{Pairs} \to \catname{Groups}$ extending $S$ in the obvious sense.
+Relativization of a functor is not unique.
 
@@
 Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$.
+It is clear that $p_0 \Delta = p_1 \Delta = id_{R}$.
 
@@
 The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$.
-We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$.
-\begin{equation} \label{LodayRelativization}
- \xymatrix{ 1 \ar[r] & C_S(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
-\end{equation}
-
-\begin{df}
-By definition, the {\it relative Steinberg group} $\St(\Phi, R, I)$ is the result of application of Loday's relativization to the functor $\St(\Phi, -)$.
+We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$: \begin{equation} \label{LodayRelativization} \xymatrix{ 1 \ar[r] & C_S(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1.} \end{equation}
+
+\begin{df} By definition, the {\it relative Steinberg group} $\St(\Phi, R, I)$ is the result of application of Loday's relativization to the functor $\St(\Phi, -)$.
 Notice that $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ but rather its central extension by the abelian group $C_{\St(\Phi, -)}(R, I)$.
@@
 
-Our next goal is to obtain a more concrete description of the group $C(\Phi, R, I)$.
-We need to recall some additional notation and terminology.
+Our next goal is to obtain a homological interpretation of the group $C(\Phi, R, I)$.
+For doing this we need to recall some additional notation and terminology.
 
@@
 A {\it relative central extension of $\nu$} is, by definition,
-a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is $\nu$.
-The mentioned groups and morphisms fit into the following diagram.
+a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is $\nu$:
 \begin{equation} \label{RelativeCentralExtension}
- \xymatrix{ 1 \ar[r] & L \ar[r]^{\ker(\mu)} & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1} \end{equation}
+ \xymatrix{ 1 \ar[r] & L \ar[r] & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1} \end{equation}
 
 A morphism $(M, \mu) \to (M', \mu')$ of two relative central extensions of $\nu$ is, by definition, an $N$-group homomorphism $f\colon M \to M'$ such that $\mu' f = \mu$. 
-It turns out that the set  $Ext(Q, N; L)$  of isomoprhism classes of relative central extensions of $\nu$ by an abelian group $L$ can be classified by means of a certain cohomological invariant called {\it characteristic class}.
+A relative central extension is said to be {\it universal} if it is an initial object of the category of relative central extensions of $\nu$.
+
+It turns out that the set  $Ext(Q, N; L)$  of isomorphism classes of relative central extensions of $\nu$ by an abelian group $L$ can be classified by means of a certain cohomological invariant called {\it characteristic class}.
 More precisely, \cite[Th{\'e}or{\`e}me~1]{Lo78} asserts that there is a well-defined bijection $\xi \colon Ext(Q, N; L) \to \HH^3(Q, N; L)$.
 
-For the rest of this subsection $S \xrightarrow{\varphi} P \subseteq G$ is a triple of group-valued functors on the category of commutative rings satisfying the following assumptions:
+For the rest of this subsection $S \xrightarrow{\pi} P \subseteq G$ is a triple of group-valued functors on the category of commutative rings satisfying the following assumptions:
 \begin{enumerate} [label=(A\arabic*)]
  \item \label{req:left-exact} $G(D_{R, I}) \cong G(R) \times_{G(R/I)} G(R)$.
- \item \label{req:subfunc} For every $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.
- \item \label{req:uce} For every $R$ the map $ \varphi_R \colon S(R) \to P(R)$ is a universal central extension.
- %This means that $\varphi_R$ is a certain surjective and that its kernel is contained in the center of $S(R)$.
+ \item \label{req:subfunc} $P(R)$ is a perfect normal subgroup of $G(R)$.
  \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of $S(p_0), S(p_1)$ is precisely $S(R) \to S(R/I)$.
+ \item \label{req:uce} The map $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$.
 \end{enumerate}
-\begin{comment}
-\begin{example}
- The obvious triple of functors satisfying the above assumptions is as follows.
- Take the infinite general linear group functor $\mathrm{GL}(-)$ as $G$, its infinite elementary subfunctor $E(-)$ as $P$
-  and the infinite Steinberg group functor $\St(-)$ as $S$. %TODO: Why these 4 propeties hold? What is a relative central extension.
-\end{example}
-\end{comment}
-\begin{lemma}
- Suppose  for every pair $(R, I)$ the map $\mu \colon S(R, I) \to S(R)$ is the universal relative central extension of $\nu \colon S(R) \to S(R/I)$, i.\,e.
-the initial object of the category of relative central extensions of $\nu$.
- Moreover, $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+
+\begin{lemma}\label{lem:relativeH3}
+ For every pair $(R, I)$ the map $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of $\nu \colon S(R) \to S(R/I)$.
+The group $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
 \end{lemma}
 \begin{proof}
-From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi \colon S(D_{R, I}) \to G(D_{R, I}))$ therefore $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
-From~\ref{req:uce} and~\cite[Ch.~III, Theorem~5.4]{Kbook} we conclude that $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$ for all rings $R$.
-
-Using~\cite[Proposition~6]{Lo78} we obtain that the extension $S(R, I) \to S(R)$ is a universal relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$, which coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}.
-
-Now set $C = \HH_3(S(R/I), S(R), \ZZ)$, $L = C_S(R, I)$.
-Since 
-Recall from the proof of \cite[Th{\'e}or{\`e}me~2]{Lo78} that there is a map $\alpha \colon C \to L.$
-Under t
-
-of~. To see that this isomorphism is natural in $(R, I)$ notice that the map $ $
-\end{proof}
-
-Thanks to the functoriality of Quillen's plus-construction (see e.\,g.~\cite[Proposition~5.2.4]{Ro95}) one can define a functor 
-%TODO: can also refer to Weibel's IV.1.5 provided Top is replaced with hTop which apparently does not change anything
-$X_{G, P}(R) = BG(R)^+_{P(R)} \colon \catname{CRings} \to \catname{Top}$ and then define for $i \geq 1$ the corresponding K-group functors $\K_{i}(G, P, R)$ as the homotopy groups $\pi_i(X_{G, P}(R))$.
-
-%TODO: Give the definition of $D_{R, I}$ and of the category of Pairs
-\begin{prop}\label{characterization}
-For $(G, P, R)$ as above the following statements are true.
-\begin{enumerate}
- \item There are natural isomorphisms
-  \[ \K_2(G, P, R) \cong \Ker(S(R) \to G(R)), \ \K_3(G, P, R) \cong \HH_3(S(R), \ZZ). \]
- \item 
- \item There is a natural exact sequence:
- \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C(R, I).} \]
- \end{enumerate}   
-\end{prop}
-\begin{proof}
- The first claim follows from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
-Exercises~1.8--1.9 ibid.).
-%provided one verifies that all the intermediate isomorphisms are natural in $R$.
-
- The third claim now follows from the starting portion of the homology long exact sequence of the map $S(R) \to S(R/I)$ and the first two assertions.
-\end{proof}
-
-The principal example of a triple $(G,P,S)$ satisfying the above conditions is as follows.
-For $n \geq 5$ take the orthogonal group functor $\mathrm{O}_{2n}(-)$ and its elementary subfunctor $\mathrm{EO}_{2n}(-)$ as functors $G_n$ and $P_n$, respectively.
-Now set $S_n = \St(\rD_n, -)$.
-From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce}.
- The other requirements can be verified in a straightforward manner. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
-
-In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
- we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
-Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
- it would not change $\K_3(G_n, P_n, -)$.
-
-Let us formulate the stability theorem for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
-\begin{theorem}[Panin] \label{lem:Panin-stability}
- Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these respective cases.
- Then the canonical map $KO_i(2n, R) \to KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
- and an isomorphism for $\ell \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
-
-Of course, the limit groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ are exactly hermitian K-groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
-There is a modern version of hermitian K-theory, namely the theory of higher Grothendieck--Witt groups of schemes.
-We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for an introduction to this theory.
-For our purposes it would be sufficient to restrict our attention to to the affine case and to think of $\GW_i^{[k]}(R)$ as a shorthand for
-\begin{equation}
- \GW_i^{[k]}(R) = \left\{\begin{array}{ll} KO_i(R), & k = 0, \\ U_i(R), & k = 1, \\ KSp_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
-\end{equation} %TODO: Reference?
-The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
-The notation for the upper index $[k]$ suggests that Grothendieck--Witt groups are $4$-periodic in $k$.
-
-In the sequel we will need the following result.
-\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups
- \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
-\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
-
-\subsection{Relative Steinberg groups}
-Let us briefly recall the definition and basic properties of relative Steinberg groups.
-We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
-By definition, the relative Steinberg group functor $\St(\Phi, R, I)$ is obtained from the functor $\St(\Phi, R)$
- via the relativization procedure described in~\cref{sec:quillen}.
-
-\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
-$A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
-Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
-by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
-Consider the following commutative square of canonical maps.
-\[ \xymatrix{
-    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
-Then there exists a diagonal arrow which makes the diagram commute.   
-\end{lemma} 
-\begin{proof}
- Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
-  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
- Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
-
- Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
-  (cf.~\cite[\S~4]{LS17} for more details).
-\end{proof}
-%TODO: Give reference on a similar result of Lavrenov?
+The action of $S(R)$ on $S(D_{R, I})$ given by ${}^g h = S(\Delta)(g) \cdot h \cdot S(\Delta)(g)^{-1}$ induces an action of $S(R)$ on $S(R, I)$.
+With respect to this action the map $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-map.
+From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
+$G_0 \cap G_1 \subseteq \Ker(\pi_{D_{R, I}})$ and therefore is a central subgroup of $S(D_{R,I})$ by~\ref{req:uce}.
+Thus, we have verified the assumptions of~\cite[Proposition~6]{Lo78} which asserts that the map $\mu$ is a universal relative central extension of the coequalizer $\nu = \mathrm{coeq}(d_0, d_1)$.
+Since $\nu$ coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}, we have completed the proof of the first assertion of the lemma.
+
+Set $N = S(R)$, $Q = S(R/I)$, $C = \HH_3(Q, N; \ZZ)$.
+Recall from the proof of~\cite[Th{\'e}or{\`e}me~2]{Lo78} that to every relative central extension $(M, \mu)$ of $\nu$ with kernel $L$ one can associate a map of abelian groups $C \to L$.
+This map is obtained from the characteristic class $\xi(M, \mu)$ via the isomorphism $\HH^3(Q, N; L) \cong \mathrm{Hom}(C, L)$ of the universal coefficients theorem.
+
+In the special case $M = S(R, I)$ this construction produces a map $C \to C_{S}(R, I)$ which is natural in $(R, I)$ by~\cite[Proposition~3]{Lo78}.
+This map is an isomorphism by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
+\end{proof}
+
+For a triple $(S, P, G)$ we could define the unstable Quillen K-groups functors as $\K_{i}^{G, P}(R) = \pi_i(BG(R)^+_{P(R)})$. The functors with lower numbers admit the following description.
+\begin{lemma}\label{lem:lowerKgroups} There are natural isomorphisms \begin{enumerate}
+ \item $\K_1^{G,P}(R) \cong G(R) / P(R)$;
+ \item $\K_2^{G,P}(R) \cong \Ker(S(R) \to G(R))$;
+ \item $\K_3^{G,P}(R) \cong \HH_3(S(R), \ZZ).$ \end{enumerate} \end{lemma}
+\begin{proof} The first claim is obvious, the second and the third claim follow from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
+Exercises~1.8--1.9 ibid.) \end{proof}
 
@@
 \end{comment}
-Throughtout this section $A$ denotes an arbitary ring, and $I, J$ two its ideals, and $\Phi$ a simply laced root system.
+Throughtout this section $\Phi$ is a simply laced root system, $A$ denotes a commutative ring, and $I, J$ are two arbitrary ideals of $A$.
 
@@
 \section{First injectivity theorem}
+
+The principal example of a triple $(G,P,S)$ satisfying the above conditions is as follows.
+For $n \geq 5$ take the orthogonal group functor $\mathrm{O}_{2n}(-)$ and its elementary subfunctor $\mathrm{EO}_{2n}(-)$ as functors $G_n$ and $P_n$, respectively.
+Now set $S_n = \St(\rD_n, -)$.
+From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce}.
+ The other requirements can be verified in a straightforward manner. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
+
+In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
+ we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
+Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
+ it would not change $\K_3(G_n, P_n, -)$.
+
+Let us formulate the stability theorem for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
+\begin{theorem}[Panin] \label{lem:Panin-stability}
+ Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these respective cases.
+ Then the canonical map $KO_i(2n, R) \to KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
+ and an isomorphism for $\ell \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
+
+Of course, the limit groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ are exactly hermitian K-groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
+There is a modern version of hermitian K-theory, namely the theory of higher Grothendieck--Witt groups of schemes.
+We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for an introduction to this theory.
+For our purposes it would be sufficient to restrict our attention to to the affine case and to think of $\GW_i^{[k]}(R)$ as a shorthand for
+\begin{equation}
+ \GW_i^{[k]}(R) = \left\{\begin{array}{ll} KO_i(R), & k = 0, \\ U_i(R), & k = 1, \\ KSp_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
+\end{equation} %TODO: Reference?
+The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
+The notation for the upper index $[k]$ suggests that Grothendieck--Witt groups are $4$-periodic in $k$.
+
+In the sequel we will need the following result.
+\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups
+ \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
+\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+
+\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
+$A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
+Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
+by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
+Consider the following commutative square of canonical maps.
+\[ \xymatrix{
+    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
+Then there exists a diagonal arrow which makes the diagram commute.   
+\end{lemma} 
+\begin{proof}
+ Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
+  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
+ Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
+
+ Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
+  (cf.~\cite[\S~4]{LS17} for more details).
+\end{proof}
+%TODO: Give reference on a similar result of Lavrenov?
+
 If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
@@
 In the notation of~\cref{lem:lemma32} assume additionally that the residue field $k$ is of characteristic $\neq 2$.
-Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$.
-\end{lemma}
-\begin{proof}
-  Consider the following commutative diagram with rows obtained from~\cref{characterization}:
+Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
+\begin{proof}
+
+There is a natural exact sequence:
+ \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C_S(R, I).} \]
+Writing the starting portion of the homology long exact sequence for the map $S(R) \to S(R/I)$ 
+and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain a commutative diagram
 \begin{equation*}\xymatrix{
@@
  KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-In view of~\cref{lem:Panin-stability} the central vertical map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+In view of~\cref{lem:Panin-stability} the map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
 Invoking~\cref{bass-ft} (or~\cite[Corollary~5.3]{Ho05}) we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]

### 2019-07-24 dl-paper.tex
Minor fixes

@@
 
-For a triple $(S, P, G)$ we could define the unstable Quillen K-groups functors as $\K_{i}^{G, P}(R) = \pi_i(BG(R)^+_{P(R)})$. The functors with lower numbers admit the following description.
+Define the unstable Quillen K-groups functors as $\K_{i}^{G, P}(R) = \pi_i(BG(R)^+_{P(R)})$, $i\geq 1$. The functors with lower numbers admit the following description.
 \begin{lemma}\label{lem:lowerKgroups} There are natural isomorphisms \begin{enumerate}
@@
 
-\subsection{Some elementary lemmas}
+\subsection{Elementary calculations in relative Steinberg groups}
 \begin{comment}
@@
 \end{comment}
-Throughtout this section $\Phi$ is a simply laced root system, $A$ denotes a commutative ring, and $I, J$ are two arbitrary ideals of $A$.
-
-We define the following two families of elements of $\St(\Phi, A)$:
+Throughtout this section $\Phi$ is a simply laced root system, $A$ is a commutative ring, and $I, J$ are two its ideals.
+
+We denote by $\overline{\St}(\Phi, A, I)$ the kernel of the map $\St(\Phi, A) \to \St(\Phi, A/I)$.
+This group coincides with the image in $\St(\Phi, A)$ of the relative group $\St(\Phi, A, I)$ defined in the previous subsection.
+
+We define the following two families of elements of $\overline{\St}(\Phi, A, I)$:
 \begin{itemize}
@@
 \begin{rem} For a simply-laced $\Phi$ the second assertion of~\cref{thm:Stepanov} can be deduced from the first one by means of~\cref{Zrels}.
-Indeed, for a root subset $U\subseteq \Phi$ consider the following operation: \[dU := U \cup (U - U)\cap \Phi.\] In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
-It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n$ (in fact, for $n=2$).
-It remains to see that relation~\eqref{Z5} immediately implies the following assertion: every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
+Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
+In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
+It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^2(\Sigma_S) = \Phi$.
+It remains to see that relation~\eqref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
 \end{rem}

### 2019-07-26 dl-paper.tex
Major reorganization of the paper, many issues fixed

@@
 \usepackage[breaklinks=true,unicode]{hyperref}
-\usepackage[hyperref=true, backend=biber, bibencoding=utf8, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem*{theorem*}{Theorem}
 \newtheorem{corollary}{Corollary}
@@
 \DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\KO}{KO}
 \DeclareMathOperator{\GW}{GW}
@@
 Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
+
+Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
+ for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced $\Psi\subseteq \Phi$ is well-defined).
 
@@
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In the computations below we will be using identities~\eqref{eq:simplest} without explicit reference.
+In the computations below we use identities~\eqref{eq:simplest} without explicit reference.
 
@@
 Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ the morphism category $\catname{CRings}^\rightarrow$.
+If a pair $(R, I)$ is such that $R$ is a local ring with maximal ideal $I$, we call such a pair a {\it local pair}.
 
@@
  \item \label{req:left-exact} $G(D_{R, I}) \cong G(R) \times_{G(R/I)} G(R)$.
+ \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of $S(p_0), S(p_1)$ is precisely $S(R) \to S(R/I)$.
  \item \label{req:subfunc} $P(R)$ is a perfect normal subgroup of $G(R)$.
- \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of $S(p_0), S(p_1)$ is precisely $S(R) \to S(R/I)$.
  \item \label{req:uce} The map $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$.
@@
 The action of $S(R)$ on $S(D_{R, I})$ given by ${}^g h = S(\Delta)(g) \cdot h \cdot S(\Delta)(g)^{-1}$ induces an action of $S(R)$ on $S(R, I)$.
-With respect to this action the map $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-map.
+The map $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-map with respect to this action.
 From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
@@
 
-In the special case $M = S(R, I)$ this construction produces a map $C \to C_{S}(R, I)$ which is natural in $(R, I)$ by~\cite[Proposition~3]{Lo78}.
-This map is an isomorphism by~\cite[Th{\'e}or{\`e}me~2]{Lo78}.
-\end{proof}
-
-Define the unstable Quillen K-groups functors as $\K_{i}^{G, P}(R) = \pi_i(BG(R)^+_{P(R)})$, $i\geq 1$. The functors with lower numbers admit the following description.
+In the special case $M = S(R, I)$ this construction produces a map $C \to C_{S}(R, I)$ whose naturality in $(R, I)$ follows from~\cite[Proposition~3]{Lo78}. 
+This map is an isomorphism by~\cite[Th{\'e}or{\`e}me~2]{Lo78}. \end{proof}
+
+We retain our notation for the functors $S, P$ and $G$.
+For $i\geq 1$ we define the unstable Quillen K-functors $\K_{i}^{G, P}$ via
+\[ \K_i^{G,P}(R) = \pi_i(BG(R)^+_{P(R)}). \]
+It is not hard to obtain the following concrete description of these functors in the cases $i=1,2,3$.
 \begin{lemma}\label{lem:lowerKgroups} There are natural isomorphisms \begin{enumerate}
@@
 
-\subsection{Elementary calculations in relative Steinberg groups}
+Now let us give the example of a triple $(G, P, S)$ playing a key role in the present paper.
+We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively
+ (see e.\,g.~\cite{Su82} for the definition of these groups).
+Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_n, -)$ and let $\pi$ be the obvious projection $S_n \to P_n$.
+
+It is easy to see that functors $G_n$, $P_n$ and $S_n$ satisfy \ref{req:left-exact} and \ref{req:coeq}.
+By~\cite{Su82} the requirement~\ref{req:subfunc} is also satisfied for $n \geq 3$.
+Finally, from~\cite[Corollary~5.4]{St71} and~\cite[Theorem~1]{LS17} it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce} for $n \geq 5$.
+We write $\KO_i(2n, R)$ as a shorthand for $\K_i^{G_n, P_n}(R)$.
+%Notice that $\K_2(\rD_n, R) \subset \mathrm{KO}_2(n, R)$.
+
+\begin{comment}
+In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
+ we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
+Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
+ it would not change $\K_3(G_n, P_n, -)$.
+\end{comment}
+
+We conclude this subsection with the following stability result (see~\cite[Theorem~9.4]{Pa89}).
+\begin{theorem*}[Panin] \label{lem:Panin-stability}
+ Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these three cases, respectively.
+ Then the stability map $\KO_i(2n, R) \to \KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
+ and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem*}
+
+\section{Proof of the first part of the injectivity theorem}
+We start this section by recalling basic notation and facts pertaining to hermitian K-theory.
+First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}.
+We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
+Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings developed in~\cite{Ka80}.
+We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for the introduction to it.
+
+For our purposes it suffices to restrict attention to the affine case, in which we can consider Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$
+ simply as a shorthand for the following groups
+\begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
+The groups ${}_{\pm 1}\!U_i(R)$, $\mathrm{KSp}_i(R)$ are defined in~\cite{Ka80} and we will not use their definition. 
+What we need from Grothendieck--Witt groups is the following result due to M.~Schlichting.
+\begin{theorem*}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
+then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem*}
+\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
+
+%If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
+%\begin{equation} \label{relSteinberg-def}  \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.} \end{equation}
+%The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
+
+For the rest of this section let us fix the following notation.
+Let $A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
+Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
+by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
+
+\begin{lemma} \label{lem:prop41}
+Assume additionally that the residue field $k$ is of characteristic $\neq 2$.
+Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
+\begin{proof}
+%There is a natural exact sequence:
+% \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C_S(R, I).} \]
+Writing the starting portion of the homology long exact sequence for the map $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
+and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
+\begin{equation*}\xymatrix{
+ \KO_3(2\ell, B) \ar[r] \ar[d] & \KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
+ \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
+In view of Panin stability theorem the map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+By Bass fundamental theorem $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
+but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the map $f'$ (and hence $f$) is surjective.
+\end{proof}
+
+We will also need the following property of relative Steinberg groups which is a special case of {\it ``Tulenbayev lifting property''} discussed in~\cite{LS17}.
+\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
+Consider the following commutative square of canonical maps.
+\[ \xymatrix{
+    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
+    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
+Then there exists a diagonal arrow which makes the diagram commute.   
+\end{lemma} 
+\begin{proof}
+ Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
+  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
+ Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
+ In the general case the assertion of the lemma is a corollary of amalgamation theorem~\cite[Theorem~9]{S15} 
+  (see~\cite[\S~2]{LS17} for more details).
+\end{proof}
+
+\begin{theorem} \label{thm41}
+Suppose that $2 \in A^*$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
+\end{theorem}
+\begin{proof}
+ Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
+\begin{equation*} \xymatrix{
+ C(\rD_\ell, B, I) \ar[r]^{\lambda_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
+ \St(\rD_\ell, B) \ar[r]^{\nu_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
+ C(\rD_\ell, R, I) \ar[r]^{\lambda_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
+ \St(\rD_\ell, R) \ar[r]^-{\nu_R}        & \St(\rD_\ell, k[X, X^{-1}]).
+}\end{equation*}
+Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
+ also lies in $\Ker(\nu_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
+Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $\lambda_R(c) = g(b)$. 
+By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$.
+The required assertion now follows from the following computation:
+ \[ 1 = \mu_B\lambda_B(d) = tg\lambda_B(d) = t\lambda_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
+\end{proof}
+
+\section{Elementary calculations in relative Steinberg groups}
 \begin{comment}
@@
 \end{comment}
-Throughtout this section $\Phi$ is a simply laced root system, $A$ is a commutative ring, and $I, J$ are two its ideals.
-
-We denote by $\overline{\St}(\Phi, A, I)$ the kernel of the map $\St(\Phi, A) \to \St(\Phi, A/I)$.
-This group coincides with the image in $\St(\Phi, A)$ of the relative group $\St(\Phi, A, I)$ defined in the previous subsection.
-
-We define the following two families of elements of $\overline{\St}(\Phi, A, I)$:
+Throughtout this let $\Phi$ is a simply laced root system, $R$ is a commutative ring, and $I, J$ are two its ideals. 
+We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the map $\St(\Phi, R) \to \St(\Phi, R/I)$.
+This group coincides with the image in $\St(\Phi, R)$ of the relative group $\St(\Phi, R, I)$ defined in~\cref{sec:quillen}.
+
+Denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
+It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
+We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^\times$, $v \in R^\times$, $\alpha\in \Phi$.
+
+We define the following two families of elements of $\overline{\St}(\Phi, R, I)$:
 \begin{itemize}
- \item $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$ defined for $\xi \in A$, $s \in I$;
+ \item $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$ defined for $\xi \in R$, $s \in I$;
  \item $c_\alpha(s, t) = [x_\alpha(s), x_{-\alpha}(t)]$ defined for $s \in I$, $t \in J$.
@@
 
-\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in A$, $s\in I$:
+\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in R$, $s\in I$:
 \begin{enumerate} 
@@
 
+Let us mention an immediate application of the just proved lemma. 
+First of all, recall the following two results in which two generating sets for the group $\overline{\St}(\Phi, R, I)$ are described.
+\begin{theorem*}[Stein--Tits--Vaserstein]
+ For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+\end{theorem*} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}. \end{proof}
+
 For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
 
-\begin{theorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
-
-In fact, it is generated as a group by even smaller subset $\mathcal{Z}(\Sigma_S, R, I)$. Here $\Sigma_S$ denotes the special part of arbitrary parabolic subset of roots $S \subseteq \Phi$.
-\end{theorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
-
-\begin{rem} For a simply-laced $\Phi$ the second assertion of~\cref{thm:Stepanov} can be deduced from the first one by means of~\cref{Zrels}.
+\begin{theorem*}[Stepanov] For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group subset $\mathcal{Z}(\Sigma_S, R, I)$.
+ Here $\Sigma_S$ denotes the special part of arbitrary parabolic subset of roots $S \subseteq \Phi$.
+\end{theorem*} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+
+\begin{rem} For a simply-laced $\Phi$ Stepanov's theorem can be deduced from Stein--Tits-Vaserstein theorem by means of~\cref{Zrels}.
 Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
 In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
-It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^2(\Sigma_S) = \Phi$.
+It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ (in fact, $n=2$).
 It remains to see that relation~\eqref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
@@
 
-For the proof of the following lemma we will need the following variant of Hall--Witt identity:
+We will need the following variant of Hall--Witt identity:
 \begin{equation} \label{HW-variant} [[x, y], z] = \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}.\end{equation}
-
 \begin{lemma} \label{Crels}
-The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in A$.
+The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in R$.
  \begin{enumerate}
@@
 
-\section{First injectivity theorem}
-
-The principal example of a triple $(G,P,S)$ satisfying the above conditions is as follows.
-For $n \geq 5$ take the orthogonal group functor $\mathrm{O}_{2n}(-)$ and its elementary subfunctor $\mathrm{EO}_{2n}(-)$ as functors $G_n$ and $P_n$, respectively.
-Now set $S_n = \St(\rD_n, -)$.
-From [Stein's paper] and [Lemma on centrality] it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce}.
- The other requirements can be verified in a straightforward manner. We write $KO_i(n, R)$ as a shorthand for $\K_i(G_n, P_n, R)$.
-
-In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
- we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
-Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
- it would not change $\K_3(G_n, P_n, -)$.
-
-Let us formulate the stability theorem for orthogonal Quillen K-groups (see~\cite[Theorem~9.4]{Pa89}).
-\begin{theorem}[Panin] \label{lem:Panin-stability}
- Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these respective cases.
- Then the canonical map $KO_i(2n, R) \to KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
- and an isomorphism for $\ell \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
-
-Of course, the limit groups $\K_i(\mathrm{O}_\infty, \mathrm{EO}_\infty, R) = KO_i(R)$ are exactly hermitian K-groups ${}_{-1}\!L_i(R)$ defined in~\cite{Ka80}.
-There is a modern version of hermitian K-theory, namely the theory of higher Grothendieck--Witt groups of schemes.
-We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for an introduction to this theory.
-For our purposes it would be sufficient to restrict our attention to to the affine case and to think of $\GW_i^{[k]}(R)$ as a shorthand for
-\begin{equation}
- \GW_i^{[k]}(R) = \left\{\begin{array}{ll} KO_i(R), & k = 0, \\ U_i(R), & k = 1, \\ KSp_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right.
-\end{equation} %TODO: Reference?
-The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition.
-The notation for the upper index $[k]$ suggests that Grothendieck--Witt groups are $4$-periodic in $k$.
-
-In the sequel we will need the following result.
-\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups
- \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem}
-\begin{proof} This is a special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
-
-\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
-$A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
-Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
-by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
-Consider the following commutative square of canonical maps.
-\[ \xymatrix{
-    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
-Then there exists a diagonal arrow which makes the diagram commute.   
-\end{lemma} 
-\begin{proof}
- Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
-  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
- Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
-
- Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
-  (cf.~\cite[\S~4]{LS17} for more details).
-\end{proof}
-%TODO: Give reference on a similar result of Lavrenov?
-
-If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
-\begin{equation} \label{relSteinberg-def}
- \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.}
-\end{equation}
-The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
-The following result plays a key role in the proof of~\cref{thm41}.
-\begin{lemma} \label{lem:prop41}
-In the notation of~\cref{lem:lemma32} assume additionally that the residue field $k$ is of characteristic $\neq 2$.
-Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
-\begin{proof}
-
-There is a natural exact sequence:
- \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C_S(R, I).} \]
-Writing the starting portion of the homology long exact sequence for the map $S(R) \to S(R/I)$ 
-and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain a commutative diagram
-\begin{equation*}\xymatrix{
- KO_3(2\ell, B) \ar[r] \ar[d] & KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
- KO_3(2\ell, R) \ar[r]        & KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-In view of~\cref{lem:Panin-stability} the map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
-Invoking~\cref{bass-ft} (or~\cite[Corollary~5.3]{Ho05}) we obtain that \[\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k).\]
-By \cite[Lemma~2.2]{FRS12} the group $\GW_2^{[3]}(k)$ is trivial, therefore $f'$ (and hence $f$) are surjective.
-\end{proof}
-
-\begin{theorem} \label{thm41}
-Assume the notation of~\cref{lem:lemma32} and suppose additionally that $2$ is invertible in $A$.
-Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
-\end{theorem}
-\begin{proof}
- Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
-\begin{equation*} \xymatrix{
- C(\rD_\ell, B, I) \ar[r]^{j_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
- \St(\rD_\ell, B) \ar[r]^{\pi_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
- C(\rD_\ell, R, I) \ar[r]^{j_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
- \St(\rD_\ell, R) \ar[r]^-{\pi_R}        & \St(\rD_\ell, k[X, X^{-1}]).
-}\end{equation*}
-Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
- also lies in $\Ker(\pi_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
-Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $j_R(c) = g(b)$. 
-By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$ and we obtain the required assertion:
- \[ 1 = \mu_Bj_B(d) = tgj_B(d) = tj_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
-\end{proof}
-
-\section{Second injectivity theorem}
+\subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}
+For the rest of this subsection $A$ denotes a local ring with maximal ideal $M$.
+The aim of this subsection is to describe a generating set for the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
+induced by the ring homomorphism of evaluation at $0$. Denote this kernel by $K(A[X], M[X])$.
+
+It is obvious that $K(A[X], M[X])$ contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$.
+It turns out that although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described.
+
+Since $ev_{X=0}^*$ admits a section, we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
+ moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
+\begin{lemma} The following decomposition holds
+ \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
+\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+ It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
+
+ Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
+ Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
+ (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
+ which implies the assertion. \qedhere \end{proof}
+
+\begin{theorem}[Stein] \label{thmStein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+\end{proof}
+
+\begin{prop} \label{Kgen} The subgroup $K(A[X], M[X])$ is generated as an abstract group by the subgroup $\overline{\St}(\Phi, A[X], XM[X])$ and
+ the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
+\begin{proof} Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
+
+Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$.
+It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
+Since $C_0$ is generated by the above commutators and $\overline{\St}(\Phi, A[X], XM[X])$ is a normal subgroup of $\St(\Phi, A[X])$
+we obtain that $C_0 \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1$ and consequently that
+$K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1.$
+
+It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
+Thus, it remains to show that commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
+Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
+Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, 
+ and in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}
+
+\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$.
+\end{corollary}
+\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
+ $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
+The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
+\end{proof}
+
+\section{Proof of the second part of the injectivity theorem}
 
@@
 
-\subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}
-For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
-We also denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
-It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
-We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^\times$, $v \in R^\times$, $\alpha\in \Phi$.
-
-The aim of this subsection is to describe the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
-induced by the ring homomorphism of evaluation at $0$.
-Clearly, this kernel, denote it by $K(A[X], M[X])$, contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$, however, apriori it may be larger, so our goal will be to describe the explicit extra elements sufficient to generate it.
-
-Obviously, $ev_{X=0}^*$ admits a section hence we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
- moreover, the following decomposition holds:
-\begin{equation} \label{relZero-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).\end{equation}
-\begin{lemma} The following decomposition holds
- \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
-\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
- It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
-
- Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
- Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
- (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
- which implies the assertion. \qedhere \end{proof}
-
-\begin{theorem}[Stein] \label{thmStein} For a local ring $A$ with maximal ideal $M$ holds \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
-\end{proof}
-
-\begin{prop} \label{Kgen} For $A$ and $M$ as above the subgroup $K(A[X], M[X])$ is generated as a group by its subgroup $\overline{\St}(\Phi, A[X], XM[X])$ and
- the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
-\begin{proof} Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
-
-Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$.
-It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
-\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
-Since $C_0$ is generated by the above commutators and $\overline{\St}(\Phi, A[X], XM[X])$ is a normal subgroup of $\St(\Phi, A[X])$
-we obtain that $C_0 \subseteq \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1$ and consequently that
-$K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot C_1.$
-
-It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
-Thus, it remains to show that commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
-Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
-Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, 
- and in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}
-
-\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$.
-\end{corollary}
-\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
- $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
-The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
-\end{proof}
-
 \subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} 
@@
 \begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. Then the subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by Stepanov theorem $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
 The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
@@
 \begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$. 
-Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
+Applying Stepanov theorem to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
 By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
@@
 
-\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
+% \begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
 \begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.

### 2019-07-26 dl-paper.tex
Small fixes

@@
 
-\subsection{$\K_2$-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our treatment of symbols follows~\cite{DS73}.
@@
 
-\begin{theorem*}[Stepanov] For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group subset $\mathcal{Z}(\Sigma_S, R, I)$.
- Here $\Sigma_S$ denotes the special part of arbitrary parabolic subset of roots $S \subseteq \Phi$.
+\begin{theorem*}[Stepanov] For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group by the subset $\mathcal{Z}(\Sigma_S, R, I)$.
+ Here $\Sigma_S$ denotes the special part of an arbitrary parabolic subset of roots $S \subseteq \Phi$.
 \end{theorem*} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
+\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements (as before, $\xi \in A[X]$, $f\in M[X]$):
  \begin{enumerate}
@@
 Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$. 
-In particular, $K(\alpha, \beta)$ does not depend on a choice of the root $\delta$. \end{prop}
+In particular, $K(\alpha, \beta)$ does not depend on the choice of the root $\delta$. \end{prop}
 \begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$. 
-Applying Stepanov theorem to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
-By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
+Applying Stepanov theorem to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, 
+$\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$. By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
 
@@
 
-\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\text{R3}_{\leq 0, 1}$. \end{lemma}
+\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
 \begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
@@
 
-\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\text{R2}_{\leq -1, 1}$. \end{lemma}
+\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
 \begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
@@
 
-The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations of types $\text{R2}_{0,1}$ and $\text{R3}_{1,1}^{\angle}$. \end{prop}
+%The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+
+\begin{lemma} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
+\begin{proof}
+Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
+We can assume that $p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)$ for some $m,m' \in M$.
+Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
+\begin{multline} \nonumber
+ T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, h, u\right) = 
+ T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
+ \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
+ = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \end{multline}
+where 
+\begin{multline} \nonumber
+ h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
+    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
+ = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
+ \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
+\end{multline}
+The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which shows that the desired relation holds.
+\end{proof}
+
+\begin{lemma} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
 \begin{proof} 
@@
 \end{comment}
-Let us verify $\text{R2}_{0,1}$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
-Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$.
+Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
+As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
 Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
@@
  = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
- h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
+ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
 \end{multline}
-
-Now let us prove $\text{R3}_{1,1}^\angle$. As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$.
-Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
-\begin{gather*} \begin{multlined} \nonumber
- T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, h, u\right) = 
- T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
- \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
- = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multlined} \\
-\begin{multlined} \nonumber
- h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
-    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
- = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
- \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
-\end{multlined}
-\end{gather*}
-The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which shows that the desired relation holds.
 \end{proof}

### 2019-07-26 dl-paper.tex
Minor fix

@@
 
-\begin{theorem}[Stein] \label{thmStein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
-\end{proof}
+\begin{theorem*}[Stein] One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem*} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}
 

### 2019-07-30 dl-paper.tex
Changed numbering conventions, added main proposition

@@
 
-\newtheorem{prop}{Proposition}
 \newtheorem{theorem}{Theorem}
 \newtheorem*{theorem*}{Theorem}
-\newtheorem{corollary}{Corollary}
 \newtheorem{lemma}{Lemma}
+\newtheorem{prop}[lemma]{Proposition}
+\newtheorem{corollary}[lemma]{Corollary}
 \theoremstyle{remark}
@@
 \theoremstyle{definition}
+\numberwithin{lemma}{section}
+\numberwithin{prop}{section}
+\numberwithin{corollary}{section}
 \newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
@@
 \subsection{Presentation of Steinberg groups by homogeneous generators}
+\label{sec:presentation}
 %Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
@@
 
-\begin{prop} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
+\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
 In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
@@
 
-\subsection{The proof of the injectivity theorem}
+\subsection{Construction of a model for $\St(\Phi, M[X] + A[X^{-1}])$}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
+Let $A$ be a local ring with maximal ideal $M$.
 We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-For shortness we also write $G_M^0$ instead of $\overline{\St}(\Phi, A, M)$.
+If we set $t = X^{-1}$, the notation of the present subsection becomes consistent with that of~\cref{sec:presentation}.
+
+For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
@@
 Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
-Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times$ consisting of those triples $(g, h, u)$ for which 
-$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
+Denote by $V$ the subset of \[\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
+\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
 We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
 It is clear that this action is well defined.
-Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
-Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$ and say that these triples are congruent.
+Denote by $\overline{V}$ the set of orbits of this action.
+Whenever two triples $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$ and say that these triples are congruent.
+We also use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
+We denote by $\overline{p}$ the function $\overline{V} \to \St(\Phi, A[X, X\inv])/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.
 
@@
 If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
-\[ t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
+\begin{equation} \label{T_1} t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\end{equation}
 
@@
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
-
- Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of representative.
+  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$ congruent to $(g, h, u)$.
+
+ Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of the representative.
  Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
@@
  the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
- By~\cref{thmStein} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}.
+ It follows from Stein's theorem that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}.
 Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
@@
 For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
-\[ T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h\cdot x_{\alpha}(-a), u).  \]
+\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h\cdot x_{\alpha}(-a), u).  \end{equation}
 It is easy to see that this definition is correct.
 
-\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
+Thus far we have specified the action of the generators of the "truncated'' Steinberg group $\St^{\leq 1}(\Phi, B)$ from~\cref{sec:presentation} on $\overline{V}$ using formulae~\eqref{T_1} and~\eqref{T_leq0}.
+We need to verify that this action respects the defining relations of the group $\St^{\leq 1}(\Phi, B)$ (notice that $\leq 1$ here stands for the degree of relations with respect to $t = X^{-1}$).
+This is accomplished in the series of lemmas below.
+
+\begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
 \begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
@@
 
-\begin{lemma} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
+\begin{lemma} \label{R3_leqm1_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
 \begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
@@
 
-\begin{lemma} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
+\begin{lemma} \label{R3_1_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
 \begin{proof}
@@
 \end{multline}
-The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which shows that the desired relation holds.
-\end{proof}
-
-\begin{lemma} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
+The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies that the desired relation holds.
+\end{proof}
+
+\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
 \begin{proof} 
@@
 
+We are ready to formulate the main result of this subsection.
+
+\begin{prop} 
+For $\Phi$ as in the statement of~\cref{lemma33}.
+the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.
+
+This action satisfies the following additional property.
+If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $g_1 \in \St(\Phi, A[X\inv])$ holds $\overline{p}(j_-(g_1) \cdot v) = \overline{1}$.
+\end{prop}
+\begin{proof}
+  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
+On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} which implies the first assertion.
+
+  Let us verify the second assertion...
+\end{proof}
+
+\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
+
 \begin{comment}

### 2019-07-31 dl-paper.tex
Minor fix

@@
 We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-If we set $t = X^{-1}$, the notation of the present subsection becomes consistent with that of~\cref{sec:presentation}.
+The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X^{-1}$, $I = M$.
 
@@
 
-  Let us verify the second assertion...
-\end{proof}
+  The second assertion can be verified directly using~\eqref{T_1}, \eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
+\end{proof}
+
+We need to verify the following property: for $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$.
+It suffices to verify this for $g = z_\alpha(f, \xi)$, $f \in M[X]$, $\xi\in A[X]$.
 

### 2019-08-01 dl-paper.tex
Notation fix

@@
 Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
+Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
 Denote by $V$ the subset of \[\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
 \[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
+
 We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
-It is clear that this action is well defined.
-Denote by $\overline{V}$ the set of orbits of this action.
-Whenever two triples $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$ and say that these triples are congruent.
-We also use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
-We denote by $\overline{p}$ the function $\overline{V} \to \St(\Phi, A[X, X\inv])/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.
-
-The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
+This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
+Whenever two triples $v_1, v_2 \in V$ lie in the same orbit we use the notation $v_1 \sim v_2$ and say that they are congruent.
+The same notation $h_1 \cong h_2$ is also used for the elements of $\St(\Phi, A[X\inv])$ that are right-adjacent with respect to $G^0_M$.
+
+We denote by $\overline{V}$ the set of orbits of this action.
+We use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
+We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.
+
+We start by defining for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
 This function is defined for the triples $(g, h, u)$ satisfying $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
+If $p(g, h, u)$ belongs to $P_\alpha(m)$ for some $m \in M$, then we define $t_\alpha(aX^{-1})$ by the following identity:
 \begin{equation} \label{T_1} t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\end{equation}
@@
 \[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
-therefore the operation $t_\alpha(aX^{-1})$ is well-defined.
+therefore $t_\alpha(aX^{-1})$ is well-defined.
 
@@
  $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$ congruent to $(g, h, u)$.
+  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
 
@@
 For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
-\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h\cdot x_{\alpha}(-a), u).  \end{equation}
+\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, [h], u) = (x_\alpha(a + Xf) \cdot g, [h], u).  \end{equation}
 It is easy to see that this definition is correct.
@@
 \begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
-\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
-Write $b = b_0 + Xf$ for some $f \in M[X]$.
+\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, [h], u) = (g, [h], u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b\in A + XM[X]$.
+Write $b = b_0 + Xf$ for some $b_0 \in A$, $f \in M[X]$.
 We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
-It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that 
-\begin{gather*}
-\begin{multlined} \nonumber
-  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, h, u) \sim \\
-  \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0), u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, h \cdot h', u] \right) \sim \left(g, h, u\right), \end{multlined} \\
-\begin{multlined} \nonumber \text{ where }
- h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b_0) = \\
- = h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right),\ x_\beta(b_0)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}
+It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b_0)$, therefore by~\cref{SR:additivity} we have
+\begin{multline} \nonumber
+  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, [h], u) = \\
+  = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha(-aX^{-1}) \cdot g, [h'], u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h''], u] \right) = \left(g, [h], u\right), \end{multline}
+where $h' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0)$ and
+\begin{multline} \nonumber
+ h'' = h' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = \\
+ = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am). \qedhere \end{multline}
 \end{proof}
@@
 \begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
- \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, h, u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, h, u\right). \]
-
-As before, we may assume that $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+ \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, [h], u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, [h], u\right). \]
+
+As before, we may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
 Since $x_\beta(Xf)$ belongs to $P_\alpha(0)$ we obtain from~\cref{SR:additivity} that:
-\begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ h,\ u\right) \sim \\ 
-\sim T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am),\ u(1-am)\right) = \\ = \left( [x_\beta(Xf), x_\alpha(aX^{-1})] \cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right),\ u \right) \sim \\ \sim (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ h,\ u).
+\begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ [h],\ u\right) = \\ 
+= T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am)\right],\ u(1-am)\right) = \\ = \left([x_\beta(Xf),\ x_\alpha(aX^{-1})] \cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right)\right],\ u \right) = \\ = (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ [h],\ u).
 \qedhere \end{multline} \end{proof}
@@
 Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
-We can assume that $p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)$ for some $m,m' \in M$.
+From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)\text{ for some }m,m' \in M.\]
 Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
 \begin{multline} \nonumber
- T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, h, u\right) = 
- T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
- \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
- = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \end{multline}
+ T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = 
+ T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
+ = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am')\right],\ u(1 + am)\right) = \\
+ = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, [h'], u(1 + am + bm')), \end{multline}
 where 
@@
 \end{multline}
-The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies that the desired relation holds.
+If we swapped $(a,\alpha,m)$ with $(b,\beta,m')$, 
+the expressions in the right-hand sides of the above formulae would remain unchanged. This implies the required assertion.
 \end{proof}
@@
 \begin{multline} \nonumber
-[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
- = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
- \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h', u (1 - am) \right) = \\
- = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g, h'', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
- where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot$ 
-  and the last congruence is obtained as follows:
+[T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
+ %= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right)\right], u (1 - am) \right) = \\
+ = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
+ = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
+ where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
+  and the last equality is obtained as follows:
  \begin{multline} \nonumber

### 2019-08-01 dl-paper.tex
Proving 5.30

@@
 
-\section{Proof of the first part of the injectivity theorem}
+\section{Proof of the first part of the injectivity theorem} \label{firstPart}
 We start this section by recalling basic notation and facts pertaining to hermitian K-theory.
@@
 
-We will also need the following property of relative Steinberg groups which is a special case of {\it ``Tulenbayev lifting property''} discussed in~\cite{LS17}.
+We will also need the following property of relative Steinberg groups which is a special case of {\it ``Tulenbayev lifting property''} discussed in~\cite[\S~2]{LS17}.
 \begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
@@
     \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur] & \St(\Phi, R) } \]
-Then there exists a diagonal arrow which makes the diagram commute.   
+    \St(\Phi, R, I) \ar[r] \ar@{-->}^t[ur] & \St(\Phi, R) } \]
+Then there exists a diagonal map $t$ which makes the diagram commute.   
 \end{lemma} 
@@
 
-\subsection{Construction of a model for $\St(\Phi, M[X] + A[X^{-1}])$}
+\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
 Let $A$ be a local ring with maximal ideal $M$.
-We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
-The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X^{-1}$, $I = M$.
+As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of $A[X, X\inv]$.
+The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X\inv$, $I = M$.
 
 For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
+Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
-              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
-Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
-Denote by $V$ the subset of \[\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
+              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]) &  } \] 
+We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
+Denote by $V$ the subset of \[\St(\Phi, A[X, X\inv]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
 \[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
@@
 This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
-Whenever two triples $v_1, v_2 \in V$ lie in the same orbit we use the notation $v_1 \sim v_2$ and say that they are congruent.
-The same notation $h_1 \cong h_2$ is also used for the elements of $\St(\Phi, A[X\inv])$ that are right-adjacent with respect to $G^0_M$.
-
-We denote by $\overline{V}$ the set of orbits of this action.
+Whenever two triples $v_1, v_2 \in V$ lie in the same orbit we use the notation $v_1 \sim v_2$ and say that they are {\it congruent}.
+The same notation $h_1 \sim h_2$ is also used for the elements of $\St(\Phi, A[X\inv])$ lying in the same left $G^0_M$-coset.
+
+We denote by $\overline{V}$ the set of orbits of the action of $G_M^0$.
 We use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
-We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.
+We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ sending each $(g, [h], u) \in V$ to the left coset $p(g, h, u)G_M^0$.
 
@@
 This function is defined for the triples $(g, h, u)$ satisfying $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
-If $p(g, h, u)$ belongs to $P_\alpha(m)$ for some $m \in M$, then we define $t_\alpha(aX^{-1})$ by the following identity:
+If $p(g, h, u)$ belongs to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is defined via the following identity:
 \begin{equation} \label{T_1} t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\end{equation}
@@
 This action satisfies the following additional property.
-If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $g_1 \in \St(\Phi, A[X\inv])$ holds $\overline{p}(j_-(g_1) \cdot v) = \overline{1}$.
+If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_-(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_-(h_1) \cdot v) = \overline{1}$.
 \end{prop}
@@
 
-We need to verify the following property: for $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$.
-It suffices to verify this for $g = z_\alpha(f, \xi)$, $f \in M[X]$, $\xi\in A[X]$.
+\begin{lemma}
+For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
+\end{lemma}
+\begin{proof}
+ It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ ($f \in M[X]$, $\xi\in A[X]$).
+ %Notice that in the case $\xi = 0$ the assertion immediately follows from~\eqref{T_leq0} since $t(x_\alpha(f)) = x_\alpha(f)$. 
+ We verify the assertion by induction on the degree of $\xi$ in $X$.
+
+ First of all, consider the case $\xi = aX$, $a\in A$. Notice that
+ \[t(z_\alpha(f, aX)) = [x_{\beta}(X^{-1}) \cdot x_{\beta-\alpha}(a),\ x_{\alpha-\beta}(-fX) \cdot x_{-\beta}(afX^2)].\]
+ \[ [x_\beta(X^{-1})^{x_{-\alpha}(aX)},\ x_{\alpha-\beta}(Xf)^{x_{-\alpha}(aX)}] \]
+\end{proof}
+
+\begin{multline}z_{\alpha+\beta}(f\xi, X) = x_\alpha(\epsilon f) \cdot x_{-\beta}(-fX) \cdot x_{\beta}(fX\xi^2) \cdot x_{\alpha+\beta}(f \xi) \cdot \\ \cdot z_\alpha(-\epsilon f, -\epsilon X\xi) \cdot
+  x_{-\alpha}(-\epsilon fX^2\xi^2) \cdot x_{-\alpha-\beta}(- f X^2 \xi) \cdot z_{-\beta}(fX, -\xi)\end{multline}
+
+\begin{multline}
+ z_{\alpha+\beta}(f, ax) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
+\end{multline}
+
+$s := fX$, $\eta := X^{-1}$, $\xi = aX$
 

### 2019-08-02 dl-paper.tex
Proving 5.30

@@
 \item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
-\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
+\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
   x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
@@
 \begin{proof}
- It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ ($f \in M[X]$, $\xi\in A[X]$).
- %Notice that in the case $\xi = 0$ the assertion immediately follows from~\eqref{T_leq0} since $t(x_\alpha(f)) = x_\alpha(f)$. 
- We verify the assertion by induction on the degree of $\xi$ in $X$.
+ It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
+ Set $I = M[X, X\inv]$. It is not hard to verify the assertion for the element $g_1 = z_\alpha(X^2f, aX^{-1}) \in \St(\Phi, B, I)$.
+ Indeed, using the fact that $x_{\alpha}(X^2f) \in P_{-\alpha}(0)$ we obtain that
+ \begin{multline}
+  g_1 \cdot (g, [h], u) = x_{-\alpha}(-aX^{-1}) (x_\alpha(X^2f)x_{-\alpha}(aX^{-1})g, [h \cdot x_{-\alpha}(\tfrac{-aX^{-1}}{1+am})] )
+\end{multline}
+
+   \[ g_1 \cdot (g,\ [h],\ u) = () \]
+ Consider the case $\xi = aX^{-1}$, $f = X^2f'$
+
+ We verify the assertion by induction on the degree of $\xi$ in $X$ starting from $-1$.
 
@@
 \begin{multline}
- z_{\alpha+\beta}(f, ax) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
+ z_{\alpha+\beta}(f, aX) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
 \end{multline}

### 2019-08-02 dl-paper.tex
Proving 5.30

@@
 \begin{proof} 
- It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
- Set $I = M[X, X\inv]$. It is not hard to verify the assertion for the element $g_1 = z_\alpha(X^2f, aX^{-1}) \in \St(\Phi, B, I)$.
- Indeed, using the fact that $x_{\alpha}(X^2f) \in P_{-\alpha}(0)$ we obtain that
+It suffices to verify the assertion for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
+We accomplished this by induction on the degree of $\xi$ in $X$.
+It is obvious, that the assertion holds in the case $\xi = a \in A$.
+
+Suppose that the assertion is true for all $g_1 = z_\alpha(f, \xi)$ with $\xi$ of degree $\leq n$.
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, A[X, X\inv], M[X, X\inv])$:
 \begin{multline}
-  g_1 \cdot (g, [h], u) = x_{-\alpha}(-aX^{-1}) (x_\alpha(X^2f)x_{-\alpha}(aX^{-1})g, [h \cdot x_{-\alpha}(\tfrac{-aX^{-1}}{1+am})] )
+ z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1})
 \end{multline}
-
-   \[ g_1 \cdot (g,\ [h],\ u) = () \]
- Consider the case $\xi = aX^{-1}$, $f = X^2f'$
-
- We verify the assertion by induction on the degree of $\xi$ in $X$ starting from $-1$.
-
- First of all, consider the case $\xi = aX$, $a\in A$. Notice that
- \[t(z_\alpha(f, aX)) = [x_{\beta}(X^{-1}) \cdot x_{\beta-\alpha}(a),\ x_{\alpha-\beta}(-fX) \cdot x_{-\beta}(afX^2)].\]
- \[ [x_\beta(X^{-1})^{x_{-\alpha}(aX)},\ x_{\alpha-\beta}(Xf)^{x_{-\alpha}(aX)}] \]
-\end{proof}
-
-\begin{multline}z_{\alpha+\beta}(f\xi, X) = x_\alpha(\epsilon f) \cdot x_{-\beta}(-fX) \cdot x_{\beta}(fX\xi^2) \cdot x_{\alpha+\beta}(f \xi) \cdot \\ \cdot z_\alpha(-\epsilon f, -\epsilon X\xi) \cdot
-  x_{-\alpha}(-\epsilon fX^2\xi^2) \cdot x_{-\alpha-\beta}(- f X^2 \xi) \cdot z_{-\beta}(fX, -\xi)\end{multline}
-
-\begin{multline}
- z_{\alpha+\beta}(f, aX) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
-\end{multline}
-
-$s := fX$, $\eta := X^{-1}$, $\xi = aX$
+It is not hard to verify the assertion for all the factors in the right hand side of the above expression
+ (except for the fifth factor, for which it is precisely the inductive assumption). It remains to see that
+  $t(z_\alpha(f, X\xi + a)) = x_\alpha(-a) \cdot t(z_\alpha(f, X\xi)) \cdot x_\alpha(a)$.
+\end{proof}
 

### 2019-08-05 dl-paper.tex
Proving 5.30

@@
 
-%If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
-%\begin{equation} \label{relSteinberg-def}  \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.} \end{equation}
-%The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.
-
 For the rest of this section let us fix the following notation.
@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
-\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
+\item If $\alpha+\beta\in\Phi$, then holds:
+\begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
   x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
@@
 \end{multline}
-
-\begin{comment}
-\begin{multline} 
- [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
-\end{multline}
-\end{comment}
 \end{proof}
@@
 \section{Proof of the second part of the injectivity theorem}
-
 \subsection{Presentation of Steinberg groups by homogeneous generators}
 \label{sec:presentation}
-%Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
-Let $I\trianglelefteq A$ be an ideal of a commutative ring $A$.
+Let $M\trianglelefteq A$ be an ideal of a commutative ring $A$.
 We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
-We denote by $B = B(A, I)$ the subring $A[t] + I[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
-As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$.
-Obviously, $B = A[t]$ in the case $I=0$ and $B = A[t, t\inv]$ in the case $I=A$.
+We denote by $B = B(A, M)$ the subring $A[t] + M[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
+As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$.
+Obviously, $B = A[t]$ in the case $M=0$ and $B = A[t, t\inv]$ in the case $M=A$.
 
@@
 Finally, suppose $g$ has type $5$.
-Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
+Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
 \begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
@@
 Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} we obtain that
 \begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
@@
 Let $A$ be a local ring with maximal ideal $M$.
-As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of $A[X, X\inv]$.
-The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X\inv$, $I = M$.
+As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.
 
 For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
-Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
+Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$.
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
-              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]) &  } \] 
+              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R) &  } \] 
 We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
-Denote by $V$ the subset of \[\St(\Phi, A[X, X\inv]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
+Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
 \[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
@@
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
- $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
-  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
+ $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
 
@@
  By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
- From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
- the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
+ From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
 It follows from Stein's theorem that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}.
@@
 \qedhere \end{multline} \end{proof}
-
-%The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
 
@@
 \begin{proof} 
-\begin{comment}
-Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
-Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
-  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
-The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
-\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
-T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
- = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
-\end{comment}
 Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
@@
   By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
-On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} which implies the first assertion.
+On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).
 
@@
 
-\begin{lemma}
-For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
-\end{lemma}
-\begin{proof} 
-It suffices to verify the assertion for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
-We accomplished this by induction on the degree of $\xi$ in $X$.
-It is obvious, that the assertion holds in the case $\xi = a \in A$.
-
-Suppose that the assertion is true for all $g_1 = z_\alpha(f, \xi)$ with $\xi$ of degree $\leq n$.
-Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, A[X, X\inv], M[X, X\inv])$:
-\begin{multline}
- z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1})
-\end{multline}
-It is not hard to verify the assertion for all the factors in the right hand side of the above expression
- (except for the fifth factor, for which it is precisely the inductive assumption). It remains to see that
-  $t(z_\alpha(f, X\xi + a)) = x_\alpha(-a) \cdot t(z_\alpha(f, X\xi)) \cdot x_\alpha(a)$.
+Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (and also of $R$).
+We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from~\cref{lem:lemma32}.
+\begin{lemma} For $v\in \overline{V}$ and any $g \in \St(\Phi, R, I)$ holds $\overline{p}(t(g) \cdot v) = \mu_R(g) \cdot \overline{p}(v)$. \end{lemma}
+\begin{proof} First of all, notice that the assertion of the lemma can be verified by direct computation using~\eqref{T_1} and~\eqref{T_leq0} in the cases $g = z_\alpha(f, a)$ or $g = z_\alpha(X^2f, aX^{-1})$ for all $a\in A$, $f\in M[X]$.
+Notice that in both cases $g$ is contained in the image of $\St(\Phi, B, I)$, therefore $t$ acts identically on it.
+
+It suffices to verify the assertion of the lemma for the generators $g = z_\alpha(f, \xi)$ of $\St(\Phi, R, I)$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
+induction on the degree of $\xi$ in $X$. The base of induction is clear by the above observation.
+
+Now, suppose that the assertion holds for all $g = z_\alpha(f, \xi)$ in which $\xi$ has degree $\leq n$.
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} and using the definition of $t$ we obtain the following equality in $\St(\Phi, B)$ (in which $\epsilon = N_{\alpha, \beta}$):
+\begin{multline*}
+ t(z_{\alpha+\beta}(f, X\xi)) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot t(z_\alpha(-\epsilon Xf, -\epsilon \xi)) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}).
+\end{multline*}
+By inductive assumption the assertion of the lemma holds for all the factors in the right-hand side, therefore it also holds for  $z_\alpha(f, X\xi)$.
+From this it is not hard to deduce the assertion for $g = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
 \end{proof}
@@
 \subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
-
-\begin{comment}
-$n \geq m$
-$b = \epsilon  X^{-m}$
-$\epsilon \in R^*$, $d \in R$
-$abc = d X^{-n}$
-
-$|a| = n-m$, $|b| = m$, $|c| = 0$
-
-\begin{align*}
-[x_{il}(abc), x_{jk}(b)] &= 1 & \text{R3}_{n,m} \\
-[x_{ij}(a), x_{kl}(c)] &= 1 & \text{R3}_{n-m, 0}\\
-[x_{ik}(ab), x_{kl}(c)] &= x_{il}(abc), & \text{R2}_{n, 0} \\
-[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
-[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab), & \text{R2}_{n-m, m}\\
-[x_{ij}(a), x_{jl}(bc)] &= x_{il}(abc),& \text{R2}_{n-m, m}\\
-[x_{jk}(b), x_{kl}(c)] &= x_{jl}(bc), & \text{R2}_{m, 0}\\
-[x_{ij}(a), x_{jk}(b)] &= x_{ik}(ab) & \text{R2}_{n-m, m}
-\end{align*}
-
-\begin{lemma} For any simply laced root system $\Phi$ of rank $\geq 3$, a local ring $A$ and any $1 \leq m \leq n$ the relation $\text{R3}_{n,m}^\bot$ follows from $\text{R1}_n$, $\text{R2}_{n,0}$, $\text{R2}_{m,0}$ and $\text{R2}_{n-m,m}$ and $\text{R3}_{n-m, 0}^\bot$.
-\end{lemma}
-\begin{proof}
-We need to show that $[x_{\alpha}(cX^{n}), x_{\beta}(dX^{m})] = 1$ for all $c, d\in A$, $\alpha \perp \beta$.
-Notice that in the special case $c = \epsilon \in A^*$ the assertion follows from a consideration of \cite[Fig.~4]{KS99} in which one substitutes $a = \epsilon^{-1} d \cdot X^{-(n-m)}$, $b = \epsilon X^{-m}$, $c = 1$.
-
-Now if $c \in M$ we can express it as a difference $c = \epsilon_1 - \epsilon_2$ of two invertible elements.
-The required assertion now follows from $\text{R1}_{n}$, the standard commutator identity $[ab, c] = {}^a[b, c] [a, c]$ and the just considered case.
-\end{proof}
-
-\begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
- = [x_{-\beta}(b'X^{-1}), {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$3_1$ for sharp angles}\\
- = [[x_{-\beta-\gamma}(b''), x_\gamma(X^{-1})], {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
- = [x_{-\beta-\gamma}(b''), [x_\gamma(X^{-1}), x_{\alpha+\beta}(1)]] & \text{ by R$3_0$}\\
- = x_{\alpha}(b'''X^{-1}) & \text{ by R$2_1$.} \end{align*}
-
-\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
- = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
- = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
- = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
- = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
-
-\include{rehmann}
 \end{comment}

### 2019-08-05 dl-paper.tex
Minor fix
Started proof of Horrocks theorem

@@
 
-Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (and also of $R$).
-We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from~\cref{lem:lemma32}.
-\begin{lemma} For $v\in \overline{V}$ and any $g \in \St(\Phi, R, I)$ holds $\overline{p}(t(g) \cdot v) = \mu_R(g) \cdot \overline{p}(v)$. \end{lemma}
-\begin{proof} First of all, notice that the assertion of the lemma can be verified by direct computation using~\eqref{T_1} and~\eqref{T_leq0} in the cases $g = z_\alpha(f, a)$ or $g = z_\alpha(X^2f, aX^{-1})$ for all $a\in A$, $f\in M[X]$.
-Notice that in both cases $g$ is contained in the image of $\St(\Phi, B, I)$, therefore $t$ acts identically on it.
-
-It suffices to verify the assertion of the lemma for the generators $g = z_\alpha(f, \xi)$ of $\St(\Phi, R, I)$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
-induction on the degree of $\xi$ in $X$. The base of induction is clear by the above observation.
-
-Now, suppose that the assertion holds for all $g = z_\alpha(f, \xi)$ in which $\xi$ has degree $\leq n$.
-Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} and using the definition of $t$ we obtain the following equality in $\St(\Phi, B)$ (in which $\epsilon = N_{\alpha, \beta}$):
+\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
+We retain notation of the previous subsection and assume additionally that the map $\St(\Phi, B) \to \St(\Phi, R)$ is injective.
+This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
+%Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (it is also an ideal of $R$).
+Notice that by~\cref{lem:lemma32} the subgroup $\overline{G}^{\geq 0}_M$ is contained in $\St(\Phi, B)$.
+
+%We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from.
+\begin{lemma} For $v\in \overline{V}$ and any $g \in \overline{G}^{\geq 0}_M$ holds $\overline{p}(g \cdot v) = g \cdot \overline{p}(v)$. \end{lemma}
+\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $g = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
+Using~\cref{SR:additivity} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $g = z_\alpha(X^2f, aX^{-1})$.
+
+It suffices to verify the assertion of the lemma for the generators $g = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
+induction on the degree of $\xi$ in $X$. The base of induction is clear.
+
+Suppose that the assertion holds for all $g = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, B)$:
 \begin{multline*}
- t(z_{\alpha+\beta}(f, X\xi)) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot t(z_\alpha(-\epsilon Xf, -\epsilon \xi)) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}).
+ z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}),\text{ where $\epsilon = N_{\alpha, \beta}$.}
 \end{multline*}
-By inductive assumption the assertion of the lemma holds for all the factors in the right-hand side, therefore it also holds for  $z_\alpha(f, X\xi)$.
-From this it is not hard to deduce the assertion for $g = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
-\end{proof}
-
-\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
-\end{comment}
+From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds holds for $g = z_\alpha(f, X\xi)$.
+It is easy to deduce from this that the assertion also holds for $g = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
+\end{proof}
+
+\begin{theorem}
+ Suppose that $\Phi$ is as in the statement of~\cref{lemma33}. Then the map $j_+\colon \St(\Phi, A[X]) \to \St(\Phi, R)$ is injective.
+
+ Suppose, moreover, that $\St(\Phi, B) \to \St(\Phi, R)$ is injective. Then the following square is a pullback square in which all arrows are injective
+ \begin{equation} \nonumber
+  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R).}
+ \end{equation}
+\end{theorem}
+\begin{proof}
+
+\end{proof}
 

### 2019-08-06 dl-paper.tex
Minor fix
Proving P1-glueing

@@
 
-\section{Proof of the second part of the injectivity theorem}
+\section{Proof of the main result}
 \subsection{Presentation of Steinberg groups by homogeneous generators}
@@
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
-Let $A$ be a local ring with maximal ideal $M$.
+Let $A$ be a local ring with maximal ideal $M$ and residue field $k$.
 As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.
@@
 
-\begin{prop} 
+\begin{prop} \label{prop43}
 For $\Phi$ as in the statement of~\cref{lemma33}.
@@
 \begin{theorem}
- Suppose that $\Phi$ is as in the statement of~\cref{lemma33}. Then the map $j_+\colon \St(\Phi, A[X]) \to \St(\Phi, R)$ is injective.
-
- Suppose, moreover, that $\St(\Phi, B) \to \St(\Phi, R)$ is injective. Then the following square is a pullback square in which all arrows are injective
+ If $\Phi$ is as in the statement of~\cref{lemma33}, then the map $j_-$ is injective.
+ If, moreover, $\St(\Phi, A[X]) \to \St(\Phi, B)$ is injective, then the following square is pullback
  \begin{equation} \nonumber
@@
 \begin{proof}
-
+ Let us show that $j_-$ is injective. Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_-)$.
+ By~\cref{prop43} holds $v_0 = j_-(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g=1$.
+
+ Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_-)$.
+From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
+Dividing $g_+$ and $g_-$ by $g_0$ we can achieve
 \end{proof}

### 2019-08-08 dl-paper.tex
Fixes

@@
 
-\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
-\begin{proof} Follows from consideration of the following commutative diagram:
+\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
+Moreover, the intersection of images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.
+\end{corollary}
+\begin{proof} The first assertion follows from consideration of the following commutative diagram:
 \[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
                \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}]),} \]
-in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}
+in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}.
+
+Let us verify the second assertion. Let $g$ be an element of the intersection of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$.
+Clearly, the image of $g$ in $G(\Phi, k[X, X\inv])$ lies in $G(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[t]) = \K_2(\Phi, k)$.
+Thus, we conclude that $g \in \St(\Phi, k)$.
+\end{proof}
 
@@
 This action satisfies the following additional property.
-If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_-(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_-(h_1) \cdot v) = \overline{1}$.
+If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_B(h_1) \cdot v) = \overline{1}$.
+Here $j_B$ denotes the obvious map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$.
 \end{prop}
@@
 \subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
-We retain notation of the previous subsection and assume additionally that the map $\St(\Phi, B) \to \St(\Phi, R)$ is injective.
+We retain notation of the previous subsection and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective.
 This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
@@
 \begin{theorem}
- If $\Phi$ is as in the statement of~\cref{lemma33}, then the map $j_-$ is injective.
- If, moreover, $\St(\Phi, A[X]) \to \St(\Phi, B)$ is injective, then the following square is pullback
+ Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
+ %Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
+ Then the map $j_-$ is injective and the following commutative square is pullback
  \begin{equation} \nonumber
-  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R).}
+  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]).}
  \end{equation}
@@
 \begin{proof}
- Let us show that $j_-$ is injective. Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_-)$.
- By~\cref{prop43} holds $v_0 = j_-(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g=1$.
+ Since $j_- = j_R j_B$, where $j_B$ is as in~\cref{prop43}, it suffices to show that $j_B$ is injective.
+ Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
+ By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g = 1$.
 
@@
 From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
-Dividing $g_+$ and $g_-$ by $g_0$ we can achieve
+ Set $g_+' = g_+g_0^{-1}$ and $g_-' = g_-g_0^{-1}$.
+ %Clearly, $g_+' \in \overline{\St}(\Phi, A[X], M[X])$. Set $v = () $
 \end{proof}
@@
 \printbibliography
-
 \end{document}

### 2019-08-13 dl-paper.tex
Added V_T, finished proof of main result

@@
 We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$.
+
 Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
@@
 We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ sending each $(g, [h], u) \in V$ to the left coset $p(g, h, u)G_M^0$.
+The set $\overline{V}$ is the one upon which we will construct an action of $\St(\Phi, B)$.
+
+Before we proceed further let us explain how our sets $V$ and $\overline{V}$ compare with the constructions used by Tulenbaev in his proof of~\cite[Proposition~4.3]{Tu83}.
+This may also help to explain the intuition behind our definition of $\overline{V}$.
+Recall that Tulenbaev constructs an action of $\St(\Phi, B)$ (of course, only for $\Phi = \rA_\ell$) on a different set, which we denote by $\overline{V}_T$.
+This set $\overline{V}_T$ is defined as the quotient of the set of triples $V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times$ modulo the equivalence relation given by $(p \gamma, h, u) \sim (p, \gamma h, u)$, $\gamma \in G^0_M$.
+Tulenbaev denotes the image of $(p, h, u)$ in $\overline{V}_T$ by $[p, h, u]$.
+
+The isomorphism between the sets $\overline{V}$ and $\overline{V}_T$ is given by the following two maps:
+\begin{equation} \label{eq:VVT} \xymatrix @R0.3pc {\overline{V} \ar[r]^{\cong} & \ar[l] \overline{V}_T \\ (g, [h], u) \ar@{|->}[r] & [p(g, h, u), h^{-1}, u] \\ (p \cdot j_-(h) \cdot \{u, X\}, [h^{-1}], u) & \ar@{|->}[l] [p, h, u].
+} \end{equation}
+It is easy to see that these two maps are mutually inverse.
+This isomorphism allows us to treat these two sets as more or less the same object.
+In certain situations, however, it is preferable to work with one of them rather than the other.
+For example, specifying the action of $\St(\Phi, B)$ in terms of $\overline{V}$ leads to much shorter calculations in Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1}, while the statements of~\cref{sec:P1glueing} look more natural when stated for~$\overline{V}_T$.
+
+Now we are ready to proceed with the construction of the action of $\St(\Phi, B)$ on $\overline{V}$.
 
@@
 We are ready to formulate the main result of this subsection.
-
 \begin{prop} \label{prop43}
 For $\Phi$ as in the statement of~\cref{lemma33}.
-the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.
+the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V} \cong \overline{V}$.
 
 This action satisfies the following additional property.
-If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_B(h_1) \cdot v) = \overline{1}$.
-Here $j_B$ denotes the obvious map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$.
+For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (here we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
 \end{prop}
@@
 
-\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
+\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
 We retain notation of the previous subsection and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 
 This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
-%Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (it is also an ideal of $R$).
-Notice that by~\cref{lem:lemma32} the subgroup $\overline{G}^{\geq 0}_M$ is contained in $\St(\Phi, B)$.
-
+By~\cref{lem:lemma32} $\St(\Phi, B)$ contains $\overline{G}^{\geq 0}_M$.
 %We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from.
-\begin{lemma} For $v\in \overline{V}$ and any $g \in \overline{G}^{\geq 0}_M$ holds $\overline{p}(g \cdot v) = g \cdot \overline{p}(v)$. \end{lemma}
-\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $g = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
-Using~\cref{SR:additivity} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $g = z_\alpha(X^2f, aX^{-1})$.
-
-It suffices to verify the assertion of the lemma for the generators $g = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
+\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ holds $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
+\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
+Using~\cref{SR:additivity} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
+
+It suffices to verify the assertion of the lemma for the generators $p_1 = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
 induction on the degree of $\xi$ in $X$. The base of induction is clear.
 
-Suppose that the assertion holds for all $g = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
+Suppose that the assertion holds for all $p_1 = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
 Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, B)$:
@@
 \end{multline*}
-From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds holds for $g = z_\alpha(f, X\xi)$.
-It is easy to deduce from this that the assertion also holds for $g = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
+From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds holds for $p_1 = z_\alpha(f, X\xi)$.
+It is easy to deduce from this that the assertion also holds for $p_1 = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
 \end{proof}
@@
 \end{theorem}
-\begin{proof}
- Since $j_- = j_R j_B$, where $j_B$ is as in~\cref{prop43}, it suffices to show that $j_B$ is injective.
- Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
- By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g = 1$.
+\begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B$ is injective.
+ Set $v_0 = [1, 1, 1] \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
+ By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.
 
@@
 From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
- Set $g_+' = g_+g_0^{-1}$ and $g_-' = g_-g_0^{-1}$.
- %Clearly, $g_+' \in \overline{\St}(\Phi, A[X], M[X])$. Set $v = () $
+
+ Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$, $v_0 = (1, [j_-(h_-)], 1)$.
+ It is clear that $h_+ \in \overline{\St}(\Phi, A[X], M[X])$, $h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])$ and that $j_-(h_-) = j_+(h_+)$.
+ From~\cref{prop43} and~\cref{lem:action} we obtain that
+ \[ [j_-(h_+), h_-, 1] = j_B^+(h_+) \cdot [1, h_-, 1] = j_B^-(h_-) j_B^+(h_+) \cdot [1, 1, 1] = [1, 1, 1], \]
+ from which it follows that $h_-$ (and hence $h_+$) come from some element of $G_M^0$.
  \end{proof}

### 2019-08-13 dl-paper.tex
Fixed some errors

@@
 
-The isomorphism between the sets $\overline{V}$ and $\overline{V}_T$ is given by the following two maps:
+The isomorphism between the sets $\overline{V}$ and $\overline{V}_T$ is given by the following two maps, which are easily seen to be mutually inverse to each other:
 \begin{equation} \label{eq:VVT} \xymatrix @R0.3pc {\overline{V} \ar[r]^{\cong} & \ar[l] \overline{V}_T \\ (g, [h], u) \ar@{|->}[r] & [p(g, h, u), h^{-1}, u] \\ (p \cdot j_-(h) \cdot \{u, X\}, [h^{-1}], u) & \ar@{|->}[l] [p, h, u].
 } \end{equation}
-It is easy to see that these two maps are mutually inverse.
-This isomorphism allows us to treat these two sets as more or less the same object.
-In certain situations, however, it is preferable to work with one of them rather than the other.
-For example, specifying the action of $\St(\Phi, B)$ in terms of $\overline{V}$ leads to much shorter calculations in Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1}, while the statements of~\cref{sec:P1glueing} look more natural when stated for~$\overline{V}_T$.
+The above isomorphism allows us to treat $\overline{V}$ and $\overline{V}_T$ as a single object, for which we can interchangeably use either of the two notations,
+ depending on which of them is more convenient in a given situation.
+For example, specifying the action of $\St(\Phi, B)$ in terms of $\overline{V}$ leads to much shorter calculations in Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1},
+ while the statements of~\cref{sec:P1glueing} look more natural when formulated for~$\overline{V}_T$.
 
@@
 For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
-\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, [h], u) = (x_\alpha(a + Xf) \cdot g, [h], u).  \end{equation}
+\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, [h], u) = (x_\alpha(a + Xf) \cdot g, [h \cdot x_{\alpha}(-a)], u).  \end{equation}
 It is easy to see that this definition is correct.
@@
  \begin{multline} \nonumber
- h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
- = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
- h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
+ h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
+ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
+\qedhere
 \end{multline}
@@
 
-We are ready to formulate the main result of this subsection.
+We are ready to prove the main result of this subsection.
 \begin{prop} \label{prop43}
 For $\Phi$ as in the statement of~\cref{lemma33}.
-the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V} \cong \overline{V}$.
+the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.
 
 This action satisfies the following additional property.
-For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (here we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
+For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
 \end{prop}
@@
 \end{multline*}
-From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds holds for $p_1 = z_\alpha(f, X\xi)$.
+From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds  for $p_1 = z_\alpha(f, X\xi)$.
 It is easy to deduce from this that the assertion also holds for $p_1 = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
@@
  Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
- %Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
+ Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
  Then the map $j_-$ is injective and the following commutative square is pullback

### 2019-08-13 dl-paper.tex
Some fixes

@@
 
-\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
+%\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
+\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
@@
 For example, specifying the action of $\St(\Phi, B)$ in terms of $\overline{V}$ leads to much shorter calculations in Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1},
- while the statements of~\cref{sec:P1glueing} look more natural when formulated for~$\overline{V}_T$.
+ while the statements of~\cref{prop43} and~\cref{lem:action} are more natural when expressed in terms of~$\overline{V}_T$.
 
@@
 
-We are ready to prove the main result of this subsection.
 \begin{prop} \label{prop43}
@@
 
-\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
-We retain notation of the previous subsection and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 
+For the rest of this section we assume that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 
 This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
-By~\cref{lem:lemma32} $\St(\Phi, B)$ contains $\overline{G}^{\geq 0}_M$.
+Being considered in this way $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
+This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
+\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, M[X, X\inv]) \ar[r]^(.65){t} & \St(\Phi, B) \ar[d]^{j_R} \\
+   \St(\Phi, A[X]) \ar[rr]^{j_+} & & \St(\Phi, R). } \]
+
 %We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from.
@@
 
+We are ready to prove the key result of this subsection.
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B$ is injective.
+\begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.
  Set $v_0 = [1, 1, 1] \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
@@
  From~\cref{prop43} and~\cref{lem:action} we obtain that
- \[ [j_-(h_+), h_-, 1] = j_B^+(h_+) \cdot [1, h_-, 1] = j_B^-(h_-) j_B^+(h_+) \cdot [1, 1, 1] = [1, 1, 1], \]
- from which it follows that $h_-$ (and hence $h_+$) come from some element of $G_M^0$.
+ \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1]. \]
+ Thus, $h_-$ (and hence $h_+$) come from some element of $G_M^0$, which implies that $g_+$ and $g_-$ are images of some element of $\St(\Phi, A)$.
  \end{proof}

### 2019-08-14 dl-paper.tex
Minor fix

@@
 
-%\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
 \subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
@@
 
-We are ready to prove the key result of this subsection.
+We are ready to prove the key result of this section.
 \begin{theorem}
@@
 
- Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$, $v_0 = (1, [j_-(h_-)], 1)$.
- It is clear that $h_+ \in \overline{\St}(\Phi, A[X], M[X])$, $h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])$ and that $j_-(h_-) = j_+(h_+)$.
+ Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$.
+ It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]), h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
  From~\cref{prop43} and~\cref{lem:action} we obtain that

### 2019-08-14 dl-paper.tex
Minor

@@
 \section{Proof of the main result}
+The main result of this section is~\cref{thm:P1glueing}.
+The proof of this theorem is rather long and technical, so before setting out technical details, we briefly describe its main steps which closely follow~\cite{Tu83}.
+
+The object playing a key role in the proof of~\cref{thm:P1glueing} is an action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$.
+To be able to write an explicit formula for this action we need two major ingredients.
+The first one is a presentation of $G$, which involves fewer generations and relations.
+We obtain this presentation in~\cref{lemma33}, which can be considered as a generalization of~\cite[Lemma~3.3]{Tu83}.
+
 \subsection{Presentation of Steinberg groups by homogeneous generators}
@@
 
-We are ready to prove the key result of this section.
-\begin{theorem}
+We are ready to prove our main result.
+\begin{theorem} \label{thm:P1glueing}
  Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.

### 2019-08-14 dl-paper.tex
Minor

--- 2019-08-14 dl-paper.tex
@@
 \section{Proof of the main result}
+The main result of this section is~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+The proof of this theorem is rather long and technical, so before setting out technical details, we briefly describe the main steps of this proof.
+
+The object playing a key role in the proof of~\cref{thm:P1glueing} is a certain action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$.
+To be able to write an explicit formula for this action we need two major ingredients.
+The first one is a presentation of $G$, which involves much fewer generations and relations.
+We obtain this presentation in~\cref{lemma33}.
+The other ingredient are the subgroups $P_\alpha(0)$ of $\St(\Phi, A[X, X\inv])$, whose definition and properties are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
+
 \subsection{Presentation of Steinberg groups by homogeneous generators}
@@
 
+The following proposition is the main result of this subsection and also a direct generalization of~\cite[Lemma~3.3]{Tu83}.
 \begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
@@
 
-\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} 
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} \label{sec:Pa0-basic}
 For a root system $\Phi$ consider the following subsets of $\Phi$:
@@
 
-\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
+\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties} \label{sec:Pa0-Steinberg}
 Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
@@
 We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
-
 Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
@@
 For example, specifying the action of $\St(\Phi, B)$ in terms of $\overline{V}$ leads to much shorter calculations in Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1},
- while the statements of~\cref{prop43} and~\cref{lem:action} are more natural when expressed in terms of~$\overline{V}_T$.
+ while the statements of~\cref{prop43} and~\cref{lem:action} look more natural when formulated in terms of~$\overline{V}_T$.
 
 Now we are ready to proceed with the construction of the action of $\St(\Phi, B)$ on $\overline{V}$.
-
 We start by defining for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.

### 2019-08-15 dl-paper.tex
Changed style of external theorems; added VZ preprint

@@
 \newtheorem{corollary}[lemma]{Corollary}
+\newtheorem{externaltheorem}[lemma]{Theorem}
 \theoremstyle{remark}
@@
 \numberwithin{corollary}{section}
+\numberwithin{externaltheorem}{section}
 \newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
@@
 We conclude this subsection with the following stability result (see~\cite[Theorem~9.4]{Pa89}).
-\begin{theorem*}[Panin] \label{lem:Panin-stability}
+\begin{externaltheorem}[Panin] \label{Panin-stability}
  Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these three cases, respectively.
  Then the stability map $\KO_i(2n, R) \to \KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
- and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem*}
+ and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{externaltheorem}
 
@@
  \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-In view of Panin stability theorem the map $f'$ is precisely the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+By~\cref{Panin-stability} theorem the map $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
 By Bass fundamental theorem $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
@@
 
-We will also need the following property of relative Steinberg groups which is a special case of {\it ``Tulenbayev lifting property''} discussed in~\cite[\S~2]{LS17}.
+We will also need the following property of relative Steinberg groups which is a special case of a more general property discussed in~\cite[\S~2]{LS17}.
 \begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
@@
  Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.
- In the general case the assertion of the lemma is a corollary of amalgamation theorem~\cite[Theorem~9]{S15} 
-  (see~\cite[\S~2]{LS17} for more details).
+ In the general case the assertion of the lemma is a corollary of amalgamation theorem~\cite[Theorem~9]{S15}.
+%  (see~\cite[\S~2]{LS17} for more details).
 \end{proof}
@@
 \end{comment}
-Throughtout this let $\Phi$ is a simply laced root system, $R$ is a commutative ring, and $I, J$ are two its ideals. 
+Throughout this section $\Phi$ denotes a simply laced root system, $R$ a commutative ring, and $I, J$ are two ideals of $R$. 
 We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the map $\St(\Phi, R) \to \St(\Phi, R/I)$.
@@
 
+\subsection{Generators of relative Steinberg groups}
 Denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
@@
 First of all, recall the following two results in which two generating sets for the group $\overline{\St}(\Phi, R, I)$ are described.
-\begin{theorem*}[Stein--Tits--Vaserstein]
- For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
-\end{theorem*} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}. \end{proof}
+\begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+\end{externaltheorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
+\end{proof}
 
@@
 
-\begin{theorem*}[Stepanov] For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group by the subset $\mathcal{Z}(\Sigma_S, R, I)$.
+\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group by the subset $\mathcal{Z}(\Sigma_S, R, I)$.
  Here $\Sigma_S$ denotes the special part of an arbitrary parabolic subset of roots $S \subseteq \Phi$.
-\end{theorem*} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
-
-\begin{rem} For a simply-laced $\Phi$ Stepanov's theorem can be deduced from Stein--Tits-Vaserstein theorem by means of~\cref{Zrels}.
+\end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+
+\begin{rem} For a simply-laced $\Phi$~\cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
 Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
@@
 
-We will need the following variant of Hall--Witt identity:
+For the following lemma we will need the following variant of Hall--Witt identity:
 \begin{equation} \label{HW-variant} [[x, y], z] = \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}.\end{equation}
@@
 The aim of this subsection is to describe a generating set for the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
-induced by the ring homomorphism of evaluation at $0$. Denote this kernel by $K(A[X], M[X])$.
+induced by the ring homomorphism of evaluation at $0$. We denote this kernel by $K(A[X], M[X])$.
 
@@
 
-\begin{theorem*}[Stein] One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem*} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}
+\begin{externaltheorem}[Stein] \label{thm:Stein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+\end{proof}
 
@@
 The main result of this section is~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}. 
-The proof of this theorem is rather long and technical, so before setting out technical details, we briefly describe the main steps of this proof.
-
-The object playing a key role in the proof of~\cref{thm:P1glueing} is a certain action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$.
+The object playing a key role in its proof is a certain action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$ (see the begining of~\cref{sec:P1glueing} for the definition).
 To be able to write an explicit formula for this action we need two major ingredients.
-The first one is a presentation of $G$, which involves much fewer generations and relations.
-We obtain this presentation in~\cref{lemma33}.
-The other ingredient are the subgroups $P_\alpha(0)$ of $\St(\Phi, A[X, X\inv])$, whose definition and properties are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
+The first one is a certain presentation of $G$ involving much fewer generations and relations than the the usual one.
+This presentation is obtained in~\cref{lemma33}.
+The other ingredient are certain subgroups $P_\alpha(0)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
+Their precise definition and immediate properties are given in section~\ref{sec:Pa0-basic}, while the facts about them, which are needed to verify that the action of $G$ satisfies Steinberg relations, are placed in~\cref{sec:Pa0-Steinberg}.
 
@@
  while the degree of a relation of type $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
-%For such a ring $R$ one can assume in the definition of the Steinberg group that the generators $x_\alpha(a)$ and relations R1--R3 are defined only for homogeneous elements.
 
@@
 \begin{rem}
- We needed to exclude relations of type $\text{R3}^\bot$ from the presentation of $\St^{\leq n}(\Phi, B)$ in the proof of the above proposition because already in the case $\Phi=\rD_\ell$ the pair of simple roots $\alpha_{\ell-1}$, $\alpha_{\ell}$ cannot be embedded into a root subsystem of type $\rA_4$.
-
+ The relations of type $\text{R3}^\bot$ were excluded from the presentation of $\St^{\leq n}(\Phi, B)$ in the proof of the above proposition because already in the case $\Phi=\rD_\ell$ the pair of simple roots $\alpha_{\ell-1}$, $\alpha_{\ell}$ cannot be embedded into a root subsystem of type $\rA_4$.
+\end{rem}
+\begin{rem}
  In the special case $M=A$, $B = A[t, t\inv]$ the assertion of the above proposition also holds in the cases $\Phi=\rA_2, \rA_3, \rD_4$.
-This is an easy consequence of the presentation of D.~Allcock applied to the affine Steinberg group $\St(\Phi, A[t, t\inv]) \cong \St(\widetilde{\Phi}^{(1)}, A)$ (Allcock's presentation implies that $\St(\Phi, A[t, t\inv])$ can be presented using only generators and relations of degree $\leq 1$ with respect to both $t$ and $t^{-1}$, see~\cite[Corollary~1.3]{A13}).
+This is an easy consequence of the presentation of D.~Allcock applied to the affine Steinberg group $\St(\Phi, A[t, t\inv]) \cong \St(\widetilde{\Phi}^{(1)}, A)$.
+Allcock's presentation implies that $\St(\Phi, A[t, t\inv])$ can be presented using only generators and relations of degree $\leq 1$ with respect to both $t$ and $t^{-1}$, see~\cite[Corollary~1.3]{A13}.
 

### 2019-08-19 dl-paper.tex
Rewritten stuff

@@
 
-\title{On the presentation of orthogonal groups over polynomial rings}
+\title{A Horrocks-type theorem for orthogonal $K_2$}
 \keywords {Steinberg group, $K_2$-functor, Serre problem
@@
 
+\begin{theorem*} Suppose $A$ is a local ring with maximal ideal $M$. Then for any $\ell \geq 7$ and $2 \in A^*$ the following commutative square is a pullback in which all arrows are injective:
+ \begin{equation} \nonumber
+  \xymatrix{ \St(\rD_\ell, A) \ar[r] \ar[d] & \St(\rD_\ell, A[X]) \ar[d] \\ \St(\rD_\ell, A[X\inv]) \ar[r] & \St(\rD_\ell, A[X, X\inv]).}
+ \end{equation}
+\end{theorem*}
+
 \section{Preliminaries}
-$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
-Our convention for Cartan matrices is 
-$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
+%$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$ Our convention for Cartan matrices is $A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
 
@@
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
-Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ (where $\alpha\in\Phi, s\in R$) and relations:
+Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$
+%(where $\alpha\in\Phi, s\in R$)
+and relations:
 \begin{align}
@@
 Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
- for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced $\Psi\subseteq \Phi$ is well-defined).
+ for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced by the embedding $\Psi\subseteq \Phi$ is well-defined).
 
@@
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In the computations below we use identities~\eqref{eq:simplest} without explicit reference.
+In our computations we will be using the identity~\eqref{eq:simplest} without explicit reference.
 
@@
 \subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
-Notice that our treatment of symbols follows~\cite{DS73}.
+Notice that our notational conventions for symbols follow~\cite{DS73} and not more modern textbooks such as~\cite{Kbook}.
 Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
@@
 \subsection{Relative Steinberg groups and unstable K-groups} \label{sec:quillen}
-In this subsection we recall the definitions and basic facts pertaining to relative Steinberg groups as defined by J.-L.~Loday in~\cite{Lo78}, where a theory of relative central extensions was developed and then applied to the stable Steinberg group $\St(R)$ from algebraic K-theory.
-The main goal of this subsection is to show that Loday's results can be applied to unstable Steinberg groups, and that the resulting relative groups enjoy many good properties of their stable counterparts.
+In this subsection we recall the definitions and basic facts pertaining to the theory of relative extensions developed by J.-L.~Loday in~\cite{Lo78}.
+This theory was applied by J.~Loday to the stable Steinberg group $\St(R)$ from algebraic K-theory.
+The main goal of this subsection is to show that Loday's theory can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy the same good properties as their stable counterparts.
 Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
@@
 
-Now let us give the example of a triple $(G, P, S)$ playing a key role in the present paper.
+Now let us give an example of the triple $(G, P, S)$ playing a key role in the present paper.
 We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively
@@
 \section{Proof of the first part of the injectivity theorem} \label{firstPart}
-We start this section by recalling basic notation and facts pertaining to hermitian K-theory.
-First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}.
+We start this section by recalling basic notation and facts pertaining to Grothendieck--Witt groups.
+%First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}.
 We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
 Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings developed in~\cite{Ka80}.
-We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for the introduction to it.
-
-For our purposes it suffices to restrict attention to the affine case, in which we can consider Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$
- simply as a shorthand for the following groups
+We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to it.
+
+For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following groups:
 \begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
-The groups ${}_{\pm 1}\!U_i(R)$, $\mathrm{KSp}_i(R)$ are defined in~\cite{Ka80} and we will not use their definition. 
-What we need from Grothendieck--Witt groups is the following result due to M.~Schlichting.
+Here the groups $\mathrm{KO}_i(R)$ are the stable analogues of the groups $\KO_i(2n, R)$ considered in the previous chapter.
+Similarly, one can also define the symplectic $K$-groups $\mathrm{KSp}_i(R)$.
+The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition directly.
+
+The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
 \begin{theorem*}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem*}
-\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
+%\begin{proof} This is a very special case of and the remark that follows it. \end{proof}
 We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
@@
 It is obvious that $K(A[X], M[X])$ contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$.
-It turns out that although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described.
+It turns out that, although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described (see~\cref{Kgen} and the corollary that follows it).
+
+It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the double commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups then the resulting assertion becomes a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).
 
@@
  moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
-\begin{lemma} The following decomposition holds
+\begin{lemma} \label{Kdecomp1} The following decomposition holds
  \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}

### 2019-08-19 dl-paper.tex
Writing the introduction

@@
 \begin{document}
+\begin{abstract} We prove an analogue of Horrocks theorem for orthogonal Steinberg groups. \end{abstract}
 \maketitle
@@
 
+The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the achievements of the mathematics of the 70's,
+ which played a significant role in the development of modern algebraic K-theory.
+In its simplest form it asks whether any projective module over a polynomial ring $k[x_1,\ldots, x_n]$ over a field $k$ is free.
+
+We refer the reader to the textbook~\cite{Lam10} for a more complete introduction to the problem and its history.
+
+Numerous analogues of Serre problem have been studied subsequently. For example, A.~Suslin himself solved the so-called $K_1$-analogue of Serre's problem, see~\cite{Su77}.
+His results were generalized by E.~Abe in~\cite{Abe83} and later by A.~Stavrova in~\cite{St-poly}.
+
+There are three main ingredients in the proof of any analogue of Serre's problem: Quillen--Suslin local-global principle, Horrocks theorem, Zariski glueing.
+In~\cite{LS17} the authors have already shown that Steinberg groups $\St(\Phi, R)$ satisfy the local-global principle. In this paper we make another step towards
+ transferring Tulenbayev's result to Steiberg groups and prove the following theorem.
 \begin{theorem*} Suppose $A$ is a local ring with maximal ideal $M$. Then for any $\ell \geq 7$ and $2 \in A^*$ the following commutative square is a pullback in which all arrows are injective:
@@
 \end{theorem*}
+This result should be compared with~\cite[Theorem~1.1]{St-poly}...
+
+The proof of our main result breaks into two parts.
+
+\subsection{Acknowledgements} Theorem 1 is due to the first-named author who acknowledges the financial support of RSCF grant No ???.
+Theorem 2 is due to the second-named author who acknowledges the financial support of GazpromNeft and RFBR grant No ???
+
+The authors would also to express their gratitude to A.~Stavrova for posing the problem and also
+ to A.~Stepanov and N.~Vavilov for many useful comments and also their interest in this work.
 
@@
 For $i\geq 1$ we define the unstable Quillen K-functors $\K_{i}^{G, P}$ via
-\[ \K_i^{G,P}(R) = \pi_i(BG(R)^+_{P(R)}). \]
+\begin{equation} \label{plus-constr} \K_i^{G,P}(R) = \pi_i(BG(R)^+_{P(R)}). \end{equation}
 It is not hard to obtain the following concrete description of these functors in the cases $i=1,2,3$.
@@
 \section{Proof of the first part of the injectivity theorem} \label{firstPart}
-We start this section by recalling basic notation and facts pertaining to Grothendieck--Witt groups.
+We start this section by recalling basic notation and facts pertaining to the theory of Grothendieck--Witt groups.
 %First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}.
@@
 
-For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following groups:
+For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following 4 groups:
 \begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
-Here the groups $\mathrm{KO}_i(R)$ are the stable analogues of the groups $\KO_i(2n, R)$ considered in the previous chapter.
-Similarly, one can also define the symplectic $K$-groups $\mathrm{KSp}_i(R)$.
-The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition directly.
+Here $\mathrm{KO}_i(R)$ denotes the usual orthogonal K-group defined via~\eqref{plus-constr} in which $G(R) = O_\infty(R)$ and $P(R) = [G(R), G(R)]$.
+Replacing the stable orthogonal group with the stable symplectic group one can also define the symplectic $K$-groups $\mathrm{KSp}_i(R)$.
+We refer the reader to~\cite{Ka80} for the definition and properties of the groups ${}_{\pm 1}\!U_i(R)$.
+We will not directly use the definitions of these groups.
 
 The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
-\begin{theorem*}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
-then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem*}
+\begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
+then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
 %\begin{proof} This is a very special case of and the remark that follows it. \end{proof}
-We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
+We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
 
@@
 By~\cref{Panin-stability} theorem the map $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
-By Bass fundamental theorem $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
+By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
 but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the map $f'$ (and hence $f$) is surjective.
@@
 Let us mention an immediate application of the just proved lemma. 
-First of all, recall the following two results in which two generating sets for the group $\overline{\St}(\Phi, R, I)$ are described.
+First of all, recall the following two results which give two generating sets for the group $\overline{\St}(\Phi, R, I)$.
 \begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
@@
  From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
-It follows from Stein's theorem that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}.
+It follows from~\cref{thm:Stein} that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and hence by~\cref{Z-DS} it is contained in $Z_\alpha(A, M)$.
 Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that

### 2019-08-20 dl-paper.tex
Many minor fixes

@@
 all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$.
-Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
+The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G(\Phi, R)$.
+Several different methods of computing signs of these constants have been proposed in the literature, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
+
+For an additive subgroup $A\subseteq R$ and $\alpha \in \Phi$ we denote by $X_\alpha(A)$ the corresponding {\it root subgroup} of $\St(\Phi, R)$, i.\,e.
+the subgroup generated by all $x_\alpha(a)$, $a \in A$.
 
 Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
- for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced by the embedding $\Psi\subseteq \Phi$ is well-defined).
+ for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the map defined by $x_\alpha(\xi) \mapsto x_\alpha(\xi)$ on the generators yields a well-defined map of groups).
 
@@
 In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta} = N_{\alpha, \beta, 1, 1} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
-Although there is still some degree of freedom in their choice, these constants always must satisfy the relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
+Although there is still some degree of freedom in their choice, they always must satisfy the relations, indicated in the following lemma (cf.~\cite[\S~14]{VP}).
 \begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
 \begin{equation} \label{eq:simplest} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
-If, moreover, $\gamma \in \Phi$ is such that $\alpha,\beta,\gamma$ form a basis of a root subsystem of type $\rA_3$ then holds
+If, moreover, $\gamma \in \Phi$ is such that $\alpha,\beta,\gamma$ form a basis of a root subsystem of type $\rA_3$ then one has
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In our computations we will be using the identity~\eqref{eq:simplest} without explicit reference.
+In our computations below we will be using identities~\eqref{eq:simplest} without futher reference.
 
@@
 \end{align}
+Here $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$.
 
 \subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
-Notice that our notational conventions for symbols follow~\cite{DS73} and not more modern textbooks such as~\cite{Kbook}.
+Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
 Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
@@
 recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
-\begin{lemma}\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
+\begin{lemma}\label{K2-laurent-field}Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
 \[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ in which} \]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
@@
 We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
-Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings developed in~\cite{Ka80}.
-We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to it.
+Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings (see e.\,g.~\cite{Ka80}).
+We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to Grothendieck--Witt groups.
 
@@
 \begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
-Here $\mathrm{KO}_i(R)$ denotes the usual orthogonal K-group defined via~\eqref{plus-constr} in which $G(R) = O_\infty(R)$ and $P(R) = [G(R), G(R)]$.
-Replacing the stable orthogonal group with the stable symplectic group one can also define the symplectic $K$-groups $\mathrm{KSp}_i(R)$.
-We refer the reader to~\cite{Ka80} for the definition and properties of the groups ${}_{\pm 1}\!U_i(R)$.
-We will not directly use the definitions of these groups.
+Here $\mathrm{KO}_i(R)$ denotes the usual orthogonal K-group defined via~\eqref{plus-constr} with $G(R) = O_\infty(R)$ and $P(R) = [G(R), G(R)]$.
+Replacing the stable orthogonal group with the stable symplectic group one can also define the symplectic K-groups $\mathrm{KSp}_i(R)$.
+We refer the reader to~\cite{Ka80} for the definition and properties of the groups ${}_{\pm 1}\!U_i(R)$. We will not use these definitions directly.
 
@@
 
-It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the double commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups then the resulting assertion becomes a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).
+It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the double commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups, the resulting assertion turns into a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).
 
@@
 \begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.
- Set $v_0 = [1, 1, 1] \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
- By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.
-
- Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_-)$.
- From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
+ Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B)$.
+ By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.
+
+ Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_B^-(g_-) = j_+(g_+)$.
+ From~\cref{field-injectivity} it follows that the image of $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
 

### 2019-08-20 dl-paper.tex
Added 1 more theorme

@@
 In its simplest form it asks whether any projective module over a polynomial ring $k[x_1,\ldots, x_n]$ over a field $k$ is free.
-
 We refer the reader to the textbook~\cite{Lam10} for a more complete introduction to the problem and its history.
@@
 
-There are three main ingredients in the proof of any analogue of Serre's problem: Quillen--Suslin local-global principle, Horrocks theorem, Zariski glueing.
+There are three main ingredients in the proof of the $\K_2$-analogue of Serre's problem. These ingredients are Quillen--Suslin local-global principle, Horrocks theorem, Zariski glueing.
 In~\cite{LS17} the authors have already shown that Steinberg groups $\St(\Phi, R)$ satisfy the local-global principle. In this paper we make another step towards
- transferring Tulenbayev's result to Steiberg groups and prove the following theorem.
-\begin{theorem*} Suppose $A$ is a local ring with maximal ideal $M$. Then for any $\ell \geq 7$ and $2 \in A^*$ the following commutative square is a pullback in which all arrows are injective:
+ transferring Tulenbayev's result to orthogonal Steiberg groups and prove the following theorem (cf.~\cite[Theorem~5.1]{Tu83})
+\begin{theorem}\label{thm:main} Suppose $A$ is a commutative ring in which $2$ is invertible.
+Then for any $\ell \geq 7$ the following commutative square is a pullback in which all arrows are injective:
 \begin{equation} \nonumber
   \xymatrix{ \St(\rD_\ell, A) \ar[r] \ar[d] & \St(\rD_\ell, A[X]) \ar[d] \\ \St(\rD_\ell, A[X\inv]) \ar[r] & \St(\rD_\ell, A[X, X\inv]).}
- \end{equation}
-\end{theorem*}
-This result should be compared with~\cite[Theorem~1.1]{St-poly}...
-
-The proof of our main result breaks into two parts.
-
-\subsection{Acknowledgements} Theorem 1 is due to the first-named author who acknowledges the financial support of RSCF grant No ???.
-Theorem 2 is due to the second-named author who acknowledges the financial support of GazpromNeft and RFBR grant No ???
-
-The authors would also to express their gratitude to A.~Stavrova for posing the problem and also
- to A.~Stepanov and N.~Vavilov for many useful comments and also their interest in this work.
+\end{equation} \end{theorem}
+It is easy to see that in the statement of the above theorem the groups $\St(\rD_\ell, -)$  can be replaced with the groups $\K_2(\rD_\ell, -)$.
+Thus, the above result can be thought of as a direct $\K_2$-analogue of~\cite[Theorem~6.8]{Su82}.
+
+The proof of~\cref{thm:main} goes as follows.
+After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $\St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ comes down to proving injectivity of the following two maps
+\[ \xymatrix{ \St(\rD_\ell, A[X]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv].) }\]
+The injectivity of the second map is obtained in~\cref{thm41}.
+This is the only place in our proof which uses the invertibility of $2$ assumption.
+This result involves some previously known computations with Grothendieck--Witt groups and also the stabilization theorem for the orthogonal K-theory.
+The injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+In the proof of this result we also make explicit many of the details which are left implicit in Tulenbaev's proof.
+
+\subsection{Acknowledgements} Theorem 2 is due to the first-named author who acknowledges the financial support of RSCF grant No ???.
+Theorem 3 is due to the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
+
+The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for many useful comments and also their interest in this work.
 
@@
 
-\section{Proof of the first part of the injectivity theorem} \label{firstPart}
+\section{An injectivity theorem for Steinberg groups} \label{firstPart}
 We start this section by recalling basic notation and facts pertaining to the theory of Grothendieck--Witt groups.
@@
 
-We are ready to prove our main result.
+We are ready for the first main result of this section.
 \begin{theorem} \label{thm:P1glueing}
@@
 
+\begin{proof}[Proof of~\cref{thm:main}]
+ The assertion of the theorem follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
+
+ Now if $g \in \St(\rD_\ell, A[X])$ is such that its image in $\St(\rD_\ell, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\rD_\ell, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
+By the just established local case the images of $g$ in all $\St(\rD_\ell, A_M[X])$ are also trivial hence by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is also trivial.
+
+ The proof of the fact the square of Steinberg groups is pullback is very similar   to the above argument (cf. also with~\cite[Theorem~5.1a]{Tu83}).
+\end{proof}
+
 \printbibliography

### 2019-08-20 dl-paper.tex
Finished sketching the introduction

@@
 
-\title{A Horrocks-type theorem for orthogonal $K_2$}
+\title{A Horrocks-type theorem for even orthogonal $K_2$}
 \keywords {Steinberg group, $K_2$-functor, Serre problem
@@
 \begin{document}
-\begin{abstract} We prove an analogue of Horrocks theorem for orthogonal Steinberg groups. \end{abstract}
+\begin{abstract} We prove an analogue of Horrocks theorem for even-dimensional orthogonal Steinberg groups.
+This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also a $\K_2$-analogue of an earlier result of A.~Suslin and V.~Kopeiko.
+\end{abstract}
 \maketitle
 \section{Introduction}
-
-The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the achievements of the mathematics of the 70's,
- which played a significant role in the development of modern algebraic K-theory.
-In its simplest form it asks whether any projective module over a polynomial ring $k[x_1,\ldots, x_n]$ over a field $k$ is free.
-We refer the reader to the textbook~\cite{Lam10} for a more complete introduction to the problem and its history.
-
-Numerous analogues of Serre problem have been studied subsequently. For example, A.~Suslin himself solved the so-called $K_1$-analogue of Serre's problem, see~\cite{Su77}.
-His results were generalized by E.~Abe in~\cite{Abe83} and later by A.~Stavrova in~\cite{St-poly}.
-
-There are three main ingredients in the proof of the $\K_2$-analogue of Serre's problem. These ingredients are Quillen--Suslin local-global principle, Horrocks theorem, Zariski glueing.
-In~\cite{LS17} the authors have already shown that Steinberg groups $\St(\Phi, R)$ satisfy the local-global principle. In this paper we make another step towards
- transferring Tulenbayev's result to orthogonal Steiberg groups and prove the following theorem (cf.~\cite[Theorem~5.1]{Tu83})
-\begin{theorem}\label{thm:main} Suppose $A$ is a commutative ring in which $2$ is invertible.
-Then for any $\ell \geq 7$ the following commutative square is a pullback in which all arrows are injective:
+The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of modern algebraic K-theory.
+In its weakest form Serre problem asks whether any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
+We refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent affirmative solution.
+
+After the original Serre problem had been solved, numerous analogous statements have drawn the attention of specialists.
+For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
+This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has trivial values on polynomial rings $k[x_1, \ldots x_n]$ over fields for all $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
+Suslin's results were subsequently generalized to $\K_1$-functors modeled on other linear groups (see the definition below).
+For example, for even-dimensional orthogonal groups the corresponding result was obtained by A.~Suslin and V.
+Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
+Recently, A.~Stavrova has obtained probably the most general result in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G/k$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly}).
+
+Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the group $G(\Phi, R)$ called {\it simply-connected Chevalley group} (see~\cite[\S~3]{St71} or~\cite{VP}) and the group $\St(\Phi, R)$ called {\it Steinberg group} (see~\cref{sec:Steinberg-intro} for the definition).
+There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
+The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$ groups modeled on Chevalley group $G(\Phi, -)$:
+\[ \xymatrix{ 1 \ar[r] & \K_2(\Phi, R) \ar[r] & \St(\Phi, R) \ar^{\pi}[r] & G(\Phi, R) \ar[r] & \K_1(\Phi, R) \ar[r] & 1.} \]
+
+One might ask whether any analogue of Serre's problem also exists for the functor $\K_2$ and it turns out that it is indeed so.
+More precisely, in~\cite{Tu83} M.
+Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^M_2(k)$ immediately follows for $\ell \geq 4$.
+While a number of new results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Abe83, St-poly}), little progress has been made for the $\K_2$-analogue since~\cite{Tu83}.
+Currently the conjecture still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+
+In~\cite{LS17} the authors have shown that Steinberg groups $\St(\Phi, R)$ satisfy Quillen--Suslin local-global principle provided $\Phi$ is simply-laced and has rank $\geq 3$.
+This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem.
+The aim of the present article is to make yet another step towards the solution of the problem.
+Our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
+also with~\cite[Theorem~VI.5.2]{Lam10} and~\cite[Theorem~1.1]{St-poly}).
+\begin{theorem}[Horrocks theorem for orthogonal $\K_2$]\label{thm:main} Suppose $A$ is a commutative ring in which $2$ is invertible.
+Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all arrows are injective:
 \begin{equation} \nonumber
   \xymatrix{ \St(\rD_\ell, A) \ar[r] \ar[d] & \St(\rD_\ell, A[X]) \ar[d] \\ \St(\rD_\ell, A[X\inv]) \ar[r] & \St(\rD_\ell, A[X, X\inv]).}  
-\end{equation} \end{theorem}
-It is easy to see that in the statement of the above theorem the groups $\St(\rD_\ell, -)$  can be replaced with the groups $\K_2(\rD_\ell, -)$.
-Thus, the above result can be thought of as a direct $\K_2$-analogue of~\cite[Theorem~6.8]{Su82}.
-
-The proof of~\cref{thm:main} goes as follows.
+\end{equation} 
+Moreover, the same assertion remains true if one replaces the functor $\St(\rD_\ell, -)$ with $\K_2(\rD_\ell, -)$. \end{theorem}
+
+Our proof of~\cref{thm:main} goes as follows.
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
@@
 The injectivity of the second map is obtained in~\cref{thm41}.
-This is the only place in our proof which uses the invertibility of $2$ assumption.
-This result involves some previously known computations with Grothendieck--Witt groups and also the stabilization theorem for the orthogonal K-theory.
+This is the only place in our proof which invokes the assumption that $2$ is invertible.
+The proof of~\cref{thm41} depends on certain computations with Grothendieck--Witt groups and also on the stability theorem for the higher orthogonal K-groups.
 The injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-In the proof of this result we also make explicit many of the details which are left implicit in Tulenbaev's proof.
-
-\subsection{Acknowledgements} Theorem 2 is due to the first-named author who acknowledges the financial support of RSCF grant No ???.
-Theorem 3 is due to the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
-
-The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for many useful comments and also their interest in this work.
+%In the proof of~\cref{thm:P1glueing} we also write explicitly many of the details left implicit in Tulenbaev's paper.
+
+\subsection{Acknowledgements} Theorem 2 is obtained by the first-named author who acknowledges the financial support of RSCF grant No ???.
+Theorem 3 is obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
+
+The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for many useful comments and their interest in this work.
 
@@
 
-\subsection{Steinberg groups}
+\subsection{Steinberg groups} \label{sec:Steinberg-intro}
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
@@
  Now if $g \in \St(\rD_\ell, A[X])$ is such that its image in $\St(\rD_\ell, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\rD_\ell, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
-By the just established local case the images of $g$ in all $\St(\rD_\ell, A_M[X])$ are also trivial hence by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is also trivial.
+By the just established local case the images of $g$ in all $\St(\rD_\ell, A_M[X])$ are also trivial.
+Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
 

### 2019-08-21 dl-paper.tex
Added more citations

@@
 \section{Introduction}
-The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of modern algebraic K-theory.
+The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of modern algebraic K-theory, see~\cite{Su76, Qu76}.
 In its weakest form Serre problem asks whether any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently, A.~Stavrova has obtained probably the most general result in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G/k$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly}).
+Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly} for the result over a field and ~\cite[Corollary~1.2]{St-Ded} for its further generalization to Dedekind domains of arithmetic type).
 
@@
 Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^M_2(k)$ immediately follows for $\ell \geq 4$.
-While a number of new results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Abe83, St-poly}), little progress has been made for the $\K_2$-analogue since~\cite{Tu83}.
+While a number of new results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Abe83, St-poly, St-Ded}), little progress has been made for the $\K_2$-analogue since~\cite{Tu83}.
 Currently the conjecture still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
@@
 
-\subsection{Acknowledgements} Theorem 2 is obtained by the first-named author who acknowledges the financial support of RSCF grant No ???.
-Theorem 3 is obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
+\subsection{Acknowledgements} \cref{thm41} is obtained by the first-named author who acknowledges the financial support of RSCF grant No ???.
+\cref{thm:P1glueing} is obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
 
@@
 We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
-Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings (see e.\,g.~\cite{Ka80}).
+Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings (see~\cite{Ka80}).
 We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to Grothendieck--Witt groups.
@@
 
-\begin{theorem} \label{thm41}
-Suppose that $2 \in A^*$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
-\end{theorem}
+\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^*$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
 \begin{proof}
@@
 In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
-It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ (in fact, $n=2$).
+It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n>1$ (in fact, $n=2$).
 It remains to see that relation~\eqref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
@@
 We are ready for the first main result of this section.
-\begin{theorem} \label{thm:P1glueing}
+\begin{externaltheorem} \label{thm:P1glueing}
  Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
@@
  \end{equation}
-\end{theorem}
+\end{externaltheorem}
 \begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.

### 2019-08-22 dl-paper.tex
Minor fixes
Fixed all problems

@@
 \renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
-\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
 \DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
@@
 In its weakest form Serre problem asks whether any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
-We refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent affirmative solution.
-
-After the original Serre problem had been solved, numerous analogous statements have drawn the attention of specialists.
+We refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
+
+After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see~\cite{Su77, Su82, Abe83, Tu83, Lam10, Das17, St-poly, St-Ded}).
 For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
-This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has trivial values on polynomial rings $k[x_1, \ldots x_n]$ over fields for all $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
+This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_{1,n}(k[x_1, \ldots x_n]) = \K_{1,n}(k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
 Suslin's results were subsequently generalized to $\K_1$-functors modeled on other linear groups (see the definition below).
@@
 More precisely, in~\cite{Tu83} M.
-Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^M_2(k)$ immediately follows for $\ell \geq 4$.
-While a number of new results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Abe83, St-poly, St-Ded}), little progress has been made for the $\K_2$-analogue since~\cite{Tu83}.
+Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^\mathrm{M}_2(k)$ immediately follows for $\ell \geq 4$.
+While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
 Currently the conjecture still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
@@
 This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem.
-The aim of the present article is to make yet another step towards the solution of the problem.
-Our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
+The aim of the present article is to make yet another step towards the solution of the problem, namely  to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups.
+
+Thus, our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
 also with~\cite[Theorem~VI.5.2]{Lam10} and~\cite[Theorem~1.1]{St-poly}).
-\begin{theorem}[Horrocks theorem for orthogonal $\K_2$]\label{thm:main} Suppose $A$ is a commutative ring in which $2$ is invertible.
-Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all arrows are injective:
+\begin{theorem}[Horrocks theorem for orthogonal $\K_2$]\label{thm:main} Let $A$ be a commutative ring in which $2$ is invertible.
+Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all maps are injective:
 \begin{equation} \nonumber
-  \xymatrix{ \St(\rD_\ell, A) \ar[r] \ar[d] & \St(\rD_\ell, A[X]) \ar[d] \\ \St(\rD_\ell, A[X\inv]) \ar[r] & \St(\rD_\ell, A[X, X\inv]).}  
+  \xymatrix{ \KO_2(2\ell, A) \ar[r] \ar[d] & \KO_2(2\ell, A[X]) \ar[d] \\ \KO_2(2\ell, A[X\inv]) \ar[r] & \KO_2(2\ell, A[X, X\inv]).}  
 \end{equation} 
-Moreover, the same assertion remains true if one replaces the functor $\St(\rD_\ell, -)$ with $\K_2(\rD_\ell, -)$. \end{theorem}
-
-Our proof of~\cref{thm:main} goes as follows.
+Moreover, the same assertion holds if one replaces the functor $\KO_2(2\ell, -)$ with $\K_2(\rD_\ell, -)$ or $\St(\rD_\ell, -)$. \end{theorem}
+In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $K_2$-functor (see~\cref{sec:quillen}).
+
+Our proof of~\cref{thm:main} goes as follows. We notice that it suffices to prove the $\St(\rD_\ell, -)$-variant of the theorem, moreover, the proof of the injectivity of
+ $j_+ \colon \St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part of the proof.
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
-Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $\St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ comes down to proving injectivity of the following two maps
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two maps
 \[ \xymatrix{ \St(\rD_\ell, A[X]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv].) }\]
@@
 This is the only place in our proof which invokes the assumption that $2$ is invertible.
-The proof of~\cref{thm41} depends on certain computations with Grothendieck--Witt groups and also on the stability theorem for the higher orthogonal K-groups.
-The injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-%In the proof of~\cref{thm:P1glueing} we also write explicitly many of the details left implicit in Tulenbaev's paper.
+The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain computations with Grothendieck--Witt groups
+(these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
+Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
 
@@
 recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
-\begin{lemma}\label{K2-laurent-field}Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field. Then there is a split exact sequence of abelian groups
+\begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
+Then there is a split exact sequence of abelian groups
 \[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ in which} \]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^* & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^\times & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
@@
 From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
-$G_0 \cap G_1 \subseteq \Ker(\pi_{D_{R, I}})$ and therefore is a central subgroup of $S(D_{R,I})$ by~\ref{req:uce}.
+$G_0 \cap G_1 \subseteq \Ker(\pi_{D_{R, I}})$ hence it is a central subgroup of $S(D_{R,I})$ by~\ref{req:uce}.
 Thus, we have verified the assumptions of~\cite[Proposition~6]{Lo78} which asserts that the map $\mu$ is a universal relative central extension of the coequalizer $\nu = \mathrm{coeq}(d_0, d_1)$.
@@
 Finally, from~\cite[Corollary~5.4]{St71} and~\cite[Theorem~1]{LS17} it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce} for $n \geq 5$.
-We write $\KO_i(2n, R)$ as a shorthand for $\K_i^{G_n, P_n}(R)$.
+We use the notation $\KO_i(2n, R)$ as a shorthand for $\K_i^{G_n, P_n}(R)$.
+
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ is a larger subgroup of $\St(\rD_\ell, R)$ than $\K_2(\rD_\ell, R)$.
+More precisely, from~\cite[157]{Ba74} and Snake lemma it follows that \[\KO_2(2n, R)/\K_2(\rD_n, R) \cong \Ker(\mathrm{Spin}(2n, R) \to \mathrm{SO}(2n, R)) = \mu_2(R).\]
+On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which
+$G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is the elementary subfunctor of $G$.
 %Notice that $\K_2(\rD_n, R) \subset \mathrm{KO}_2(n, R)$.
@@
 For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following 4 groups:
-\begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
+\begin{equation} \label{GW-concrete} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3.
+\end{array}\right.
+\end{equation}
 Here $\mathrm{KO}_i(R)$ denotes the usual orthogonal K-group defined via~\eqref{plus-constr} with $G(R) = O_\infty(R)$ and $P(R) = [G(R), G(R)]$.
@@
 
-Typically, the ideal $M$ from the above definition is precisely the maximal ideal of $A$, however, sometimes (e.\,g. in~\cref{P0-conj-invariant}) we also use the subgroups defined above for $M=A$.
-
-\begin{lemma}\label{P0_normal} The subgroup $P_{\alpha, M}(0)$ is normal in $P_{\alpha, M}(*)$. In particular, there is a short exact sequence, which is split by the map $m \mapsto x_{-\alpha}(mX)$:
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar@{->>}[r]^{p_\alpha} & M^+ \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
+Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
+The only exception to this is~\cref{P0-conj-invariant} where the above subgroups are also used for $M=A$.
+
+\begin{lemma}\label{P0_normal} The subgroup $P_{\alpha, M}(0)$ is normal in $P_{\alpha, M}(*)$.
+In particular, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
+\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
@@
 To obtain the assertion for $P_{\alpha, M}(0)$ consider the following commutative diagram.
-\[ \xymatrix{ P_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & P_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & M^+ \ar@{^{(}->}[d] \\ P_{\alpha, A}(0) \ar@{^{(}->}[r] & P_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & A^+} \]
+\[ \xymatrix{ P_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & P_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & (M, +) \ar@{^{(}->}[d] \\ P_{\alpha, A}(0) \ar@{^{(}->}[r] & P_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & (A, +)} \]
 Notice that $x_\beta(b) \in P_{\alpha, A}(0)$ therefore for $g \in P_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
@@
 \begin{proof}[Proof of~\cref{thm:main}]
- The assertion of the theorem follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
+ Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follows from the assertion for $\St(\rD_\ell, -)$.
+ In turn, the latter assertion follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
 

### 2019-08-22 dl-paper.tex
Minor fixes

@@
 
-Thus, our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
+Our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
 also with~\cite[Theorem~VI.5.2]{Lam10} and~\cite[Theorem~1.1]{St-poly}).
@@
 
-\subsection{Acknowledgements} \cref{thm41} is obtained by the first-named author who acknowledges the financial support of RSCF grant No ???.
-\cref{thm:P1glueing} is obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044
+\subsection{Acknowledgements} \cref{thm41} was obtained by the first-named author who acknowledges the financial support of RSF grant No 17-11-01261.
+\cref{thm:P1glueing} was obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044.
 
@@
 \subsection{Relative Steinberg groups and unstable K-groups} \label{sec:quillen}
-In this subsection we recall the definitions and basic facts pertaining to the theory of relative extensions developed by J.-L.~Loday in~\cite{Lo78}.
+In this subsection we recall the definitions and basic facts pertaining to the theory of relative central extensions developed by J.-L.~Loday in~\cite{Lo78}.
 This theory was applied by J.~Loday to the stable Steinberg group $\St(R)$ from algebraic K-theory.
-The main goal of this subsection is to show that Loday's theory can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy the same good properties as their stable counterparts.
+The main goal of this subsection is to show that Loday's theory also can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy many good properties of their stable counterparts.
 Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
@@
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which
-$G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is the elementary subfunctor of $G$.
+$G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
 %Notice that $\K_2(\rD_n, R) \subset \mathrm{KO}_2(n, R)$.

### 2019-08-23 dl-paper.tex
Fixed small bugs

@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ is a larger subgroup of $\St(\rD_\ell, R)$ than $\K_2(\rD_\ell, R)$.
-More precisely, from~\cite[157]{Ba74} and Snake lemma it follows that \[\KO_2(2n, R)/\K_2(\rD_n, R) \cong \Ker(\mathrm{Spin}(2n, R) \to \mathrm{SO}(2n, R)) = \mu_2(R).\]
-On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which
-$G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
-%Notice that $\K_2(\rD_n, R) \subset \mathrm{KO}_2(n, R)$.
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_\ell, R)$, but the converse is not true.
+On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
 

### 2019-08-27 dl-paper.tex
Minor fixes

@@
 There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$ groups modeled on Chevalley group $G(\Phi, -)$:
+The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$ groups modeled on Chevalley group $G(\Phi, -)$ (see~\cite{St78}).
 \[ \xymatrix{ 1 \ar[r] & \K_2(\Phi, R) \ar[r] & \St(\Phi, R) \ar^{\pi}[r] & G(\Phi, R) \ar[r] & \K_1(\Phi, R) \ar[r] & 1.} \]
@@
 Moreover, the same assertion holds if one replaces the functor $\KO_2(2\ell, -)$ with $\K_2(\rD_\ell, -)$ or $\St(\rD_\ell, -)$. \end{theorem}
-In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $K_2$-functor (see~\cref{sec:quillen}).
+In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $\K_2$-functor (see~\cref{sec:quillen}).
 
@@
 
-\subsection{Acknowledgements} \cref{thm41} was obtained by the first-named author who acknowledges the financial support of RSF grant No 17-11-01261.
-\cref{thm:P1glueing} was obtained by the second-named author who acknowledges the financial support of JSC Gazpromneft and RFBR grant No 18-31-20044.
-
-The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for many useful comments and their interest in this work.
+\subsection{Acknowledgements} 
+\cref{thm41} was obtained with support from RSF grant 19-71-30002,
+ while \cref{thm:P1glueing} was obtained with support from RFBR grant No 18-31-20044.
+The authors of this paper were also supported by ``Native towns'', a social investment program of PJSC ``Gazprom Neft''.
+
+The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
 
@@
 \end{comment}
-The classical Matsumoto theorem (see~\cite[Theorem~5.10]{Ma69}) allows one to compute the group $\K_2(\Phi, R)$ in the special case when $R=k$ is a field.
-More concretely, it asserts that $\K_2(\Phi, k) \cong \K_2^\mathrm{MW}(k)$ provided $\Phi$ is symplectic and  $\K_2(\Phi, k) \cong \K_2^\mathrm{M}(k)$ otherwise.
-In the following lemma we
-recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
+Recall that the classical Matsumoto theorem (see~\cite[Theorem~5.10]{Ma69}) allows one to compute the group $\K_2(\Phi, R)$ in the special case when $R=k$ is a field.
+Using the modern language of Milnor--Witt K-theory (see~\cite{Mo04}) it can be formulated as the following computation:
+\[\K_2(\Phi, k) = \left\{\begin{array}{ll} \K_2^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_2^\mathrm{M}(k) & \text{otherwise.}\end{array}\right. \]
+In the following lemma we recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
 \begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
@@
 Here $I^2(k)$ stands for the second power of the fundamental ideal $I(k)$ in the Witt ring $W(k)$ of $k$.
-Recall that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
+Recall from~\cite{Mo04} that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
 \[ \xymatrix{ \K_1^\mathrm{MW}(k) \ar[r] \ar[d] & I(k) \ar[d] \\ \K_1(k) \ar[r] & I(k)/I^2(k), } \]
@@
 %\begin{proof} This is a very special case of and the remark that follows it. \end{proof}
-We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
+We will use the above theorem only in the special case $k=0$, in which it boils down to an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
 
@@
 \end{align}
-By the degree of a Steinberg relation we mean the maximum of degrees of generators that appear in it.
+By the degree of a Steinberg relation we mean the maximum of degrees of generators that appear in the relation.
 For example, the degree of every relation of type $\text{R2}_{d,e}$ is $\max(d,e,d+e)$ 
@@
       [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
- where $\beta$ is an arbitrary root of $\Phi$ forming a sharp angle with $\alpha$.
+ where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
  Standard argument (cf.~\cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}_n$ does not depend on the choice of $\beta$.

### 2019-08-27 dl-paper.tex
Minor fixes

@@
 
-After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see~\cite{Su77, Su82, Abe83, Tu83, Lam10, Das17, St-poly, St-Ded}).
+After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}).
 For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
@@
 
-\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
+\begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
 Moreover, the intersection of images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.
-\end{corollary}
+\end{lemma}
 \begin{proof} The first assertion follows from consideration of the following commutative diagram:

### 2019-09-02 dl-paper.tex
Restored broken statement
Found some explicit element

@@
 \subsection{Acknowledgements} 
-\cref{thm41} was obtained with support from RSF grant 19-71-30002,
- while \cref{thm:P1glueing} was obtained with support from RFBR grant No 18-31-20044.
 The authors of this paper were also supported by ``Native towns'', a social investment program of PJSC ``Gazprom Neft''.
+The second-named author also acknowledges the financial support of RFBR grant No 18-31-20044.
 
@@
 In this subsection we recall the definitions and basic facts pertaining to the theory of relative central extensions developed by J.-L.~Loday in~\cite{Lo78}.
-This theory was applied by J.~Loday to the stable Steinberg group $\St(R)$ from algebraic K-theory.
+This theory was applied to the stable Steinberg group $\St(R)$ from algebraic K-theory.
 The main goal of this subsection is to show that Loday's theory also can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy many good properties of their stable counterparts.
@@
 The main result of this section is~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}. 
-The object playing a key role in its proof is a certain action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$ (see the begining of~\cref{sec:P1glueing} for the definition).
+The object playing a key role in its proof is a certain action of the group $G\St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$ (see the begining of~\cref{sec:P1glueing} for the definition).
 To be able to write an explicit formula for this action we need two major ingredients.
@@
 
-% \begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
 \begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
@@
 
-\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
+\subsection{Construction of a ''torsor`` for \texorpdfstring{$\St(\Phi, B)$}{St(Ф, B)}.} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
@@
 
-For the rest of this section we assume that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 
-This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
+\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
+We retain the notation of the previous section.
+Throughtout this section we assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective,
+ which allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
 Being considered in this way $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
@@
 
+\begin{rem}
+\begin{comment}
+\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
+
+\begin{multline*}
+ t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
+ = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
+\end{multline*}
+
+This implies that 
+\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
+\end{multline*}
+
+\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
+\end{equation}
+\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
+\end{equation} \end{comment}
+\begin{equation*}
+  \langle a, m \rangle^{-1} \cdot \langle aX^{-1}, mX \rangle [1, 1, 1] = [1, 1, 1+am]
+\end{equation*}
+\end{rem}
+
 \printbibliography

### 2019-09-03 dl-paper.tex
Fixed some issues

@@
 \title{A Horrocks-type theorem for even orthogonal $K_2$}
-\keywords {Steinberg group, $K_2$-functor, Serre problem
- {\em Mathematical Subject Classification (2010):} 19C20}
+\keywords {Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing. {\em Mathematical Subject Classification (2010):} 19C20}
 \author{Andrei Lavrenov}
@@
 \begin{document}
-\begin{abstract} We prove an analogue of Horrocks theorem for even-dimensional orthogonal Steinberg groups.
-This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also a $\K_2$-analogue of an earlier result of A.~Suslin and V.~Kopeiko.
+\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups.
+This result, which is an analogue of Horrocks theorem, transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of an earlier result of A.~Suslin and V.~Kopeiko.
 \end{abstract}
@@
 
-After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}).
+After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see e.\,g.~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}).
 For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
@@
 There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$ groups modeled on Chevalley group $G(\Phi, -)$ (see~\cite{St78}).
+The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$-groups modeled on Chevalley group $G(\Phi, -)$ (see~\cite{St78}).
 \[ \xymatrix{ 1 \ar[r] & \K_2(\Phi, R) \ar[r] & \St(\Phi, R) \ar^{\pi}[r] & G(\Phi, R) \ar[r] & \K_1(\Phi, R) \ar[r] & 1.} \]
 
-One might ask whether any analogue of Serre's problem also exists for the functor $\K_2$ and it turns out that it is indeed so.
+It turns out that an assertion similar to Serre problem also holds for the functor $\K_2$.
 More precisely, in~\cite{Tu83} M.
 Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^\mathrm{M}_2(k)$ immediately follows for $\ell \geq 4$.
+Notice that $\K_2(\rA_\ell, R)$ here is just another notation for the unstable linear K-functor $\K_2(n, R)$.
+
 While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
-Currently the conjecture still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+Currently the problem still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
 
@@
 Our proof of~\cref{thm:main} goes as follows. We notice that it suffices to prove the $\St(\rD_\ell, -)$-variant of the theorem, moreover, the proof of the injectivity of
- $j_+ \colon \St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part of the proof.
+$j_+ \colon \St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part.
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
-Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two maps
-\[ \xymatrix{ \St(\rD_\ell, A[X]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv].) }\]
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two maps:
+\[ \xymatrix{ \St(\rD_\ell, A[X]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\]
 The injectivity of the second map is obtained in~\cref{thm41}.
 This is the only place in our proof which invokes the assumption that $2$ is invertible.
-The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain computations with Grothendieck--Witt groups
-(these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
+The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain basic computations with Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
 Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+This part of the proof is obtained in somewhat greater generality and is applicable Steinberg groups of type $\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
 
@@
 
-The authors would also to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
+The authors would like to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
 
@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_\ell, R)$, but the converse is not true.
-On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ as $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
-
-\begin{comment}
-In the above definition we could have replaced the group $\mathrm{O}_{2n}$ with a different isogeneous form of the orthogonal group, e.\,g. 
- we could have chosen $G_n = \mathrm{SO}_{2n}$ or $G_n = \mathrm{Spin}_{2n}$ and then have defined $P_n$ as its elementary subfunctor.
-Of course, this would change the functors $\K_i(G_n, P_n, -)$ for $i=1,2$ however, as the proof of~\cref{characterization} suggests
- it would not change $\K_3(G_n, P_n, -)$.
-\end{comment}
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_\ell, R)$, but the converse is not generally true.
+On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
 
@@
 We start this section by recalling basic notation and facts pertaining to the theory of Grothendieck--Witt groups.
-%First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}.
-We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
 Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings (see~\cite{Ka80}).
@@
 The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
-\begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
+\begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
@@
 
-\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^*$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
+\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
 \begin{proof}
@@
 The main result of this section is~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}. 
-The object playing a key role in its proof is a certain action of the group $G\St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$ (see the begining of~\cref{sec:P1glueing} for the definition).
+The object playing a key role in its proof is a certain action of the group $G = \St(\Phi, A[X\inv] + M[X])$ on a certain set $\overline{V}$, which is defined in~\cref{sec:V-construction}.
+Later, we will see that $\overline{V}$ is, in fact, a set-theoretic $G$-torsor.
 To be able to write an explicit formula for this action we need two major ingredients.
-The first one is a certain presentation of $G$ involving much fewer generations and relations than the the usual one.
-This presentation is obtained in~\cref{lemma33}.
+The first one is a certain presentation of $G$ involving much fewer generations and relation, see~\cref{lemma33}.
 The other ingredient are certain subgroups $P_\alpha(0)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
@@
 
-\subsection{Construction of a ''torsor`` for \texorpdfstring{$\St(\Phi, B)$}{St(Ф, B)}.} \label{sec:V-construction}
+\subsection{Construction of a torsor for \texorpdfstring{$\St(\Phi, B)$}{St(Ф, B)}.} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
@@
 
+We are ready for the first main result of this subsection.
 \begin{prop} \label{prop43}
@@
 
-This action satisfies the following additional property.
-For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
+This action satisfies the following additional properties.
+\begin{enumerate}
+ \item For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
+ \item If we consider $\St(\Phi, A[X, X\inv])$ as a group with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-groups.
+\end{enumerate}
 \end{prop}
@@
 
-  The second assertion can be verified directly using~\eqref{T_1}, \eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
+  The first property can be verified directly using~\eqref{T_1}, \eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
+The second property can be verified in a similar fashion.
 \end{proof}
@@
 \subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
-We retain the notation of the previous section.
-Throughtout this section we assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective,
- which allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
-Being considered in this way $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
+We retain the notation of the previous section and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 
+Being considered as a subgroup of $\St(\Phi, R)$ the group $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
 This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
@@
 
-We are ready for the first main result of this section.
 \begin{externaltheorem} \label{thm:P1glueing}
@@
 \begin{rem}
+Although we did not use this in our proof, it can be noted that $\overline{V}$ is a (left) $\St(\Phi, B)$-torsor, i.\,e.
+the action of $\St(\Phi, B)$ on $\overline{V}$ is both transitive and faithful.
+The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
 \begin{comment}
@@
 \end{equation} \end{comment}
-\begin{equation*}
-  \langle a, m \rangle^{-1} \cdot \langle aX^{-1}, mX \rangle [1, 1, 1] = [1, 1, 1+am]
-\end{equation*}
-\end{rem}
+The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following computation, which we leave as an exercise:
+\begin{equation*} \langle 1, m \rangle^{-1} \langle X^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+m]. \end{equation*} \end{rem}
 

### 2019-09-03 dl-paper.tex
Fixed some more issues

@@
 In this subsection we recall the definitions and basic facts pertaining to the theory of relative central extensions developed by J.-L.~Loday in~\cite{Lo78}.
-This theory was applied to the stable Steinberg group $\St(R)$ from algebraic K-theory.
-The main goal of this subsection is to show that Loday's theory also can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy many good properties of their stable counterparts.
-Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).
+The main goal of this subsection is to show that Loday's theory also can be applied to unstable Steinberg groups, and that the resulting relative unstable Steinberg groups have many of the good properties of their stable counterparts.
+Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf.
+e.\,g.
+Corollaries 3--4).
 
@@
 A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
-Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ the morphism category $\catname{CRings}^\rightarrow$.
-If a pair $(R, I)$ is such that $R$ is a local ring with maximal ideal $I$, we call such a pair a {\it local pair}.
+Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ to the morphism category $\catname{CRings}^\rightarrow$.
+If a pair $(R, I)$ is such that $R$ is a local ring with maximal ideal $I$, we call such pair a {\it local pair}.
 
@@
 The first one is a certain presentation of $G$ involving much fewer generations and relation, see~\cref{lemma33}.
-The other ingredient are certain subgroups $P_\alpha(0)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
+The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
 Their precise definition and immediate properties are given in section~\ref{sec:Pa0-basic}, while the facts about them, which are needed to verify that the action of $G$ satisfies Steinberg relations, are placed in~\cref{sec:Pa0-Steinberg}.
@@
 We need one more technical definition.
-\begin{df} Denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.\end{df}
+We denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
 
@@
 } \end{equation}
-The above isomorphism allows us to treat $\overline{V}$ and $\overline{V}_T$ as a single object, for which we can interchangeably use either of the two notations,
+The above isomorphism allows us to treat $\overline{V}$ and $\overline{V}_T$ like the same object, for which we can interchangeably use either of the two notations,
  depending on which of them is more convenient in a given situation.
@@
 
+\begin{rem}
+Although we will not need this for our main result, it can be noted that $\overline{V}$ is a left $\St(\Phi, B)$-torsor, i.\,e.
+the action of $\St(\Phi, B)$ on $\overline{V}$ is both transitive and faithful.
+The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
+\begin{comment}
+\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
+
+\begin{multline*}
+ t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
+ = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
+\end{multline*}
+
+This implies that 
+\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
+\end{multline*}
+
+\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
+\end{equation}
+\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
+\end{equation} \end{comment}
+The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following computation, which we leave as an exercise to the reader:
+\begin{equation*} \langle 1, m \rangle^{-1} \langle X^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+m]. \end{equation*} \end{rem}
+
 \begin{externaltheorem} \label{thm:P1glueing}
@@
 
-\begin{rem}
-Although we did not use this in our proof, it can be noted that $\overline{V}$ is a (left) $\St(\Phi, B)$-torsor, i.\,e.
-the action of $\St(\Phi, B)$ on $\overline{V}$ is both transitive and faithful.
-The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
-\begin{comment}
-\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
-
-\begin{multline*}
- t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
- = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
-\end{multline*}
-
-This implies that 
-\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
-\end{multline*}
-
-\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
-\end{equation}
-\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
-\end{equation} \end{comment}
-The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following computation, which we leave as an exercise:
-\begin{equation*} \langle 1, m \rangle^{-1} \langle X^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+m]. \end{equation*} \end{rem}
-
 \printbibliography

### 2019-09-03 dl-paper.tex
Purged all comments

@@
 \section{Preliminaries}
-%$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$ Our convention for Cartan matrices is $A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.
-
 \subsection{Steinberg groups} \label{sec:Steinberg-intro}
 Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
-Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$
-%(where $\alpha\in\Phi, s\in R$)
-and relations:
+Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ and relations:
 \begin{align}
@@
  \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
-%Using~\eqref{eq:conj-h-h} it is easy to verify that \[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}.\] 
 Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced.
@@
 
-\begin{comment}
-Suppose for a moment that $\langle \alpha, \beta \rangle = -1$ and  $\langle \beta, \alpha \rangle = -1$ then
-\[ \{s, t^{-1} \} = \{s,  t^{-1}\}_\alpha = \{t, s^{-1} \}_\beta^{-1} = \{s^{-1}, t\} \]
-In particular, $\{s, s^{-1}\} = \{s, s^{-1}\}^{-1}$ 
-\end{comment}
 Recall that the classical Matsumoto theorem (see~\cite[Theorem~5.10]{Ma69}) allows one to compute the group $\K_2(\Phi, R)$ in the special case when $R=k$ is a field.
@@
  $\mu \colon M\to N$ of $N$-groups satisfying {\it Peiffer identity} $\mu(m) \cdot m' = m m' m^{-1}$. It can be shown that the image of $\mu$ is always
-  a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$. %TODO: There's a problem with the side of the action :(
+  a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$.
 
@@
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
-%\begin{proof} This is a very special case of and the remark that follows it. \end{proof}
 We will use the above theorem only in the special case $k=0$, in which it boils down to an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
@@
 \begin{proof}
-%There is a natural exact sequence:
-% \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & C_S(R, I).} \]
 Writing the starting portion of the homology long exact sequence for the map $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
@@
  In the general case the assertion of the lemma is a corollary of amalgamation theorem~\cite[Theorem~9]{S15}.
-%  (see~\cite[\S~2]{LS17} for more details).
 \end{proof}
@@
 \section{Elementary calculations in relative Steinberg groups}
-\begin{comment}
-Hall-Witt identity
-\[ [[ y^{-1}, x], z] ^ {y^{-1}}  [[ z^{-1}, y], x] ^ {z^{-1}}  [[ x^{-1}, z], y] ^ {x^{-1}} = 1 \]
-\[ [[ y^{-1}, x], z]  \cdot [[ z^{-1}, y], x] ^ {z^{-1}y} \cdot  [[ x^{-1}, z], y] ^ {x^{-1}y} = 1. \]
-\[ [[ z^{-1}, y^{-1}], x] ^ {z^{-1}y^{-1}} \cdot  [[ x^{-1}, z], y^{-1}] ^ {x^{-1}y^{-1}} = [z, [ y, x]] . \]
-\[  . \]
-\end{comment}
 Throughout this section $\Phi$ denotes a simply laced root system, $R$ a commutative ring, and $I, J$ are two ideals of $R$. 
@@
 For the proof we will need the following commutator identities:
-\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
+\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\
  \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}
@@
 [T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
- %= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right)\right], u (1 - am) \right) = \\
  = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
@@
 
-%We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from.
 \begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ holds $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
@@
 The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
-\begin{comment}
-\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
-
-\begin{multline*}
- t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
- = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
-\end{multline*}
-
-This implies that 
-\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
-\end{multline*}
-
-\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
-\end{equation}
-\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
-\end{equation} \end{comment}
 The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following computation, which we leave as an exercise to the reader:

### 2019-09-03 dl-paper.tex
Minor fixes in texorpdfstring

--- 2019-09-03 dl-paper.tex
@@
 
-\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{\texorpdfstring{$\K_2$}{K\texttwoinferior}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
@@
 
-\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} \label{sec:Pa0-basic}
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{P(0)}, \texorpdfstring{$P_\alpha(*)$}{P(*)} and their properties.} \label{sec:Pa0-basic}
 For a root system $\Phi$ consider the following subsets of $\Phi$:
@@
 
-\subsection{Construction of a torsor for \texorpdfstring{$\St(\Phi, B)$}{St(Ф, B)}.} \label{sec:V-construction}
+\subsection{Construction of a torsor for \texorpdfstring{$\St(\Phi, B)$}{St(B)}.} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
@@
 
-\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.} \label{sec:P1glueing}
+\subsection{Proof of the \texorpdfstring{$\mathbb{P}^1$}{P\textonesuperior}-glueing theorem.} \label{sec:P1glueing}
 We retain the notation of the previous section and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 

### 2019-09-04 dl-paper.tex
Added Volkel's master thesis

@@
 \newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, book]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \renewcommand*{\bibfont}{\footnotesize}
@@
 Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^\mathrm{M}_2(k)$ immediately follows for $\ell \geq 4$.
-Notice that $\K_2(\rA_\ell, R)$ here is just another notation for the unstable linear K-functor $\K_2(n, R)$.
+Notice that $\K_2(\rA_\ell, R)$ here is just another notation for the unstable linear functor $\K_2(\ell+1, R)$.
 
 While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
-Currently the problem still remains open for all $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+It has been conjectured by Wendt, see~\cite[Vermutung~6.22]{Vo11} that the $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
 
@@
 
-We are ready for the first main result of this subsection.
+Now we are ready to prove the main result of this subsection.
 \begin{prop} \label{prop43}
@@
 \end{prop}
-\begin{proof}
-  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
+\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
 On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

### 2019-09-04 dl-paper.tex
Minor fixes

@@
 \section{Introduction}
-The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of modern algebraic K-theory, see~\cite{Su76, Qu76}.
+The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of algebraic K-theory, see~\cite{Su76, Qu76}.
 In its weakest form Serre problem asks whether any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
@@
 More precisely, in~\cite{Tu83} M.
-Tulenbaev demonstrates an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^\mathrm{M}_2(k)$ immediately follows for $\ell \geq 4$.
+Tulenbaev demonstrated an ``early stability theorem'' from which the isomorphism $\K_2(\rA_\ell, k[x_1, \ldots x_n]) \cong \K_2(\rA_\ell, k) = \K^\mathrm{M}_2(k)$ follows for $\ell \geq 4$.
 Notice that $\K_2(\rA_\ell, R)$ here is just another notation for the unstable linear functor $\K_2(\ell+1, R)$.
@@
 While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
-It has been conjectured by Wendt, see~\cite[Vermutung~6.22]{Vo11} that the $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+It has been conjectured by M.~Wendt, see~\cite[Vermutung~6.22]{Vo11} that the $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
 
@@
 
+\begin{rem} The above lemma can be considered as the unstable version of~\cite[Lemma~4.1.1]{AF17} (compute~$\mathrm{KSp}_2(k[X, X\inv])$ using~\eqref{GW-concrete} and~\cref{bass-ft} below). \end{rem}
+
 \begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
@@
 To be able to write an explicit formula for this action we need two major ingredients.
-The first one is a certain presentation of $G$ involving much fewer generations and relation, see~\cref{lemma33}.
+The first one is ~\cref{lemma33}, which delivers a presentation of $G$ with much fewer generations and relations than~\eqref{rel:add}-\eqref{rel:CCF}.
 The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
-Their precise definition and immediate properties are given in section~\ref{sec:Pa0-basic}, while the facts about them, which are needed to verify that the action of $G$ satisfies Steinberg relations, are placed in~\cref{sec:Pa0-Steinberg}.
+The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
 

### 2019-09-05 dl-paper.tex
Switchoff showkeys
Minor fixes

--- 2019-09-04 dl-paper.tex
@@
 Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-This part of the proof is obtained in somewhat greater generality and is applicable Steinberg groups of type $\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
+This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced $\Phi$ of rank $\geq 5$.
+%$\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
 
@@
 We start this section by recalling basic notation and facts pertaining to the theory of Grothendieck--Witt groups.
-Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings (see~\cite{Ka80}).
+Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings.
 We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to Grothendieck--Witt groups.
@@
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
-We will use the above theorem only in the special case $k=0$, in which it boils down to an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
+We will need only the special case $k=0$ of the above theorem, in which case it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
 

### 2019-09-05 dl-paper.tex
Some further revisions

@@
 \begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups.
-This result, which is an analogue of Horrocks theorem, transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of an earlier result of A.~Suslin and V.~Kopeiko.
+This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of an earlier result of A.~Suslin and V.~Kopeiko.
 \end{abstract}
@@
 \section{Introduction}
-The solution of the famous Serre problem on projective modules by D.~Quillen and A.~Suslin was one of the brilliant achievements of mathematics of the 70's, which bolstered the development of algebraic K-theory, see~\cite{Su76, Qu76}.
-In its weakest form Serre problem asks whether any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
-We refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
+Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
+The problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and the solution of the problem played an important role in the development of algebraic K-theory.
+We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
 
@@
 
-Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the group $G(\Phi, R)$ called {\it simply-connected Chevalley group} (see~\cite[\S~3]{St71} or~\cite{VP}) and the group $\St(\Phi, R)$ called {\it Steinberg group} (see~\cref{sec:Steinberg-intro} for the definition).
+Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $G(\Phi, R)$ (see~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
 There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1$ and $\K_2$-groups modeled on Chevalley group $G(\Phi, -)$ (see~\cite{St78}).
-\[ \xymatrix{ 1 \ar[r] & \K_2(\Phi, R) \ar[r] & \St(\Phi, R) \ar^{\pi}[r] & G(\Phi, R) \ar[r] & \K_1(\Phi, R) \ar[r] & 1.} \]
+The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on Chevalley group $G(\Phi, -)$, see~\cite{St78}.
 
@@
 This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem.
-The aim of the present article is to make yet another step towards the solution of the problem, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups.
-
-Our main result is the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
+The aim of the present article is to make yet another step towards its solution, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups.
+
+Our main result is, thus, the following theorem, which is the orthogonal analogue of~\cite[Theorem~5.1]{Tu83} and the $\K_2$-analogue of~\cite[Theorem~6.8]{Su82} (cf.
 also with~\cite[Theorem~VI.5.2]{Lam10} and~\cite[Theorem~1.1]{St-poly}).
@@
 
-Our proof of~\cref{thm:main} goes as follows. We notice that it suffices to prove the $\St(\rD_\ell, -)$-variant of the theorem, moreover, the proof of the injectivity of
+The proof of~\cref{thm:main} goes as follows. We notice that it suffices to prove the $\St(\rD_\ell, -)$-variant of the theorem. Moreover, the proof of the injectivity of
 $j_+ \colon \St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part.
@@
 Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced $\Phi$ of rank $\geq 5$.
+This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ of rank $\geq 5$.
 %$\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
@@
 It suffices to verify that the image of every relator $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
-In the special case $\Phi=\rA_{\geq 4}$ this has already been demonstrated by Tulenbayev in~\cite[Lemma~3.3]{Tu83}, so in this case the proof of the proposition is complete.
-We will deduce the assertion in the remaining cases $\Phi=\rD_\ell,\rE_\ell$ from the special case $\Phi=\rA_4$ of Tulenbayev's result.
+In the special case $\Phi=\rA_{\geq 4}$ this has already been demonstrated by Tulenbaev in~\cite[Lemma~3.3]{Tu83}, so in this case the proof of the proposition is complete.
+We will deduce the assertion in the remaining cases $\Phi=\rD_\ell,\rE_\ell$ from the special case $\Phi=\rA_4$ of Tulenbaev's result.
 
@@
 The relation $R$ lies in the image of the left arrow, therefore it comes from some relation $R' \in \mathcal{R}^\Psi_{n+1}$.
-The image of $R'$ in $\St^{\leq n}(\Psi, B)$ under $j_n^\Psi$ is trivial by Tulenbayev's result.
+The image of $R'$ in $\St^{\leq n}(\Psi, B)$ under $j_n^\Psi$ is trivial by Tulenbaev's result.
 But this implies that the image of $R$ under $\widetilde{j}_n^\Phi$ is also trivial and hence that $\widetilde{j}_n^\Phi$ gives rise to the desired map $j_n$.
@@
 
-\begin{lemma} \label{lem:Tulenbayev-formula} 
+\begin{lemma} \label{lem:Tulenbaev-formula} 
 One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
@@
 \] \end{lemma}
-\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
 \end{multline}
@@
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
-              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R) &  } \] 
+              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R). &  } \] 
 We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$.               
-Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
-\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
-
-We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
-This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
-Whenever two triples $v_1, v_2 \in V$ lie in the same orbit we use the notation $v_1 \sim v_2$ and say that they are {\it congruent}.
-The same notation $h_1 \sim h_2$ is also used for the elements of $\St(\Phi, A[X\inv])$ lying in the same left $G^0_M$-coset.
-
-We denote by $\overline{V}$ the set of orbits of the action of $G_M^0$.
-We use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
+Denote by $\overline{V}_T$ the quotient of the set of triples 
+\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \gamma, h, u)_T \sim (p, \gamma h, u)_T$, $\gamma \in G^0_M$.
+We denote the image of $(p, h, u)_T$ in $\overline{V}_T$ by $[p, h, u]$.
+$\overline{V}_T$ is precisely the set upon which M.~Tulenbaev constructs an action of $\St(\Phi, B)$ in~\cite[Proposition~4.3]{Tu83}.
+
+Sometimes it will be more convenient for us to work with another set $\overline{V}$ isomorphic to $\overline{V}_T$.
+Denote by $V$ the subset of $\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times$ consisting of those triples $(g, h, u)$ for which $p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
+
+We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$. This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
+We denote by $\overline{V}$ the set of orbits of this action of $G_M^0$ and use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
+Whenever $v_1, v_2 \in V$ lie in the same $G_M^0$-orbit we use the notation $v_1 \sim v_2$.
 We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ sending each $(g, [h], u) \in V$ to the left coset $p(g, h, u)G_M^0$.
-The set $\overline{V}$ is the one upon which we will construct an action of $\St(\Phi, B)$.
-
-Before we proceed further let us explain how our sets $V$ and $\overline{V}$ compare with the constructions used by Tulenbaev in his proof of~\cite[Proposition~4.3]{Tu83}.
-This may also help to explain the intuition behind our definition of $\overline{V}$.
-Recall that Tulenbaev constructs an action of $\St(\Phi, B)$ (of course, only for $\Phi = \rA_\ell$) on a different set, which we denote by $\overline{V}_T$.
-This set $\overline{V}_T$ is defined as the quotient of the set of triples $V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times$ modulo the equivalence relation given by $(p \gamma, h, u) \sim (p, \gamma h, u)$, $\gamma \in G^0_M$.
-Tulenbaev denotes the image of $(p, h, u)$ in $\overline{V}_T$ by $[p, h, u]$.
 
@@
 } \end{equation}
-The above isomorphism allows us to treat $\overline{V}$ and $\overline{V}_T$ like the same object, for which we can interchangeably use either of the two notations,
+The above isomorphism allows us to regard $\overline{V}$ and $\overline{V}_T$ as one and the same object, for which we can interchangeably use either of the two notations,
  depending on which of them is more convenient in a given situation.
@@
  First of all, let us show that the resulting function is total. 
- Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
+ Fix $v_0 = (g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
- $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.
+ $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$ lying in the same $G_M^0$-orbit as $v_0$.
 
  Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of the representative.
- Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
+ Let $v_1 = (g, h_1, u)$ and $v_2 = (g, h_2, u)$ be two elements of the same $G_M^0$-orbit for which both $p(v_1)$ and $p(v_2)$ belong to $P_\alpha(*)$.
  By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
-  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
+  $p(v_1)^{-1} \cdot p(v_2) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
  By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
@@
  \begin{multline} \nonumber
-  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
-  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
+  t_\alpha(aX^{-1})(v_1) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
+  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(v_2). \qedhere
  \end{multline} \end{proof}
@@
 \end{multline}
+In the last computation notation $h \sim h'$ means that $h$ and $h'$ lie in the same left $G_M^0$-coset.
 If we swapped $(a,\alpha,m)$ with $(b,\beta,m')$, 
@@
 
+From the second property we also immediately obtain the following group factorization.
+\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X] + M[X\inv]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}
+
 \subsection{Proof of the \texorpdfstring{$\mathbb{P}^1$}{P\textonesuperior}-glueing theorem.} \label{sec:P1glueing}

### 2019-09-05 dl-paper.tex
Fixed compilation at arxiv

@@
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
-\usepackage[breaklinks=true,unicode]{hyperref}
-\usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\usepackage[breaklinks=false,unicode]{hyperref}
+\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 \newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, book]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \renewcommand*{\bibfont}{\footnotesize}
@@
 
-\subsection{\texorpdfstring{$\K_2$}{K\texttwoinferior}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{$\K_2$-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
@@
 
-\subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}
+\subsection{Computation of the kernel of the map of evaluation at $0$.}
 For the rest of this subsection $A$ denotes a local ring with maximal ideal $M$.
@@
 
-\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{P(0)}, \texorpdfstring{$P_\alpha(*)$}{P(*)} and their properties.} \label{sec:Pa0-basic}
+\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} \label{sec:Pa0-basic}
 For a root system $\Phi$ consider the following subsets of $\Phi$:
@@
 
-\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties} \label{sec:Pa0-Steinberg}
+\subsection{The subgroups $K(\alpha, \beta)$ and their properties} \label{sec:Pa0-Steinberg}
 Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
@@
 
-\subsection{Construction of a torsor for \texorpdfstring{$\St(\Phi, B)$}{St(B)}.} \label{sec:V-construction}
+\subsection{Construction of a $\St(\Phi, B)$-torsor.} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
@@
 
-\subsection{Proof of the \texorpdfstring{$\mathbb{P}^1$}{P\textonesuperior}-glueing theorem.} \label{sec:P1glueing}
+\subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
 We retain the notation of the previous section and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. 

### 2019-09-09 dl-paper.tex
Fix misprint
Minor

@@
 
-The authors would like to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
+The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
 
@@
 From the second property we also immediately obtain the following group factorization.
-\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X] + M[X\inv]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}
+\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X\inv] + M[X]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}
 

### 2019-09-20 dl-paper.tex
Fix misprint
Minor

@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly} for the result over a field and ~\cite[Corollary~1.2]{St-Ded} for its further generalization to Dedekind domains of arithmetic type).
+Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly}).
+See also \cite[Corollary~1.2]{St-Ded} for the generalization of Abe's result to Dedekind domains of arithmetic type.
 

### 2019-09-20 dl-paper.tex
Minor

@@
 Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
-The problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and the solution of the problem played an important role in the development of algebraic K-theory.
+Thшы problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory.
 We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
@@
 Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two maps:
-\[ \xymatrix{ \St(\rD_\ell, A[X]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\]
+\[ \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\]
 The injectivity of the second map is obtained in~\cref{thm41}.
@@
 Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
-This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ of rank $\geq 5$.
+This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ containing a subsystem of type $\rA_4$.
 %$\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
@@
 x_\alpha(s) \cdot x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
-& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
- x_{i\alpha + j\beta}\left(N_{\alpha,\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
+& [x_\alpha(s), x_\beta(t)] = \prod
+ x_{i\alpha + j\beta}\left(N_{\alpha,\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq-\beta,\ s,t\in R. \label{rel:CCF}
 \end{align}
@@
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In our computations below we will be using identities~\eqref{eq:simplest} without futher reference.
+In our computations below we will be using identities~\eqref{eq:simplest} without further reference.
 
@@
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{h} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
+\[\xymatrixcolsep{5pc}\xymatrix{k^\times \ar[r]^-{h} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
                                                                                       &                                 & \K_2^\mathrm{M}(k(X)),} \]
@@
 Consider now the case when $\Phi$ is symplectic. In this case the assertion of the lemma is just a reformulation of~\cite[Theorem~B]{MR91},
-which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv] \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
-$P(k)$ is the set $k^* \times I_2(k)$ with the group structure given by
+which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv]) \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
+$P(k)$ is the set $k^\times \times I_2(k)$ with the group structure given by
 \[ (u, y) \cdot (v, z) = (uv, y + z - \langle\langle u, v\rangle\rangle).\]
@@
 \begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
-Moreover, the intersection of images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.
+Moreover, the intersection of the images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.
 \end{lemma}
@@
 In this subsection we recall the definitions and basic facts pertaining to the theory of relative central extensions developed by J.-L.~Loday in~\cite{Lo78}.
-The main goal of this subsection is to show that Loday's theory also can be applied to unstable Steinberg groups, and that the resulting relative unstable Steinberg groups have many of the good properties of their stable counterparts.
+The main goal of this subsection is to show that Loday's theory can be applied to unstable Steinberg groups, and that the resulting relative unstable Steinberg groups have many of the properties of their stable counterparts.
 Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf.
@@
 Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ to the morphism category $\catname{CRings}^\rightarrow$.
-If a pair $(R, I)$ is such that $R$ is a local ring with maximal ideal $I$, we call such pair a {\it local pair}.
+If $(R, I)$ is such that $R$ is a local ring with maximal ideal $I$, we call such pair a {\it local pair}.
 
@@
 Our next goal is to obtain a homological interpretation of the group $C(\Phi, R, I)$.
-For doing this we need to recall some additional notation and terminology.
+In order to do this, we need to recall some additional notation and terminology.
 

### 2019-09-20 dl-paper.tex
Minor

@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly}).
-See also \cite[Corollary~1.2]{St-Ded} for the generalization of Abe's result to Dedekind domains of arithmetic type.
+Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
 
@@
 \section{Elementary calculations in relative Steinberg groups}
-Throughout this section $\Phi$ denotes a simply laced root system, $R$ a commutative ring, and $I, J$ are two ideals of $R$. 
+Throughout this section $\Phi$ denotes an irreducible root system of rank $\geq 2$, $R$ a commutative ring, and $I, J$ denote a pair of ideals of $R$.
+Unless stated otherwise we assume $\Phi$ to be simply laced.
 We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the map $\St(\Phi, R) \to \St(\Phi, R/I)$.
@@
 
+For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
+
 Let us mention an immediate application of the just proved lemma.
-First of all, recall the following two results which give two generating sets for the group $\overline{\St}(\Phi, R, I)$.
-\begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+First of all, recall the following two results which deliver two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results apply even if $\Phi$ is not simply laced)
+\begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
 \end{externaltheorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
@@
 
-For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
-
-\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} For arbitrary $\Phi$ of rank $\geq 2$ the group $\overline{\St}(\Phi, R, I)$ is generated as a group by the subset $\mathcal{Z}(\Sigma_S, R, I)$.
- Here $\Sigma_S$ denotes the special part of an arbitrary parabolic subset of roots $S \subseteq \Phi$.
+Recall that a closed subset $S \subseteq \Phi$ is called {\it parabolic} if $S \cup -S = \Phi$.
+Its {\it special part} $\Sigma_S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
+\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
+Let $S \subseteq \Phi$ be a parabolic subset of $\Phi$. Then the group $\overline{\St}(\Phi, R, I)$ is generated by the set $\mathcal{Z}(\Sigma_S, R, I)$.
  \end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
 
-\begin{rem} For a simply-laced $\Phi$~\cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
+\begin{rem} We claim that in the simply-laced case \cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
 Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
@@
 \begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$.
-Direct computation using~\eqref{eq:conj-h-x},\eqref{eq:conj-h-h},\eqref{eq:steinberg},\eqref{eq:dennis-stein},\eqref{eq:symbol-properties} shows that
+Direct computation using~\eqref{eq:conj-h-x}--\eqref{eq:dennis-stein},\eqref{eq:symbol-properties} shows that
  \begin{multline*}

### 2019-09-23 dl-paper.tex
Minor

@@
 Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
- for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the map defined by $x_\alpha(\xi) \mapsto x_\alpha(\xi)$ on the generators yields a well-defined map of groups).
+ for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the mapping $x_\alpha(\xi) \mapsto x_\alpha(\xi)$ yields a group homomorphism $\St(\Psi, R) \to \St(\Phi, R)$).
 
@@
 In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta} = N_{\alpha, \beta, 1, 1} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$.
-Although there is still some degree of freedom in their choice, they always must satisfy the relations, indicated in the following lemma (cf.~\cite[\S~14]{VP}).
+Although there is still some degree of freedom in their choice, they always must satisfy the relations, indicated in the following lemma (cf.
+\cite[\S~14]{VP}).
 \begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item If $\alpha+\beta\in\Phi$, then holds:
+\item If $\alpha+\beta\in\Phi$ then holds:
 \begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
@@
 Let us mention an immediate application of the just proved lemma.
-First of all, recall the following two results which deliver two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results apply even if $\Phi$ is not simply laced)
+First of all, recall the following two results which give two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results are applicable for arbitrary $\Phi$)
 \begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
@@
 
-\begin{rem} We claim that in the simply-laced case \cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
+\begin{rem} We claim that in the simply-laced case the stronger \cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
 Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
@@
 
-For the following lemma we will need the following variant of Hall--Witt identity:
-\begin{equation} \label{HW-variant} [[x, y], z] = \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}.\end{equation}
 \begin{lemma} \label{Crels}
@@
  \begin{enumerate}
- \item \label{C1} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(- st\xi) \cdot x_{\beta+\alpha}(N_{\alpha,\beta}s^2t\xi)$ if $\alpha+\beta \in \Phi$;
- \item \label{C2} $[c_\beta(s, t), x_{\alpha}(\xi)] = x_{\alpha}(st\xi + s^2t^2\xi) \cdot x_{\alpha-\beta}(N_{-\alpha, \beta}st^2\xi)$ if $\alpha-\beta \in \Phi$;  
- \item \label{C3} $[c_\beta(s, t), x_{\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;  
+ \item \label{C1} $[c_\beta(s, t),\ x_{\alpha}(\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta}\cdot s^2t\xi)$ if $\alpha+\beta \in \Phi$;
+ \item \label{C2} $[c_\beta(s, t),\ x_{\alpha}(\xi)] = x_{\alpha}(st\xi + s^2t^2\xi) \cdot x_{\alpha-\beta}(N_{-\alpha, \beta}\cdot st^2\xi)$ if $\alpha-\beta \in \Phi$;  
+ \item \label{C3} $[c_\beta(s, t),\ x_{\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;  
  \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
-  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
+  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
   where $\epsilon = N_{\alpha,\beta}$.
@@
 \begin{proof}
-To verify~\eqref{C1} suppose $\alpha + \beta \in \Phi$ and compute
-\begin{multline} \nonumber [c_{\beta}(s, t), x_{\alpha}(\xi)]  = [x_{\beta}(s), x_{-\beta}(t)] \cdot [x_{-\beta}(t), x_{\beta}(s)\cdot x_{\beta+\alpha}(N_{\alpha, \beta} \cdot s\xi)] = \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t), x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
-
-In the case $\alpha-\beta \in \Phi$ the second assertion directly follows from~\eqref{HW-variant}:
+First of all, notice that the following equalities hold for elements $x,y,z$ of any group:
+\begin{align}
+ [x, yz]^y =& [y^{-1}, x] \cdot [x, z], \label{rel43} \\
+  [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant}
+\end{align}
+
+The first assertion follows from the following computation:
+\begin{multline} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)]  = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] = \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
+
+The second assertion follows directly from~\eqref{HW-variant}:
 \begin{multline} \nonumber
-[[x_\beta(s), x_{-\beta}(t)], x_{\alpha}(\xi)] = \\
-= \left([x_\beta(-s), [ x_{-\beta}(-t), x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot [x_{-\beta}(t), [ x_{\alpha}(-\xi), x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\right)^{x_\beta(-s)} = \\
+[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = \\
+= \left([x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot [x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\right)^{x_\beta(-s)} = \\
 = x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = \\
@@
 
-Finally, the final relation can be verified by the following direct computation, which involves identity $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ and \eqref{HW-variant} with both sides of the equation inverted:
-\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
-= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
-= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
-= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
-= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
-= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
+Finally, the last assertion can be verified via the following direct computation, which uses~\eqref{rel43} and \eqref{HW-variant} (with both sides of the equality inverted):
+\begin{multline} \nonumber [x_{\alpha+\beta}(s),\ x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s),\ [x_{-\alpha}(-\epsilon t),\ x_{-\beta}(\xi)]] = \\ 
+= \left([[x_{\alpha+\beta}(-s),\ x_{-\alpha}(\epsilon t)],\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi),\ x_{\alpha+\beta}(s)],\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)]^{x_{-\alpha}(\epsilon t)} = \\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{-\alpha}(-\epsilon t),\ x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha-\beta}(t\xi)] = \\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
 \end{multline}
@@
  where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
- Standard argument (cf.~\cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}_n$ does not depend on the choice of $\beta$.
+ Standard argument (cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}_n$ does not depend on the choice of $\beta$.
 
@@
 \begin{rem}
- The relations of type $\text{R3}^\bot$ were excluded from the presentation of $\St^{\leq n}(\Phi, B)$ in the proof of the above proposition because already in the case $\Phi=\rD_\ell$ the pair of simple roots $\alpha_{\ell-1}$, $\alpha_{\ell}$ cannot be embedded into a root subsystem of type $\rA_4$.
+ Notice that in the case $\Phi=\rD_\ell$ the pair $\{\alpha_{\ell-1}, \alpha_{\ell}\}$ of orthogonal simple roots cannot be embedded into a root subsystem of type $\rA_4$.
+This explains why we needed to exclude relations $\text{R3}^\bot$ from the presentation of $\St^{\leq n}(\Phi, B)$ in the proof of the above proposition.
 \end{rem}
@@
  In the special case $M=A$, $B = A[t, t\inv]$ the assertion of the above proposition also holds in the cases $\Phi=\rA_2, \rA_3, \rD_4$.
-This is an easy consequence of the presentation of D.~Allcock applied to the affine Steinberg group $\St(\Phi, A[t, t\inv]) \cong \St(\widetilde{\Phi}^{(1)}, A)$.
+This is a consequence of the presentation of D.~Allcock applied to the affine untwisted Steinberg group $\St(\Phi, A[t, t\inv]) \cong \St(\widetilde{\Phi}^{(1)}, A)$.
 Allcock's presentation implies that $\St(\Phi, A[t, t\inv])$ can be presented using only generators and relations of degree $\leq 1$ with respect to both $t$ and $t^{-1}$, see~\cite[Corollary~1.3]{A13}.
@@
 By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
-By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z.
+By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z\@.
 The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 1.

### 2019-09-24 dl-paper.tex
Minor

@@
 the subgroup generated by all $x_\alpha(a)$, $a \in A$.
+We denote by $U(\Phi^+, A)$ (resp. $U(\Phi^-, A)$) the subgroup of $\St(\Phi, R)$ generated by root subgroups $X_\alpha(A)$ corresponding to all positive (resp. negative) roots of $\Phi$.
 
@@
 \subsection{Computation of the kernel of the map of evaluation at $0$.}
-For the rest of this subsection $A$ denotes a local ring with maximal ideal $M$.
+Let $A$ be a local ring with maximal ideal $M$.
 The aim of this subsection is to describe a generating set for the kernel of the map $ev_{X=0}^*\colon\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$
@@
 It is obvious that $K(A[X], M[X])$ contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$.
-It turns out that, although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described (see~\cref{Kgen} and the corollary that follows it).
+It turns out that, although $K(A[X], M[X])$ is generally strictly larger than $\overline{\St}(\Phi, A[X], XM[X])$,
+ it contains very few extra generators, which can all be explicitly described (see~\cref{Kgen} and the corollary that follows it).
 
@@
  Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
  Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
@@
  the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
-\begin{proof} Notice that it follows from~\eqref{eq:conj-h-x} $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
-
-Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]), \St(\Phi, M)]$.
+\begin{proof} From~\eqref{eq:conj-h-x} we obtain that $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
+
+Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]),\ \St(\Phi, M)]$.
 It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
-\[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
+\[ [g,\ h u^+ u^-] = [g,\ h] \cdot [{}^{h}\!g,\ {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
 Since $C_0$ is generated by the above commutators and $\overline{\St}(\Phi, A[X], XM[X])$ is a normal subgroup of $\St(\Phi, A[X])$

### 2019-09-25 dl-paper.tex
Minor

@@
 \newcommand{\catname}[1]{{\normalfont\textbf{#1}}} %Category name
+\newcommand{\myol}[2][3]{{}\mkern#1mu\overline{\mkern-#1mu#2}}
 
@@
 the subgroup generated by all $x_\alpha(a)$, $a \in A$.
-We denote by $U(\Phi^+, A)$ (resp. $U(\Phi^-, A)$) the subgroup of $\St(\Phi, R)$ generated by root subgroups $X_\alpha(A)$ corresponding to all positive (resp. negative) roots of $\Phi$.
 
@@
 It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
-We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^\times$, $v \in R^\times$, $\alpha\in \Phi$.
+We also denote by $\myol{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^\times$, $v \in R^\times$, $\alpha\in \Phi$.
 
@@
 
-Recall that a closed subset $S \subseteq \Phi$ is called {\it parabolic} if $S \cup -S = \Phi$.
-Its {\it special part} $\Sigma_S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
+Recall that a closed root subset $S \subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $S \cup -S = \Phi$ (resp. $S = -S$, resp. $S \cap (-S) = \varnothing$).
+The {\it special part} $\Sigma_S$ of a parabolic subset $S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
 \begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
@@
 \begin{proof}
-First of all, notice that the following equalities hold for elements $x,y,z$ of any group:
+The first assertion follows from the following computation:
+\begin{multline} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)]  = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] = \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
+
+For the proof of the other assertions we will need the following commutator identities:
 \begin{align}
@@
 \end{align}
-
-The first assertion follows from the following computation:
-\begin{multline} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)]  = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] = \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
 
@@
  \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
- Since the subgroup $C_0 = \left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\overline{\St}(\Phi, A, M)$ 
- (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
+ It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$.
+Thus, we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
  which implies the assertion. \qedhere \end{proof}
 
-\begin{externaltheorem}[Stein] \label{thm:Stein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+For a closed root subset $S \subseteq \Phi$ we denote by $U(S, M)$ the subgroup of $\St(\Phi, A)$ generated by root subgroups $X_\alpha(M)$ corresponding to all $\alpha \in S$.
+We denote by $\Phi^+$ (resp.
+$\Phi^-$) the subsets of positive (resp.
+negative) roots of $\Phi$ with respect to some chosen order on $\Phi$.
+
+\begin{externaltheorem}[Stein] \label{thm:Stein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
 \end{proof}
@@
  the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
-\begin{proof} From~\eqref{eq:conj-h-x} we obtain that $\overline{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\overline{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
+\begin{proof} From~\eqref{eq:conj-h-x} we obtain that $\myol{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\myol{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
 
 Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]),\ \St(\Phi, M)]$.
-It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \overline{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \myol{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
 \[ [g,\ h u^+ u^-] = [g,\ h] \cdot [{}^{h}\!g,\ {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
@@
 To be able to write an explicit formula for this action we need two major ingredients.
-The first one is ~\cref{lemma33}, which delivers a presentation of $G$ with much fewer generations and relations than~\eqref{rel:add}-\eqref{rel:CCF}.
-The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$, which are modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
-The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
+The first one is ~\cref{lemma33}, which gives a presentation of $G$ with much fewer generations and relations than in the original presentation~\eqref{rel:add}-\eqref{rel:CCF}.
+The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$ modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
+%The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
 
@@
 It is not hard to show that $\St(\Phi, B)$ can be presented by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations
- between them (below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
+(below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
 \begin{align}
@@
  $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$.
-It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes \hat{U}(Z_+(\alpha), M). \]
+It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes U(Z_+(\alpha), M). \]
 It is clear, that $Z_\alpha(A, M)$ centralizes the root subgroup $X_\alpha(A)$ (cf. \cite[984]{St71}).
 
-For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a root of $\Phi$.
+For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a fixed root of $\Phi$.
 Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.

### 2019-09-25 dl-paper.tex
Minor

@@
 
-It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
-Thus, it remains to show that commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
+It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the commutator subgroup $C_1$ is generated by elements of the form $[x_\alpha(m),\ x_{-\alpha}(X\xi)]^g$, where $m \in M$, $\xi \in A[X]$, $g \in \St(\Phi, A[X])$.
+Thus, it remains to show that commutators $[[x_\alpha(m),\ x_{-\alpha}(X\xi)],\ g]$ belong to $\overline{\St}(\Phi, A[X], XM[X])$.
 Since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a member of some generating set for $\St(\Phi, A[X])$.
@@
 The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$ modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
-%The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
+The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
 
@@
 For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
+We denote by $F(\mathcal{X}^\Phi_{\leq n})$ the free group on $\mathcal{X}^\Phi_{\leq n}$.
 
@@
 \begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
-[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_2 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
- = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_2 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
- = {}^{x_{-\beta}(t^d)} [x_{\gamma}(- bt^e), x_{\alpha+\beta}(-\delta_2 \cdot a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
+[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
+ = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_1 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
+ = {}^{x_{-\beta}(t^d)} [x_{\gamma}(- bt^e), x_{\alpha+\beta}(-\delta_1 \cdot a)] & \text{ by $\text{R2}_{e-d,d}$, $\text{R3}^\angle_{d,e}$} \nonumber \\ 
  = {}^{x_{-\beta}(t^d)} [x_{\beta + \gamma}(\epsilon_1 \cdot bt^{e-d}), x_{\alpha}(at^d)] & \text{ by $\text{R2}_{e,0}$, $\text{R2}_{e-d,d}$} \nonumber \\ 
@@
  = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
- where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha+\beta,\gamma}$, $\delta_2 = N_{\alpha,\beta}$
- and in the fourth equality we use~\eqref{eq:cocycle}.
-
-\item In the case $d \leq 0 \leq e \leq n$ relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
+ where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.
+
+\item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
 \begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
  = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
- = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{e+d-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{d+e-1,1}$,} \end{align*} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
+ = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
+ = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
  \end{enumerate}
@@
 The following proposition is the main result of this subsection and also a direct generalization of~\cite[Lemma~3.3]{Tu83}.
-\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism.
+\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism.
 In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
@@
  We need to construct a map $j_n$ which would be the inverse of $i_n$. 
- We start with a word map $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
- \[ \widetilde{j}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
+ We start with a map $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
+ \[ \widetilde{j}^{\Phi}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
       [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
  where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
- Standard argument (cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}_n$ does not depend on the choice of $\beta$.
+ Standard argument (cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.
 
@@
  Let $R$ be a relation from $\mathcal{R}^\Phi_{n+1}$.
-By~\cref{superfluous-relations} we may assume that $R$ is not of type $\text{R3}^\bot$, hence the roots $\alpha, \beta$ appearing in $R$ are contained in a root subsystem of $\Phi$ of type $\rA_2$.
+By~\cref{superfluous-relations} we may assume that $R$ is not of type $\text{R3}^\bot$, therefore the roots $\alpha, \beta$ appearing in $R$ are contained in a root subsystem of $\Phi$ of type $\rA_2$.
 Our assumptions on $\Phi$ guarantee that there exists some root subsystem $\Psi$ of type $\rA_4$ containing $\alpha$ and $\beta$.

### 2019-09-25 dl-paper.tex
Minor

@@
 
-\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, hence the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
+\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty.
+In particular, if $A$ is a local ring with maximal ideal $M$ the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
 By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^\times$, $m\in M$. \end{rem}
@@
 \begin{df} \label{defP0}
-Let $M$ be an ideal of a local ring $A$. We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
- map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
-\begin{enumerate} \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
+Let $M$ be an ideal of a local ring $A$.
+We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
+\begin{enumerate} \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
  \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
@@
 
-\begin{rem}\label{rem:c-DS} It is easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
-In particular, it contains the relative Dennis--Stein and Steinberg symbols.
-Notice that $P_\alpha(0)$ also contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3). \end{rem}
+\begin{rem}\label{rem:c-DS} Notice that $P_{\alpha, M}(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3).
+It is also easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
+In particular, if $M$ is the maximal ideal of $A$, the subgroup $P_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. \end{rem}
 

### 2019-09-25 dl-paper.tex
Minor

@@
 Let $M$ be an ideal of a local ring $A$.
-We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
+We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five types elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
 \begin{enumerate} \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
@@
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
-The assertion is obvious for the generators of type 3 and 4.
+The assertion is obvious for generators of type 3 and 4.
 
@@
   z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \end{align}
-The expressions in the right hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
+The expressions in the right-hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
 
@@
 The following lemma shows that $P_{\alpha, M}(*)$ is sufficiently large.
-\begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. Then the subgroup $P_\alpha(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by Stepanov theorem $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
+\begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. Then the subgroup $P_{\alpha, M}(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
 The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
@@
 
-\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it consists precisely of images under $j_+$ of the elements 
- $g \in \overline{\St}(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
+\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it conincides with the image under $j_+$ of the subgroup 
+of $\overline{\St}(\Phi, A[X], M[X])$ consisting of those elements $g$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
 
@@
 The assertion is clear for generators of type 3 and 5.
-First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
+First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
 \begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
-Clearly, the expression in the right hand side is a product of generators of type 5, 2, 1.
-
-Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
-Computing the conjugates of these generators using~\cref{Zrels} we obtain that
+Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.
+
+Now consider the case $\alpha - \beta \in \Phi$, which is possible for generators of type 1 and 2.
+By~\cref{Zrels} we obtain that
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \\
@@
 
-Let us verify the assertion for the generator of type 4.
+Let us verify the assertion for a generator of type 4.
 Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 

### 2019-09-26 dl-paper.tex
Minor

@@
 First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
-\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
+\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
 Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.
 
-Now consider the case $\alpha - \beta \in \Phi$, which is possible for generators of type 1 and 2.
-By~\cref{Zrels} we obtain that
+Now consider the case $\alpha - \beta \in \Phi$, which is possible for generators of type 1 and 2. By~\cref{Zrels} we obtain that
 \begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \\

### 2019-09-28 dl-paper.tex
Gave different proof to proposition 5.18

@@
 
-For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
-
 Let us mention an immediate application of the just proved lemma.
@@
 The {\it special part} $\Sigma_S$ of a parabolic subset $S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
+
+For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
 \begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
@@
  \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
-  \[c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\]
+  \begin{equation} \label{eq:C4} c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\end{equation}
   where $\epsilon = N_{\alpha,\beta}$.
@@
 \end{corollary}
-\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
+\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\eqref{eq:C4} we obtain that modulo 
  $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements (as before, $\xi \in A[X]$, $f\in M[X]$):
+\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X], M[X])$ generated by the following five families of elements (below $\xi \in A[X]$, $f\in M[X]$):
  \begin{enumerate}
@@
   \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
-  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
-
-\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$. 
-Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$. 
-In particular, $K(\alpha, \beta)$ does not depend on the choice of the root $\delta$. \end{prop}
-\begin{proof} Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$. 
-Applying Stepanov theorem to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of $z_\gamma(Xf, \xi)$, 
-$\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$. By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 5.
-
- The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
- $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position conjugating by $x_{\epsilon}(mX)$ all factors along the way.
- Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after simplification of these conjugates, so this process is guaranteed to terminate.
- To see this notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-3} 
- (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into them) have terms of degree at least $2$ in $X$.
-
- As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ might transform into factors of the form $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
-We can express each factor $z_\alpha(Xf, X\xi)$ through the generators of $K(\alpha, \beta)$ as follows.
-Pick a root $\gamma \in \Phi\setminus \Psi$ forming an obtuse angle with $\alpha$ and then invoke~\eqref{eq:zalpha}:
- \begin{multline} z_\alpha(Xf, X\xi) = x_{\alpha+\gamma}(\epsilon X^2f) \cdot x_{\gamma}(-X^3 \xi f) \cdot x_{-\gamma}(Xf\xi) \cdot x_\alpha(Xf) \cdot \\ 
- \cdot z_{\alpha+\gamma}(-\epsilon X^2 f, -\epsilon \xi) \cdot z_{-\gamma}(-Xf\xi, -X) \cdot x_{-\alpha-\gamma}(-\epsilon X^2\xi^2 f) \cdot x_{-\alpha}(-X^3 f \xi^2),\ \text{for } \epsilon = N_{\alpha, \gamma}.
-\end{multline}
- The expression in the right-hand side is a product of generators of type 1, 1, 1, 3, 1, 1, 1, 2. Similar argument also applies to $z_\beta(Xf, X\xi)$.
-
- After collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression we obtain the desired decomposition for $g$.
+  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate}
+Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ in $\St(\Phi, A[X, X\inv])$. \end{df}
+
+\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in \widetilde{K}(\alpha, \beta)$.
+Consequently, $K(\alpha, \beta)$ coincides with the intersection $\mathrm{Im}(K(A[X], M[X]) \to \St(\Phi, A[X, X\inv])) \cap P_\alpha(0) \cap P_\beta(0)$.
+In particular, $K(\alpha, \beta)$ does not depend on the choice of the root $\delta$.
+\end{prop}
+\begin{proof} 
+For $i=1..5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
+By~\cref{thm:Stepanov} every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
+In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
+%We are going to rewrite this product so that the generators of $\widetilde{K}(\alpha, \beta)$ accumulate on the left-hand side of this expression, while the elements of the root subgroups $X_{-\alpha}(MX)$ and $X_{-\beta}(MX)$ accumulate on the right-hand side.
+
+By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \St(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
+By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, where $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
+
+Now let us study the structure of the subgroup $\langle \mathcal{G}' \rangle$.
+It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$, $\gamma_1, \gamma_2 \in \Psi$.
+On the other hand, for $\gamma \in \Psi$ any commutator $c_{\gamma}(mX, m'X)$ is congruent to some generator of $\mathcal{G}_5$  modulo $G_0$ (cf.
+the proof of~\cref{Kgen-strong}) and, therefore, commutes with the elements of $\mathcal{G}'$ modulo $G_0$.
+
+Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f', m'$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
+By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after the simplification of these conjugates.
+Thus, we can rewrite $g_2$ as $g_{21} \cdot g_{22}$, where $g_{21} \in \langle \mathcal{G}_2, \mathcal{G}_3, \mathcal{G}_4, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_{22} \in \langle X_{-\alpha}(MX), X_{-\beta}(MX) \rangle = X_{-\alpha}(MX) \cdot X_{-\beta}(MX)$.
+Thus, we have obtained the desired decomposition for $g$.
 

### 2019-09-28 dl-paper.tex
Fix 5.19

@@
 \subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} \label{sec:Pa0-basic}
-For a root system $\Phi$ consider the following subsets of $\Phi$:
+Let $\Phi$ be a root system and $\alpha \in \Phi$ be its element.
+Consider the following subsets of $\Phi$:
 \begin{align} Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X], M[X])$ generated by the following five families of elements (below $\xi \in A[X]$, $f\in M[X]$):
+\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following five families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
  \begin{enumerate}
@@
   \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate}
-Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ in $\St(\Phi, A[X, X\inv])$. \end{df}
+Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}
 
 \begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in \widetilde{K}(\alpha, \beta)$.
-Consequently, $K(\alpha, \beta)$ coincides with the intersection $\mathrm{Im}(K(A[X], M[X]) \to \St(\Phi, A[X, X\inv])) \cap P_\alpha(0) \cap P_\beta(0)$.
+Consequently, $K(\alpha, \beta)$ coincides with the intersection $j_+(K(A[X], M[X])) \cap P_\alpha(0) \cap P_\beta(0)$.
 In particular, $K(\alpha, \beta)$ does not depend on the choice of the root $\delta$.
@@
 \begin{proof} 
-For $i=1..5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
+For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
 By~\cref{thm:Stepanov} every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
 In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
-%We are going to rewrite this product so that the generators of $\widetilde{K}(\alpha, \beta)$ accumulate on the left-hand side of this expression, while the elements of the root subgroups $X_{-\alpha}(MX)$ and $X_{-\beta}(MX)$ accumulate on the right-hand side.
-
-By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \St(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
-By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, where $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
-
-Now let us study the structure of the subgroup $\langle \mathcal{G}' \rangle$.
+
+By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
+By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, for some $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
+
 It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$, $\gamma_1, \gamma_2 \in \Psi$.
 On the other hand, for $\gamma \in \Psi$ any commutator $c_{\gamma}(mX, m'X)$ is congruent to some generator of $\mathcal{G}_5$  modulo $G_0$ (cf.
-the proof of~\cref{Kgen-strong}) and, therefore, commutes with the elements of $\mathcal{G}'$ modulo $G_0$.
+the proof of~\cref{Kgen-strong}) and hence commutes with the elements of $\mathcal{G}'$ modulo $G_0$.
 
 Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f', m'$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
-By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after the simplification of these conjugates.
+By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after simplification of these conjugates.
 Thus, we can rewrite $g_2$ as $g_{21} \cdot g_{22}$, where $g_{21} \in \langle \mathcal{G}_2, \mathcal{G}_3, \mathcal{G}_4, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_{22} \in \langle X_{-\alpha}(MX), X_{-\beta}(MX) \rangle = X_{-\alpha}(MX) \cdot X_{-\beta}(MX)$.
@@
 
-It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
-The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
+It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$.
+The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
 \end{proof}
@@
 
-\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
+\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under conjugation by $x_\alpha(aX^{-1})$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$  generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
 \end{lemma}
 \begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
-By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type Z, Z, 1.
-By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z\@.
-The conjugation by $x_\alpha(aX^{-1})$ fixes both generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 1.
-As for the remaining generators of type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type Z, Z, 5.
+By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1.
+\cref{Crels} also shows that the conjugate to a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
+
+The conjugation by $x_\alpha(aX^{-1})$ fixes both types of generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 4.
+The conjugation also fixes $x_{-\alpha-\beta}(Xf)$ and transforms $x_{\beta-\alpha}(Xf)$ into a product of generators of type 4, Z.
+
+Now pick a root $\gamma \in \Phi \setminus \Psi$ such that $\alpha + \gamma \in \Phi$.
+From~\eqref{eq:Zconj3} in which $\gamma$ is substituted for $\beta$ it follows that  $z_{-\alpha}(X^2f, aX^{-1})$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z\@.
 \end{proof}

### 2019-09-28 dl-paper.tex
Fix 5.20

@@
 \begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
- Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
-  $\gamma = \alpha - \beta$, a contradiction. \end{proof}
+\begin{proof} 
+By the above lemma it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$.
+Let $g = x_{\gamma}(f, X\xi)$ be a generator of $Z_{\alpha, \beta}$.
+Notice that $\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence $\gamma = \alpha - \beta$, a contradiction.
+
+If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}.
+Finally, $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g.
+from Remarks~\ref{Pstar-char}--\ref{rem:palpha}).
+\end{proof}
 

### 2019-09-28 dl-paper.tex
Minor

@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following five families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
+\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
  \begin{enumerate}
@@
 It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$.
-The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
+The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ holds $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
 \end{proof}
@@
 If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}.
-Finally, $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g.
+Finally, if $\gamma = \beta$ the element $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g.
 from Remarks~\ref{Pstar-char}--\ref{rem:palpha}).

### 2019-09-30 dl-paper.tex
Minor

@@
 \begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
-By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1.
-\cref{Crels} also shows that the conjugate to a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
+By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate of a generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1.
+\cref{Crels} also shows that the conjugate of a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
 
@@
 \begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of generators of type 4, 1, 1.
-Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
-By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.
+\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type 4, 1, 1.
+By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type 5 is either $g$ or a product of generators of type 5, 4, 1.
+
+Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
 Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
@@
 
-\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
-\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate of $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
+\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate of each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
 Throughout the proof we understand generator types according to~\cref{defP0}.

### 2019-10-01 dl-paper.tex
Minor

@@
 Recall from~\cite[Lemma~5.2]{Ma69} that the following relations hold for semisimple root elements:
-\begin{align} \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u), \\ \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}.
-\end{align}
+\begin{align} \label{eq:conj-h-x} {}^{h_\alpha(t)}\!x_\beta(u) & = x_\beta(t^{\langle \beta,  \alpha \rangle}u), \\
+              \label{eq:conj-h-h} {}^{h_\alpha(t)}\!h_\beta(u) & = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}, \\
+              \label{eq:h-inv}    h_\alpha(t)^{-1}             & = h_{-\alpha}(t). \end{align}
 Here $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$.
@@
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.
+From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$, which allows us to give the following definition.
 
@@
 Finally, if $\gamma = \beta$ the element $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g.
-from Remarks~\ref{Pstar-char}--\ref{rem:palpha}).
+from~\cref{rem:palpha}).
 \end{proof}
@@
 \begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate of each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
-Throughout the proof we understand generator types according to~\cref{defP0}.
+Throughout this proof we understand generator types according to~\cref{defP0}.
 It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
@@
 In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
-\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{-\alpha + \gamma + \beta} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi.
+\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\beta - \alpha + \gamma} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi).
 \] Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
@@
 Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
-we obtain that $\alpha - \beta + \gamma = \alpha$. Thus, by \eqref{Z3} of~\cref{Zrels}
-\[z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\gamma,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\gamma}(f, X\xi). \]
+we obtain that $\alpha - \beta + \gamma = \alpha$, i.\,e. $\beta=\gamma$. Thus, by \eqref{Z3} of~\cref{Zrels}
+\[z_{\beta}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\beta,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\beta}(f, X\xi). \]
 The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
@@
 \begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
-From the definition of $S_\alpha(a, -)$ we obtain that
+From the definition of $S_\alpha(a, -)$, \cref{lem:Tulenbaev-formula}, \eqref{eq:conj-h-x}, \eqref{eq:h-inv} and~\eqref{eq:dennis-stein} we obtain that
  \begin{multline} \label{eq:SRobtuse-computation}
- S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
+ S_\alpha\left(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)\right) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
  = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
@@
 \end{multline}
-Denote by $h_0$ the product of all terms except the first and the last one in the above formula.
+Denote by $h_0$ the product of all factors in the above formula except the first and the last one.
 It is clear that $h_0$ lies in $P_\alpha(0)$.
@@
 For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
-Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$.
+Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$. Consider the following commutative diagram.
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
@@
 We denote the image of $(p, h, u)_T$ in $\overline{V}_T$ by $[p, h, u]$.
-$\overline{V}_T$ is precisely the set upon which M.~Tulenbaev constructs an action of $\St(\Phi, B)$ in~\cite[Proposition~4.3]{Tu83}.
+$\overline{V}_T$ is precisely the set upon which M.~Tulenbaev in~\cite[Proposition~4.3]{Tu83} constructs an action of $\St(\Phi, B)$.
 
@@
 We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$. This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
-We denote by $\overline{V}$ the set of orbits of this action of $G_M^0$ and use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
+We denote by $\overline{V}$ the set of orbits of this action and use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
 Whenever $v_1, v_2 \in V$ lie in the same $G_M^0$-orbit we use the notation $v_1 \sim v_2$.
@@
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
- $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$ lying in the same $G_M^0$-orbit as $v_0$.
-
- Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of the representative.
+ $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_-(h_0), u)$ lying in the same $G_M^0$-orbit as $v_0$.
+
+ Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
  Let $v_1 = (g, h_1, u)$ and $v_2 = (g, h_2, u)$ be two elements of the same $G_M^0$-orbit for which both $p(v_1)$ and $p(v_2)$ belong to $P_\alpha(*)$.
@@
 We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
-It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b_0)$, therefore by~\cref{SR:additivity} we have
+It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation by $x_\beta(b_0)$, therefore by~\cref{SR:additivity} we have
 \begin{multline} \nonumber
@@
 Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
-From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)\text{ for some }m,m' \in M.\]
+From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
 Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
@@
  = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am')\right],\ u(1 + am)\right) = \\
- = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, [h'], u(1 + am + bm')), \end{multline}
+ = (x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g, [h'], u(1 + am + bm')), \end{multline}
 where 
@@
 \end{multline}
-In the last computation notation $h \sim h'$ means that $h$ and $h'$ lie in the same left $G_M^0$-coset.
-If we swapped $(a,\alpha,m)$ with $(b,\beta,m')$, 
-the expressions in the right-hand sides of the above formulae would remain unchanged. This implies the required assertion.
+In the last calculation notation $h \sim h'$ means that $h$ and $h'$ lie in the same left $G_M^0$-coset.
+If we swap $(a,\alpha,m)$ with $(b,\beta,m')$, the expressions in the right-hand sides of the above formulae will remain unchanged. This implies the required assertion.
 \end{proof}
@@
 Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
-As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
+As before, we may assume $p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')$ for some $m, m' \in M$.
 Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
@@
 \begin{multline} \nonumber
-[T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
- = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
- = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
+[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
+ = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right) = \\
+ = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
  where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
@@
 \begin{prop} \label{prop43}
-For $\Phi$ as in the statement of~\cref{lemma33}.
-the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.
+For $\Phi$ as in the statement of~\cref{lemma33} the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.
 

### 2019-10-02 dl-paper.tex
Minor

@@
 Denote by $\overline{V}_T$ the quotient of the set of triples 
-\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \gamma, h, u)_T \sim (p, \gamma h, u)_T$, $\gamma \in G^0_M$.
+\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \cdot j_+(i_+(\gamma)), h, u)_T \sim (p, i_-(\gamma) \cdot h, u)_T$, $\gamma \in G^0_M$.
 We denote the image of $(p, h, u)_T$ in $\overline{V}_T$ by $[p, h, u]$.
@@
  \item For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
- \item If we consider $\St(\Phi, A[X, X\inv])$ as a group with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-groups.
+ \item If we consider $\St(\Phi, A[X, X\inv])$ as a set with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-sets.
 \end{enumerate}
@@
 
-From the second property we also immediately obtain the following group factorization.
-\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X\inv] + M[X]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}
+For a pair $(R, I)$ denote by $\E(\Phi, R, I)$ the {\it relative elementary subgroup} of $G(\Phi, R)$, i.\,e.
+the image of the relative Steinberg group $\overline{\St}(\Phi, R, I)$ under the map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$.
+From the second property of the above proposition we immediately obtain the following group factorization.
+\begin{corollary} For $\Phi$ as in the statement of~\cref{lemma33} one has
+\[\E(\Phi, A[X\inv] + M[X]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).\] \end{corollary}
 
@@
 \begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
-Using~\cref{SR:additivity} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
+Using~\eqref{eq:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
 
@@
 Suppose that the assertion holds for all $p_1 = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
-Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, B)$:
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ into~\eqref{Z5} we obtain the following equality in $\St(\Phi, B)$:
 \begin{multline*}
- z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}),\text{ where $\epsilon = N_{\alpha, \beta}$.}
+ z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-X^2 f\xi ) \cdot x_{\beta}(\xi f) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon X\xi^2f) \cdot x_{-\alpha-\beta}(- X^2f \xi^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}),\text{ where $\epsilon = N_{\alpha, \beta}$.}
 \end{multline*}
@@
 The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
-The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following computation, which we leave as an exercise to the reader:
+The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following calculation, which we leave as an exercise to the reader:
 \begin{equation*} \langle 1, m \rangle^{-1} \langle X^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+m]. \end{equation*} \end{rem}
+
+\begin{comment}
+\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
+
+\begin{multline*}
+ t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
+ = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
+\end{multline*}
+
+This implies that 
+\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
+\end{multline*}
+
+\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
+\end{equation}
+\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
+\end{equation} \end{comment}
 
@@
 \begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.
- Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B)$.
- By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore $g \in G_M^0$ and consequently $g = 1$.
+ Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B^-)$.
+ By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ satisfying $j_+i_+(\gamma) = 1$,
+  which implies that $g = 1$.
 
@@
  Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$.
- It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]), h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
+ It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]),\ h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
  From~\cref{prop43} and~\cref{lem:action} we obtain that
@@
 \begin{proof}[Proof of~\cref{thm:main}]
- Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follows from the assertion for $\St(\rD_\ell, -)$.
+ Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follow from the assertion for $\St(\rD_\ell, -)$.
  In turn, the latter assertion follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.

### 2019-10-02 dl-paper.tex
Minor

@@
 \usepackage[breaklinks=false,unicode]{hyperref}
-\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\usepackage[backend=bibtex, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
-Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$. Consider the following commutative diagram.
+Notice that the map $j_+i_+$ is split by the map $ev^*_{X=a}$ of evaluation at $a\neq 0$, hence $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$. Consider the following commutative diagram.
 \[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
@@
 Denote by $\overline{V}_T$ the quotient of the set of triples 
-\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \cdot j_+(i_+(\gamma)), h, u)_T \sim (p, i_-(\gamma) \cdot h, u)_T$, $\gamma \in G^0_M$.
+\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \cdot j_+i_+(\gamma), h, u)_T \sim (p, i_-(\gamma) \cdot h, u)_T$, $\gamma \in G^0_M$.
 We denote the image of $(p, h, u)_T$ in $\overline{V}_T$ by $[p, h, u]$.
@@
 We retain the notation of the previous section and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective.
-Being considered as a subgroup of $\St(\Phi, R)$ the group $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
+This assumption allows us to consider the group $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
+Being considered in this way, $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
 This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
@@
  Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B^-)$.
- By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ satisfying $j_+i_+(\gamma) = 1$,
-  which implies that $g = 1$.
+ By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore, by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
+ Since $j_+i_+$ is injective, we conclude that $g = 1$.
 
@@
 \begin{proof}[Proof of~\cref{thm:main}]
- Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follow from the assertion for $\St(\rD_\ell, -)$.
- In turn, the latter assertion follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
-
- Now if $g \in \St(\rD_\ell, A[X])$ is such that its image in $\St(\rD_\ell, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\rD_\ell, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
-By the just established local case the images of $g$ in all $\St(\rD_\ell, A_M[X])$ are also trivial.
+ Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follow from the assertion for $\St(\rD_\ell, -)$,
+ which, in turn, follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
+
+ Now let $A$ be arbitrary commutative ring and $\Phi = \rD_\ell$.
+If $g \in \St(\Phi, A[X])$ is such that its image in $\St(\Phi, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\Phi, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
+By the just established local case the images of $g$ in all $\St(\Phi, A_M[X])$ are also trivial.
 Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
 
- The proof of the fact the square of Steinberg groups is pullback is very similar   to the above argument (cf. also with~\cite[Theorem~5.1a]{Tu83}).
+ Now suppose that $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_+(g_+) = j_-(g_-)$.
+Set $g_0 = ev^*_{X=0}(g_+)$, $h_+ = g_+ \cdot i_+(g_0^{-1})$, $h_- = g_- \cdot i_-(g_0^{-1})$.
+ Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$, the image of $h_+$ in $\St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}.
+ Thus, again by the local-global principle~\cite[Theorem~2]{LS17} the element $h_+$ is trivial, therefore $g_+ = i_+(g_0)$.
+ Using similar argument one can show that $g_- = i_-(g_0')$ for some $g_0' \in \St(\Phi, A)$. But $g_0'$ must coincide with $g_0$ since $j_+i_+ = j_-i_-$ is injective.
 \end{proof}

### 2019-10-02 dl-paper.tex
Fix bibliography

@@
 \usepackage[breaklinks=false,unicode]{hyperref}
-\usepackage[backend=bibtex, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 
- Now let $A$ be arbitrary commutative ring and $\Phi = \rD_\ell$.
+ Now let $A$ be arbitrary commutative ring and $\Phi = \rD_\ell$, $\ell \geq 7$.
 If $g \in \St(\Phi, A[X])$ is such that its image in $\St(\Phi, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\Phi, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
-By the just established local case the images of $g$ in all $\St(\Phi, A_M[X])$ are also trivial.
+By the just established local case of the theorem the images $\lambda_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.
 Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
@@
 Set $g_0 = ev^*_{X=0}(g_+)$, $h_+ = g_+ \cdot i_+(g_0^{-1})$, $h_- = g_- \cdot i_-(g_0^{-1})$.
- Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$, the image of $h_+$ in $\St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}.
+ Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$ the image $\lambda_M(h_+)\in \St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}
+  (since $j_+(\lambda_M(h_+)) = j_-(\lambda_M(h_-))$).
  Thus, again by the local-global principle~\cite[Theorem~2]{LS17} the element $h_+$ is trivial, therefore $g_+ = i_+(g_0)$.

### 2019-10-02 dl-paper.tex
Arxiv version

@@
 \begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups.
-This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of an earlier result of A.~Suslin and V.~Kopeiko.
+This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of a result of A.~Suslin and V.~Kopeiko for the functor $\K_2$.
 \end{abstract}
@@
 
-Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $G(\Phi, R)$ (see~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
+Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $G(\Phi, R)$ (see e.\,g.~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
 There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
@@
 The faithfulness follows from the second property of~\cref{prop43} and our assumption that $j_R$ is injective.
-The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following calculation, which we leave as an exercise to the reader:
-\begin{equation*} \langle 1, m \rangle^{-1} \langle X^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+m]. \end{equation*} \end{rem}
+The transitivity follows from~\cref{lem:action}, the first property of~\cref{prop43} and the following formula, which is a direct consequence of~\cref{lem:Tulenbaev-formula} and~\eqref{T_1}--\eqref{T_leq0}:
+\begin{equation*} \langle a, m \rangle^{-1} \cdot \langle aX^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+am]. \end{equation*} \end{rem}
 
@@
 \begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
-\end{equation} \end{comment}
+\end{equation}
+\end{comment}
 

### 2019-10-02 dl-paper.tex
Minor

@@
 \begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups.
-This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue of a result of A.~Suslin and V.~Kopeiko for the functor $\K_2$.
+This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue for the functor $\K_2$ of a 1982 result of A.~Suslin and V.~Kopeiko.
 \end{abstract}
@@
 While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
-It has been conjectured by M.~Wendt, see~\cite[Vermutung~6.22]{Vo11} that the $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+It has been conjectured by M.~Wendt, see~\cite[Vermutung~6.22]{Vo11} that a $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
 
 In~\cite{LS17} the authors have shown that Steinberg groups $\St(\Phi, R)$ satisfy Quillen--Suslin local-global principle provided $\Phi$ is simply-laced and has rank $\geq 3$.
-This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem.
-The aim of the present article is to make yet another step towards its solution, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups.
+This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem for Chevalley groups.
+The aim of the present article is to make yet another step towards the solution of the problem, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups of type $\rD_\ell$.
 
@@
 If $g \in \St(\Phi, A[X])$ is such that its image in $\St(\Phi, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\Phi, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
-By the just established local case of the theorem the images $\lambda_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.
+ We denote by $\lambda_{M}$ (resp.
+$\lambda_{M, -}$) the localization map $A[X] \to A_M[X]$ (resp.
+$A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding maps of Steinberg groups.
+ By the just established local case of the theorem the images $\lambda^*_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.
 Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
@@
 Set $g_0 = ev^*_{X=0}(g_+)$, $h_+ = g_+ \cdot i_+(g_0^{-1})$, $h_- = g_- \cdot i_-(g_0^{-1})$.
- Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$ the image $\lambda_M(h_+)\in \St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}
-  (since $j_+(\lambda_M(h_+)) = j_-(\lambda_M(h_-))$).
+ Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$ the image $\lambda_M^*(h_+)\in \St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}
+  (since $j_+(\lambda^*_M(h_+)) = j_-(\lambda^*_{M,-}(h_-))$).
  Thus, again by the local-global principle~\cite[Theorem~2]{LS17} the element $h_+$ is trivial, therefore $g_+ = i_+(g_0)$.

### 2019-10-02 dl-paper.tex
Added texorpdfstrings

@@
 
-\subsection{$\K_2$-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
@@
 
-\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} \label{sec:Pa0-basic}
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} \label{sec:Pa0-basic}
 Let $\Phi$ be a root system and $\alpha \in \Phi$ be its element.
@@
 
-\subsection{The subgroups $K(\alpha, \beta)$ and their properties} \label{sec:Pa0-Steinberg}
+\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties} \label{sec:Pa0-Steinberg}
 Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
@@
 
-\subsection{Construction of a $\St(\Phi, B)$-torsor.} \label{sec:V-construction}
+\subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor.} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.

### 2019-11-24 dl-paper.tex
Update grant line

@@
 \subsection{Acknowledgements} 
-The authors of this paper were also supported by ``Native towns'', a social investment program of PJSC ``Gazprom Neft''.
-The second-named author also acknowledges the financial support of RFBR grant No 18-31-20044.
+The first-named author acknowledges the financial support of Russian Science Foundation grant No 17-11-01261.
+The second-named author acknowledges the financial support of RFBR grant No 18-31-20044.
 

### 2019-11-30 dl-paper.tex
dl-paper.tex
minor

@@
 \author{Andrei Lavrenov}
-\address{Mathematisches Institut der Universit\"at M\"unchen, Theresienstr. 39, D-80333 M\"unchen}
 \email{avlavrenov at gmail.com}
-
 \author {Sergey Sinchuk}
+\email {sinchukss at gmail.com}
 \address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
-\email {sinchukss at gmail.com}
 \date {\today}
@@
 \subsection{Acknowledgements} 
-The first-named author acknowledges the financial support of Russian Science Foundation grant No 17-11-01261.
-The second-named author acknowledges the financial support of RFBR grant No 18-31-20044.
+The work of the first-named author (\S~3) was supported by the Russian Science Foundation grant No 17-11-01261.
+The work of the second-named author (\S~4--5) was supported by RFBR grant No 18-31-20044.
 

### 2019-12-10 dl-paper.tex
Fix misprint

@@
 which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv]) \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
-$P(k)$ is the set $k^\times \times I_2(k)$ with the group structure given by
+$P(k)$ is the set $k^\times \times I^2(k)$ with the group structure given by
 \[ (u, y) \cdot (v, z) = (uv, y + z - \langle\langle u, v\rangle\rangle).\]

### 2020-01-26 dl-paper.tex
Minor language fixes

@@
 This is the only place in our proof which invokes the assumption that $2$ is invertible.
-The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain basic computations with Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
+The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain basic calculations with Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
 Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
@@
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In our computations below we will be using identities~\eqref{eq:simplest} without further reference.
+In our calculations below we will be using identities~\eqref{eq:simplest} without further reference.
 
@@
 
-\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
+\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our calculations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
 Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
@@
 Recall that the classical Matsumoto theorem (see~\cite[Theorem~5.10]{Ma69}) allows one to compute the group $\K_2(\Phi, R)$ in the special case when $R=k$ is a field.
-Using the modern language of Milnor--Witt K-theory (see~\cite{Mo04}) it can be formulated as the following computation:
+Using the modern language of Milnor--Witt K-theory (see~\cite{Mo04}) it can be formulated as follows:
 \[\K_2(\Phi, k) = \left\{\begin{array}{ll} \K_2^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_2^\mathrm{M}(k) & \text{otherwise.}\end{array}\right. \]
@@
 By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$.
-The required assertion now follows from the following computation:
+The required assertion now follows from the following calculation:
  \[ 1 = \mu_B\lambda_B(d) = tg\lambda_B(d) = t\lambda_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
@@
 } \end{equation}
-The above isomorphism allows us to regard $\overline{V}$ and $\overline{V}_T$ as one and the same object, for which we can interchangeably use either of the two notations,
+The above isomorphism allows us to regard $\overline{V}$ and $\overline{V}_T$ as the same object, for elements of which we can interchangeably use either of the two notations,
  depending on which of them is more convenient in a given situation.

### 2020-03-13 dl-paper.tex
Fixed some language issues

@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
+Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on an arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
 
@@
 There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on Chevalley group $G(\Phi, -)$, see~\cite{St78}.
-
-It turns out that an assertion similar to Serre problem also holds for the functor $\K_2$.
+The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on the Chevalley group $G(\Phi, -)$, see~\cite{St78}.
+
+It turns out that an assertion similar to the Serre problem also holds for the functor $\K_2$.
 More precisely, in~\cite{Tu83} M.
@@
 While numerous results on the $\K_1$-analogue of Serre's problem have appeared in the literature since~\cite{Su77} (see e.\,g.~\cite{Su82, Abe83, St-poly, St-Ded}), little progress has been made on the $\K_2$-analogue.
-It has been conjectured by M.~Wendt, see~\cite[Vermutung~6.22]{Vo11} that a $\K_2$-analogue of Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
-
-In~\cite{LS17} the authors have shown that Steinberg groups $\St(\Phi, R)$ satisfy Quillen--Suslin local-global principle provided $\Phi$ is simply-laced and has rank $\geq 3$.
-This result is one of the ingredients needed in the proof of the $\K_2$-analogue of Serre problem for Chevalley groups.
+It has been conjectured by M.~Wendt, see~\cite[Vermutung~6.22]{Vo11} that a $\K_2$-analogue of the Serre problem holds for $\K_2(\Phi, -)$ for all $\Phi$ of rank $\geq 3$, however this conjecture still remains open for $\Phi$ different from $\rA_\ell$, $\ell \geq 4$.
+
+In~\cite{LS17} the authors have shown that the Steinberg groups $\St(\Phi, R)$ satisfy the Quillen--Suslin local-global principle provided $\Phi$ is simply-laced and has rank $\geq 3$.
+This result is one of the ingredients needed in the proof of the $\K_2$-analogue of the Serre problem for Chevalley groups.
 The aim of the present article is to make yet another step towards the solution of the problem, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups of type $\rD_\ell$.
@@
 \subsection{Steinberg groups} \label{sec:Steinberg-intro}
-Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
+Let $\Phi$ be a reduced and irreducible root system of rank $\ell \geq 2$ and $R$ be a commutative ring with $1$.
 Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ and relations:
@@
 \cite[\S~14]{VP}).
-\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
+\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then the following identities hold for the structure constants:
 \begin{equation} \label{eq:simplest} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
@@
               \label{eq:h-inv}    h_\alpha(t)^{-1}             & = h_{-\alpha}(t). \end{align}
-Here $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$.
+Here $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$ (we denote by $(-,-)$ the inner product on the euclidean space $\mathbb{R}^\ell$ containing $\Phi$).
 
@@
 Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
+In particular, the product of symbols is written multiplicatively.
+
 Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
@@
 In the following lemma we recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
-\begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
+\begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be an arbitrary field.
 Then there is a split exact sequence of abelian groups
@@
                                                                                       &                                 & \K_2^\mathrm{M}(k(X)),} \]
-in which $h = \{ -, X \}_{\alpha}$ and the vertical map is an isomorphism by Matsumoto theorem.
+in which $h = \{ -, X \}_{\alpha}$ and the vertical map is an isomorphism by Matsumoto's theorem.
 Notice that the diagonal map is split by the obvious residue homomorphism and therefore is injective. This, in turn, implies that $h$ is also injective.

### 2020-03-16 dl-paper.tex
More fixes

@@
 Using the modern language of Milnor--Witt K-theory (see~\cite{Mo04}) it can be formulated as follows:
-\[\K_2(\Phi, k) = \left\{\begin{array}{ll} \K_2^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_2^\mathrm{M}(k) & \text{otherwise.}\end{array}\right. \]
+\begin{equation*} \K_2(\Phi, k) = \left\{\begin{array}{ll} \K_2^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_2^\mathrm{M}(k) & \text{otherwise.}\end{array}\right. \end{equation*}
 In the following lemma we recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
@@
 Notice that the diagonal map is split by the obvious residue homomorphism and therefore is injective. This, in turn, implies that $h$ is also injective.
-The assertion of the lemma now follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi$ holds $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
+The assertion of the lemma now follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi$ one has $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
 
@@
 
-\begin{rem} The above lemma can be considered as the unstable version of~\cite[Lemma~4.1.1]{AF17} (compute~$\mathrm{KSp}_2(k[X, X\inv])$ using~\eqref{GW-concrete} and~\cref{bass-ft} below). \end{rem}
+\begin{rem} It is possible to directly prove the stable symplectic counterpart of the above lemma. Indeed, we have the following chain of isomorphisms:
+\[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
+in which the first two are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
+Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups. \end{rem}
 
@@
 \end{lemma}
-\begin{proof} The first assertion follows from consideration of the following commutative diagram:
+\begin{proof} The first assertion follows from the commutative diagram
 \[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
-               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}]),} \]
-in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}.
+               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
+and the injectivity of its diagonal arrows. Indeed, the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}.
 
 Let us verify the second assertion. Let $g$ be an element of the intersection of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$.
-Clearly, the image of $g$ in $G(\Phi, k[X, X\inv])$ lies in $G(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[t]) = \K_2(\Phi, k)$.
+Clearly, the image of $g$ in $G(\Phi, k[X, X\inv])$ lies in $G(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[X]) = \K_2(\Phi, k)$.
 Thus, we conclude that $g \in \St(\Phi, k)$.
@@
 Recall that the category of (commutative) pairs $\catname{Pairs}$ is defined as follows.
-Its objects are pairs $(R, I)$, in which $R$ is a commutative ring and $I$ is an ideal of $R$.
-A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
+Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with a unit and $I$ is an ideal of $R$.
+A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a unit-preserving ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
 Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ to the morphism category $\catname{CRings}^\rightarrow$.
@@
 
-First of all, recall that a {\it central extension} of a group $G$ is a surjective map $\widetilde{G} \to G$, whose kernel is contained in the center of $\widetilde{G}$. 
-A morphism of central extensions is a group-theoretic map $\widetilde{G} \to \widetilde{G}'$ over $G$.
+First of all, recall that a {\it central extension} of a group $G$ is a surjective homomorphism $\widetilde{G} \to G$, whose kernel is contained in the center of $\widetilde{G}$. 
+A morphism of central extensions is a homomorphism $\widetilde{G} \to \widetilde{G}'$ over $G$.
 A central extension is said to be {\it universal} if it is an initial object of the category of central extensions of $G$.
@@
 
-Let $\nu \colon N \twoheadrightarrow Q$ be a surjective group-theoretic map.
+Let $\nu \colon N \twoheadrightarrow Q$ be a surjective homomorphism.
 A {\it relative central extension of $\nu$} is, by definition,

### 2020-03-19 dl-paper.tex
Fixes sections 2 (part 2)-3

@@
 Recall that the category of (commutative) pairs $\catname{Pairs}$ is defined as follows.
-Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with a unit and $I$ is an ideal of $R$.
+Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with $1$ and $I$ is a (not neccessarily proper) ideal of $R$.
 A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a unit-preserving ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
@@
 
-Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of a group $N$ acting on itself by left conjugation, an $N$-group $M$ and a map
- $\mu \colon M\to N$ of $N$-groups satisfying {\it Peiffer identity} $\mu(m) \cdot m' = m m' m^{-1}$. It can be shown that the image of $\mu$ is always
-  a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$.
+Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of the following data:
+\begin{enumerate}
+ \item a group $N$ acting on itself by left conjugation (i.\,e. ${}^{n}\!n' = n n' n^{-1}$).
+ \item a group $M$ with a left action of $N$ (we call such a group an $N$-group and use the notation ${}^n m$ to denote the image of an element $m\in M$ under the action of $n \in N$);
+ \item a homorphism $\mu \colon M\to N$ preserving the action of $N$-groups and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
+\end{enumerate}
+It can be shown that the image of $\mu$ is always a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$.
 
@@
 
-It is easy to see that functors $G_n$, $P_n$ and $S_n$ satisfy \ref{req:left-exact} and \ref{req:coeq}.
+It is easy to see that the functors $G_n$, $P_n$ and $S_n$ satisfy \ref{req:left-exact} and \ref{req:coeq}.
 By~\cite{Su82} the requirement~\ref{req:subfunc} is also satisfied for $n \geq 3$.
@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_\ell, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_\ell, R)$, but the converse is not generally true.
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_n, R)$, but the converse is not generally true.
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
@@
 \section{An injectivity theorem for Steinberg groups} \label{firstPart}
-We start this section by recalling basic notation and facts pertaining to the theory of Grothendieck--Witt groups.
+We start this section by recalling basic notation and facts pertaining to the theory of higher Grothendieck--Witt groups.
 Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings.
@@
 For the rest of this section let us fix the following notation.
-Let $A$ be arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
+Let $A$ be an arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
 Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
@@
 \begin{proof}
- Consider the following commutative diagram with exact rows, in which the lifting $t$ is obtained from~\cref{lem:lemma32}:
+ Consider the following commutative diagram with exact rows obtained from~\eqref{LodayRelativization}:
 \begin{equation*} \xymatrix{
@@
 }\end{equation*}
+The lifting $t$ in the above diagram is obtained from~\cref{lem:lemma32}.
 Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$

### 2020-03-23 dl-paper.tex
Fixes sections 3-4

@@
 \section{Preliminaries}
+If $x$ and $y$ are elements of a group $G$ then $[x, y]$ denotes the left-normed commutator $xyx^{-1}y^{-1}$.
+We denote by $x^y$ (resp. ${}^y\!x$) the element $y^{-1}xy$ (resp. $yxy^{-1}$). 
+Throughout the paper we make use of the following commutator identities:
+\begin{align}
+ [x, yz]^y =& [y^{-1}, x] \cdot [x, z], \label{rel43} \\ 
+ \label{eq:H1ii} [xy, z] =& {}^x[y, z] \cdot [x,z]. \\
+ [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant} \end{align}
+Sometimes we will also be using the fact that 
+\begin{equation} \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz]. \end{equation}
+
 \subsection{Steinberg groups} \label{sec:Steinberg-intro}
@@
 \begin{align}
-&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
+&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1} \label{Steinberg-additivity}\\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \label{Chevalley-CCF1} \\
+&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3} \label{Chevalley-CCF2}
 \end{align}
@@
  \item a group $M$ with a left action of $N$ (we call such a group an $N$-group and use the notation ${}^n m$ to denote the image of an element $m\in M$ under the action of $n \in N$);
- \item a homorphism $\mu \colon M\to N$ preserving the action of $N$-groups and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
+ \item a homomorphism $\mu \colon M\to N$ preserving the action of $N$-groups and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
 \end{enumerate}
@@
 
-\begin{lemma}\label{Zrels} The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in R$, $s\in I$:
+\begin{lemma}\label{Zrels} Let $\Phi$ be a simply laced root system.
+The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in R$, $s\in I$:
 \begin{enumerate} 
@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item If $\alpha+\beta\in\Phi$ then holds:
+\item If $\alpha+\beta\in\Phi$ then one has:
 \begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
@@
 The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
-Direct computation shows that
+Direct computation using Chevalley commutator identities~\eqref{Chevalley-CCF1}--\eqref{Chevalley-CCF2} shows that
 \begin{multline} \nonumber
@@
 
-Let us mention an immediate application of the just proved lemma.
-First of all, recall the following two results which give two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results are applicable for arbitrary $\Phi$)
+Let us mention an immediate application of~\cref{Zrels}.
+First of all, recall the following two results which give two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results apply to general irreducible $\Phi$ of rank $\geq 2$, i.\,e.
+not neccessarily simply-laced ones).
 \begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
@@
 
-Recall that a closed root subset $S \subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $S \cup -S = \Phi$ (resp. $S = -S$, resp. $S \cap (-S) = \varnothing$).
+\begin{df} \label{df:root-subsets}
+Recall that a root subset $S \subseteq \Phi$ is called {\it closed} if $\alpha, \beta \in S$ and $\alpha+\beta\in \Phi$ imply $\alpha + \beta \in S$. 
+Recall that a closed root subset $S$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $S \cup -S = \Phi$ (resp. $S = -S$, resp. $S \cap (-S) = \varnothing$).
 The {\it special part} $\Sigma_S$ of a parabolic subset $S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
+\end{df}
 
@@
 \begin{rem} We claim that in the simply-laced case the stronger \cref{thm:Stepanov} can be deduced from~\cref{thm:Tits} by means of~\cref{Zrels}.
-Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets given by $d(U) = U \cup (U - U)\cap \Phi$, $U \subseteq \Phi$.
-In other words, $d$ adjoins to $U$ all differences of roots from $U$ which are themselves roots.
+Indeed, consider the operator $d \colon 2^\Phi \to 2^\Phi$ of root subsets, whose value on each $U \subseteq \Phi$ is given by \[d(U) = U \cup \left((U - U)\cap \Phi\right).\]
+Here $(U-U) \cap \Phi$ denotes the set of all differences of roots from $U$ which are themselves roots.
 It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n>1$ (in fact, $n=2$).
@@
 
-\begin{lemma} \label{Crels}
-The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in R$.
+\begin{lemma} \label{Crels} Let $\Phi$ be a simply-laced root system.
+The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in R$:
  \begin{enumerate}
@@
  \item \label{C3} $[c_\beta(s, t),\ x_{\alpha}(\xi)] = 1$ if $\alpha \perp \beta$;  
- \item \label{C4} If $\alpha+\beta\in\Phi$ then holds:
+ \item \label{C4} If $\alpha+\beta\in\Phi$ then
   \begin{equation} \label{eq:C4} c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\end{equation}
@@
 
-For the proof of the other assertions we will need the following commutator identities:
-\begin{align}
- [x, yz]^y =& [y^{-1}, x] \cdot [x, z], \label{rel43} \\
-  [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant}
-\end{align}
-
-The second assertion follows directly from~\eqref{HW-variant}:
+The second assertion follows directly from~\eqref{HW-variant} and Chevalley commutator identities:
 \begin{multline} \nonumber
@@
 
-Finally, the last assertion can be verified via the following direct computation, which uses~\eqref{rel43} and \eqref{HW-variant} (with both sides of the equality inverted):
-\begin{multline} \nonumber [x_{\alpha+\beta}(s),\ x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s),\ [x_{-\alpha}(-\epsilon t),\ x_{-\beta}(\xi)]] = \\ 
-= \left([[x_{\alpha+\beta}(-s),\ x_{-\alpha}(\epsilon t)],\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi),\ x_{\alpha+\beta}(s)],\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)]^{x_{-\alpha}(\epsilon t)} = \\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{-\alpha}(-\epsilon t),\ x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha-\beta}(t\xi)] = \\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
-\end{multline}
+Finally, the last assertion can be verified via the following direct computation:
+\begin{align*}
+[x_{\alpha+\beta}(s),\ x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s),\ [x_{-\alpha}(-\epsilon t),\ x_{-\beta}(\xi)]]&\ \text{by~\eqref{Chevalley-CCF1}}\\
+\begin{split}
+    =\bigl( [[x_{\alpha+\beta}(-s),\ x_{-\alpha}(\epsilon t)],\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot \hspace{70pt} \\
+        \cdot [[ x_{-\beta}(-\xi),\ x_{\alpha+\beta}(s)],\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)}\bigr)^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{HW-variant}}
+\end{split}\\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1}}\\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)]^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{-\alpha}(-\epsilon t),\ x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha-\beta}(t\xi)] &\ \text{by~\eqref{rel43}}\\
+= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2)  &\ \text{by~\eqref{Chevalley-CCF1}}.
+\qedhere
+\end{align*}
 \end{proof}
@@
 It turns out that, although $K(A[X], M[X])$ is generally strictly larger than $\overline{\St}(\Phi, A[X], XM[X])$,
- it contains very few extra generators, which can all be explicitly described (see~\cref{Kgen} and the corollary that follows it).
+ it contains very few extra generators, which all can be explicitly described (see~\cref{Kgen} and the corollary that follows it).
 
@@
  moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
-\begin{lemma} \label{Kdecomp1} The following decomposition holds
+\begin{lemma} \label{Kdecomp1} The following decomposition holds:
  \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
-\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
+\begin{proof} Let us fix $g(X) \in K(A[X], M[X])$.
+By~\cref{thm:Tits} we can write it as $\prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
  It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
@@
 
-For a closed root subset $S \subseteq \Phi$ we denote by $U(S, M)$ the subgroup of $\St(\Phi, A)$ generated by root subgroups $X_\alpha(M)$ corresponding to all $\alpha \in S$.
+Let $S \subseteq \Phi$ be a closed root subset (see~\cref{df:root-subsets}).
+We denote by $U(S, M)$ the subgroup of $\St(\Phi, A)$ generated by root subgroups $X_\alpha(M)$ corresponding to all $\alpha \in S$.
 We denote by $\Phi^+$ (resp.
@@
 \begin{proof}
-For the proof we will need the following commutator identities:
-\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\
- \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}
-
 The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree
@@
 
-\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it conincides with the image under $j_+$ of the subgroup 
+\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it coincides with the image under $j_+$ of the subgroup 
 of $\overline{\St}(\Phi, A[X], M[X])$ consisting of those elements $g$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}

### 2020-03-25 dl-paper.tex
Fixed some of the remaining issues with sections 1-4

@@
 In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $\K_2$-functor (see~\cref{sec:quillen}).
+Notice also that in the special case when $A=k$ is a field the above theorem follows from the results of U.~Rehmann, J.~Hurrelbrink and J.~Morita (see~\cref{field-injectivity} below).
 
@@
 \subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our calculations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}.
-Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook}.
-In particular, the product of symbols is written multiplicatively.
+Notice that our notational conventions for symbols follow~\cite{DS73} and {\it not} more modern textbooks such as~\cite{Kbook} (cf.
+with~Definition~III.5.11 ibid.).
+Notice also that the operation on $\K_2(\Phi, R)$ is always written multiplicatively.
 
@@
 
-\begin{rem} It is possible to directly prove the stable symplectic counterpart of the above lemma. Indeed, we have the following chain of isomorphisms:
+\begin{rem} It is possible to directly prove the stable symplectic counterpart of the above lemma (under the additional assumption that the characteristic of $k$ is not $2$).
+Indeed, we have the following chain of isomorphisms:
 \[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
-in which the first two are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
-Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups. \end{rem}
+in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
+Thus, we see that in the stable range the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups. \end{rem}
 
@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ contains $\K_2(\rD_n, R)$, but the converse is not generally true.
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ does not coincide with $\K_2(\rD_n, R) = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))$ but rather is related with it via the exact sequence
+\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
+which can be obtained from the exact sequence~\cite[p.~189]{Ba74} by means of the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
@@
  \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-By~\cref{Panin-stability} theorem the map $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+By~\cref{Panin-stability} the map $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
 By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$

### 2020-03-25 dl-paper.tex
Fixed some issues with section 5

@@
 In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $\K_2$-functor (see~\cref{sec:quillen}).
-Notice also that in the special case when $A=k$ is a field the above theorem follows from the results of U.~Rehmann, J.~Hurrelbrink and J.~Morita (see~\cref{field-injectivity} below).
+Notice also that in the special case when $A=k$ is a field the assertion of the above theorem follows from the results of U.~Rehmann, J.~Hurrelbrink and J.~Morita (see~\cref{field-injectivity} below).
 
@@
  [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant} \end{align}
-Sometimes we will also be using the fact that 
+We will also be using the fact that 
 \begin{equation} \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz]. \end{equation}
@@
 
+Throughout this section we will employ the following notation:
+\begin{itemize}
+ \item $R$ denotes the Laurent polynomial ring $A[t, t^{-1}]$;
+ \item $B$ denotes the subring $A[t] + m[t^{-1}]$ of $R$ consisting of Laurent polynomials $f(t,t^{-1})$ whose coefficients of terms of negative degree belong to $m$;
+ \item $I$ denotes the ideal $m[t, t^{-1}]$ of $R$ (which can be also considered as an ideal of $B$).
+\end{itemize}
 \subsection{Presentation of Steinberg groups by homogeneous generators}
@@
 
-For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
+For $n\geq 1$ we define the ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
 We denote by $F(\mathcal{X}^\Phi_{\leq n})$ the free group on $\mathcal{X}^\Phi_{\leq n}$.
@@
  where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
- Standard argument (cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}) shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.
+ A standard argument, cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}, shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.
 
  Set $\mathcal{R}^\Phi_{n+1} = \mathcal{R}^\Phi_{\leq n+1} \setminus \mathcal{R}^\Phi_{\leq n}$.
-It suffices to verify that the image of every relator $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
+It suffices to verify that the image of every relation $R \in \mathcal{R}^\Phi_{n+1}$ under $\widetilde{j}^\Phi_n$ is a trivial element of $\St^{\leq n}(\Phi, B)$.
 In the special case $\Phi=\rA_{\geq 4}$ this has already been demonstrated by Tulenbaev in~\cite[Lemma~3.3]{Tu83}, so in this case the proof of the proposition is complete.
@@
 \subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} \label{sec:Pa0-basic}
-Let $\Phi$ be a root system and $\alpha \in \Phi$ be its element.
+Let $\Phi$ be a root system and $\alpha$ be an element of $\Phi$.
 Consider the following subsets of $\Phi$:
@@
 \begin{lemma}\label{P0_normal} The subgroup $P_{\alpha, M}(0)$ is normal in $P_{\alpha, M}(*)$.
-In particular, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
+Moreover, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
 \[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}

### 2020-03-25 dl-paper.tex
Introduce notation before 5.1

@@
 
-Throughout this section we will employ the following notation:
+Throughout this section we adopt the following notation:
 \begin{itemize}
- \item $R$ denotes the Laurent polynomial ring $A[t, t^{-1}]$;
- \item $B$ denotes the subring $A[t] + m[t^{-1}]$ of $R$ consisting of Laurent polynomials $f(t,t^{-1})$ whose coefficients of terms of negative degree belong to $m$;
- \item $I$ denotes the ideal $m[t, t^{-1}]$ of $R$ (which can be also considered as an ideal of $B$).
+ \item $A$ is an arbitarary commutative ring and $M$ is an ideal of $A$. 
+ In Section~\ref{sec:presentation} there are no restrictions on $(A, M)$, but in later sections the pair $(A, M)$ is assumed to be local.
+ \item $R$ denotes the Laurent polynomial ring $A[X, X^{-1}]$. It will be convenient for us to set $t = X^{-1}$, so also $R = A[t, t^{-1}]$.
+ \item $B$ denotes the subring $A[t] + M[t^{-1}]$ of $R$ consisting of Laurent polynomials $f(t,t^{-1})$ whose coefficients of terms of negative degree belong to $M$;
+ \item $I$ denotes the ideal $M[t, t^{-1}]$ of $R$. $I$ can also be considered as an ideal of $B$.
 \end{itemize}
@@
 Let $M$ be an ideal of a local ring $A$.
-We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five types elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
+We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five types of elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
 \begin{enumerate} \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$

### 2020-03-26 dl-paper.tex
Fixing issues found by myself

@@
 
-Throughout this section we adopt the following notation:
+Throughout this section we use the following notations and conventions:
 \begin{itemize}
- \item $A$ is an arbitarary commutative ring and $M$ is an ideal of $A$. 
- In Section~\ref{sec:presentation} there are no restrictions on $(A, M)$, but in later sections the pair $(A, M)$ is assumed to be local.
- \item $R$ denotes the Laurent polynomial ring $A[X, X^{-1}]$. It will be convenient for us to set $t = X^{-1}$, so also $R = A[t, t^{-1}]$.
- \item $B$ denotes the subring $A[t] + M[t^{-1}]$ of $R$ consisting of Laurent polynomials $f(t,t^{-1})$ whose coefficients of terms of negative degree belong to $M$;
- \item $I$ denotes the ideal $M[t, t^{-1}]$ of $R$. $I$ can also be considered as an ideal of $B$.
+ \item Let $A$ be an arbitarary commutative ring and $M$ be an ideal of $A$. Starting from subsection~\ref{sec:Pa0-basic} we also assume that $A$ is local and $M$ is the maximal ideal of $A$.
+ \item We denote by $R$ the Laurent polynomial ring $A[X, X^{-1}]$. We set $t = X^{-1}$, so that $R = A[X, X^{-1}] = A[t, t^{-1}]$.
+ \item $B = B_{A, M}$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$. Obviously, $B = A[t]$ in the case $M=0$ and $B = R$ in the case $M=A$.
  \end{itemize}
@@
 \label{sec:presentation}
-Let $M\trianglelefteq A$ be an ideal of a commutative ring $A$.
-We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
-We denote by $B = B(A, M)$ the subring $A[t] + M[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
-As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$.
-Obviously, $B = A[t]$ in the case $M=0$ and $B = A[t, t\inv]$ in the case $M=A$.
+We consider $R = A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
+This grading induces the grading on the subring $B \subseteq R$.
+For an integer $d$ we denote by $R_d$ (resp.
+$B_d$) the degree $d$ part of the ring $R$ (resp.
+$B$).
+Obviously, $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$.
+With this notation, $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ as an $A$-module.
 
@@
  we call the corresponding generator $g$ {\it homogeneous of degree $d$}.
-It is not hard to show that $\St(\Phi, B)$ can be presented by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations
+We denote by $\St^h(\Phi, B)$ the Steinberg group in the homogeneous presentation, i.\,e.
+the group given by the set of all homogeneous Steinberg generators modulo the following set of relations which we call homogeneous Steinberg relations
 (below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
@@
 \end{align}
+\begin{rem}
+Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they, in fact, follow from~\eqref{eq:H1iii},~$\text{R2}_{d,e}$ and $R3_{d,e}^\angle$: \[ ???.
+\]
+\end{rem}
+
+It is not hard to show that the map $\St^h(\Phi, B) \to \St(\Phi, B)$ induced by the obvious embedding of generators is an isomorphism.
+
 By the degree of a Steinberg relation we mean the maximum of degrees of generators that appear in the relation.
@@
 
-For $n\geq 1$ we define the ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
+For $n\geq 1$ we define the ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of homogeneous Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
 We denote by $F(\mathcal{X}^\Phi_{\leq n})$ the free group on $\mathcal{X}^\Phi_{\leq n}$.
+
+Notice that $\lim\limits_{n \to +\infty} \St^{\leq n}(\Phi, B) = \St^h(\Phi, B) \cong \St(\Phi, B)$.
 

### 2020-03-27 dl-paper.tex
Fix 1-7 of 3.5

@@
 
-\section{Elementary calculations in relative Steinberg groups}
+\section{Elementary calculations in relative Steinberg groups}\label{sec:elementary}
 Throughout this section $\Phi$ denotes an irreducible root system of rank $\geq 2$, $R$ a commutative ring, and $I, J$ denote a pair of ideals of $R$.
 Unless stated otherwise we assume $\Phi$ to be simply laced.
+
 We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the map $\St(\Phi, R) \to \St(\Phi, R/I)$.
@@
 
-We define the following two families of elements of $\overline{\St}(\Phi, R, I)$:
-\begin{itemize}
- \item $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$ defined for $\xi \in R$, $s \in I$;
- \item $c_\alpha(s, t) = [x_\alpha(s), x_{-\alpha}(t)]$ defined for $s \in I$, $t \in J$.
-\end{itemize}
+For $s\in I$, $\xi \in R$, $t \in J$ we define the following two families of elements of $\overline{\St}(\Phi, R, I)$ 
+\begin{align}
+ z_\alpha(s, \xi) &= x_\alpha(s)^{x_{-\alpha}(\xi)}, \label{Zdef}\\
+ c_\alpha(s, t)   &= [x_\alpha(s), x_{-\alpha}(t)]. \label{Cdef}
+\end{align}
 
@@
 
-Let $S \subseteq \Phi$ be a closed root subset (see~\cref{df:root-subsets}).
+Let $S \subseteq \Phi$ be a special root subset (see~\cref{df:root-subsets}).
 We denote by $U(S, M)$ the subgroup of $\St(\Phi, A)$ generated by root subgroups $X_\alpha(M)$ corresponding to all $\alpha \in S$.
@@
 \begin{itemize}
- \item Let $A$ be an arbitarary commutative ring and $M$ be an ideal of $A$. Starting from subsection~\ref{sec:Pa0-basic} we also assume that $A$ is local and $M$ is the maximal ideal of $A$.
+ \item $A$ denotes an arbitarary commutative ring and $M$ is an ideal of $A$. Starting from subsection~\ref{sec:Pa0-basic} we also assume that $A$ is local and $M$ is the maximal ideal of $A$.
  \item We denote by $R$ the Laurent polynomial ring $A[X, X^{-1}]$. We set $t = X^{-1}$, so that $R = A[X, X^{-1}] = A[t, t^{-1}]$.
@@
  we call the corresponding generator $g$ {\it homogeneous of degree $d$}.
-We denote by $\St^h(\Phi, B)$ the Steinberg group in the homogeneous presentation, i.\,e.
-the group given by the set of all homogeneous Steinberg generators modulo the following set of relations which we call homogeneous Steinberg relations
+We denote by $\St^h(\Phi, B)$ the group given by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations between them
 (below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
@@
 \begin{rem}
-Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they, in fact, follow from~\eqref{eq:H1iii},~$\text{R2}_{d,e}$ and $R3_{d,e}^\angle$: \[ ???.
+Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they follow from~$\text{R2}_{e,0}$, \eqref{eq:H1iii} and $\text{R3}_{d,e}^\angle$.
+Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we have that \[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1.
 \]
@@
 It is not hard to show that the map $\St^h(\Phi, B) \to \St(\Phi, B)$ induced by the obvious embedding of generators is an isomorphism.
+Thus, $\St^h(\Phi, B)$ can be considered as an alternative presentation of $\St(\Phi, B)$ by homogeneous generators.
 
 By the degree of a Steinberg relation we mean the maximum of degrees of generators that appear in the relation.
-For example, the degree of every relation of type $\text{R2}_{d,e}$ is $\max(d,e,d+e)$ 
- while the degree of a relation of type $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
-
-For $n\geq 1$ we define the ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the set of homogeneous Steinberg relations $\mathcal{R}_{\leq n}^\Phi$ of degree $\leq n$.
+For example, the degree of every relation of type $\text{R2}_{d,e}$ is $\max(d,e,d+e)$, while the degree of a relation of type $\text{R3}^\bot_{d,e}$ or $\text{R3}^\angle_{d,e}$ is $\max(d,e)$.
+
+For $n\geq 1$ we define the ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ by means of the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ and the subset $\mathcal{R}_{\leq n}^\Phi$ of the above set of Steinberg relations consisting of all relations of degree $\leq n$.
 We denote by $F(\mathcal{X}^\Phi_{\leq n})$ the free group on $\mathcal{X}^\Phi_{\leq n}$.
-
-Notice that $\lim\limits_{n \to +\infty} \St^{\leq n}(\Phi, B) = \St^h(\Phi, B) \cong \St(\Phi, B)$.
+Notice that $\varinjlim\limits \St^{\leq n}(\Phi, B) = \St^h(\Phi, B) \cong \St(\Phi, B)$.
 
@@
 \begin{proof}
-The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree
- $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree.
-Let us fix some relation $[x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$. Denote this relation by $R$.
-
+The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree (modulo the remaining relations of $\St^{\leq n}(\Phi, B)$, i.\,e.
+relations of type R2 and $\text{R3}^{\angle}$).
+The commutator formulae $\text{R2}$ are used to reduce the degree of the monomials appearing in $R$.
+
+Let us fix some relation $R = [x_\alpha(at^d),\ x_\gamma(bt^e)] = 1$ of type $\text{R3}^\bot_{d,e}$ for some $\alpha\perp\gamma$.
 We can find $\beta \in \Phi$ forming an obtuse angle with both $\alpha$ and $\gamma$ (see e.\,g.~\cite[Lemma~3.1.2]{RS76}).
@@
 
-The assertion of the lemma now follows from the above observation by induction on the degree of $R$ and the fact
- that by~\eqref{first-computation} relation $\text{R3}^\bot_{1,1}$ is a consequence of $\text{R3}^\bot_{0,0}$.
+The assertion of the lemma now follows from the above observation by induction on the degree of $R$ and the fact that by~\eqref{first-computation} the relation $\text{R3}^\bot_{1,1}$ is a consequence of $\text{R3}^\bot_{0,0}$.
 \end{proof}
@@
    Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align}
-Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$.
+Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$ (see~\cref{df:root-subsets} for the terminology).
 
 We denote by $Z_\alpha(A, M)$ the subgroup of $\overline{\St}(\Phi, A, M)$ generated by elements
- $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$.
+ $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ (see the beginning of~\cref{sec:elementary} for the definition of the elements $z_\gamma(m, \zeta)$ and the group $\overline{\St}(\Phi, A, M)$).
 It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes U(Z_+(\alpha), M). \]
-It is clear, that $Z_\alpha(A, M)$ centralizes the root subgroup $X_\alpha(A)$ (cf. \cite[984]{St71}).
+In the above formula $U(Z_+(\alpha), M)$ denotes the subgroup defined before~\cref{thm:Stein}.
+It is clear, that $Z_\alpha(A, M)$ centralizes the root subgroup $X_\alpha(A)$ (cf.~\cite[984]{St71}).
 
@@
  \item $x_{\alpha}(f)$. \end{enumerate}
-In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$.
+In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. Notice also that by~\eqref{Zdef} one has $z_\beta(f, 0) = x_\beta(f)$.
 
@@
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
-The assertion is obvious for generators of type 3 and 4.
-
-Suppose $g$ has type 1 or 2 and $\alpha - \beta \in \Phi$. By~\cref{Zrels} we obtain that
-\begin{align} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi), \label{eq3-1} \\
-  z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} = & x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi), \label{eq3-2} \end{align}
-The expressions in the right-hand sides of~\eqref{eq3-1} and~\eqref{eq3-2} are products of generators of type 4, 1, 1 and 4, 1, 2, respectively.
-
-Suppose $g$ has type 1 and $\alpha + \beta \in \Phi$. By~\cref{Zrels} 
-\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi). \end{equation}
+The assertion is obvious for the generators of type 3 and 4.
+
+Let $g = z_\beta(Xf, \xi)$ be a generator of type 1 such that $\alpha - \beta \in \Phi$.
+By~\cref{Zrels}(2) we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
+\label{eq3-1} \end{equation}
+The first and the last factors in the right-hand side of the above equation are generators of type $4$ and $1$, respectively.
+It is easy to see that the second factor is also a generator of type 1, indeed:
+\[ x_{\beta - \alpha} (N_{\beta,-\alpha} \cdot mX^2 f) = z_{\beta'}(Xf', 0)\text{ for } f' = N_{\beta,-\alpha} \cdot mX f\text{ and }\beta' = \beta - \alpha \text{ (clearly, $\alpha + \beta' \in \Phi$).}\]
+Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}(2)
+\begin{equation}
+z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi). \label{eq3-2} \end{equation}
+It is easy to see that the expression in the right-hand side of~\eqref{eq3-2} is a product of generators of type 4, 1, 2.
+
+Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}(3) 
+\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
 and the latter expression is a product of generators of type $4, 1, 1$.
 
-Finally, suppose $g$ has type $5$.
-Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
-\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
+Finally, let $g = x_\alpha(f)$ be a generator of type $5$.
+Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, $\epsilon = N_{\alpha, \beta}$ and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
+\begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
  \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}

### 2020-03-28 dl-paper.tex
Fix 8-9 of 3.5

@@
 \begin{df} \label{df:root-subsets}
-Recall that a root subset $S \subseteq \Phi$ is called {\it closed} if $\alpha, \beta \in S$ and $\alpha+\beta\in \Phi$ imply $\alpha + \beta \in S$. 
-Recall that a closed root subset $S$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $S \cup -S = \Phi$ (resp. $S = -S$, resp. $S \cap (-S) = \varnothing$).
+Recall from~\cite[Ch.~VI, \S~1.7]{Bou81} that a root subset $S \subseteq \Phi$ is called {\it closed} if $\alpha, \beta \in S$ and $\alpha+\beta\in \Phi$ imply $\alpha + \beta \in S$. 
+Recall that a closed root subset $S$ is called {\it parabolic} (resp. {\it symmetric}, resp. {\it special}) if $S \cup -S = \Phi$ (resp. $S = -S$, resp. $S \cap (-S) = \varnothing$).
 The {\it special part} $\Sigma_S$ of a parabolic subset $S$, by definition, consists of all $\alpha \in S$ such that $-\alpha \not\in S$.
@@
 
-\subsection{Computation of the kernel of the map of evaluation at $0$.}
+\subsection{Computation of the kernel of the map of evaluation at $0$.}\label{sec:computationOfK}
 Let $A$ be a local ring with maximal ideal $M$.
@@
    Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align}
-Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$ (see~\cref{df:root-subsets} for the terminology).
+Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a symmetric (resp. special) subset of $\Phi$ (see~\cref{df:root-subsets} for the terminology).
 
@@
 Let $M$ be an ideal of a local ring $A$.
-We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five types of elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
-\begin{enumerate} \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
- \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
- \item $x_{-\alpha}(X^2f);$
- \item $x_{\alpha}(f)$. \end{enumerate}
-In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$. Notice also that by~\eqref{Zdef} one has $z_\beta(f, 0) = x_\beta(f)$.
-
-We also denote by $P_{\alpha, M}(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_{\alpha, M}(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five families of elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
+\begin{enumerate} 
+ \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi,\ f \in M[X],\ \xi \in A[X];$
+ \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi,\ f\in M[X],\ \xi\in A[X];$
+ \item $z_{\beta}(f, \xi),\ \beta \perp \alpha,\ f\in M[X],\ \xi\in A[X];$
+ \item $x_{-\alpha}(X^2f),\ f \in M[X];$
+ \item $x_{\alpha}(f),\ f \in M[X]$. \end{enumerate}
+Notice that in the above definition we use letter $f$ (resp. $\xi$) to denote an element of $M[X]$ (resp. $A[X]$).
+We adhere to this convention until the end of this section.
+Notice also that by~\eqref{Zdef} one has $z_\beta(f, 0) = x_\beta(f)$.
+
+We denote by $P_{\alpha, M}(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_{\alpha, M}(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
 \end{df}
@@
 
-\begin{rem}\label{rem:c-DS} Notice that $P_{\alpha, M}(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3).
-It is also easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
+\begin{rem}\label{rem:c-DS} By~\eqref{Cdef} one has $c_\beta(f, X\xi) = x_{\beta} (f) \cdot z_{\beta}(-f, -X\xi)$.
+This implies that for $\beta \in Z_+(\alpha)$ (resp.
+$\beta \in Z_0(\alpha)$) the element $c_\beta(f, X\xi)$ is a product of two generators of type 2 (resp.
+3).
+Thus, the elements $c_{\beta}(f, X\xi)$ lie in $P_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$.
+
+It is also easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
 In particular, if $M$ is the maximal ideal of $A$, the subgroup $P_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. \end{rem}
@@
 The following lemma shows that $P_{\alpha, M}(*)$ is sufficiently large.
-\begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. Then the subgroup $P_{\alpha, M}(*)$ contains the image of $K(A[X], M[X])$ in $\St(\Phi, A[X, X^{-1}])$. \end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$ hence by~\cref{thm:Stepanov} $P_\alpha(*)$ contains whole $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
-The required assertion now follows from~\cref{Kgen-strong} and the preceding remark.
+\begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. 
+Then the subgroup $P_{\alpha, M}(*)$ contains the image in $\St(\Phi, A[X, X^{-1}])$ of the subgroup $K(A[X], M[X]) \leq \overline{\St}(\Phi, A[X], M[X])$ defined in the beginning of~\cref{sec:computationOfK}.
+\end{lemma}
+\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$, therefore by~\cref{thm:Stepanov} $P_\alpha(*)$ contains all of $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
+The required assertion now follows from~\cref{Kgen-strong} and~\cref{rem:c-DS}.
 \end{proof}

### 2020-03-28 dl-paper.tex
Fix 10 of 3.5 + some extra fixes

@@
 The following proposition is the main result of this subsection and also a direct generalization of~\cite[Lemma~3.3]{Tu83}.
-\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism.
-In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
+\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the homomorphism $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism.
+In particular, the obvious homomorphism $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
 \end{prop}
 \begin{proof}
- We need to construct a map $j_n$ which would be the inverse of $i_n$. 
- We start with a map $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
+ We need to construct a homomorphism $j_n$ which would be the inverse of $i_n$. 
+ We start with a homomorphism $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
  \[ \widetilde{j}^{\Phi}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
@@
 \begin{df} \label{defP0}
-Let $M$ be an ideal of a local ring $A$.
-We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following five families of elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
+Let $M$ be an ideal of a local ring $A$. Denote by $\widetilde{P}_{\alpha, M}(0)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following five families of elements:
 \begin{enumerate} 
@@
  \item $x_{\alpha}(f),\ f \in M[X]$. \end{enumerate}
-Notice that in the above definition we use letter $f$ (resp. $\xi$) to denote an element of $M[X]$ (resp. $A[X]$).
-We adhere to this convention until the end of this section.
+In the sequel we continue to denote the elements of $M[X]$ (resp. $A[X]$) by $f$ (resp. $\xi$).
 Notice also that by~\eqref{Zdef} one has $z_\beta(f, 0) = x_\beta(f)$.
 
-We denote by $P_{\alpha, M}(*)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $P_{\alpha, M}(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
+We denote by $\widetilde{P}_{\alpha, M}(*)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by $\widetilde{P}_{\alpha, M}(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$.
 \end{df}
-
+%We denote by $P_{\alpha, M}(0)$ the image of $\widetilde{P}_{\alpha, M}(0)$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$. 
 Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
@@
 
-\begin{lemma}\label{P0_normal} The subgroup $P_{\alpha, M}(0)$ is normal in $P_{\alpha, M}(*)$.
+\begin{lemma}\label{P0_normal} The subgroup $\widetilde{P}_{\alpha, M}(0)$ is normal in $\widetilde{P}_{\alpha, M}(*)$.
 Moreover, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
-\[\xymatrix{1 \ar[r] & P_\alpha(0) \ar[r] & P_\alpha(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $P_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $P_\alpha(0)$.
+\[\xymatrix{1 \ar[r] & \widetilde{P}_\alpha(0) \ar[r] & \widetilde{P}_\alpha(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
 The assertion is obvious for the generators of type 3 and 4.
@@
 3).
-Thus, the elements $c_{\beta}(f, X\xi)$ lie in $P_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$.
-
-It is also easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
-In particular, if $M$ is the maximal ideal of $A$, the subgroup $P_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. \end{rem}
-
-The following lemma shows that $P_{\alpha, M}(*)$ is sufficiently large.
+Thus, the elements $c_{\beta}(f, X\xi)$ lie in $\widetilde{P}_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$.
+
+It is easy to check that $\widetilde{P}_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \overline{\St}(\Phi, A[X], M[X])$.
+In particular, if $M$ is the maximal ideal of $A$, the subgroup $\widetilde{P}_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols.
+It is also easy to see that, in fact, the image of $\widetilde{P}_{\alpha, M}(0)$ under the homomorphism $ev_{X=0}^*$ coincides with $Z_\alpha(A, M)$.
+\end{rem}
+
+The following lemma shows that $\widetilde{P}_{\alpha, M}(*)$ is sufficiently large.
 \begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. 
-Then the subgroup $P_{\alpha, M}(*)$ contains the image in $\St(\Phi, A[X, X^{-1}])$ of the subgroup $K(A[X], M[X]) \leq \overline{\St}(\Phi, A[X], M[X])$ defined in the beginning of~\cref{sec:computationOfK}.
-\end{lemma}
-\begin{proof} Clearly, $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$, therefore by~\cref{thm:Stepanov} $P_\alpha(*)$ contains all of $j_+(\overline{\St}(\Phi, A[X], XM[X]))$.
+Then the subgroup $\widetilde{P}_{\alpha, M}(*)$ contains the subgroup $K(A[X], M[X]) \leq \overline{\St}(\Phi, A[X], M[X])$ defined in the beginning of~\cref{sec:computationOfK}. \end{lemma}
+\begin{proof} Clearly, $\widetilde{P}_{\alpha, M}(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$, therefore by~\cref{thm:Stepanov} $\widetilde{P}_{\alpha, M}(*)$ contains all of $\overline{\St}(\Phi, A[X], XM[X])$.
 The required assertion now follows from~\cref{Kgen-strong} and~\cref{rem:c-DS}.
@@
 
-\begin{rem} \label{Pstar-char} The above lemma allows us to characterize $P_{\alpha, M}(*)$ as follows: it coincides with the image under $j_+$ of the subgroup 
-of $\overline{\St}(\Phi, A[X], M[X])$ consisting of those elements $g$ for which $ev_{X=0}^*(g)$ lies in the subgroup $Z_\alpha(A, M)$. \end{rem}
+\begin{rem} \label{Pstar-char} 
+By the above lemma and~\cref{rem:c-DS} the subgroup $\widetilde{P}_{\alpha, M}(*)$ coincides with the preimage of the subgroup $Z_\alpha(A, M) \leq \overline{\St}(\Phi, A, M)$ under the homomorphism
+ \[ev_{X=0}^*\colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M).\] \end{rem}
 
@@
 \begin{lemma} \label{P0-conj-invariant} Suppose $(A, M)$ is a local pair.
-Then for any $\beta \in Z(\alpha)$ and $b \in A$ the subgroups $P_{\alpha, M}(0)$ and $P_{\alpha, M}(*)$ are stable under conjugation by $x_\beta(b)$.
+Then for any $\beta \in Z(\alpha)$ and $b \in A$ the subgroups $\widetilde{P}_{\alpha, M}(0)$ and $\widetilde{P}_{\alpha, M}(*)$ are stable under conjugation by $x_\beta(b)$.
 \end{lemma}
 \begin{proof}
-Notice that both $Z_\alpha(A, M)$ and $K(A[X], M[X])$ are stable under the specified conjugation, which implies the assertion for $P_{\alpha, M}(*)$. 
+Notice that both $Z_\alpha(A, M)$ and $K(A[X], M[X])$ are stable under the specified conjugation, which implies the assertion for $\widetilde{P}_{\alpha, M}(*)$. 
 To obtain the assertion for $P_{\alpha, M}(0)$ consider the following commutative diagram.
-\[ \xymatrix{ P_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & P_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & (M, +) \ar@{^{(}->}[d] \\ P_{\alpha, A}(0) \ar@{^{(}->}[r] & P_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & (A, +)} \]
-Notice that $x_\beta(b) \in P_{\alpha, A}(0)$ therefore for $g \in P_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
-
-For the rest of this section $M$ denotes the maximal ideal of $A$, so everywhere below we shorten the notation for $P_{\alpha, M}(*)$ (resp.
-$P_{\alpha, M}(0)$) to just $P_{\alpha}(*)$ (resp.
-$P_{\alpha}(0)$).
+\[ \xymatrix{ \widetilde{P}_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & \widetilde{P}_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & (M, +) \ar@{^{(}->}[d] \\ \widetilde{P}_{\alpha, A}(0) \ar@{^{(}->}[r] & \widetilde{P}_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & (A, +)} \]
+Notice that $x_\beta(b) \in \widetilde{P}_{\alpha, A}(0)$ therefore for $g \in \widetilde{P}_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
+
+For the rest of this section $M$ denotes the maximal ideal of $A$.
+\begin{df} 
+Define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
+\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
+where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious embedding.
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$, which allows us to give the following definition.
-
-\begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$.
+
+Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
 \[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}
-It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
+It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
 \begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\end{equation}
 
-It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the map of left conjugation by $x_\alpha(aX^{-1})$.
+It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
 

### 2020-03-30 dl-paper.tex
Fix 11 of 3.5 + small fixes

@@
 Let $g = z_\beta(Xf, \xi)$ be a generator of type 1 such that $\alpha - \beta \in \Phi$.
-By~\cref{Zrels}(2) we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
+By~\cref{Zrels}\eqref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
 \label{eq3-1} \end{equation}
@@
 \[ x_{\beta - \alpha} (N_{\beta,-\alpha} \cdot mX^2 f) = z_{\beta'}(Xf', 0)\text{ for } f' = N_{\beta,-\alpha} \cdot mX f\text{ and }\beta' = \beta - \alpha \text{ (clearly, $\alpha + \beta' \in \Phi$).}\]
-Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}(2)
+Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}\eqref{Z2}
 \begin{equation}
@@
 
-Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}(3) 
+Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\eqref{Z3}
 \begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
@@
 \begin{df} 
-Define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
+We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
 \[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
-where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious embedding.
+where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious homomorphism.
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
+
 From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$.
-
-Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
 \[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}
-It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
-\begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\end{equation}
-
+
+In the sequel we often use the following property of $S_\alpha(a, -)$.
+\begin{lemma} \label{lem:Smult}
+For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
+$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
+\end{lemma} \begin{proof} Since $g_2\in P_\alpha(m')$ for some $m' \in M$, we have that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
+\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) \cdot g_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot g_2 \cdot x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \{X, (1+am)(1 + \tfrac{am'}{1+am})\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
+\qedhere \end{multline*}
+\end{proof}
 It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
-
 \begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
+\begin{proof} 
+We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g$ from~\cref{defP0} lies in $P_\alpha(0)$. 
 The assertion is clear for generators of type 3 and 5.
@@
 Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
-Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
+Now by~\cref{lem:Smult} and~\cref{P0_conj} one has
 \begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
@@
 \] \end{lemma}
-\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\cref{lem:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
 \end{multline}
@@
 Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$.
-The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
+The required assertion now follows from \cref{lem:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
 \begin{multline} \nonumber
@@
 \begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
-Using~\eqref{eq:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
+Using~\cref{lem:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
 

### 2020-03-31 dl-paper.tex
Fix 12

@@
 \usepackage[notref,notcite]{showkeys}
+\usepackage{MnSymbol}
 
@@
  \item $x_{\alpha}(f),\ f \in M[X]$. \end{enumerate}
-In the sequel we continue to denote the elements of $M[X]$ (resp. $A[X]$) by $f$ (resp. $\xi$).
-Notice also that by~\eqref{Zdef} one has $z_\beta(f, 0) = x_\beta(f)$.
 
@@
 \end{df}
-%We denote by $P_{\alpha, M}(0)$ the image of $\widetilde{P}_{\alpha, M}(0)$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$. 
+
 Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
 The only exception to this is~\cref{P0-conj-invariant} where the above subgroups are also used for $M=A$.
+\begin{rem} \label{rem:recognition}
+  From the above definition it follows that an element $z_\gamma(f, \xi)$ is a generator of type 1 provided $X \divides f$, $\gamma\neq\pm\alpha$ and $\gamma$ is not orthogonal to $\alpha$.
+  Since $x_\gamma(f) = z_\gamma(f, 0)$, it follows that under the same assumptions $x_{\gamma}(f)$ is also a generator of type 1.
+  In particular, if $\beta, \alpha - \beta \in \Phi$ then $x_{\pm(\alpha-\beta)}(Xf)$ is a generator of type 1.
+
+  Similarly, if $\gamma - \alpha \in \Phi$ and $X \divides \xi$ then $z_\gamma(f, \xi)$ is a generator of type 2.
+  In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\alpha+\beta}(f)$ is a generator of type 2.
+\end{rem}
 
@@
 
-Let $g = z_\beta(Xf, \xi)$ be a generator of type 1 such that $\alpha - \beta \in \Phi$.
+Let $\beta\in\Phi$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type 1.
 By~\cref{Zrels}\eqref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
 \label{eq3-1} \end{equation}
-The first and the last factors in the right-hand side of the above equation are generators of type $4$ and $1$, respectively.
-It is easy to see that the second factor is also a generator of type 1, indeed:
-\[ x_{\beta - \alpha} (N_{\beta,-\alpha} \cdot mX^2 f) = z_{\beta'}(Xf', 0)\text{ for } f' = N_{\beta,-\alpha} \cdot mX f\text{ and }\beta' = \beta - \alpha \text{ (clearly, $\alpha + \beta' \in \Phi$).}\]
-Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}\eqref{Z2}
+The expression in the right-hand side is a product of generators of type 4, 1, 1 (see~\cref{rem:recognition}).
+Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$ (so that $\alpha-\beta\in\Phi$). Again by~\cref{Zrels}\eqref{Z2}
 \begin{equation}
@@
 $S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
-\end{lemma} \begin{proof} Since $g_2\in P_\alpha(m')$ for some $m' \in M$, we have that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
+\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
 \begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) \cdot g_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot g_2 \cdot x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \{X, (1+am)(1 + \tfrac{am'}{1+am})\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
@@
 \begin{proof} 
-We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g$ from~\cref{defP0} lies in $P_\alpha(0)$. 
-The assertion is clear for generators of type 3 and 5.
-First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
-\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
-Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.
-
-Now consider the case $\alpha - \beta \in \Phi$, which is possible for generators of type 1 and 2. By~\cref{Zrels} we obtain that
-\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \\
-z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \nonumber \end{align}
-The expressions in the right-hand side are products of generators of type 5, 2, 1 and 5, 1, 2.
+Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
+The assertion is clear for the generators of type 3 and 5.
+
+Let $\beta$ be such that $\alpha + \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type $1$.
+By~\cref{Zrels}\eqref{Z2}
+\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
+and the latter expression a product of generators of type 5, 2, 1 (see~\cref{rem:recognition}).
+
+Let $\beta$ be such that $\alpha - \beta \in \Phi$ and let $g = z_{\beta}(Xf, \xi)$ be a generator of type $1$. From~\cref{Zrels}~\eqref{Z3} we obtain that
+\begin{equation} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
+and the expression in the right-hand side is a product of generators of type 5, 2, 1.
+Now let $g = z_{\beta}(f, X\xi)$ be a generator of type 2 (for $\beta$ as above). Again by~\cref{Zrels}~\ref{Z3}
+\begin{equation} z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
+\end{equation}
+and the expression in the right-hand side are products of generators of type 5, 1, 2.
 

### 2020-04-01 dl-paper.tex
Fix 13, 14 of 3.5

@@
 \usepackage[notref,notcite]{showkeys}
-\usepackage{MnSymbol}
 
@@
 Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free.
-Thшы problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory.
+This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory.
 We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
@@
 For these and other properties of symbols we refer the reader to~\cite{DS73}.
+From~\eqref{eq:symbol-properties} it follows that
+\begin{equation} \label{eq:symbol-inverse} \{u, v\}^{-1} = \{u^{-1}, v\} = \{u, v^{-1}\}. \end{equation}
 
@@
 \begin{rem} \label{rem:recognition}
-  From the above definition it follows that an element $z_\gamma(f, \xi)$ is a generator of type 1 provided $X \divides f$, $\gamma\neq\pm\alpha$ and $\gamma$ is not orthogonal to $\alpha$.
-  Since $x_\gamma(f) = z_\gamma(f, 0)$, it follows that under the same assumptions $x_{\gamma}(f)$ is also a generator of type 1.
-  In particular, if $\beta, \alpha - \beta \in \Phi$ then $x_{\pm(\alpha-\beta)}(Xf)$ is a generator of type 1.
-
-  Similarly, if $\gamma - \alpha \in \Phi$ and $X \divides \xi$ then $z_\gamma(f, \xi)$ is a generator of type 2.
-  In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\alpha+\beta}(f)$ is a generator of type 2.
+  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type 1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$.
+Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1.
+In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
 \end{rem}
@@
 Finally, let $g = x_\alpha(f)$ be a generator of type $5$.
-Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, $\epsilon = N_{\alpha, \beta}$ and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
+Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
 \begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
  \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
-and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}
+where $\epsilon = N_{\alpha, \beta}$. It is clear that the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}
 
@@
 For the rest of this section $M$ denotes the maximal ideal of $A$.
-\begin{df} 
+\begin{df}\label{S-def}
 We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
@@
 This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
-\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}
+\begin{equation}\label{eq:S-def} S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\end{equation} \end{df}
 
@@
 $S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
-\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
-\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) \cdot g_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot g_2 \cdot x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \{X, (1+am)(1 + \tfrac{am'}{1+am})\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
+\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$.
+The assertion now follows from the definition of $S_\alpha(a, -)$ and the centrality of Steinberg symbols:
+\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
 \qedhere \end{multline*}
@@
 By~\cref{Zrels}\eqref{Z2}
-\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
+\begin{equation}\label{eq:Zconj1} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
 and the latter expression a product of generators of type 5, 2, 1 (see~\cref{rem:recognition}).
 
-Let $\beta$ be such that $\alpha - \beta \in \Phi$ and let $g = z_{\beta}(Xf, \xi)$ be a generator of type $1$. From~\cref{Zrels}~\eqref{Z3} we obtain that
-\begin{equation} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
+Let $\beta$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type 1. By~\cref{Zrels}\eqref{Z3}
+\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
 and the expression in the right-hand side is a product of generators of type 5, 2, 1.
-Now let $g = z_{\beta}(f, X\xi)$ be a generator of type 2 (for $\beta$ as above). Again by~\cref{Zrels}~\ref{Z3}
-\begin{equation} z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
-\end{equation}
-and the expression in the right-hand side are products of generators of type 5, 1, 2.
-
-Let us verify the assertion for a generator of type 4.
+
+Now if $g = z_{\beta}(f, X\xi)$ is a generator of type 2 for $\alpha - \beta \in \Phi$, we obtain by~\cref{Zrels}\eqref{Z3} that
+\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
+\end{equation} and the expression in the right-hand side is a product of generators of type 5, 1, 2.
+
+It remains to verify the assertion for a generator $g = x_{-\alpha}(X^2f)$ of type 4.
 Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
@@
 \end{lemma}
-\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$.
-Direct computation using~\eqref{eq:conj-h-x}--\eqref{eq:dennis-stein},\eqref{eq:symbol-properties} shows that
- \begin{multline*}
- x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
- = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}, \end{multline*}
-which implies the assertion. \end{proof}
-
-\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
-Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
+\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
+ \begin{align} 
+ x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) &\text{ by~\eqref{eq:conj-h-x}} \label{eq:Tf-comp} \\
+ = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) &\text{ by~\eqref{eq:dennis-stein}} \nonumber \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) &\text{ by~\eqref{eq:conj-h-x}, \eqref{eq:conj-h-h}} \nonumber \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right)&\text{ by~\eqref{eq:steinberg}} \nonumber \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}.
+\nonumber \end{align}
+The assertion of the lemma now follows from the following computation:
+\begin{align*}
+ S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}  \end{proof}
+
+\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am).
+\]\end{corollary} \begin{proof}
 Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
-Now by~\cref{lem:Smult} and~\cref{P0_conj} one has
-\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
-\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}
-
-The second assertion can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}
+Direct computation shows that
+\begin{align*}
+ S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)&\text{ by~\cref{lem:Smult}} \\\
+ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle &\text{ by~\cref{lem:Tulenbaev-formula}.}
+\end{align*}
+By \cref{P0_conj} and \cref{rem:c-DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$.
+Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$.
+
+The second assertion of the lemma can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}
 

### 2020-04-01 dl-paper.tex
Minor

@@
 In particular, if $M$ is the maximal ideal of $A$, the subgroup $\widetilde{P}_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols.
-It is also easy to see that, in fact, the image of $\widetilde{P}_{\alpha, M}(0)$ under the homomorphism $ev_{X=0}^*$ coincides with $Z_\alpha(A, M)$.
+It is also easy to see that the image of $\widetilde{P}_{\alpha, M}(0)$ under the homomorphism $ev_{X=0}^*$ coincides with $Z_\alpha(A, M)$.
 \end{rem}
@@
 \end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$.
-The assertion now follows from the definition of $S_\alpha(a, -)$ and the centrality of Steinberg symbols:
+The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
 \begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).

### 2020-04-02 dl-paper.tex
Fix most of 16 of 3.5

@@
 \begin{df} \label{defP0}
-Let $M$ be an ideal of a local ring $A$. Denote by $\widetilde{P}_{\alpha, M}(0)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following five families of elements:
+Let $M$ be an ideal of a local ring $A$.
+Denote by $\widetilde{P}_{\alpha, M}(0)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parameterized by $f \in M[X]$, $\xi \in A[X]$:
 \begin{enumerate} 
  \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi,\ f \in M[X],\ \xi \in A[X];$
- \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi,\ f\in M[X],\ \xi\in A[X];$
- \item $z_{\beta}(f, \xi),\ \beta \perp \alpha,\ f\in M[X],\ \xi\in A[X];$
- \item $x_{-\alpha}(X^2f),\ f \in M[X];$
- \item $x_{\alpha}(f),\ f \in M[X]$. \end{enumerate}
+ \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
+ \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
+ \item $x_{-\alpha}(X^2f)$;
+ \item $x_{\alpha}(f)$. \end{enumerate}
 
@@
 \end{df}
-
 Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
 The only exception to this is~\cref{P0-conj-invariant} where the above subgroups are also used for $M=A$.
+
+In the sequel we continue using letters $f$ and $\xi$ to denote elements of $M[X]$ and $A[X]$, respectively.
+
 \begin{rem} \label{rem:recognition}
@@
 Moreover, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
-\[\xymatrix{1 \ar[r] & \widetilde{P}_\alpha(0) \ar[r] & \widetilde{P}_\alpha(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
+\[\xymatrix{1 \ar[r] & \widetilde{P}_{\alpha,M}(0) \ar[r] & \widetilde{P}_{\alpha,M}(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
@@
 \begin{df}\label{S-def}
-We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
-\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
-where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious homomorphism.
+Define the subgroup $P_\alpha(0)$ (resp. $P_{\alpha}(*)$) of $\overline{\St}(\Phi, R, M[X, X^{-1}])$
+ as the image of the subgroup $\widetilde{P}_{\alpha, M}(0)$ (resp. $\widetilde{P}_{\alpha, M}(*)$) 
+ under the obvious homomorphism  $j_+ \colon \overline{\St}(\Phi, A[X]) \to \overline{\St}(\Phi, R)$.
+
 For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
-
 From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$.
@@
 We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df}\label{def:Kab} Denote by $\widetilde{K}(\alpha, \beta)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
+\begin{df}\label{def:Kab} 
+Fix a root $\delta \in \Phi \setminus \Psi$.
+Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
  \begin{enumerate}
@@
   \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
-  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate}
+  \item $c_{\delta}(f, X\xi)$. \end{enumerate}
 Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}
-
 \begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in \widetilde{K}(\alpha, \beta)$.
@@
 For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
-By~\cref{thm:Stepanov} every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
-In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
-
-By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
+Notice that $\Phi \setminus \Psi$ contains the parabolic set of roots $(\Phi \setminus \Psi)\cap \Phi^+$.
+Thus, by~\cref{thm:Stepanov} every element of $\overline{\St}(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
+In turn, by~\cref{Kgen-strong} one can express $g \in K(A[X], M[X])$ as a product of these generators and generators $\mathcal{G}_5$.
+
+By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
 By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, for some $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
 
-It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$, $\gamma_1, \gamma_2 \in \Psi$.
+It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$ for $\gamma_1, \gamma_2 \in \Psi$.
 On the other hand, for $\gamma \in \Psi$ any commutator $c_{\gamma}(mX, m'X)$ is congruent to some generator of $\mathcal{G}_5$  modulo $G_0$ (cf.
@@
 
-Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f', m'$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
+Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f' \in M[X]$, $m' \in M$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
 By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after simplification of these conjugates.
@@
 It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$. 
-The reverse inclusion follows from the just proved decomposition and the fact that for $g\in j_+(K(A[X], M[X]))$ holds $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$ (cf.~\cref{rem:palpha}).
+Let us prove the reverse inclusion. Let $g$ be an element of the intersection $P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$.
+By the first part of the proposition $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\alpha}(m'X)$ for some $g_0 \in K(\alpha, \beta)$ and $m, m' \in M$.
+From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $K(\alpha, \beta)$, as required.
 \end{proof}

### 2020-04-03 dl-paper.tex
Minor fixes

@@
 From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$.
-This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+This allows us to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
 \begin{equation}\label{eq:S-def} S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\end{equation} \end{df}

### 2020-04-04 dl-paper.tex
Many minor fixes

@@
 \begin{enumerate} 
- \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi,\ f \in M[X],\ \xi \in A[X];$
+ \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
  \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
@@
 \[\xymatrix{1 \ar[r] & \widetilde{P}_{\alpha,M}(0) \ar[r] & \widetilde{P}_{\alpha,M}(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~Definition~\ref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~\cref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
 The assertion is obvious for the generators of type 3 and 4.
@@
 
-\begin{rem}\label{rem:c-DS} By~\eqref{Cdef} one has $c_\beta(f, X\xi) = x_{\beta} (f) \cdot z_{\beta}(-f, -X\xi)$.
+\begin{rem}\label{rem:c} By~\eqref{Cdef} one has $c_\beta(f, X\xi) = x_{\beta} (f) \cdot z_{\beta}(-f, -X\xi)$.
 This implies that for $\beta \in Z_+(\alpha)$ (resp.
@@
 3).
-Thus, the elements $c_{\beta}(f, X\xi)$ lie in $\widetilde{P}_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$.
-
+Thus, the elements $c_{\beta}(f, X\xi)$ lie in $\widetilde{P}_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$. \end{rem}
+\begin{rem}\label{rem:DS}
 It is easy to check that $\widetilde{P}_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \overline{\St}(\Phi, A[X], M[X])$.
@@
 \begin{proof} Clearly, $\widetilde{P}_{\alpha, M}(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$, therefore by~\cref{thm:Stepanov} $\widetilde{P}_{\alpha, M}(*)$ contains all of $\overline{\St}(\Phi, A[X], XM[X])$.
-The required assertion now follows from~\cref{Kgen-strong} and~\cref{rem:c-DS}.
+The required assertion now follows from~\cref{Kgen-strong} and~\cref{rem:c}.
 \end{proof}
@@
 \begin{rem} \label{Pstar-char} 
-By the above lemma and~\cref{rem:c-DS} the subgroup $\widetilde{P}_{\alpha, M}(*)$ coincides with the preimage of the subgroup $Z_\alpha(A, M) \leq \overline{\St}(\Phi, A, M)$ under the homomorphism
- \[ev_{X=0}^*\colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M).\] \end{rem}
+By the above lemma and~\cref{rem:DS} the subgroup $\widetilde{P}_{\alpha, M}(*)$ coincides with the preimage of the subgroup $Z_\alpha(A, M) \leq \overline{\St}(\Phi, A, M)$ under the homomorphism \[ev_{X=0}^*\colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M).\] \end{rem}
 
@@
 Notice that both $Z_\alpha(A, M)$ and $K(A[X], M[X])$ are stable under the specified conjugation, which implies the assertion for $\widetilde{P}_{\alpha, M}(*)$. 
-To obtain the assertion for $P_{\alpha, M}(0)$ consider the following commutative diagram.
+To obtain the assertion for $\widetilde{P}_{\alpha, M}(0)$ consider the following commutative diagram.
 \[ \xymatrix{ \widetilde{P}_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & \widetilde{P}_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & (M, +) \ar@{^{(}->}[d] \\ \widetilde{P}_{\alpha, A}(0) \ar@{^{(}->}[r] & \widetilde{P}_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & (A, +)} \]
-Notice that $x_\beta(b) \in \widetilde{P}_{\alpha, A}(0)$ therefore for $g \in \widetilde{P}_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
+Notice that $x_\beta(b) \in \widetilde{P}_{\alpha, A}(0)$, therefore for $g \in \widetilde{P}_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
 
@@
  as the image of the subgroup $\widetilde{P}_{\alpha, M}(0)$ (resp. $\widetilde{P}_{\alpha, M}(*)$) 
- under the obvious homomorphism  $j_+ \colon \overline{\St}(\Phi, A[X]) \to \overline{\St}(\Phi, R)$.
+ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.
 
@@
 \end{align*}
-By \cref{P0_conj} and \cref{rem:c-DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$.
+By \cref{P0_conj} and \cref{rem:DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$.
 Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$.
@@
  Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B^-)$.
- By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$ therefore, by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
+ By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
  Since $j_+i_+$ is injective, we conclude that $g = 1$.

### 2020-04-06 dl-paper.tex
Restructuring...

@@
 Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.
-$Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
+$Z_0(\alpha) = \{ \beta\in\Phi \mid \alpha \perp \beta \}$
 (cf.~\cite[Proposition~5.7]{St71}).
@@
 We need one more technical definition.
-We denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $z_\gamma(f, X\xi)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+We denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $x_\gamma(f)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ and $f \in M[X]$.
+To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
 
@@
 \end{lemma}
-\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
-By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate of a generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1.
-\cref{Crels} also shows that the conjugate of a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
-
-The conjugation by $x_\alpha(aX^{-1})$ fixes both types of generators of type 3 and transforms $x_{-\beta}(X^2f)$ into a product of generators of type 2, 4.
-The conjugation also fixes $x_{-\alpha-\beta}(Xf)$ and transforms $x_{\beta-\alpha}(Xf)$ into a product of generators of type 4, Z.
-
-Now pick a root $\gamma \in \Phi \setminus \Psi$ such that $\alpha + \gamma \in \Phi$.
+\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ of every generator from~\cref{def:Kab} lies in the specified subgroup.
+
+Let $g = z_\gamma(Xf, \xi)$ be a generator of type $1$ for some $\gamma \in \Phi \setminus \Psi$.
+In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
+If $\gamma$ is such that $\alpha + \gamma \in \Phi$ we obtain from~\cref{Zrels}\eqref{Z2} that
+\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\gamma} (N_{\gamma, \alpha}\cdot af) \cdot z_{\gamma}(Xf, \xi). \end{equation}
+If, on the other hand, $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
+\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
+By the choice of $\gamma$ both $\alpha + \gamma$ and $\alpha - \gamma$ lie in $Z_+(\alpha) \setminus \{\alpha - \beta\}$, therefore in both cases the expressions in the right-hand side are products of generators of type Z, Z, 1.
+
+A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
+
+Now let us verify the assertion for the generators of types 2--4.
+By~\eqref{Chevalley-CCF2} the conjugation by $x_\alpha(aX^{-1})$ fixes root subgroups $X_{\alpha}(X\cdot M[X])$, $X_{\beta}(X\cdot M[X])$, $X_{\alpha-\beta}(X\cdot M[X])$. 
+On the other hand, from~\eqref{Chevalley-CCF1} we get that
+\begin{align*}
+ x_{-\beta}(X^2f)^{x_\alpha(aX^{-1})}     &= x_{-\beta}(X^2f) \cdot x_{\alpha-\beta}(N_{-\beta, \alpha} \cdot aXf);\\
+ x_{\beta-\alpha}(Xf)^{x_\alpha(aX^{-1})} &= x_{\beta-\alpha}(Xf) \cdot x_{\beta}(N_{\alpha,-\beta}\cdot af).
+\end{align*}
+Clearly, the expressions in the right-hand side are products of generators of type 2, 4 and 4, Z.
+
+Now pick a root $\gamma \in \Phi \setminus \Psi$ such that $\alpha + \gamma \in \Phi$. Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \gamma$ into~\eqref{Z5} we obtain that
+\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\gamma}(\epsilon Xf) \cdot x_{-\gamma}(-af) \cdot x_{\gamma}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
+ \cdot z_{-\alpha-\gamma}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\gamma}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\gamma}(a f, -X), \end{multline*}
+where $\epsilon = N_{\gamma,\alpha}$. 
+It is clear that the the first 7 factors in the right-hand side are generators of type
+1, Z, 1, 2, 1, 1, Z.
+
 From~\eqref{eq:Zconj3} in which $\gamma$ is substituted for $\beta$ it follows that  $z_{-\alpha}(X^2f, aX^{-1})$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z\@.
+\end{proof}
+
+\begin{lemma} \label{P0_conj-alternative} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
+\begin{proof} It follows from~\cref{K-a-b} that $\widetilde{P}_\alpha(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
+Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
+$\widetilde{P}_\alpha(0) =  \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right) \rtimes Z_\alpha(A, M).$
+
+Thus, in view of~\cref{image-K-a-b} it remains to show that $X_{-\beta}(MX)^{x_\alpha(aX^{-1})} \subseteq P_\alpha(0)$ and $Z_{\alpha, \beta}^{x_\alpha(aX^{-1})} \subseteq P_\alpha(0)$.
 \end{proof}

### 2020-04-07 dl-paper.tex
Change definition of Zab

@@
 \begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
-\begin{proof} 
-Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
-The assertion is clear for the generators of type 3 and 5.
-
-Let $\beta$ be such that $\alpha + \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type $1$.
-By~\cref{Zrels}\eqref{Z2}
-\begin{equation}\label{eq:Zconj1} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
-and the latter expression a product of generators of type 5, 2, 1 (see~\cref{rem:recognition}).
-
-Let $\beta$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type 1. By~\cref{Zrels}\eqref{Z3}
-\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
-and the expression in the right-hand side is a product of generators of type 5, 2, 1.
-
-Now if $g = z_{\beta}(f, X\xi)$ is a generator of type 2 for $\alpha - \beta \in \Phi$, we obtain by~\cref{Zrels}\eqref{Z3} that
-\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
-\end{equation} and the expression in the right-hand side is a product of generators of type 5, 1, 2.
-
-It remains to verify the assertion for a generator $g = x_{-\alpha}(X^2f)$ of type 4.
-Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} we obtain that
-\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
- \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
-where $\epsilon = N_{-\alpha-\beta,\beta}$. 
-Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}
+\begin{proof} ??? \end{proof}
 
@@
 Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}
-\begin{prop} \label{K-a-b} Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in \widetilde{K}(\alpha, \beta)$.
-Consequently, $K(\alpha, \beta)$ coincides with the intersection $j_+(K(A[X], M[X])) \cap P_\alpha(0) \cap P_\beta(0)$.
-In particular, $K(\alpha, \beta)$ does not depend on the choice of the root $\delta$.
+\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. 
 \end{prop} 
 \begin{proof}
+It is clear that $K(A[X], M[X]) \supseteq \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$.
+Let us prove the reverse inclusion.
+Fix an element $g\in K(A[X], M[X])$.
+We need to show that $g$ lies in the product of subgroups in the right-hand side.
+
 For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
@@
 Thus, by~\cref{thm:Stepanov} every element of $\overline{\St}(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
-In turn, by~\cref{Kgen-strong} one can express $g \in K(A[X], M[X])$ as a product of these generators and generators $\mathcal{G}_5$.
+In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
 
@@
 Thus, we can rewrite $g_2$ as $g_{21} \cdot g_{22}$, where $g_{21} \in \langle \mathcal{G}_2, \mathcal{G}_3, \mathcal{G}_4, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_{22} \in \langle X_{-\alpha}(MX), X_{-\beta}(MX) \rangle = X_{-\alpha}(MX) \cdot X_{-\beta}(MX)$.
-Thus, we have obtained the desired decomposition for $g$.
-
-It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$. 
-Let us prove the reverse inclusion. Let $g$ be an element of the intersection $P_\alpha(0) \cap P_\beta(0) \cap j_+(K(A[X], M[X]))$.
-By the first part of the proposition $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\alpha}(m'X)$ for some $g_0 \in K(\alpha, \beta)$ and $m, m' \in M$.
-From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $K(\alpha, \beta)$, as required.
-\end{proof}
+Thus, we have obtained the desired decomposition for $g$. \end{proof}
+
+\begin{corollary} \label{K-a-b-cor}
+One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$.
+In particular, $\widetilde{K}(\alpha, \beta)$ and $K(\alpha, \beta)$ do not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
+\end{corollary}
+\begin{proof} It is clear that $\widetilde{K}(\alpha, \beta) \subseteq \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$. 
+Let us prove the reverse inclusion. Let $g$ be an element of the intersection of subgroups in the right-hand side.
+By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\alpha}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
+From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}
+
+\begin{corollary} \label{K-a-b-cor2}
+ One has $\widetilde{P}_\alpha(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
+\end{corollary}
+\begin{proof} ??? \end{proof}
 
@@
 
-Let $g = z_\gamma(Xf, \xi)$ be a generator of type $1$ for some $\gamma \in \Phi \setminus \Psi$.
+Let $z_\gamma(Xf, \xi)$ be a generator of type $1$ for some $\gamma \in \Phi \setminus \Psi$.
 In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
@@
 \begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\gamma} (N_{\gamma, \alpha}\cdot af) \cdot z_{\gamma}(Xf, \xi). \end{equation}
-If, on the other hand, $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
+On the other hand, if $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
 \begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
@@
 
-Now let us verify the assertion for the generators of types 2--4.
+Let us verify the assertion for the generators of types 2--4.
 By~\eqref{Chevalley-CCF2} the conjugation by $x_\alpha(aX^{-1})$ fixes root subgroups $X_{\alpha}(X\cdot M[X])$, $X_{\beta}(X\cdot M[X])$, $X_{\alpha-\beta}(X\cdot M[X])$. 
-On the other hand, from~\eqref{Chevalley-CCF1} we get that
+Further, from~\eqref{Chevalley-CCF1} we obtain that
 \begin{align*}
  x_{-\beta}(X^2f)^{x_\alpha(aX^{-1})}     &= x_{-\beta}(X^2f) \cdot x_{\alpha-\beta}(N_{-\beta, \alpha} \cdot aXf);\\
- x_{\beta-\alpha}(Xf)^{x_\alpha(aX^{-1})} &= x_{\beta-\alpha}(Xf) \cdot x_{\beta}(N_{\alpha,-\beta}\cdot af).
+ x_{\beta-\alpha}(Xf)^{x_\alpha(aX^{-1})} &= x_{\beta-\alpha}(Xf) \cdot x_{\beta}(N_{\alpha,-\beta}\cdot af),
 \end{align*}
-Clearly, the expressions in the right-hand side are products of generators of type 2, 4 and 4, Z.
-
-Now pick a root $\gamma \in \Phi \setminus \Psi$ such that $\alpha + \gamma \in \Phi$. Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \gamma$ into~\eqref{Z5} we obtain that
-\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\gamma}(\epsilon Xf) \cdot x_{-\gamma}(-af) \cdot x_{\gamma}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
- \cdot z_{-\alpha-\gamma}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\gamma}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\gamma}(a f, -X), \end{multline*}
-where $\epsilon = N_{\gamma,\alpha}$. 
-It is clear that the the first 7 factors in the right-hand side are generators of type
-1, Z, 1, 2, 1, 1, Z.
-
-From~\eqref{eq:Zconj3} in which $\gamma$ is substituted for $\beta$ it follows that  $z_{-\alpha}(X^2f, aX^{-1})$ is a product of generators of type 1, Z, 1, 2, 1, 1, Z, Z\@.
-\end{proof}
+and the expressions in the right-hand side are products of generators of type 2, 4 and 4, Z.
+
+It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type 2.
+By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e.
+$\alpha-\delta \in \Phi$.
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$ into~\eqref{Z5} we obtain that
+\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
+ \cdot z_{\delta-\alpha}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha-\delta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{\delta}(a f, -X), \end{multline*}
+where $\epsilon = N_{-\delta,\alpha}$. 
+The first 7 factors in the right-hand side are generators of type 1, Z, 1, 2, 1, 1, Z.
+The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and therefore is a product of generators of type Z and 5. \end{proof}
 
 \begin{lemma} \label{P0_conj-alternative} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
-\begin{proof} It follows from~\cref{K-a-b} that $\widetilde{P}_\alpha(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
-Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
+\begin{proof} Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
 $\widetilde{P}_\alpha(0) =  \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right) \rtimes Z_\alpha(A, M).$

### 2020-04-07 dl-paper.tex
Minor fixes

@@
 Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1.
-In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
+In particular, if $\beta$ is such that $\alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
 \end{rem}
@@
 
-\begin{rem} \label{Pstar-char} 
-By the above lemma and~\cref{rem:DS} the subgroup $\widetilde{P}_{\alpha, M}(*)$ coincides with the preimage of the subgroup $Z_\alpha(A, M) \leq \overline{\St}(\Phi, A, M)$ under the homomorphism \[ev_{X=0}^*\colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M).\] \end{rem}
+\begin{rem} \label{Pstar-char} From the above lemma and~\cref{rem:DS} it follows that the subgroup $\widetilde{P}_{\alpha, M}(*)$ admits decomposition $\widetilde{P}_{\alpha, M}(*) = Z_\alpha(A, M) \ltimes K(A[X], M[X]).$ \end{rem}
 
@@
 It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
-\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
-\begin{proof} ??? \end{proof}
 
@@
 \begin{corollary} \label{K-a-b-cor2}
- One has $\widetilde{P}_\alpha(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
+ One has $\widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X]) =  \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
 \end{corollary}
@@
 
-\begin{lemma} \label{P0_conj-alternative} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
+\begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
 \begin{proof} Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
@@
 
+\subsection{The map \texorpdfstring{$S_\alpha$}{Sa} and its properties.}
+
 \subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor.} \label{sec:V-construction}

### 2020-04-08 dl-paper.tex
Fix 17-18

@@
 Since $ev_{X=0}^*$ admits a section, we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
- moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
+ moreover, one has 
+\begin{equation} \label{eq:sd-decomp} \overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \ltimes K(A[X], M[X]).\end{equation}
 \begin{lemma} \label{Kdecomp1} The following decomposition holds:
@@
 Denote by $\widetilde{P}_{\alpha, M}(0)$ the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parameterized by $f \in M[X]$, $\xi \in A[X]$:
-\begin{enumerate} 
+\begin{enumerate}[label=(P\arabic*)]
  \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
@@
 \begin{rem} \label{rem:recognition}
-  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type 1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$.
-Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1.
-In particular, if $\beta$ is such that $\alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
+  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type P1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$.
+Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type P1.
+In particular, if $\beta$ is such that $\alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type P1 and $x_{\alpha+\beta}(f)$ is a generator of type P2.
 \end{rem}
@@
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~\cref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
-The assertion is obvious for the generators of type 3 and 4.
-
-Let $\beta\in\Phi$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type 1.
+The assertion is obvious for the generators of type P3 and P4.
+
+Let $\beta\in\Phi$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type P1.
 By~\cref{Zrels}\eqref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
 \label{eq3-1} \end{equation}
-The expression in the right-hand side is a product of generators of type 4, 1, 1 (see~\cref{rem:recognition}).
-Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$ (so that $\alpha-\beta\in\Phi$). Again by~\cref{Zrels}\eqref{Z2}
+The expression in the right-hand side is a product of generators of type P4, P1, P1 (see~\cref{rem:recognition}).
+Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type P2 (so that $\alpha-\beta\in\Phi$). Again by~\cref{Zrels}\eqref{Z2}
 \begin{equation}
 z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi). \label{eq3-2} \end{equation}
-It is easy to see that the expression in the right-hand side of~\eqref{eq3-2} is a product of generators of type 4, 1, 2.
-
-Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\eqref{Z3}
+It is easy to see that the expression in the right-hand side of~\eqref{eq3-2} is a product of generators of type P4, P1, P2.
+
+Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type P1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\eqref{Z3}
 \begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
-and the latter expression is a product of generators of type $4, 1, 1$.
-
-Finally, let $g = x_\alpha(f)$ be a generator of type $5$.
+and the latter expression is a product of generators of type P4, P1, P1.
+
+Finally, let $g = x_\alpha(f)$ be a generator of type P5.
 Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
@@
  \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
-where $\epsilon = N_{\alpha, \beta}$. It is clear that the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}
+where $\epsilon = N_{\alpha, \beta}$. It is clear that the latter expression is a product of generators of type P1, P1, P2, P5, P1, P2, P1, P4. \end{proof}
 
@@
 This implies that for $\beta \in Z_+(\alpha)$ (resp.
-$\beta \in Z_0(\alpha)$) the element $c_\beta(f, X\xi)$ is a product of two generators of type 2 (resp.
-3).
+$\beta \in Z_0(\alpha)$) the element $c_\beta(f, X\xi)$ is a product of two generators of type P2 (resp.
+P3).
 Thus, the elements $c_{\beta}(f, X\xi)$ lie in $\widetilde{P}_{\alpha, M}(0)$ for all $\beta \in Z(\alpha)$. \end{rem}
@@
 Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
- \begin{enumerate}
+ \begin{enumerate}[label=(K\arabic*)]
   \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
@@
 Fix an element $g\in K(A[X], M[X])$.
-We need to show that $g$ lies in the product of subgroups in the right-hand side.
-
-For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type $i$ from~\cref{def:Kab}.
+We need to show that $g$ lies in the specified product of subgroups.
+
+For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type K$i$. from~\cref{def:Kab}.
 Notice that $\Phi \setminus \Psi$ contains the parabolic set of roots $(\Phi \setminus \Psi)\cap \Phi^+$.
@@
 \end{corollary}
-\begin{proof} It is clear that $\widetilde{K}(\alpha, \beta) \subseteq \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$. 
-Let us prove the reverse inclusion. Let $g$ be an element of the intersection of subgroups in the right-hand side.
+\begin{proof} Denote $\widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$ by $K$. It is clear that $\widetilde{K}(\alpha, \beta) \subseteq K$. 
+Let us prove the reverse inclusion. Let $g$ be an element of $K$.
 By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\alpha}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
@@
 \end{corollary}
-\begin{proof} ??? \end{proof}
+\begin{proof} Set $L = \widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X])$.
+The elements of $X_{-\beta}(M\cdot X)$ are generators of type P1 for $\widetilde{P}_{\alpha, M}(0)$ (cf.~\cref{rem:recognition}),
+ therefore $X_{-\beta}(M \cdot X) \subseteq L$.
+On the other hand, by~\cref{K-a-b-cor} $\widetilde{K}(\alpha, \beta) \subseteq L$.
+Thus, we have shown that $\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X) \subseteq L$.
+The reverse inclusion immediately follows from~\cref{K-a-b} and~\cref{rem:palpha}.
+ \end{proof}
 
 We need one more technical definition.
-We denote by $Z_{\alpha, \beta}$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by elements $x_\gamma(f)$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ and $f \in M[X]$.
-To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``.
+Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.
+Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+It is clear that $Z_{\alpha,\beta} \subseteq j_+(Z_\alpha(A, M))$.
 
@@
 \begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ of every generator from~\cref{def:Kab} lies in the specified subgroup.
-
-Let $z_\gamma(Xf, \xi)$ be a generator of type $1$ for some $\gamma \in \Phi \setminus \Psi$.
+To simplify notation we call the generators of  $Z_{\alpha,\beta}$ ``generators of type Z``.
+
+Let $z_\gamma(Xf, \xi)$ be a generator of type K1 for some $\gamma \in \Phi \setminus \Psi$.
 In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
@@
 \begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
-By the choice of $\gamma$ both $\alpha + \gamma$ and $\alpha - \gamma$ lie in $Z_+(\alpha) \setminus \{\alpha - \beta\}$, therefore in both cases the expressions in the right-hand side are products of generators of type Z, Z, 1.
-
-A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.
-
-Let us verify the assertion for the generators of types 2--4.
+By the choice of $\gamma$ both $\alpha + \gamma$ and $\alpha - \gamma$ lie in $Z_+(\alpha) \setminus \{\alpha - \beta\}$, therefore in both cases the expressions in the right-hand side are products of generators of type Z, Z, K1.
+
+A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type K5 is either the generator itself or a product of generators of type Z, Z, K5.
+
+Let us verify the assertion for the generators of types K2, K3, K4.
 By~\eqref{Chevalley-CCF2} the conjugation by $x_\alpha(aX^{-1})$ fixes root subgroups $X_{\alpha}(X\cdot M[X])$, $X_{\beta}(X\cdot M[X])$, $X_{\alpha-\beta}(X\cdot M[X])$. 
@@
 \end{align*}
-and the expressions in the right-hand side are products of generators of type 2, 4 and 4, Z.
-
-It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type 2.
+and the expressions in the right-hand side are products of generators of type K2, K4 and K4, Z, respectively.
+
+It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
 By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e.
@@
 where $\epsilon = N_{-\delta,\alpha}$. 
-The first 7 factors in the right-hand side are generators of type 1, Z, 1, 2, 1, 1, Z.
-The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and therefore is a product of generators of type Z and 5. \end{proof}
+The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
+The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}), which is a product of generators of type Z and K5. \end{proof}
 
 \begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
-\begin{proof} Since any subgroup $H \leq \St(\Phi, A[X], M[X])$ satisfies $H = \left(H \cap K(A[X], M[X])\right) \rtimes ev^*_{X=0}\left(H\right)$, we obtain from~\cref{rem:DS} that
-$\widetilde{P}_\alpha(0) =  \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right) \rtimes Z_\alpha(A, M).$
-
-Thus, in view of~\cref{image-K-a-b} it remains to show that $X_{-\beta}(MX)^{x_\alpha(aX^{-1})} \subseteq P_\alpha(0)$ and $Z_{\alpha, \beta}^{x_\alpha(aX^{-1})} \subseteq P_\alpha(0)$.
-\end{proof}
-
-\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} 
-By the above lemma it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$.
-Let $g = x_{\gamma}(f, X\xi)$ be a generator of $Z_{\alpha, \beta}$.
-Notice that $\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence $\gamma = \alpha - \beta$, a contradiction.
-
-If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}.
-Finally, if $\gamma = \beta$ the element $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g.
-from~\cref{rem:palpha}).
-\end{proof}
+\begin{proof} 
+Intersecting the factors of~\eqref{eq:sd-decomp} with $\widetilde{P}_{\alpha, M}(0)$ and invoking~\cref{rem:DS} and~\cref{K-a-b-cor2} we obtain that $\widetilde{P}_{\alpha, M}(0) =  Z_\alpha(A, M) \ltimes \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right).$
+It suffices to show that the image of each of these three subgroups under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\alpha(0)$.
+
+It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$ (and hence $Z_{\alpha, \beta}$). By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
+$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ Finally, from~\cref{image-K-a-b} we get that
+$K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.
+\end{proof}
+
+\begin{corollary} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{proof} 
+In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
+$\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
+Notice that $\gamma$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence that $\gamma = \alpha - \beta$, a contradiction.
+Now if $\langle \beta, \gamma \rangle$ is $0$, $1$ or $2$, then $g$ is a generator of type P3, P2 or P5 for $P_\beta(0)$, respectively.\end{proof}
 

### 2020-04-08 dl-paper.tex
Fix bug

@@
 Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
-It is clear that $Z_{\alpha,\beta} \subseteq j_+(Z_\alpha(A, M))$.
 
@@
 The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
-The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}), which is a product of generators of type Z and K5. \end{proof}
+The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and hence is a product of generators of type Z and K5. \end{proof}
 
@@
 
-It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$ (and hence $Z_{\alpha, \beta}$). By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
-$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ Finally, from~\cref{image-K-a-b} we get that
+It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
+$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ 
+Notice that the generators of $Z_{\alpha,\beta}$ are generators of type P2 for $P_\alpha(0)$.
+Thus, from~\cref{image-K-a-b} we get that
 $K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.

### 2020-04-08 dl-paper.tex
Fix 19

@@
 
+\begin{corollary} \label{K-a-b-P-b} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{proof} 
+In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
+$\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
+Notice that $\gamma$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence that $\gamma = \alpha - \beta$, a contradiction.
+Now if $\langle \beta, \gamma \rangle$ is $0$, $1$ or $2$, then $g$ is a generator of type P3, P2 or P5 for $P_\beta(0)$, respectively.\end{proof}
+
 \begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
@@
 
-It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
+It is clear that the specified conjugation fixes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
 $X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ 
@@
 
-\begin{corollary} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} 
-In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
-$\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
-Notice that $\gamma$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence that $\gamma = \alpha - \beta$, a contradiction.
-Now if $\langle \beta, \gamma \rangle$ is $0$, $1$ or $2$, then $g$ is a generator of type P3, P2 or P5 for $P_\beta(0)$, respectively.\end{proof}
-
-\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
+\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
 \] \end{lemma}
-\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\cref{lem:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am).
-\end{multline}
-The assertion now follows from the preceding corollary.
+\begin{proof} By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
+By~\cref{K-a-b-P-b} the element $g_1 = S_\alpha(a, g_0) $ lies in $P_\beta(0)$.
+Since $x_{-\beta}(m'X) \in P_\alpha(0)$ we get that
+\begin{align*}
+  S_\alpha(a, g) = g_1 \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) & \text{ by~\cref{lem:Smult}} \\ 
+  = g_1 \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) & \text{ by~\cref{lem:Tulenbaev-formula},\eqref{Chevalley-CCF1}} \\
+  = g_1 \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am) & \text{ by~\eqref{eq:conj-h-x}}.
+\end{align*}
+The required assertion now follows from~\cref{rem:palpha}.
 \end{proof}
@@
 \begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type 4, 1, 1.
-By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type 5 is either $g$ or a product of generators of type 5, 4, 1.
-
-Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
+\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type K1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type K4, K1, K1.
+By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type K5 is either $g$ or a product of generators of type K5, K4, K1.
+
+Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
 Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.

### 2020-04-08 dl-paper.tex
Fix misprint

@@
 Let us prove the reverse inclusion. Let $g$ be an element of $K$.
-By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\alpha}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
+By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
 From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}
@@
 
-Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.
+Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type K2 or K3.
 Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.

### 2020-04-09 dl-paper.tex
Fix 20-21

@@
 
-\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate of $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
-\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate of each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
-Throughout this proof we understand generator types according to~\cref{defP0}.
-It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
-
-In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
-\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\beta - \alpha + \gamma} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi).
-\] Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
- hence $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$ and the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2.
+\begin{lemma} \label{conj-S-a-x-bma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate of $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
+\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it suffices to show that the conjugate $g_1$ of each generator $g = x_\gamma(f)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+It is clear that $g$ itself is a generator of type P2 for $P_\alpha(0)$, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
+
+In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from~\eqref{Chevalley-CCF1} that
+$g_1 = x_{\beta - \alpha + \gamma} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot x_{\gamma}(f).$ Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
+ therefore $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$. Thus, $g_1$ is a product of generators of type P2, P2 or P3, P2.
 
@@
 Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
-we obtain that $\alpha - \beta + \gamma = \alpha$, i.\,e. $\beta=\gamma$. Thus, by \eqref{Z3} of~\cref{Zrels}
-\[z_{\beta}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (bXf\xi) \cdot x_{-\alpha} (N_{\beta,\alpha - \beta}\cdot bX^2 f\xi^2) \cdot z_{\beta}(f, X\xi). \]
-The expression in the right-hand side is a product of generators of type 1, 4, 2. \end{proof}
+we obtain that $\alpha - \beta + \gamma = \alpha$, i.\,e. $\beta=\gamma$. Thus, by~\eqref{Chevalley-CCF2} $g_1 = x_\beta(f)^{x_{\beta-\alpha}(b)} = x_\beta(f)$. \end{proof}
 
@@
 \begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
-From the definition of $S_\alpha(a, -)$, \cref{lem:Tulenbaev-formula}, \eqref{eq:conj-h-x}, \eqref{eq:h-inv} and~\eqref{eq:dennis-stein} we obtain that
- \begin{multline} \label{eq:SRobtuse-computation}
- S_\alpha\left(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)\right) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
- = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
- = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
- = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
- =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
- = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
-\end{multline}
+Notice that $1 - \epsilon abc^{-1}m' = c^{-1}$, therefore by~\eqref{eq:dennis-stein}
+\begin{equation} \label{eq:computation-SR-obtuse} x_{\alpha-\beta}(\epsilon am') \cdot x_{\beta-\alpha}(-bc^{-1}) = x_{\beta-\alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}(\epsilon acm').\end{equation}
+Notice that $x_{-\beta}(m'X) \in P_\alpha(0)$ therefore from the definition of $S_\alpha(a, -)$ we obtain that
+\begin{align*}
+ S_\alpha\left(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)\right) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) \\ 
+ = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) &\text{ by~\cref{lem:Smult}}\\
+ = S_\alpha(a, x_{-\beta}(m'X)) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) &\text{ by~\cref{lem:Tulenbaev-formula}}\\
+ = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) &\text{ by~\eqref{Chevalley-CCF1},~\eqref{Chevalley-CCF2}, \eqref{eq:conj-h-x}}\\
+ \begin{split}= x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot \hspace{100pt} \\ \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) &\text{ by~\eqref{eq:computation-SR-obtuse}} \end{split}\\
+ =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 &\text{ by~\eqref{Chevalley-CCF1},~\eqref{eq:conj-h-x},~\eqref{eq:h-inv}}\\
+ = x_{\beta-\alpha}(-b) \cdot x_{-\beta}(m'c^{-1}X) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right) &\text{ by~\eqref{Chevalley-CCF1}.}
+\end{align*}
 Denote by $h_0$ the product of all factors in the above formula except the first and the last one.
@@
 Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$.
-The required assertion now follows from \cref{lem:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
+The required assertion now follows from \cref{lem:Smult},\cref{conj-S-a-x-bma} and the above computation:
 \begin{multline} \nonumber

### 2020-04-09 dl-paper.tex
Many small fixes

@@
  [x, yz]^y =& [y^{-1}, x] \cdot [x, z], \label{rel43} \\ 
- \label{eq:H1ii} [xy, z] =& {}^x[y, z] \cdot [x,z]. \\
+ \label{eq:H1ii} [xy, z] =& {}^x[y, z] \cdot [x,z], \\
  [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant} \end{align}
-We will also be using the fact that 
+Recall also from~\cite[Lemma~3.1.1]{RS76} that
 \begin{equation} \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz]. \end{equation}
@@
 all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G(\Phi, R)$.
+The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers which can only take values $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G(\Phi, R)$.
 Several different methods of computing signs of these constants have been proposed in the literature, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
@@
 The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
-Direct computation using Chevalley commutator identities~\eqref{Chevalley-CCF1}--\eqref{Chevalley-CCF2} shows that
+Direct computation using~\eqref{Chevalley-CCF1}--\eqref{Chevalley-CCF2} shows that
 \begin{multline} \nonumber
@@
 \begin{proof}
-The proof is based on the following observation: every relation of type $\text{R3}^\bot_{d,e}$ of degree $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree (modulo the remaining relations of $\St^{\leq n}(\Phi, B)$, i.\,e.
-relations of type R2 and $\text{R3}^{\angle}$).
-The commutator formulae $\text{R2}$ are used to reduce the degree of the monomials appearing in $R$.
+The proof is based on the following observation: every relation $R$ of type $\text{R3}^\bot_{d,e}$ of degree $\geq 2$ is a consequence of some relation of type $\text{R3}^\bot$ of strictly smaller degree modulo the remaining relations of $\St^{\leq n}(\Phi, B)$, i.\,e.
+relations of type R2 and $\text{R3}^{\angle}$ (we use the commutator formulae $\text{R2}$ to reduce the degree of the monomials appearing in $R$).
 
@@
 
-\begin{rem} \label{Pstar-char} From the above lemma and~\cref{rem:DS} it follows that the subgroup $\widetilde{P}_{\alpha, M}(*)$ admits decomposition $\widetilde{P}_{\alpha, M}(*) = Z_\alpha(A, M) \ltimes K(A[X], M[X]).$ \end{rem}
+\begin{rem} \label{Pstar-char} From the above lemma,~\eqref{eq:sd-decomp} and~\cref{rem:DS} it follows that the subgroup $\widetilde{P}_{\alpha, M}(*)$ admits decomposition $\widetilde{P}_{\alpha, M}(*) = Z_\alpha(A, M) \ltimes K(A[X], M[X]).$ \end{rem}
 
@@
 $S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
-\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$.
+\end{lemma} \begin{proof} Suppose $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$.
 The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
@@
 $\alpha-\delta \in \Phi$.
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$ into~\eqref{Z5} we obtain that
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\eqref{Z5} we obtain that
 \begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
@@
 
-\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
+\begin{lemma} \label{SR:sharp} For $g \in j_+(K(A[X], M[X])) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
 \] \end{lemma}
@@
 Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type K2 or K3.
-Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
+Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in j_+(K(A[X], M[X])) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
 \end{proof}
@@
 
-\begin{lemma} \label{SR:obtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
+\begin{lemma} \label{SR:obtuse} For $g \in j_+(K(A[X], M[X])) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
  belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
@@
 \begin{equation} \label{eq:computation-SR-obtuse} x_{\alpha-\beta}(\epsilon am') \cdot x_{\beta-\alpha}(-bc^{-1}) = x_{\beta-\alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}(\epsilon acm').\end{equation}
-Notice that $x_{-\beta}(m'X) \in P_\alpha(0)$ therefore from the definition of $S_\alpha(a, -)$ we obtain that
+Notice that $x_{-\beta}(m'X) \in P_\alpha(0)$, therefore from the definition of $S_\alpha(a, -)$ we obtain that
 \begin{align*}
@@
 It is clear that $h_0$ lies in $P_\alpha(0)$.
-Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$.
+Using~\cref{K-a-b} we can decompose $g$ as $g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$, $m, m' \in M$.
 The required assertion now follows from \cref{lem:Smult},\cref{conj-S-a-x-bma} and the above computation:

### 2020-04-09 dl-paper.tex
Finish restructure

@@
 The other ingredients are certain subgroups $P_\alpha(0)$, $P_\alpha(*)$ of $\St(\Phi, A[X, X\inv])$ modeled after the nameless groups from~\cite[Lemma~3.4]{Tu83}.
-The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:Pa0-Steinberg}.
+The definition and properties of these groups are given in Sections~\ref{sec:Pa0-basic}--\ref{sec:S-a}.
 
@@
  \item $B = B_{A, M}$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$. Obviously, $B = A[t]$ in the case $M=0$ and $B = R$ in the case $M=A$.
+ \item $I$ denotes the ideal $M[X, X^{-1}]$ of $R$. Notice that $I$ is also an ideal of $B$.
  \end{itemize}
@@
 
-\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} \label{sec:Pa0-basic}
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)}, \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties.} \label{sec:Pa0-basic}
 Let $\Phi$ be a root system and $\alpha$ be an element of $\Phi$.
@@
 
-For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a fixed root of $\Phi$.
-Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e.
-$Z_0(\alpha) = \{ \beta\in\Phi \mid \alpha \perp \beta \}$
+For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$.
+Let $\alpha$ be a fixed root of $\Phi$. 
+Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e. $Z_0(\alpha) = \{ \beta\in\Phi \mid \alpha \perp \beta \}$
 (cf.~\cite[Proposition~5.7]{St71}).
@@
 
-\begin{df} \label{defP0}
+\begin{df}\label{defP0}
 Let $M$ be an ideal of a local ring $A$.
@@
 
-\begin{rem} \label{rem:recognition}
-  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type P1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$.
+\begin{rem} \label{rem:recognition} From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type P1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$.
 Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type P1.
@@
 \begin{lemma} \label{Pstar-large} Suppose that $(A, M)$ is a local pair. 
-Then the subgroup $\widetilde{P}_{\alpha, M}(*)$ contains the subgroup $K(A[X], M[X]) \leq \overline{\St}(\Phi, A[X], M[X])$ defined in the beginning of~\cref{sec:computationOfK}. \end{lemma}
+Then the subgroup $\widetilde{P}_{\alpha, M}(*)$ contains the subgroup $K(A[X], M[X]) \leq \overline{\St}(\Phi, A[X], M[X])$ defined at the beginning of~\cref{sec:computationOfK}. \end{lemma}
 \begin{proof} Clearly, $\widetilde{P}_{\alpha, M}(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, \xi)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $\xi\in A[X]$, therefore by~\cref{thm:Stepanov} $\widetilde{P}_{\alpha, M}(*)$ contains all of $\overline{\St}(\Phi, A[X], XM[X])$.
@@
 
-For the rest of this section $M$ denotes the maximal ideal of $A$.
-\begin{df}\label{S-def}
-Define the subgroup $P_\alpha(0)$ (resp. $P_{\alpha}(*)$) of $\overline{\St}(\Phi, R, M[X, X^{-1}])$
- as the image of the subgroup $\widetilde{P}_{\alpha, M}(0)$ (resp. $\widetilde{P}_{\alpha, M}(*)$) 
- under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.
+For the rest of this subsection $M$ is the maximal ideal $A$.
+We denote by $\beta$ another fixed root of $\Phi$ forming a sharp angle with $\alpha$ (i.\,e.
+$\langle \alpha, \beta \rangle = 1$).
+We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
+\begin{df}\label{def:Kab} 
+Fix a root $\delta \in \Phi \setminus \Psi$.
+Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
+ \begin{enumerate}[label=(K\arabic*)]
+  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
+  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
+  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
+  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
+  \item $c_{\delta}(f, X\xi)$. \end{enumerate} \end{df}
+\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. 
+\end{prop} 
+\begin{proof}
+It is clear that $K(A[X], M[X]) \supseteq \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$.
+Let us prove the reverse inclusion.
+Fix an element $g\in K(A[X], M[X])$.
+We need to show that $g$ lies in the specified product of subgroups.
+
+For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type K$i$. from~\cref{def:Kab}.
+Notice that $\Phi \setminus \Psi$ contains the parabolic set of roots $(\Phi \setminus \Psi)\cap \Phi^+$.
+Thus, by~\cref{thm:Stepanov} every element of $\overline{\St}(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
+In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
+
+By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
+By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, for some $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
+
+It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$ for $\gamma_1, \gamma_2 \in \Psi$.
+On the other hand, for $\gamma \in \Psi$ any commutator $c_{\gamma}(mX, m'X)$ is congruent to some generator of $\mathcal{G}_5$  modulo $G_0$ (cf.
+the proof of~\cref{Kgen-strong}) and hence commutes with the elements of $\mathcal{G}'$ modulo $G_0$.
+
+Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f' \in M[X]$, $m' \in M$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
+By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after simplification of these conjugates.
+Thus, we can rewrite $g_2$ as $g_{21} \cdot g_{22}$, where $g_{21} \in \langle \mathcal{G}_2, \mathcal{G}_3, \mathcal{G}_4, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_{22} \in \langle X_{-\alpha}(MX), X_{-\beta}(MX) \rangle = X_{-\alpha}(MX) \cdot X_{-\beta}(MX)$.
+Thus, we have obtained the desired decomposition for $g$. \end{proof}
+
+\begin{corollary} \label{K-a-b-cor}
+One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$.
+In particular, $\widetilde{K}(\alpha, \beta)$ and $K(\alpha, \beta)$ do not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
+\end{corollary}
+\begin{proof} Denote $\widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$ by $K$. It is clear that $\widetilde{K}(\alpha, \beta) \subseteq K$. 
+Let us prove the reverse inclusion. Let $g$ be an element of $K$.
+By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
+From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}
+
+\begin{corollary} \label{K-a-b-cor2}
+ One has $\widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
+\end{corollary}
+\begin{proof} Set $L = \widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X])$.
+The elements of $X_{-\beta}(M\cdot X)$ are generators of type P1 for $\widetilde{P}_{\alpha, M}(0)$ (cf.~\cref{rem:recognition}),
+ therefore $X_{-\beta}(M \cdot X) \subseteq L$.
+On the other hand, by~\cref{K-a-b-cor} $\widetilde{K}(\alpha, \beta) \subseteq L$.
+Thus, we have shown that $\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X) \subseteq L$.
+The reverse inclusion immediately follows from~\cref{K-a-b} and~\cref{rem:palpha}.
+ \end{proof}
+
+\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $\widetilde{K}(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq \widetilde{K}(\alpha, \beta)$. \end{lemma}
+\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type K1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type K4, K1, K1.
+By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type K5 is either $g$ or a product of generators of type K5, K4, K1.
+
+Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type K2 or K3.
+Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap \widetilde{P}_\alpha(0) \cap \widetilde{P}_{\beta}(0) = \widetilde{K}(\alpha, \beta)$.
+\end{proof}
+
+We come to the central concept of this subsection.
+\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$ and $K(\alpha, \beta)$ of $\overline{\St}(\Phi, R, M[X, X^{-1}])$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$ and $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
+
+We need one more technical definition.
+Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.
+Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+
+\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
+\end{lemma}
+\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ of every generator from~\cref{def:Kab} lies in the specified subgroup.
+To simplify notation we call the generators of  $Z_{\alpha,\beta}$ ``generators of type Z``.
+
+Let $z_\gamma(Xf, \xi)$ be a generator of type K1 for some $\gamma \in \Phi \setminus \Psi$.
+In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
+If $\gamma$ is such that $\alpha + \gamma \in \Phi$ we obtain from~\cref{Zrels}\eqref{Z2} that
+\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\gamma} (N_{\gamma, \alpha}\cdot af) \cdot z_{\gamma}(Xf, \xi). \end{equation}
+On the other hand, if $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
+\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
+By the choice of $\gamma$ both $\alpha + \gamma$ and $\alpha - \gamma$ lie in $Z_+(\alpha) \setminus \{\alpha - \beta\}$, therefore in both cases the expressions in the right-hand side are products of generators of type Z, Z, K1.
+
+A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type K5 is either the generator itself or a product of generators of type Z, Z, K5.
+
+Let us verify the assertion for the generators of types K2, K3, K4.
+By~\eqref{Chevalley-CCF2} the conjugation by $x_\alpha(aX^{-1})$ fixes root subgroups $X_{\alpha}(X\cdot M[X])$, $X_{\beta}(X\cdot M[X])$, $X_{\alpha-\beta}(X\cdot M[X])$. 
+Further, from~\eqref{Chevalley-CCF1} we obtain that
+\begin{align*}
+ x_{-\beta}(X^2f)^{x_\alpha(aX^{-1})}     &= x_{-\beta}(X^2f) \cdot x_{\alpha-\beta}(N_{-\beta, \alpha} \cdot aXf);\\
+ x_{\beta-\alpha}(Xf)^{x_\alpha(aX^{-1})} &= x_{\beta-\alpha}(Xf) \cdot x_{\beta}(N_{\alpha,-\beta}\cdot af),
+\end{align*}
+and the expressions in the right-hand side are products of generators of type K2, K4 and K4, Z, respectively.
+
+It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
+By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e.
+$\alpha-\delta \in \Phi$.
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\eqref{Z5} we obtain that
+\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
+ \cdot z_{\delta-\alpha}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha-\delta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{\delta}(a f, -X), \end{multline*}
+where $\epsilon = N_{-\delta,\alpha}$. 
+The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
+The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and hence is a product of generators of type Z and K5. \end{proof}
+
+\begin{corollary} \label{K-a-b-P-b} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\beta(0)$. \end{corollary}
+\begin{proof} 
+In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
+$\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
+Notice that $\gamma$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence that $\gamma = \alpha - \beta$, a contradiction.
+Now if $\langle \beta, \gamma \rangle$ is $0$, $1$ or $2$, then $g$ is a generator of type P3, P2 or P5 for $P_\beta(0)$, respectively.\end{proof}
+
+\begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
+\begin{proof} 
+Intersecting the factors of~\eqref{eq:sd-decomp} with $\widetilde{P}_{\alpha, M}(0)$ and invoking~\cref{rem:DS} and~\cref{K-a-b-cor2} we obtain that $P_{\alpha}(0) =  j_+(Z_\alpha(A, M)) \ltimes \left(K(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right).$
+It suffices to show that the image of each of these three subgroups under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\alpha(0)$.
+
+It is clear that the specified conjugation fixes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
+$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ 
+Notice that the generators of $Z_{\alpha,\beta}$ are generators of type P2 for $P_\alpha(0)$.
+Thus, from~\cref{image-K-a-b} we get that
+$K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.
+\end{proof}
+
+\begin{lemma} \label{conj-S-a-x-bma} For $a, b\in A$ the image of $K(\alpha,\beta)^{x_\alpha(aX^{-1})}$ under the automorphism of conjugation by $x_{\beta-\alpha}(b)$ is contained in $P_\alpha(0)$.
+\end{lemma}
+\begin{proof} By Lemmas~\ref{conj-K-a-b}--\ref{image-K-a-b} it suffices to show that the conjugate $g_1$ of each generator $g = x_\gamma(f)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+It is clear that $g$ itself is a generator of type P2 for $P_\alpha(0)$, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
+
+In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from~\eqref{Chevalley-CCF1} that
+$g_1 = x_{\beta - \alpha + \gamma} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot x_{\gamma}(f).$ Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
+ therefore $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$. Thus, $g_1$ is a product of generators of type P2, P2 or P3, P2.
+
+Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
+Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
+we obtain that $\alpha - \beta + \gamma = \alpha$, i.\,e. $\beta=\gamma$. Thus, by~\eqref{Chevalley-CCF2} $g_1 = x_\beta(f)^{x_{\beta-\alpha}(b)} = x_\beta(f)$. \end{proof}
+
+\subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties.} \label{sec:S-a}
+Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming a sharp angle.
 
@@
 From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. 
-This allows us to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
+\begin{df}\label{S-def}
+Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$ via the following formula:
 \begin{equation}\label{eq:S-def} S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\end{equation} \end{df}
+Notice that the restriction of the map $S_\alpha(a, -)$ to the subgroup $P_\alpha(0)$ coincides with the automorphism of left conjugation by $x_\alpha(aX^{-1})$.
 
@@
 \end{proof}
-It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
 
@@
 
-\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties} \label{sec:Pa0-Steinberg}
-Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e.
-$\langle \alpha, \beta \rangle = 1$).
-We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
-\begin{df}\label{def:Kab} 
-Fix a root $\delta \in \Phi \setminus \Psi$.
-Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
- \begin{enumerate}[label=(K\arabic*)]
-  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
-  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
-  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
-  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
-  \item $c_{\delta}(f, X\xi)$. \end{enumerate}
-Denote by $K(\alpha, \beta)$ the image of $\widetilde{K}(\alpha, \beta)$ under $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X\inv])$. \end{df}
-\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. 
-\end{prop} 
-\begin{proof}
-It is clear that $K(A[X], M[X]) \supseteq \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$.
-Let us prove the reverse inclusion.
-Fix an element $g\in K(A[X], M[X])$.
-We need to show that $g$ lies in the specified product of subgroups.
-
-For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type K$i$. from~\cref{def:Kab}.
-Notice that $\Phi \setminus \Psi$ contains the parabolic set of roots $(\Phi \setminus \Psi)\cap \Phi^+$.
-Thus, by~\cref{thm:Stepanov} every element of $\overline{\St}(\Phi, A[X], XM[X])$ can be presented as a product of generators $\mathcal{G}_1$ and generators $\mathcal{G}' = \{ x_{\gamma}(Xf) \mid \gamma \in \Psi\}$.
-In turn, by~\cref{Kgen-strong} one can express $g$ as a product of these generators and generators $\mathcal{G}_5$.
-
-By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
-By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, for some $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
-
-It is clear that  $x_{\gamma_1}(mX)$ and $x_{\gamma_2}(m'X)$ commute modulo $G_0$ whenever $\gamma_1 \neq - \gamma_2$ for $\gamma_1, \gamma_2 \in \Psi$.
-On the other hand, for $\gamma \in \Psi$ any commutator $c_{\gamma}(mX, m'X)$ is congruent to some generator of $\mathcal{G}_5$  modulo $G_0$ (cf.
-the proof of~\cref{Kgen-strong}) and hence commutes with the elements of $\mathcal{G}'$ modulo $G_0$.
-
-Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f' \in M[X]$, $m' \in M$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
-By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after simplification of these conjugates.
-Thus, we can rewrite $g_2$ as $g_{21} \cdot g_{22}$, where $g_{21} \in \langle \mathcal{G}_2, \mathcal{G}_3, \mathcal{G}_4, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_{22} \in \langle X_{-\alpha}(MX), X_{-\beta}(MX) \rangle = X_{-\alpha}(MX) \cdot X_{-\beta}(MX)$.
-Thus, we have obtained the desired decomposition for $g$. \end{proof}
-
-\begin{corollary} \label{K-a-b-cor}
-One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$.
-In particular, $\widetilde{K}(\alpha, \beta)$ and $K(\alpha, \beta)$ do not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
-\end{corollary}
-\begin{proof} Denote $\widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$ by $K$. It is clear that $\widetilde{K}(\alpha, \beta) \subseteq K$. 
-Let us prove the reverse inclusion. Let $g$ be an element of $K$.
-By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$.
-From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}
-
-\begin{corollary} \label{K-a-b-cor2}
- One has $\widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X).$ 
-\end{corollary}
-\begin{proof} Set $L = \widetilde{P}_{\alpha, M}(0) \cap K(A[X], M[X])$.
-The elements of $X_{-\beta}(M\cdot X)$ are generators of type P1 for $\widetilde{P}_{\alpha, M}(0)$ (cf.~\cref{rem:recognition}),
- therefore $X_{-\beta}(M \cdot X) \subseteq L$.
-On the other hand, by~\cref{K-a-b-cor} $\widetilde{K}(\alpha, \beta) \subseteq L$.
-Thus, we have shown that $\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X) \subseteq L$.
-The reverse inclusion immediately follows from~\cref{K-a-b} and~\cref{rem:palpha}.
- \end{proof}
-
-We need one more technical definition.
-Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.
-Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
-
-\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under conjugation by $x_\alpha(aX^{-1})$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$.
-\end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ of every generator from~\cref{def:Kab} lies in the specified subgroup.
-To simplify notation we call the generators of  $Z_{\alpha,\beta}$ ``generators of type Z``.
-
-Let $z_\gamma(Xf, \xi)$ be a generator of type K1 for some $\gamma \in \Phi \setminus \Psi$.
-In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
-If $\gamma$ is such that $\alpha + \gamma \in \Phi$ we obtain from~\cref{Zrels}\eqref{Z2} that
-\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\gamma} (N_{\gamma, \alpha}\cdot af) \cdot z_{\gamma}(Xf, \xi). \end{equation}
-On the other hand, if $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
-\begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
-By the choice of $\gamma$ both $\alpha + \gamma$ and $\alpha - \gamma$ lie in $Z_+(\alpha) \setminus \{\alpha - \beta\}$, therefore in both cases the expressions in the right-hand side are products of generators of type Z, Z, K1.
-
-A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type K5 is either the generator itself or a product of generators of type Z, Z, K5.
-
-Let us verify the assertion for the generators of types K2, K3, K4.
-By~\eqref{Chevalley-CCF2} the conjugation by $x_\alpha(aX^{-1})$ fixes root subgroups $X_{\alpha}(X\cdot M[X])$, $X_{\beta}(X\cdot M[X])$, $X_{\alpha-\beta}(X\cdot M[X])$. 
-Further, from~\eqref{Chevalley-CCF1} we obtain that
-\begin{align*}
- x_{-\beta}(X^2f)^{x_\alpha(aX^{-1})}     &= x_{-\beta}(X^2f) \cdot x_{\alpha-\beta}(N_{-\beta, \alpha} \cdot aXf);\\
- x_{\beta-\alpha}(Xf)^{x_\alpha(aX^{-1})} &= x_{\beta-\alpha}(Xf) \cdot x_{\beta}(N_{\alpha,-\beta}\cdot af),
-\end{align*}
-and the expressions in the right-hand side are products of generators of type K2, K4 and K4, Z, respectively.
-
-It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
-By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e.
-$\alpha-\delta \in \Phi$.
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\eqref{Z5} we obtain that
-\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
- \cdot z_{\delta-\alpha}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha-\delta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{\delta}(a f, -X), \end{multline*}
-where $\epsilon = N_{-\delta,\alpha}$. 
-The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
-The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and hence is a product of generators of type Z and K5. \end{proof}
-
-\begin{corollary} \label{K-a-b-P-b} The image of $K(\alpha, \beta)$ under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\beta(0)$. \end{corollary}
-\begin{proof} 
-In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
-$\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
-Notice that $\gamma$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence that $\gamma = \alpha - \beta$, a contradiction.
-Now if $\langle \beta, \gamma \rangle$ is $0$, $1$ or $2$, then $g$ is a generator of type P3, P2 or P5 for $P_\beta(0)$, respectively.\end{proof}
-
-\begin{lemma} \label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a \in A$. \end{lemma}
-\begin{proof} 
-Intersecting the factors of~\eqref{eq:sd-decomp} with $\widetilde{P}_{\alpha, M}(0)$ and invoking~\cref{rem:DS} and~\cref{K-a-b-cor2} we obtain that $\widetilde{P}_{\alpha, M}(0) =  Z_\alpha(A, M) \ltimes \left(\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X)\right).$
-It suffices to show that the image of each of these three subgroups under the automorphism of conjugation by $x_\alpha(aX^{-1})$ is contained in $P_\alpha(0)$.
-
-It is clear that the specified conjugation fixes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
-$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ 
-Notice that the generators of $Z_{\alpha,\beta}$ are generators of type P2 for $P_\alpha(0)$.
-Thus, from~\cref{image-K-a-b} we get that
-$K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.
-\end{proof}
-
 \begin{lemma} \label{SR:sharp} For $g \in j_+(K(A[X], M[X])) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
@@
 \end{proof}
-
-\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
-\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type K1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type K4, K1, K1.
-By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type K5 is either $g$ or a product of generators of type K5, K4, K1.
-
-Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type K2 or K3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type K2 or K3.
-Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in j_+(K(A[X], M[X])) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$.
-\end{proof}
-
-\begin{lemma} \label{conj-S-a-x-bma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate of $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
-\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it suffices to show that the conjugate $g_1$ of each generator $g = x_\gamma(f)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
-It is clear that $g$ itself is a generator of type P2 for $P_\alpha(0)$, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
-
-In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from~\eqref{Chevalley-CCF1} that
-$g_1 = x_{\beta - \alpha + \gamma} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot x_{\gamma}(f).$ Notice that $\langle \alpha - \beta - \gamma, \alpha \rangle = \langle \alpha, \alpha \rangle - \langle \beta, \alpha \rangle - \langle \gamma, \alpha \rangle \leq 2 - 1 - 1 = 0$,
- therefore $\langle \alpha - \beta - \gamma, \alpha \rangle = -1,0$. Thus, $g_1$ is a product of generators of type P2, P2 or P3, P2.
-
-Now suppose that the other alternative holds, namely that $\alpha - \beta + \gamma \in \Phi$.
-Since $\langle \alpha - \beta + \gamma, \alpha \rangle = \langle \alpha , \alpha \rangle - \langle \beta, \alpha \rangle + \langle \gamma, \alpha \rangle \geq 2 - 1 + 1 = 2$
-we obtain that $\alpha - \beta + \gamma = \alpha$, i.\,e. $\beta=\gamma$. Thus, by~\eqref{Chevalley-CCF2} $g_1 = x_\beta(f)^{x_{\beta-\alpha}(b)} = x_\beta(f)$. \end{proof}
 
@@
 
-\subsection{The map \texorpdfstring{$S_\alpha$}{Sa} and its properties.}
-
 \subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor.} \label{sec:V-construction}

### 2020-04-09 dl-paper.tex
Cosmetics

@@
 Thus, we have shown that $\widetilde{K}(\alpha, \beta) \cdot X_{-\beta}(M \cdot X) \subseteq L$.
-The reverse inclusion immediately follows from~\cref{K-a-b} and~\cref{rem:palpha}.
+The reverse inclusion immediately follows from~\cref{rem:palpha} and~\cref{K-a-b}.
  \end{proof}
@@
 We come to the central concept of this subsection.
-\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$ and $K(\alpha, \beta)$ of $\overline{\St}(\Phi, R, M[X, X^{-1}])$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$ and $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
+\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$ and $K(\alpha, \beta)$ of $\overline{\St}(\Phi, R, I)$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$ and $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
 
@@
 \begin{proof} 
-In view of~\cref{image-K-a-b} and~\cref{K-a-b-cor} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
+By~\cref{K-a-b-cor} and~\cref{image-K-a-b} it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$. Let $g = x_{\gamma}(f)$ be a generator of $Z_{\alpha, \beta}$ for some
 $\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$.
@@
 \end{lemma}
-\begin{proof} By Lemmas~\ref{conj-K-a-b}--\ref{image-K-a-b} it suffices to show that the conjugate $g_1$ of each generator $g = x_\gamma(f)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
+\begin{proof} By Lemmas~\ref{conj-K-a-b}, \ref{image-K-a-b} it suffices to show that the conjugate $g_1$ of each generator $g = x_\gamma(f)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$.
 It is clear that $g$ itself is a generator of type P2 for $P_\alpha(0)$, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
@@
 It is clear that $h_0$ lies in $P_\alpha(0)$.
-Using~\cref{K-a-b} we can decompose $g$ as $g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$, $m, m' \in M$.
-The required assertion now follows from \cref{lem:Smult},\cref{conj-S-a-x-bma} and the above computation:
+By~\cref{K-a-b} we can decompose $g$ as $g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$, $m, m' \in M$.
+The required assertion now follows from Lemmas~\ref{conj-S-a-x-bma}, \ref{lem:Smult} and the above computation:
 \begin{multline} \nonumber
@@
 This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
-\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, M[X, X\inv]) \ar[r]^(.65){t} & \St(\Phi, B) \ar[d]^{j_R} \\
+\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, I) \ar[r]^(.65){t} & \St(\Phi, B) \ar[d]^{j_R} \\
    \St(\Phi, A[X]) \ar[rr]^{j_+} & & \St(\Phi, R). } \]

### 2020-04-09 dl-paper.tex
Beautify 4.6

@@
  \label{eq:H1ii} [xy, z] =& {}^x[y, z] \cdot [x,z], \\
+ \label{eq:H1ii-2}[x, yz] =& [x, y] \cdot {}^{y}\![x, z], \\
  [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant} \end{align}
@@
 \begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
-In our calculations below we will be using identities~\eqref{eq:simplest} without further reference.
+In our calculations below we repeatedly use identities~\eqref{eq:simplest} without explicit reference.
 
@@
               \label{eq:h-inv}    h_\alpha(t)^{-1}             & = h_{-\alpha}(t). \end{align}
-Here $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$ (we denote by $(-,-)$ the inner product on the euclidean space $\mathbb{R}^\ell$ containing $\Phi$).
+In the above formulae $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$ (we denote by $(\text{-},\text{-})$ the inner product on the euclidean space $\mathbb{R}^\ell$ containing $\Phi$).
 
@@
 \begin{proof}
-The first assertion follows from the following computation:
-\begin{multline} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)]  = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] = \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi). \end{multline}
-
-The second assertion follows directly from~\eqref{HW-variant} and Chevalley commutator identities:
-\begin{multline} \nonumber
-[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = \\
-= \left([x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot [x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\right)^{x_\beta(-s)} = \\
-= x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = \\
-= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi). \end{multline}
-
-Finally, the last assertion can be verified via the following direct computation:
+The first two assertions can be verified by direct calculation:
+\begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1};} \end{align*}
+\begin{align*} \nonumber
+\begin{split}[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = \bigl([x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot \hspace{50pt} \\ \cdot [x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\bigr)^{x_\beta(-s)} & \text{ by~\eqref{HW-variant}}\end{split} \\
+= x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
+= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
+The assertion~\eqref{C3} is obvious. Finally, last assertion can be obtained as follows:
 \begin{align*}
@@
 \end{align*}
+
 \end{proof}
@@
 \[\xymatrix{1 \ar[r] & \widetilde{P}_{\alpha,M}(0) \ar[r] & \widetilde{P}_{\alpha,M}(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
-\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ to every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~\cref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
+\begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ of every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~\cref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
 The assertion is obvious for the generators of type P3 and P4.

### 2020-04-09 dl-paper.tex
Improve phrasing

@@
 \begin{df} By definition, the {\it relative Steinberg group} $\St(\Phi, R, I)$ is the result of application of Loday's relativization to the functor $\St(\Phi, -)$.
-Notice that $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ but rather its central extension by the abelian group $C_{\St(\Phi, -)}(R, I)$.
+Notice that $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ but a central extension of a subgroup of $\St(\Phi, R)$ by the abelian group $C_{\St(\Phi, -)}(R, I)$.
 For shortness we rename the latter group to $C(\Phi, R, I)$.
@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ does not coincide with $\K_2(\rD_n, R) = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))$ but rather is related with it via the exact sequence
+Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ is different from $\K_2(\rD_n, R) = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))$.
+The relationship between these groups is illustrated by the exact sequence
 \[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
-which can be obtained from the exact sequence~\cite[p.~189]{Ba74} by means of the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
+which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} by means of the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.

### 2020-04-09 dl-paper.tex
Minor fixes

@@
 One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$.
-In particular, $\widetilde{K}(\alpha, \beta)$ and $K(\alpha, \beta)$ do not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
+In particular, $\widetilde{K}(\alpha, \beta)$ does not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
 \end{corollary}
@@
 
-We come to the central concept of this subsection.
-\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$ and $K(\alpha, \beta)$ of $\overline{\St}(\Phi, R, I)$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$ and $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
+\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$, $K(\alpha, \beta) \leq \overline{\St}(\Phi, R, I)$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$, $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
 

### 2020-04-10 dl-paper.tex
Fixed most of the issues up to 27

@@
 Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.
-Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
+Recall that this means that $Z_{\alpha, \beta}$ is the group generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
 
@@
 
-\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am).
-\]\end{corollary} \begin{proof}
+\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$
+.%, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]
+\end{corollary} \begin{proof}
 Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
@@
 Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$.
-
-The second assertion of the lemma can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}
+%The second assertion of the lemma can be verified directly using~\eqref{eq:symbol-properties}. 
+\end{proof}
 
@@
 \subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor.} \label{sec:V-construction}
-Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
-Let $A$ be a local ring with maximal ideal $M$ and residue field $k$.
-As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.
-
-For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
-Notice that the map $j_+i_+$ is split by the map $ev^*_{X=a}$ of evaluation at $a\neq 0$, hence $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$. Consider the following commutative diagram.
-\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
-              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R). &  } \] 
-We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$.               
+Throughout this subsection $\Phi$ denotes an arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. 
+\begin{df}\label{df:GM0_geq0}
+Denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$. 
+Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
+\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R)} \]
+Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. \end{df}
+Notice that the map $j_+^Mi_+^M$ is split by the homomorphism $ev^*_{X=a}$ of evaluation at $a\neq 0$, therefore $G_M^0$ can be considered as a subgroup of $\overline{G}^{\geq 0}_M$.
+
 Denote by $\overline{V}_T$ the quotient of the set of triples 
@@
 
-Sometimes it will be more convenient for us to work with another set $\overline{V}$ isomorphic to $\overline{V}_T$.
-Denote by $V$ the subset of $\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times$ consisting of those triples $(g, h, u)$ for which $p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
-
-We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$. This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$.
+Sometimes it will be more convenient for us to work with another set $\overline{V}$ isomorphic to $\overline{V}_T$ (this isomorphism will be established below).
+Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which $p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
+
+We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$. Since $G^0_M \subset \overline{G}^{\geq 0}_M$, we see that $V \cdot G_M^0 \subseteq V$.
+
 We denote by $\overline{V}$ the set of orbits of this action and use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
@@
 
-From~\cref{SR:additivity} it follows that
-\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
-therefore $t_\alpha(aX^{-1})$ is well-defined.
-
+Notice that $t_\alpha(aX^{-1}) (g, h, u) \in V$. Indeed, from~\cref{SR:additivity} we obtain that
+\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq \overline{G}_M^{\geq 0}.\]
 \begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
@@
  First of all, let us show that the resulting function is total. 
- Fix $v_0 = (g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
+ Fix $v_0 = (g, h, u) \in V$.
+Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$ Notice that the map $i_+$ is split by $ev^*_{X=0}$.
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
- $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$, which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_-(h_0), u)$ lying in the same $G_M^0$-orbit as $v_0$.
-
- Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
+ $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])).$ The latter subgroup is contained in $P_\alpha(*)$ by~\cref{Pstar-large}.
+Thus, $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_-(h_0), u)$ lying in the same $G_M^0$-orbit as $v_0$.
+
+ Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of representative.
  Let $v_1 = (g, h_1, u)$ and $v_2 = (g, h_2, u)$ be two elements of the same $G_M^0$-orbit for which both $p(v_1)$ and $p(v_2)$ belong to $P_\alpha(*)$.
@@
 
-For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
-\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, [h], u) = (x_\alpha(a + Xf) \cdot g, [h \cdot x_{\alpha}(-a)], u).  \end{equation}
-It is easy to see that this definition is correct.
+Our next goal is to define for $a + Xf \in A + XM[X]$ the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$.
+Let $(g, h, u)$ be an element of $V$. We define the value of $T_\alpha(a + Xf)$ on $(g, h, u)$ via the following identity:
+\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h \cdot x_{\alpha}(-a), u).  \end{equation}
+Notice that $p(T_\alpha(a + Xf) \cdot (g, h, u)) = x_\alpha(Xf) \cdot {}^{x_\alpha(a)}p(g, h, u) \in \overline{G}_M^{\geq 0},$ therefore
+ the right-hand side of~\eqref{T_leq0} lies in $V$. Finally, the fact that~\eqref{T_leq0} gives rise to a well-defined map $\overline{V} \to \overline{V}$ follows
+  from the following identity:
+\[T_\alpha(a + Xf) \cdot ((g, h, u) \cdot h_0) = (T_\alpha(a + Xf) \cdot (g, h, u)) \cdot {}^{x_{\alpha}(a)}\!h_0.\]
+
+It is easy to see that the expression in the right-hand side of~\eqref{T_leq0} does not depend on the choice of the representative for $h$.
 
@@
 
-\begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
-\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, [h], u) = (g, [h], u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b\in A + XM[X]$.
+\begin{lemma} \label{R1_d} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R1}_d$ for all $d \leq 1$. \end{lemma}
+\begin{proof}
+ For $d \leq 0$ the assertion immediately follows from~\eqref{T_leq0}, so let us consider the case $d = 1$.
+
+ Let $a$ and $b$ be elements of $A$ and $(g, h, u)$ be an element of $V$.
+ By the first part of the proof of~\cref{lem:orbit-action} we may assume that $p(g,h,u)\in P_\alpha(m)$ for some $m \in M$.
+ From~\eqref{T_1} we obtain that 
+ \begin{equation}\label{add-computation}
+  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
+ \end{equation}
+ where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.
+ Notice that we can not naively invoke~\eqref{T_1} for the second time because the value of the function $p$ on the triple $(x_\alpha(aX^{-1})\cdot g ,\ h',\ u \cdot (1 + am))$ does not belong to $P_\alpha(*)$.
+
+ However, it is very easy to fix this. Indeed, we are free to replace $[h]$ with $[h \cdot h_0]$ for any $h_0 \in G_M^0$, so in~\eqref{add-computation} we
+  can replace $h'$ with $h'' = h' \cdot h^{-1}_\alpha(1+am)$. Now from~\cref{SR:additivity} we obtain that
+ \[ p(x_\alpha(aX^{-1})\cdot g ,\ h'',\ u \cdot (1 + am)) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1+am) \in P_\alpha\left(\tfrac{m}{1+am}\right).\]
+ Now we can invoke~\eqref{T_1} once again and can continue~\eqref{add-computation} as follows:
+ \begin{equation}\label{add-computation2}
+  \ldots = \left(x_\alpha((a + b)X^{-1})\cdot g ,\ \left[ h'' \cdot x_\alpha\left(\tfrac{-bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \right],\ u \cdot (1 + am) \cdot \left(1+\tfrac{bm}{1+am}\right)\right).
+ \end{equation} 
+ Notice that 
+ \[ \left[h'' \cdot x_\alpha\left(\tfrac{-b(1+am)X^{-1}}{1+am + bm}\right)\right] = \left[h \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1 + am}\right) \cdot x_\alpha\left(\tfrac{-bX^{-1}}{(1+am)(1+am+bm)}\right)\right] =
+ \left[h \cdot x_\alpha\left(\tfrac{-(a+b)X^{-1}}{1+(a+b)m}\right)\right].\] 
+ Thus, the expression in~\eqref{add-computation2} coincides with the expression for $T_\alpha((a+b)X^{-1})\cdot (g, [h], u)$ given by~\eqref{T_1}. \end{proof}
+
+\begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}^\angle_{d, 1}$, $\mathrm{R3}^\bot_{d,1}$ for $d\leq 0$. \end{lemma}
+\begin{proof}
+We will verify $\mathrm{R3}^\angle_{d, 1}$ and $\mathrm{R3}^\bot_{d, 1}$ simultaneously. Fix some $\beta \in Z(\alpha) = Z_0(\alpha) \sqcup Z_+(\alpha)$.
+
+We need to show that $[T_\beta(b), T_\alpha(aX^{-1})](g, [h], u) = (g, [h], u)$ for $a\in A$, $b\in A + XM[X]$. 
 Write $b = b_0 + Xf$ for some $b_0 \in A$, $f \in M[X]$.
-We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
-It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation by $x_\beta(b_0)$, therefore by~\cref{SR:additivity} we have
-\begin{multline} \nonumber
-  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, [h], u) = \\
-  = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha(-aX^{-1}) \cdot g, [h'], u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h''], u] \right) = \left(g, [h], u\right), \end{multline}
-where $h' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0)$ and
-\begin{multline} \nonumber
- h'' = h' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = \\
- = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am). \qedhere \end{multline}
+As in the proof of the previous lemma, we may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+From~\eqref{T_leq0}--\eqref{T_1} we obtain that
+\begin{equation} \label{R3leq0-computation}
+  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, [h], u) = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(g', [h'], u(1-am)\right), \end{equation}
+where $g' = x_\beta(-b) \cdot x_\alpha(-aX^{-1}) \cdot g$, $h' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot x_\beta(b_0)$.
+
+Notice that by~\eqref{eq:conj-h-x} $[h'] = [h'']$, where $h'' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0).$
+From~\cref{P0-conj-invariant} and \cref{SR:additivity} we obtain that
+\begin{multline*} p(g',h'',u(1-am)) = x_{\beta}(-Xf) \cdot \left(S_\alpha(a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\right)^{x_\beta(b_0)} \in \\ \in x_{\beta}(-Xf) \cdot P_\alpha(\tfrac{m}{1-am})^{x_\beta(b_0)} \subseteq P_\alpha(\tfrac{m}{1-am}).\end{multline*}
+Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
+\begin{equation*} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation*}
+where in the last equaltity we use the following computation:
+\begin{equation} \nonumber
+ h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am).
+\end{equation}
 \end{proof}
@@
 \begin{lemma} \label{R3_leqm1_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
-\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
- \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, [h], u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, [h], u\right). \]
+\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle one has 
+ \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, [h], u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, [h], u\right) = T_{\alpha+\beta}(N_{\beta, \alpha} \cdot af) (g, [h], u). \]
 
@@
 \end{prop}
-\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
+\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R1_d}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
 On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

### 2020-04-11 dl-paper.tex
Minor fix

@@
 \begin{equation*} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation*}
-where in the last equaltity we use the following computation:
+where in the last equality we use the following computation:
 \begin{equation} \nonumber
@@
 Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
-From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
+From~\cref{K-a-b-cor} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
 Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that

### 2020-04-12 dl-paper.tex
Fix 28 and 29

--- 2020-04-10 dl-paper.tex
@@
  \item We denote by $R$ the Laurent polynomial ring $A[X, X^{-1}]$. We set $t = X^{-1}$, so that $R = A[X, X^{-1}] = A[t, t^{-1}]$.
- \item $B = B_{A, M}$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$. Obviously, $B = A[t]$ in the case $M=0$ and $B = R$ in the case $M=A$.
+ \item $B = B_{A, M}$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$.
  \item $I$ denotes the ideal $M[X, X^{-1}]$ of $R$. Notice that $I$ is also an ideal of $B$.
@@
 Notice that $p(T_\alpha(a + Xf) \cdot (g, h, u)) = x_\alpha(Xf) \cdot {}^{x_\alpha(a)}p(g, h, u) \in \overline{G}_M^{\geq 0},$ therefore
- the right-hand side of~\eqref{T_leq0} lies in $V$. Finally, the fact that~\eqref{T_leq0} gives rise to a well-defined map $\overline{V} \to \overline{V}$ follows
-  from the following identity:
-\[T_\alpha(a + Xf) \cdot ((g, h, u) \cdot h_0) = (T_\alpha(a + Xf) \cdot (g, h, u)) \cdot {}^{x_{\alpha}(a)}\!h_0.\]
-
-It is easy to see that the expression in the right-hand side of~\eqref{T_leq0} does not depend on the choice of the representative for $h$.
+ the right-hand side of~\eqref{T_leq0} lies in $V$. Notice that for $h_0 \in G^0_M$ one has
+\[T_\alpha(a + Xf) \cdot ((g, h, u) \cdot h_0) = (T_\alpha(a + Xf) \cdot (g, h, u)) \cdot {}^{x_{\alpha}(a)}\!h_0,\]  
+therefore~\eqref{T_leq0}, indeed, gives rise to a well-defined map $\overline{V} \to \overline{V}$.
 
@@
  where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.
- Notice that we can not naively invoke~\eqref{T_1} for the second time because the value of the function $p$ on the triple $(x_\alpha(aX^{-1})\cdot g ,\ h',\ u \cdot (1 + am))$ does not belong to $P_\alpha(*)$.
+ Notice that we can not invoke~\eqref{T_1} for the second time because the value of the function $p$ on the triple $(x_\alpha(aX^{-1})\cdot g ,\ h',\ u \cdot (1 + am))$ does not belong to $P_\alpha(*)$.
 
@@
 Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
-\begin{equation*} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation*}
-where in the last equaltity we use the following computation:
+\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}
+where in the last equality we use the following computation:
 \begin{equation} \nonumber
@@
 \end{equation}
-\end{proof}
+The assertion of the lemma now follows from~\eqref{R3leq0-computation}--\eqref{R3leq0-computation2}. \end{proof}
 
 \begin{lemma} \label{R3_leqm1_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
-\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle one has 
- \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, [h], u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, [h], u\right) = T_{\alpha+\beta}(N_{\beta, \alpha} \cdot af) (g, [h], u). \]
-
-As before, we may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
-Since $x_\beta(Xf)$ belongs to $P_\alpha(0)$ we obtain from~\cref{SR:additivity} that:
+\begin{proof} Let $a \in A$, $f \in M[X]$ and $\alpha$, $\beta$ be a pair of roots forming an obtuse angle. As before, we may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
+From~\eqref{T_1}--\eqref{T_leq0} and the fact that $x_\beta(Xf) \in P_\alpha(0)$ we obtain that
 \begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ [h],\ u\right) = \\ 
-= T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am)\right],\ u(1-am)\right) = \\ = \left([x_\beta(Xf),\ x_\alpha(aX^{-1})] \cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right)\right],\ u \right) = \\ = (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ [h],\ u).
-\qedhere \end{multline} \end{proof}
+= T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am)\right],\ u(1-am)\right) = \\ = \left([x_\beta(Xf),\ x_\alpha(aX^{-1})] \cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right)\right],\ u \right) = \\ = (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ [h],\ u) = T_{\alpha+\beta}(N_{\beta, \alpha} \cdot af) (g, [h], u).
+\end{multline}
+
+As in the proof of Lemmas~\ref{R1_d}--\ref{R3_leq0_1}, in the above computation we had to add the factor $h_\alpha^{-1}(1-am)$ to the second triple, so that we could pass from the second line to the third one (again, we need to invoke \cref{SR:additivity} to check that the value of $p$ on the second triple lies in the coset $P_\alpha(\tfrac{m}{1-am})$).
+\end{proof}
 
@@
 \begin{proof}
-Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
+Let $a, b \in A$ and $\alpha$, $\beta$ be a pair of roots forming a sharp angle.
+Set $\epsilon = N_{\alpha,-\beta}$.
 From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\beta}(m')\text{ for some }m,m' \in M.\]
-Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
-\begin{multline} \nonumber
- T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = 
- T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
- = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am')\right],\ u(1 + am)\right) = \\
- = (x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g, [h'], u(1 + am + bm')), \end{multline}
-where 
-\begin{multline} \nonumber
- h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
-    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
- = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
- \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
+From~\eqref{T_1} we obtain that
+\begin{multline} \label{R3_1_1-computation}
+ T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = \\
+ = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
+ = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h'\right],\ u(1 + am)\right),
  \end{multline}
-In the last calculation notation $h \sim h'$ means that $h$ and $h'$ lie in the same left $G_M^0$-coset.
-If we swap $(a,\alpha,m)$ with $(b,\beta,m')$, the expressions in the right-hand sides of the above formulae will remain unchanged. This implies the required assertion.
+where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am').$
+Notice that by~\cref{SR:sharp}
+\[ p(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)) = S_\alpha(p(g, h, u) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
+therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
+\begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g, \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right], u(1 + am + bm')\right).
+\end{equation}
+The second component of the above triple can be simplified using~\eqref{eq:conj-h-x} as follows:
+\begin{multline*}
+ \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
+ = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right)\right] = \\
+ = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am)\right] = \\
+ = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right)\right].
+\end{multline*}
+Thus, we see that the expression in the right-hand side of~\eqref{R3_1_1-computation2} would remain unchanged if we swapped $(a,\alpha,m)$ with $(b,\beta,m')$. This implies the required assertion.
 \end{proof}
@@
 \begin{proof} 
-Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
-As before, we may assume $p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')$ for some $m, m' \in M$.
-Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
+Let $a, b \in A$ and $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. Set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
+
+As before, we may assume that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')\ttxt{ for some $m, m' \in M\].
+
 Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 

### 2020-04-12 dl-paper.tex
Fix 30-31

@@
 From~\cref{P0-conj-invariant} and \cref{SR:additivity} we obtain that
-\begin{multline*} p(g',h'',u(1-am)) = x_{\beta}(-Xf) \cdot \left(S_\alpha(a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\right)^{x_\beta(b_0)} \in \\ \in x_{\beta}(-Xf) \cdot P_\alpha(\tfrac{m}{1-am})^{x_\beta(b_0)} \subseteq P_\alpha(\tfrac{m}{1-am}).\end{multline*}
+\begin{multline*} p(g',h'',u(1-am)) = x_{\beta}(-Xf) \cdot \left(S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\right)^{x_\beta(b_0)} \in \\ \in x_{\beta}(-Xf) \cdot P_\alpha(\tfrac{m}{1-am})^{x_\beta(b_0)} \subseteq P_\alpha(\tfrac{m}{1-am}).\end{multline*}
 Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
@@
 Notice that by~\cref{SR:sharp}
-\[ p(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)) = S_\alpha(p(g, h, u) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
+\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
 therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
-\begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g, \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right], u(1 + am + bm')\right).
+\begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g,\ \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right],\ u(1 + am + bm')\right).
 \end{equation}
@@
 
-As before, we may assume that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')\ttxt{ for some $m, m' \in M\].
-
+As before, we may assume that \[p(g, h, u) \in j_+\left(K(A[X], M[X])\right) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m')\text{ for some $m, m' \in M$.} \]
+
+%Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
+%
+From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
+\begin{multline} \label{R2_0_1-computation}
+[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
+= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\beta}(b)],\ u (1 - am) \right) = \\
+= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
+ \end{multline} 
+ where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$.
 Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that
+\begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
+ x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha(\tfrac{m+\epsilon bm'}{1-am}). \end{multline*}
+Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
+\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained via~\eqref{eq:conj-h-x} as follows:
  \begin{multline} \nonumber
-[T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
- = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right) = \\
- = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
- where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
-  and the last equality is obtained as follows:
- \begin{multline} \nonumber
- h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
- = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
-\qedhere
+ [h''] = \left[ h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
+ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].
 \end{multline}
+The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.
 \end{proof}
@@
 \begin{enumerate}
- \item For any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
+ \item For any $h_1 \in \St(\Phi, A[X\inv])$ one has $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
  \item If we consider $\St(\Phi, A[X, X\inv])$ as a set with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-sets.

### 2020-04-12 dl-paper.tex
Minor fixes

@@
 \begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
- x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha(\tfrac{m+\epsilon bm'}{1-am}). \end{multline*}
+ x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha\left(\tfrac{m+\epsilon bm'}{1-am}\right). \end{multline*}
 Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
-\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained via~\eqref{eq:conj-h-x} as follows:
+\begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained from~\eqref{eq:conj-h-x} as follows:
  \begin{multline} \nonumber
@@
 \end{prop}
-\begin{proof} By~\cref{superfluous-relations} and Lemmas~\ref{R1_d}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined.
-On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).
-
-The first property can be verified directly using~\eqref{T_1}, \eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
+\begin{proof} By Lemmas~\ref{R1_d}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1}--\eqref{T_leq0} is well-defined (thanks to~\cref{superfluous-relations} we do not need to verify that it satisfies $\text{R3}_{1,1}^\bot$).
+On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (recall that $t = X^{-1}$).
+
+The first property can be verified directly using~\eqref{T_1}--\eqref{T_leq0} and the fact that $\St(\Phi, A[X\inv])$ is generated by $x_\alpha(a)$ and $x_\alpha(aX\inv)$ for $\alpha\in\Phi$, $a\in A$.
 The second property can be verified in a similar fashion.

### 2020-04-12 dl-paper.tex
Fix 33-34

@@
 This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
-\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, I) \ar[r]^(.65){t} & \St(\Phi, B) \ar[d]^{j_R} \\
+\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, I) \ar[r]^{t} & \St(\Phi, B) \ar[d]^{j_R} \\
    \St(\Phi, A[X]) \ar[rr]^{j_+} & & \St(\Phi, R). } \]
 
-\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ holds $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
-\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$.
+\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
+\begin{proof} 
+In view of~\cref{thm:Tits} it suffices to verify the assertion of the lemma for the generators $p_1 = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$.
+We accomplish this by induction on the degree of $\xi$ in $X$.
+
+First of all, notice that the base case $\xi = a \in A$ can be verified by direct computation involving~\eqref{eq:VVT} and~\eqref{T_leq0}.
 Using~\cref{lem:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
-
-It suffices to verify the assertion of the lemma for the generators $p_1 = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
-induction on the degree of $\xi$ in $X$. The base of induction is clear.
 
@@
 \begin{equation*} \langle a, m \rangle^{-1} \cdot \langle aX^{-1}, mX \rangle \cdot [1, 1, 1] = [1, 1, 1+am]. \end{equation*} \end{rem}
-
-\begin{comment}
-\begin{equation} \label{T_2} t_\alpha(aX^{-1}) (g, h, u) = \left[ x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right) h ,\ u \cdot (1 + am)\right].\end{equation}
-
-\begin{multline*}
- t_\alpha(aX^{-1}) (x_{-\alpha}(mX), 1, 1) = \left[ x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \{ X, 1+am \} ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right] = \\
- = \left[ x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) ,\ x_\alpha\left(\tfrac{aX^{-1}}{1 + am}\right),\  (1 + am)\right]
-\end{multline*}
-
-This implies that 
-\begin{multline*} x_{\alpha}\left(\tfrac{-aX^{-1}}{1+am}\right) \cdot h_\alpha(1+am)^{-1} \cdot \langle a, m \rangle^{-1} \cdot x_{-\alpha}\left(\tfrac{-mX}{1+am}\right) x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) [1, 1, 1] = [1, 1, 1+am]
-\end{multline*}
-
-\begin{equation} \langle a,m \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- m}{1 + am}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(m) \cdot x_{\alpha}\left(\tfrac{- a}{1+am}\right) \cdot h_{\alpha}^{-1}(1 + am).
-\end{equation}
-\begin{equation} \langle a,m \rangle _ \alpha ^{-1} =  h_{\alpha}(1 + am) \cdot x_{\alpha}\left(\tfrac{a}{1+am}\right) \cdot x_{-\alpha}(-m) \cdot x_{\alpha}(-a) \cdot x_{-\alpha}\left(\tfrac{m}{1 + am}\right).
-\end{equation}
-\end{comment}
 
@@
  By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
- Since $j_+i_+$ is injective, we conclude that $g = 1$.
+ Notice that $j_+i_+$ is split by the evaluation homomorphism $ev_{X=a}^*$, $a\neq 0$ and therefore is injective. Thus, we conclude that $g = 1$.
 

### 2020-04-12 dl-paper.tex
Some further fixes

@@
 Denote by $C_1$ the commutator subgroup $[\St(\Phi, XA[X]),\ \St(\Phi, M)]$.
-It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \myol{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
+It is clear that for $g \in \St(\Phi, XA[X])$, $h \in \myol{H}(\Phi, A, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ one has:
 \[ [g,\ h u^+ u^-] = [g,\ h] \cdot [{}^{h}\!g,\ {}^{h}\!(u^+u^-)] \in \St(\Phi, A[X], XM[X]) \cdot C_1.\]
@@
  In the cases $\Phi = \rA_3, \rD_4$, $M \neq A$ it is still possible to prove the injectivity of $i_n$ starting from $n\geq 2$ using a variation of the argument of Rehmann--Soul{\'e} (cf.
-the lower bound for $m$ in~\cite[3.2.1]{RS76}).
+the lower bound for $m$ in 3.2.1 of~\cite{RS76}).
 However, apparently, it is not possible to establish the injectivity of $i_1$ in the specified cases using arguments similar to~\cite{RS76}.
@@
  Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B^-)$.
- By~\cref{prop43} holds $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
+ By~\cref{prop43} one has $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
  Notice that $j_+i_+$ is split by the evaluation homomorphism $ev_{X=a}^*$, $a\neq 0$ and therefore is injective. Thus, we conclude that $g = 1$.

### 2020-04-14 dl-paper.tex
Fix Lavrenov issues

--- 2020-04-12 dl-paper.tex
@@
 \DeclareMathOperator{\St}{St}
-\DeclareMathOperator{\GG}{G}
 \DeclareMathOperator{\E}{E}
@@
 \newcommand{\myol}[2][3]{{}\mkern#1mu\overline{\mkern-#1mu#2}}
-
+\newcommand{\GG}{\mathrm{G}_{\mathrm{sc}}}
 \newcommand{\ZZ}{\mathbb{Z}}
@@
 For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
-This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_{1,n}(k[x_1, \ldots x_n]) = \K_{1,n}(k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
+This result asserts that the functor $\K_1(n, R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_1(n, k[x_1, \ldots x_n]) = \K_1(n, k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
 Suslin's results were subsequently generalized to $\K_1$-functors modeled on other linear groups (see the definition below).
@@
 
-Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $G(\Phi, R)$ (see e.\,g.~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
-There is a well-defined map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on the Chevalley group $G(\Phi, -)$, see~\cite{St78}.
+Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $\GG(\Phi, R)$ (see e.\,g.~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
+There is a well-defined map $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
+The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on the Chevalley group $\GG(\Phi, -)$, see~\cite{St78}.
 
@@
 all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers which can only take values $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G(\Phi, R)$.
+The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers which can only take values $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $\GG(\Phi, R)$.
 Several different methods of computing signs of these constants have been proposed in the literature, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.
@@
 Let us verify the second assertion. Let $g$ be an element of the intersection of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$.
-Clearly, the image of $g$ in $G(\Phi, k[X, X\inv])$ lies in $G(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[X]) = \K_2(\Phi, k)$.
+Clearly, the image of $g$ in $\GG(\Phi, k[X, X\inv])$ lies in $\GG(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[X]) = \K_2(\Phi, k)$.
 Thus, we conclude that $g \in \St(\Phi, k)$.
@@
  For every pair $(R, I)$ the map $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of $\nu \colon S(R) \to S(R/I)$.
-The group $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R), S(R/I), \ZZ)$.
+The group $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R/I), S(R); \ZZ)$.
 \end{lemma}
@@
 The map $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-map with respect to this action.
-From~\ref{req:left-exact} and $\varphi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
+From~\ref{req:left-exact} and $\pi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
 $G_0 \cap G_1 \subseteq \Ker(\pi_{D_{R, I}})$ hence it is a central subgroup of $S(D_{R,I})$ by~\ref{req:uce}.
@@
  By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
- From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
+ From the last equality and the injectivity of the map $\GG(\Phi, A[X]) \to \GG(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $\GG(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
 It follows from~\cref{thm:Stein} that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and hence by~\cref{Z-DS} it is contained in $Z_\alpha(A, M)$.
@@
 
-For a pair $(R, I)$ denote by $\E(\Phi, R, I)$ the {\it relative elementary subgroup} of $G(\Phi, R)$, i.\,e.
-the image of the relative Steinberg group $\overline{\St}(\Phi, R, I)$ under the map $\pi \colon \St(\Phi, R) \to G(\Phi, R)$.
+For a pair $(R, I)$ denote by $\E(\Phi, R, I)$ the {\it relative elementary subgroup} of $\GG(\Phi, R)$, i.\,e.
+the image of the relative Steinberg group $\overline{\St}(\Phi, R, I)$ under the map $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$.
 From the second property of the above proposition we immediately obtain the following group factorization.

### 2020-04-14 dl-paper.tex
Use nonitalic font for enumerate

@@
 \newtheorem{cond}[lemma]{Condition}
-
-\newlist{proplist}{enumerate}{1} \setlist[proplist]{label=(\roman{proplisti}), ref=\thethm.(\roman{proplisti}),noitemsep} \Crefname{proplisti}{Proposition}{Propositions}
-\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelem.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
 
@@
 Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of the following data:
-\begin{enumerate}
+\begin{enumerate} [label=\normalfont(\arabic*)]
  \item a group $N$ acting on itself by left conjugation (i.\,e. ${}^{n}\!n' = n n' n^{-1}$).
@@
 For the rest of this subsection $S \xrightarrow{\pi} P \subseteq G$ is a triple of group-valued functors on the category of commutative rings satisfying the following assumptions:
-\begin{enumerate} [label=(A\arabic*)]
+\begin{enumerate} [label=\normalfont(A\arabic*)]
  \item \label{req:left-exact} $G(D_{R, I}) \cong G(R) \times_{G(R/I)} G(R)$.
@@
 It is not hard to obtain the following concrete description of these functors in the cases $i=1,2,3$.
-\begin{lemma}\label{lem:lowerKgroups} There are natural isomorphisms \begin{enumerate}
+\begin{lemma}\label{lem:lowerKgroups} There are natural isomorphisms \begin{enumerate} [label=\normalfont(\arabic*)]
  \item $\K_1^{G,P}(R) \cong G(R) / P(R)$;
@@
 The elements $z_\alpha(s, \xi)$ satisfy the following relations for all $\xi, \eta\in R$, $s\in I$:
-\begin{enumerate} 
+\begin{enumerate} [label=\normalfont(\arabic*)]
 \item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item If $\alpha+\beta\in\Phi$ then one has:
+\item If $\alpha+\beta\in\Phi$ then
 \begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
-  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
+  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta),\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
 \end{enumerate} \end{lemma}
@@
 \end{multline} 
-and the required assertion follows from~\eqref{Z2}.
+and the required assertion follows from~\ref{Z2}.
 \end{proof}
@@
 It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n>1$ (in fact, $n=2$).
-It remains to see that relation~\eqref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
+It remains to see that relation~\ref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
 \end{rem}
@@
 The elements $c_\alpha(s, t)$ satisfy the following relations for all $s\in I,\ t\in J,\ \xi\in R$:
- \begin{enumerate}
+ \begin{enumerate} [label=\normalfont(\arabic*)]
  \item \label{C1} $[c_\beta(s, t),\ x_{\alpha}(\xi)] = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta}\cdot s^2t\xi)$ if $\alpha+\beta \in \Phi$;
@@
 = x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
-The assertion~\eqref{C3} is obvious. Finally, last assertion can be obtained as follows:
+The assertion~\ref{C3} is obvious. Finally, last assertion can be obtained as follows:
 \begin{align*}
@@
 Clearly, the set consisting of $x_\beta(\xi)$, $\xi \in A[X]$, $\beta \neq \pm \alpha$ is such a generating set, 
- and in this case the required inclusions follow from~\eqref{C1}--\eqref{C3} of~\cref{Crels}. \end{proof}
+ and in this case the required inclusions follow from~\ref{C1}--\ref{C3} of~\cref{Crels}. \end{proof}
 
@@
 Let $\beta\in\Phi$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type P1.
-By~\cref{Zrels}\eqref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
+By~\cref{Zrels}\ref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi).
 \label{eq3-1} \end{equation}
 The expression in the right-hand side is a product of generators of type P4, P1, P1 (see~\cref{rem:recognition}).
-Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type P2 (so that $\alpha-\beta\in\Phi$). Again by~\cref{Zrels}\eqref{Z2}
+Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type P2 (so that $\alpha-\beta\in\Phi$). Again by~\cref{Zrels}\ref{Z2}
 \begin{equation}
@@
 
-Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type P1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\eqref{Z3}
+Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type P1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\ref{Z3}
 \begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
@@
 Finally, let $g = x_\alpha(f)$ be a generator of type P5.
-Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
+Substituting in~\ref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\ref{Z5} through other terms we obtain that
 \begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
@@
 Let $z_\gamma(Xf, \xi)$ be a generator of type K1 for some $\gamma \in \Phi \setminus \Psi$.
-In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\eqref{Z4}.
-If $\gamma$ is such that $\alpha + \gamma \in \Phi$ we obtain from~\cref{Zrels}\eqref{Z2} that
+In the case $\gamma \perp \alpha$ this generator commutes with $x_\alpha(aX^{-1})$ by~\cref{Zrels}\ref{Z4}.
+If $\gamma$ is such that $\alpha + \gamma \in \Phi$ we obtain from~\cref{Zrels}\ref{Z2} that
 \begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\gamma} (N_{\gamma, \alpha}\cdot af) \cdot z_{\gamma}(Xf, \xi). \end{equation}
-On the other hand, if $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\eqref{Z3} that
+On the other hand, if $\gamma$ is such that $\alpha - \gamma \in \Phi$, we obtain from~\cref{Zrels}\ref{Z3} that
 \begin{equation} z_{\gamma}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\gamma} (N_{\gamma,-\alpha}\cdot af\xi^2) \cdot z_{\gamma}(Xf, \xi). \end{equation}
@@
 
-A similar computation using \eqref{C1}--\eqref{C3} of \cref{Crels} shows that the conjugate of a generator of type K5 is either the generator itself or a product of generators of type Z, Z, K5.
+A similar computation using \ref{C1}--\ref{C3} of \cref{Crels} shows that the conjugate of a generator of type K5 is either the generator itself or a product of generators of type Z, Z, K5.
 
@@
 $\alpha-\delta \in \Phi$.
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\eqref{Z5} we obtain that
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\ref{Z5} we obtain that
 \begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
@@
 Suppose that the assertion holds for all $p_1 = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
-Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ into~\eqref{Z5} we obtain the following equality in $\St(\Phi, B)$:
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ into~\ref{Z5} we obtain the following equality in $\St(\Phi, B)$:
 \begin{multline*}

### 2020-04-14 dl-paper.tex
More details on UCT

@@
 Recall from the proof of~\cite[Th{\'e}or{\`e}me~2]{Lo78} that to every relative central extension $(M, \mu)$ of $\nu$ with kernel $L$ one can associate a map of abelian groups $C \to L$.
-This map is obtained from the characteristic class $\xi(M, \mu)$ via the isomorphism $\HH^3(Q, N; L) \cong \mathrm{Hom}(C, L)$ of the universal coefficients theorem.
+This map is obtained from the characteristic class $\xi(M, \mu)$ via the isomorphism $\HH^3(Q, N; L) \cong \mathrm{Hom}(C, L)$ of the universal coefficients theorem for cohomology (for this isomorphism we need the vanishing of $\HH_2(Q, N; \ZZ)$, which is a consequence of~\ref{req:uce}).
 
@@
  \item $\K_3^{G,P}(R) \cong \HH_3(S(R), \ZZ).$ \end{enumerate} \end{lemma}
-\begin{proof} The first claim is obvious, the second and the third claim follow from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
+\begin{proof} The first claim is obvious, the other ones follow from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
 Exercises~1.8--1.9 ibid.) \end{proof}
@@
 Set $g_0 = ev^*_{X=0}(g_+)$, $h_+ = g_+ \cdot i_+(g_0^{-1})$, $h_- = g_- \cdot i_-(g_0^{-1})$.
- Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$ the image $\lambda_M^*(h_+)\in \St(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}
+ Notice that $h_+ \in \overline{\St}(\Phi, A[X], XA[X])$, moreover, for every maximal ideal $M$ of $A$ the image $\lambda_M^*(h_+)\in \overline{\St}(\Phi, A_M[X], XA_M[X])$ is trivial by~\cref{thm:P1glueing}
   (since $j_+(\lambda^*_M(h_+)) = j_-(\lambda^*_{M,-}(h_-))$).

### 2020-04-14 dl-paper.tex
Many fixes

@@
 Recall that to every irreducible root system $\Phi$ and a commutative ring $R$ one can associate two groups: the {\it simply-connected Chevalley group} $\GG(\Phi, R)$ (see e.\,g.~\cite[\S~3]{St71} or~\cite{VP}) and the {\it Steinberg group} $\St(\Phi, R)$ (see~\cref{sec:Steinberg-intro} for the definition).
-There is a well-defined map $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this map are, by definition, the $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$-functors modeled on the Chevalley group $\GG(\Phi, -)$, see~\cite{St78}.
+There is a well-defined homomorphism $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
+The cokernel and the kernel of this homomorphism (denoted $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$, respectively) are, by definition, the values of the so-called $\mathrm{K}_1$ and $\mathrm{K_2}$-functors modeled on the Chevalley group $\GG(\Phi, -)$, see~\cite{St78}.
 
@@
 \begin{theorem}[Horrocks theorem for orthogonal $\K_2$]\label{thm:main} Let $A$ be a commutative ring in which $2$ is invertible.
-Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all maps are injective:
+Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all homomorphisms are injective:
 \begin{equation} \nonumber
@@
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
-Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two maps:
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two homomorphisms:
 \[ \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\]
-The injectivity of the second map is obtained in~\cref{thm41}.
+The injectivity of the second homomorphism is obtained in~\cref{thm41}.
 This is the only place in our proof which invokes the assumption that $2$ is invertible.
 The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain basic calculations with Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
-Finally, the injectivity of the first map is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+Finally, the injectivity of the first homomorphism is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
 This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ containing a subsystem of type $\rA_4$.
@@
 
-\begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
+\begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the homomorphism $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
 Moreover, the intersection of the images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.
@@
 Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with $1$ and $I$ is a (not neccessarily proper) ideal of $R$.
-A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a unit-preserving ring map $f \colon R \to R'$ such that $f(I) \subseteq I'$.
+A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a (unit-preserving) ring homomorphism $f \colon R \to R'$ such that $f(I) \subseteq I'$.
 Notice that the mapping $(R, I) \mapsto (R \to R/I)$ defines a functor from $\catname{Pairs}$ to the morphism category $\catname{CRings}^\rightarrow$.
@@
 Set $G_i = \Ker(S(p_i))$ and define {\it Loday's relativization} $S(R, I)$ as $ G_0 / [G_0, G_1]$.
-The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$.
+The homomorphism $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$.
 We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$: \begin{equation} \label{LodayRelativization} \xymatrix{ 1 \ar[r] & C_S(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1.} \end{equation}
@@
  \item \label{req:subfunc} $P(R)$ is a perfect normal subgroup of $G(R)$.
- \item \label{req:uce} The map $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$.
+ \item \label{req:uce} The homomorphism $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$.
 \end{enumerate}
@@
 \begin{lemma}\label{lem:relativeH3}
- For every pair $(R, I)$ the map $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of $\nu \colon S(R) \to S(R/I)$.
+ For every pair $(R, I)$ the homomorphism $\mu \colon S(R, I) \to S(R)$ is a universal relative central extension of $\nu \colon S(R) \to S(R/I)$.
 The group $C_S(R, I)$ is naturally isomorphic to the relative homology group $\HH_3(S(R/I), S(R); \ZZ)$.
@@
 The action of $S(R)$ on $S(D_{R, I})$ given by ${}^g h = S(\Delta)(g) \cdot h \cdot S(\Delta)(g)^{-1}$ induces an action of $S(R)$ on $S(R, I)$.
-The map $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-map with respect to this action.
+The homomorphism $\mu \colon S(R, I) \to S(R)$ from~\eqref{LodayRelativization} is an $S(R)$-homomorphism with respect to this action.
 From~\ref{req:left-exact} and $\pi(G_i) \subseteq \Ker(G(p_i))$ we obtain that 
 $G_0 \cap G_1 \subseteq \Ker(\pi_{D_{R, I}})$ hence it is a central subgroup of $S(D_{R,I})$ by~\ref{req:uce}.
-Thus, we have verified the assumptions of~\cite[Proposition~6]{Lo78} which asserts that the map $\mu$ is a universal relative central extension of the coequalizer $\nu = \mathrm{coeq}(d_0, d_1)$.
+Thus, we have verified the assumptions of~\cite[Proposition~6]{Lo78} which asserts that the homomorphism $\mu$ is a universal relative central extension of the coequalizer $\nu = \mathrm{coeq}(d_0, d_1)$.
 Since $\nu$ coincides with $S(R) \to S(R/I)$ by~\ref{req:coeq}, we have completed the proof of the first assertion of the lemma.
@@
 Set $N = S(R)$, $Q = S(R/I)$, $C = \HH_3(Q, N; \ZZ)$.
-Recall from the proof of~\cite[Th{\'e}or{\`e}me~2]{Lo78} that to every relative central extension $(M, \mu)$ of $\nu$ with kernel $L$ one can associate a map of abelian groups $C \to L$.
-This map is obtained from the characteristic class $\xi(M, \mu)$ via the isomorphism $\HH^3(Q, N; L) \cong \mathrm{Hom}(C, L)$ of the universal coefficients theorem for cohomology (for this isomorphism we need the vanishing of $\HH_2(Q, N; \ZZ)$, which is a consequence of~\ref{req:uce}).
-
-In the special case $M = S(R, I)$ this construction produces a map $C \to C_{S}(R, I)$ whose naturality in $(R, I)$ follows from~\cite[Proposition~3]{Lo78}. 
-This map is an isomorphism by~\cite[Th{\'e}or{\`e}me~2]{Lo78}. \end{proof}
+Recall from the proof of~\cite[Th{\'e}or{\`e}me~2]{Lo78} that to every relative central extension $(M, \mu)$ of $\nu$ with kernel $L$ one can associate a homomorphism of abelian groups $C \to L$.
+This homomorphism is obtained from the characteristic class $\xi(M, \mu)$ via the isomorphism $\HH^3(Q, N; L) \cong \mathrm{Hom}(C, L)$ of the universal coefficients theorem for cohomology (for this isomorphism we need the vanishing of $\HH_2(Q, N; \ZZ)$, which is a consequence of~\ref{req:uce}).
+
+In the special case $M = S(R, I)$ this construction produces a homomorphism $C \to C_{S}(R, I)$ whose naturality in $(R, I)$ follows from~\cite[Proposition~3]{Lo78}. 
+This homomorphism is an isomorphism by~\cite[Th{\'e}or{\`e}me~2]{Lo78}. \end{proof}
 
@@
 Let $A$ be an arbitrary commutative local ring with maximal ideal $M$ and residue field $k$.
-Denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
+Denote by $B$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
 by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
@@
 Assume additionally that the residue field $k$ is of characteristic $\neq 2$.
-Then the canonical map $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
-\begin{proof}
-Writing the starting portion of the homology long exact sequence for the map $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
+Then the canonical homomorphism $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
+\begin{proof}
+Writing the starting portion of the homology long exact sequence for the homomorphism $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
 and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
@@
  \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-By~\cref{Panin-stability} the map $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
 By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
-but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the map $f'$ (and hence $f$) is surjective.
+but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the homomorphism $f'$ (and hence $f$) is surjective.
 \end{proof}
@@
 \begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$,
-Consider the following commutative square of canonical maps.
+Consider the following commutative square of canonical homomorphisms.
 \[ \xymatrix{
@@
     \St(\Phi, R, I) \ar[r] \ar@{-->}^t[ur] & \St(\Phi, R) } \]
-Then there exists a diagonal map $t$ which makes the diagram commute.   
+Then there exists a diagonal homomorphism $t$ which makes the diagram commute.   
 \end{lemma} 
@@
 
-\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
+\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical homomorphism $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
 \begin{proof}
@@
 
-We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the map $\St(\Phi, R) \to \St(\Phi, R/I)$.
+We denote by $\overline{\St}(\Phi, R, I)$ the kernel of the homomorphism $\St(\Phi, R) \to \St(\Phi, R/I)$.
 This group coincides with the image in $\St(\Phi, R)$ of the relative group $\St(\Phi, R, I)$ defined in~\cref{sec:quillen}.
@@
 \subsection{Generators of relative Steinberg groups}
-Denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
+Denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by all root subgroups $X_\alpha(I)$, $\alpha\in\Phi$.
 It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
@@
 
-It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the double commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups, the resulting assertion turns into a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).
+It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups, the resulting assertion turns into a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).
 
@@
  \item We denote by $R$ the Laurent polynomial ring $A[X, X^{-1}]$. We set $t = X^{-1}$, so that $R = A[X, X^{-1}] = A[t, t^{-1}]$.
- \item $B = B_{A, M}$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$.
+ \item $B$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$.
  \item $I$ denotes the ideal $M[X, X^{-1}]$ of $R$. Notice that $I$ is also an ideal of $B$.
@@
 \[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R)} \]
-Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. \end{df}
-Notice that the map $j_+^Mi_+^M$ is split by the homomorphism $ev^*_{X=a}$ of evaluation at $a\neq 0$, therefore $G_M^0$ can be considered as a subgroup of $\overline{G}^{\geq 0}_M$.
+Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
+Notice that the homomorphism $j_+^Mi_+^M$ is split by the homomorphism $ev^*_{X=1}$ of evaluation at $1$, therefore $G_M^0$ can be considered as a subgroup of $\overline{G}^{\geq 0}_M$.
 
@@
  Fix $v_0 = (g, h, u) \in V$.
-Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$ Notice that the map $i_+$ is split by $ev^*_{X=0}$.
+Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$ Notice that the homomorphism $i_+$ is split by $ev^*_{X=0}$.
  Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
@@
  By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
- From the last equality and the injectivity of the map $\GG(\Phi, A[X]) \to \GG(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $\GG(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
+ From the last equality and the injectivity of the homomorphism $\GG(\Phi, A[X]) \to \GG(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $\GG(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$.
 It follows from~\cref{thm:Stein} that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and hence by~\cref{Z-DS} it is contained in $Z_\alpha(A, M)$.
@@
 
-%Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
-%
 From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
@@
 \begin{multline*} p\left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ h',\ u (1 - am) \right) = \\ =
- x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha\left(\tfrac{m+\epsilon bm'}{1-am}\right). \end{multline*}
+ x_\beta(-b) \cdot S_\alpha(-a, p(g,h,u)) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc) \in P_\alpha\left(\tfrac{m-\epsilon bm'}{1-am}\right). \end{multline*}
 Thus, we can continue~\eqref{R2_0_1-computation} using~\eqref{T_1}--\eqref{T_leq0}:
@@
 \begin{enumerate}
- \item For any $h_1 \in \St(\Phi, A[X\inv])$ one has $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
+ \item For any $h_1 \in \St(\Phi, A[X\inv])$ one has $j_B^-(h_1) \cdot [1, h, u] = [1, h_1 h, u]$, where $j_B^-$ denotes the homomorphism $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$ (we identify $\overline{V}$ with $\overline{V}_T$ using the isomorphism~\eqref{eq:VVT}).
  \item If we consider $\St(\Phi, A[X, X\inv])$ as a set with the left multiplication action of $\St(\Phi, B)$ then the map $\overline{V} \to \St(\Phi, A[X, X\inv])$ given by $(g, [h], u) \mapsto g$ is a map of $\St(\Phi, B)$-sets.
@@
 For a pair $(R, I)$ denote by $\E(\Phi, R, I)$ the {\it relative elementary subgroup} of $\GG(\Phi, R)$, i.\,e.
-the image of the relative Steinberg group $\overline{\St}(\Phi, R, I)$ under the map $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$.
+the image of the relative Steinberg group $\overline{\St}(\Phi, R, I)$ under the homomorphism $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$.
 From the second property of the above proposition we immediately obtain the following group factorization.
@@
 \subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
-We retain the notation of the previous section and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective.
+We retain the notation of the previous section and assume additionally that the homomorphism $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective.
 This assumption allows us to consider the group $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
 Being considered in this way, $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
-This follows from a consideration of the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
+This follows from a consideration of the following commutative diagram, in which the homomorphism $t$ is obtained from~\cref{lem:lemma32}:
 \[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, I) \ar[r]^{t} & \St(\Phi, B) \ar[d]^{j_R} \\
@@
  Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
- Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
- Then the map $j_-$ is injective and the following commutative square is pullback
+ Suppose that the homomorphism $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
+ Then the homomorphism $j_-$ is injective and the following commutative square is pullback
  \begin{equation} \nonumber
@@
  By~\cref{prop43} one has $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
- Notice that $j_+i_+$ is split by the evaluation homomorphism $ev_{X=a}^*$, $a\neq 0$ and therefore is injective. Thus, we conclude that $g = 1$.
+ Notice that $j_+i_+$ is split by the evaluation homomorphism $ev_{X=1}^*$ and therefore is injective. Thus, we conclude that $g = 1$.
 
@@
  We denote by $\lambda_{M}$ (resp.
-$\lambda_{M, -}$) the localization map $A[X] \to A_M[X]$ (resp.
-$A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding maps of Steinberg groups.
+$\lambda_{M, -}$) the localization homomorphism $A[X] \to A_M[X]$ (resp.
+$A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding homomorphism of Steinberg groups.
  By the just established local case of the theorem the images $\lambda^*_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.

### 2020-04-14 dl-paper.tex
Minor change in formula

@@
  \begin{multline} \nonumber
- [h''] = \left[ h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
+ [h''] = \left[ h' \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1+\tfrac{a(m-\epsilon bm')}{1-am}}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
  = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].

### 2020-04-15 dl-paper.tex
Minor fix
Some further fixes

@@
 There is a well-defined homomorphism $\pi \colon \St(\Phi, R) \to \GG(\Phi, R)$ sending each generator $x_\alpha(\xi)$ to the elementary root unipotent $t_\alpha(\xi)$.
-The cokernel and the kernel of this homomorphism (denoted $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$, respectively) are, by definition, the values of the so-called $\mathrm{K}_1$ and $\mathrm{K_2}$-functors modeled on the Chevalley group $\GG(\Phi, -)$, see~\cite{St78}.
+The cokernel and the kernel of this homomorphism are denoted $\K_1(\Phi, R)$ and $\K_2(\Phi, R)$, respectively.
+The latter groups are functorial in $R$.
+The functors $\K_1(\Phi, -)$ and $\K_2(\Phi, -)$ are called {\it the $\mathrm{K}_1$ and $\mathrm{K_2}$-functors modeled on the Chevalley group $\GG(\Phi, -)$}, see~\cite{St78}.
 
@@
  \label{eq:H1ii-2}[x, yz] =& [x, y] \cdot {}^{y}\![x, z], \\
- [[x, y], z] =& \left([x^{-1}, [ y^{-1}, z]] ^ {y^{-1}} \cdot [y, [ z^{-1}, x^{-1}]] ^ {z^{-1}} \right)^{x^{-1}}. \label{HW-variant} \end{align}
+ [[x, y], z] =& {}^{x}\!\left({}^{y}[x^{-1}, [ y^{-1}, z]] \cdot {}^z[y, [ z^{-1}, x^{-1}]] \right). \label{HW-variant} \end{align}
 Recall also from~\cite[Lemma~3.1.1]{RS76} that
@@
 Denote by $B$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$ and
-by $I$ the ideal $M[X, X^{-1}]$ of $B$ (it is clear that $I$ is also an ideal of $R$).
+by $I$ the ideal $M[X, X^{-1}]$ of $R$ (it is clear that $I$ is also an ideal of $B$).
 
@@
 \begin{align*} \nonumber
-\begin{split}[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = \bigl([x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] ^ {x_{-\beta}(-t)} \cdot \hspace{50pt} \\ \cdot [x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] ^ {x_{\alpha}(-\xi)}\bigr)^{x_\beta(-s)} & \text{ by~\eqref{HW-variant}}\end{split} \\
-= x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} = x_{\alpha}(s t \xi) ^ {x_{-\beta}(-t) \cdot x_\beta(-s)} & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
+\begin{split}[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = {}^{x_\beta(s)}\!\bigl( {}^{x_{-\beta}(t)}[x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] \cdot \hspace{50pt} \\ \cdot {}^{x_{\alpha}(\xi)}[x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] \bigr)^{} & \text{ by~\eqref{HW-variant}}\end{split} \\
+= {}^{x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) = {}^{ x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(s t \xi) & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
 = x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
-The assertion~\ref{C3} is obvious. Finally, last assertion can be obtained as follows:
+The assertion~\ref{C3} is obvious. Finally, the last assertion can be obtained as follows:
 \begin{align*}
@@
 \begin{split}
-    =\bigl( [[x_{\alpha+\beta}(-s),\ x_{-\alpha}(\epsilon t)],\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot \hspace{70pt} \\
-        \cdot [[ x_{-\beta}(-\xi),\ x_{\alpha+\beta}(s)],\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)}\bigr)^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{HW-variant}}
+    ={}^{x_{-\alpha}(-\epsilon t)}\!\bigl( {}^{x_{\alpha+\beta}(s)}[[x_{\alpha+\beta}(-s),\ x_{-\alpha}(\epsilon t)],\ x_{-\beta}(\xi)]  \cdot \hspace{70pt} \\
+        \cdot {}^{x_{-\beta}(\xi)}[[ x_{-\beta}(-\xi),\ x_{\alpha+\beta}(s)],\ x_{-\alpha}(\epsilon t)]\bigr) &\ \text{by~\eqref{HW-variant}}
 \end{split}\\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t)]^{x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1}}\\
-= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)]^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
+= \left({}^{x_{\alpha+\beta}(s)}[x_{\beta}(st),\ x_{-\beta}(\xi)] \cdot {}^{x_{-\beta}(\xi)}[x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t)]\right)^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1}}\\
+= \left({}^ {x_{\alpha+\beta}(s)}[x_{\beta}(st),\ x_{-\beta}(\xi)] \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha}(\epsilon t) \cdot x_{-\alpha-\beta}(t\xi)]\right)^{x_{-\alpha}(\epsilon t)} &\ \text{by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
 = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot [x_{-\alpha}(-\epsilon t),\ x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi),\ x_{-\alpha-\beta}(t\xi)] &\ \text{by~\eqref{rel43}}\\
@@
  \item $B$ denotes the subring $A[t] + M[t^{-1}] = A[X^{-1}] + M[X]$ of $R$.
- \item $I$ denotes the ideal $M[X, X^{-1}]$ of $R$. Notice that $I$ is also an ideal of $B$.
+ \item $I$ denotes the ideal $M[X, X^{-1}]$ of $R$ (it is clear that $I$ is also an ideal of $B$).
  \end{itemize}
@@
 $\lambda_{M, -}$) the localization homomorphism $A[X] \to A_M[X]$ (resp.
-$A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding homomorphism of Steinberg groups.
+$A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding homomorphisms of Steinberg groups.
  By the just established local case of the theorem the images $\lambda^*_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.

### 2020-04-15 dl-paper.tex
Minor fix

@@
 
-Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ is different from $\K_2(\rD_n, R) = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))$.
-The relationship between these groups is illustrated by the exact sequence
+Now set $\widetilde{G}_n = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $\widetilde{P}_n = \mathrm{E}(\rD_n, -) = \mathrm{Epin}(2n, -)$.
+Notice that for $n\geq 3$ the groups
+\begin{align*}
+   \KO_2(2n, R) &= \K_2^{G_n,P_n} = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R)), \\
+ \K_2(\rD_n, R) &= \K_2^{\widetilde{G}_n,\widetilde{P}_n} = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))
+\end{align*}
+are related via the exact sequence
 \[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
-which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} by means of the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
-On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.
+which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} using the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
+On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong K_3^{\widetilde{G}_n, \widetilde{P}_n}$.
 

### 2020-04-16 dl-paper.tex
Fix 32

@@
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
-Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving injectivity of the following two homomorphisms:
-\[ \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\]
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving the injectivity of the following two homomorphisms:
+\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\end{equation*}
 The injectivity of the second homomorphism is obtained in~\cref{thm41}.
@@
 Consider the following commutative square of canonical homomorphisms.
-\[ \xymatrix{
+\begin{equation*} \xymatrix{
     \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}^t[ur] & \St(\Phi, R) } \]
+    \St(\Phi, R, I) \ar[r] \ar@{-->}^t[ur] & \St(\Phi, R) } \end{equation*}
 Then there exists a diagonal homomorphism $t$ which makes the diagram commute.   
@@
 Denote by $\overline{V}_T$ the quotient of the set of triples 
-\[V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times\] by the equivalence relation given by $(p \cdot j_+i_+(\gamma), h, u)_T \sim (p, i_-(\gamma) \cdot h, u)_T$, $\gamma \in G^0_M$.
+\begin{equation}\label{VT-def} V_T = \overline{G}_M^{\geq 0} \times \St(\Phi, A[X\inv]) \times (1+M)^\times \end{equation} by the equivalence relation given by $(p \cdot j_+i_+(\gamma), h, u)_T \sim (p, i_-(\gamma) \cdot h, u)_T$, $\gamma \in G^0_M$.
 We denote the image of $(p, h, u)_T$ in $\overline{V}_T$ by $[p, h, u]$.
@@
 \subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
-We retain the notation of the previous section and assume additionally that the homomorphism $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective.
-This assumption allows us to consider the group $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
-Being considered in this way, $\St(\Phi, B)$ contains the subgroup $\overline{G}^{\geq 0}_M$ of $\St(\Phi, R)$.
-This follows from a consideration of the following commutative diagram, in which the homomorphism $t$ is obtained from~\cref{lem:lemma32}:
-\[ \xymatrix{ \St(\Phi, A[X], M[X]) \ar[d] \ar[r] & \St(\Phi, R, I) \ar[r]^{t} & \St(\Phi, B) \ar[d]^{j_R} \\
-   \St(\Phi, A[X]) \ar[rr]^{j_+} & & \St(\Phi, R). } \]
+Before we proceed with the proof of~\cref{thm:main} let us briefly remind the reader the relevant notation.
+Recall that $A$ is a local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both $R=A[X, X\inv]$ and $B = A[X\inv] + M[X]$.
+
+Consider the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
+\begin{equation} \label{big-picture}
+ \xymatrix{ & \St(\Phi, A[X], M[X]) \ar[r]_(0.55){\mu_{A[X]}} \ar[d] & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ & \St(\Phi, R, I) \ar[d]^t & \\ \St(\Phi, A[X\inv]) \ar[r]^{j_B^-} & \St(\Phi, B) \ar[r]^{j_R} & \St(\Phi, R).
+} \end{equation}
+Notice that the subgroup $\overline{G}_M^{\geq 0}$ (see~\cref{df:GM0_geq0}) coincides with the image of $j_+\mu_{A[X]}$.
+
+Our goal is to prove that the homomorphism $j_B^-$ is injective. 
+In order to be able to do this we need to show that $\St(\Phi, B)$ acts transitively on the first components of the triples from $\overline{V}_T$.
+These first components are parametrized by cosets $\overline{G}_M^{\geq 0}/G_M^0$ (cf.~\eqref{VT-def}).
+It is clear from~\eqref{big-picture} that $\overline{G}_M^{\geq 0}$ lies in the image of $j_R$.
+To simplify notation we want to consider $\overline{G}_M^{\geq 0}$ as a subgroup of $\St(\Phi, B)$.
+Thus, throughout this section we additionally assume that $j_R$ is injective.
+This assumption is innocent, since we already know from~\cref{thm41} that $j_R$ is injective under the assumptions of~\cref{thm:main}.
 
@@
 
-\begin{rem}
-Although we will not need this for our main result, it can be noted that $\overline{V}$ is a left $\St(\Phi, B)$-torsor, i.\,e.
+\begin{rem} Although we will not need this for our main result, it can be noted that $\overline{V}$ is a left $\St(\Phi, B)$-torsor, i.\,e.
 the action of $\St(\Phi, B)$ on $\overline{V}$ is both transitive and faithful.
@@
 
-\begin{externaltheorem} \label{thm:P1glueing}
+\begin{theorem} \label{thm:P1glueing}
  Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
- Suppose that the homomorphism $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
+ Assume additionally that the homomorphism $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
  Then the homomorphism $j_-$ is injective and the following commutative square is pullback
@@
  \end{equation}
-\end{externaltheorem}
+\end{theorem}
 \begin{proof} Since $j_- = j_R j_B^-$, where $j_B^-$ is as in~\cref{prop43}, it suffices to show that $j_B^-$ is injective.

### 2020-04-16 dl-paper.tex
Fix misprints

@@
 which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} using the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
-On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong K_3^{\widetilde{G}_n, \widetilde{P}_n}$.
+On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.
 
@@
  x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
-  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
+  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{(m -\epsilon bm')X}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}).
+\qedhere
 \end{multline}

### 2020-04-16 dl-paper.tex
Minor fix

@@
 Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$.
-%The second assertion of the lemma can be verified directly using~\eqref{eq:symbol-properties}. 
-\end{proof}
-
+\end{proof}
+\begin{comment}
+\begin{corollary}\label{cor:additivity} For $a, b \in A$ and $g \in P_\alpha(m)$ one has
+ \[S_\alpha(a + b, g) = S_\alpha\left(b, S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am)\right) \cdot h_\alpha(1+am).\]
+\end{corollary}
+\begin{proof}
+The assertion immediately follows from the above corollary:
+ \begin{align*}
+  S_\alpha\left(b, S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am)\right) \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:S-def}} \\
+  = x_\alpha(bX^{-1}) \cdot S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \cdot \{X, 1+\tfrac{bm}{1+am}\} \cdot h_\alpha(1+am)&\text{ by~\eqref{eq:conj-h-x}} \\
+  = x_\alpha(bX^{-1}) \cdot S_\alpha(a, g) \cdot x_\alpha\left(\tfrac{-bX^{-1}}{(1+am)(1+am+bm)}\right) \cdot \left\{X, 1+\tfrac{bm}{1+am} \right\}&\text{ by~\eqref{eq:S-def}}\\
+  = x_\alpha((a+b)X^{-1}) \cdot h \cdot x_\alpha\left(- \tfrac{aX^{-1}(1+am+bm) + bX^{-1}}{(1+am)(1+am+bm)} \right) \cdot \{ X, 1+(a+b)m \} = S_\alpha(a+b, g) &\text{ by~\eqref{eq:S-def}.} \end{align*}
+\end{proof}
+\end{comment}
 \begin{lemma} \label{SR:sharp} For $g \in j_+(K(A[X], M[X])) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right).
@@
 \end{proof}
+\begin{comment}
+In the sequel it will be convenient to have explicit formulas for the action of operators $T_\alpha(aX^{-1})$ and $T_\alpha(a + Xf)$ on $\overline{V}_T$.
+These formulas are the analogues of~\eqref{T_1}--\eqref{T_leq0} and are easily obtained from them using~\eqref{eq:VVT}.
+\begin{align}\label{T_1-VT}
+ T_\alpha(aX^{-1}) \cdot [p, h, u] &= [ S_\alpha(a, p),\ x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot h,\ u(1+am)],\text{ where }p\in P_\alpha(m); \\
+ T_\alpha(a + Xf) \cdot [p, h, u] &= [x_\alpha(a + Xf) \cdot p \cdot x_\alpha(-a),\ x_\alpha(a) \cdot h, u]. \label{T_leq0-VT}
+\end{align}
+\end{comment}
 
@@
 
-First of all, notice that the base case $\xi = a \in A$ can be verified by direct computation involving~\eqref{eq:VVT} and~\eqref{T_leq0}.
-Using~\cref{lem:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
-
+Notice that the assertion in the base case $\xi = a \in A$ is an immediate consequence of of~\eqref{T_leq0}.
+Since $x_\beta(X^2f) \in P_\alpha(0)$, an argument similar to the proof of~\cref{R1_d} shows that the assertion of the lemma also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
+
+Now let us verify the induction step.
 Suppose that the assertion holds for all $p_1 = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.

### 2020-04-16 dl-paper.tex
Fix 6 of 3.1

@@
 In the above statement $\KO_2(2\ell, -)$ denotes the unstable orthogonal $\K_2$-functor (see~\cref{sec:quillen}).
-Notice also that in the special case when $A=k$ is a field the assertion of the above theorem follows from the results of U.~Rehmann, J.~Hurrelbrink and J.~Morita (see~\cref{field-injectivity} below).
+Notice also that in the special case when $A=k$ is a field the assertion of the above theorem is a consequence of the results of U.~Rehmann and J.~Hurrelbrink (see~\cref{field-injectivity} below).
 
 The proof of~\cref{thm:main} goes as follows. We notice that it suffices to prove the $\St(\rD_\ell, -)$-variant of the theorem. Moreover, the proof of the injectivity of
-$j_+ \colon \St(\rD_\ell, A[X]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part.
+$j_- \colon \St(\rD_\ell, A[X\inv]) \to \St(\rD_\ell, A[X, X\inv])$ turns out to be the hardest part.
 After invoking the local-global principle~\cite[Theorem~2]{LS17} the proof reduces to the special case when $A$ is local.
-Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_+$ comes down to proving the injectivity of the following two homomorphisms:
-\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r] & \St(\rD_\ell, A[X\inv] + M[X]) \ar[r] & \St(\rD_\ell, A[X, X\inv]). }\end{equation*}
-The injectivity of the second homomorphism is obtained in~\cref{thm41}.
-This is the only place in our proof which invokes the assumption that $2$ is invertible.
-The proof of~\cref{thm41} depends on the stability theorem for higher orthogonal K-groups and also on certain basic calculations with Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
-Finally, the injectivity of the first homomorphism is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
+Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_-$ comes down to proving the injectivity of the following two homomorphisms:
+\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r]{j_B^-} & \St(\rD_\ell, B) \ar[r]{j_R} & \St(\rD_\ell, R), }\end{equation*}
+where $B = A[X\inv] + M[X]$ and $R = A[X, X\inv]$.
+The injectivity of $j_R$ is obtained in~\cref{thm41}.
+This step of the proof relies on the theory of relative Steinberg groups developed by J.-L.~Loday in~\cite{Lo78}.
+According to it the relative Steinberg group $\St(\Phi, R, I)$ is not the kernel of $\St(\Phi, R) \to \St(\Phi, R/I)$ but rather a central extension of it by a certain subgroup, which we denote $C(\Phi, R, I)$.
+It turns out that a simple diagram chasing argument combined with a certain lifting property of relative Steinberg groups (see~\cref{lem:lemma32}) reduces the sought injectivity of $j_R$ to the surjectivity of the map \[C(\rD_\ell, B, M[X, X\inv]) \to C(\rD_\ell, R, M[X, X\inv]).\] This surjectivity is then obtained as a corollary of Panin's stability theorem for orthogonal K-theory and the Bass Fundamental Theorem for higher Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
+This is the only step of our proof which invokes the assumption that $2$ is invertible.
+
+Finally, the injectivity of the homomorphism $j_B^-$ is obtained in~\cref{thm:P1glueing}, which is a direct generalization of~\cite[Proposition~4.3]{Tu83}.
 This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ containing a subsystem of type $\rA_4$.
-%$\rD_\ell$, $\ell=5,6$ and also $\rE_\ell$, $\ell=6,7,8$.
-
+The main idea of the proof of~\cref{thm:P1glueing} is to express the underlying set of $\St(\Phi, A[X\inv] + M[X])$ as an explicit quotient of the Cartesian product of three other groups, one of which is precisely $\St(\Phi, A[X\inv])$ (see~\eqref{VT-def}).
+This can be considered as some sort of a decomposition for $\St(\Phi, A[X\inv] + M[X])$.
+This technique for working with Steinberg groups probably dates back to~\cite{ST76}.
+The proof of~\cref{thm:P1glueing} requires a certain amount of preparatory work.
+One of the neccessary ingredients in it is~\cref{lemma33}, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
 \subsection{Acknowledgements} 
@@
 
-Notice that the assertion in the base case $\xi = a \in A$ is an immediate consequence of of~\eqref{T_leq0}.
+Notice that in the base case $\xi = a \in A$ the assertion of the lemma is an immediate consequence of of~\eqref{T_leq0}.
 Since $x_\beta(X^2f) \in P_\alpha(0)$, an argument similar to the proof of~\cref{R1_d} shows that the assertion of the lemma also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
@@
 \end{multline*}
-From the first part of the proof and inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds for $p_1 = z_\alpha(f, X\xi)$.
+From the inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds for $p_1 = z_\alpha(f, X\xi)$.
 It is easy to deduce from this that the assertion also holds for $p_1 = z_\alpha(f, X\xi + a) = x_\alpha(-a) \cdot z_\alpha(f, X\xi) \cdot x_\alpha(a)$.
@@
 
- Now let $A$ be arbitrary commutative ring and $\Phi = \rD_\ell$, $\ell \geq 7$.
+ Now let $A$ be an arbitrary commutative ring and $\Phi = \rD_\ell$, $\ell \geq 7$.
 If $g \in \St(\Phi, A[X])$ is such that its image in $\St(\Phi, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\Phi, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.

### 2020-04-16 dl-paper.tex
Minor fix

@@
 Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_-$ comes down to proving the injectivity of the following two homomorphisms:
-\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r]{j_B^-} & \St(\rD_\ell, B) \ar[r]{j_R} & \St(\rD_\ell, R), }\end{equation*}
+\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r]^(0.55){j_B^-} & \St(\rD_\ell, B) \ar[r]^{j_R} & \St(\rD_\ell, R), }\end{equation*}
 where $B = A[X\inv] + M[X]$ and $R = A[X, X\inv]$.
@@
 This part of the proof is obtained in somewhat greater generality and is applicable to all simply-laced root systems $\Phi$ containing a subsystem of type $\rA_4$.
-The main idea of the proof of~\cref{thm:P1glueing} is to express the underlying set of $\St(\Phi, A[X\inv] + M[X])$ as an explicit quotient of the Cartesian product of three other groups, one of which is precisely $\St(\Phi, A[X\inv])$ (see~\eqref{VT-def}).
-This can be considered as some sort of a decomposition for $\St(\Phi, A[X\inv] + M[X])$.
-This technique for working with Steinberg groups probably dates back to~\cite{ST76}.
+The main idea of the proof of~\cref{thm:P1glueing} is to express the underlying set of $\St(\Phi, B)$ as an explicit quotient of the Cartesian product of three other groups, one of which is precisely $\St(\Phi, A[X\inv])$, see~\eqref{VT-def}.
+This can be considered as some sort of a decomposition for $\St(\Phi, B)$.
+Such technique for working with Steinberg groups probably dates back to~\cite{ST76}.
 The proof of~\cref{thm:P1glueing} requires a certain amount of preparatory work.
-One of the neccessary ingredients in it is~\cref{lemma33}, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
+One of the necessary ingredients used is~\cref{lemma33}, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
 \subsection{Acknowledgements} 
@@
 Recall that the category of (commutative) pairs $\catname{Pairs}$ is defined as follows.
-Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with $1$ and $I$ is a (not neccessarily proper) ideal of $R$.
+Its objects are pairs $(R, I)$, in which $R$ is a commutative ring with $1$ and $I$ is a (not necessarily proper) ideal of $R$.
 A morphism of pairs $f \colon (R, I) \to (R', I')$ is, by definition, a (unit-preserving) ring homomorphism $f \colon R \to R'$ such that $f(I) \subseteq I'$.
@@
 First of all, recall the following two results which give two different generating sets for the group $\overline{\St}(\Phi, R, I)$ (notice that both results apply to general irreducible $\Phi$ of rank $\geq 2$, i.\,e.
-not neccessarily simply-laced ones).
+not necessarily simply-laced ones).
 \begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.

### 2020-04-18 dl-paper.tex
Minor fix

@@
 The proof of~\cref{thm:P1glueing} requires a certain amount of preparatory work.
-One of the necessary ingredients used is~\cref{lemma33}, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
+One of the necessary ingredients is a certain presentation theorem for Steinberg groups similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev, see~\cref{lemma33} (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
 \subsection{Acknowledgements} 

### 2020-04-18 dl-paper.tex
Fix vagueness of statements

@@
  \item \label{req:coeq} For every pair $(R, I)$ the coequalizer of $S(p_0), S(p_1)$ is precisely $S(R) \to S(R/I)$.
- \item \label{req:subfunc} $P(R)$ is a perfect normal subgroup of $G(R)$.
- \item \label{req:uce} The homomorphism $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $\HH_1(S(R), \ZZ) = \HH_2(S(R), \ZZ) = 0$.
+ \item \label{req:subfunc} $P(R)$ is a normal subgroup of $G(R)$.
+ \item \label{req:uce} The homomorphism $ \pi_R \colon S(R) \to P(R)$ is a universal central extension for all $R$. In particular, $S(R)$ and $P(R)$ are perfect and $\HH_2(S(R), \ZZ) = 0$.
 \end{enumerate}
@@
  \item $\K_3^{G,P}(R) \cong \HH_3(S(R), \ZZ).$ \end{enumerate} \end{lemma}
-\begin{proof} The first claim is obvious, the other ones follow from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
+\begin{proof} The first claim is obvious, the other claims follow from~\ref{req:subfunc} and~\ref{req:uce} using the standard properties of the plus-construction, see \cite[\S~IV.1]{Kbook}   (cf.
 Exercises~1.8--1.9 ibid.) \end{proof}
 
-Now let us give an example of the triple $(G, P, S)$ playing a key role in the present paper.
-We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively
- (see e.\,g.~\cite{Su82} for the definition of these groups).
-Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_n, -)$ and let $\pi$ be the obvious projection $S_n \to P_n$.
-
-It is easy to see that the functors $G_n$, $P_n$ and $S_n$ satisfy \ref{req:left-exact} and \ref{req:coeq}.
-By~\cite{Su82} the requirement~\ref{req:subfunc} is also satisfied for $n \geq 3$.
-Finally, from~\cite[Corollary~5.4]{St71} and~\cite[Theorem~1]{LS17} it follows that $S_n$ and $P_n$ satisfy~\ref{req:uce} for $n \geq 5$.
-We use the notation $\KO_i(2n, R)$ as a shorthand for $\K_i^{G_n, P_n}(R)$.
-
-Now set $\widetilde{G}_n = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $\widetilde{P}_n = \mathrm{E}(\rD_n, -) = \mathrm{Epin}(2n, -)$.
-Notice that for $n\geq 3$ the groups
-\begin{align*}
-   \KO_2(2n, R) &= \K_2^{G_n,P_n} = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R)), \\
- \K_2(\rD_n, R) &= \K_2^{\widetilde{G}_n,\widetilde{P}_n} = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))
-\end{align*}
-are related via the exact sequence
+We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively (see e.\,g.~\cite{Su82} for the definition of these groups).
+Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_\ell, R)$.
+The triple $(G_n, P_n, S_n)$ plays a key role in the present paper.
+
+We need to introduce more notation. Denote by $\widetilde{G}_n$ the Chevalley group $\GG(\rD_n, -) = \mathrm{Spin}(2n, -)$
+ and by $\widetilde{P}_n$ its elementary subfunctor $\mathrm{E}(\rD_n, -) = \mathrm{Epin}(2n, -)$.
+
+It is clear that both $G_n$ and $\widetilde{G}_n$ satisfy~\ref{req:left-exact} and that $S_n$ satisfies \ref{req:coeq}.
+It is well known that $P_n$ (resp.
+$\widetilde{P}_n$) is a normal subgroup of $G_n$ (resp.
+$\widetilde{G}_n$) for $n\geq 3$ (see~\cite{Su82},\cite{Ta84}).
+Thus,~\ref{req:subfunc} is satisfied for $P_n$ and $\widetilde{P}_n$.
+
+By~\cite[Corollary~5.4]{St71} the group $S_n$ is {\it centrally closed} for $n \geq 5$, i.\,e. every its central extension splits.
+On the other hand, \cite[Theorem~1]{LS17} shows that $\K_2(\rD_\ell, R) = \Ker(S_n \to \widetilde{G}_n)$ is a central subgroup of $S_n$ for $n\geq 4$.
+
+Recall from p.~189 of~\cite{Ba74} that there is an exact sequence
+\begin{equation} \label{eq:Bass-ES} \xymatrix{1 \ar[r] & \mu_2(R) \ar[r] & \widetilde{P}_n(R) \ar[r] & P_n(R) \ar[r] & 1,}
+\end{equation}
+in which the group $\mu_2(R) = \{ a \in R^\times \mid a^2 = 1 \}$ is a central subgroup of $\widetilde{P}_n(R)$.
+Now by~\cite[\S~7(v)]{Ste67} the group $\KO_2(2n, R) = \Ker(S_n \to G_n)$ is also central in $S_n$.
+Thus, we see that $S_n$ is a universal central extension of both $P_n$ and $\widetilde{P}_n$ for $n\geq 5$.
+
+We have checked that both triples $(G_n, P_n, S_n)$ and $(\widetilde{G}_n, \widetilde{P}_n, S_n)$ satisfy the requirements~\ref{req:left-exact}--\ref{req:uce} for $n \geq 5$.
+In the sequel we use the notation $\KO_i(2n, R)$ as a shorthand for $\K_i^{G_n, P_n}(R)$.
+
+Notice that for $n\geq 3$ the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
 \[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
-which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} using the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
+which follows from~\eqref{eq:Bass-ES} via the snake lemma  (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.

### 2020-04-18 dl-paper.tex
Minor fix

@@
 
-Recall from p.~189 of~\cite{Ba74} that there is an exact sequence
+Recall from p.~189 of~\cite{Ba74} that for $n\geq 3$ there is an exact sequence
 \begin{equation} \label{eq:Bass-ES} \xymatrix{1 \ar[r] & \mu_2(R) \ar[r] & \widetilde{P}_n(R) \ar[r] & P_n(R) \ar[r] & 1,}
@@
 
-Notice that for $n\geq 3$ the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
+Notice that the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
 \[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
-which follows from~\eqref{eq:Bass-ES} via the snake lemma  (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
+which is obtained from~\eqref{eq:Bass-ES} and the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.

### 2020-04-26 dl-paper.tex
Fixed some of Andrei's comments

@@
 \usepackage{enumitem}
-\usepackage[notref,notcite]{showkeys}
 
@@
 
-In~\cite{LS17} the authors have shown that the Steinberg groups $\St(\Phi, R)$ satisfy the Quillen--Suslin local-global principle provided $\Phi$ is simply-laced and has rank $\geq 3$.
-This result is one of the ingredients needed in the proof of the $\K_2$-analogue of the Serre problem for Chevalley groups.
+In~\cite{LS17,La18} the authors have shown that the Steinberg groups $\St(\Phi, R)$ satisfy the Quillen--Suslin local-global principle provided $\Phi$ has rank $\geq 3$ and is either simply-laced or has type $\rC_\ell$.
+The local-global principle is one of the ingredients needed in the proof of the $\K_2$-analogue of the Serre problem for Chevalley groups.
 The aim of the present article is to make yet another step towards the solution of the problem, namely to prove an analogue of Horrocks theorem~\cite{Ho64} for Steinberg groups of type $\rD_\ell$.
@@
 The injectivity of $j_R$ is obtained in~\cref{thm41}.
-This step of the proof relies on the theory of relative Steinberg groups developed by J.-L.~Loday in~\cite{Lo78}.
-According to it the relative Steinberg group $\St(\Phi, R, I)$ is not the kernel of $\St(\Phi, R) \to \St(\Phi, R/I)$ but rather a central extension of it by a certain subgroup, which we denote $C(\Phi, R, I)$.
+This step of the proof relies on the theory of relative central extensions developed by J.-L.~Loday in~\cite{Lo78}.
+According to this theory, the relative Steinberg group $\St(\Phi, R, I)$ is a central extension of $\Ker(\St(\Phi, R) \to \St(\Phi, R/I))$ by a certain subgroup, which we denote $C(\Phi, R, I)$.
 It turns out that a simple diagram chasing argument combined with a certain lifting property of relative Steinberg groups (see~\cref{lem:lemma32}) reduces the sought injectivity of $j_R$ to the surjectivity of the map \[C(\rD_\ell, B, M[X, X\inv]) \to C(\rD_\ell, R, M[X, X\inv]).\] This surjectivity is then obtained as a corollary of Panin's stability theorem for orthogonal K-theory and the Bass Fundamental Theorem for higher Grothendieck--Witt groups (these groups include the stable orthogonal K-groups as a special case, see~\eqref{GW-concrete}).
@@
 The proof of~\cref{thm:P1glueing} requires a certain amount of preparatory work.
-One of the necessary ingredients is a certain presentation theorem for Steinberg groups similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev, see~\cref{lemma33} (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
+One of the necessary ingredients is a certain presentation theorem for Steinberg groups over graded rings, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev, see~\cref{lemma33} (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
 \subsection{Acknowledgements} 
-The work of the first-named author (\S~3) was supported by the Russian Science Foundation grant No 17-11-01261.
+The work of the first-named author (\S~3) was supported by the Russian Science Foundation grant No 17-11-01261. The first-named author is a winner of the contest ``Young Russian Mathematics``.
 The work of the second-named author (\S~4--5) was supported by RFBR grant No 18-31-20044.
 
-The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.
+The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work, and to the anonymous referee for his careful reading of an earlier version of the paper and suggesting a number of improvements.
 
@@
 
-\begin{rem} It is possible to directly prove the stable symplectic counterpart of the above lemma (under the additional assumption that the characteristic of $k$ is not $2$).
+\begin{rem} It is possible to give a different proof of the above lemma in the case $\Phi = \rC_\ell$ for $\ell \geq 5$ under the additional assumption that the characteristic of $k$ is not $2$.
 Indeed, we have the following chain of isomorphisms:
@@
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
-Thus, we see that in the stable range the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups. \end{rem}
+It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the nonstable case.
+Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups.
+\end{rem}
 
@@
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
-We will need only the special case $k=0$ of the above theorem, in which case it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
+We will need only the special case $k=0$ of the above theorem, in which it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
 
@@
 \item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
-\item If $\alpha+\beta\in\Phi$ then
-\begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
-  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta),\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
+\item\label{Z5} If $\alpha+\beta\in\Phi$ then
+\begin{multline*} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
+  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta),\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline*}
 \end{enumerate} \end{lemma}
@@
 It is not hard to show that for any parabolic subset $S \subseteq \Phi$ the subset $\Sigma_S$ has the property that $d^n(\Sigma_S) = \Phi$ for some $n>1$ (in fact, $n=2$).
-It remains to see that relation~\ref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
+It remains to see that \cref{Zrels}\ref{Z5} immediately implies that every group $G$ containing $\mathcal{Z}(U, R, I)$ also contains $\mathcal{Z}(dU, R, I)$.
 \end{rem}
@@
 \end{align*}
-
 \end{proof}
@@
 Finally, let $g = x_\alpha(f)$ be a generator of type P5.
-Substituting in~\ref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\ref{Z5} through other terms we obtain that
+Substituting $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ into the identity of~\cref{Zrels}\ref{Z5} and expressing the fifth factor in the right-hand side of it through other terms we obtain that
 \begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
@@
 $\alpha-\delta \in \Phi$.
-Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\ref{Z5} we obtain that
+Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$, $\beta = -\delta$ into~\cref{Zrels}\ref{Z5} we obtain that
 \begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
@@
 Suppose that the assertion holds for all $p_1 = z_\alpha(f, \xi)$ for which $\xi$ has degree $\leq n$.
-Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ into~\ref{Z5} we obtain the following equality in $\St(\Phi, B)$:
+Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ into~\cref{Zrels}\ref{Z5} we obtain the following equality in $\St(\Phi, B)$:
 \begin{multline*}

### 2020-04-27 dl-paper.tex
Better abstract

@@
 \begin{document}
-\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups.
-This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue for the functor $\K_2$ of a 1982 result of A.~Suslin and V.~Kopeiko.
+
+\begin{abstract} 
+We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal $\K_2$-functor.
+This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also one of the ingredients needed for the proof of the orthogonal $\K_2$-analogue of Serre's problem.
+The final result holds for general commutative rings containing $\tfrac{1}{2}$, however some of the intermediate steps in its proof are obtained without this assumption.
 \end{abstract}
@@
 After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see e.\,g.~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}).
-For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem.
+For example, A.~Suslin formulated and solved the so-called $\K_1$-analogue of Serre's problem.
 This result asserts that the functor $\K_1(n, R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_1(n, k[x_1, \ldots x_n]) = \K_1(n, k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}.
@@
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
-It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the nonstable case.
+It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case.
 Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups.
@@
 $\widetilde{P}_n$) is a normal subgroup of $G_n$ (resp.
-$\widetilde{G}_n$) for $n\geq 3$ (see~\cite{Su82},\cite{Ta84}).
+$\widetilde{G}_n$) for $n\geq 3$ (see~\cite{Su82},\cite{Ta86}).
 Thus,~\ref{req:subfunc} is satisfied for $P_n$ and $\widetilde{P}_n$.
@@
 \begin{equation*} \xymatrix{
-    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r] \ar@{-->}^t[ur] & \St(\Phi, R) } \end{equation*}
+    \St(\Phi, B, I) \ar[r]^{\mu_B} \ar[d] & \St(\Phi, B) \ar[d] \\
+    \St(\Phi, R, I) \ar[r]^{\mu_R} \ar@{-->}^t[ur] & \St(\Phi, R) } \end{equation*}
 Then there exists a diagonal homomorphism $t$ which makes the diagram commute.   
@@
 \subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
-Before we proceed with the proof of~\cref{thm:main} let us briefly remind the reader the relevant notation.
+Before we proceed with the proof of~\cref{thm:main} let us recall the relevant notation.
 Recall that $A$ is a local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both $R=A[X, X\inv]$ and $B = A[X\inv] + M[X]$.

### 2020-04-27 dl-paper.tex
Minor fix

@@
 
-\begin{abstract} 
-We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal $\K_2$-functor.
-This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also one of the ingredients needed for the proof of the orthogonal $\K_2$-analogue of Serre's problem.
-The final result holds for general commutative rings containing $\tfrac{1}{2}$, however some of the intermediate steps in its proof are obtained without this assumption.
-\end{abstract}
+\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal Steinberg groups.
+$\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
+ positive solution of which currently is only known in the case of linear Steinberg groups. \end{abstract}
 \maketitle

### 2020-04-27 dl-paper.tex
Minor fix

@@
 
-\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal Steinberg groups.
-$\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
- positive solution of which currently is only known in the case of linear Steinberg groups. \end{abstract}
+\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem (also called Horrocks theorem) for the unstable even-dimensional orthogonal Steinberg groups.
+Horrocks theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
+ positive solution of which currently is only known in the linear case. \end{abstract}
 \maketitle
@@
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
-It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case.
-Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups.
-\end{rem}
+It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. \end{rem}
 

### 2020-04-27 dl-paper.tex
Fixed even more issues

@@
 
-\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem (also called Horrocks theorem) for the unstable even-dimensional orthogonal Steinberg groups.
-Horrocks theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
- positive solution of which currently is only known in the linear case. \end{abstract}
+\begin{abstract} We prove the $\mathbb{P}^1$-glueing theorem (aka Horrocks theorem) for the unstable even-dimensional orthogonal Steinberg groups.
+The $\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the principal ingredients needed in the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
+\end{abstract}
 \maketitle
@@
 \begin{df} By definition, the {\it relative Steinberg group} $\St(\Phi, R, I)$ is the result of application of Loday's relativization to the functor $\St(\Phi, -)$.
-Notice that $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ but a central extension of a subgroup of $\St(\Phi, R)$ by the abelian group $C_{\St(\Phi, -)}(R, I)$.
+Notice that $\St(\Phi, R, I)$ is a central extension of $\Ker(\St(\Phi, R) \to \St(\Phi, R/I))$ by the abelian group $C_{\St(\Phi, -)}(R, I)$.
 For shortness we rename the latter group to $C(\Phi, R, I)$.
@@
 We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively (see e.\,g.~\cite{Su82} for the definition of these groups).
-Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_\ell, R)$.
+Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(-)$, $S_n = \St(\rD_\ell, -)$.
 The triple $(G_n, P_n, S_n)$ plays a key role in the present paper.
@@
 
-By~\cite[Corollary~5.4]{St71} the group $S_n$ is {\it centrally closed} for $n \geq 5$, i.\,e. every its central extension splits.
+By~\cite[Corollary~5.4]{St71} the group $S_n$ is {\it centrally closed} for $n \geq 5$, in other words every central extension of $S_n$ splits.
 On the other hand, \cite[Theorem~1]{LS17} shows that $\K_2(\rD_\ell, R) = \Ker(S_n \to \widetilde{G}_n)$ is a central subgroup of $S_n$ for $n\geq 4$.
@@
 \subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
-Before we proceed with the proof of~\cref{thm:main} let us recall the relevant notation.
-Recall that $A$ is a local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both $R=A[X, X\inv]$ and $B = A[X\inv] + M[X]$.
+Before we proceed with the proof of~\cref{thm:P1glueing} let us briefly recall the relevant notation.
+As before, $A$ denotes an arbitary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
 
@@
 
-Our goal is to prove that the homomorphism $j_B^-$ is injective. 
-In order to be able to do this we need to show that $\St(\Phi, B)$ acts transitively on the first components of the triples from $\overline{V}_T$.
+Our main goal is to prove that the homomorphism $j_B^-$ is injective. 
+In order to achieve this we need to show that $\St(\Phi, B)$ acts transitively on the first components of the triples from $\overline{V}_T$.
 These first components are parametrized by cosets $\overline{G}_M^{\geq 0}/G_M^0$ (cf.~\eqref{VT-def}).
@@
 
-\begin{rem} Although we will not need this for our main result, it can be noted that $\overline{V}$ is a left $\St(\Phi, B)$-torsor, i.\,e.
+\begin{rem} Although we do not need this for our main result, it can be noted that $\overline{V}$ is a left $\St(\Phi, B)$-torsor, i.\,e.
 the action of $\St(\Phi, B)$ on $\overline{V}$ is both transitive and faithful.
@@
  Set $v_0 = [1, 1, 1] \in \overline{V}_T$ and suppose $g \in \Ker(j_B^-)$.
- By~\cref{prop43} one has $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ such that $j_+i_+(\gamma) = 1$.
- Notice that $j_+i_+$ is split by the evaluation homomorphism $ev_{X=1}^*$ and therefore is injective. Thus, we conclude that $g = 1$.
-
- Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_B^-(g_-) = j_+(g_+)$.
- From~\cref{field-injectivity} it follows that the image of $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
-
- Set $h_+ = g_+g_0^{-1}$ and $h_- = g_-g_0^{-1}$.
+ By~\cref{prop43} one has $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ satisfying $j_-i_-(\gamma) = j_+i_+(\gamma) = 1$.
+ Notice that the homomorphism $j_+i_+ = j_-i_-$ is split by the evaluation homomorphism $ev_{X=1}^*$ and therefore is injective. Thus, we conclude that $g = 1$.
+
+ Now suppose that $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_B^-(g_-) = j_+(g_+)$.
+ By~\cref{field-injectivity} the image of $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
+
+ Set $h_+ = g_+\cdot g_0^{-1}$ and $h_- = g_- \cdot g_0^{-1}$.
  It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]),\ h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
  From~\cref{prop43} and~\cref{lem:action} we obtain that
- \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1]. \]
- Thus, $h_-$ (and hence $h_+$) come from some element of $G_M^0$, which implies that $g_+$ and $g_-$ are images of some element of $\St(\Phi, A)$.
+ \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1], \]
+  therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
+
+Denote by $T$ the isomorphism $\St(\Phi, A[X]) \to \St(\Phi, A[X\inv])$ induced by the obvious isomorphism of polynomial rings sending $X$ to $X^{-1}$.
+Repeating the above argument (now with $T(h_+)$ and $T^{-1}(h_-)$ playing the role of $h_-$ and $h_+$, respectively) we obtain that $h_+ =i_+(\gamma_2)$ for some $\gamma_2 \in G_M^0$.
+Since $j_+i_+ = j_- i_-$ is injective, we conclude that $\gamma_1 = \gamma_2$.
+Thus, we have shown that $g_+$ and $g_-$ are the images of $\gamma_1 \cdot g_0 \in \St(\Phi, A)$ under $i_+$ and $i_-$, respectively.
  \end{proof}
@@
 \begin{proof}[Proof of~\cref{thm:main}]
- Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follow from the assertion for $\St(\rD_\ell, -)$,
- which, in turn, follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
-
- Now let $A$ be an arbitrary commutative ring and $\Phi = \rD_\ell$, $\ell \geq 7$.
+ Notice that the assertions of the theorem for $\KO_2(2\ell, -)$ and $\K_2(\rD_\ell, -)$ follow from the assertion for $\St(\rD_\ell, -)$.
+It is also clear that the latter assertion follows from~\cref{thm41} and~\cref{thm:P1glueing} in the special case when $A$ is a local ring.
+
+ Now let $A$ be an arbitrary commutative ring and $\Phi = \rD_\ell$ for $\ell \geq 7$.
 If $g \in \St(\Phi, A[X])$ is such that its image in $\St(\Phi, A[X, X\inv])$ is trivial, then so is its image in all localizations $\St(\Phi, A_M[X, X\inv])$, where $M$ ranges over the maximal ideals of $A$.
@@
 $A[X\inv] \to A_M[X\inv]$) and by $\lambda_M^*$, $\lambda_{M,-}^*$ the corresponding homomorphisms of Steinberg groups.
- By the just established local case of the theorem the images $\lambda^*_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial.
-Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
+ By the previous paragraph the images $\lambda^*_M(g)$ in all $\St(\Phi, A_M[X])$ are also trivial. Now by the local-global principle \cite[Theorem~2]{LS17} the element $g$ is trivial as well.
 

### 2020-04-27 dl-paper.tex
Fix comments

@@
 
-\begin{abstract} We prove the $\mathbb{P}^1$-glueing theorem (aka Horrocks theorem) for the unstable even-dimensional orthogonal Steinberg groups.
-The $\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the principal ingredients needed in the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
+\begin{abstract} We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
+The Horrocks theorem for Steinberg groups is one of the principal ingredients needed in the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
 \end{abstract}
@@
 Such technique for working with Steinberg groups probably dates back to~\cite{ST76}.
-The proof of~\cref{thm:P1glueing} requires a certain amount of preparatory work.
-One of the necessary ingredients is a certain presentation theorem for Steinberg groups over graded rings, which is similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev, see~\cref{lemma33} (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
+The proof of~\cref{thm:P1glueing} is based on a number of preparatory statements.
+One of these is a certain presentation theorem for Steinberg groups over graded rings similar to the results of U.~Rehmann, C.~Soul{\'e} and M.~Tulenbaev, see~\cref{lemma33} (cf.~\cite[Satz~2]{Re75},\cite[Theorem~2]{RS76},\cite[Lemma~3.3]{Tu83}).
 \subsection{Acknowledgements} 
-The work of the first-named author (\S~3) was supported by the Russian Science Foundation grant No 17-11-01261. The first-named author is a winner of the contest ``Young Russian Mathematics``.
+The work of the first-named author (\S~3) was supported by the Russian Science Foundation grant No 17-11-01261. 
 The work of the second-named author (\S~4--5) was supported by RFBR grant No 18-31-20044.
@@
 \[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
-in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
+in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
 It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. \end{rem}
@@
 The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
-Direct computation using~\eqref{Chevalley-CCF1}--\eqref{Chevalley-CCF2} shows that
+Notice that by~\eqref{Chevalley-CCF2} the elements $x_\beta(\eta)$ and $x_{-\alpha}(\epsilon s \eta)$ commute with each other, therefore from~\eqref{Chevalley-CCF1}--\eqref{Chevalley-CCF2} we obtain that
 \begin{multline} \nonumber
@@
  \item \label{C4} If $\alpha+\beta\in\Phi$ then
-  \begin{equation} \label{eq:C4} c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\end{equation}
+  \begin{equation*} c_{\alpha+\beta}(s, t\xi) = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2),\end{equation*}
   where $\epsilon = N_{\alpha,\beta}$.
@@
 \begin{proof}
-The first two assertions can be verified by direct calculation:
+Notice that~\ref{C3} is an obvious consequence of~\eqref{Chevalley-CCF2}. Let us verify the first two assertions. Suppose that $\alpha + \beta \in \Phi$.  We have that
 \begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1};} \end{align*}
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
+ Now suppose that $\alpha - \beta \in \Phi$. We have that
 \begin{align*} \nonumber
@@
 = x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
-The assertion~\ref{C3} is obvious. Finally, the last assertion can be obtained as follows:
+Finally, let us prove~\ref{C4}. Suppose that $\alpha + \beta \in \Phi$. The required identity can be obtained as follows:
 \begin{align*}
@@
 \end{corollary}
-\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\eqref{eq:C4} we obtain that modulo 
+\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\cref{Crels}\ref{C4} we obtain that modulo 
  $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.

### 2020-04-27 dl-paper.tex
More issues fixed

@@
 This can be considered as some sort of a decomposition for $\St(\Phi, B)$.
-Such technique for working with Steinberg groups probably dates back to~\cite{ST76}.
+The technique of such decompositions probably dates back to~\cite{ST76}.
 The proof of~\cref{thm:P1glueing} is based on a number of preparatory statements.
@@
 in which the group $\mu_2(R) = \{ a \in R^\times \mid a^2 = 1 \}$ is a central subgroup of $\widetilde{P}_n(R)$.
-Now by~\cite[\S~7(v)]{Ste67} the group $\KO_2(2n, R) = \Ker(S_n \to G_n)$ is also central in $S_n$.
+Now by~\cite[\S~7(v)]{St67} the group $\KO_2(2n, R) = \Ker(S_n \to G_n)$ is also central in $S_n$.
 Thus, we see that $S_n$ is a universal central extension of both $P_n$ and $\widetilde{P}_n$ for $n\geq 5$.
@@
 Before we proceed with the proof of~\cref{thm:P1glueing} let us briefly recall the relevant notation.
-As before, $A$ denotes an arbitary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
+As before, $A$ denotes an arbitary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both the ring $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
 
@@
 It is clear from~\eqref{big-picture} that $\overline{G}_M^{\geq 0}$ lies in the image of $j_R$.
-To simplify notation we want to consider $\overline{G}_M^{\geq 0}$ as a subgroup of $\St(\Phi, B)$.
+To simplify notation we want to identify $\overline{G}_M^{\geq 0}$ with a subgroup of $\St(\Phi, B)$ by means of $j_R$.
 Thus, throughout this section we additionally assume that $j_R$ is injective.
@@
 
-\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
+\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has $j_R^{-1}(p_1) \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
 \begin{proof} 
@@
 
-Notice that in the base case $\xi = a \in A$ the assertion of the lemma is an immediate consequence of of~\eqref{T_leq0}.
+Notice that in the base case $\xi = a \in A$ the assertion of the lemma is an immediate consequence of~\eqref{T_leq0}.
 Since $x_\beta(X^2f) \in P_\alpha(0)$, an argument similar to the proof of~\cref{R1_d} shows that the assertion of the lemma also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
@@
  By~\cref{prop43} one has $v_0 = j_B^-(g) \cdot v_0 = [1, g, 1]$, therefore by the definition of $\overline{V}_T$, $g = i_-(\gamma)$ for some $\gamma \in G_M^0$ satisfying $j_-i_-(\gamma) = j_+i_+(\gamma) = 1$.
- Notice that the homomorphism $j_+i_+ = j_-i_-$ is split by the evaluation homomorphism $ev_{X=1}^*$ and therefore is injective. Thus, we conclude that $g = 1$.
-
- Now suppose that $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_B^-(g_-) = j_+(g_+)$.
+ Notice that the homomorphism $j_+i_+ = j_-i_-$ is split by the evaluation homomorphism $ev_{X=1}^*$ and therefore is injective.
+Thus, we conclude that $g = 1$ and that $j_-$ is injective.
+By symmetry, we also have that $j_+$ is injective (we can swap $X$ with $X^{-1}$ in all statements, including the statement of our assumption that $j_R$ is injective).
+
+ Now suppose that $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_+)$.
  By~\cref{field-injectivity} the image of $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$.
@@
  From~\cref{prop43} and~\cref{lem:action} we obtain that
- \[ [j_+(h_+)^{-1}, h_-, 1] = j_+(h_+)^{-1} \cdot [1, h_-, 1] = j_+(h_+)^{-1} j_B^-(h_-) \cdot [1, 1, 1] = [1, 1, 1], \]
-  therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
-
-Denote by $T$ the isomorphism $\St(\Phi, A[X]) \to \St(\Phi, A[X\inv])$ induced by the obvious isomorphism of polynomial rings sending $X$ to $X^{-1}$.
-Repeating the above argument (now with $T(h_+)$ and $T^{-1}(h_-)$ playing the role of $h_-$ and $h_+$, respectively) we obtain that $h_+ =i_+(\gamma_2)$ for some $\gamma_2 \in G_M^0$.
-Since $j_+i_+ = j_- i_-$ is injective, we conclude that $\gamma_1 = \gamma_2$.
+ \[ [j_+(h_+)^{-1}, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1}) \cdot [1, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1} \cdot j_-(h_-)) \cdot [1, 1, 1] = [1, 1, 1], \] therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$, $j_+(h_+) = j_+i_+(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
+Since $j_+$ is injective we obtain that $h_+ = i_+(\gamma_1)$.
 Thus, we have shown that $g_+$ and $g_-$ are the images of $\gamma_1 \cdot g_0 \in \St(\Phi, A)$ under $i_+$ and $i_-$, respectively.

### 2020-04-27 dl-paper.tex
Minor fix

@@
 \begin{abstract} We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
-The Horrocks theorem for Steinberg groups is one of the principal ingredients needed in the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
+The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
 \end{abstract}
@@
 \begin{proof} 
+By our assumption of the injectivity of $j_R$ and the above discussion the preimage $j_R^{-1}(p_1)$ consists of only one element, so the statement of the lemma is unambiguous.
+
 In view of~\cref{thm:Tits} it suffices to verify the assertion of the lemma for the generators $p_1 = z_\alpha(f, \xi)$ of $\overline{G}_M^{\geq 0}$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$.

### 2020-04-28 dl-paper.tex
Minor fix

@@
 
-The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work, and to the anonymous referee for his careful reading of an earlier version of the paper and suggesting a number of improvements.
+The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work, and to the anonymous referee for his careful reading of an earlier version of the paper and for suggesting a number of improvements.
 

### 2020-06-13 dl-paper.tex
Fix misprint
Fix misprints

@@
 \begin{equation*}\xymatrix{
- \KO_3(2\ell, B) \ar[r] \ar[d] & \KO_3(2\ell, k[X]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
+ \KO_3(2\ell, B) \ar[r] \ar[d] & \KO_3(2\ell, k[X^{-1}]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
  \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
-By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
+By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X^{-1}]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
 By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
@@
  C(\rD_\ell, B, I) \ar[r]^{\lambda_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
- \St(\rD_\ell, B) \ar[r]^{\nu_B} \ar[d]_{h} & \St(\rD_\ell, k[X]) \ar[d]_{i} \\
+ \St(\rD_\ell, B) \ar[r]^{\nu_B} \ar[d]_{h} & \St(\rD_\ell, k[X^{-1}]) \ar[d]_{i} \\
  C(\rD_\ell, R, I) \ar[r]^{\lambda_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
@@
 
-For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type K$i$. from~\cref{def:Kab}.
+For $i=1,\ldots,5$ denote by $\mathcal{G}_i$ the set of all generators of type K$i$ from~\cref{def:Kab}.
 Notice that $\Phi \setminus \Psi$ contains the parabolic set of roots $(\Phi \setminus \Psi)\cap \Phi^+$.
@@
 Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
-\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R)} \]
+\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R).} \]
 Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
@@
 \[T_\alpha(a + Xf) \cdot ((g, h, u) \cdot h_0) = (T_\alpha(a + Xf) \cdot (g, h, u)) \cdot {}^{x_{\alpha}(a)}\!h_0,\]  
-therefore~\eqref{T_leq0}, indeed, gives rise to a well-defined map $\overline{V} \to \overline{V}$.
+therefore~\eqref{T_leq0} indeed gives rise to a well-defined map $\overline{V} \to \overline{V}$.
 
@@
 
-\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
+\begin{lemma} \label{R2_0_1} The operators $T_\alpha$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
 \begin{proof} 

### 2020-06-17 dl-paper.tex
Use document style and fix overfulls

@@
-\documentclass[oneside, 8pt]{amsart}
+%
+%    Documenta-LaTeX.sty (2e)
+%
+%    Version 0.52
+%
+%    Copyright (C) 1996-2017 Ulf Rehmann
+%    rehmann@math.uni-bielefeld.de
+%
+% ------------------------------ PROLOGUE -----------------------------
+%
+% This prologue is to be prepended to your LaTeX file in order to
+% give it the layout required by Documenta Mathematica.
+% Please edit the \documentclass line below, add \usepackage lines
+% according to your needs and
+% go to the line starting with \Title below, fill in title,
+% authors' names and so on and follow the further instructions there.
+% 
+% Choose one of the commands \documentclass[]{} or \documentstyle[]{}
+% depending on the version of LaTeX you use:
+%
+%
+% If you use LaTeX 2e use the following line (or similar):
+\documentclass[10pt,a4paper,twoside]{article}
+%%\usepackage{hyperref}
+% Append here commands \usepackage{...} if you want.
+%
+% If you use LaTeX 2.09 or earlier use the following line (or similar):
+%\documentstyle[10pt,twoside]{article}
+%
+% Please go to the line starting with \Title below, fill in title,
+% authors' names and so on and follow the further instructions there.
+%
+% The final values of the following 4 uncommented lines will be filled in
+% by Doc. Math. after the manuscript has been accepted for publication.
+%
+\def\YEAR{\year}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
+\def\firstpage{1}\def\lastpage{1000}
+\def\received{}\def\revised{}
+\def\communicated{}
+%
+
+\makeatletter
+\def\magnification{\afterassignment\m@g\count@}
+\def\m@g{\mag=\count@\hsize6.5truein\vsize8.9truein\dimen\footins8truein}
+\makeatother
+
+%%% Choose 10pt/12pt:
+%\oddsidemargin1.66cm\evensidemargin1.66cm\voffset1.2cm%10pt
+\oddsidemargin1.91cm\evensidemargin1.91cm\voffset1.4cm%10pt
+%\magnification1200\oddsidemargin.41cm\evensidemargin.41cm\voffset-.75cm%12pt
+
+%\textwidth12.5cm\textheight19.5cm
+\textwidth12.0cm\textheight19.0cm
+
+\font\eightrm=cmr8
+\font\caps=cmcsc10                    % Theorem, Lemma etc
+\font\ccaps=cmcsc10                   % Sections
+\font\Caps=cmcsc10 scaled \magstep1   % Title
+\font\scaps=cmcsc8
+
+%
+%-----------------headlines-----------------------------------
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
@@
 \renewcommand*{\bibfont}{\footnotesize}
+\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}
 
@@
 
-\title{A Horrocks-type theorem for even orthogonal $K_2$}
-\keywords {Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing. {\em Mathematical Subject Classification (2010):} 19C20}
-\author{Andrei Lavrenov}
-\email{avlavrenov at gmail.com}
-\author {Sergey Sinchuk}
-\email {sinchukss at gmail.com}
-\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
-\date {\today}
+\pagestyle{myheadings}
+\pagenumbering{arabic}
+\setcounter{page}{\firstpage}
+\def\bfseries{\normalsize\caps}
+
+\makeatletter
+\setlength\topmargin {14\p@}
+\setlength\headsep   {15\p@}  
+\setlength\footskip  {25\p@}  
+\setlength\parindent {20\p@} 
+\@specialpagefalse\headheight=8.5pt
+\def\DocMath{{\def\th{\thinspace}\scaps Documenta Math.}}
+\renewcommand{\@oddfoot}{\hfill\scaps Documenta Mathematica 
+    \number\VOL\  (\number\YEAR) \number\firstpage--\lastpage\hfill}
+\renewcommand{\@evenfoot}{\ifnum\thepage>\lastpage\hfill\scaps
+    Documenta Mathematica \number\VOL\  (\number\YEAR)\hfill\else\@oddfoot\fi}%
+
+\renewcommand{\@evenhead}{%
+    \ifnum\thepage>\lastpage\rlap{\thepage}\hfill%
+    \else\rlap{\thepage}\slshape\leftmark\hfill{\caps\SAuthor}\hfill\fi}%
+\renewcommand{\@oddhead}{%
+    \ifnum\thepage=\firstpage{\DocMath\hfill\llap{\thepage}}%
+    \else{\slshape\rightmark}\hfill{\caps\STitle}\hfill\llap{\thepage}\fi}%
+\makeatother
+
+\def\TSkip{\bigskip}
+\newbox\TheTitle{\obeylines\gdef\GetTitle #1
+\ShortTitle  #2
+\SubTitle    #3
+\Author      #4
+\ShortAuthor #5
+\EndTitle
+{\setbox\TheTitle=\vbox{\baselineskip=20pt\let\par=\cr\obeylines%
+\halign{\centerline{\Caps##}\cr\noalign{\medskip}\cr#1\cr}}%
+	\copy\TheTitle\TSkip\TSkip%
+\def\next{#2}\ifx\next\empty\gdef\STitle{#1}\else\gdef\STitle{#2}\fi%
+\def\next{#3}\ifx\next\empty%
+    \else\setbox\TheTitle=\vbox{\baselineskip=20pt\let\par=\cr\obeylines%
+    \halign{\centerline{\caps##} #3\cr}}\copy\TheTitle\TSkip\TSkip\fi%
+%\setbox\TheTitle=\vbox{\let\par=\cr\obeylines%
+%\halign{\centerline{\caps##} #4\cr}}\copy\TheTitle\TSkip\TSkip%
+\centerline{\caps #4}\TSkip\TSkip%
+\def\next{#5}\ifx\next\empty\gdef\SAuthor{#4}\else\gdef\SAuthor{#5}\fi%
+\ifx\received\empty\relax
+    \else\centerline{\eightrm Received: \received}\fi%
+\ifx\revised\empty\TSkip%
+    \else\centerline{\eightrm Revised: \revised}\TSkip\fi%
+\ifx\communicated\empty\relax
+    \else\centerline{\eightrm Communicated by \communicated}\fi\TSkip\TSkip%
+\catcode'015=5}}\def\Title{\obeylines\GetTitle}
+\def\Abstract{\begingroup\narrower
+    \parskip=\medskipamount\parindent=0pt{\caps Abstract. }}
+\def\EndAbstract{\par\endgroup\TSkip}
+
+\long\def\MSC#1\EndMSC{\def\arg{#1}\ifx\arg\empty\relax\else
+     {\par\narrower\noindent%
+     2010 Mathematics Subject Classification: #1\par}\fi}
+
+\long\def\KEY#1\EndKEY{\def\arg{#1}\ifx\arg\empty\relax\else
+	{\par\narrower\noindent Keywords and Phrases: #1\par}\fi\TSkip}
+
+\newbox\TheAdd\def\Addresses{\vfill\copy\TheAdd\vfill
+    \ifodd\number\lastpage\vfill\eject\phantom{.}\vfill\eject\fi}
+{\obeylines\gdef\GetAddress #1
+\Address #2 
+\Address #3
+\Address #4
+\EndAddress
+{\def\xs{4.8truecm}\parindent=0pt
+\setbox0=\vtop{{\obeylines\hsize=\xs#1\par}}\def\next{#2}
+\ifx\next\empty % 1 address
+     \setbox\TheAdd=\hbox to\hsize{\hfill\copy0\hfill}
+\else\setbox1=\vtop{{\obeylines\hsize=\xs#2\par}}\def\next{#3}
+\ifx\next\empty % 2 addresses
+     \setbox\TheAdd=\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
+\else\setbox2=\vtop{{\obeylines\hsize=\xs#3\par}}\def\next{#4}
+\ifx\next\empty\ % 3 addresses
+     \setbox\TheAdd=\vtop{\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
+                \vskip20pt\hbox to\hsize{\hfill\copy2\hfill}}
+\else\setbox3=\vtop{{\obeylines\hsize=\xs#4\par}}
+     \setbox\TheAdd=\vtop{\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
+	        \vskip20pt\hbox to\hsize{\hfill\copy2\hfill\copy3\hfill}}
+\fi\fi\fi\catcode'015=5}}\gdef\Address{\obeylines\GetAddress}
+
+\hfuzz=0.1pt\tolerance=2000\emergencystretch=20pt\overfullrule=5pt
+
+%%%%% Embedded files should be stored in a separate subdirectory named
+%%%%% <filename>.files where <filename> is the same as the name of the
+%%%%% main tex file without the extension .tex.
+
+%%%%% In order for tex to find those embedded files, \input and
+%%%%% \includegraphics commands etc. have to reflect the embedded
+%%%%% files path by using the '\LOCAL' macro defined below, like
+%%%%% \input{\LOCAL/introduction} for embedding a file named
+%%%%% 'introduction.tex', or
+%%%%% \includegraphics[width=0.95\textwidth]{\LOCAL/knot.eps} for
+%%%%% embedding a graphics file named 'knot.eps', or
+%%%%% \bibselect{\LOCAL/references} in case references are embedded
+%%%%% from a file named 'references.ltb' etc.
+
+%%%%% Graphics files should always be submitted in encapsulated
+%%%%% postscript format (extension '.eps').
+
+\def\LOCAL{\jobname.files}
 
 \begin{document}
-
-\begin{abstract} We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
+%%%%% ------------- fill in your data below this line  -------------------
+%%%%%    The following lines \Title ... \EndAddress must ALL be present
+%%%%%    and in the given order.
+\Title
+A Horrocks-type theorem for even orthogonal $K_2$
+\ShortTitle 
+A Horrocks-type theorem for $\mathrm{KO}_2$ 
+\SubTitle   
+%%%%%    A possible subtitle goes here.
+\Author 
+Andrei Lavrenov, Sergey Sinchuk
+\ShortAuthor 
+Lavrenov and Sinchuk
+\EndTitle
+\Abstract 
+We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
 The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
-\end{abstract}
-\maketitle
+\EndAbstract
+\MSC 
+19C20
+\EndMSC
+\KEY 
+Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
+\EndKEY
+%%%%%    All 4 \Address lines below must be present. To center the last
+%%%%%    entry, no empty lines must be between the following \Address
+%%%%%    and \EndAddress lines.
+\Address
+Andrei Lavrenov
+avlavrenov@gmail.com
+\Address
+Sergey Sinchuk
+sinchukss@gmail.com
+\Address
+Chebyshev laboratory, 
+St. Petersburg State University, 
+14th. Line V.O. 29b
+199178, St. Petersburg, Russia
+\Address
+\EndAddress
+%%
+%%       Make sure the last tex command in your manuscript
+%%       before the first \end{document} is the command  \Addresses
+%%
+%%---------------------Here the prologue ends---------------------------------
+%%--------------------Here the manuscript starts------------------------------
+
+%%--------------------Here the manuscript ends--------------------------------
+\Addresses
 \section{Introduction}
@@
 Indeed, we have the following chain of isomorphisms:
-\[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
+\begin{multline} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \\ \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{multline}
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
@@
 \begin{multline*} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
-  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta),\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline*}
+  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta),\end{multline*}
+ where $\epsilon = N_{\alpha,\beta}$.
 \end{enumerate} \end{lemma}
@@
 \begin{multline} \nonumber
-  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
-  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
+  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] = \\
+  = [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
   = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
@@
 Notice that~\ref{C3} is an obvious consequence of~\eqref{Chevalley-CCF2}. Let us verify the first two assertions. Suppose that $\alpha + \beta \in \Phi$.  We have that
-\begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
+\newline \scalebox{.88}{\begin{minipage}{1.13\linewidth} \begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
  Now suppose that $\alpha - \beta \in \Phi$. We have that
-\begin{align*} \nonumber
+\newline \scalebox{.86}{\begin{minipage}{1.16\linewidth}\begin{align*} \nonumber
 \begin{split}[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = {}^{x_\beta(s)}\!\bigl( {}^{x_{-\beta}(t)}[x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] \cdot \hspace{50pt} \\ \cdot {}^{x_{\alpha}(\xi)}[x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] \bigr)^{} & \text{ by~\eqref{HW-variant}}\end{split} \\
-= {}^{x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(-N_{\beta, \alpha-\beta} N_{\alpha,-\beta} \cdot s t \xi) = {}^{ x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(s t \xi) & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
-= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
+= {}^{x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}\left(-N_{\beta, \alpha-\beta} \cdot N_{\alpha,-\beta} \cdot s t \xi\right) = {}^{ x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(s t \xi) & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
+= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
 Finally, let us prove~\ref{C4}. Suppose that $\alpha + \beta \in \Phi$. The required identity can be obtained as follows:
-\begin{align*}
+\newline \scalebox{.84}{\begin{minipage}{1.17\linewidth}\begin{align*}
 [x_{\alpha+\beta}(s),\ x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s),\ [x_{-\alpha}(-\epsilon t),\ x_{-\beta}(\xi)]]&\ \text{by~\eqref{Chevalley-CCF1}}\\
@@
 = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2)  &\ \text{by~\eqref{Chevalley-CCF1}}.
-\qedhere
-\end{align*}
-\end{proof}
-
-\subsection{Computation of the kernel of the map of evaluation at $0$.}\label{sec:computationOfK}
+\qedhere \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
+\end{proof}
+
+\subsection{Computation of the kernel of the map of evaluation at 0.}\label{sec:computationOfK}
 Let $A$ be a local ring with maximal ideal $M$.
@@
  Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows: 
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
+ \scalebox{0.96}{\begin{minipage}{1.04\linewidth}
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]\end{minipage}}
  It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$.
@@
 Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they follow from~$\text{R2}_{e,0}$, \eqref{eq:H1iii} and $\text{R3}_{d,e}^\angle$.
-Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we have that \[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1.
-\]
+Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we have that
+\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
+\[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1.
+\]\end{minipage}}
 \end{rem}
@@
 \item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
+\newline
+\scalebox{0.85}{\begin{minipage}{1.16\linewidth}
 \begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
@@
  = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
- = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
+ = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}\end{minipage}} \vskip \belowdisplayshortskip
  where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.
@@
 \item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
+\newline \scalebox{0.85}{\begin{minipage}{1.16\linewidth}
 \begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
@@
  = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
+ = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
  \end{enumerate}
@@
 The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
+\newline\scalebox{0.82}{\begin{minipage}{1.21\linewidth}
 \begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1 x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
-\qedhere \end{multline*}
+\qedhere \end{multline*}\end{minipage}}
 \end{proof}
@@
 \begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
+\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}
  \begin{align} 
@@
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}.
-\nonumber \end{align}
+\nonumber \end{align}\end{minipage}}
 The assertion of the lemma now follows from the following computation:
-\begin{align*}
+\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{align*}
  S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}  \end{proof}
-
-\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$
-.%, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}\end{minipage}}  \end{proof}
+
+\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am}).$
+%, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]
 \end{corollary} \begin{proof}
@@
 Direct computation shows that
-\begin{align*}
+\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{align*}
  S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)&\text{ by~\cref{lem:Smult}} \\\
  = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle &\text{ by~\cref{lem:Tulenbaev-formula}.}
-\end{align*}
+\end{align*}\end{minipage}} \vskip \belowdisplayshortskip
 By \cref{P0_conj} and \cref{rem:DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$.
@@
 Since $x_{-\beta}(m'X) \in P_\alpha(0)$ we get that
-\begin{align*}
+\newline\scalebox{.8}{\begin{minipage}{1.25\linewidth}\begin{align*}
   S_\alpha(a, g) = g_1 \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) & \text{ by~\cref{lem:Smult}} \\ 
@@
   = g_1 \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am) & \text{ by~\eqref{eq:conj-h-x}}.
-\end{align*}
+\end{align*}\end{minipage}} \vskip \belowdisplayshortskip
 The required assertion now follows from~\cref{rem:palpha}.
@@
 Notice that $x_{-\beta}(m'X) \in P_\alpha(0)$, therefore from the definition of $S_\alpha(a, -)$ we obtain that
+\newline \scalebox{0.75}{\begin{minipage}{1.33\linewidth}
 \begin{align*}
@@
  = x_{\beta-\alpha}(-b) \cdot x_{-\beta}(m'c^{-1}X) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right) &\text{ by~\eqref{Chevalley-CCF1}.}
-\end{align*}
+\end{align*}\end{minipage}} \vskip \belowdisplayshortskip
 Denote by $h_0$ the product of all factors in the above formula except the first and the last one.
@@
 Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
-\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R).} \]
+\newline \scalebox{0.80}{\begin{minipage}{1.15\linewidth}
+\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R).} \]\end{minipage}} \vskip \belowdisplayshortskip
 Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
@@
 Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
- \begin{multline} \nonumber
+ \newline \scalebox{0.95}{\begin{minipage}{1.05\linewidth}\begin{multline} \nonumber
   t_\alpha(aX^{-1})(v_1) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
   \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(v_2). \qedhere
- \end{multline} \end{proof}
+ \end{multline}\end{minipage}}\end{proof}
 
@@
  From~\eqref{T_1} we obtain that 
- \begin{equation}\label{add-computation}
-  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
- \end{equation}
+ \begin{multline}\label{add-computation}
+  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = \\ = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
+ \end{multline}
  where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.
@@
  Now we can invoke~\eqref{T_1} once again and can continue~\eqref{add-computation} as follows:
- \begin{equation}\label{add-computation2}
-  \ldots = \left(x_\alpha((a + b)X^{-1})\cdot g ,\ \left[ h'' \cdot x_\alpha\left(\tfrac{-bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \right],\ u \cdot (1 + am) \cdot \left(1+\tfrac{bm}{1+am}\right)\right).
- \end{equation} 
+ \newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{equation}\label{add-computation2}
+  \ldots = \left(x_\alpha((a + b)X^{-1})\cdot g ,\ \left[ h'' \cdot x_\alpha\left(\tfrac{-bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \right],\ u \cdot (1 + am) \cdot \left(1+\tfrac{bm}{1+am}\right)\right).\end{equation}\end{minipage}}\vskip \belowdisplayshortskip
  Notice that 
- \[ \left[h'' \cdot x_\alpha\left(\tfrac{-b(1+am)X^{-1}}{1+am + bm}\right)\right] = \left[h \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1 + am}\right) \cdot x_\alpha\left(\tfrac{-bX^{-1}}{(1+am)(1+am+bm)}\right)\right] =
- \left[h \cdot x_\alpha\left(\tfrac{-(a+b)X^{-1}}{1+(a+b)m}\right)\right].\] 
+ \begin{multline} \nonumber \left[h'' \cdot x_\alpha\left(\tfrac{-b(1+am)X^{-1}}{1+am + bm}\right)\right] = \left[h \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1 + am}\right) \cdot x_\alpha\left(\tfrac{-bX^{-1}}{(1+am)(1+am+bm)}\right)\right] = \\ =
+ \left[h \cdot x_\alpha\left(\tfrac{-(a+b)X^{-1}}{1+(a+b)m}\right)\right].\end{multline}
  Thus, the expression in~\eqref{add-computation2} coincides with the expression for $T_\alpha((a+b)X^{-1})\cdot (g, [h], u)$ given by~\eqref{T_1}. \end{proof}
@@
 Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
-\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}
+\newline\scalebox{0.84}{\begin{minipage}{1.16\linewidth}\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}\end{minipage}}\vskip \belowdisplayshortskip
 where in the last equality we use the following computation:
-\begin{equation} \nonumber
- h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am).
-\end{equation}
+\begin{multline} \nonumber
+ h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = \\ = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am).
+\end{multline}
 The assertion of the lemma now follows from~\eqref{R3leq0-computation}--\eqref{R3leq0-computation2}. \end{proof}
@@
 From~\eqref{T_1}--\eqref{T_leq0} and the fact that $x_\beta(Xf) \in P_\alpha(0)$ we obtain that
+\newline\scalebox{0.79}{\begin{minipage}{1.26\linewidth}
 \begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ [h],\ u\right) = \\ 
 = T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am)\right],\ u(1-am)\right) = \\ = \left([x_\beta(Xf),\ x_\alpha(aX^{-1})] \cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right)\right],\ u \right) = \\ = (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ [h],\ u) = T_{\alpha+\beta}(N_{\beta, \alpha} \cdot af) (g, [h], u).
-\end{multline}
+\end{multline}\end{minipage}}\vskip \belowdisplayshortskip
 
@@
 Notice that by~\cref{SR:sharp}
-\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
+\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]\end{minipage}}\vskip\belowdisplayshortskip
 therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
+\newline\scalebox{0.88}{\begin{minipage}{1.13\linewidth}
 \begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g,\ \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right],\ u(1 + am + bm')\right).
-\end{equation}
+\end{equation}\end{minipage}}\vskip \belowdisplayshortskip
 The second component of the above triple can be simplified using~\eqref{eq:conj-h-x} as follows:
+\newline\scalebox{0.96}{\begin{minipage}{1.04\linewidth}
 \begin{multline*}
@@
  = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right)\right].
-\end{multline*}
+\end{multline*}\end{minipage}}\vskip \belowdisplayshortskip
 Thus, we see that the expression in the right-hand side of~\eqref{R3_1_1-computation2} would remain unchanged if we swapped $(a,\alpha,m)$ with $(b,\beta,m')$. This implies the required assertion.
@@
 From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
-\begin{multline} \label{R2_0_1-computation}
+\newline\scalebox{0.9}{\begin{minipage}{1.1\linewidth}\begin{multline} \label{R2_0_1-computation}
 [T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
@@
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
- \end{multline} 
+ \end{multline}\end{minipage}}\vskip\belowdisplayshortskip
  where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$.
@@
 \begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained from~\eqref{eq:conj-h-x} as follows:
- \begin{multline} \nonumber
+\newline\scalebox{0.8}{\begin{minipage}{1.2\linewidth}\begin{multline} \nonumber
  [h''] = \left[ h' \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1+\tfrac{a(m-\epsilon bm')}{1-am}}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
- = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].
-\end{multline}
+ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].\end{multline}\end{minipage}}\vskip \belowdisplayshortskip
 The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.
@@
 \begin{multline*}
- z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-X^2 f\xi ) \cdot x_{\beta}(\xi f) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon X\xi^2f) \cdot x_{-\alpha-\beta}(- X^2f \xi^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}),\text{ where $\epsilon = N_{\alpha, \beta}$.}
-\end{multline*}
+ z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-X^2 f\xi ) \cdot x_{\beta}(\xi f) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon X\xi^2f) \cdot x_{-\alpha-\beta}(- X^2f \xi^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1}), \end{multline*}
+where $\epsilon = N_{\alpha, \beta}$.
+
 From the inductive assumption we obtain that the assertion of the lemma holds for all the factors in the right-hand side and, therefore, also holds for $p_1 = z_\alpha(f, X\xi)$.
@@
  Set $h_+ = g_+\cdot g_0^{-1}$ and $h_- = g_- \cdot g_0^{-1}$.
- It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]),\ h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\text{ and that }j_-(h_-) = j_+(h_+).\]
+ It is clear that \[ h_+ \in \overline{\St}(\Phi, A[X], M[X]),\ h_- \in \overline{\St}(\Phi, A[X\inv], M[X\inv])\]
+ and that $j_-(h_-) = j_+(h_+).$
+
  From~\cref{prop43} and~\cref{lem:action} we obtain that
- \[ [j_+(h_+)^{-1}, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1}) \cdot [1, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1} \cdot j_-(h_-)) \cdot [1, 1, 1] = [1, 1, 1], \] therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$, $j_+(h_+) = j_+i_+(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
+ \begin{multline} \nonumber [j_+(h_+)^{-1}, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1}) \cdot [1, h_-, 1] = \\ = j_R^{-1}(j_+(h_+)^{-1} \cdot j_-(h_-)) \cdot [1, 1, 1] = [1, 1, 1], \end{multline} therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$, $j_+(h_+) = j_+i_+(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
 Since $j_+$ is injective we obtain that $h_+ = i_+(\gamma_1)$.

### 2020-06-17 horrocks.tex
Rename paper + fix some bugs

--- 2020-06-17 dl-paper.tex
@@
 
-\addbibresource{paper.bib}
+%%%%% Embedded files should be stored in a separate subdirectory named
+%%%%% <filename>.files where <filename> is the same as the name of the
+%%%%% main tex file without the extension .tex.
+
+%%%%% In order for tex to find those embedded files, \input and
+%%%%% \includegraphics commands etc. have to reflect the embedded
+%%%%% files path by using the '\LOCAL' macro defined below, like
+%%%%% \input{\LOCAL/introduction} for embedding a file named
+%%%%% 'introduction.tex', or
+%%%%% \includegraphics[width=0.95\textwidth]{\LOCAL/knot.eps} for
+%%%%% embedding a graphics file named 'knot.eps', or
+%%%%% \bibselect{\LOCAL/references} in case references are embedded
+%%%%% from a file named 'references.ltb' etc.
+
+%%%%% Graphics files should always be submitted in encapsulated
+%%%%% postscript format (extension '.eps').
+
+\def\LOCAL{\horrocks.files}
+
+\addbibresource{horrocks.files/references.bib}
 \renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
@@
 \hfuzz=0.1pt\tolerance=2000\emergencystretch=20pt\overfullrule=5pt
-
-%%%%% Embedded files should be stored in a separate subdirectory named
-%%%%% <filename>.files where <filename> is the same as the name of the
-%%%%% main tex file without the extension .tex.
-
-%%%%% In order for tex to find those embedded files, \input and
-%%%%% \includegraphics commands etc. have to reflect the embedded
-%%%%% files path by using the '\LOCAL' macro defined below, like
-%%%%% \input{\LOCAL/introduction} for embedding a file named
-%%%%% 'introduction.tex', or
-%%%%% \includegraphics[width=0.95\textwidth]{\LOCAL/knot.eps} for
-%%%%% embedding a graphics file named 'knot.eps', or
-%%%%% \bibselect{\LOCAL/references} in case references are embedded
-%%%%% from a file named 'references.ltb' etc.
-
-%%%%% Graphics files should always be submitted in encapsulated
-%%%%% postscript format (extension '.eps').
-
-\def\LOCAL{\jobname.files}
 
@@
 %%--------------------Here the manuscript ends--------------------------------
-\Addresses
 \section{Introduction}
@@
  Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows: 
- \scalebox{0.96}{\begin{minipage}{1.04\linewidth}
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]\end{minipage}}
+\newline\scalebox{0.96}{\begin{minipage}{1.04\linewidth}
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]\end{minipage}}\vskip \belowdisplayshortskip
  It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$.
@@
  the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in A[X]$, $\alpha \in \Phi$. \end{prop}
-\begin{proof} From~\eqref{eq:conj-h-x} we obtain that $\myol{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that $[\myol{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X])$.
+\begin{proof} From~\eqref{eq:conj-h-x} we obtain that $\myol{H}(\Phi, A, M)$ normalizes both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ and, moreover, that \[[\myol{H}(\Phi, A, M),\ \St(\Phi, XA[X])] \subseteq \overline{\St}(\Phi, A[X], XM[X]).\]
 
@@
 Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they follow from~$\text{R2}_{e,0}$, \eqref{eq:H1iii} and $\text{R3}_{d,e}^\angle$.
-Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we have that
-\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
+Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we obtain that
+\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
 \[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1.
@@
 \newline
-\scalebox{0.85}{\begin{minipage}{1.16\linewidth}
+\scalebox{0.84}{\begin{minipage}{1.16\linewidth}
 \begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
-[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
+[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \nonumber \\ 
  = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_1 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
@@
  = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
- = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}\end{minipage}} \vskip \belowdisplayshortskip
+ = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \label{first-computation} \end{align}\end{minipage}} \vskip \belowdisplayshortskip
  where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.
@@
   \item $c_{\delta}(f, X\xi)$. \end{enumerate} \end{df}
-\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X)$. 
+\begin{prop} \label{K-a-b} One has \[K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X).\] 
 \end{prop} 
@@
 
-By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$, so it suffices to obtain the required presentation of $g$ modulo $G_0$.
+Set $G_0 = \overline{\St}(\Phi, A[X], X^2M[X])$.
+By~\cref{thm:Stepanov} $\widetilde{K}(\alpha, \beta)$ contains the normal subgroup $G_0$ therefore it suffices to obtain the required presentation of $g$ modulo $G_0$.
 By~\cref{Zrels} and~\cref{Crels} the elements of $\mathcal{G}'$ commute with the elements of $\mathcal{G}_1$ and $\mathcal{G}_5$ modulo $G_0$, therefore we can rewrite $g$ as $g_1 \cdot g_2$, for some $g_1 \in \langle \mathcal{G}_1, \mathcal{G}_5, G_0 \rangle \subseteq \widetilde{K}(\alpha, \beta)$ and $g_2 \in \langle \mathcal{G}' \rangle$.
@@
 \printbibliography
+\Addresses
 \end{document}

### 2020-06-19 horrocks.tex
Minor fix
Final version with integrated bibliography

@@
 \usepackage{enumitem}
+\usepackage{filecontents}
 
@@
 \def\LOCAL{\horrocks.files}
-
-\addbibresource{horrocks.files/references.bib}
+\begin{filecontents}{horrocks.bib}
+@Article{Abe83,
+    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
+    Author = {Abe, Eiichi},
+    Journal = {Comm. Alg.},
+    Year = {1983},
+    Number = {12},
+    Pages = {1271-1307},
+    Volume = {11},
+    Doi = {10.1080/00927878308822906} }
+
+@book{BHS11,
+    title = {Nonabelian algebraic topology},
+    author = {Brown, Ronald and Higgins, Philip J. and Sivera, Rafael},
+    series = {EMS Tracts in Mathematics},
+    volume = {15},
+    year = {2011} }
+
+@book{HOM,
+    Title = {The classical groups and $K$-theory},
+    Author = {Hahn, Alexander J. and O'Meara, Timothy},
+    Year = {1989},
+    Publisher = {Springer} }
+
+@Article{Ka77,
+    Title = {Another presentation for {S}teinberg groups},
+    Author = {Kallen, Wilberd van der},
+    Journal = {Indag. Math.},
+    Volume = {80},
+    Number = {4},
+    Pages = {304--312},
+    Year = {1977},
+    Doi = {10.1016/1385-7258(77)90026-9} }
+
+@Book{Lam10,
+    Title = {Serre's problem on projective modules},
+    Author = {Lam, Tsit-Yuen},
+    Publisher = {Springer Science \& Business Media},
+    Year = {2010},
+    Doi = {10.1007/978-3-540-34575-6} }
+
+@online{La15,
+    Title = {Local-global principle for symplectic $K_2$},
+    Author = {Lavrenov, Andrei},
+    Year = {2015} }
+
+@Article{LS17,
+    Title = {Centrality of odd orthogonal $K_2$},
+    Author = {Lavrenov, A. and Sinchuk, S.},
+    Journal = {J. Pure Appl. Alg.},
+    Volume = {221},
+    Year = {2017},
+    Pages = {1134--1145},
+    url = {https://arxiv.org/pdf/1606.00272.pdf} }
+
+@Inproceedings{RS76,
+    Title = {Finitely presented groups of matrices},
+    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
+    Booktitle = {Algebraic K-Theory},
+    Publisher = {Springer},
+    Year = {1976},
+    Pages = {164--169},
+    Series = {Lect. Notes. Math.},
+    Volume = {551},
+    Doi = {10.1007/BFb0079999} }
+
+@Article{S15,
+    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
+    Author = {Sinchuk, Sergey},
+    Journal = {J. Pure Appl. Alg.},
+    Year = {2016},
+    Number = {2},
+    Pages = {857--875},
+    Volume = {220},
+    Doi = {10.1016/j.jpaa.2015.08.003} }
+
+@Article{St-poly,
+    Title = {Homotopy invariance of non-stable $K_1$-functors},
+    Author = {Stavrova, Anastasia},
+    Journal = {J. K-th.},
+    Year = {2014},
+    Number = {2},
+    Pages = {199--248},
+    Volume = {13},
+    Doi = {10.1017/is013006012jkt232} }
+
+@Article{St-serr,
+    Title = {Non-stable $K_1$-functors of multiloop groups},
+    Author = {Stavrova, Anastasia},
+    Journal = {Canad. J. Math.},
+    Year = {2014},
+    Doi = {10.4153/CJM-2015-035-2} }
+
+@Book{St67,
+    Title = {Lectures on Chevalley groups},
+    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
+    Year = {1967},
+    Publisher = {Yale Univ. New Haven}}
+
+@Article{Ste73,
+    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
+    Author = {Stein, Michael R.},
+    Journal = {Trans. Amer. Math. Soc.},
+    Year = {1973},
+    Pages = {165--191},
+    Volume = {178},
+    Doi = {10.2307/1996696} }
+
+@Article{Su77,
+    Title = {On the structure of the special linear group over commutative rings},
+    Author = {Suslin, Andrei},
+    Journal = {Math. USSR Izv.},
+    Year = {1977},
+    Pages = {221--238},
+    Volume = {11},
+    Doi = {10.1070/IM1977v011n02ABEH001709} }
+
+@Article{Tu83,
+    Title = {The {S}teinberg group of a polynomial ring},
+    Author = {Tulenbaev, Marat},
+    Journal = {Math. USSR Sb.},
+    Year = {1983},
+    Pages = {131--144},
+    Volume = {45},
+    Doi = {10.1070/SM1983v045n01ABEH002591} }
+
+@Article{ST76,
+  author    = {Suslin, Andrei and Tulenbaev, Marat},
+  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
+  journal   = {J. Soviet Math.},
+  year      = {1981},
+  volume    = {17},
+  number    = {2},
+  pages     = {1804-1819},
+  doi       = {10.1007/BF01091768}}
+
+@Book{Kbook,
+    Title = {The $K$-book: An introduction to algebraic $K$-theory},
+    Author = {Weibel, Charles A},
+    Volume = {145},
+    Year = {2013},
+    Publisher = {Amer. Math. Soc.},
+    Series = {Grad. Texts Math.} }
+
+@Article{Vav09,
+    Title = {Weight elements of Chevalley groups},
+    Author = {Vavilov, Nikolai A.},
+    Journal = {St. Petersburg Math. J.},
+    Year = {2009},
+    Number = {1},
+    Pages = {23--57},
+    Volume = {20},
+    Doi = {10.1090/S1061-0022-08-01036-4} }
+
+@Article{We14,
+    Title = {On homology of linear groups over $k[t]$},
+    Author = {Wendt, Matthias},
+    Journal = {Math. Res. Lett.},
+    Year = {2014},
+    Number = {6},
+    Volume = {21},
+    Doi = {10.4310/MRL.2014.v21.n6.a15} }
+
+@Article{Ma69,
+    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
+    author = {Matsumoto, H.},
+    journal = {Ann. Sci. ENS},
+    year = {1969},
+    number = {1},
+    pages = {1--62},
+    volume = {2},
+    url = {http://eudml.org/doc/81843} }
+
+@article{AF17,
+    title = {An explicit KO-degree map and applications},
+    author = {Asok, Aravind and Fasel, Jean},
+    doi = {10.1112/topo.12007},
+    volume = 10,
+    Issue = 1,
+    Year = 2017,
+    Pages = {268-300},
+    Journal = {J. Top.} }
+
+@article{Ste13,
+    author = {Stepanov, A.},
+    title = {Elementary calculus in Chevalley groups over rings},
+    journal = {J. Prime Res. Math.},
+    volume = {9},
+    year = {2013},
+    pages = {79--95},
+    url = {http://alexei.stepanov.spb.ru/papers/errors.pdf} }
+
+@article{Sch16,
+    author = {Schlichting, Marco},
+    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
+    year = 2017,
+    volume = 221,
+    Issue = 7,
+    Pages = {1729--1844},
+    Doi = {10.1016/j.jpaa.2016.12.026},
+    Journal = {J. Pure Appl. Alg.} }
+
+@article{FRS12,
+    title = {On stably free modules over affine algebras},
+    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
+    Volume = 116,
+    Issue = 1,
+    Pages = {223--243},
+    Year = 2012,
+    Journal = {Publ. Math. IH{\'E}S},
+    doi = {10.1007/s10240-012-0041-y} }
+
+@article{Lo78,
+    author = {Loday, Jean-Louis},
+    journal = {J. Alg.},
+    title = {Cohomologie et groupes de Steinberg relatifs},
+    year = {1978},
+    volume = {54},
+    number = {1},
+    doi = {10.1016/0021-8693(78)90025-X},
+    pages = {178--202} }
+
+@article{Pa89,
+    author = {Panin, Ivan},
+    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
+    journal = {Leningrad Math. J.},
+    year = {1990},
+    volume = {1},
+    number = {3},
+    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
+    pages = {741--754} }
+
+@article{Ka80,
+    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
+    author = {Karoubi, Max},
+    journal = {Ann. Math.},
+    volume = {112},
+    number = {2},
+    pages = {259--282},
+    year = {1980},
+    doi = {10.2307/1971147} }
+
+@article{Hur77,
+    author = {Hurrelbrink, J{\"u}rgen},
+    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
+    journal = {Math. Ann.},
+    volume = {225},
+    year = {1977},
+    number = {2},
+    pages = {123--129},
+    doi = {10.1007/BF01351716} }
+
+@online{Re75,
+    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
+    author = {Rehmann, Ulf},
+    year = {1975} }
+
+@article{MR91,
+    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
+    author = {Morita, Jun and Rehmann, Ulf},
+    journal = {Math. Z.},
+    volume = {206},
+    number = {1},
+    pages = {57--66},
+    year = {1991},
+    doi = {10.1007/BF02571324} }
+
+@article{VP,
+    year = {1996},
+    journal = {Acta Appl. Math.},
+    volume = {45},
+    issue = {1},
+    doi = {10.1007/BF00047884},
+    title = {Chevalley groups over commutative rings: I. Elementary calculations},
+    author = {Vavilov, Nikolai A. and Plotkin, E.},
+    pages = {73--113} }
+
+@article{St71,
+    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
+    author = {Stein, Michael R},
+    journal = {Amer. J. Math.},
+    volume = {93},
+    number = {4},
+    pages = {965--1004},
+    year = {1971},
+    doi = {10.2307/2373742} }
+
+@inproceedings{DS73,
+    title = {The functor $K_2$: A survey of computations and problems},
+    author = {Dennis, R Keith and Stein, Michael R},
+    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
+    pages = {241--303},
+    year = {1973},
+    publisher = {Springer},
+    doi = {10.1007/BFb0073728} }
+
+@article{Ho05,
+    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
+    author = {Hornbostel, Jens},
+    journal = {J. Top.},
+    volume = {44},
+    number = {3},
+    pages = {661--687},
+    year = {2005},
+    doi = {10.1016/j.top.2004.10.004} }
+
+@Article{V00,
+    title = {A third look at weight diagrams},
+    author = {Vavilov, Nikolai A.},
+    journal = {Rend. Sem. Mat. Univ. Padova},
+    year = {2000},
+    pages = {201--250},
+    volume = {104},
+    Url = {http://eudml.org/doc/108535} }
+
+@article{A13,
+    author = {Allcock, Daniel},
+    title = {Steinberg groups as amalgams},
+    journal = {Alg. Number Th.},
+    year = {2016},
+    volume = {10},
+    number = {8},
+    pages = {1791--1843},
+    doi = {10.2140/ant.2016.10.1791} }
+
+@article{Su82,
+    title = {Quadratic modules and the orthogonal group over polynomial rings},
+    author = {Suslin, A.~A. and Kopeiko, V.~I.},
+    journal = {J. Soviet Math.},
+    volume = {20},
+    number = {6},
+    pages = {2665--2691},
+    year = {1982},
+    doi = {10.1007/BF01681481} }
+
+@article{Va86,
+    author = {Vaserstein, L.},
+    title = {On normal subgroups of Chevalley groups over commutative rings},
+    journal = {Tohoku Math. J.},
+    volume = {38},
+    issue = {2},
+    pages = {219--230},
+    year = {1986},
+    doi = {10.2748/tmj/1178228489} }
+
+@online{VZ18,
+    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
+    title = {Generation of relative commutator subgroup in Chevalley groups, II},
+    archivePrefix = "arXiv",
+    eprint = "1811.11263",
+    primaryClass = "math.GR",
+    year = {2018} }
+
+@article{St-Ded,
+    author = {Stavrova, Anastasia},
+    title = {Chevalley groups of polynomial rings over Dedekind domains},
+    journal = {J. Gr. Th.},
+    volume = {23},
+    issue = {1},
+    doi = {10.1515/jgth-2019-0100},
+    year = {2020}}
+
+@article{Das17,
+    title = {$\mathbb{P}^1$-gluing for local complete intersections},
+    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
+    journal = {Math. Z.},
+    pages = {1--19},
+    year = {2017},
+    doi = {10.1007/s00209-019-02299-5} }
+
+@article{Su76,
+    title = {Projective modules over polynomial rings are free},
+    author = {Suslin, Andrei},
+    journal = {Dokl. Akad. nauk SSSR},
+    volume = {229},
+    pages = {1063--1066},
+    year = {1976},
+    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }
+
+@article{Qu76,
+    author = "Quillen, Daniel",
+    title = "Projective modules over polynomial rings",
+    journal = "Inv. Math.",
+    year = "1976",
+    volume = "36",
+    number = "1",
+    pages = "167--171",
+    doi = "10.1007/BF01390008" }
+
+@article{Ho64,
+    title = {Projective modules over an extension of a local ring},
+    author = {Horrocks, Geoffrey},
+    journal = {Proc. London Math. Soc.},
+    volume = {3},
+    number = {4},
+    pages = {714--718},
+    year = {1964},
+    doi = {10.1112/plms/s3-14.4.714} }
+
+@article{Mo04,
+    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
+    author = {Morel, Fabien},
+    journal = {Comm. Math. Helv.},
+    volume = {79},
+    number = {4},
+    pages = {689--703},
+    year = {2004},
+    publisher = {Springer},
+    doi = {10.1007/s00014-004-0815-z} }
+
+@article{St78,
+    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
+    author = {Stein, M.~R.},
+    journal = {Japan J. Math.},
+    volume = {4},
+    issue = {1},
+    year = {1978},
+    pages = {77--108},
+    doi = {10.4099/math1924.4.77} }
+
+@mastersthesis{Vo11,
+    author = {V{\"o}lkel, Konrad},
+    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
+    school = {Uni. Freiburg},
+    year = {2011},
+    type = {Diplomarbeit}}
+
+@article{Ba74,
+  title={Clifford algebras and spinor norms over a commutative ring},
+  author={Bass, Hyman},
+  journal={Amer. J. Math.},
+  volume={96},
+  number={1},
+  pages={156--206},
+  year={1974},
+  doi={10.2307/2373586}}
+
+@book{Bou81,
+  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
+  author={Bourbaki, Nicolas},
+  year={1981},
+  publisher={Masson}}
+
+@InProceedings{Ta86,
+  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
+  Author                   = {Taddei, Giovanni},
+  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
+  Year                     = {1986},
+  Pages                    = {693--710},
+  Series                   = {Contemp. Math},
+  Volume                   = {55},
+  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
+
+@article{La18,
+  title={A local-global principle for symplectic $K_2$},
+  author={Lavrenov, Andrei},
+  year={2018},
+  journal={Doc. Math.},
+  volume={23},
+  pages={653--675},
+  doi={10.25537/dm.2018v23.653-675}}
+\end{filecontents}
+
+\addbibresource{horrocks.bib}
 \renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
@@
 \Title
-A Horrocks-type theorem for even orthogonal $K_2$
+A Horrocks-type theorem for even orthogonal $\mathrm{K}_2$
 \ShortTitle 
@@
 \Author 
-Andrei Lavrenov, Sergey Sinchuk
+Andrei Lavrenov and Sergey Sinchuk
 \ShortAuthor 
-Lavrenov and Sinchuk
 \EndTitle
@@
 \KEY 
-Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
+Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
 \EndKEY
@@
 
-%%--------------------Here the manuscript ends--------------------------------
 \section{Introduction}
@@
 
-\begin{externaltheorem}[Stein] \label{thm:Stein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+\begin{externaltheorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
 \end{proof}
@@
 \item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
-\newline
-\scalebox{0.84}{\begin{minipage}{1.16\linewidth}
-\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
+\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = \hspace{4cm} \label{first-computation} \\ =
 [x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \nonumber \\ 
@@
  = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
- = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \label{first-computation} \end{align}\end{minipage}} \vskip \belowdisplayshortskip
+ = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
  where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.
@@
 \item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
-\newline \scalebox{0.85}{\begin{minipage}{1.16\linewidth}
-\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
+\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
+\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = \hspace{4cm} \\ = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
  = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
  = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}} where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
+ = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}}\vskip \belowdisplayshortskip
+where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
 \end{enumerate}
@@
 For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
-$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
+\[S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\]
 \end{lemma} \begin{proof} Suppose $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$.
@@
 
-\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has $j_R^{-1}(p_1) \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
+\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ one has 
+\[j_R^{-1}(p_1) \cdot [p, h, u] = [p_1p, h, u].\] \end{lemma}
 \begin{proof} 

### 2020-06-19 horrocks.tex
Move bibliography to the end of the paper

@@
 %%\usepackage{hyperref}
+
 % Append here commands \usepackage{...} if you want.
@@
 %
-\def\YEAR{\year}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
+\def\YEAR{2020}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
 \def\firstpage{1}\def\lastpage{1000}
-\def\received{}\def\revised{}
-\def\communicated{}
+\def\received{October 2, 2019}\def\revised{June 11, 2020}
+\def\communicated{Max Karoubi}
 %
@@
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
+\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage[breaklinks=false,unicode]{hyperref}
+\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
+\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
+\usepackage{color} 
+%\usepackage[breaklinks=false,unicode]{hyperref}
 \usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
@@
 \def\LOCAL{\horrocks.files}
-\begin{filecontents}{horrocks.bib}
-@Article{Abe83,
-    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
-    Author = {Abe, Eiichi},
-    Journal = {Comm. Alg.},
-    Year = {1983},
-    Number = {12},
-    Pages = {1271-1307},
-    Volume = {11},
-    Doi = {10.1080/00927878308822906} }
-
-@book{BHS11,
-    title = {Nonabelian algebraic topology},
-    author = {Brown, Ronald and Higgins, Philip J. and Sivera, Rafael},
-    series = {EMS Tracts in Mathematics},
-    volume = {15},
-    year = {2011} }
-
-@book{HOM,
-    Title = {The classical groups and $K$-theory},
-    Author = {Hahn, Alexander J. and O'Meara, Timothy},
-    Year = {1989},
-    Publisher = {Springer} }
-
-@Article{Ka77,
-    Title = {Another presentation for {S}teinberg groups},
-    Author = {Kallen, Wilberd van der},
-    Journal = {Indag. Math.},
-    Volume = {80},
-    Number = {4},
-    Pages = {304--312},
-    Year = {1977},
-    Doi = {10.1016/1385-7258(77)90026-9} }
-
-@Book{Lam10,
-    Title = {Serre's problem on projective modules},
-    Author = {Lam, Tsit-Yuen},
-    Publisher = {Springer Science \& Business Media},
-    Year = {2010},
-    Doi = {10.1007/978-3-540-34575-6} }
-
-@online{La15,
-    Title = {Local-global principle for symplectic $K_2$},
-    Author = {Lavrenov, Andrei},
-    Year = {2015} }
-
-@Article{LS17,
-    Title = {Centrality of odd orthogonal $K_2$},
-    Author = {Lavrenov, A. and Sinchuk, S.},
-    Journal = {J. Pure Appl. Alg.},
-    Volume = {221},
-    Year = {2017},
-    Pages = {1134--1145},
-    url = {https://arxiv.org/pdf/1606.00272.pdf} }
-
-@Inproceedings{RS76,
-    Title = {Finitely presented groups of matrices},
-    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
-    Booktitle = {Algebraic K-Theory},
-    Publisher = {Springer},
-    Year = {1976},
-    Pages = {164--169},
-    Series = {Lect. Notes. Math.},
-    Volume = {551},
-    Doi = {10.1007/BFb0079999} }
-
-@Article{S15,
-    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
-    Author = {Sinchuk, Sergey},
-    Journal = {J. Pure Appl. Alg.},
-    Year = {2016},
-    Number = {2},
-    Pages = {857--875},
-    Volume = {220},
-    Doi = {10.1016/j.jpaa.2015.08.003} }
-
-@Article{St-poly,
-    Title = {Homotopy invariance of non-stable $K_1$-functors},
-    Author = {Stavrova, Anastasia},
-    Journal = {J. K-th.},
-    Year = {2014},
-    Number = {2},
-    Pages = {199--248},
-    Volume = {13},
-    Doi = {10.1017/is013006012jkt232} }
-
-@Article{St-serr,
-    Title = {Non-stable $K_1$-functors of multiloop groups},
-    Author = {Stavrova, Anastasia},
-    Journal = {Canad. J. Math.},
-    Year = {2014},
-    Doi = {10.4153/CJM-2015-035-2} }
-
-@Book{St67,
-    Title = {Lectures on Chevalley groups},
-    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
-    Year = {1967},
-    Publisher = {Yale Univ. New Haven}}
-
-@Article{Ste73,
-    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
-    Author = {Stein, Michael R.},
-    Journal = {Trans. Amer. Math. Soc.},
-    Year = {1973},
-    Pages = {165--191},
-    Volume = {178},
-    Doi = {10.2307/1996696} }
-
-@Article{Su77,
-    Title = {On the structure of the special linear group over commutative rings},
-    Author = {Suslin, Andrei},
-    Journal = {Math. USSR Izv.},
-    Year = {1977},
-    Pages = {221--238},
-    Volume = {11},
-    Doi = {10.1070/IM1977v011n02ABEH001709} }
-
-@Article{Tu83,
-    Title = {The {S}teinberg group of a polynomial ring},
-    Author = {Tulenbaev, Marat},
-    Journal = {Math. USSR Sb.},
-    Year = {1983},
-    Pages = {131--144},
-    Volume = {45},
-    Doi = {10.1070/SM1983v045n01ABEH002591} }
-
-@Article{ST76,
-  author    = {Suslin, Andrei and Tulenbaev, Marat},
-  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
-  journal   = {J. Soviet Math.},
-  year      = {1981},
-  volume    = {17},
-  number    = {2},
-  pages     = {1804-1819},
-  doi       = {10.1007/BF01091768}}
-
-@Book{Kbook,
-    Title = {The $K$-book: An introduction to algebraic $K$-theory},
-    Author = {Weibel, Charles A},
-    Volume = {145},
-    Year = {2013},
-    Publisher = {Amer. Math. Soc.},
-    Series = {Grad. Texts Math.} }
-
-@Article{Vav09,
-    Title = {Weight elements of Chevalley groups},
-    Author = {Vavilov, Nikolai A.},
-    Journal = {St. Petersburg Math. J.},
-    Year = {2009},
-    Number = {1},
-    Pages = {23--57},
-    Volume = {20},
-    Doi = {10.1090/S1061-0022-08-01036-4} }
-
-@Article{We14,
-    Title = {On homology of linear groups over $k[t]$},
-    Author = {Wendt, Matthias},
-    Journal = {Math. Res. Lett.},
-    Year = {2014},
-    Number = {6},
-    Volume = {21},
-    Doi = {10.4310/MRL.2014.v21.n6.a15} }
-
-@Article{Ma69,
-    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
-    author = {Matsumoto, H.},
-    journal = {Ann. Sci. ENS},
-    year = {1969},
-    number = {1},
-    pages = {1--62},
-    volume = {2},
-    url = {http://eudml.org/doc/81843} }
-
-@article{AF17,
-    title = {An explicit KO-degree map and applications},
-    author = {Asok, Aravind and Fasel, Jean},
-    doi = {10.1112/topo.12007},
-    volume = 10,
-    Issue = 1,
-    Year = 2017,
-    Pages = {268-300},
-    Journal = {J. Top.} }
-
-@article{Ste13,
-    author = {Stepanov, A.},
-    title = {Elementary calculus in Chevalley groups over rings},
-    journal = {J. Prime Res. Math.},
-    volume = {9},
-    year = {2013},
-    pages = {79--95},
-    url = {http://alexei.stepanov.spb.ru/papers/errors.pdf} }
-
-@article{Sch16,
-    author = {Schlichting, Marco},
-    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
-    year = 2017,
-    volume = 221,
-    Issue = 7,
-    Pages = {1729--1844},
-    Doi = {10.1016/j.jpaa.2016.12.026},
-    Journal = {J. Pure Appl. Alg.} }
-
-@article{FRS12,
-    title = {On stably free modules over affine algebras},
-    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
-    Volume = 116,
-    Issue = 1,
-    Pages = {223--243},
-    Year = 2012,
-    Journal = {Publ. Math. IH{\'E}S},
-    doi = {10.1007/s10240-012-0041-y} }
-
-@article{Lo78,
-    author = {Loday, Jean-Louis},
-    journal = {J. Alg.},
-    title = {Cohomologie et groupes de Steinberg relatifs},
-    year = {1978},
-    volume = {54},
-    number = {1},
-    doi = {10.1016/0021-8693(78)90025-X},
-    pages = {178--202} }
-
-@article{Pa89,
-    author = {Panin, Ivan},
-    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
-    journal = {Leningrad Math. J.},
-    year = {1990},
-    volume = {1},
-    number = {3},
-    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
-    pages = {741--754} }
-
-@article{Ka80,
-    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
-    author = {Karoubi, Max},
-    journal = {Ann. Math.},
-    volume = {112},
-    number = {2},
-    pages = {259--282},
-    year = {1980},
-    doi = {10.2307/1971147} }
-
-@article{Hur77,
-    author = {Hurrelbrink, J{\"u}rgen},
-    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
-    journal = {Math. Ann.},
-    volume = {225},
-    year = {1977},
-    number = {2},
-    pages = {123--129},
-    doi = {10.1007/BF01351716} }
-
-@online{Re75,
-    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
-    author = {Rehmann, Ulf},
-    year = {1975} }
-
-@article{MR91,
-    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
-    author = {Morita, Jun and Rehmann, Ulf},
-    journal = {Math. Z.},
-    volume = {206},
-    number = {1},
-    pages = {57--66},
-    year = {1991},
-    doi = {10.1007/BF02571324} }
-
-@article{VP,
-    year = {1996},
-    journal = {Acta Appl. Math.},
-    volume = {45},
-    issue = {1},
-    doi = {10.1007/BF00047884},
-    title = {Chevalley groups over commutative rings: I. Elementary calculations},
-    author = {Vavilov, Nikolai A. and Plotkin, E.},
-    pages = {73--113} }
-
-@article{St71,
-    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
-    author = {Stein, Michael R},
-    journal = {Amer. J. Math.},
-    volume = {93},
-    number = {4},
-    pages = {965--1004},
-    year = {1971},
-    doi = {10.2307/2373742} }
-
-@inproceedings{DS73,
-    title = {The functor $K_2$: A survey of computations and problems},
-    author = {Dennis, R Keith and Stein, Michael R},
-    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
-    pages = {241--303},
-    year = {1973},
-    publisher = {Springer},
-    doi = {10.1007/BFb0073728} }
-
-@article{Ho05,
-    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
-    author = {Hornbostel, Jens},
-    journal = {J. Top.},
-    volume = {44},
-    number = {3},
-    pages = {661--687},
-    year = {2005},
-    doi = {10.1016/j.top.2004.10.004} }
-
-@Article{V00,
-    title = {A third look at weight diagrams},
-    author = {Vavilov, Nikolai A.},
-    journal = {Rend. Sem. Mat. Univ. Padova},
-    year = {2000},
-    pages = {201--250},
-    volume = {104},
-    Url = {http://eudml.org/doc/108535} }
-
-@article{A13,
-    author = {Allcock, Daniel},
-    title = {Steinberg groups as amalgams},
-    journal = {Alg. Number Th.},
-    year = {2016},
-    volume = {10},
-    number = {8},
-    pages = {1791--1843},
-    doi = {10.2140/ant.2016.10.1791} }
-
-@article{Su82,
-    title = {Quadratic modules and the orthogonal group over polynomial rings},
-    author = {Suslin, A.~A. and Kopeiko, V.~I.},
-    journal = {J. Soviet Math.},
-    volume = {20},
-    number = {6},
-    pages = {2665--2691},
-    year = {1982},
-    doi = {10.1007/BF01681481} }
-
-@article{Va86,
-    author = {Vaserstein, L.},
-    title = {On normal subgroups of Chevalley groups over commutative rings},
-    journal = {Tohoku Math. J.},
-    volume = {38},
-    issue = {2},
-    pages = {219--230},
-    year = {1986},
-    doi = {10.2748/tmj/1178228489} }
-
-@online{VZ18,
-    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
-    title = {Generation of relative commutator subgroup in Chevalley groups, II},
-    archivePrefix = "arXiv",
-    eprint = "1811.11263",
-    primaryClass = "math.GR",
-    year = {2018} }
-
-@article{St-Ded,
-    author = {Stavrova, Anastasia},
-    title = {Chevalley groups of polynomial rings over Dedekind domains},
-    journal = {J. Gr. Th.},
-    volume = {23},
-    issue = {1},
-    doi = {10.1515/jgth-2019-0100},
-    year = {2020}}
-
-@article{Das17,
-    title = {$\mathbb{P}^1$-gluing for local complete intersections},
-    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
-    journal = {Math. Z.},
-    pages = {1--19},
-    year = {2017},
-    doi = {10.1007/s00209-019-02299-5} }
-
-@article{Su76,
-    title = {Projective modules over polynomial rings are free},
-    author = {Suslin, Andrei},
-    journal = {Dokl. Akad. nauk SSSR},
-    volume = {229},
-    pages = {1063--1066},
-    year = {1976},
-    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }
-
-@article{Qu76,
-    author = "Quillen, Daniel",
-    title = "Projective modules over polynomial rings",
-    journal = "Inv. Math.",
-    year = "1976",
-    volume = "36",
-    number = "1",
-    pages = "167--171",
-    doi = "10.1007/BF01390008" }
-
-@article{Ho64,
-    title = {Projective modules over an extension of a local ring},
-    author = {Horrocks, Geoffrey},
-    journal = {Proc. London Math. Soc.},
-    volume = {3},
-    number = {4},
-    pages = {714--718},
-    year = {1964},
-    doi = {10.1112/plms/s3-14.4.714} }
-
-@article{Mo04,
-    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
-    author = {Morel, Fabien},
-    journal = {Comm. Math. Helv.},
-    volume = {79},
-    number = {4},
-    pages = {689--703},
-    year = {2004},
-    publisher = {Springer},
-    doi = {10.1007/s00014-004-0815-z} }
-
-@article{St78,
-    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
-    author = {Stein, M.~R.},
-    journal = {Japan J. Math.},
-    volume = {4},
-    issue = {1},
-    year = {1978},
-    pages = {77--108},
-    doi = {10.4099/math1924.4.77} }
-
-@mastersthesis{Vo11,
-    author = {V{\"o}lkel, Konrad},
-    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
-    school = {Uni. Freiburg},
-    year = {2011},
-    type = {Diplomarbeit}}
-
-@article{Ba74,
-  title={Clifford algebras and spinor norms over a commutative ring},
-  author={Bass, Hyman},
-  journal={Amer. J. Math.},
-  volume={96},
-  number={1},
-  pages={156--206},
-  year={1974},
-  doi={10.2307/2373586}}
-
-@book{Bou81,
-  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
-  author={Bourbaki, Nicolas},
-  year={1981},
-  publisher={Masson}}
-
-@InProceedings{Ta86,
-  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
-  Author                   = {Taddei, Giovanni},
-  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
-  Year                     = {1986},
-  Pages                    = {693--710},
-  Series                   = {Contemp. Math},
-  Volume                   = {55},
-  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
-
-@article{La18,
-  title={A local-global principle for symplectic $K_2$},
-  author={Lavrenov, Andrei},
-  year={2018},
-  journal={Doc. Math.},
-  volume={23},
-  pages={653--675},
-  doi={10.25537/dm.2018v23.653-675}}
-\end{filecontents}
 
@@
      {\par\narrower\noindent%
-     2010 Mathematics Subject Classification: #1\par}\fi}
+     2020 Mathematics Subject Classification: #1\par}\fi}
 
@@
 \Title
-A Horrocks-type theorem for even orthogonal $\mathrm{K}_2$
+A Horrocks-Type Theorem for Even Orthogonal $\mathrm{K}_2$
 \ShortTitle 
-A Horrocks-type theorem for $\mathrm{KO}_2$ 
+A Horrocks-Type Theorem for $\mathrm{KO}_2$ 
 \SubTitle   
@@
 \ShortAuthor 
+A. Lavrenov, S. Sinchuk
 \EndTitle
@@
 \KEY 
-Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
+Steinberg group, $\mathrm{K}_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing
 \EndKEY
@@
 Andrei Lavrenov
+Chebyshev Laboratory 
+St. Petersburg State University 
+14th. Line V.O. 29b
+199178, St. Petersburg
+Russia
 avlavrenov@gmail.com
@@
 Sergey Sinchuk
+Chebyshev Laboratory 
+St. Petersburg State University 
+14th. Line V.O. 29b
+199178, St. Petersburg
+Russia
 sinchukss@gmail.com
 \Address
-Chebyshev laboratory, 
-St. Petersburg State University, 
-14th. Line V.O. 29b
-199178, St. Petersburg, Russia
 \Address
@@
 \Addresses
+\begin{filecontents}{horrocks.bib}
+@Article{Abe83,
+    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
+    Author = {Abe, Eiichi},
+    Journal = {Comm. Alg.},
+    Year = {1983},
+    Number = {12},
+    Pages = {1271-1307},
+    Volume = {11},
+    Doi = {10.1080/00927878308822906} }
+
+@book{BHS11,
+    title = {Nonabelian algebraic topology},
+    author = {Brown, Ronald and Higgins, Philip J. and Sivera, Rafael},
+    series = {EMS Tracts in Mathematics},
+    volume = {15},
+    year = {2011} }
+
+@book{HOM,
+    Title = {The classical groups and $K$-theory},
+    Author = {Hahn, Alexander J. and O'Meara, Timothy},
+    Year = {1989},
+    Publisher = {Springer} }
+
+@Article{Ka77,
+    Title = {Another presentation for {S}teinberg groups},
+    Author = {Kallen, Wilberd van der},
+    Journal = {Indag. Math.},
+    Volume = {80},
+    Number = {4},
+    Pages = {304--312},
+    Year = {1977},
+    Doi = {10.1016/1385-7258(77)90026-9} }
+
+@Book{Lam10,
+    Title = {Serre's problem on projective modules},
+    Author = {Lam, Tsit-Yuen},
+    Publisher = {Springer Science \& Business Media},
+    Year = {2010},
+    Doi = {10.1007/978-3-540-34575-6} }
+
+@online{La15,
+    Title = {Local-global principle for symplectic $K_2$},
+    Author = {Lavrenov, Andrei},
+    Year = {2015} }
+
+@Article{LS17,
+    Title = {Centrality of odd orthogonal $K_2$},
+    Author = {Lavrenov, A. and Sinchuk, S.},
+    Journal = {J. Pure Appl. Alg.},
+    Volume = {221},
+    Year = {2017},
+    Pages = {1134--1145},
+    url = {https://arxiv.org/pdf/1606.00272.pdf} }
+
+@Inproceedings{RS76,
+    Title = {Finitely presented groups of matrices},
+    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
+    Booktitle = {Algebraic K-Theory},
+    Publisher = {Springer},
+    Year = {1976},
+    Pages = {164--169},
+    Series = {Lect. Notes. Math.},
+    Volume = {551},
+    Doi = {10.1007/BFb0079999} }
+
+@Article{S15,
+    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
+    Author = {Sinchuk, Sergey},
+    Journal = {J. Pure Appl. Alg.},
+    Year = {2016},
+    Number = {2},
+    Pages = {857--875},
+    Volume = {220},
+    Doi = {10.1016/j.jpaa.2015.08.003} }
+
+@Article{St-poly,
+    Title = {Homotopy invariance of non-stable $K_1$-functors},
+    Author = {Stavrova, Anastasia},
+    Journal = {J. K-th.},
+    Year = {2014},
+    Number = {2},
+    Pages = {199--248},
+    Volume = {13},
+    Doi = {10.1017/is013006012jkt232} }
+
+@Article{St-serr,
+    Title = {Non-stable $K_1$-functors of multiloop groups},
+    Author = {Stavrova, Anastasia},
+    Journal = {Canad. J. Math.},
+    Year = {2014},
+    Doi = {10.4153/CJM-2015-035-2} }
+
+@Book{St67,
+    Title = {Lectures on Chevalley groups},
+    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
+    Year = {1967},
+    Publisher = {Yale Univ. New Haven}}
+
+@Article{Ste73,
+    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
+    Author = {Stein, Michael R.},
+    Journal = {Trans. Amer. Math. Soc.},
+    Year = {1973},
+    Pages = {165--191},
+    Volume = {178},
+    Doi = {10.2307/1996696} }
+
+@Article{Su77,
+    Title = {On the structure of the special linear group over commutative rings},
+    Author = {Suslin, Andrei},
+    Journal = {Math. USSR Izv.},
+    Year = {1977},
+    Pages = {221--238},
+    Volume = {11},
+    Doi = {10.1070/IM1977v011n02ABEH001709} }
+
+@Article{Tu83,
+    Title = {The {S}teinberg group of a polynomial ring},
+    Author = {Tulenbaev, Marat},
+    Journal = {Math. USSR Sb.},
+    Year = {1983},
+    Pages = {131--144},
+    Volume = {45},
+    Doi = {10.1070/SM1983v045n01ABEH002591} }
+
+@Article{ST76,
+  author    = {Suslin, Andrei and Tulenbaev, Marat},
+  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
+  journal   = {J. Soviet Math.},
+  year      = {1981},
+  volume    = {17},
+  number    = {2},
+  pages     = {1804-1819},
+  doi       = {10.1007/BF01091768}}
+
+@Book{Kbook,
+    Title = {The $K$-book: An introduction to algebraic $K$-theory},
+    Author = {Weibel, Charles A},
+    Volume = {145},
+    Year = {2013},
+    Publisher = {Amer. Math. Soc.},
+    Series = {Grad. Texts Math.} }
+
+@Article{Vav09,
+    Title = {Weight elements of Chevalley groups},
+    Author = {Vavilov, Nikolai A.},
+    Journal = {St. Petersburg Math. J.},
+    Year = {2009},
+    Number = {1},
+    Pages = {23--57},
+    Volume = {20},
+    Doi = {10.1090/S1061-0022-08-01036-4} }
+
+@Article{We14,
+    Title = {On homology of linear groups over $k[t]$},
+    Author = {Wendt, Matthias},
+    Journal = {Math. Res. Lett.},
+    Year = {2014},
+    Number = {6},
+    Volume = {21},
+    Doi = {10.4310/MRL.2014.v21.n6.a15} }
+
+@Article{Ma69,
+    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
+    author = {Matsumoto, H.},
+    journal = {Ann. Sci. ENS},
+    year = {1969},
+    number = {1},
+    pages = {1--62},
+    volume = {2},
+    url = {http://eudml.org/doc/81843} }
+
+@article{AF17,
+    title = {An explicit KO-degree map and applications},
+    author = {Asok, Aravind and Fasel, Jean},
+    doi = {10.1112/topo.12007},
+    volume = 10,
+    Issue = 1,
+    Year = 2017,
+    Pages = {268-300},
+    Journal = {J. Top.} }
+
+@article{Ste13,
+    author = {Stepanov, A.},
+    title = {Elementary calculus in Chevalley groups over rings},
+    journal = {J. Prime Res. Math.},
+    volume = {9},
+    year = {2013},
+    pages = {79--95},
+    url = {http://alexei.stepanov.spb.ru/papers/errors.pdf} }
+
+@article{Sch16,
+    author = {Schlichting, Marco},
+    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
+    year = 2017,
+    volume = 221,
+    Issue = 7,
+    Pages = {1729--1844},
+    Doi = {10.1016/j.jpaa.2016.12.026},
+    Journal = {J. Pure Appl. Alg.} }
+
+@article{FRS12,
+    title = {On stably free modules over affine algebras},
+    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
+    Volume = 116,
+    Issue = 1,
+    Pages = {223--243},
+    Year = 2012,
+    Journal = {Publ. Math. IH{\'E}S},
+    doi = {10.1007/s10240-012-0041-y} }
+
+@article{Lo78,
+    author = {Loday, Jean-Louis},
+    journal = {J. Alg.},
+    title = {Cohomologie et groupes de Steinberg relatifs},
+    year = {1978},
+    volume = {54},
+    number = {1},
+    doi = {10.1016/0021-8693(78)90025-X},
+    pages = {178--202} }
+
+@article{Pa89,
+    author = {Panin, Ivan},
+    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
+    journal = {Leningrad Math. J.},
+    year = {1990},
+    volume = {1},
+    number = {3},
+    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
+    pages = {741--754} }
+
+@article{Ka80,
+    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
+    author = {Karoubi, Max},
+    journal = {Ann. Math.},
+    volume = {112},
+    number = {2},
+    pages = {259--282},
+    year = {1980},
+    doi = {10.2307/1971147} }
+
+@article{Hur77,
+    author = {Hurrelbrink, J{\"u}rgen},
+    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
+    journal = {Math. Ann.},
+    volume = {225},
+    year = {1977},
+    number = {2},
+    pages = {123--129},
+    doi = {10.1007/BF01351716} }
+
+@online{Re75,
+    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
+    author = {Rehmann, Ulf},
+    year = {1975} }
+
+@article{MR91,
+    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
+    author = {Morita, Jun and Rehmann, Ulf},
+    journal = {Math. Z.},
+    volume = {206},
+    number = {1},
+    pages = {57--66},
+    year = {1991},
+    doi = {10.1007/BF02571324} }
+
+@article{VP,
+    year = {1996},
+    journal = {Acta Appl. Math.},
+    volume = {45},
+    issue = {1},
+    doi = {10.1007/BF00047884},
+    title = {Chevalley groups over commutative rings: I. Elementary calculations},
+    author = {Vavilov, Nikolai A. and Plotkin, E.},
+    pages = {73--113} }
+
+@article{St71,
+    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
+    author = {Stein, Michael R},
+    journal = {Amer. J. Math.},
+    volume = {93},
+    number = {4},
+    pages = {965--1004},
+    year = {1971},
+    doi = {10.2307/2373742} }
+
+@inproceedings{DS73,
+    title = {The functor $K_2$: A survey of computations and problems},
+    author = {Dennis, R Keith and Stein, Michael R},
+    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
+    pages = {241--303},
+    year = {1973},
+    publisher = {Springer},
+    doi = {10.1007/BFb0073728} }
+
+@article{Ho05,
+    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
+    author = {Hornbostel, Jens},
+    journal = {J. Top.},
+    volume = {44},
+    number = {3},
+    pages = {661--687},
+    year = {2005},
+    doi = {10.1016/j.top.2004.10.004} }
+
+@Article{V00,
+    title = {A third look at weight diagrams},
+    author = {Vavilov, Nikolai A.},
+    journal = {Rend. Sem. Mat. Univ. Padova},
+    year = {2000},
+    pages = {201--250},
+    volume = {104},
+    Url = {http://eudml.org/doc/108535} }
+
+@article{A13,
+    author = {Allcock, Daniel},
+    title = {Steinberg groups as amalgams},
+    journal = {Alg. Number Th.},
+    year = {2016},
+    volume = {10},
+    number = {8},
+    pages = {1791--1843},
+    doi = {10.2140/ant.2016.10.1791} }
+
+@article{Su82,
+    title = {Quadratic modules and the orthogonal group over polynomial rings},
+    author = {Suslin, A.~A. and Kopeiko, V.~I.},
+    journal = {J. Soviet Math.},
+    volume = {20},
+    number = {6},
+    pages = {2665--2691},
+    year = {1982},
+    doi = {10.1007/BF01681481} }
+
+@article{Va86,
+    author = {Vaserstein, L.},
+    title = {On normal subgroups of Chevalley groups over commutative rings},
+    journal = {Tohoku Math. J.},
+    volume = {38},
+    issue = {2},
+    pages = {219--230},
+    year = {1986},
+    doi = {10.2748/tmj/1178228489} }
+
+@online{VZ18,
+    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
+    title = {Generation of relative commutator subgroup in Chevalley groups, II},
+    archivePrefix = "arXiv",
+    eprint = "1811.11263",
+    primaryClass = "math.GR",
+    year = {2018} }
+
+@article{St-Ded,
+    author = {Stavrova, Anastasia},
+    title = {Chevalley groups of polynomial rings over Dedekind domains},
+    journal = {J. Gr. Th.},
+    volume = {23},
+    issue = {1},
+    doi = {10.1515/jgth-2019-0100},
+    year = {2020}}
+
+@article{Das17,
+    title = {$\mathbb{P}^1$-gluing for local complete intersections},
+    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
+    journal = {Math. Z.},
+    pages = {1--19},
+    year = {2017},
+    doi = {10.1007/s00209-019-02299-5} }
+
+@article{Su76,
+    title = {Projective modules over polynomial rings are free},
+    author = {Suslin, Andrei},
+    journal = {Dokl. Akad. nauk SSSR},
+    volume = {229},
+    pages = {1063--1066},
+    year = {1976},
+    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }
+
+@article{Qu76,
+    author = "Quillen, Daniel",
+    title = "Projective modules over polynomial rings",
+    journal = "Inv. Math.",
+    year = "1976",
+    volume = "36",
+    number = "1",
+    pages = "167--171",
+    doi = "10.1007/BF01390008" }
+
+@article{Ho64,
+    title = {Projective modules over an extension of a local ring},
+    author = {Horrocks, Geoffrey},
+    journal = {Proc. London Math. Soc.},
+    volume = {3},
+    number = {4},
+    pages = {714--718},
+    year = {1964},
+    doi = {10.1112/plms/s3-14.4.714} }
+
+@article{Mo04,
+    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
+    author = {Morel, Fabien},
+    journal = {Comm. Math. Helv.},
+    volume = {79},
+    number = {4},
+    pages = {689--703},
+    year = {2004},
+    publisher = {Springer},
+    doi = {10.1007/s00014-004-0815-z} }
+
+@article{St78,
+    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
+    author = {Stein, M.~R.},
+    journal = {Japan J. Math.},
+    volume = {4},
+    issue = {1},
+    year = {1978},
+    pages = {77--108},
+    doi = {10.4099/math1924.4.77} }
+
+@mastersthesis{Vo11,
+    author = {V{\"o}lkel, Konrad},
+    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
+    school = {Uni. Freiburg},
+    year = {2011},
+    type = {Diplomarbeit}}
+
+@article{Ba74,
+  title={Clifford algebras and spinor norms over a commutative ring},
+  author={Bass, Hyman},
+  journal={Amer. J. Math.},
+  volume={96},
+  number={1},
+  pages={156--206},
+  year={1974},
+  doi={10.2307/2373586}}
+
+@book{Bou81,
+  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
+  author={Bourbaki, Nicolas},
+  year={1981},
+  publisher={Masson}}
+
+@InProceedings{Ta86,
+  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
+  Author                   = {Taddei, Giovanni},
+  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
+  Year                     = {1986},
+  Pages                    = {693--710},
+  Series                   = {Contemp. Math},
+  Volume                   = {55},
+  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
+
+@article{La18,
+  title={A local-global principle for symplectic $K_2$},
+  author={Lavrenov, Andrei},
+  year={2018},
+  journal={Doc. Math.},
+  volume={23},
+  pages={653--675},
+  doi={10.25537/dm.2018v23.653-675}}
+\end{filecontents}
 \end{document}

### 2020-06-19 horrocks.tex
remove unused bibliography

@@
 
-@book{BHS11,
-    title = {Nonabelian algebraic topology},
-    author = {Brown, Ronald and Higgins, Philip J. and Sivera, Rafael},
-    series = {EMS Tracts in Mathematics},
-    volume = {15},
-    year = {2011} }
-
-@book{HOM,
-    Title = {The classical groups and $K$-theory},
-    Author = {Hahn, Alexander J. and O'Meara, Timothy},
-    Year = {1989},
-    Publisher = {Springer} }
-
 @Article{Ka77,
@@
     Doi = {10.1007/978-3-540-34575-6} }
-
-@online{La15,
-    Title = {Local-global principle for symplectic $K_2$},
-    Author = {Lavrenov, Andrei},
-    Year = {2015} }
 
@@
 
-@article{Ste13,
-    author = {Stepanov, A.},
-    title = {Elementary calculus in Chevalley groups over rings},
-    journal = {J. Prime Res. Math.},
-    volume = {9},
-    year = {2013},
-    pages = {79--95},
-    url = {http://alexei.stepanov.spb.ru/papers/errors.pdf} }
-
 @article{Sch16,

### 2020-06-30 horrocks.tex
Beautify bibliography

@@
  \item a group $M$ with a left action of $N$ (we call such a group an $N$-group and use the notation ${}^n m$ to denote the image of an element $m\in M$ under the action of $n \in N$);
- \item a homomorphism $\mu \colon M\to N$ preserving the action of $N$-groups and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
+ \item a homomorphism $\mu \colon M\to N$ preserving the action of $N$ and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
 \end{enumerate}
@@
 @Article{Abe83,
+    Author    = {Abe, Eiichi},
     Title     = {Whitehead groups of {C}hevalley groups over polynomial rings},    
-    Author = {Abe, Eiichi},
     Journal   = {Comm. Alg.},    
-    Year = {1983},
-    Number = {12},
-    Pages = {1271-1307},
-    Volume = {11},
-    Doi = {10.1080/00927878308822906} }
-
-@Article{Ka77,
-    Title = {Another presentation for {S}teinberg groups},
-    Author = {Kallen, Wilberd van der},
-    Journal = {Indag. Math.},
-    Volume = {80},
-    Number = {4},
-    Pages = {304--312},
-    Year = {1977},
-    Doi = {10.1016/1385-7258(77)90026-9} }
+    Number    = 12,
+    Volume    = 11,
+    Pages     = {1271--1307},
+    Year      = 1983,    
+    Doi       = {10.1080/00927878308822906}}
+
+@Article{A13,
+    Author    = {Allcock, Daniel},
+    Title     = {Steinberg groups as amalgams},
+    Journal   = {Alg. Number Th.},    
+    Volume    = 10,
+    Number    = 8,
+    Pages     = {1791--1843},
+    Year      = 2016,
+    Doi       = {10.2140/ant.2016.10.1791}}
+
+@Article{AF17,
+    Author    = {Asok, Aravind and Fasel, Jean},
+    Title     = {An explicit KO-degree map and applications},    
+    Journal   = {J. Top.},
+    Volume    = 10,
+    Issue     = 1,
+    Pages     = {268--300},
+    Year      = 2017,    
+    Doi       = {10.1112/topo.12007}}
+
+@Article{Ba74,
+    Author    = {Bass, Hyman},
+    Title     = {Clifford algebras and spinor norms over a commutative ring},    
+    Journal   = {Amer. J. Math.},
+    Volume    = 96,
+    Number    = 1,
+    Pages     = {156--206},
+    Year      = 1974,
+    Doi       = {10.2307/2373586}}
+
+@Book{Bou81,
+    Author    = {Bourbaki, Nicolas},
+    Title     = {Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
+    Publisher = {Masson},
+    Year      = 1981}
+
+@Inproceedings{DS73,
+    Author    = {Dennis, R. Keith and Stein, Michael R.},
+    Title     = {The functor $K_2$: A survey of computations and problems},    
+    Booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
+    Publisher = {Springer},
+    Pages     = {241--303},
+    Year      = 1973,
+    Doi       = {10.1007/BFb0073728}}
+
+@Article{FRS12,
+    Author    = {Fasel, Jean and Rao, Ravi and Swan, Richard},
+    Title     = {On stably free modules over affine algebras},
+    Journal   = {Publ. Math. IH{\'E}S},
+    Volume    = 116,
+    Issue     = 1,
+    Pages     = {223--243},
+    Year      = 2012,
+    Doi       = {10.1007/s10240-012-0041-y}}
+
+@Article{Ho05,
+    Author    = {Hornbostel, Jens},
+    Title     = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},    
+    Journal   = {J. Top.},
+    Volume    = 44,
+    Number    = 3,
+    Pages     = {661--687},
+    Year      = 2005,
+    Doi       = {10.1016/j.top.2004.10.004}}
+
+@Article{Ho64,
+    Author    = {Horrocks, Geoffrey},
+    Title     = {Projective modules over an extension of a local ring},    
+    Journal   = {Proc. London Math. Soc.},
+    Volume    = 3,
+    Number    = 4,
+    Pages     = {714--718},
+    Year      = 1964,
+    Doi       = {10.1112/plms/s3-14.4.714}}
+
+@Article{Hur77,
+    Author    = {Hurrelbrink, J{\"u}rgen},
+    Title     = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
+    Journal   = {Math. Ann.},
+    Volume    = 225,    
+    Number    = 2,
+    Pages     = {123--129},
+    Year      = 1977,
+    Doi       = {10.1007/BF01351716}}
+
+@Article{Ka80,
+    Author    = {Karoubi, Max},
+    Title     = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},    
+    Journal   = {Ann. Math.},
+    Volume    = 112,
+    Number    = 2,
+    Pages     = {259--282},
+    Year      = 1980,
+    Doi       = {10.2307/1971147}}
 
@@
     Year      = {2010},
-    Doi = {10.1007/978-3-540-34575-6} }
+    Doi       = {10.1007/978-3-540-34575-6}}
 
 @Article{LS17,
+    Author    = {Lavrenov, Andrei and Sinchuk, Sergey},
     Title     = {Centrality of odd orthogonal $K_2$},    
-    Author = {Lavrenov, A. and Sinchuk, S.},
     Journal   = {J. Pure Appl. Alg.},
-    Volume = {221},
-    Year = {2017},
+    Volume    = 221,
     Pages     = {1134--1145},
-    url = {https://arxiv.org/pdf/1606.00272.pdf} }
+    Year      = 2017,    
+    Url       = {https://arxiv.org/pdf/1606.00272.pdf}}
+
+@Article{La18,
+    Author    = {Lavrenov, Andrei},
+    Title     = {A local-global principle for symplectic $K_2$},    
+    Journal   = {Doc. Math.},    
+    Volume    = 23,
+    Pages     = {653--675},
+    Year      = 2018,
+    Doi       = {10.25537/dm.2018v23.653-675}}
+
+@Article{Lo78,
+    Author    = {Loday, Jean-Louis},
+    Title     = {Cohomologie et groupes de Steinberg relatifs},
+    Journal   = {J. Alg.},    
+    Volume    = 54,
+    Number    = 1,
+    Pages     = {178--202},
+    Year      = 1978,
+    Doi       = {10.1016/0021-8693(78)90025-X}}
+
+@Article{Ma69,
+    Author    = {Matsumoto, Hideya},
+    Title     = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},    
+    Journal   = {Ann. Sci. ENS},
+    Volume    = 2,
+    Number    = 1,
+    Pages     = {1--62},
+    Year      = 1969,
+    Url       = {http://eudml.org/doc/81843}}
+
+@Article{Mo04,
+    Author    = {Morel, Fabien},
+    Title     = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},    
+    Journal   = {Comm. Math. Helv.},
+    Volume    = 79,
+    Number    = 4,
+    Pages     = {689--703},
+    Year      = 2004,
+    Doi       = {10.1007/s00014-004-0815-z}}
+
+@Article{MR91,
+    Author    = {Morita, Jun and Rehmann, Ulf},
+    Title     = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},    
+    Journal   = {Math. Z.},
+    Volume    = 206,
+    Number    = 1,
+    Pages     = {57--66},
+    Year      = 1991,
+    Doi       = {10.1007/BF02571324}}
+
+@Article{Pa89,
+    Author    = {Panin, Ivan},
+    Title     = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
+    Journal   = {Leningrad Math. J.},    
+    Volume    = 1,
+    Number    = 3,
+    Pages     = {741--754},
+    Year      = 1990,
+    Url       = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf}}
+
+@Article{Qu76,
+    Author    = {Quillen, Daniel},
+    Title     = {Projective modules over polynomial rings},
+    Journal   = {Inv. Math.},    
+    Volume    = 36,
+    Number    = 1,
+    Pages     = {167--171},
+    Year      = 1976,
+    Doi       = {10.1007/BF01390008}}
+
+@Article{Re75,
+    Author    = {Rehmann, Ulf},
+    Title     = {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$},    
+    Year      = {1975},
+    Url       = {http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}}
 
 @Inproceedings{RS76,
+    Author    = {Rehmann, Ulf and Soul{\'e} , Christophe},
     Title     = {Finitely presented groups of matrices},    
-    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
     Booktitle = {Algebraic K-Theory},
     Publisher = {Springer},        
-    Year = {1976},
+    Series    = {Lect. Notes. Math.},
+    Volume    = 551,
     Pages     = {164--169},
-    Series = {Lect. Notes. Math.},
-    Volume = {551},
-    Doi = {10.1007/BFb0079999} }
-
-@Article{S15,
-    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
-    Author = {Sinchuk, Sergey},
+    Year      = 1976,
+    Doi       = {10.1007/BFb0079999}}
+
+@Article{Sch16,
+    Author    = {Schlichting, Marco},
+    Title     = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
     Journal   = {J. Pure Appl. Alg.},    
-    Year = {2016},
-    Number = {2},
-    Pages = {857--875},
-    Volume = {220},
-    Doi = {10.1016/j.jpaa.2015.08.003} }
-
-@Article{St-poly,
-    Title = {Homotopy invariance of non-stable $K_1$-functors},
-    Author = {Stavrova, Anastasia},
-    Journal = {J. K-th.},
-    Year = {2014},
-    Number = {2},
-    Pages = {199--248},
-    Volume = {13},
-    Doi = {10.1017/is013006012jkt232} }
-
-@Article{St-serr,
-    Title = {Non-stable $K_1$-functors of multiloop groups},
-    Author = {Stavrova, Anastasia},
-    Journal = {Canad. J. Math.},
-    Year = {2014},
-    Doi = {10.4153/CJM-2015-035-2} }
-
-@Book{St67,
-    Title = {Lectures on Chevalley groups},
-    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
-    Year = {1967},
-    Publisher = {Yale Univ. New Haven}}
-
-@Article{Ste73,
-    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
-    Author = {Stein, Michael R.},
-    Journal = {Trans. Amer. Math. Soc.},
-    Year = {1973},
-    Pages = {165--191},
-    Volume = {178},
-    Doi = {10.2307/1996696} }
-
-@Article{Su77,
-    Title = {On the structure of the special linear group over commutative rings},
-    Author = {Suslin, Andrei},
-    Journal = {Math. USSR Izv.},
-    Year = {1977},
-    Pages = {221--238},
-    Volume = {11},
-    Doi = {10.1070/IM1977v011n02ABEH001709} }
-
-@Article{Tu83,
-    Title = {The {S}teinberg group of a polynomial ring},
-    Author = {Tulenbaev, Marat},
-    Journal = {Math. USSR Sb.},
-    Year = {1983},
-    Pages = {131--144},
-    Volume = {45},
-    Doi = {10.1070/SM1983v045n01ABEH002591} }
-
-@Article{ST76,
-  author    = {Suslin, Andrei and Tulenbaev, Marat},
-  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
-  journal   = {J. Soviet Math.},
-  year      = {1981},
-  volume    = {17},
-  number    = {2},
-  pages     = {1804-1819},
-  doi       = {10.1007/BF01091768}}
-
-@Book{Kbook,
-    Title = {The $K$-book: An introduction to algebraic $K$-theory},
-    Author = {Weibel, Charles A},
-    Volume = {145},
-    Year = {2013},
-    Publisher = {Amer. Math. Soc.},
-    Series = {Grad. Texts Math.} }
-
-@Article{Vav09,
-    Title = {Weight elements of Chevalley groups},
-    Author = {Vavilov, Nikolai A.},
-    Journal = {St. Petersburg Math. J.},
-    Year = {2009},
-    Number = {1},
-    Pages = {23--57},
-    Volume = {20},
-    Doi = {10.1090/S1061-0022-08-01036-4} }
-
-@Article{We14,
-    Title = {On homology of linear groups over $k[t]$},
-    Author = {Wendt, Matthias},
-    Journal = {Math. Res. Lett.},
-    Year = {2014},
-    Number = {6},
-    Volume = {21},
-    Doi = {10.4310/MRL.2014.v21.n6.a15} }
-
-@Article{Ma69,
-    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
-    author = {Matsumoto, H.},
-    journal = {Ann. Sci. ENS},
-    year = {1969},
-    number = {1},
-    pages = {1--62},
-    volume = {2},
-    url = {http://eudml.org/doc/81843} }
-
-@article{AF17,
-    title = {An explicit KO-degree map and applications},
-    author = {Asok, Aravind and Fasel, Jean},
-    doi = {10.1112/topo.12007},
-    volume = 10,
-    Issue = 1,
-    Year = 2017,
-    Pages = {268-300},
-    Journal = {J. Top.} }
-
-@article{Sch16,
-    author = {Schlichting, Marco},
-    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
-    year = 2017,
-    volume = 221,
+    Volume    = 221,
     Issue     = 7,
     Pages     = {1729--1844},
-    Doi = {10.1016/j.jpaa.2016.12.026},
-    Journal = {J. Pure Appl. Alg.} }
-
-@article{FRS12,
-    title = {On stably free modules over affine algebras},
-    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
-    Volume = 116,
+    Year      = 2017,
+    Doi       = {10.1016/j.jpaa.2016.12.026}}
+
+@Article{S15,
+    Author    = {Sinchuk, Sergey},
+    Title     = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },    
+    Journal   = {J. Pure Appl. Alg.},
+    Volume    = 220,    
+    Number    = 2,    
+    Pages     = {857--875},
+    Year      = 2016,
+    Doi       = {10.1016/j.jpaa.2015.08.003}}
+
+@Article{St-Ded,
+    Author    = {Stavrova, Anastasia},
+    Title     = {Chevalley groups of polynomial rings over Dedekind domains},
+    Journal   = {J. Gr. Th.},
+    Volume    = 23,
     Issue     = 1,
-    Pages = {223--243},
-    Year = 2012,
-    Journal = {Publ. Math. IH{\'E}S},
-    doi = {10.1007/s10240-012-0041-y} }
-
-@article{Lo78,
-    author = {Loday, Jean-Louis},
-    journal = {J. Alg.},
-    title = {Cohomologie et groupes de Steinberg relatifs},
-    year = {1978},
-    volume = {54},
-    number = {1},
-    doi = {10.1016/0021-8693(78)90025-X},
-    pages = {178--202} }
-
-@article{Pa89,
-    author = {Panin, Ivan},
-    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
-    journal = {Leningrad Math. J.},
-    year = {1990},
-    volume = {1},
-    number = {3},
-    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
-    pages = {741--754} }
-
-@article{Ka80,
-    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
-    author = {Karoubi, Max},
-    journal = {Ann. Math.},
-    volume = {112},
-    number = {2},
-    pages = {259--282},
-    year = {1980},
-    doi = {10.2307/1971147} }
-
-@article{Hur77,
-    author = {Hurrelbrink, J{\"u}rgen},
-    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
-    journal = {Math. Ann.},
-    volume = {225},
-    year = {1977},
-    number = {2},
-    pages = {123--129},
-    doi = {10.1007/BF01351716} }
-
-@online{Re75,
-    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
-    author = {Rehmann, Ulf},
-    year = {1975} }
-
-@article{MR91,
-    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
-    author = {Morita, Jun and Rehmann, Ulf},
-    journal = {Math. Z.},
-    volume = {206},
-    number = {1},
-    pages = {57--66},
-    year = {1991},
-    doi = {10.1007/BF02571324} }
-
-@article{VP,
-    year = {1996},
-    journal = {Acta Appl. Math.},
-    volume = {45},
-    issue = {1},
-    doi = {10.1007/BF00047884},
-    title = {Chevalley groups over commutative rings: I. Elementary calculations},
-    author = {Vavilov, Nikolai A. and Plotkin, E.},
-    pages = {73--113} }
-
-@article{St71,
-    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
-    author = {Stein, Michael R},
-    journal = {Amer. J. Math.},
-    volume = {93},
-    number = {4},
-    pages = {965--1004},
-    year = {1971},
-    doi = {10.2307/2373742} }
-
-@inproceedings{DS73,
-    title = {The functor $K_2$: A survey of computations and problems},
-    author = {Dennis, R Keith and Stein, Michael R},
-    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
-    pages = {241--303},
-    year = {1973},
-    publisher = {Springer},
-    doi = {10.1007/BFb0073728} }
-
-@article{Ho05,
-    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
-    author = {Hornbostel, Jens},
-    journal = {J. Top.},
-    volume = {44},
-    number = {3},
-    pages = {661--687},
-    year = {2005},
-    doi = {10.1016/j.top.2004.10.004} }
+    Pages     = {121--132},
+    Year      = 2020,
+    Doi       = {10.1515/jgth-2019-0100}}
+
+@Article{St-poly,
+    Author    = {Stavrova, Anastasia},
+    Title     = {Homotopy invariance of non-stable $K_1$-functors},    
+    Journal   = {J. K-th.},
+    Volume    = 13,
+    Number    = 2,
+    Pages     = {199--248},   
+    Year      = 2014,
+    Doi       = {10.1017/is013006012jkt232}}
+
+@Article{St78,
+    Author    = {Stein, Michael R.},
+    Title     = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},    
+    Journal   = {Japan J. Math.},
+    Volume    = 4,
+    Issue     = 1,
+    Pages     = {77--108},
+    Year      = 1978,
+    Doi       = {10.4099/math1924.4.77}}
+
+@Article{St71,
+    Author    = {Stein, Michael R},
+    Title     = {Generators, relations and coverings of Chevalley groups over commutative rings},
+    Journal   = {Amer. J. Math.},
+    Volume    = 93,
+    Number    = 4,
+    Pages     = {965--1004},
+    Year      = 1971,
+    Doi       = {10.2307/2373742}}
+
+@Article{Ste73,
+    Author    = {Stein, Michael R.},
+    Title     = {Surjective stability in dimension 0 for $K_2$ and related functors},    
+    Journal   = {Trans. Amer. Math. Soc.},
+    Volume    = 178,
+    Pages     = {165--191},
+    Year      = 1973,
+    Doi       = {10.2307/1996696}}
+
+@Book{St67,
+    Author    = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
+    Title     = {Lectures on Chevalley groups},        
+    Publisher = {Yale Univ. New Haven},
+    Year      = 1967}
+
+@Article{Su77,
+    Author    = {Suslin, Andrei},
+    Title     = {On the structure of the special linear group over commutative rings},    
+    Journal   = {Math. USSR Izv.},        
+    Volume    = 11,
+    Pages     = {221--238},
+    Year      = 1977,
+    Doi       = {10.1070/IM1977v011n02ABEH001709}}
+
+@Article{Su76,
+    Author    = {Suslin, Andrei},
+    Title     = {Projective modules over polynomial rings are free},    
+    Journal   = {Dokl. Akad. nauk SSSR},
+    Volume    = 229,
+    Pages     = {1063--1066},
+    Year      = 1976,
+    Url       = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf}}
+
+@Article{Su82,
+    Author    = {Suslin, Andrei and Kopeiko, Vyacheslav},
+    Title     = {Quadratic modules and the orthogonal group over polynomial rings},    
+    Journal   = {J. Soviet Math.},
+    Volume    = 20,
+    Number    = 6,
+    Pages     = {2665--2691},
+    Year      = 1982,
+    Doi       = {10.1007/BF01681481}}
+
+@Article{ST76,
+    Author    = {Suslin, Andrei and Tulenbaev, Marat},
+    Title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
+    Journal   = {J. Soviet Math.},    
+    Volume    = 17,
+    Number    = 2,
+    Pages     = {1804--1819},
+    Year      = 1981,
+    Doi       = {10.1007/BF01091768}}
+
+@InProceedings{Ta86,
+    Author    = {Taddei, Giovanni},
+    Title     = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},    
+    Booktitle = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
+    Series    = {Contemp. Math},
+    Volume    = 55,
+    Pages     = {693--710},       
+    Year      = 1986,
+    Url       = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
+
+@Article{Tu83,
+    Author    = {Tulenbaev, Marat},
+    Title     = {The Steinberg group of a polynomial ring},    
+    Journal   = {Math. USSR Sb.},        
+    Volume    = 45,
+    Pages     = {131--144},
+    Year      = 1983,
+    Doi       = {10.1070/SM1983v045n01ABEH002591}}
+
+@Article{Va86,
+    Author    = {Vaserstein, Leonid},
+    Title     = {On normal subgroups of Chevalley groups over commutative rings},
+    Journal   = {Tohoku Math. J.},
+    Volume    = 38,
+    Issue     = 2,
+    Pages     = {219--230},
+    Year      = 1986,
+    Doi       = {10.2748/tmj/1178228489}}
 
 @Article{V00,
-    title = {A third look at weight diagrams},
-    author = {Vavilov, Nikolai A.},
-    journal = {Rend. Sem. Mat. Univ. Padova},
-    year = {2000},
-    pages = {201--250},
-    volume = {104},
-    Url = {http://eudml.org/doc/108535} }
-
-@article{A13,
-    author = {Allcock, Daniel},
-    title = {Steinberg groups as amalgams},
-    journal = {Alg. Number Th.},
-    year = {2016},
-    volume = {10},
-    number = {8},
-    pages = {1791--1843},
-    doi = {10.2140/ant.2016.10.1791} }
-
-@article{Su82,
-    title = {Quadratic modules and the orthogonal group over polynomial rings},
-    author = {Suslin, A.~A. and Kopeiko, V.~I.},
-    journal = {J. Soviet Math.},
-    volume = {20},
-    number = {6},
-    pages = {2665--2691},
-    year = {1982},
-    doi = {10.1007/BF01681481} }
-
-@article{Va86,
-    author = {Vaserstein, L.},
-    title = {On normal subgroups of Chevalley groups over commutative rings},
-    journal = {Tohoku Math. J.},
-    volume = {38},
-    issue = {2},
-    pages = {219--230},
-    year = {1986},
-    doi = {10.2748/tmj/1178228489} }
-
-@online{VZ18,
-    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
-    title = {Generation of relative commutator subgroup in Chevalley groups, II},
-    archivePrefix = "arXiv",
-    eprint = "1811.11263",
-    primaryClass = "math.GR",
-    year = {2018} }
-
-@article{St-Ded,
-    author = {Stavrova, Anastasia},
-    title = {Chevalley groups of polynomial rings over Dedekind domains},
-    journal = {J. Gr. Th.},
-    volume = {23},
-    issue = {1},
-    doi = {10.1515/jgth-2019-0100},
-    year = {2020}}
-
-@article{Das17,
-    title = {$\mathbb{P}^1$-gluing for local complete intersections},
-    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
-    journal = {Math. Z.},
-    pages = {1--19},
-    year = {2017},
-    doi = {10.1007/s00209-019-02299-5} }
-
-@article{Su76,
-    title = {Projective modules over polynomial rings are free},
-    author = {Suslin, Andrei},
-    journal = {Dokl. Akad. nauk SSSR},
-    volume = {229},
-    pages = {1063--1066},
-    year = {1976},
-    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }
-
-@article{Qu76,
-    author = "Quillen, Daniel",
-    title = "Projective modules over polynomial rings",
-    journal = "Inv. Math.",
-    year = "1976",
-    volume = "36",
-    number = "1",
-    pages = "167--171",
-    doi = "10.1007/BF01390008" }
-
-@article{Ho64,
-    title = {Projective modules over an extension of a local ring},
-    author = {Horrocks, Geoffrey},
-    journal = {Proc. London Math. Soc.},
-    volume = {3},
-    number = {4},
-    pages = {714--718},
-    year = {1964},
-    doi = {10.1112/plms/s3-14.4.714} }
-
-@article{Mo04,
-    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
-    author = {Morel, Fabien},
-    journal = {Comm. Math. Helv.},
-    volume = {79},
-    number = {4},
-    pages = {689--703},
-    year = {2004},
-    publisher = {Springer},
-    doi = {10.1007/s00014-004-0815-z} }
-
-@article{St78,
-    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
-    author = {Stein, M.~R.},
-    journal = {Japan J. Math.},
-    volume = {4},
-    issue = {1},
-    year = {1978},
-    pages = {77--108},
-    doi = {10.4099/math1924.4.77} }
-
-@mastersthesis{Vo11,
-    author = {V{\"o}lkel, Konrad},
-    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
-    school = {Uni. Freiburg},
-    year = {2011},
-    type = {Diplomarbeit}}
-
-@article{Ba74,
-  title={Clifford algebras and spinor norms over a commutative ring},
-  author={Bass, Hyman},
-  journal={Amer. J. Math.},
-  volume={96},
-  number={1},
-  pages={156--206},
-  year={1974},
-  doi={10.2307/2373586}}
-
-@book{Bou81,
-  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
-  author={Bourbaki, Nicolas},
-  year={1981},
-  publisher={Masson}}
-
-@InProceedings{Ta86,
-  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
-  Author                   = {Taddei, Giovanni},
-  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
-  Year                     = {1986},
-  Pages                    = {693--710},
-  Series                   = {Contemp. Math},
-  Volume                   = {55},
-  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
-
-@article{La18,
-  title={A local-global principle for symplectic $K_2$},
-  author={Lavrenov, Andrei},
-  year={2018},
-  journal={Doc. Math.},
-  volume={23},
-  pages={653--675},
-  doi={10.25537/dm.2018v23.653-675}}
+    Author    = {Vavilov, Nikolai},
+    Title     = {A third look at weight diagrams},    
+    Journal   = {Rend. Sem. Mat. Univ. Padova},   
+    Volume    = 104,
+    Pages     = {201--250},    
+    Year      = 2000,
+    Url       = {http://eudml.org/doc/108535}}
+
+@Article{VP,
+    Author    = {Vavilov, Nikolai and Plotkin, Eugene},
+    Title     = {Chevalley groups over commutative rings: I. Elementary calculations},
+    Journal   = {Acta Appl. Math.},    
+    Volume    = 45,
+    Issue     = 1,
+    Pages     = {73--113},
+    Year      = {1996},       
+    Doi       = {10.1007/BF00047884}}
+
+@Article{VZ18,
+    Author    = {Vavilov, Nikolai and Zhang, Zuhong},
+    Title     = {Generation of relative commutator subgroups in Chevalley groups. II},    
+    Journal   = {Proc. Edinburgh Math. Soc.},
+    Volume    = 63,
+    Number    = 2,
+    Pages     = {497--511},
+    Year      = 2020,
+    Doi       = {10.1017/S0013091519000555}}
+
+@Mastersthesis{Vo11,
+    Author    = {V{\"o}lkel, Konrad},
+    Title     = {\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}{Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
+    School    = {Uni. Freiburg},
+    Type      = {Diplomarbeit}
+    Year      = 2011}
+
+@Book{Kbook,
+    Author    = {Weibel, Charles A},
+    Title     = {The $K$-book: An introduction to algebraic $K$-theory},        
+    Publisher = {Amer. Math. Soc.},
+    Series    = {Grad. Texts Math.},
+    Volume    = 145,
+    Year      = 2013}
 \end{filecontents}

### 2020-06-30 horrocks.tex
Convert bibliography to the thebibliography format

@@
 \usepackage{color} 
-%\usepackage[breaklinks=false,unicode]{hyperref}
-\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[capitalize]{cleveref}
@@
 \usepackage{enumitem}
-\usepackage{filecontents}
 
@@
 \def\LOCAL{\horrocks.files}
-
-\addbibresource{horrocks.bib}
-\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
-\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
-\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\renewcommand*{\bibfont}{\footnotesize}
-\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}
+%\renewcommand*{\bibfont}{\footnotesize}
+%\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}
 
@@
 \begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the homomorphism $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism.
-In particular, the obvious homomorphism $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
+Consequently, the obvious homomorphism $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism.
 \end{prop}
@@
 
-\printbibliography
+\begin{thebibliography}{1000}
+\bibitem{Abe83}
+ E.~Abe, 
+ \emph{\href{https://dx.doi.org/10.1080/00927878308822906} 
+ {Whitehead groups of {C}hevalley groups over polynomial rings}},
+ Comm. Alg. \textbf{11} (1983), no.~12, 1271--1307.
+
+\bibitem{A13}
+ D.~Allcock, 
+ \emph{\href{https://dx.doi.org/10.2140/ant.2016.10.1791} 
+ {Steinberg groups as amalgams}},
+ Alg. Number Th. \textbf{10} (2016), no.~8, 1791--1843.
+
+\bibitem{AF17}
+ A.~Asok and J.~Fasel, 
+ \emph{\href{https://dx.doi.org/10.1112/topo.12007} 
+ {An explicit KO-degree map and applications}},
+ J. Top. \textbf{10} (2017), 268--300.
+
+\bibitem{Ba74}
+ H.~Bass, 
+ \emph{\href{https://dx.doi.org/10.2307/2373586} 
+ {Clifford algebras and spinor norms over a commutative ring}},
+ Amer. J. Math. \textbf{96} (1974), no.~1, 156--206.
+
+\bibitem{Bou81}
+ N.~Bourbaki, 
+ \emph{Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
+ Masson, 1981.
+
+\bibitem{DS73}
+ R.~K.~Dennis and M.~R.~Stein,
+ \emph{\href{https://dx.doi.org/10.1007/BFb0073728} 
+ {The functor $\K_2$: A survey of computations and problems}},
+ Classical Algebraic K-Theory, and Connections with Arithmetic, Springer, 1973, pp.~241--303.
+
+\bibitem{FRS12}
+ J.~Fasel, R.~Rao, and R.~Swan,
+ \emph{\href{https://dx.doi.org/10.1007/s10240-012-0041-y} 
+ {On stably free modules over affine algebras}},
+ Publ. Math. IH{\'E}S \textbf{116} (2012), 223--243.
+
+\bibitem{Ho05}
+ J.~Hornbostel, 
+ \emph{\href{https://dx.doi.org/10.1016/j.top.2004.10.004} 
+ {$\mathbb{A}^1$-representability of hermitian K-theory and Witt groups}},
+ J. Top. \textbf{44} (2005), no.~3, 661--687.
+
+\bibitem{Ho64}
+ G.~Horrocks, 
+ \emph{\href{https://dx.doi.org/10.1112/plms/s3-14.4.714} 
+ {Projective modules over an extension of a local ring}},
+ Proc. London Math. Soc. \textbf{3} (1964), no.~4, 714--718.
+
+\bibitem{Hur77}
+ J.~Hurrelbrink, 
+ \emph{\href{https://dx.doi.org/10.1007/BF01351716} 
+ {Endlich pr\"asentierte arithmetische gruppen und $K_{2}$ {\"u}ber Laurent-polynomringen}},
+ Math. Ann. \textbf{225} (1977), no.~2, 123--129.
+
+\bibitem{Ka80}
+ M.~Karoubi, 
+ \emph{\href{https://dx.doi.org/10.2307/1971147} 
+ {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne}},
+ Ann. Math. \textbf{112} (1980), no.~2, 259--282.
+
+\bibitem{Lam10}
+ T.-Y.~Lam, 
+ \emph{Serre's problem on projective modules},
+ Springer Science \& Business Media, 2010.
+
+\bibitem{La18}
+ A.~Lavrenov, 
+ \emph{\href{https://dx.doi.org/10.25537/dm.2018v23.653-675}
+ {A local-global principle for symplectic $\K_2$}},
+ Doc. Math. \textbf{23} (2018), 653--675.
+
+\bibitem{LS17}
+ A.~Lavrenov and S.~Sinchuk,
+ \emph{\href{https://arxiv.org/pdf/1606.00272.pdf} 
+ {Centrality of odd orthogonal $\K_2$}},
+ J. Pure Appl. Alg. \textbf{221} (2017), 1134--1145.
+
+\bibitem{Lo78}
+ J.-L.~Loday,
+ \emph{\href{https://dx.doi.org/10.1016/0021-8693(78)90025-X}
+ {Cohomologie et groupes de Steinberg relatifs}}, 
+ J. Alg. \textbf{54} (1978), no.~1, 178--202.
+
+\bibitem{Ma69}
+ H.~Matsumoto,
+ \emph{\href{http://eudml.org/doc/81843} 
+ {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s}},
+ Ann. Sci. ENS \textbf{2} (1969), no.~1, 1--62.
+
+\bibitem{Mo04}
+ F.~Morel,
+ \emph{\href{https://dx.doi.org/10.1007/s00014-004-0815-z} 
+ {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt}},
+ Comm. Math. Helv. \textbf{79} (2004), no.~4, 689--703.
+
+\bibitem{MR91}
+ J.~Morita and U.~Rehmann,
+ \emph{\href{https://dx.doi.org/10.1007/BF02571324} 
+ {Symplectic $\K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings}},
+ Math. Z. \textbf{206} (1991), no.~1, 57--66.
+
+\bibitem{Pa89}
+ I.~Panin, 
+ \emph{\href{http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf} 
+ {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)}},
+ Leningrad Math. J. \textbf{1} (1990), no.~3, 741--754.
+
+\bibitem{Qu76}
+ D.~Quillen, 
+ \emph{\href{https://dx.doi.org/10.1007/BF01390008} 
+ {Projective modules over polynomial rings}},
+ Inv. Math. \textbf{36} (1976), no.~1, 167--171.
+
+\bibitem{Re75}
+ U.~Rehmann, 
+ \emph{\href{http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}
+ {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$}}, preprint (1975).
+
+\bibitem{RS76}
+ U.~Rehmann and C.~Soul{\'e},
+ \emph{\href{https://dx.doi.org/10.1007/BFb0079999} 
+ {Finitely presented groups of matrices}}, 
+ Algebraic K-Theory, Lect. Notes. Math., vol. 551, Springer, 1976, pp.~164--169.
+
+\bibitem{Sch16}
+ M.~Schlichting, 
+ \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2016.12.026} 
+ {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem}},
+ J. Pure Appl. Alg. \textbf{221} (2017), 1729--1844.
+
+\bibitem{S15}
+ S.~Sinchuk, 
+ \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2015.08.003}
+ {On centrality of $K_2$ for Chevalley groups of type $\mathsf{E}_\ell$}},
+ J. Pure Appl. Alg. \textbf{220} (2016), no.~2, 857--875.
+
+\bibitem{St-poly}
+ A.~Stavrova, 
+ \emph{\href{https://dx.doi.org/10.1017/is013006012jkt232} 
+ {Homotopy invariance of non-stable $\K_1$-functors}}, 
+ J. K-th. \textbf{13} (2014), no.~2, 199--248.
+
+\bibitem{St-Ded}
+ A.~Stavrova, 
+ \emph{\href{https://dx.doi.org/10.1515/jgth-2019-0100} 
+ {Chevalley groups of polynomial rings over Dedekind domains}}, 
+ J. Gr. Th. \textbf{23} (2020), 121--132.
+
+\bibitem{St71}
+ M.~R.~Stein, 
+ \emph{\href{https://dx.doi.org/10.2307/2373742} 
+ {Generators, relations and coverings of Chevalley groups over commutative rings}},
+ Amer. J. Math. \textbf{93} (1971), no.~4, 965--1004.
+
+\bibitem{Ste73}
+ M.~R.~Stein, 
+ \emph{\href{https://dx.doi.org/10.2307/1996696} 
+ {Surjective stability in dimension 0 for $\K_2$ and related functors}},
+ Trans. Amer. Math. Soc. \textbf{178} (1973), 165--191.
+
+\bibitem{St78}
+ M.~R.~Stein, 
+ \emph{\href{https://dx.doi.org/10.4099/math1924.4.77} 
+ {Stability theorems for $\K_1$, $\K_2$ and related functors modeled on Chevalley groups}},
+ Japan J. Math. \textbf{4} (1978), 77--108.
+
+\bibitem{St67}
+ R.~Steinberg, J.~Faulkner, and R.~Wilson, 
+ \emph{Lectures on Chevalley groups},
+ Yale Univ. New Haven, 1967.
+
+\bibitem{Su76}
+ A.~Suslin, 
+ \emph{\href{http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} 
+ {Projective modules over polynomial rings are free}}, 
+ Dokl. Akad. Nauk SSSR \textbf{229} (1976), 1063--1066.
+
+\bibitem{Su77}
+ A.~Suslin, 
+ \emph{\href{https://dx.doi.org/10.1070/IM1977v011n02ABEH001709} 
+ {On the structure of the special linear group over commutative rings}},
+ Math. USSR Izv. \textbf{11} (1977), 221--238.
+
+\bibitem{Su82}
+ A.~Suslin and V.~Kopeiko, 
+ \emph{\href{https://dx.doi.org/10.1007/BF01681481} 
+ {Quadratic modules and the orthogonal group over polynomial rings}},
+ J. Soviet Math. \textbf{20} (1982), no.~6, 2665--2691.
+
+\bibitem{ST76}
+ A.~Suslin and M.~Tulenbaev, 
+ \emph{\href{https://dx.doi.org/10.1007/BF01091768} 
+ {Stabilization theorem for the Milnor $K_2$-functor}},
+ J. Soviet Math. \textbf{17} (1981), no.~2, 1804--1819.
+
+\bibitem{Ta86}
+ G.~Taddei, 
+ \emph{\href{http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}
+ {Normalit\'e des groupes \'el\'ementaires dans les groupes de Chevalley sur un anneau}},
+ Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983),
+ Contemp. Math, vol.~55, 1986, pp.~693--710.
+
+\bibitem{Tu83}
+ M.~Tulenbaev, 
+ \emph{\href{https://dx.doi.org/10.1070/SM1983v045n01ABEH002591}
+ {The Steinberg group of a polynomial ring}},
+ Math. USSR Sb. \textbf{45} (1983), 131--144.
+
+\bibitem{Va86}
+ L.~Vaserstein, 
+ \emph{\href{https://dx.doi.org/10.2748/tmj/1178228489}
+ {On normal subgroups of Chevalley groups over commutative rings}},
+ Tohoku Math. J. \textbf{38} (1986), 219--230.
+
+\bibitem{V00}
+ N.~Vavilov, 
+ \emph{\href{http://eudml.org/doc/108535}
+ {A third look at weight diagrams}}, 
+ Rend. Sem. Mat. Univ. Padova \textbf{104} (2000), 201--250.
+
+\bibitem{VP}
+ N.~Vavilov and E.~Plotkin, 
+ \emph{\href{https://dx.doi.org/10.1007/BF00047884}
+ {Chevalley groups over commutative rings: I. Elementary calculations}},
+ Acta Appl. Math. \textbf{45} (1996), 73--113.
+
+\bibitem{VZ18}
+ N.~Vavilov and Z.~Zhang, 
+ \emph{\href{https://dx.doi.org/10.1017/S0013091519000555}
+ {Generation of relative commutator subgroups in Chevalley groups. II}},
+ Proc. Edinburgh Math. Soc. \textbf{63} (2020), no.~2, 497--511.
+
+\bibitem{Vo11}
+ K.~V{\"o}lkel,
+ \emph{\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}
+ {Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
+ Diplomarbeit, Uni. Freiburg.
+
+\bibitem{Kbook}
+ C.~A.~Weibel, 
+ \emph{The $K$-book: An introduction to algebraic $K$-theory},
+ Grad. Texts Math., vol. 145, Amer. Math. Soc., 2013.
+\end{thebibliography}
+
 \Addresses
-\begin{filecontents}{horrocks.bib}
-@Article{Abe83,
-    Author    = {Abe, Eiichi},
-    Title     = {Whitehead groups of {C}hevalley groups over polynomial rings},    
-    Journal   = {Comm. Alg.},    
-    Number    = 12,
-    Volume    = 11,
-    Pages     = {1271--1307},
-    Year      = 1983,    
-    Doi       = {10.1080/00927878308822906}}
-
-@Article{A13,
-    Author    = {Allcock, Daniel},
-    Title     = {Steinberg groups as amalgams},
-    Journal   = {Alg. Number Th.},    
-    Volume    = 10,
-    Number    = 8,
-    Pages     = {1791--1843},
-    Year      = 2016,
-    Doi       = {10.2140/ant.2016.10.1791}}
-
-@Article{AF17,
-    Author    = {Asok, Aravind and Fasel, Jean},
-    Title     = {An explicit KO-degree map and applications},    
-    Journal   = {J. Top.},
-    Volume    = 10,
-    Issue     = 1,
-    Pages     = {268--300},
-    Year      = 2017,    
-    Doi       = {10.1112/topo.12007}}
-
-@Article{Ba74,
-    Author    = {Bass, Hyman},
-    Title     = {Clifford algebras and spinor norms over a commutative ring},    
-    Journal   = {Amer. J. Math.},
-    Volume    = 96,
-    Number    = 1,
-    Pages     = {156--206},
-    Year      = 1974,
-    Doi       = {10.2307/2373586}}
-
-@Book{Bou81,
-    Author    = {Bourbaki, Nicolas},
-    Title     = {Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
-    Publisher = {Masson},
-    Year      = 1981}
-
-@Inproceedings{DS73,
-    Author    = {Dennis, R. Keith and Stein, Michael R.},
-    Title     = {The functor $K_2$: A survey of computations and problems},    
-    Booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
-    Publisher = {Springer},
-    Pages     = {241--303},
-    Year      = 1973,
-    Doi       = {10.1007/BFb0073728}}
-
-@Article{FRS12,
-    Author    = {Fasel, Jean and Rao, Ravi and Swan, Richard},
-    Title     = {On stably free modules over affine algebras},
-    Journal   = {Publ. Math. IH{\'E}S},
-    Volume    = 116,
-    Issue     = 1,
-    Pages     = {223--243},
-    Year      = 2012,
-    Doi       = {10.1007/s10240-012-0041-y}}
-
-@Article{Ho05,
-    Author    = {Hornbostel, Jens},
-    Title     = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},    
-    Journal   = {J. Top.},
-    Volume    = 44,
-    Number    = 3,
-    Pages     = {661--687},
-    Year      = 2005,
-    Doi       = {10.1016/j.top.2004.10.004}}
-
-@Article{Ho64,
-    Author    = {Horrocks, Geoffrey},
-    Title     = {Projective modules over an extension of a local ring},    
-    Journal   = {Proc. London Math. Soc.},
-    Volume    = 3,
-    Number    = 4,
-    Pages     = {714--718},
-    Year      = 1964,
-    Doi       = {10.1112/plms/s3-14.4.714}}
-
-@Article{Hur77,
-    Author    = {Hurrelbrink, J{\"u}rgen},
-    Title     = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
-    Journal   = {Math. Ann.},
-    Volume    = 225,    
-    Number    = 2,
-    Pages     = {123--129},
-    Year      = 1977,
-    Doi       = {10.1007/BF01351716}}
-
-@Article{Ka80,
-    Author    = {Karoubi, Max},
-    Title     = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},    
-    Journal   = {Ann. Math.},
-    Volume    = 112,
-    Number    = 2,
-    Pages     = {259--282},
-    Year      = 1980,
-    Doi       = {10.2307/1971147}}
-
-@Book{Lam10,
-    Title     = {Serre's problem on projective modules},
-    Author    = {Lam, Tsit-Yuen},
-    Publisher = {Springer Science \& Business Media},
-    Year      = {2010},
-    Doi       = {10.1007/978-3-540-34575-6}}
-
-@Article{LS17,
-    Author    = {Lavrenov, Andrei and Sinchuk, Sergey},
-    Title     = {Centrality of odd orthogonal $K_2$},    
-    Journal   = {J. Pure Appl. Alg.},
-    Volume    = 221,
-    Pages     = {1134--1145},
-    Year      = 2017,    
-    Url       = {https://arxiv.org/pdf/1606.00272.pdf}}
-
-@Article{La18,
-    Author    = {Lavrenov, Andrei},
-    Title     = {A local-global principle for symplectic $K_2$},    
-    Journal   = {Doc. Math.},    
-    Volume    = 23,
-    Pages     = {653--675},
-    Year      = 2018,
-    Doi       = {10.25537/dm.2018v23.653-675}}
-
-@Article{Lo78,
-    Author    = {Loday, Jean-Louis},
-    Title     = {Cohomologie et groupes de Steinberg relatifs},
-    Journal   = {J. Alg.},    
-    Volume    = 54,
-    Number    = 1,
-    Pages     = {178--202},
-    Year      = 1978,
-    Doi       = {10.1016/0021-8693(78)90025-X}}
-
-@Article{Ma69,
-    Author    = {Matsumoto, Hideya},
-    Title     = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},    
-    Journal   = {Ann. Sci. ENS},
-    Volume    = 2,
-    Number    = 1,
-    Pages     = {1--62},
-    Year      = 1969,
-    Url       = {http://eudml.org/doc/81843}}
-
-@Article{Mo04,
-    Author    = {Morel, Fabien},
-    Title     = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},    
-    Journal   = {Comm. Math. Helv.},
-    Volume    = 79,
-    Number    = 4,
-    Pages     = {689--703},
-    Year      = 2004,
-    Doi       = {10.1007/s00014-004-0815-z}}
-
-@Article{MR91,
-    Author    = {Morita, Jun and Rehmann, Ulf},
-    Title     = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},    
-    Journal   = {Math. Z.},
-    Volume    = 206,
-    Number    = 1,
-    Pages     = {57--66},
-    Year      = 1991,
-    Doi       = {10.1007/BF02571324}}
-
-@Article{Pa89,
-    Author    = {Panin, Ivan},
-    Title     = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
-    Journal   = {Leningrad Math. J.},    
-    Volume    = 1,
-    Number    = 3,
-    Pages     = {741--754},
-    Year      = 1990,
-    Url       = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf}}
-
-@Article{Qu76,
-    Author    = {Quillen, Daniel},
-    Title     = {Projective modules over polynomial rings},
-    Journal   = {Inv. Math.},    
-    Volume    = 36,
-    Number    = 1,
-    Pages     = {167--171},
-    Year      = 1976,
-    Doi       = {10.1007/BF01390008}}
-
-@Article{Re75,
-    Author    = {Rehmann, Ulf},
-    Title     = {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$},    
-    Year      = {1975},
-    Url       = {http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}}
-
-@Inproceedings{RS76,
-    Author    = {Rehmann, Ulf and Soul{\'e} , Christophe},
-    Title     = {Finitely presented groups of matrices},    
-    Booktitle = {Algebraic K-Theory},
-    Publisher = {Springer},        
-    Series    = {Lect. Notes. Math.},
-    Volume    = 551,
-    Pages     = {164--169},
-    Year      = 1976,
-    Doi       = {10.1007/BFb0079999}}
-
-@Article{Sch16,
-    Author    = {Schlichting, Marco},
-    Title     = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
-    Journal   = {J. Pure Appl. Alg.},    
-    Volume    = 221,
-    Issue     = 7,
-    Pages     = {1729--1844},
-    Year      = 2017,
-    Doi       = {10.1016/j.jpaa.2016.12.026}}
-
-@Article{S15,
-    Author    = {Sinchuk, Sergey},
-    Title     = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },    
-    Journal   = {J. Pure Appl. Alg.},
-    Volume    = 220,    
-    Number    = 2,    
-    Pages     = {857--875},
-    Year      = 2016,
-    Doi       = {10.1016/j.jpaa.2015.08.003}}
-
-@Article{St-Ded,
-    Author    = {Stavrova, Anastasia},
-    Title     = {Chevalley groups of polynomial rings over Dedekind domains},
-    Journal   = {J. Gr. Th.},
-    Volume    = 23,
-    Issue     = 1,
-    Pages     = {121--132},
-    Year      = 2020,
-    Doi       = {10.1515/jgth-2019-0100}}
-
-@Article{St-poly,
-    Author    = {Stavrova, Anastasia},
-    Title     = {Homotopy invariance of non-stable $K_1$-functors},    
-    Journal   = {J. K-th.},
-    Volume    = 13,
-    Number    = 2,
-    Pages     = {199--248},   
-    Year      = 2014,
-    Doi       = {10.1017/is013006012jkt232}}
-
-@Article{St78,
-    Author    = {Stein, Michael R.},
-    Title     = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},    
-    Journal   = {Japan J. Math.},
-    Volume    = 4,
-    Issue     = 1,
-    Pages     = {77--108},
-    Year      = 1978,
-    Doi       = {10.4099/math1924.4.77}}
-
-@Article{St71,
-    Author    = {Stein, Michael R},
-    Title     = {Generators, relations and coverings of Chevalley groups over commutative rings},
-    Journal   = {Amer. J. Math.},
-    Volume    = 93,
-    Number    = 4,
-    Pages     = {965--1004},
-    Year      = 1971,
-    Doi       = {10.2307/2373742}}
-
-@Article{Ste73,
-    Author    = {Stein, Michael R.},
-    Title     = {Surjective stability in dimension 0 for $K_2$ and related functors},    
-    Journal   = {Trans. Amer. Math. Soc.},
-    Volume    = 178,
-    Pages     = {165--191},
-    Year      = 1973,
-    Doi       = {10.2307/1996696}}
-
-@Book{St67,
-    Author    = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
-    Title     = {Lectures on Chevalley groups},        
-    Publisher = {Yale Univ. New Haven},
-    Year      = 1967}
-
-@Article{Su77,
-    Author    = {Suslin, Andrei},
-    Title     = {On the structure of the special linear group over commutative rings},    
-    Journal   = {Math. USSR Izv.},        
-    Volume    = 11,
-    Pages     = {221--238},
-    Year      = 1977,
-    Doi       = {10.1070/IM1977v011n02ABEH001709}}
-
-@Article{Su76,
-    Author    = {Suslin, Andrei},
-    Title     = {Projective modules over polynomial rings are free},    
-    Journal   = {Dokl. Akad. nauk SSSR},
-    Volume    = 229,
-    Pages     = {1063--1066},
-    Year      = 1976,
-    Url       = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf}}
-
-@Article{Su82,
-    Author    = {Suslin, Andrei and Kopeiko, Vyacheslav},
-    Title     = {Quadratic modules and the orthogonal group over polynomial rings},    
-    Journal   = {J. Soviet Math.},
-    Volume    = 20,
-    Number    = 6,
-    Pages     = {2665--2691},
-    Year      = 1982,
-    Doi       = {10.1007/BF01681481}}
-
-@Article{ST76,
-    Author    = {Suslin, Andrei and Tulenbaev, Marat},
-    Title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
-    Journal   = {J. Soviet Math.},    
-    Volume    = 17,
-    Number    = 2,
-    Pages     = {1804--1819},
-    Year      = 1981,
-    Doi       = {10.1007/BF01091768}}
-
-@InProceedings{Ta86,
-    Author    = {Taddei, Giovanni},
-    Title     = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},    
-    Booktitle = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
-    Series    = {Contemp. Math},
-    Volume    = 55,
-    Pages     = {693--710},       
-    Year      = 1986,
-    Url       = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}
-
-@Article{Tu83,
-    Author    = {Tulenbaev, Marat},
-    Title     = {The Steinberg group of a polynomial ring},    
-    Journal   = {Math. USSR Sb.},        
-    Volume    = 45,
-    Pages     = {131--144},
-    Year      = 1983,
-    Doi       = {10.1070/SM1983v045n01ABEH002591}}
-
-@Article{Va86,
-    Author    = {Vaserstein, Leonid},
-    Title     = {On normal subgroups of Chevalley groups over commutative rings},
-    Journal   = {Tohoku Math. J.},
-    Volume    = 38,
-    Issue     = 2,
-    Pages     = {219--230},
-    Year      = 1986,
-    Doi       = {10.2748/tmj/1178228489}}
-
-@Article{V00,
-    Author    = {Vavilov, Nikolai},
-    Title     = {A third look at weight diagrams},    
-    Journal   = {Rend. Sem. Mat. Univ. Padova},   
-    Volume    = 104,
-    Pages     = {201--250},    
-    Year      = 2000,
-    Url       = {http://eudml.org/doc/108535}}
-
-@Article{VP,
-    Author    = {Vavilov, Nikolai and Plotkin, Eugene},
-    Title     = {Chevalley groups over commutative rings: I. Elementary calculations},
-    Journal   = {Acta Appl. Math.},    
-    Volume    = 45,
-    Issue     = 1,
-    Pages     = {73--113},
-    Year      = {1996},       
-    Doi       = {10.1007/BF00047884}}
-
-@Article{VZ18,
-    Author    = {Vavilov, Nikolai and Zhang, Zuhong},
-    Title     = {Generation of relative commutator subgroups in Chevalley groups. II},    
-    Journal   = {Proc. Edinburgh Math. Soc.},
-    Volume    = 63,
-    Number    = 2,
-    Pages     = {497--511},
-    Year      = 2020,
-    Doi       = {10.1017/S0013091519000555}}
-
-@Mastersthesis{Vo11,
-    Author    = {V{\"o}lkel, Konrad},
-    Title     = {\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}{Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
-    School    = {Uni. Freiburg},
-    Type      = {Diplomarbeit}
-    Year      = 2011}
-
-@Book{Kbook,
-    Author    = {Weibel, Charles A},
-    Title     = {The $K$-book: An introduction to algebraic $K$-theory},        
-    Publisher = {Amer. Math. Soc.},
-    Series    = {Grad. Texts Math.},
-    Volume    = 145,
-    Year      = 2013}
-\end{filecontents}
 \end{document}

### 2020-07-10 horrocks.tex
Fix couple of defects

@@
 We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
-The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
+The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre’s problem,  whose positive solution is currently known only in the linear case.
 \EndAbstract
@@
 \begin{align}
- [x, yz]^y =& [y^{-1}, x] \cdot [x, z], \label{rel43} \\ 
- \label{eq:H1ii} [xy, z] =& {}^x[y, z] \cdot [x,z], \\
- \label{eq:H1ii-2}[x, yz] =& [x, y] \cdot {}^{y}\![x, z], \\
- [[x, y], z] =& {}^{x}\!\left({}^{y}[x^{-1}, [ y^{-1}, z]] \cdot {}^z[y, [ z^{-1}, x^{-1}]] \right). \label{HW-variant} \end{align}
+ [x, yz]^y               & =   [y^{-1}, x] \cdot [x, z], \label{rel43} \\ 
+ \label{eq:H1ii} [xy, z] & =   {}^x[y, z] \cdot [x,z], \\
+ \label{eq:H1ii-2}[x, yz]& =   [x, y] \cdot {}^{y}\![x, z], \\
+ [[x, y], z] & =   {}^{x}\!\left({}^{y}[x^{-1}, [ y^{-1}, z]] \cdot {}^z[y, [ z^{-1}, x^{-1}]] \right). \label{HW-variant} \end{align}
 Recall also from~\cite[Lemma~3.1.1]{RS76} that
@@
 \begin{align}
-&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1} \label{Steinberg-additivity}\\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \label{Chevalley-CCF1} \\
-&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3} \label{Chevalley-CCF2}
+x_{\alpha}(a)\cdot x_{\alpha}(b)&=x_{\alpha}(a+b), \tag{R1} \label{Steinberg-additivity}\\
+[x_{\alpha}(a),\,x_{\beta}(b)]  &=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \label{Chevalley-CCF1} \\
+[x_{\alpha}(a),\,x_{\beta}(b)]  &=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3} \label{Chevalley-CCF2}
 \end{align}
@@
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^\times \ar[r]^-{h} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
+\[\xymatrixcolsep{5pc}\xymatrix{k^\times \ar[drr]_{\{-, X\}} \ar[r]^-{h}  & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
                                                                                       &                                 & \K_2^\mathrm{M}(k(X)),} \]
@@
 Recall that {\it the double ring} $D_{R, I}$ of a pair $(R, I)$ is, by definition, the pullback ring $R \times_{R/I} R$.
-In other words, it is the ring consisting of pairs of elements of $R$ congruent modulo $I$.
+In other words, it is the ring consisting of pairs of elements of~$R$ congruent modulo $I$.
 Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$.
@@
 
-\subsection{Computation of the kernel of the map of evaluation at 0.}\label{sec:computationOfK}
+\subsection{Computation of the kernel of the map of evaluation at 0}\label{sec:computationOfK}
 Let $A$ be a local ring with maximal ideal $M$.
@@
 
-\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)}, \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties.} \label{sec:Pa0-basic}
+\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)}, \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties} \label{sec:Pa0-basic}
 Let $\Phi$ be a root system and $\alpha$ be an element of $\Phi$.
@@
 \begin{rem} \label{rem:palpha} It follows from~\cref{P0_normal} and~\cref{Pstar-large} that the value of the function $p_\alpha$ from the statement of~\cref{P0_normal} on an element $g\in K(A[X], M[X])$ can be computed via the following procedure.
-Start with any presentation of $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. 
+Start with any presentation of~$g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta\in Z_0(\alpha)$. 
 Now pick among these factors those that correspond to the root $\beta = -\alpha$ (i.\,e. pick all factors $z_{-\alpha}(Xf_i, \xi_i)$). 
@@
 
-Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for $g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f' \in M[X]$, $m' \in M$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
+Now pick each factor $x_{\gamma}(Xf)$, $\gamma \in \{ -\alpha, -\beta \}$ appearing in the presentation for~$g_2$, decompose it as $x_{\gamma}(X^2f') \cdot x_{\gamma}(m'X)$ for some $f' \in M[X]$, $m' \in M$ and then move the second factor to the rightmost position within $g_2$ conjugating all factors along the way.
 By the previous paragraph only elements of  $\mathcal{G}_5$ may appear modulo $G_0$ after simplification of these conjugates.
@@
 
-\subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties.} \label{sec:S-a}
+\subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties} \label{sec:S-a}
 Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming a sharp angle.
@@
 
-\subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor.} \label{sec:V-construction}
+\subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor} \label{sec:V-construction}
 Throughout this subsection $\Phi$ denotes an arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. 
@@
 
-\subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
+\subsection{Proof of Horrocks theorem} \label{sec:P1glueing}
 Before we proceed with the proof of~\cref{thm:P1glueing} let us briefly recall the relevant notation.
@@
  E.~Abe, 
- \emph{\href{https://dx.doi.org/10.1080/00927878308822906} 
- {Whitehead groups of {C}hevalley groups over polynomial rings}},
+ \emph{Whitehead groups of {C}hevalley groups over polynomial rings},
  Comm. Alg. \textbf{11} (1983), no.~12, 1271--1307.
@@
  D.~Allcock, 
- \emph{\href{https://dx.doi.org/10.2140/ant.2016.10.1791} 
- {Steinberg groups as amalgams}},
+ \emph{Steinberg groups as amalgams},
  Alg. Number Th. \textbf{10} (2016), no.~8, 1791--1843.
@@
  A.~Asok and J.~Fasel, 
- \emph{\href{https://dx.doi.org/10.1112/topo.12007} 
- {An explicit KO-degree map and applications}},
+ \emph{An explicit KO-degree map and applications},
  J. Top. \textbf{10} (2017), 268--300.
@@
  H.~Bass, 
- \emph{\href{https://dx.doi.org/10.2307/2373586} 
- {Clifford algebras and spinor norms over a commutative ring}},
+ \emph{Clifford algebras and spinor norms over a commutative ring},
  Amer. J. Math. \textbf{96} (1974), no.~1, 156--206.
@@
  R.~K.~Dennis and M.~R.~Stein,
- \emph{\href{https://dx.doi.org/10.1007/BFb0073728} 
- {The functor $\K_2$: A survey of computations and problems}},
+ \emph{The functor $\K_2$: A survey of computations and problems},
  Classical Algebraic K-Theory, and Connections with Arithmetic, Springer, 1973, pp.~241--303.
@@
  J.~Fasel, R.~Rao, and R.~Swan,
- \emph{\href{https://dx.doi.org/10.1007/s10240-012-0041-y} 
- {On stably free modules over affine algebras}},
+ \emph{On stably free modules over affine algebras},
  Publ. Math. IH{\'E}S \textbf{116} (2012), 223--243.
@@
  J.~Hornbostel, 
- \emph{\href{https://dx.doi.org/10.1016/j.top.2004.10.004} 
- {$\mathbb{A}^1$-representability of hermitian K-theory and Witt groups}},
+ \emph{$\mathbb{A}^1$-representability of hermitian K-theory and Witt groups},
  J. Top. \textbf{44} (2005), no.~3, 661--687.
@@
  G.~Horrocks, 
- \emph{\href{https://dx.doi.org/10.1112/plms/s3-14.4.714} 
- {Projective modules over an extension of a local ring}},
+ \emph{Projective modules over an extension of a local ring},
  Proc. London Math. Soc. \textbf{3} (1964), no.~4, 714--718.
@@
  J.~Hurrelbrink, 
- \emph{\href{https://dx.doi.org/10.1007/BF01351716} 
- {Endlich pr\"asentierte arithmetische gruppen und $K_{2}$ {\"u}ber Laurent-polynomringen}},
+ \emph{Endlich pr\"asentierte arithmetische gruppen und $K_{2}$ {\"u}ber Laurent-polynomringen},
  Math. Ann. \textbf{225} (1977), no.~2, 123--129.
@@
  M.~Karoubi, 
- \emph{\href{https://dx.doi.org/10.2307/1971147} 
- {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne}},
+ \emph{Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
  Ann. Math. \textbf{112} (1980), no.~2, 259--282.
@@
  A.~Lavrenov, 
- \emph{\href{https://dx.doi.org/10.25537/dm.2018v23.653-675}
- {A local-global principle for symplectic $\K_2$}},
+ \emph{A local-global principle for symplectic $\K_2$},
  Doc. Math. \textbf{23} (2018), 653--675.
@@
  A.~Lavrenov and S.~Sinchuk,
- \emph{\href{https://arxiv.org/pdf/1606.00272.pdf} 
- {Centrality of odd orthogonal $\K_2$}},
+ \emph{entrality of odd orthogonal $\K_2$},
  J. Pure Appl. Alg. \textbf{221} (2017), 1134--1145.
@@
  J.-L.~Loday,
- \emph{\href{https://dx.doi.org/10.1016/0021-8693(78)90025-X}
- {Cohomologie et groupes de Steinberg relatifs}}, 
+ \emph{Cohomologie et groupes de Steinberg relatifs}, 
  J. Alg. \textbf{54} (1978), no.~1, 178--202.
@@
  H.~Matsumoto,
- \emph{\href{http://eudml.org/doc/81843} 
- {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s}},
+ \emph{Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
  Ann. Sci. ENS \textbf{2} (1969), no.~1, 1--62.
@@
  F.~Morel,
- \emph{\href{https://dx.doi.org/10.1007/s00014-004-0815-z} 
- {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt}},
+ \emph{Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
  Comm. Math. Helv. \textbf{79} (2004), no.~4, 689--703.
@@
  J.~Morita and U.~Rehmann,
- \emph{\href{https://dx.doi.org/10.1007/BF02571324} 
- {Symplectic $\K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings}},
+ \emph{Symplectic $\K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
  Math. Z. \textbf{206} (1991), no.~1, 57--66.
@@
  I.~Panin, 
- \emph{\href{http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf} 
- {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)}},
+ \emph{On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
  Leningrad Math. J. \textbf{1} (1990), no.~3, 741--754.
@@
  D.~Quillen, 
- \emph{\href{https://dx.doi.org/10.1007/BF01390008} 
- {Projective modules over polynomial rings}},
+ \emph{Projective modules over polynomial rings},
  Inv. Math. \textbf{36} (1976), no.~1, 167--171.
@@
  U.~Rehmann, 
- \emph{\href{http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}
- {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$}}, preprint (1975).
+ \emph{Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$}, preprint (1975).
 
@@
  U.~Rehmann and C.~Soul{\'e},
- \emph{\href{https://dx.doi.org/10.1007/BFb0079999} 
- {Finitely presented groups of matrices}}, 
+ \emph{Finitely presented groups of matrices}, 
  Algebraic K-Theory, Lect. Notes. Math., vol. 551, Springer, 1976, pp.~164--169.
@@
  M.~Schlichting, 
- \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2016.12.026} 
- {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem}},
+ \emph{Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
  J. Pure Appl. Alg. \textbf{221} (2017), 1729--1844.
@@
  S.~Sinchuk, 
- \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2015.08.003}
- {On centrality of $K_2$ for Chevalley groups of type $\mathsf{E}_\ell$}},
+ \emph{On centrality of $K_2$ for Chevalley groups of type $\mathsf{E}_\ell$},
  J. Pure Appl. Alg. \textbf{220} (2016), no.~2, 857--875.
@@
  A.~Stavrova, 
- \emph{\href{https://dx.doi.org/10.1017/is013006012jkt232} 
- {Homotopy invariance of non-stable $\K_1$-functors}}, 
- J. K-th. \textbf{13} (2014), no.~2, 199--248.
+ \emph{Homotopy invariance of non-stable $\K_1$-functors}, 
+ J. K-Th. \textbf{13} (2014), no.~2, 199--248.
 
@@
  A.~Stavrova, 
- \emph{\href{https://dx.doi.org/10.1515/jgth-2019-0100} 
- {Chevalley groups of polynomial rings over Dedekind domains}}, 
+ \emph{Chevalley groups of polynomial rings over Dedekind domains}, 
  J. Gr. Th. \textbf{23} (2020), 121--132.
@@
  M.~R.~Stein, 
- \emph{\href{https://dx.doi.org/10.2307/2373742} 
- {Generators, relations and coverings of Chevalley groups over commutative rings}},
+ \emph{Generators, relations and coverings of Chevalley groups over commutative rings},
  Amer. J. Math. \textbf{93} (1971), no.~4, 965--1004.
@@
  M.~R.~Stein, 
- \emph{\href{https://dx.doi.org/10.2307/1996696} 
- {Surjective stability in dimension 0 for $\K_2$ and related functors}},
+ \emph{Surjective stability in dimension 0 for $\K_2$ and related functors},
  Trans. Amer. Math. Soc. \textbf{178} (1973), 165--191.
@@
  M.~R.~Stein, 
- \emph{\href{https://dx.doi.org/10.4099/math1924.4.77} 
- {Stability theorems for $\K_1$, $\K_2$ and related functors modeled on Chevalley groups}},
+ \emph{Stability theorems for $\K_1$, $\K_2$ and related functors modeled on Chevalley groups},
  Japan J. Math. \textbf{4} (1978), 77--108.
@@
  \emph{Lectures on Chevalley groups},
- Yale Univ. New Haven, 1967.
+ Yale Univ. New Haven, 1968.
 
@@
  A.~Suslin, 
- \emph{\href{http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} 
- {Projective modules over polynomial rings are free}}, 
+ \emph{Projective modules over polynomial rings are free}, 
  Dokl. Akad. Nauk SSSR \textbf{229} (1976), 1063--1066.
@@
  A.~Suslin, 
- \emph{\href{https://dx.doi.org/10.1070/IM1977v011n02ABEH001709} 
- {On the structure of the special linear group over commutative rings}},
+ \emph{On the structure of the special linear group over commutative rings},
  Math. USSR Izv. \textbf{11} (1977), 221--238.
@@
  A.~Suslin and V.~Kopeiko, 
- \emph{\href{https://dx.doi.org/10.1007/BF01681481} 
- {Quadratic modules and the orthogonal group over polynomial rings}},
+ \emph{Quadratic modules and the orthogonal group over polynomial rings},
  J. Soviet Math. \textbf{20} (1982), no.~6, 2665--2691.
@@
  A.~Suslin and M.~Tulenbaev, 
- \emph{\href{https://dx.doi.org/10.1007/BF01091768} 
- {Stabilization theorem for the Milnor $K_2$-functor}},
+ \emph{Stabilization theorem for the Milnor $K_2$-functor},
  J. Soviet Math. \textbf{17} (1981), no.~2, 1804--1819.
@@
  G.~Taddei, 
- \emph{\href{http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}
- {Normalit\'e des groupes \'el\'ementaires dans les groupes de Chevalley sur un anneau}},
+ \emph{Normalit\'e des groupes \'el\'ementaires dans les groupes de Chevalley sur un anneau},
  Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983),
@@
  M.~Tulenbaev, 
- \emph{\href{https://dx.doi.org/10.1070/SM1983v045n01ABEH002591}
- {The Steinberg group of a polynomial ring}},
+ \emph{The Steinberg group of a polynomial ring},
  Math. USSR Sb. \textbf{45} (1983), 131--144.
@@
  L.~Vaserstein, 
- \emph{\href{https://dx.doi.org/10.2748/tmj/1178228489}
- {On normal subgroups of Chevalley groups over commutative rings}},
+ \emph{On normal subgroups of Chevalley groups over commutative rings},
  Tohoku Math. J. \textbf{38} (1986), 219--230.
@@
  N.~Vavilov, 
- \emph{\href{http://eudml.org/doc/108535}
- {A third look at weight diagrams}}, 
+ \emph{A third look at weight diagrams}, 
  Rend. Sem. Mat. Univ. Padova \textbf{104} (2000), 201--250.
@@
  N.~Vavilov and E.~Plotkin, 
- \emph{\href{https://dx.doi.org/10.1007/BF00047884}
- {Chevalley groups over commutative rings: I. Elementary calculations}},
+ \emph{Chevalley groups over commutative rings: I. Elementary calculations},
  Acta Appl. Math. \textbf{45} (1996), 73--113.
@@
  N.~Vavilov and Z.~Zhang, 
- \emph{\href{https://dx.doi.org/10.1017/S0013091519000555}
- {Generation of relative commutator subgroups in Chevalley groups. II}},
+ \emph{Generation of relative commutator subgroups in Chevalley groups. II},
  Proc. Edinburgh Math. Soc. \textbf{63} (2020), no.~2, 497--511.
@@
  K.~V{\"o}lkel,
- \emph{\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}
- {Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
- Diplomarbeit, Uni. Freiburg.
+ \emph{Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie},
+ Diplomarbeit, Uni. Freiburg, 2011.
 

### 2020-07-10 horrocks.tex
Convert diagrams to TikZ

@@
 \usepackage[capitalize]{cleveref}
-\usepackage[matrix,arrow,curve]{xy}
-\usepackage{tikz}
+\usepackage{tikz,tikz-cd}
 \usepackage{enumitem}
@@
 \newtheorem{corollary}[lemma]{Corollary}
-\newtheorem{externaltheorem}[lemma]{Theorem}
 \theoremstyle{remark}
@@
 \numberwithin{corollary}{section}
-\numberwithin{externaltheorem}{section}
 \newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
@@
 \newcommand{\rG}{\mathsf{G}}
+\tikzcdset{scale cd/.style={every label/.append style={scale=#1},
+    cells={nodes={scale=#1}}}}
 
@@
 Then for any $\ell \geq 7$ the following commutative square is a pullback square in which all homomorphisms are injective:
-\begin{equation} \nonumber
-  \xymatrix{ \KO_2(2\ell, A) \ar[r] \ar[d] & \KO_2(2\ell, A[X]) \ar[d] \\ \KO_2(2\ell, A[X\inv]) \ar[r] & \KO_2(2\ell, A[X, X\inv]).}  
-\end{equation} 
+\[\begin{tikzcd} \KO_2(2\ell, A) \arrow{r} \arrow{d} & \KO_2(2\ell, A[X]) \arrow{d} \\ \KO_2(2\ell, A[X\inv]) \arrow{r} & \KO_2(2\ell, A[X, X\inv]). \end{tikzcd}\]
 Moreover, the same assertion holds if one replaces the functor $\KO_2(2\ell, -)$ with $\K_2(\rD_\ell, -)$ or $\St(\rD_\ell, -)$. \end{theorem}
@@
 Now if $M$ is the maximal ideal of $A$, the proof of the injectivity of $j_-$ comes down to proving the injectivity of the following two homomorphisms:
-\begin{equation*} \xymatrix{ \St(\rD_\ell, A[X^{-1}]) \ar[r]^(0.55){j_B^-} & \St(\rD_\ell, B) \ar[r]^{j_R} & \St(\rD_\ell, R), }\end{equation*}
+\[\begin{tikzcd} \St(\rD_\ell, A[X^{-1}]) \arrow{r}{j_B^-} & \St(\rD_\ell, B) \arrow{r}{j_R} & \St(\rD_\ell, R), \end{tikzcd} \]
 where $B = A[X\inv] + M[X]$ and $R = A[X, X\inv]$.
@@
 Then there is a split exact sequence of abelian groups
-\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ in which} \]
+\[\begin{tikzcd} 0 \arrow{r} & \K_2(\Phi, k) \arrow{r} & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & H(\Phi, k) \arrow{r} & 0, \end{tikzcd}\text{ in which}\]
 \[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^\times & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
-\begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^\times \ar[drr]_{\{-, X\}} \ar[r]^-{h}  & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
-                                                                                      &                                 & \K_2^\mathrm{M}(k(X)),} \]
+\begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian group
+\[\begin{tikzcd}[column sep=5pc] k^\times \arrow{drr}[swap]{\{-, X\}} \arrow{r}{h}  & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & \K_2(\Phi, k(X)) \arrow{d}{\cong} \\
+ & & \K_2^\mathrm{M}(k(X)), \end{tikzcd}\]
 in which $h = \{ -, X \}_{\alpha}$ and the vertical map is an isomorphism by Matsumoto's theorem.
@@
 Recall from~\cite{Mo04} that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
-\[ \xymatrix{ \K_1^\mathrm{MW}(k) \ar[r] \ar[d] & I(k) \ar[d] \\ \K_1(k) \ar[r] & I(k)/I^2(k), } \]
+\[ \begin{tikzcd} \K_1^\mathrm{MW}(k) \arrow{r} \arrow{d} & I(k) \arrow{d} \\ \K_1(k) \arrow{r} & I(k)/I^2(k), \end{tikzcd} \]
 in other words, it consists of pairs $[u, x]$ such that $x - \langle \langle u \rangle \rangle \in I^2(k)$.
@@
 \begin{proof} The first assertion follows from the commutative diagram
-\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
-               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}])} \]
+\[\begin{tikzcd}  & \K_2(\Phi, k) \arrow{dl}[swap]{\cong} \arrow[dr, hookrightarrow] & \\ \K_2(\Phi, k[X]) \arrow{rr} & & \K_2(\Phi, k[X, X^{-1}]) \end{tikzcd} \]
 and the injectivity of its diagonal arrows. Indeed, the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}.
@@
 In other words, it is the ring consisting of pairs of elements of~$R$ congruent modulo $I$.
-Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$.
-It is clear that $p_0 \Delta = p_1 \Delta = id_{R}$.
+Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map
+\begin{tikzcd} D_{R, I} \arrow[r, shift right=2] \arrow[r] & R. \arrow[l, shift right=2] \end{tikzcd} It is clear that $p_0 \Delta = p_1 \Delta = id_{R}$.
 
@@
 The homomorphism $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$.
-We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$: \begin{equation} \label{LodayRelativization} \xymatrix{ 1 \ar[r] & C_S(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1.} \end{equation}
+We denote this map by $\mu = \mu_{R,I}$ and its kernel by $C_S(R, I)$:
+\begin{equation} \label{LodayRelativization} \begin{tikzcd} 1 \arrow{r} & C_S(R, I) \arrow{r} & S(R, I) \arrow{r}{\mu} & S(R) \arrow{r} & S(R/I) \arrow{r} & 1. \end{tikzcd} \end{equation}
 
@@
 a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is $\nu$:
-\begin{equation} \label{RelativeCentralExtension}
- \xymatrix{ 1 \ar[r] & L \ar[r] & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1} \end{equation}
+\begin{equation} \label{RelativeCentralExtension} \begin{tikzcd} 1 \arrow{r} & L \arrow{r} & M \arrow{r}{\mu} & N \arrow{r}{\nu} & Q \arrow{r} & 1 \end{tikzcd} \end{equation}
 
@@
 Recall from p.~189 of~\cite{Ba74} that for $n\geq 3$ there is an exact sequence
-\begin{equation} \label{eq:Bass-ES} \xymatrix{1 \ar[r] & \mu_2(R) \ar[r] & \widetilde{P}_n(R) \ar[r] & P_n(R) \ar[r] & 1,}
-\end{equation}
+\begin{equation}\label{eq:Bass-ES} \begin{tikzcd} 1 \arrow{r} & \mu_2(R) \arrow{r} & \widetilde{P}_n(R) \arrow{r} & P_n(R) \arrow{r} & 1, \end{tikzcd} \end{equation}
 in which the group $\mu_2(R) = \{ a \in R^\times \mid a^2 = 1 \}$ is a central subgroup of $\widetilde{P}_n(R)$.
@@
 Notice that the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
-\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
+\[ \begin{tikzcd} 1 \arrow{r} & \K_2(\rD_n, R) \arrow{r} & \KO_2(2n, R) \arrow{r} & \mu_2(R) \arrow{r} & 1, \end{tikzcd} \]
 which is obtained from~\eqref{eq:Bass-ES} and the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
@@
 We conclude this subsection with the following stability result (see~\cite[Theorem~9.4]{Pa89}).
-\begin{externaltheorem}[Panin] \label{Panin-stability}
+\begin{theorem}[Panin] \label{Panin-stability}
  Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these three cases, respectively.
  Then the stability map $\KO_i(2n, R) \to \KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
- and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{externaltheorem}
+ and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
 
@@
 The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
-\begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
-then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
+\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
+then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups 
+\[ \begin{tikzcd} 0 \arrow{r} & \GW_i^{[k]}(R) \arrow{r} & \GW_i^{[k]}(R[X, X^{-1}]) \arrow{r} & \GW_{i-1}^{[k-1]}(R) \arrow{r} & 0. \end{tikzcd} \] \end{theorem}
 We will need only the special case $k=0$ of the above theorem, in which it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
@@
 and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
-\begin{equation*}\xymatrix{
- \KO_3(2\ell, B) \ar[r] \ar[d] & \KO_3(2\ell, k[X^{-1}]) \ar[d]_{f'} \ar@{->>}[r] & \ar[d]_{f} C(\rD_\ell, B, I) \\
- \KO_3(2\ell, R) \ar[r]        & \KO_3(2\ell, k[X, X^{-1}]) \ar@{->>}[r]        & C(\rD_\ell, R, I).}\end{equation*}
+\[\begin{tikzcd} \KO_3(2\ell, B) \arrow{r} \arrow{d} & \KO_3(2\ell, k[X^{-1}]) \arrow{d}[swap]{f'} \ar[r, twoheadrightarrow] & \ar{d}[swap]{f} C(\rD_\ell, B, I) \\
+ \KO_3(2\ell, R) \arrow{r} & \KO_3(2\ell, k[X, X^{-1}]) \ar[r, twoheadrightarrow] & C(\rD_\ell, R, I). \end{tikzcd} \]
 By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X^{-1}]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
@@
 Consider the following commutative square of canonical homomorphisms.
-\begin{equation*} \xymatrix{
-    \St(\Phi, B, I) \ar[r]^{\mu_B} \ar[d] & \St(\Phi, B) \ar[d] \\
-    \St(\Phi, R, I) \ar[r]^{\mu_R} \ar@{-->}^t[ur] & \St(\Phi, R) } \end{equation*}
+\[\begin{tikzcd} \St(\Phi, B, I) \arrow{r}{\mu_B} \arrow{d} & \St(\Phi, B) \arrow{d} \\ \St(\Phi, R, I) \arrow{r}{\mu_R} \ar[ur, "t", dashrightarrow] & \St(\Phi, R) \end{tikzcd} \]
 Then there exists a diagonal homomorphism $t$ which makes the diagram commute.   
@@
 
-\begin{externaltheorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical homomorphism $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{externaltheorem}
+\begin{theorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical homomorphism $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{theorem}
 \begin{proof}
  Consider the following commutative diagram with exact rows obtained from~\eqref{LodayRelativization}:
-\begin{equation*} \xymatrix{
- C(\rD_\ell, B, I) \ar[r]^{\lambda_B} \ar@{->>}[d]_{f} & \St(\rD_\ell, B, I) \ar[r]^{\mu_B} \ar[d]_{g} &
- \St(\rD_\ell, B) \ar[r]^{\nu_B} \ar[d]_{h} & \St(\rD_\ell, k[X^{-1}]) \ar[d]_{i} \\
- C(\rD_\ell, R, I) \ar[r]^{\lambda_R}         & \St(\rD_\ell, R, I) \ar[r]^{\mu_R} \ar@{-->}[ur]^{t}&
- \St(\rD_\ell, R) \ar[r]^-{\nu_R}        & \St(\rD_\ell, k[X, X^{-1}]).
-}\end{equation*}
+\[\begin{tikzcd} C(\rD_\ell, B, I) \arrow{r}{\lambda_B} \arrow[d, swap, "f", twoheadrightarrow] & \St(\rD_\ell, B, I) \arrow{r}{\mu_B} \arrow{d}[swap]{g} & \St(\rD_\ell, B) \arrow{r}{\nu_B} \arrow{d}[swap]{h} & \St(\rD_\ell, k[X^{-1}]) \arrow{d}[swap]{i} \\ C(\rD_\ell, R, I) \arrow{r}{\lambda_R} & \St(\rD_\ell, R, I) \arrow{r}{\mu_R} \arrow[ur, "t", dashrightarrow] & \St(\rD_\ell, R) \arrow{r}{\nu_R} & \St(\rD_\ell, k[X, X^{-1}]).\end{tikzcd}\]
 The lifting $t$ in the above diagram is obtained from~\cref{lem:lemma32}.
@@
 not necessarily simply-laced ones).
-\begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
-\end{externaltheorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
+\begin{theorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+\end{theorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
 \end{proof}
@@
 For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
-\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
+\begin{theorem}[Stepanov] \label{thm:Stepanov} 
 Let $S \subseteq \Phi$ be a parabolic subset of $\Phi$. Then the group $\overline{\St}(\Phi, R, I)$ is generated by the set $\mathcal{Z}(\Sigma_S, R, I)$.
- \end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+ \end{theorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
 
@@
 
-\begin{externaltheorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+\begin{theorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
 \end{proof}
@@
 Consider the following commutative diagram in which the vertical arrows are induced by the embedding $\Psi\subseteq\Phi$.
-  \begin{equation} \nonumber \xymatrix{
- F(\mathcal{X}_{\leq n+1}^\Psi) \ar[r]^{j_n^\Psi} \ar[d] & \St^{\leq n}(\Psi, B) \ar[d] \\
- F(\mathcal{X}_{\leq n+1}^\Phi) \ar[r]^{j_n^\Phi} & \St^{\leq n}(\Phi, B) }
- \end{equation}
+ \[\begin{tikzcd} F(\mathcal{X}_{\leq n+1}^\Psi) \arrow{r}{j_n^\Psi} \arrow{d} & \St^{\leq n}(\Psi, B) \arrow{d} \\ F(\mathcal{X}_{\leq n+1}^\Phi) \arrow{r}{j_n^\Phi} & \St^{\leq n}(\Phi, B) \end{tikzcd} \]
 The relation $R$ lies in the image of the left arrow, therefore it comes from some relation $R' \in \mathcal{R}^\Psi_{n+1}$.
@@
 Moreover, there is a short exact sequence of groups, which is split by the map $m \mapsto x_{-\alpha}(mX)$ (we denote by $(M, +)$ the additive group of the ideal $M$):
-\[\xymatrix{1 \ar[r] & \widetilde{P}_{\alpha,M}(0) \ar[r] & \widetilde{P}_{\alpha,M}(*) \ar@{->>}[r]^{p_\alpha} & (M, +) \ar@<5pt>@{-->}[l] \ar[r] & 1}.\] \end{lemma}
+\[\begin{tikzcd} 1 \arrow{r} & \widetilde{P}_{\alpha,M}(0) \arrow{r} & \widetilde{P}_{\alpha,M}(*) \ar[r, "p_\alpha", twoheadrightarrow] & (M, +) \arrow[l, dashrightarrow, shift left=2] \arrow{r} & 1.
+\end{tikzcd} \] \end{lemma}
 \begin{proof} We need to verify that the conjugate by $x_{-\alpha}(mX)$ of every generator $g$ of $\widetilde{P}_\alpha(0)$ listed in~\cref{defP0} belongs to $\widetilde{P}_\alpha(0)$.
@@
 Notice that both $Z_\alpha(A, M)$ and $K(A[X], M[X])$ are stable under the specified conjugation, which implies the assertion for $\widetilde{P}_{\alpha, M}(*)$. 
-To obtain the assertion for $\widetilde{P}_{\alpha, M}(0)$ consider the following commutative diagram.
-\[ \xymatrix{ \widetilde{P}_{\alpha, M}(0) \ar@{^{(}->}[r] \ar@{^{(}->}[d] & \widetilde{P}_{\alpha, M}(*) \ar@{->>}[r]^{p_{\alpha, M}} \ar@{^{(}->}[d] & (M, +) \ar@{^{(}->}[d] \\ \widetilde{P}_{\alpha, A}(0) \ar@{^{(}->}[r] & \widetilde{P}_{\alpha, A}(*) \ar@{->>}[r]^{p_{\alpha, A}} & (A, +)} \]
+To obtain the assertion for $\widetilde{P}_{\alpha, M}(0)$ consider the following commutative diagram:
+\[\begin{tikzcd} \widetilde{P}_{\alpha, M}(0) \arrow[r, hookrightarrow] \arrow[d, hookrightarrow] & \widetilde{P}_{\alpha, M}(*) \arrow[r, "p_{\alpha, M}", twoheadrightarrow] \ar[d, hookrightarrow] & (M, +) \ar[d, hookrightarrow] \\ \widetilde{P}_{\alpha, A}(0) \ar[r, hookrightarrow] & \widetilde{P}_{\alpha, A}(*) \ar[r, "p_{\alpha, A}", twoheadrightarrow] & (A, +).
+\end{tikzcd} \]
 Notice that $x_\beta(b) \in \widetilde{P}_{\alpha, A}(0)$, therefore for $g \in \widetilde{P}_{\alpha, M}(0)$ one has \[p_{\alpha, M}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(x_\beta(b) \cdot g \cdot x_\beta(-b)) = p_{\alpha, A}(g) = 0,\] which implies the assertion.\end{proof}
@@
 Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
-\newline \scalebox{0.80}{\begin{minipage}{1.15\linewidth}
-\[\xymatrix{ G_M^0 \ar@{^{(}->}[rr]^{i_+^M} \ar@<-5pt>@{^{(}->}[dd]^{i_-^M} \ar@<-5pt>@{^{(}->}[rd] & & \overline{\St}(\Phi, A[X], M[X]) \ar[dd]_(.3){j_+^M} \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A) \ar@{^{(}->}[rr]^(.3){i_+} \ar@<-2.5pt>@{^{(}->}[dd]^(.3){i_-} & & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \ar@<-2.5pt>@{^{(}->}[rd] \ar[rr]^(.35){j_-^M} & & \overline{\St}(\Phi, R, I) \ar@<-2.5pt>@{^{(}->}[rd] & \\ & \St(\Phi, A[X\inv]) \ar[rr]_{j_-} & & \St(\Phi, R).} \]\end{minipage}} \vskip \belowdisplayshortskip
+\[\begin{tikzcd}[scale cd=0.8]
+   G_M^0 \arrow[rr, "i_+^M", hookrightarrow] \arrow[dd, "i_-^M", hookrightarrow] \arrow[rd, hookrightarrow] & & \overline{\St}(\Phi, A[X], M[X]) \arrow[dd, "j_+^M", swap, near start] \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A) \arrow[rr, "i_+", near start, hookrightarrow] \arrow[dd, "i_-", near start, hookrightarrow] & & \St(\Phi, A[X]) \arrow{dd}{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \arrow[rd, hookrightarrow] \arrow[rr, "j_-^M", near start] & & \overline{\St}(\Phi, R, I) \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A[X\inv]) \arrow{rr}[swap]{j_-} & & \St(\Phi, R).
+  \end{tikzcd}\]
 Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
@@
 The isomorphism between the sets $\overline{V}$ and $\overline{V}_T$ is given by the following two maps, which are easily seen to be mutually inverse to each other:
-\begin{equation} \label{eq:VVT} \xymatrix @R0.3pc {\overline{V} \ar[r]^{\cong} & \ar[l] \overline{V}_T \\ (g, [h], u) \ar@{|->}[r] & [p(g, h, u), h^{-1}, u] \\ (p \cdot j_-(h) \cdot \{u, X\}, [h^{-1}], u) & \ar@{|->}[l] [p, h, u].
-} \end{equation}
+\begin{equation} \label{eq:VVT} \begin{tikzcd}[row sep=tiny] \overline{V} \arrow{r}{\cong} & \arrow{l} \overline{V}_T \\ (g, [h], u) \arrow[r, mapsto] & \left[p(g, h, u), h^{-1}, u\right] \\ (p \cdot j_-(h) \cdot \{u, X\}, [h^{-1}], u) & \arrow[l, mapsto] [p, h, u].
+\end{tikzcd} \end{equation}
 The above isomorphism allows us to regard $\overline{V}$ and $\overline{V}_T$ as the same object, for elements of which we can interchangeably use either of the two notations,
@@
 Consider the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
-\begin{equation} \label{big-picture}
- \xymatrix{ & \St(\Phi, A[X], M[X]) \ar[r]_(0.55){\mu_{A[X]}} \ar[d] & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ & \St(\Phi, R, I) \ar[d]^t & \\ \St(\Phi, A[X\inv]) \ar[r]^{j_B^-} & \St(\Phi, B) \ar[r]^{j_R} & \St(\Phi, R).
-} \end{equation}
+\begin{equation} \label{big-picture} \begin{tikzcd} & \St(\Phi, A[X], M[X]) \arrow{r}[swap]{\mu_{A[X]}} \arrow{d} & \St(\Phi, A[X]) \arrow{dd}{j_+} \\ & \St(\Phi, R, I) \arrow{d}{t} & \\ \St(\Phi, A[X\inv]) \arrow{r}{j_B^-} & \St(\Phi, B) \arrow{r}{j_R} & \St(\Phi, R).
+\end{tikzcd} \end{equation}
 Notice that the subgroup $\overline{G}_M^{\geq 0}$ (see~\cref{df:GM0_geq0}) coincides with the image of $j_+\mu_{A[X]}$.
@@
  Then the homomorphism $j_-$ is injective and the following commutative square is pullback
- \begin{equation} \nonumber
-  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]).}
- \end{equation}
+ \[ \begin{tikzcd} \St(\Phi, A) \arrow{r} \arrow{d} & \St(\Phi, A[X]) \arrow{d}{j_+} \\ \St(\Phi, A[X\inv]) \arrow{r}{j_-} & \St(\Phi, A[X, X\inv]). \end{tikzcd} \] 
 \end{theorem}

### 2020-07-17 horrocks.tex
Restore externaltheorem

@@
 We conclude this subsection with the following stability result (see~\cite[Theorem~9.4]{Pa89}).
-\begin{theorem}[Panin] \label{Panin-stability}
+\begin{externaltheorem}[Panin] \label{Panin-stability}
  Let $R$ be either a field, principal ideal domain or a Dedekind domain. Set $a = 1,2$ or $3$ in each of these three cases, respectively.
  Then the stability map $\KO_i(2n, R) \to \KO_i(2(n+1), R)$ is an epimorphism for $n \geq b$ 
- and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{theorem}
+ and an isomorphism for $n \geq b + 1$, where $b = \mathrm{max}(2i, a+i-1)$. \end{externaltheorem}
 
@@
 The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
-\begin{theorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
+\begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
 then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups 
-\[ \begin{tikzcd} 0 \arrow{r} & \GW_i^{[k]}(R) \arrow{r} & \GW_i^{[k]}(R[X, X^{-1}]) \arrow{r} & \GW_{i-1}^{[k-1]}(R) \arrow{r} & 0. \end{tikzcd} \] \end{theorem}
+\[ \begin{tikzcd} 0 \arrow{r} & \GW_i^{[k]}(R) \arrow{r} & \GW_i^{[k]}(R[X, X^{-1}]) \arrow{r} & \GW_{i-1}^{[k-1]}(R) \arrow{r} & 0. \end{tikzcd} \] \end{externaltheorem}
 We will need only the special case $k=0$ of the above theorem, in which it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
@@
 not necessarily simply-laced ones).
-\begin{theorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
-\end{theorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
+\begin{externaltheorem}[Stein--Tits--Vaserstein] \label{thm:Tits} The group $\overline{\St}(\Phi, R, I)$ is generated (as an abstract group) by elements $z_\alpha(s, \xi)$, $\alpha \in \Phi$, $s \in I$, $\xi \in R$.
+\end{externaltheorem} \begin{proof} See e.\,g.~\cite[Theorem 2]{Va86}.
 \end{proof}
@@
 For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
-\begin{theorem}[Stepanov] \label{thm:Stepanov} 
+\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
 Let $S \subseteq \Phi$ be a parabolic subset of $\Phi$. Then the group $\overline{\St}(\Phi, R, I)$ is generated by the set $\mathcal{Z}(\Sigma_S, R, I)$.
- \end{theorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
+ \end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
 
@@
 
-\begin{theorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
+\begin{externaltheorem}[Stein] \label{thm:Stein} One has \[\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \myol{H}(\Phi, A, M) \cdot U(\Phi^-, M).\] \end{externaltheorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}.
 \end{proof}

### 2020-07-17 horrocks.tex
Fix misprint

@@
 \[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^\times & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
-\begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian group
+\begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
 \[\begin{tikzcd}[column sep=5pc] k^\times \arrow{drr}[swap]{\{-, X\}} \arrow{r}{h}  & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & \K_2(\Phi, k(X)) \arrow{d}{\cong} \\

### 2020-07-23 horrocks.tex
Replace sharp by acute

@@
       [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
- where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
+ where $\beta$ is any root of $\Phi$ forming an acute angle with $\alpha$.
  A standard argument, cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}, shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.
@@
 For the rest of this subsection $M$ is the maximal ideal $A$.
-We denote by $\beta$ another fixed root of $\Phi$ forming a sharp angle with $\alpha$ (i.\,e.
+We denote by $\beta$ another fixed root of $\Phi$ forming an acute angle with $\alpha$ (i.\,e.
 $\langle \alpha, \beta \rangle = 1$).
@@
 It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
-By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e.
+By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms an acute angle with $\alpha$, i.\,e.
 $\alpha-\delta \in \Phi$.
@@
 \subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties} \label{sec:S-a}
-Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming a sharp angle.
+Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming an acute angle.
 
@@
 \begin{proof}
-Let $a, b \in A$ and $\alpha$, $\beta$ be a pair of roots forming a sharp angle.
+Let $a, b \in A$ and $\alpha$, $\beta$ be a pair of roots forming an acute angle.
 Set $\epsilon = N_{\alpha,-\beta}$.

### 2020-08-06 horrocks.tex
Fix misprints

@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on an arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
+Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on an arbitrary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
 
@@
 
-Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
+Whenever we speak of the Steinberg group $\St(\Psi, R)$ parameterized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
  for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the mapping $x_\alpha(\xi) \mapsto x_\alpha(\xi)$ yields a group homomorphism $\St(\Psi, R) \to \St(\Phi, R)$).
@@
               \label{eq:h-inv}    h_\alpha(t)^{-1}             & = h_{-\alpha}(t). \end{align}
-In the above formulae $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$ (we denote by $(\text{-},\text{-})$ the inner product on the euclidean space $\mathbb{R}^\ell$ containing $\Phi$).
+In the above formulae $\langle \beta, \alpha \rangle$ denotes the integer $\tfrac{2(\beta, \alpha)}{(\alpha, \alpha)}$ (we denote by $(\text{-},\text{-})$ the inner product on the Euclidean space $\mathbb{R}^\ell$ containing $\Phi$).
 
@@
 \begin{itemize}
- \item $A$ denotes an arbitarary commutative ring and $M$ is an ideal of $A$. Starting from subsection~\ref{sec:Pa0-basic} we also assume that $A$ is local and $M$ is the maximal ideal of $A$.
+ \item $A$ denotes an arbitrary commutative ring and $M$ is an ideal of $A$. Starting from subsection~\ref{sec:Pa0-basic} we also assume that $A$ is local and $M$ is the maximal ideal of $A$.
  \item We denote by $R$ the Laurent polynomial ring $A[X, X^{-1}]$. We set $t = X^{-1}$, so that $R = A[X, X^{-1}] = A[t, t^{-1}]$.
@@
 Fix a root $\delta \in \Phi \setminus \Psi$.
-Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parametrized by $\xi \in A[X]$, $f\in M[X]$:
+Define $\widetilde{K}(\alpha, \beta)$ as the subgroup of $\overline{\St}(\Phi, A[X], M[X])$ generated by the following 5 families of elements parameterized by $\xi \in A[X]$, $f\in M[X]$:
  \begin{enumerate}[label=(K\arabic*)]
@@
 Before we proceed with the proof of~\cref{thm:P1glueing} let us briefly recall the relevant notation.
-As before, $A$ denotes an arbitary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both the ring $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
+As before, $A$ denotes an arbitrary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both the ring $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
 
@@
 In order to achieve this we need to show that $\St(\Phi, B)$ acts transitively on the first components of the triples from $\overline{V}_T$.
-These first components are parametrized by cosets $\overline{G}_M^{\geq 0}/G_M^0$ (cf.~\eqref{VT-def}).
+These first components are parameterized by cosets $\overline{G}_M^{\geq 0}/G_M^0$ (cf.~\eqref{VT-def}).
 It is clear from~\eqref{big-picture} that $\overline{G}_M^{\geq 0}$ lies in the image of $j_R$.
@@
  J.~Hurrelbrink, 
- \emph{Endlich pr\"asentierte arithmetische gruppen und $K_{2}$ {\"u}ber Laurent-polynomringen},
+ \emph{Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
  Math. Ann. \textbf{225} (1977), no.~2, 123--129.
@@
  A.~Lavrenov and S.~Sinchuk,
- \emph{entrality of odd orthogonal $\K_2$},
+ \emph{Centrality of odd orthogonal $\K_2$},
  J. Pure Appl. Alg. \textbf{221} (2017), 1134--1145.

### 2020-08-10 horrocks.tex
Fix misprint

@@
 We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
-The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre’s problem,  whose positive solution is currently known only in the linear case.
+The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem,  whose positive solution is currently known only in the linear case.
 \EndAbstract

### 2020-09-08 dl-paper.tex
Fix mispring
Merge with release

@@
-%
-%    Documenta-LaTeX.sty (2e)
-%
-%    Version 0.52
-%
-%    Copyright (C) 1996-2017 Ulf Rehmann
-%    rehmann@math.uni-bielefeld.de
-%
-% ------------------------------ PROLOGUE -----------------------------
-%
-% This prologue is to be prepended to your LaTeX file in order to
-% give it the layout required by Documenta Mathematica.
-% Please edit the \documentclass line below, add \usepackage lines
-% according to your needs and
-% go to the line starting with \Title below, fill in title,
-% authors' names and so on and follow the further instructions there.
-% 
-% Choose one of the commands \documentclass[]{} or \documentstyle[]{}
-% depending on the version of LaTeX you use:
-%
-%
-% If you use LaTeX 2e use the following line (or similar):
-\documentclass[10pt,a4paper,twoside]{article}
-%%\usepackage{hyperref}
-% Append here commands \usepackage{...} if you want.
-%
-% If you use LaTeX 2.09 or earlier use the following line (or similar):
-%\documentstyle[10pt,twoside]{article}
-%
-% Please go to the line starting with \Title below, fill in title,
-% authors' names and so on and follow the further instructions there.
-%
-% The final values of the following 4 uncommented lines will be filled in
-% by Doc. Math. after the manuscript has been accepted for publication.
-%
-\def\YEAR{\year}\newcount\VOL\VOL=\YEAR\advance\VOL by-1995
-\def\firstpage{1}\def\lastpage{1000}
-\def\received{}\def\revised{}
-\def\communicated{}
-%
-
-\makeatletter
-\def\magnification{\afterassignment\m@g\count@}
-\def\m@g{\mag=\count@\hsize6.5truein\vsize8.9truein\dimen\footins8truein}
-\makeatother
-
-%%% Choose 10pt/12pt:
-%\oddsidemargin1.66cm\evensidemargin1.66cm\voffset1.2cm%10pt
-\oddsidemargin1.91cm\evensidemargin1.91cm\voffset1.4cm%10pt
-%\magnification1200\oddsidemargin.41cm\evensidemargin.41cm\voffset-.75cm%12pt
-
-%\textwidth12.5cm\textheight19.5cm
-\textwidth12.0cm\textheight19.0cm
-
-\font\eightrm=cmr8
-\font\caps=cmcsc10                    % Theorem, Lemma etc
-\font\ccaps=cmcsc10                   % Sections
-\font\Caps=cmcsc10 scaled \magstep1   % Title
-\font\scaps=cmcsc8
-
-%
-%-----------------headlines-----------------------------------
+\documentclass[oneside, 8pt]{amsart}
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
 \usepackage[breaklinks=false,unicode]{hyperref}
-\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
+\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
+\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
+\usepackage{color} 
 \usepackage[capitalize]{cleveref}
-\usepackage[matrix,arrow,curve]{xy}
-\usepackage{tikz}
+\usepackage{tikz,tikz-cd}
 \usepackage{enumitem}
@@
 \newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, book]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \renewcommand*{\bibfont}{\footnotesize}
-\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}
 
@@
 
+\newlist{proplist}{enumerate}{1} \setlist[proplist]{label=(\roman{proplisti}), ref=\thethm.(\roman{proplisti}),noitemsep} \Crefname{proplisti}{Proposition}{Propositions}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelem.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
+
 \DeclareMathOperator{\Ker}{Ker}
@@
 \DeclareMathOperator{\St}{St}
+\DeclareMathOperator{\GG}{G}
 \DeclareMathOperator{\E}{E}
@@
 \newcommand{\myol}[2][3]{{}\mkern#1mu\overline{\mkern-#1mu#2}}
-\newcommand{\GG}{\mathrm{G}_{\mathrm{sc}}}
+
 \newcommand{\ZZ}{\mathbb{Z}}
@@
 
-\pagestyle{myheadings}
-\pagenumbering{arabic}
-\setcounter{page}{\firstpage}
-\def\bfseries{\normalsize\caps}
-
-\makeatletter
-\setlength\topmargin {14\p@}
-\setlength\headsep   {15\p@}  
-\setlength\footskip  {25\p@}  
-\setlength\parindent {20\p@} 
-\@specialpagefalse\headheight=8.5pt
-\def\DocMath{{\def\th{\thinspace}\scaps Documenta Math.}}
-\renewcommand{\@oddfoot}{\hfill\scaps Documenta Mathematica 
-    \number\VOL\  (\number\YEAR) \number\firstpage--\lastpage\hfill}
-\renewcommand{\@evenfoot}{\ifnum\thepage>\lastpage\hfill\scaps
-    Documenta Mathematica \number\VOL\  (\number\YEAR)\hfill\else\@oddfoot\fi}%
-
-\renewcommand{\@evenhead}{%
-    \ifnum\thepage>\lastpage\rlap{\thepage}\hfill%
-    \else\rlap{\thepage}\slshape\leftmark\hfill{\caps\SAuthor}\hfill\fi}%
-\renewcommand{\@oddhead}{%
-    \ifnum\thepage=\firstpage{\DocMath\hfill\llap{\thepage}}%
-    \else{\slshape\rightmark}\hfill{\caps\STitle}\hfill\llap{\thepage}\fi}%
-\makeatother
-
-\def\TSkip{\bigskip}
-\newbox\TheTitle{\obeylines\gdef\GetTitle #1
-\ShortTitle  #2
-\SubTitle    #3
-\Author      #4
-\ShortAuthor #5
-\EndTitle
-{\setbox\TheTitle=\vbox{\baselineskip=20pt\let\par=\cr\obeylines%
-\halign{\centerline{\Caps##}\cr\noalign{\medskip}\cr#1\cr}}%
-	\copy\TheTitle\TSkip\TSkip%
-\def\next{#2}\ifx\next\empty\gdef\STitle{#1}\else\gdef\STitle{#2}\fi%
-\def\next{#3}\ifx\next\empty%
-    \else\setbox\TheTitle=\vbox{\baselineskip=20pt\let\par=\cr\obeylines%
-    \halign{\centerline{\caps##} #3\cr}}\copy\TheTitle\TSkip\TSkip\fi%
-%\setbox\TheTitle=\vbox{\let\par=\cr\obeylines%
-%\halign{\centerline{\caps##} #4\cr}}\copy\TheTitle\TSkip\TSkip%
-\centerline{\caps #4}\TSkip\TSkip%
-\def\next{#5}\ifx\next\empty\gdef\SAuthor{#4}\else\gdef\SAuthor{#5}\fi%
-\ifx\received\empty\relax
-    \else\centerline{\eightrm Received: \received}\fi%
-\ifx\revised\empty\TSkip%
-    \else\centerline{\eightrm Revised: \revised}\TSkip\fi%
-\ifx\communicated\empty\relax
-    \else\centerline{\eightrm Communicated by \communicated}\fi\TSkip\TSkip%
-\catcode'015=5}}\def\Title{\obeylines\GetTitle}
-\def\Abstract{\begingroup\narrower
-    \parskip=\medskipamount\parindent=0pt{\caps Abstract. }}
-\def\EndAbstract{\par\endgroup\TSkip}
-
-\long\def\MSC#1\EndMSC{\def\arg{#1}\ifx\arg\empty\relax\else
-     {\par\narrower\noindent%
-     2010 Mathematics Subject Classification: #1\par}\fi}
-
-\long\def\KEY#1\EndKEY{\def\arg{#1}\ifx\arg\empty\relax\else
-	{\par\narrower\noindent Keywords and Phrases: #1\par}\fi\TSkip}
-
-\newbox\TheAdd\def\Addresses{\vfill\copy\TheAdd\vfill
-    \ifodd\number\lastpage\vfill\eject\phantom{.}\vfill\eject\fi}
-{\obeylines\gdef\GetAddress #1
-\Address #2 
-\Address #3
-\Address #4
-\EndAddress
-{\def\xs{4.8truecm}\parindent=0pt
-\setbox0=\vtop{{\obeylines\hsize=\xs#1\par}}\def\next{#2}
-\ifx\next\empty % 1 address
-     \setbox\TheAdd=\hbox to\hsize{\hfill\copy0\hfill}
-\else\setbox1=\vtop{{\obeylines\hsize=\xs#2\par}}\def\next{#3}
-\ifx\next\empty % 2 addresses
-     \setbox\TheAdd=\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
-\else\setbox2=\vtop{{\obeylines\hsize=\xs#3\par}}\def\next{#4}
-\ifx\next\empty\ % 3 addresses
-     \setbox\TheAdd=\vtop{\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
-                \vskip20pt\hbox to\hsize{\hfill\copy2\hfill}}
-\else\setbox3=\vtop{{\obeylines\hsize=\xs#4\par}}
-     \setbox\TheAdd=\vtop{\hbox to\hsize{\hfill\copy0\hfill\copy1\hfill}
-	        \vskip20pt\hbox to\hsize{\hfill\copy2\hfill\copy3\hfill}}
-\fi\fi\fi\catcode'015=5}}\gdef\Address{\obeylines\GetAddress}
-
-\hfuzz=0.1pt\tolerance=2000\emergencystretch=20pt\overfullrule=5pt
-
-%%%%% Embedded files should be stored in a separate subdirectory named
-%%%%% <filename>.files where <filename> is the same as the name of the
-%%%%% main tex file without the extension .tex.
-
-%%%%% In order for tex to find those embedded files, \input and
-%%%%% \includegraphics commands etc. have to reflect the embedded
-%%%%% files path by using the '\LOCAL' macro defined below, like
-%%%%% \input{\LOCAL/introduction} for embedding a file named
-%%%%% 'introduction.tex', or
-%%%%% \includegraphics[width=0.95\textwidth]{\LOCAL/knot.eps} for
-%%%%% embedding a graphics file named 'knot.eps', or
-%%%%% \bibselect{\LOCAL/references} in case references are embedded
-%%%%% from a file named 'references.ltb' etc.
-
-%%%%% Graphics files should always be submitted in encapsulated
-%%%%% postscript format (extension '.eps').
-
-\def\LOCAL{\jobname.files}
+\title{A Horrocks-type theorem for even orthogonal $K_2$}
+\keywords {Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing. {\em Mathematical Subject Classification (2010):} 19C20}
+\author{Andrei Lavrenov}
+\email{avlavrenov at gmail.com}
+\author {Sergey Sinchuk}
+\email {sinchukss at gmail.com}
+
+\address{Chebyshev Laboratory, St. Petersburg State University, 14th. Line V.O. 29b, 199178, St. Petersburg, Russia}
+
+\date {\today}
 
 \begin{document}
-%%%%% ------------- fill in your data below this line  -------------------
-%%%%%    The following lines \Title ... \EndAddress must ALL be present
-%%%%%    and in the given order.
-\Title
-A Horrocks-type theorem for even orthogonal $K_2$
-\ShortTitle 
-A Horrocks-type theorem for $\mathrm{KO}_2$ 
-\SubTitle   
-%%%%%    A possible subtitle goes here.
-\Author 
-Andrei Lavrenov, Sergey Sinchuk
-\ShortAuthor 
-Lavrenov and Sinchuk
-\EndTitle
-\Abstract 
-We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
-The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, positive solution of which currently is only known in the linear case.
-\EndAbstract
-\MSC 
-19C20
-\EndMSC
-\KEY 
-Steinberg group, $K_2$-functor, Quillen--Suslin theorem, Horrocks theorem, $\mathbb{P}^1$--glueing.
-\EndKEY
-%%%%%    All 4 \Address lines below must be present. To center the last
-%%%%%    entry, no empty lines must be between the following \Address
-%%%%%    and \EndAddress lines.
-\Address
-Andrei Lavrenov
-avlavrenov@gmail.com
-\Address
-Sergey Sinchuk
-sinchukss@gmail.com
-\Address
-Chebyshev laboratory, 
-St. Petersburg State University, 
-14th. Line V.O. 29b
-199178, St. Petersburg, Russia
-\Address
-\EndAddress
-%%
-%%       Make sure the last tex command in your manuscript
-%%       before the first \end{document} is the command  \Addresses
-%%
-%%---------------------Here the prologue ends---------------------------------
-%%--------------------Here the manuscript starts------------------------------
-
-%%--------------------Here the manuscript ends--------------------------------
-\Addresses
+\begin{abstract} We prove the Horrocks theorem for unstable even-dimensional orthogonal Steinberg groups.
+The Horrocks theorem for Steinberg groups is one of the principal ingredients needed for the proof of the $\K_2$-analogue of Serre's problem,  whose positive solution is currently known only in the linear case.
+\end{abstract}
+\maketitle
 \section{Introduction}
@@
 Then there is a split exact sequence of abelian groups
-\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ in which} \]
+\[\begin{tikzcd} 0 \arrow{r} & \K_2(\Phi, k) \arrow{r} & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & H(\Phi, k) \arrow{r} & 0, \end{tikzcd}\text{ in which}\]
 \[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^\times & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
-\[\xymatrixcolsep{5pc}\xymatrix{k^\times \ar[r]^-{h} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
-                                                                                      &                                 & \K_2^\mathrm{M}(k(X)),} \]
+\[\begin{tikzcd}[column sep=5pc] k^\times \arrow{drr}[swap]{\{-, X\}} \arrow{r}{h}  & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & \K_2(\Phi, k(X)) \arrow{d}{\cong} \\
+ & & \K_2^\mathrm{M}(k(X)), \end{tikzcd}\]
 in which $h = \{ -, X \}_{\alpha}$ and the vertical map is an isomorphism by Matsumoto's theorem.
@@
 Recall that {\it the double ring} $D_{R, I}$ of a pair $(R, I)$ is, by definition, the pullback ring $R \times_{R/I} R$.
-In other words, it is the ring consisting of pairs of elements of $R$ congruent modulo $I$.
-Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$.
-It is clear that $p_0 \Delta = p_1 \Delta = id_{R}$.
+In other words, it is the ring consisting of pairs of elements of~$R$ congruent modulo $I$.
+Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map
+\begin{tikzcd} D_{R, I} \arrow[r, shift right=2] \arrow[r] & R. \arrow[l, shift right=2] \end{tikzcd} It is clear that $p_0 \Delta = p_1 \Delta = id_{R}$.
 
@@
 \begin{externaltheorem}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^\times$, 
-then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{externaltheorem}
+then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups 
+\[ \begin{tikzcd} 0 \arrow{r} & \GW_i^{[k]}(R) \arrow{r} & \GW_i^{[k]}(R[X, X^{-1}]) \arrow{r} & \GW_{i-1}^{[k-1]}(R) \arrow{r} & 0. \end{tikzcd} \] \end{externaltheorem}
 We will need only the special case $k=0$ of the above theorem, in which it turns into an earlier result of J.~Hornbostel, see~\cite[Corollary~5.3]{Ho05}.
@@
 \item In the case $0 < d \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{0,e-d}$:
-\newline
-\scalebox{0.85}{\begin{minipage}{1.16\linewidth}
-\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = 
-[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \label{first-computation} \\ 
+\begin{align} x_{\alpha+\beta+\gamma}(-\epsilon_1 \epsilon_2 \cdot abt^e) = \hspace{4cm} \label{first-computation} \\ =
+[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), [x_{-\beta}(t^d), x_{\alpha+\beta}(-\delta_1 \cdot a)] ] & \text{ by $\text{R2}_{d,0}$, $\text{R2}_{d, e-d}$} \nonumber \\ 
  = [[x_{\beta+\gamma}(\epsilon_1 \cdot bt^{e-d}), x_{-\beta}(t^d)], {}^{x_{-\beta}(t^d)} x_{\alpha+\beta}(- \delta_1 \cdot a)] & \text{ by~\eqref{eq:H1iii}, $\text{R3}^\bot_{0,e-d}$} \nonumber \\ 
@@
  = {}^{x_\gamma(bt^e)}x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by~\eqref{eq:H1ii}, $\text{R2}_{e-d,d}$} \nonumber \\
- = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}\end{minipage}} \vskip \belowdisplayshortskip
+ = x_{\alpha+\beta+\gamma}(-\epsilon_1\epsilon_2 \cdot abt^e) \cdot [x_\gamma(bt^e), x_\alpha(at^d)] & \text{ by $\text{R3}^\angle_{e,e}$}, \nonumber \end{align}
  where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$, $\delta_1 = N_{\alpha,\beta}$ and in the 4th equality we use~\eqref{eq:cocycle}.
@@
 
-\subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties.} \label{sec:S-a}
-Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming a sharp angle.
+\subsection{The map \texorpdfstring{$S_\alpha(a, -)$}{S(a,-)} and its properties} \label{sec:S-a}
+Throughout this section $(A, M)$ is a local pair and, as before, $\alpha, \beta$ are some fixed roots of $\Phi$ forming an acute angle.
 
@@
 
-\subsection{Proof of Horrocks theorem.} \label{sec:P1glueing}
+\subsection{Proof of Horrocks theorem} \label{sec:P1glueing}
 Before we proceed with the proof of~\cref{thm:P1glueing} let us briefly recall the relevant notation.
-As before, $A$ denotes an arbitary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both the ring $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
+As before, $A$ denotes an arbitrary local ring with maximal ideal $M$ and $I = M[X, X\inv]$ is an ideal of both the ring $R=A[X, X\inv]$ and its subring $B = A[X\inv] + M[X]$.
 
 Consider the following commutative diagram, in which the map $t$ is obtained from~\cref{lem:lemma32}:
-\begin{equation} \label{big-picture}
- \xymatrix{ & \St(\Phi, A[X], M[X]) \ar[r]_(0.55){\mu_{A[X]}} \ar[d] & \St(\Phi, A[X]) \ar[dd]^{j_+} \\ & \St(\Phi, R, I) \ar[d]^t & \\ \St(\Phi, A[X\inv]) \ar[r]^{j_B^-} & \St(\Phi, B) \ar[r]^{j_R} & \St(\Phi, R).
-} \end{equation}
+\begin{equation} \label{big-picture} \begin{tikzcd} & \St(\Phi, A[X], M[X]) \arrow{r}[swap]{\mu_{A[X]}} \arrow{d} & \St(\Phi, A[X]) \arrow{dd}{j_+} \\ & \St(\Phi, R, I) \arrow{d}{t} & \\ \St(\Phi, A[X\inv]) \arrow{r}{j_B^-} & \St(\Phi, B) \arrow{r}{j_R} & \St(\Phi, R).
+\end{tikzcd} \end{equation}
 Notice that the subgroup $\overline{G}_M^{\geq 0}$ (see~\cref{df:GM0_geq0}) coincides with the image of $j_+\mu_{A[X]}$.

### 2020-09-08 dl-paper.tex
Purge most of the scaleboxes

@@
 Notice that~\ref{C3} is an obvious consequence of~\eqref{Chevalley-CCF2}. Let us verify the first two assertions. Suppose that $\alpha + \beta \in \Phi$.  We have that
-\newline \scalebox{.88}{\begin{minipage}{1.13\linewidth} \begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
- = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
+\begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
+ = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
  Now suppose that $\alpha - \beta \in \Phi$. We have that
-\newline \scalebox{.86}{\begin{minipage}{1.16\linewidth}\begin{align*} \nonumber
+\begin{align*} \nonumber
 \begin{split}[[x_\beta(s),\ x_{-\beta}(t)],\ x_{\alpha}(\xi)] = {}^{x_\beta(s)}\!\bigl( {}^{x_{-\beta}(t)}[x_\beta(-s),\ [x_{-\beta}(-t),\ x_{\alpha}(\xi)]] \cdot \hspace{50pt} \\ \cdot {}^{x_{\alpha}(\xi)}[x_{-\beta}(t),\ [ x_{\alpha}(-\xi),\ x_\beta(-s)]] \bigr)^{} & \text{ by~\eqref{HW-variant}}\end{split} \\
 = {}^{x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}\left(-N_{\beta, \alpha-\beta} \cdot N_{\alpha,-\beta} \cdot s t \xi\right) = {}^{ x_\beta(s) \cdot x_{-\beta}(t)}x_{\alpha}(s t \xi) & \text{ by~\eqref{Chevalley-CCF1},\eqref{Chevalley-CCF2}}\\
-= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
+= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}
 Finally, let us prove~\ref{C4}. Suppose that $\alpha + \beta \in \Phi$. The required identity can be obtained as follows:
-\newline \scalebox{.84}{\begin{minipage}{1.17\linewidth}\begin{align*}
+\begin{align*}
 [x_{\alpha+\beta}(s),\ x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s),\ [x_{-\alpha}(-\epsilon t),\ x_{-\beta}(\xi)]]&\ \text{by~\eqref{Chevalley-CCF1}}\\
@@
 = [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2)  &\ \text{by~\eqref{Chevalley-CCF1}}.
-\qedhere \end{align*} \end{minipage}} \vskip \belowdisplayshortskip
+\qedhere \end{align*}
 \end{proof}
@@
  Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:
-\newline\scalebox{0.96}{\begin{minipage}{1.04\linewidth}
- \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]\end{minipage}}\vskip \belowdisplayshortskip
+
+ \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
  It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$.
@@
 \end{corollary}
-\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\cref{Crels}\ref{C4} we obtain that modulo 
+\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\cref{Crels}\ref{C4} we obtain that modulo the subgroup
  $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$.
@@
 Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we obtain that
-\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
-\[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1.
-\]\end{minipage}}
-\end{rem}
+\[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1. \] \end{rem}
 
@@
 \item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
-\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
 \begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = \hspace{4cm} \\ = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
@@
  = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
- = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}}\vskip \belowdisplayshortskip
+ = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}
 where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
@@
 The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
-\newline\scalebox{0.82}{\begin{minipage}{1.21\linewidth}
+
 \begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1 x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).
-\qedhere \end{multline*}\end{minipage}}
+\qedhere \end{multline*}
 \end{proof}
@@
 \begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
-\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}
  \begin{align} 
@@
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}.
-\nonumber \end{align}\end{minipage}}
+\nonumber \end{align}
 The assertion of the lemma now follows from the following computation:
-\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{align*}
+\begin{align*}
  S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
  = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
- = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}\end{minipage}}  \end{proof}
+ = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*} \end{proof}
 
@@
 Direct computation shows that
-\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{align*}
+\begin{align*}
  S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)&\text{ by~\cref{lem:Smult}} \\\
  = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle &\text{ by~\cref{lem:Tulenbaev-formula}.}
-\end{align*}\end{minipage}} \vskip \belowdisplayshortskip
+\end{align*}
 By \cref{P0_conj} and \cref{rem:DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$.
@@
 Since $x_{-\beta}(m'X) \in P_\alpha(0)$ we get that
-\newline\scalebox{.8}{\begin{minipage}{1.25\linewidth}\begin{align*}
+\newline\scalebox{.98}{\begin{minipage}{1.02\linewidth}\begin{align*}
   S_\alpha(a, g) = g_1 \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) & \text{ by~\cref{lem:Smult}} \\ 
@@
 Notice that $x_{-\beta}(m'X) \in P_\alpha(0)$, therefore from the definition of $S_\alpha(a, -)$ we obtain that
-\newline \scalebox{0.75}{\begin{minipage}{1.33\linewidth}
+\newline \scalebox{0.92}{\begin{minipage}{1.08\linewidth}
 \begin{align*}
@@
 Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
- \newline \scalebox{0.95}{\begin{minipage}{1.05\linewidth}\begin{multline} \nonumber
+ \begin{multline} \nonumber
   t_\alpha(aX^{-1})(v_1) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
   \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(v_2). \qedhere
- \end{multline}\end{minipage}}\end{proof}
+ \end{multline}\end{proof}
 
@@
  Now we can invoke~\eqref{T_1} once again and can continue~\eqref{add-computation} as follows:
- \newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{equation}\label{add-computation2}
-  \ldots = \left(x_\alpha((a + b)X^{-1})\cdot g ,\ \left[ h'' \cdot x_\alpha\left(\tfrac{-bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \right],\ u \cdot (1 + am) \cdot \left(1+\tfrac{bm}{1+am}\right)\right).\end{equation}\end{minipage}}\vskip \belowdisplayshortskip
+ \begin{equation}\label{add-computation2}
+  \ldots = \left(x_\alpha((a + b)X^{-1})\cdot g ,\ \left[ h'' \cdot x_\alpha\left(\tfrac{-bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \right],\ u \cdot (1 + am) \cdot \left(1+\tfrac{bm}{1+am}\right)\right).\end{equation}
  Notice that 
@@
 where $g' = x_\beta(-b) \cdot x_\alpha(-aX^{-1}) \cdot g$, $h' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot x_\beta(b_0)$.
-
 Notice that by~\eqref{eq:conj-h-x} $[h'] = [h'']$, where $h'' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0).$
@@
 Thus, we can invoke ~\eqref{T_1}--\eqref{T_leq0} once again and can continue~\eqref{R3leq0-computation} as follows:
-\newline\scalebox{0.84}{\begin{minipage}{1.16\linewidth}\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}\end{minipage}}\vskip \belowdisplayshortskip
+\begin{equation} \label{R3leq0-computation2} \ldots = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h'' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0)], u \right) = \left(g, [h], u\right), \end{equation}
 where in the last equality we use the following computation:
@@
 From~\eqref{T_1}--\eqref{T_leq0} and the fact that $x_\beta(Xf) \in P_\alpha(0)$ we obtain that
-\newline\scalebox{0.79}{\begin{minipage}{1.26\linewidth}
+\newline\scalebox{0.97}{\begin{minipage}{1.03\linewidth}
 \begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ [h],\ u\right) = \\ 
@@
 Notice that by~\cref{SR:sharp}
-\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]\end{minipage}}\vskip\belowdisplayshortskip
+\[ p\left(x_\alpha(aX^{-1})\cdot g, h', u(1 + am)\right) = S_\alpha(a, p(g, h, u)) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \in P_\beta(\tfrac{m'}{1+am}), \]
 therefore we can invoke~\eqref{T_1} once again and can continue~\eqref{R3_1_1-computation} as follows:
-\newline\scalebox{0.88}{\begin{minipage}{1.13\linewidth}
 \begin{equation}\label{R3_1_1-computation2} \ldots = \left(x_\beta(bX^{-1}) \cdot x_\alpha(aX^{-1}) \cdot g,\ \left[h' \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm'}{1+am}}\right)\right],\ u(1 + am + bm')\right).
-\end{equation}\end{minipage}}\vskip \belowdisplayshortskip
+\end{equation}
 The second component of the above triple can be simplified using~\eqref{eq:conj-h-x} as follows:
-\newline\scalebox{0.96}{\begin{minipage}{1.04\linewidth}
 \begin{multline*}
@@
  = \left[ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right)\right].
-\end{multline*}\end{minipage}}\vskip \belowdisplayshortskip
+\end{multline*}
 Thus, we see that the expression in the right-hand side of~\eqref{R3_1_1-computation2} would remain unchanged if we swapped $(a,\alpha,m)$ with $(b,\beta,m')$. This implies the required assertion.
@@
 From~\eqref{T_1}--\eqref{T_leq0} and~\eqref{eq:conj-h-x} we obtain that
-\newline\scalebox{0.9}{\begin{minipage}{1.1\linewidth}\begin{multline} \label{R2_0_1-computation}
+\begin{multline} \label{R2_0_1-computation}
 [T_\beta(b),\ T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
@@
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1})\cdot  g,\ [h'],\ u (1 - am) \right),
- \end{multline}\end{minipage}}\vskip\belowdisplayshortskip
+ \end{multline}
  where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$.
@@
 \begin{equation} \label{R2_0_1-computation2} \ldots = \left([x_\beta(b),\ x_\alpha(aX^{-1})]\cdot g,\ [h''],\ uc\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u), \end{equation} where the last equality is obtained from~\eqref{eq:conj-h-x} as follows:
-\newline\scalebox{0.8}{\begin{minipage}{1.2\linewidth}\begin{multline} \nonumber
+\begin{multline} \nonumber
  [h''] = \left[ h' \cdot x_\alpha\left(\tfrac{-aX^{-1}}{1+\tfrac{a(m-\epsilon bm')}{1-am}}\right) \cdot x_\beta(-b) \right] = \\ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \right] = \\
- = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].\end{multline}\end{minipage}}\vskip \belowdisplayshortskip
+ = \left[ h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \right]   = \\ = \left[ h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right) \right].\end{multline}
 The assertion of the lemma now follows from~\eqref{R2_0_1-computation}--\eqref{R2_0_1-computation2}.

### 2020-09-23 dl-paper.tex
Second version submitted to arxiv
Fix links on arxiv
Fix misprint

@@
 \documentclass[oneside, 8pt]{amsart}
+\pdfoutput=1
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
@@
 \usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
-\usepackage[breaklinks=false,unicode]{hyperref}
+\usepackage[breaklinks=true,unicode]{hyperref}
 \definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
@@
 
-For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
+For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the set consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
 \begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 

### 2020-09-23 dl-paper.tex

@@
 
-\newlist{proplist}{enumerate}{1} \setlist[proplist]{label=(\roman{proplisti}), ref=\thethm.(\roman{proplisti}),noitemsep} \Crefname{proplisti}{Proposition}{Propositions}
-\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelem.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
-
 \DeclareMathOperator{\Ker}{Ker}

### 2020-10-21 dl-paper.tex
Fix compilation
Fix display formulas

@@
 \DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\GG}{G}
 \DeclareMathOperator{\KO}{KO}
@@
 Indeed, we have the following chain of isomorphisms:
-\begin{multline} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \\ \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{multline}
+\begin{equation} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{equation}
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
@@
   \item $c_{\delta}(f, X\xi)$. \end{enumerate} \end{df}
-\begin{prop} \label{K-a-b} One has \[K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X).\] 
+\begin{prop} \label{K-a-b} One has $K(A[X], M[X]) = \widetilde{K}(\alpha, \beta) \cdot X_{-\alpha}(M \cdot X) \cdot X_{-\beta}(M \cdot X).$
 \end{prop} 
@@
  From~\eqref{T_1} we obtain that 
- \begin{multline}\label{add-computation}
-  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = \\ = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
- \end{multline}
+ \begin{equation}\label{add-computation}
+  T_\alpha(bX^{-1}) \cdot T_\alpha(aX^{-1}) (g, [h], u) = T_\alpha(bX^{-1}) \cdot \left(x_\alpha(aX^{-1})\cdot g ,\ \left[ h' \right],\ u \cdot (1 + am)\right),
+ \end{equation}
  where $h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)$.

### 2020-10-21 dl-paper.tex
Fix display formulas

@@
  From~\cref{prop43} and~\cref{lem:action} we obtain that
- \begin{multline} \nonumber [j_+(h_+)^{-1}, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1}) \cdot [1, h_-, 1] = \\ = j_R^{-1}(j_+(h_+)^{-1} \cdot j_-(h_-)) \cdot [1, 1, 1] = [1, 1, 1], \end{multline} therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$, $j_+(h_+) = j_+i_+(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
+ \begin{equation} \nonumber [j_+(h_+)^{-1}, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1}) \cdot [1, h_-, 1] = j_R^{-1}(j_+(h_+)^{-1} \cdot j_-(h_-)) \cdot [1, 1, 1] = [1, 1, 1], \end{equation} therefore, by the definition of~$\overline{V}_T$, $h_- = i_-(\gamma_1)$, $j_+(h_+) = j_+i_+(\gamma_1)$ for some $\gamma_1 \in G_M^0$.
 Since $j_+$ is injective we obtain that $h_+ = i_+(\gamma_1)$.

### 2021-02-10 dl-paper.tex
Fix misprints

@@
 Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $\lambda_R(c) = g(b)$. 
-By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$.
+By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, B, I)$.
 The required assertion now follows from the following calculation:
@@
 Denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$. 
-Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
+Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^{\pm 1}]$ and $A[X^{\pm 1}]\to R$:
 \[\begin{tikzcd}[scale cd=0.8]

### 2021-02-10 dl-paper.tex
Clearer sentence in lem:prop41

@@
 \begin{proof}
-Writing the starting portion of the homology long exact sequence for the homomorphism $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
-and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
+Writing down the starting portions of the homology long exact sequences for the homomorphisms $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$, $\St(\rD_\ell, B) \to \St(\rD_\ell, B/I)$ and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
 \[\begin{tikzcd} \KO_3(2\ell, B) \arrow{r} \arrow{d} & \KO_3(2\ell, k[X^{-1}]) \arrow{d}[swap]{f'} \ar[r, twoheadrightarrow] & \ar{d}[swap]{f} C(\rD_\ell, B, I) \\

### 2021-04-15 dl-paper.tex
Fix misprint

@@
 Indeed, we have the following chain of isomorphisms:
-\begin{equation} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{equation}
+\begin{equation} \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^{[2]}(k[X,X^{-1}]) \cong \GW_2^{[2]}(k) \oplus \GW_1^{[1]}(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\end{equation}
 in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.

### 2021-10-31 dl-paper.tex
Minor fixes

@@
 Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}.
-Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on an arbitrary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains of arithmetic type (see~\cite[Corollary~1.2]{St-Ded}).
+Recently A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on an arbitrary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ over a field (see~\cite[Theorem~1.2]{St-poly}) and also generalized Abe's result to Dedekind domains (see~\cite[Corollary~1.2]{St-Ded}).
 
@@
 
-Notice that the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
-\[ \begin{tikzcd} 1 \arrow{r} & \K_2(\rD_n, R) \arrow{r} & \KO_2(2n, R) \arrow{r} & \mu_2(R) \arrow{r} & 1, \end{tikzcd} \]
-which is obtained from~\eqref{eq:Bass-ES} and the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
+Notice that the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence of~\cite[Theorem~7.2.12]{HOM}:
+\[ \begin{tikzcd} 1 \arrow{r} & \K_2(\rD_n, R) \arrow{r} & \KO_2(2n, R) \arrow{r} & \mu_2(R) \arrow{r} & 1. \end{tikzcd} \]
+%which is obtained from~\eqref{eq:Bass-ES} and the snake lemma (cf.
+also with~\cite[Corollary~4.3.5]{Ba74}).
 On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.
@@
  $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ (see the beginning of~\cref{sec:elementary} for the definition of the elements $z_\gamma(m, \zeta)$ and the group $\overline{\St}(\Phi, A, M)$).
-It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \rtimes U(Z_+(\alpha), M). \]
+It is not hard to see that \[Z_\alpha(A, M) = \Img\left(\overline{\St}(Z_0(\alpha), A, M) \to \overline{\St}(\Phi, A, M)\right) \ltimes U(Z_+(\alpha), M). \]
 In the above formula $U(Z_+(\alpha), M)$ denotes the subgroup defined before~\cref{thm:Stein}.

### 2022-02-05 dl-paper.tex
Fix U-groups

@@
 For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following 4 groups:
-\begin{equation} \label{GW-concrete} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3.
+\begin{equation} \label{GW-concrete} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ {}_{-1}\!U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ U_i(R), & k = 3.
 \end{array}\right.

### 2023-02-22 dl-paper.tex
Fix minor issues

@@
 In the following lemma we recall the computation of the group $\K_2(\Phi, R)$ in the case $R=k[X, X\inv]$.
-\begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be an arbitrary field.
+\begin{lemma}[Hurrelbrink--Morita--Rehmann]\label{K2-laurent-field} Let $\Phi$ be a reduced irreducible root system and $k$ be an arbitrary field.
 Then there is a split exact sequence of abelian groups
 \[\begin{tikzcd} 0 \arrow{r} & \K_2(\Phi, k) \arrow{r} & \K_2(\Phi, k[X, X^{-1}]) \arrow{r} & H(\Phi, k) \arrow{r} & 0, \end{tikzcd}\text{ in which}\]
-\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ \K_1(k) \cong k^\times & \text{otherwise.}  \end{array}\right. \]  \end{lemma}
+The group $H(\Phi, k)$ admits the following description.
+One has $H(\Phi, k) \cong \K_1^\mathrm{M}(k) \cong k^\times$ if $\Phi$ is nonsymplectic.
+If $\Phi$ is symplectic and $\mathrm{char}(k)\neq 2$ then $H(\Phi, k) \cong \K_1^\mathrm{MW}(k)$.
+\end{lemma}
 \begin{proof} Let us first consider the case of nonsymplectic $\Phi$, in which one can find a long root $\alpha\in \Phi$ in such a way that there is a commutative diagram of abelian groups
@@
 Notice that the diagonal map is split by the obvious residue homomorphism and therefore is injective. This, in turn, implies that $h$ is also injective.
-The assertion of the lemma now follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi$ one has $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
+For $\Phi \neq \rG_2$ the assertion of the lemma follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi\neq\rG_2$ one has $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
+To obtain the assertion in the case $\Phi = \rG_2$ repeat the proof of~\cite[Satz~3]{Hur77} using \cite[Corollary~6]{AM88} instead \cite[Korollar~4]{Hur77}.
 
@@
 
-\begin{lemma} \label{field-injectivity} For $\Phi\neq\rG_2$ the homomorphism $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
+\begin{lemma} \label{field-injectivity} The homomorphism $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective.
 Moreover, the intersection of the images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$.

### 2023-02-22 dl-paper.tex
Fix typo

@@
 For $\Phi \neq \rG_2$ the assertion of the lemma follows from~\cite[Satz~3]{Hur77} which asserts that for a nonsymplectic $\Phi\neq\rG_2$ one has $\K_2(\Phi, k[X, X\inv]) = \mathrm{Im}(h) \oplus \K_2(\Phi, k)$.
-To obtain the assertion in the case $\Phi = \rG_2$ repeat the proof of~\cite[Satz~3]{Hur77} using \cite[Corollary~6]{AM88} instead \cite[Korollar~4]{Hur77}.
+To obtain the assertion in the case $\Phi = \rG_2$ repeat the proof of~\cite[Satz~3]{Hur77} using \cite[Corollary~6]{AM88} instead of \cite[Korollar~4]{Hur77}.
 
